### 2021-02-15 Thesis/article.tex
Initial commit

\documentclass[a4paper]{article}
\usepackage[margin=3cm]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{lipsum}
\newcommand{\todo}[1]{\textbf{\textcolor{red}{#1}}}
\title{Title}
\author{Johann Dorn}

\begin{document}
\maketitle
\iffalse
my notes
\fi

\section{Introduction}
scarce data may lead to overfitting\cite{Lecun1995conv}
\subsection{RAMAN}
\clearpage
\end{document}

### 2021-02-15 Input_DOE/get_exps.py

@@ -1,0 +1,19 @@
+import numpy as np
+np.set_printoptions(suppress=True)
+def get_exp(H,param):
+    n_exps=len(H)    # number of experiments
+    n_fact=len(H[0]) # number of factors
+    H_new=np.zeros((n_exps,n_fact))
+    for i_exps in range(n_exps):
+        for i_fact in range(n_fact):
+            if H[i_exps][i_fact] == 1:
+                H_new[i_exps][i_fact] = param["max"][i_fact]
+            else:
+                H_new[i_exps][i_fact] = param["min"][i_fact]
+    return H_new
+
+#def print_exp(H,param):
+def sort_exp(H,fact=0):
+    H_sorted = H[H[:,fact].argsort()]
+    return H_sorted
+

### 2021-02-15 Input_DOE/make_exps.py

@@ -1,0 +1,39 @@
+#!/usr/bin/python2
+import pyDOE as p
+import get_exps as get
+import numpy as np
+#""" define parameters and lower and upper limits"""
+head=["conc","nlay","Tcal","Tvel","vDOC","TDOC"]
+min=[1,4,400,60,0.1,20]
+max=[5,10,500,480,5,80]
+param={"head":head,"min":min,"max":max}
+factors=len(head)
+min2=[2,6,430,120,0.5,40]
+max2=[4,8,470,240,1,60]
+param2={"head":head,"min":min2,"max":max2}
+
+#""" choose disign pattern """
+#
+# 2-level full factorial
+#h=p.ff2n(factors)
+#
+# Plackett-Burman
+h=p.pbdesign(factors)
+#
+# 2-Level Fractional-Factorial
+#gen= "a +a b c d -d"
+#h=p.fracfact(gen)
+#print(h)
+#
+# real parameters
+h_new=get.get_exp(h,param)
+h_new2=get.get_exp(h,param2)
+h_all=np.concatenate((h_new,h_new2))
+#
+# print output
+#print(h_new)
+print(param["head"])
+print(get.sort_exp(h_new,-1))
+#print(get.sort_exp(h_new2,-1))
+print(get.sort_exp(h_all,-0))
+print(param["head"])

### 2021-02-15 Thesis/article.tex
thesis mail to theo about sol-gel process

@@
 
+Making of the solution for the sol-gel process:
+For a single concentrated solution 0.05 ml of Zr(IV)Propoxide are added while stirring to 4.95 ml of Buthan-1-ol and stirred for 15 minutes. 
+0.013 ml (or one molar equvilent of Zr) of Acetylacetone is added to the stirring solution.
+After another 15 minutes 1 ml of Aceteicacid is added and stirred for 30 minutes to stabilize the solution up to 24h.
+
+The concentration can be increased up to 5 times being stable for a minimum of 4 hours.
+The sol-gel process produces am homogeneous transparent crystalline zirconia oxide layer.
+homogeneity can be mainly controlled via blade velocity and temperature and layers can be stacked.
+
 \section{Introduction}

### 2021-03-22 Process/article.tex
process of DB added

\documentclass[a4paper]{article}
\usepackage[margin=3cm]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{lipsum}
\usepackage{ngerman}
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{url}
\usepackage{ragged2e} % to justify text
\newcommand{\todo}[1]{\textbf{\textcolor{red}{#1}}}
\newcommand{\td}[1]{\textbf{\textcolor{red}{#1}}}
\title{Doctor Blading of ZrO$_2$}
\author{Johann Dorn}

\begin{document}
\maketitle
\iffalse
my notes
\fi
\justify

\section{Cutting of the steel foil}
There is a red foil cutter in the vacuum room, which cuts the foil without much bending.
The foil is cut into 2.5 x 2.7 mm plates.
The small plates are marked with an diamond cutter pen.
The plates are cleaned with 1ml of Hellmanex III in 50-100 ml dion. water in the sonic bath for 15 min, then in dion. water for 15 min and finally in isopropanol for 15 min. 
The samples are dry blown with dry N$_2$ and stored until doctor blading.

\section{Solution}
The recipe for the solution was adapted from ref \cite{Hu2016}.
The standard concentration will be described first and then the differences of higher concentrated solutions:
4.9 ml of 1-buthanol (BuOH) are put into a beaker glass or similar while stirring. 
0.1 ml of zirconium(IV)propoxide solution (Zr(PrO)$_4$) are added and the time is written down. 
After 10 to 15 minutes 0.05 ml (approximately one mole equivalent of Zr(PrO)$_4$) acetylactate (AcAC) is added and stirred for another 10 to 15 minutes. 
Finally, 1 ml of isopropanol (IPO) is added to the mixture and stirred for additional 20-30 minutes. 
Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180. 
In order to make a double concentrated solution, the volume of Zr(PrO)$_4$ and AcAc is doubled and BoOH is decreased by the volume of Zr(PrO)$_4$.

\begin{table}[h]
	\centering
	\begin{tabular}{clllll}
		\hline
				&1F		&2F		&3F		&4F		&5F	\\
		\hline
		BuOH	&4.95	&4.9	&4.85	&4.8	&4.75	\\
		Zr(OPr)	&0.05	&0.1	&0.15	&0.2	&0.25	\\
		AcAc	&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
		IPO		&2		&2		&2		&2		&2		\\
		\hline
	\end{tabular}
\end{table}

\section{Doctor blading}
The temperature of the heating plate is set to 200 $^o$C.
The temperature is set and waited until reached.
The sample is placed on the vacuum plate and tested if it can be held by the under pressure.
The velocity is set and a mini test run is performed. 
The blade is put in position. 
100-125 $\mu$l of solution is applied with an 10-1000 $\mu$l pipette and the doctor blading is started immediately. 
After evaporation of the solution, the vacuum is turned of, the 'blade pusher' put into initial position, the blade removed and excess solution removed with a wipe. 
The small metal plate is transferred to the hot heating plate and rests on there for 3-5 min. 
The process is repeated as wished. 
\bibliographystyle{ieeetr}
\bibliography{fp}

\clearpage

\end{document}

### 2021-03-22 Process/article.tex
timestep 3 started

@@
 \documentclass[a4paper]{article}
-\usepackage[margin=3cm]{geometry}
+\usepackage[margin=2.5cm]{geometry}
 \usepackage{xcolor}
@@
 \newcommand{\td}[1]{\textbf{\textcolor{red}{#1}}}
-\title{Doctor Blading of ZrO$_2$}
+\title{ZrO$_2$ Layer via Doctor Blading }
 \author{Johann Dorn}
@@
 There is a red foil cutter in the vacuum room, which cuts the foil without much bending.
+Alternatively, the foil can be cut without bending by cutting repeatedly with a cutter knife.
 The foil is cut into 2.5 x 2.7 mm plates.
@@
 The standard concentration will be described first and then the differences of higher concentrated solutions:
-4.9 ml of 1-buthanol (BuOH) are put into a beaker glass or similar while stirring. 
-0.1 ml of zirconium(IV)propoxide solution (Zr(PrO)$_4$) are added and the time is written down. 
+4.9 ml of 1-buthanol (BuOH) are put into a beaker glass (or similar, preferably with cap) with a stirrer. 
+0.1 ml of zirconium(IV)propoxide solution (Zr(PrO)$_4$) are added while stirring.  
 After 10 to 15 minutes 0.05 ml (approximately one mole equivalent of Zr(PrO)$_4$) acetylactate (AcAC) is added and stirred for another 10 to 15 minutes. 
@@
 In order to make a double concentrated solution, the volume of Zr(PrO)$_4$ and AcAc is doubled and BoOH is decreased by the volume of Zr(PrO)$_4$. 
+The real concentration is not double of the original, though, but rather 1.7 fold because volume of IPO is kept constant.
 
@@
 		\hline
-		BuOH	&4.95	&4.9	&4.85	&4.8	&4.75	\\
-		Zr(OPr)	&0.05	&0.1	&0.15	&0.2	&0.25	\\
-		AcAc	&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
-		IPO		&2		&2		&2		&2		&2		\\
+		conc. [a.u.]	&1		&1.7	&2.6	&3.5	&4.4	\\
+		\hline
+		BuOH [ml]		&4.95	&4.9	&4.85	&4.8	&4.75	\\
+		Zr(OPr) [ml]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
+		AcAc [ml]		&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
+		IPO [ml]		&2		&2		&2		&2		&2		\\
 		\hline
@@
 The temperature of the heating plate is set to 200 $^o$C.
-The temperature is set and waited until reached.
+The temperature of the vacuum plate is set and waited until reached.
 The sample is placed on the vacuum plate and tested if it can be held by the under pressure.
@@
 
-\clearpage
+%\clearpage
 

### 2021-04-01 Process/article.tex
XRD added + process updated

@@
 \usepackage{ragged2e} % to justify text
+\usepackage{amsmath}
 \newcommand{\todo}[1]{\textbf{\textcolor{red}{#1}}}
@@
 The process is repeated as wished.
+
+\clearpage
+\section{evaluation of one sample}
+For every I-V curve (aluminium dot) the gradient $g$ at V=0 is calculated by taking 5 points after the origin and 5 points before the origin, averaging their V and I values and calculating i
+\begin{equation}
+	g = \frac{I_{n+1} - I_n}{V_{n+1} - V_n}.
+\end{equation}
+As a measure of conductance a distance D from an ideal non-conducting case. The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
+\begin{equation}
+	D = \sum_i^N \frac{ -log_{10}(g_i) - 13}{N}
+\end{equation}
+Another measure is the density of shorted species $\rho_{s}$ is calculated in following way:
+\begin{equation}
+	s_i = \begin{cases}
+	1 &\text{if} \quad -log(g_i) < 5 \\
+	0 &\text{if} \quad -log(g_i) \geq 5 \\
+	\end{cases}
+\end{equation}
+\begin{equation}
+	\rho_s = \sum_i^N \frac{s_i}{N}
+\end{equation}
+Another estimate of the conductance are the averages:
+\begin{equation}
+	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
+\end{equation}
+
+\begin{equation}
+	G_2 =  \sum_i^N \frac{log(g_i)}{N}
+\end{equation}
+
 \bibliographystyle{ieeetr}

### 2021-04-01 Code/ML/pred/find_best.py

@@ -5,18 +5,19 @@ def get_goodness(g,phd, layers, vCal):
     w=weights=[0.4,0.5,0.05, 0.05]
     return w[0]*g+ w[1]*phd+ w[2]*layers+ w[3]*vCal
 
-infile="allspace.test"
-names = ["nr", "conc", "layr", "vDOC", "vCal", "TCal", "G", "phd", "layers", "Cal_vel"]
+infile="allspace.dat"
+names = ["nr", "conc", "layr", "vDOC", "TDOC", "vCal", "TCal", "G", "phd", "layers", "Cal_vel"]
 df=pd.read_csv(infile, skiprows=1, delim_whitespace=True, names = names)
 #f = open(infile, 'r+')
+#print(df)
 bestvalues=0
 best_measure = np.inf
-fl=1
 for n in df.nr:
     i=n-1
+#    print(n,i)
     v = values = [ df.G[i], df.phd[i], df.layers[i], df.Cal_vel[i] ] 
-    print(best_measure,bestvalues)
     measure = get_goodness(float(v[0]), float(v[1]), float(v[2]), float(v[3]) )
+    print(i,best_measure,bestvalues,measure)
     if measure < best_measure:
         bestvalues=df.nr[i]
         best_measure = measure

### 2021-04-03 Process/article.tex
98 things go wrong in ML and copied process to thesis

@@
 \usepackage{lipsum}
-\usepackage{ngerman}
+%\usepackage{ngerman}
 \usepackage{pdfpages}
-\usepackage{hyperref}
-\usepackage{url}
 \usepackage{ragged2e} % to justify text
 \usepackage{amsmath}
+\usepackage{url}
+\usepackage{hyperref}
+\hypersetup{
+	colorlinks = true,
+	linkbordercolor = {white},
+	urlcolor = {blue},
+	linkcolor = {blue},
+	citecolor = {blue}
+}
 \newcommand{\todo}[1]{\textbf{\textcolor{red}{#1}}}
@@
 \section{Cutting of the steel foil}
+\label{sec:cut}
 There is a red foil cutter in the vacuum room, which cuts the foil without much bending.
@@
 \section{Solution}
+\label{sec:sol}
 The recipe for the solution was adapted from ref \cite{Hu2016}.
@@
 \section{Doctor blading}
+\label{sec:DB}
 The temperature of the heating plate is set to 200 $^o$C.
@@
 \section{evaluation of one sample}
+\label{sec:eval}
 For every I-V curve (aluminium dot) the gradient $g$ at V=0 is calculated by taking 5 points after the origin and 5 points before the origin, averaging their V and I values and calculating i
@@
 	D = \sum_i^N \frac{ -log_{10}(g_i) - 13}{N}
+	\label{eq:D}
 \end{equation}
@@
 	\rho_s = \sum_i^N \frac{s_i}{N}
+	\label{eq:rho}
 \end{equation}
-Another estimate of the conductance are the averages:
+Other estimates of the conductance are the averages:
 \begin{equation}
@@
 
+\section{Sample Selection}
+\label{sec:ss}
+An evolutionary approach was chosen, namely a multi-objective Particle Swarm Optimization (PSO) with a multi-response
+Multivariate Adaptive Regression Splines (MARS) model\cite{Villanova2010,Kennedy1995,Breiman1997,Carta2011}.
+%
+"PSO is a population based heuristic inspired by the flocking behavior of birds. 
+To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{Villanova2010}
+%
+Initially the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
+Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
+%
+%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
+\begin{table}[htb]
+	\centering
+	\begin{tabular}{cc cc cc}
+		\hline
+		Zr(PrO)$_4$ conc. [21 g/L]	&layers	&$T_{DB}$[$^o$C]	&$v_{DB}$[mm/s]	&$T_{cal}$[$^o$C]	&$v_{cal}$[$^o$C/hour]	\\
+		\hline
+		2				&4		&40					&10				&300				&120	\\
+		3				&6		&50					&12				&400				&360	\\
+		4				&8		&60					&14				&500				&600	\\
+		5				&10		&70					&16				&					&840	\\
+						&12		&80					&18				&					&1080	\\
+						&		&					&20				&					&		\\
+		\hline
+	\end{tabular}
+	\caption{Discrete levels of each input parameter}
+	\label{tab:input}
+\end{table}
+
+The first step is to select an initial population (ensemble of experiments), which is chosen randomly from the population space. 
+The samples are made, measured and evaluated according to sections \ref{sec:cut}-\ref{sec:eval} and the distance $D$ (see eq.
+\ref{eq:D}), $\rho_s$ (see eq.
+\ref{eq:rho}), $n_{layers}$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in $^o$C/min) are supplied to the program.
+The program uses this data to estimate a response for each output variable (and to choose a fraction of the initial population which is allowed to propagate).
+The response variables for the entire population space is calculated. 
+The current population - each of the particles independently - moves towards the optimum solution.
+The population for the next time step is outputted and the experiments are again executed, measured and evaluated.
+
 \bibliographystyle{ieeetr}
-\bibliography{fp}
+\bibliography{int}
 

### 2021-04-03 Thesis/article.tex
98 things go wrong in ML and copied process to thesis

@@
 \usepackage{lipsum}
+\usepackage{amsmath}
+\usepackage{pdfpages}
+\usepackage{url}
+\usepackage{hyperref}
+\hypersetup{
+	colorlinks = true,
+	linkbordercolor = {white},
+	urlcolor = {blue},
+	linkcolor = {blue},
+	citecolor = {blue}
+}
+\usepackage{acronym}
+\usepackage[acronym,nomain]{glossaries}
+\makeglossaries
 \newcommand{\todo}[1]{\textbf{\textcolor{red}{#1}}}
-\title{Title}
+\newcommand{\td}[1]{\textbf{\textcolor{red}{#1}}}
+
+\title{Functional oxide layers for electrical isolation and chemical passivation of steel substrates}
 \author{Johann Dorn}
@@
 \fi
+%\begin{acronym}
+	\newacronym{nemo}{amat}{dolorem}
+	\newacronym{zrpro}{Zr(PrO)$_4$}{zirconium(IV)propoxide}
+	\newacronym{acac}{Hacac}{acetylacetone}
+	\newacronym{acoh}{AcOH}{acetic acid}
+%\end{acronym}
+
+\printglossaries
+\section{Preface}
+some 
+\Ac{abktag}
+\gls{nemo}
+worlds
+\Ac{abktag}
+adsf
+
+\section{Introduction}
+\section{Aims and Objectives}
+\section{Experimental}
+\subsection{Substrate Preparation}
+\subsection{Cutting of the steel foil}
+\subsection{Solution Preperation}
+\label{sec:cut}
+There is a red foil cutter in the vacuum room, which cuts the foil without much bending.
+Alternatively, the foil can be cut without bending by cutting repeatedly with a cutter knife.
+The foil is cut into 2.5 x 2.7 mm plates.
+The small plates are marked with an diamond cutter pen.
+The plates are cleaned with 1ml of Hellmanex III in 50-100 ml dion. water in the sonic bath for 15 min, then in dion. water for 15 min and finally in isopropanol for 15 min. 
+The samples are dry blown with dry N$_2$ and stored until doctor blading.
+
+\subsection{Solution}
+Two main recipes were used and the ingridients varied. 
+The first recipe was adopted from Ref. \cite{Anwar2017} was based on \gls{zrpro} in 
+\subsubsection{Aquatic solution}
+\subsubsection{Buthanolic solution}
+\label{sec:sol}
+The recipe for the solution was adapted from ref \cite{Hu2016}.
+The standard concentration will be described first and then the differences of higher concentrated solutions:
+4.9 ml of 1-buthanol (BuOH) are put into a beaker glass (or similar, preferably with cap) with a stirrer. 
+0.1 ml of zirconium(IV)propoxide solution (Zr(PrO)$_4$) are added while stirring.  
+After 10 to 15 minutes 0.05 ml (approximately one mole equivalent of Zr(PrO)$_4$) acetylactate (AcAC) is added and stirred for another 10 to 15 minutes. 
+Finally, 1 ml of isopropanol (IPO) is added to the mixture and stirred for additional 20-30 minutes. 
+Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180. 
+In order to make a double concentrated solution, the volume of Zr(PrO)$_4$ and AcAc is doubled and BoOH is decreased by the volume of Zr(PrO)$_4$. 
+The real concentration is not double of the original, though, but rather 1.7 fold because volume of IPO is kept constant.
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{clllll}
+		\hline
+				&1F		&2F		&3F		&4F		&5F		\\
+		\hline
+		conc. [a.u.]	&1		&1.7	&2.6	&3.5	&4.4	\\
+		\hline
+		BuOH [ml]		&4.95	&4.9	&4.85	&4.8	&4.75	\\
+		Zr(OPr) [ml]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
+		AcAc [ml]		&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
+		IPO [ml]		&2		&2		&2		&2		&2		\\
+		\hline
+	\end{tabular}
+\end{table}
+
+\subsection{Doctor blading}
+\label{sec:DB}
+The temperature of the heating plate is set to 200 $^o$C.
+The temperature of the vacuum plate is set and waited until reached.
+The sample is placed on the vacuum plate and tested if it can be held by the under pressure.
+The velocity is set and a mini test run is performed. 
+The blade is put in position. 
+100-125 $\mu$l of solution is applied with an 10-1000 $\mu$l pipette and the doctor blading is started immediately. 
+After evaporation of the solution, the vacuum is turned of, the 'blade pusher' put into initial position, the blade removed and excess solution removed with a wipe. 
+The small metal plate is transferred to the hot heating plate and rests on there for 3-5 min. 
+The process is repeated as wished.
+
+\section{Evaluation and Computational Details}
+\subsection{Evaluation of Samples}
+\label{sec:eval}
+For every I-V curve (aluminium dot) the gradient $g$ at V=0 is calculated by taking 5 points after the origin and 5 points before the origin, averaging their V and I values and calculating i
+\begin{equation}
+	g = \frac{I_{n+1} - I_n}{V_{n+1} - V_n}.
+\end{equation}
+As a measure of conductance a distance D from an ideal non-conducting case. The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
+\begin{equation}
+	D = \sum_i^N \frac{ -log_{10}(g_i) - 13}{N}
+	\label{eq:D}
+\end{equation}
+Another measure is the density of shorted species $\rho_{s}$ is calculated in following way:
+\begin{equation}
+	s_i = \begin{cases}
+	1 &\text{if} \quad -log(g_i) < 5 \\
+	0 &\text{if} \quad -log(g_i) \geq 5 \\
+	\end{cases}
+\end{equation}
+\begin{equation}
+	\rho_s = \sum_i^N \frac{s_i}{N}
+	\label{eq:rho}
+\end{equation}
+Other estimates of the conductance are the averages:
+\begin{equation}
+	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
+\end{equation}
+
+\begin{equation}
+	G_2 =  \sum_i^N \frac{log(g_i)}{N}
+\end{equation}
+
+\subsection{Sample Selection}
+\label{sec:ss}
+An evolutionary approach was chosen, namely a multi-objective Particle Swarm Optimization (PSO) with a multi-response
+Multivariate Adaptive Regression Splines (MARS) model\cite{Villanova2010,Kennedy1995,Breiman1997,Carta2011}.
+%
+"PSO is a population based heuristic inspired by the flocking behavior of birds. 
+To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{Villanova2010}
+%
+Initially the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
+Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
+%
+%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
+\begin{table}[htb]
+	\centering
+	\begin{tabular}{cc cc cc}
+		\hline
+		Zr(PrO)$_4$ conc. [21 g/L]	&layers	&$T_{DB}$[$^o$C]	&$v_{DB}$[mm/s]	&$T_{cal}$[$^o$C]	&$v_{cal}$[$^o$C/hour]	\\
+		\hline
+		2				&4		&40					&10				&300				&120	\\
+		3				&6		&50					&12				&400				&360	\\
+		4				&8		&60					&14				&500				&600	\\
+		5				&10		&70					&16				&					&840	\\
+						&12		&80					&18				&					&1080	\\
+						&		&					&20				&					&		\\
+		\hline
+	\end{tabular}
+	\caption{Discrete levels of each input parameter}
+	\label{tab:input}
+\end{table}
+
+The first step is to select an initial population (ensemble of experiments), which is chosen randomly from the population space. 
+The samples are made, measured and evaluated according to sections \ref{sec:cut}-\ref{sec:eval} and the distance $D$ (see eq.
+\ref{eq:D}), $\rho_s$ (see eq.
+\ref{eq:rho}), $n_{layers}$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in $^o$C/min) are supplied to the program.
+The program uses this data to estimate a response for each output variable (and to choose a fraction of the initial population which is allowed to propagate).
+The response variables for the entire population space is calculated. 
+The current population - each of the particles independently - moves towards the optimum solution.
+The population for the next time step is outputted and the experiments are again executed, measured and evaluated.
+
+scarce data may lead to overfitting\cite{Lecun1995conv}
+\section{Results and Discussion}
+\section{Outlook}
 
@@
 0.013 ml (or one molar equvilent of Zr) of Acetylacetone is added to the stirring solution. 
-After another 15 minutes 1 ml of Aceteicacid is added and stirred for 30 minutes to stabilize the solution up to 24h.
+After another 15 minutes 1 ml of acetic acid is added and stirred for 30 minutes to stabilize the solution up to 24h.
 
@@
 
-\section{Introduction}
-scarce data may lead to overfitting\cite{Lecun1995conv}
-\subsection{RAMAN}
 \clearpage
+\bibliographystyle{ieeetr}
+\bibliography{int}
 \end{document}

### 2021-04-18 Thesis/article.tex
added emma table

@@
 	colorlinks = true,
+	colorlinks = false,
 	linkbordercolor = {white},
@@
 \newcommand{\td}[1]{\textbf{\textcolor{red}{#1}}}
+\newcommand{\me}[1]{\textbf{\textcolor{gray}{#1}}}
+\newcommand{\ds}[1]{}
+\newcommand{\oc}{$^o$C}
 
@@
 %\begin{acronym}
-	\newacronym{nemo}{amat}{dolorem}
+%	\newacronym{nemo}{amat}{dolorem}
 	\newacronym{zrpro}{Zr(PrO)$_4$}{zirconium(IV)propoxide}
@@
 	\newacronym{acoh}{AcOH}{acetic acid}
+	\newacronym{buoh}{BuOH}{1-buthanol}
+	\newacronym{ipo}{IPO}{2-Propanol}
+	\newacronym{ito}{ITO}{indium doped tin oxide}
+	\newacronym{fto}{FTO}{fluorine doped tin oxide}
+	\newacronym{n2}{N$_2$}{nitrogen}
+	\newacronym{water}{H$_2$O}{deionized water}
+	\newacronym{sds}{SDS}{sodium dodecyl sulfate}
+	\newacronym{hcl}{HCl}{hydrochloric acid}
+	\newacronym{h2so4}{H$_2$SO$_4$}{sulfuric acid}
+	\newacronym{naoh}{NaOH}{sodium hydroxide}
+	\newacronym{zro}{ZrO$_2$}{zirconium dioxide}
+	\newacronym{1f}{1F}{one-fold concentrated solution}
+	\newacronym{2f}{2F}{two-fold concentrated solution}
+	\newacronym{3f}{3F}{three-fold concentrated solution}
+	\newacronym{4f}{4F}{four-fold concentrated solution}
+	\newacronym{5f}{5F}{five-fold concentrated solution}
 %\end{acronym}
 
+%\clearpage
 \printglossaries
+%\clearpage
+%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Preface}
-some 
-\Ac{abktag}
-\gls{nemo}
-worlds
-\Ac{abktag}
-adsf
+%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Aims and Objectives}
+was hab ich gemacht, warum? 
+Defensio: Argumente in der Arbeit noch mal sichten, Feedback von Betreuungsperson im Kopf haben - da könnten Fragen kommen, 
+sich selbst aufnehmen
 
-\section{Introduction}
-\section{Aims and Objectives}
+Präsentieren: Visualisierungen sinnvoll? 
+Antworten überlegen/Argumente überlegen
+Limitation, Rahmen der Arbeit
+Begründung für die eigene Vorgehensweise
+%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIMENTAL
 \section{Experimental}
+\label{sec:exp}
+In this section the used chemicals and substrates, experimental procedures and any used equipment are described. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Substrate Preparation}
+Five different substrates were used throughout this work: 
+microscope glass slides (2.5~cm~x~7.5~cm) \td{from where}, thinner, squared glass plates (2.5~cm~x~2.5~cm) \td{from where}, \gls{ito} glass plates (2.5~cm~x 2.5~cm) \td{from where}, \gls{fto} glass plates (5~cm~x~5~cm) from \td{Sigma Aldrich} and steel foil (10~cm~x~10~cm) \td{provided by Sunplugged~(\url{http://sunplugged.at/)}}.
+The glass slides and \gls{fto} were cut with a \td{diamond scratcher} and broken with a \td{glass breaker} into pieces of dimensions 2.5~cm~x~2.5~cm.
+The steel foil was cut with a foil cutter\me{, a cutter knife repeatedly, a paper cutter or a scissors (ordered by increasing curvature of resulting slides)}.
+All substrates were cleaned in three steps before usage:
+\begin{enumerate}
+	\item 15 minutes in 50 ml \gls{water} and 1 ml of Hellmanex III in a sonic bath
+	\item 15 minutes in \gls{water} in a sonic bath
+	\item 15 minutes in \gls{ipo} in a sonic bath 
+\end{enumerate}
+After the last cleaning step, the samples were dry blown with dry \gls{n2} gas.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\iffalse
 \subsection{Cutting of the steel foil}
-\subsection{Solution Preperation}
 \label{sec:cut}
@@
 The small plates are marked with an diamond cutter pen.
-The plates are cleaned with 1ml of Hellmanex III in 50-100 ml dion. water in the sonic bath for 15 min, then in dion. water for 15 min and finally in isopropanol for 15 min. 
+The plates are cleaned with 1ml of Hellmanex III in 50-100 ml \gls{water} in the sonic bath for 15 min, then in \gls{water} for 15 min and finally in \gls{ipo} for 15 min. 
 The samples are dry blown with dry N$_2$ and stored until doctor blading.
-
+\fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Solution}
-Two main recipes were used and the ingridients varied. 
-The first recipe was adopted from Ref. \cite{Anwar2017} was based on \gls{zrpro} in 
+Two main recipes were used and their ingredients were varied. 
+The first recipe - adopted from Anwar et. al. \cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} 
+and the second recipe - 
+adopted from Hu et. al. \cite{Hu2016} -
+was based on \gls{zrpro} in \gls{buoh}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Aquatic solution}
+The procedure for the aquatic solution is as follows: 
+While stirring \gls{zrpro} is added to \gls{acac} and \gls{water} (including any additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) is added to \gls{ipo} in two separate vessels and stirred for 1 hour.
+The \gls{water}-\gls{ipo} mixture is added to the other solution and stirred over night. 
+The exact volumes can be taken from table \ref{tab:rec1}.
+\begin{table}[h]
+	\centering
+	\caption{}
+	\label{tab:rec1}
+	\begin{tabular}{llllllll}
+		\hline
+		recipe				&1		&2		&3		&4		&5		&6		&7\\
+%		\hline
+%		conc. [a.u.]	&1		&1.7	&2.6	&3.5	&4.4	\\
+		\hline
+		\gls{zrpro} [ml]	&8		&8		&8		&8		&8		&8		&8\\
+		\gls{acac} [ml]		&8		&8		&8		&8		&8		&8		&8\\
+		\gls{ipo} [ml]		&2		&2		&2		&2		&2		&2		&2\\
+		\gls{water} [ml]		&2.6	&2.6	&2.5	&2		&2		&2		&2\\
+		\gls{sds} [mg]		&-		&5.9	&-		&-		&-		&-		&-\\
+		\gls{hcl} [ml]		&-		&-		&-		&-		&0.5	&-		&-\\
+		\gls{h2so4} [ml]	&-		&-		&-		&-		&-		&0.5	&-\\
+		\gls{naoh} [ml] 	&-		&-		&-		&-		&-		&-		&0.5\\
+		\hline
+	\end{tabular}
+\end{table}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Buthanolic solution}
 \label{sec:sol}
-The recipe for the solution was adapted from ref \cite{Hu2016}.
-The standard concentration will be described first and then the differences of higher concentrated solutions:
-4.9 ml of 1-buthanol (BuOH) are put into a beaker glass (or similar, preferably with cap) with a stirrer. 
-0.1 ml of zirconium(IV)propoxide solution (Zr(PrO)$_4$) are added while stirring.  
-After 10 to 15 minutes 0.05 ml (approximately one mole equivalent of Zr(PrO)$_4$) acetylactate (AcAC) is added and stirred for another 10 to 15 minutes. 
-Finally, 1 ml of isopropanol (IPO) is added to the mixture and stirred for additional 20-30 minutes. 
+%The recipe for the solution was adapted from ref \cite{Hu2016}.
+Five different concentration were prepared. 
+%The first solution \td{(standard concentration/ one fold/ 1F)} 
+%followed the recipe loosely, which is described by Hu et al. \cite{Hu2016}.
+%In order to obtain thicker \gls{zro} layers the \gls{zrpro} concentration in the starting solution was raised.
+The \gls{1f}
+%one-fold concentrated solution (1F) 
+was closest to the recipe proposed by Hu et. al. \cite{Hu2016}. 
+The other four solutions (\gls{2f}, \gls{3f}, \gls{4f}, \gls{5f}) were similar with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2}).
+The procedure for obtaining the \gls{1f} solution will be explained in detail:
+%
+%was closely on the basis of ref \cite{Hu2016}. 
+%The standard concentration will be described first and then the differences of higher concentrated solutions:
+4.9 ml of solvent (\gls{buoh}) are put into a beaker glass (or similar, preferably with cap) with a stirrer. 
+0.1 ml of \gls{zrpro} are added while stirring.  
+After 10 to 15 minutes 0.05 ml (\ds{approximately }one mole equivalent of \gls{zrpro}) chelating agent (\gls{acac}) is added and stirred for another 10 to 15 minutes. 
+Finally, 1 ml of stabilisation solvent (\gls{ipo} or \gls{acoh}) is added to the mixture and stirred for additional 20-30 minutes. 
 Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180. 
-In order to make a double concentrated solution, the volume of Zr(PrO)$_4$ and AcAc is doubled and BoOH is decreased by the volume of Zr(PrO)$_4$. 
-The real concentration is not double of the original, though, but rather 1.7 fold because volume of IPO is kept constant.
+In order to make a 
+%double concentrated 
+\gls{2f}
+solution, the volume of \gls{zrpro} and \gls{acac} is doubled and \gls{buoh} is decreased by the volume of \gls{zrpro}. 
+The real concentration is not double of the original, though, but rather 1.7 fold because volume of \gls{ipo} is kept constant.
 
@@
 	\centering
-	\begin{tabular}{clllll}
+	\caption{}
+	\label{tab:rec2}
+	\begin{tabular}{rlllll}
 		\hline
@@
 		\hline
-		BuOH [ml]		&4.95	&4.9	&4.85	&4.8	&4.75	\\
-		Zr(OPr) [ml]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
-		AcAc [ml]		&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
-		IPO [ml]		&2		&2		&2		&2		&2		\\
+		\gls{buoh} [ml]		&4.95	&4.9	&4.85	&4.8	&4.75	\\
+		\gls{zrpro} [ml]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
+		\gls{acac} [ml]		&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
+		\gls{ipo}/\gls{acoh} [ml]		&2		&2		&2		&2		&2		\\
 		\hline
@@
 The process is repeated as wished.
+
+\subsection{Calcination}
+A LabTech EH45 C heating plate and a Naberterm \td{L B410} furnace were used to calcinate the doctor bladed samples. 
+The heating plate heated with a steady rate of \td{2} $^o$C/min. 
+In order to achieve a lower overall heating rate several temperature ramps and plateaus were \todo{used}. See table~\ref{tab:labtech}
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{rl ll ll ll ll ll ll }%ll ll ll ll ll ll ll}
+%			&temp [\oc]	&time/rate &temp [\oc]	&time/rate	&temp [\oc]\\
+		HP1		&&&&&&&&&&&&&\\
+		\hline
+		T [\oc]	&80		&100	&150	&160	&170 	&180	&190	&200	&250	&300	&350	&400	\\
+		t [min]	&10 	&10		&5 		&5 		&5 		&5 &5 &10 &10 &10 &10 &60 \\
+		\hline
+	\end{tabular}
+	\caption{Time the temperature was held constant at certain temperatures on the heatingplate}
+	\label{tab:labtech}
+\end{table}
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
+%			&temp [\oc]	&time/rate &temp [\oc]	&time/rate	&temp [\oc]\\
+		HP1		&&&&&\\%&&&&&&&&\\
+		\hline
+		T [\oc]				&80		&150	&200	&400	&400 	\\
+		$\theta$ [\oc/min]	&10 	&10		&5 		&5		& 		\\
+		\hline
+		name	&80-150 [\oc/min]	&150-200 [\oc/min]	&200-T$_{max}$ [\oc/min]	&T$_{max}$ [min]	&T$_{max}$ [\oc] \\
+		NT1		&2					&1					&2					&60 &400 \\
+		NT2		&2					&2					&2					&60 &400 \\
+		NT3		&3					&3					&3					&60 &400 \\
+		NT4		&4					&4					&4					&60 &400 \\
+		NT5		&4					&4					&4					&60 &500 \\
+		NT6		&1					&1					&1					&60 &400 \\
+		NT7		&max				&max				&max				&60 &600 \\
+		\hline
+	\end{tabular}
+	\caption{Heating rates and constant temperature times. \td{Macht dieser Graph ueberhaupt sinn? }}
+	\label{tab:nt}
+\end{table}
+
+\subsection{EMMA Propagation}
+\begin{table}
+	\centering
+	\begin{tabular}{ccccccc}
+		\hline
+		\hline
+conc	&layers	&vDOC	&TDOC	&vCal	&Tcal	&	\\
+		\hline
+1	&10	&5	&20	&120	&400	&\\
+1	&4	&0.1	&20	&120	&500	&\\
+5	&10	&0.1	&20	&120	&500	&\\
+5	&4	&5	&20	&480	&400	&\\
+1	&5	&5	&80	&120	&500	&\\
+1	&10	&1	&80	&480	&400	&\\
+5	&5	&1	&80	&120	&400	&\\
+5	&10	&5	&80	&480	&500	&\\
+2	&8	&0.5	&40	&360	&470	&\\
+2	&6	&2	&40	&360	&430	&\\
+		\hline
+%4	&12	&-	&-	&-	&-&\\
+1	&4	&12	&70	&120	&500	&\\
+1	&9	&18	&80	&240	&400	&\\
+%2	&5	&18	&70	&-	&-		&\\
+4	&6	&14	&60	&240	&500	&\\
+4	&6	&14	&60	&240	&500	&\\
+4	&6	&14	&60	&240	&500	&\\
+		\hline
+2	&10	&20	&40	&120	&500	&6113\\
+3	&8	&18	&70	&1080	&300	&2850\\
+3	&6	&10	&50	&1080	&400	&5526	\\
+%3	&10	&14	&50	&600	&500	&-7374	\\
+3	&10	&16	&80	&120	&500	&6554	\\
+4	&6	&16	&80	&1080	&300	&2947	\\
+3	&12	&12	&80	&840	&500	&8318	\\
+3	&10	&14	&50	&600	&500	&7374	\\
+5	&6	&10	&60	&1080	&400	&5648	\\
+5	&10	&20	&60	&360	&300	&3956	\\
+5	&12	&14	&60	&1080	&300	&2700	\\
+		\hline
+%2	&2	&10	&40	&600	&300	&-7201	\\
+2	&4	&10	&80	&1080	&300	&6101	\\
+%2	&4	&10	&40	&600	&300	&-7201	\\
+2	&4	&10	&40	&600	&300	&7201	\\
+3	&4	&12	&60	&600	&300	&1462	\\
+4	&4	&10	&80	&1080	&300	&2883	\\
+5	&12	&20	&70	&600	&300	&1680	\\
+		\hline
+2	&4	&10	&40	&120	&300	&1	\\
+2	&4	&10	&40	&120	&500	&6001	\\
+3	&4	&10	&40	&120	&500	&6102	\\
+5	&4	&10	&80	&1080	&300	&2884	\\
+5	&12	&20	&60	&120	&300	&360	\\
+		\hline
+3	&4	&10	&40	&600	&400	&4202	\\
+2	&6	&20	&40	&120	&500	&6105	\\
+%4	&4	&14	&80	&1080	&300	&-2923	\\
+5	&12	&14	&60	&600	&300	&1500	\\
+3	&6	&14	&60	&600	&300	&1486	\\
+4	&4	&14	&80	&1080	&300	&2923	\\
+		\hline
+4	&8	&18	&80	&1080	&300	&2971	\\
+3	&8	&10	&50	&1080	&300	&2530	\\
+2	&12	&16	&40	&120	&400	&3077	\\
+2	&10	&18	&60	&1080	&300	&2733	\\
+4	&10	&10	&50	&1080	&300	&2535	\\
+		\hline
+		\hline
+	\end{tabular}
+	\caption{}
+	\label{tab:emma}
+\end{table}
 
@@
 	\end{tabular}
-	\caption{Discrete levels of each input parameter}
+	\caption{Discrete levels of each input parameter \td{are concentrations correct?}}
 	\label{tab:input}
@@
 The first step is to select an initial population (ensemble of experiments), which is chosen randomly from the population space. 
-The samples are made, measured and evaluated according to sections \ref{sec:cut}-\ref{sec:eval} and the distance $D$ (see eq.
+The samples are made, measured and evaluated according to section \ref{sec:exp} and the distance $D$ (see eq.
 \ref{eq:D}), $\rho_s$ (see eq.
@@
 \section{Results and Discussion}
+The space seems to be too big for the small sample size.
+Look at relation of space size and sample size here and in Hu2016.
 \section{Outlook}
@@
 Making of the solution for the sol-gel process:
-For a single concentrated solution 0.05 ml of Zr(IV)Propoxide are added while stirring to 4.95 ml of Buthan-1-ol and stirred for 15 minutes. 
-0.013 ml (or one molar equvilent of Zr) of Acetylacetone is added to the stirring solution. 
+For a single concentrated solution 0.05 ml of \gls{zrpro} are added while stirring to 4.95 ml of \gls{buoh} and stirred for 15 minutes. 
+0.013 ml (or one molar equvilent of Zr) of \gls{acac} is added to the stirring solution. 
 After another 15 minutes 1 ml of acetic acid is added and stirred for 30 minutes to stabilize the solution up to 24h.
@@
 
-\clearpage
+%\clearpage
 \bibliographystyle{ieeetr}

### 2021-04-18 Thesis/article.tex
erichsen

@@
 	\newacronym{5f}{5F}{five-fold concentrated solution}
+	\newacronym{db}{DB}{doctor blading}
 %\end{acronym}
@@
 \section{Introduction}
+\td{describe everything what is meantioned in \ref{sec:exp}}
 %%%%%%%%%
@@
 Five different substrates were used throughout this work: 
-microscope glass slides (2.5~cm~x~7.5~cm) \td{from where}, thinner, squared glass plates (2.5~cm~x~2.5~cm) \td{from where}, \gls{ito} glass plates (2.5~cm~x 2.5~cm) \td{from where}, \gls{fto} glass plates (5~cm~x~5~cm) from \td{Sigma Aldrich} and steel foil (10~cm~x~10~cm) \td{provided by Sunplugged~(\url{http://sunplugged.at/)}}.
-The glass slides and \gls{fto} were cut with a \td{diamond scratcher} and broken with a \td{glass breaker} into pieces of dimensions 2.5~cm~x~2.5~cm.
-The steel foil was cut with a foil cutter\me{, a cutter knife repeatedly, a paper cutter or a scissors (ordered by increasing curvature of resulting slides)}.
+microscope glass slides (2.5~cm~x~7.5~cm) \td{from where}, thinner, squared glass plates (2.5~cm~x~2.5~cm) \td{from where}, \gls{ito} glass plates (2.5~cm~x 2.5~cm) \td{from where}, \gls{fto} glass plates (5~cm~x~5~cm) from \td{Sigma Aldrich} and steel foil (10~cm~x~10~cm) \td{provided by Sunplugged GmbH (\url{http://sunplugged.at/)}}.
+The glass slides and \gls{fto} were cut\td{/scratched} with a \td{diamond scratcher/scraper} and broken with a \td{glass breaker} into pieces of dimensions 2.5~cm~x~2.5~cm.
+The steel foil was cut with a foil cutter\me{, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting slides)}.
 All substrates were cleaned in three steps before usage:
@@
 \subsection{Solution}
-Two main recipes were used and their ingredients were varied. 
+Two main recipes were used and their \td{ingredients/compositions} were varied. 
 The first recipe - adopted from Anwar et. al. \cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} 
@@
 \subsubsection{Aquatic solution}
-The procedure for the aquatic solution is as follows: 
+\me{The procedure for the aquatic solution is as follows:}
 While stirring \gls{zrpro} is added to \gls{acac} and \gls{water} (including any additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) is added to \gls{ipo} in two separate vessels and stirred for 1 hour.
@@
 \label{sec:sol}
+\td{make recipe general}
 %The recipe for the solution was adapted from ref \cite{Hu2016}.
@@
 %In order to obtain thicker \gls{zro} layers the \gls{zrpro} concentration in the starting solution was raised.
-The \gls{1f}
+The \gls{1f} \td{(one fold (1F) solution /or/ one fold solution (1F))}
 %one-fold concentrated solution (1F) 
@@
 The other four solutions (\gls{2f}, \gls{3f}, \gls{4f}, \gls{5f}) were similar with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2}).
-The procedure for obtaining the \gls{1f} solution will be explained in detail:
+The procedure for obtaining the \gls{1f} solution will be explained in detail: \td{maybe just keep it general}
 %
@@
 %The standard concentration will be described first and then the differences of higher concentrated solutions:
-4.9 ml of solvent (\gls{buoh}) are put into a beaker glass (or similar, preferably with cap) with a stirrer. 
+4.9 ml of solvent (\gls{buoh}) are put into a beaker glass (or similar, preferably with \td{an air-tight} cap) with a stirrer. 
 0.1 ml of \gls{zrpro} are added while stirring.  
@@
 \label{sec:DB}
+\begin{figure}
+	\centering
+	\includegraphics[width=.8\textwidth]{Pics/erichsen.png}
+	\caption{Erichsen Coatmaster 510 
+		%Doctor blading machine 
+		with vacuum pump in the background and temperature regulator on the left.}
+	\label{fig:eric}
+\end{figure}
+\td{picture of the machine, and name of the machine}
 The temperature of the heating plate is set to 200 $^o$C.
 The temperature of the vacuum plate is set and waited until reached.
-The sample is placed on the vacuum plate and tested if it can be held by the under pressure.
-The velocity is set and a mini test run is performed. 
+The sample is placed on the vacuum plate and tested if it can be \td{held/retained} by the underpressure.
+The velocity of the \gls{db} blade is set and a mini test run is performed. 
 The blade is put in position. 

### 2021-04-18 Thesis/article.tex
buOH solution general

@@
 The other four solutions (\gls{2f}, \gls{3f}, \gls{4f}, \gls{5f}) were similar with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2}).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\iffalse
 The procedure for obtaining the \gls{1f} solution will be explained in detail: \td{maybe just keep it general}
@@
 Finally, 1 ml of stabilisation solvent (\gls{ipo} or \gls{acoh}) is added to the mixture and stirred for additional 20-30 minutes. 
+\fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The solvent (\gls{buoh}) is put into a beaker glass (or similar, preferably with \td{an air-tight} cap) with a stirrer and \gls{zrpro} is added while stirring.  
+After 10 to 15 minutes one mole equivalent chelating agent (\gls{acac}) is added and stirred for another 10 to 15 minutes. 
+Finally, the stabilisation solvent (\gls{ipo} or \gls{acoh}) is added to the mixture and stirred for additional 20-30 minutes. 
 Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180. 
-In order to make a 
-%double concentrated 
-\gls{2f}
-solution, the volume of \gls{zrpro} and \gls{acac} is doubled and \gls{buoh} is decreased by the volume of \gls{zrpro}. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In order to make a \gls{2f} solution, the volume of \gls{zrpro} and \gls{acac} is doubled and \gls{buoh} is decreased by the volume of \gls{zrpro}. 
 The real concentration is not double of the original, though, but rather 1.7 fold because volume of \gls{ipo} is kept constant.

### 2021-04-21 Thesis/article.tex
thesis powersession

--- 2021-04-18 Thesis/article.tex
@@
 \usepackage{hyperref}
+\usepackage{subcaption}
 \hypersetup{
@@
 
-%\clearpage
+\clearpage
 \printglossaries
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIMENTAL
+\section{Theoretical Background aka How does is work?}
+\subsection{Sputtering}
+\subsection{SEM}
+\subsection{Infrared absorbance}
+
 \section{Experimental}
@@
 Five different substrates were used throughout this work: 
-microscope glass slides (2.5~cm~x~7.5~cm) \td{from where}, thinner, squared glass plates (2.5~cm~x~2.5~cm) \td{from where}, \gls{ito} glass plates (2.5~cm~x 2.5~cm) \td{from where}, \gls{fto} glass plates (5~cm~x~5~cm) from \td{Sigma Aldrich} and steel foil (10~cm~x~10~cm) \td{provided by Sunplugged GmbH (\url{http://sunplugged.at/)}}.
-The glass slides and \gls{fto} were cut\td{/scratched} with a \td{diamond scratcher/scraper} and broken with a \td{glass breaker} into pieces of dimensions 2.5~cm~x~2.5~cm.
-The steel foil was cut with a foil cutter\me{, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting slides)}.
+microscope glass slides (2.5~cm~x~7.5~cm) \td{from Sigma Aldrich}, thinner, squared glass plates (2.5~cm~x~2.5~cm) \td{from Sigma Aldrich}, \gls{ito} glass plates (2.5~cm~x 2.5~cm) \td{from Sigma Aldrich}, \gls{fto} glass plates (5~cm~x~5~cm) from \td{Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
+The glass slides and \gls{fto} were \ds{cut\td{/scratched}}scratched with a scratching tool \ds{\td{(diamond scratcher/scraper)} }and broken with a \td{glass breaker} into pieces with dimensions 2.5~cm~x~2.5~cm.
+The steel foil was cut with a foil cutter, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
 All substrates were cleaned in three steps before usage:
@@
 \subsection{Solution}
-Two main recipes were used and their \td{ingredients/compositions} were varied. 
+Two main recipes were used and their compositions were varied. 
 The first recipe - adopted from Anwar et. al. \cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} 
@@
 was based on \gls{zrpro} in \gls{buoh}.
+
+%\iffalse
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		%\includegraphics[width=.99\textwidth]{Pics/sol-aq.png}
+		\includegraphics[height=0.8\textwidth]{Pics/sol-aq.png}
+		\label{fig:sol-aq}
+		\caption{Aquatic solution}
+	\end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		%\includegraphics[width=.99\textwidth]{Pics/sol-bu.png}
+		\includegraphics[height=0.8\textwidth]{Pics/sol-bu.png}
+		\label{fig:sol-bu}
+		\caption{Buthanolic solution}
+	\end{subfigure}
+	\label{fig:sol}
+	\caption{Aquatic and buthanolic solution in beaker glass sealed with Parafilm}
+\end{figure}
+%\fi
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \me{The procedure for the aquatic solution is as follows:}
-While stirring \gls{zrpro} is added to \gls{acac} and \gls{water} (including any additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) is added to \gls{ipo} in two separate vessels and stirred for 1 hour.
-The \gls{water}-\gls{ipo} mixture is added to the other solution and stirred over night. 
+\gls{zrpro} was added to \gls{acac} while stirring and in a seperate vessel \gls{water} (including any additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) was added to \gls{ipo} and both were stirred for 1 hour.
+The \gls{water}-\gls{ipo} mixture was added to the other solution and stirred over night. 
 The exact volumes can be taken from table \ref{tab:rec1}.
@@
 \label{sec:sol}
-\td{make recipe general}
-%The recipe for the solution was adapted from ref \cite{Hu2016}.
 Five different concentration were prepared. 
@@
 %In order to obtain thicker \gls{zro} layers the \gls{zrpro} concentration in the starting solution was raised.
-The \gls{1f} \td{(one fold (1F) solution /or/ one fold solution (1F))}
-%one-fold concentrated solution (1F) 
+The \gls{1f} 
 was closest to the recipe proposed by Hu et. al. \cite{Hu2016}. 
 The other four solutions (\gls{2f}, \gls{3f}, \gls{4f}, \gls{5f}) were similar with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2}).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\iffalse
 The procedure for obtaining the \gls{1f} solution will be explained in detail: \td{maybe just keep it general}
@@
 %The standard concentration will be described first and then the differences of higher concentrated solutions:
-4.9 ml of solvent (\gls{buoh}) are put into a beaker glass (or similar, preferably with \td{an air-tight} cap) with a stirrer. 
+4.9 ml of solvent (\gls{buoh}) are put into a beaker glass (or similar, preferably with an air-tight cap) with a stirrer. 
 0.1 ml of \gls{zrpro} are added while stirring.  
@@
 Finally, 1 ml of stabilisation solvent (\gls{ipo} or \gls{acoh}) is added to the mixture and stirred for additional 20-30 minutes. 
+\fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The solvent (\gls{buoh}) is put into a beaker glass (or similar, preferably with an air-tight cap) with a stirrer and \gls{zrpro} is added while stirring.  
+After stirring 10 to 15 minutes one mole equivalent chelating agent (\gls{acac}) is added and stirred for another 10 to 15 minutes. 
+Finally, the stabilisation solvent\cite{Hu2016} (\gls{ipo} or \gls{acoh}) is added to the mixture and stirred for additional 20-30 minutes. 
 Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180. 
-In order to make a 
-%double concentrated 
-\gls{2f}
-solution, the volume of \gls{zrpro} and \gls{acac} is doubled and \gls{buoh} is decreased by the volume of \gls{zrpro}. 
-The real concentration is not double of the original, though, but rather 1.7 fold because volume of \gls{ipo} is kept constant.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In order to make a \gls{2f} solution, the volume of \gls{zrpro} and \gls{acac} is doubled and \gls{buoh} is decreased by the volume of \gls{zrpro}. 
+The real concentration of a \gls{2f} solution is not double of the original, though, but rather 1.7 fold because volume of \gls{ipo} is kept constant.
 
@@
 \end{table}
+
+\subsection{Characterisation}
+\subsubsection{SEM}
+Zeiss Supra 40
+\subsubsection{Infrared}
+Bruker Vertex 70
+\subsubsection{X-Ray Defraction}
+Thermo Scientific ARL Equinox 100 X-Ray Diffractometer
+\subsubsection{Current-Voltage Curve}
+Agilent 4156C Precision Semiconductor Parameter Analyzer
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.48\textwidth}
+		\centering
+		\includegraphics[width=.9\textwidth]{Pics/i-v.png}
+		\label{fig:iv-agilent}
+		\caption{peripherals}
+	\end{subfigure}
+	\begin{subfigure}{0.48\textwidth}
+		\centering
+		\includegraphics[width=.9\textwidth]{Pics/i-v-micro.png}
+		\label{fig:iv-micro}
+		\caption{View through the microscope}
+	\end{subfigure}
+	\label{fig:iv}
+	\caption{I-V curve abnehm aperature and sicht durch das micro scope.}
+\end{figure}
 
@@
 Look at relation of space size and sample size here and in Hu2016.
+
+Would be easier to fit with single factor at a time variation or latin hyper cuber?
+Would it also be easier for PSO or ML to find fitting function?
+Every output var is independent of each other, so $v_{cal}$ can act as test
+
 \section{Outlook}

### 2021-04-21 Thesis/makefile.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+basename=article
+pdflatex $basename.tex
+bibtex $basename.aux
+makeglossaries $basename

### 2021-05-03 Thesis/article.tex
tried to make prediction data file

@@
 \end{figure}
-\td{picture of the machine, and name of the machine}
 The temperature of the heating plate is set to 200 $^o$C.
 The temperature of the vacuum plate is set and waited until reached.
-The sample is placed on the vacuum plate and tested if it can be \td{held/retained} by the underpressure.
-The velocity of the \gls{db} blade is set and a mini test run is performed. 
+The sample is placed on the vacuum plate and the vacuum is switched on. 
+The velocity of the \gls{db} blade is set and it is %\td{a mini test run is performed.} 
+tested if the sample can be retained in place by the under-pressure.
 The blade is put in position. 
+\td{After setting the heating plate temperature, the vacuum plate temperature (see figure \ref{fig:eric}) and the \gls{db} velocity, the \gls{db} blade is set up and the sample placed on the vacuum plate.
+The vacuum is switched on and the blade is sent over the sample without liquid to see if it is held in position.}
 100-125 $\mu$l of solution is applied with an 10-1000 $\mu$l pipette and the doctor blading is started immediately. 
@@
 
+\iffalse
 \subsection{EMMA Propagation}
@@
 \end{table}
+\fi
 
@@
 
-scarce data may lead to overfitting\cite{Lecun1995conv}
+\subsection{EMMA Propagation}
+\begin{table}[htb]
+	\centering
+	\begin{tabular}{ccccccc}
+		\hline
+		\hline
+conc	&layers	&vDOC	&TDOC	&vCal	&Tcal	&	\\
+		\hline
+1	&10	&5	&20	&120	&400	&\\
+1	&4	&0.1	&20	&120	&500	&\\
+5	&10	&0.1	&20	&120	&500	&\\
+5	&4	&5	&20	&480	&400	&\\
+1	&5	&5	&80	&120	&500	&\\
+1	&10	&1	&80	&480	&400	&\\
+5	&5	&1	&80	&120	&400	&\\
+5	&10	&5	&80	&480	&500	&\\
+2	&8	&0.5	&40	&360	&470	&\\
+2	&6	&2	&40	&360	&430	&\\
+		\hline
+%4	&12	&-	&-	&-	&-&\\
+1	&4	&12	&70	&120	&500	&\\
+1	&9	&18	&80	&240	&400	&\\
+%2	&5	&18	&70	&-	&-		&\\
+4	&6	&14	&60	&240	&500	&\\
+4	&6	&14	&60	&240	&500	&\\
+4	&6	&14	&60	&240	&500	&\\
+		\hline
+2	&10	&20	&40	&120	&500	&6113\\
+3	&8	&18	&70	&1080	&300	&2850\\
+3	&6	&10	&50	&1080	&400	&5526	\\
+%3	&10	&14	&50	&600	&500	&-7374	\\
+3	&10	&16	&80	&120	&500	&6554	\\
+4	&6	&16	&80	&1080	&300	&2947	\\
+3	&12	&12	&80	&840	&500	&8318	\\
+3	&10	&14	&50	&600	&500	&7374	\\
+5	&6	&10	&60	&1080	&400	&5648	\\
+5	&10	&20	&60	&360	&300	&3956	\\
+5	&12	&14	&60	&1080	&300	&2700	\\
+		\hline
+%2	&2	&10	&40	&600	&300	&-7201	\\
+2	&4	&10	&80	&1080	&300	&6101	\\
+%2	&4	&10	&40	&600	&300	&-7201	\\
+2	&4	&10	&40	&600	&300	&7201	\\
+3	&4	&12	&60	&600	&300	&1462	\\
+4	&4	&10	&80	&1080	&300	&2883	\\
+5	&12	&20	&70	&600	&300	&1680	\\
+		\hline
+2	&4	&10	&40	&120	&300	&1	\\
+2	&4	&10	&40	&120	&500	&6001	\\
+3	&4	&10	&40	&120	&500	&6102	\\
+5	&4	&10	&80	&1080	&300	&2884	\\
+5	&12	&20	&60	&120	&300	&360	\\
+		\hline
+3	&4	&10	&40	&600	&400	&4202	\\
+2	&6	&20	&40	&120	&500	&6105	\\
+%4	&4	&14	&80	&1080	&300	&-2923	\\
+5	&12	&14	&60	&600	&300	&1500	\\
+3	&6	&14	&60	&600	&300	&1486	\\
+4	&4	&14	&80	&1080	&300	&2923	\\
+		\hline
+4	&8	&18	&80	&1080	&300	&2971	\\
+3	&8	&10	&50	&1080	&300	&2530	\\
+2	&12	&16	&40	&120	&400	&3077	\\
+2	&10	&18	&60	&1080	&300	&2733	\\
+4	&10	&10	&50	&1080	&300	&2535	\\
+		\hline
+		\hline
+	\end{tabular}
+	\caption{}
+	\label{tab:emma}
+\end{table}
+
+\td{scarce data may lead to overfitting\cite{Lecun1995conv}}
+
+\subsection{Fitting via Machine Learning}
+Python and sci-kit learn \td{cite} was used to implement a linear fit model, and SVR with the kernels polynomial, rbf and sigmoid. 
+The space of hyper parameters C, the degree (in case of polynomial), epsilon and gamma was scaned.
+
+\clearpage
 \section{Results and Discussion}
@@
 Every output var is independent of each other, so $v_{cal}$ can act as test
+
+plot predictions from EMMA and ML.
 

### 2021-05-03 Code/EMMA/xspace.R

@@ -1,3 +1,4 @@
 source("inter.R")
-load("t0")
-t0$xspace
+load("t4")
+t4$xspace
+t4$yspace

### 2021-05-03 Code/ML/fit2.py

@@ -33,7 +33,6 @@ def get_sets(df,nr):
     tmax=int(ndatapoints*4/5)
     ttmin = tmax                   # test  minimum index
     ttmax=ndatapoints
-    
 
     trainx1 = conc[tmin:tmax].to_numpy()
     trainx2 = layr[tmin:tmax].to_numpy()

### 2021-05-03 Code/conc.py

@@ -1,0 +1,14 @@
+V_zrs=[50,100,150,200,250]          # ul
+rho=0.001044   # g/ul
+beta=0.7    # %
+rho_n=rho*beta
+for V_zr in V_zrs:
+    V_hacac=V_zr/4                  # ul
+    V_buoh=5000-V_zr                # ul
+    V_ipo=2000                      # ul
+    V=V_zr+V_hacac+V_buoh+V_ipo     # ul
+    m=rho*beta*V_zr                 # g/ul*ul=g
+    c=m/V*1000*1000                 # g/L
+    if V_zr == V_zrs[0]:
+        const=c
+    print(V_zr,V,c,c/const)

### 2021-05-03 Data/Predictions/EMMA/getdata.sh

@@ -27,11 +27,11 @@ part=$all
 head -n1 $filename 
 
 tail -n $(($lines-1)) $filename > $ffpp-1 & \
-	sort -hk $layrk $ffpp-1 > $ffpp-2 && part=$(($part/$layrlvl)) && head -n $(($part*1)) $ffpp-2 | tail -n $part > $ffpp-3 && \
+	sort -hk $layrk $ffpp-1 > $ffpp-2 && part=$(($part/$layrlvl)) && head -n $(($part*5)) $ffpp-2 | tail -n $part > $ffpp-3 && \
 	sort -hk $vdock $ffpp-3 > $ffpp-4 && part=$(($part/$vdoclvl)) && head -n $(($part*1)) $ffpp-4 | tail -n $part > $ffpp-5 && \
-	sort -hk $tdock $ffpp-5 > $ffpp-6 && part=$(($part/$tdoclvl)) && head -n $(($part*2)) $ffpp-6 | tail -n $part > $ffpp-7 && \
+	sort -hk $tdock $ffpp-5 > $ffpp-6 && part=$(($part/$tdoclvl)) && head -n $(($part*1)) $ffpp-6 | tail -n $part > $ffpp-7 && \
 	sort -hk $vcalk $ffpp-7 > $ffpp-8 && part=$(($part/$vcallvl)) && head -n $(($part*1)) $ffpp-8 | tail -n $part > $ffpp-9 && \
-	sort -hk $tcalk $ffpp-9 > $ffpp-0 && part=$(($part/$tcallvl)) && head -n $(($part*1)) $ffpp-0
+	sort -hk $tcalk $ffpp-9 > $ffpp-0 && part=$(($part/$tcallvl)) && head -n $(($part*2)) $ffpp-0 | tail -n $part 
 
 rm $ffpp-1
 rm $ffpp-2

### 2021-05-03 Thesis/makefile.sh
thesis.tex renamed

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-basename=article
+basename=thesis
 pdflatex $basename.tex
 bibtex $basename.aux
 makeglossaries $basename

### 2021-07-25 Code/ML/pca.py
pca started

@@ -1,0 +1,101 @@
+import math
+import numpy as np 
+#import sklearn.svm  as skl
+from sklearn.svm import SVR
+from sklearn.kernel_ridge import KernelRidge as KRR
+from sklearn.preprocessing import StandardScaler
+from sklearn.pipeline import make_pipeline
+from sklearn.utils import shuffle
+import pandas as pd
+
+infile="stat2.dat"
+names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
+df=pd.read_csv(infile, skiprows=1, delim_whitespace=True, names = names)
+df= shuffle(df)
+def get_MAE(y,ypred):
+    return (np.average(np.absolute(y-ypred)))
+def get_sets(df,nr):
+    names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
+    df=pd.read_csv(infile, skiprows=1, delim_whitespace=True, names = names)
+    conc = df.conc
+    layr = df.layers
+    vDoc = df.vDOC
+    TDoc = df.TDOC
+    vCal = df.vCal
+    TCal = df.TCal
+    G = df.conductivity
+    phd = df.phdensity
+    layers = df.layers
+    Cal_vel = df.vCal
+    
+    ndatapoints=len(conc)
+    tmin=0                      # train minimum index
+    tmax=int(ndatapoints*4/5)
+    ttmin = tmax                   # test  minimum index
+    ttmax=ndatapoints
+
+    trainx1 = conc[tmin:tmax].to_numpy()
+    trainx2 = layr[tmin:tmax].to_numpy()
+    trainx3 = vDoc[tmin:tmax].to_numpy()
+    trainx4 = TDoc[tmin:tmax].to_numpy()
+    trainx5 = vCal[tmin:tmax].to_numpy()*60
+    trainx6 = TCal[tmin:tmax].to_numpy()
+    trainy1 = G[tmin:tmax].to_numpy()
+    trainy2 = phd[tmin:tmax].to_numpy()
+    trainy3 = layr[tmin:tmax].to_numpy()
+    trainy4 = vCal[tmin:tmax].to_numpy()
+
+    testx1 = conc[ttmin:ttmax].to_numpy()
+    testx2 = layr[ttmin:ttmax].to_numpy()
[…]

### 2021-07-27 Code/ML/pca.py
pca added and tool names gefestigt

@@ -1,101 +1,0 @@
-import math
-import numpy as np 
-#import sklearn.svm  as skl
-from sklearn.svm import SVR
-from sklearn.kernel_ridge import KernelRidge as KRR
-from sklearn.preprocessing import StandardScaler
-from sklearn.pipeline import make_pipeline
-from sklearn.utils import shuffle
-import pandas as pd
-
-infile="stat2.dat"
-names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
-df=pd.read_csv(infile, skiprows=1, delim_whitespace=True, names = names)
-df= shuffle(df)
-def get_MAE(y,ypred):
-    return (np.average(np.absolute(y-ypred)))
-def get_sets(df,nr):
-    names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
-    df=pd.read_csv(infile, skiprows=1, delim_whitespace=True, names = names)
-    conc = df.conc
-    layr = df.layers
-    vDoc = df.vDOC
-    TDoc = df.TDOC
-    vCal = df.vCal
-    TCal = df.TCal
-    G = df.conductivity
-    phd = df.phdensity
-    layers = df.layers
-    Cal_vel = df.vCal
-    
-    ndatapoints=len(conc)
-    tmin=0                      # train minimum index
-    tmax=int(ndatapoints*4/5)
-    ttmin = tmax                   # test  minimum index
-    ttmax=ndatapoints
-
-    trainx1 = conc[tmin:tmax].to_numpy()
-    trainx2 = layr[tmin:tmax].to_numpy()
-    trainx3 = vDoc[tmin:tmax].to_numpy()
-    trainx4 = TDoc[tmin:tmax].to_numpy()
-    trainx5 = vCal[tmin:tmax].to_numpy()*60
-    trainx6 = TCal[tmin:tmax].to_numpy()
-    trainy1 = G[tmin:tmax].to_numpy()
-    trainy2 = phd[tmin:tmax].to_numpy()
-    trainy3 = layr[tmin:tmax].to_numpy()
-    trainy4 = vCal[tmin:tmax].to_numpy()
-
-    testx1 = conc[ttmin:ttmax].to_numpy()
-    testx2 = layr[ttmin:ttmax].to_numpy()
[…]

### 2021-07-27 Code/PCA/pca.py

@@ -1,0 +1,30 @@
+import math
+import numpy as np 
+import pandas as pd
+from sklearn.preprocessing import StandardScaler
+from sklearn.decomposition import PCA
+
+infile="db_final.dat"
+names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
+df=pd.read_csv(infile, skiprows=1, names = names)
+#df= shuffle(df)
+#print(df.head(2))
+#print(df.shape)
+
+x = StandardScaler().fit_transform(df) # normalizing 
+x = x[:,2:]
+#print(x.shape)
+#print(np.mean(x),np.std(x))
+#print(names)
+#print(x[0])
+pca_obj= PCA()
+pca_fit = pca_obj.fit_transform(x)
+#pca_df = pd.DataFrame(data = pca_fit, columns = ['pc1', 'pc2', 'pc3', 'pc4', 'pc5'])
+pca_df = pd.DataFrame(data = pca_fit)
+#print(pca_df.tail())
+pca_ratios = pca_obj.explained_variance_ratio_
+print('Explained variation per PC: {}'.format(pca_ratios))
+print(sum(pca_ratios))
+print(names[2:])
+print(pca_obj.components_[:5])
+exit

### 2021-08-13 Code/PCA/linreg.py
minor thoughts added

@@ -3,7 +3,7 @@ import numpy as np
 import pandas as pd
 from sklearn.linear_model import LinearRegression
 
-infile="db_final.dat"
+infile="db_final.csv"
 names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
 df=pd.read_csv(infile, skiprows=1, names = names)
 data=np.array(df)

### 2021-08-13 Code/PCA/pca.py

@@ -4,7 +4,7 @@ import pandas as pd
 from sklearn.preprocessing import StandardScaler
 from sklearn.decomposition import PCA
 
-infile="db_final.dat"
+infile="db_final.csv"
 names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
 df=pd.read_csv(infile, skiprows=1, names = names)
 #df= shuffle(df)

### 2021-09-07 Data/I-V/mytou.sh
before my was exchanged with u (problem in reading i-v curves)

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+for dir in I-V*;  do
+    pushd $dir
+    for file in  *L*C*; do 
+        sed -i "s/µ/u/" $file
+    done
+    popd
+done
+

### 2021-09-07 Data/I-V/stat.avg.py

@@ -12,12 +12,16 @@ def get_conductance(filename):
     n_comments=40
     print(filename)
     for r in range(n_comments):
+#        print(r)
         try:
-            df=pd.read_csv(filename,"\t",header=r,names=("V","I","i","J","j"))
+            #df=pd.read_csv(filename,sep="\t",header=r,names=("V","I","i","J","j"))
+            #df=pd.read_csv(filename,sep="\t",header=0,names=("V","I","absI","J","jcm"))
+            df=pd.read_csv(filename,sep="\t",names=("V","I","absI","J","jcm"))
         except:
             pass
-            #print("could not read",filename)
+            print("could not read",filename)
         else:
+            print(df)
             i=0             #first 
             j=len(df)-1     #last
             #TODO find pos at which V=0
@@ -38,6 +42,7 @@ def get_conductance(filename):
                     iup=iup + float(df["I"][i])
                 dv= vup-vdown
                 di= iup-idown
+                print(dv,di)
                 i=i+1
                 j=j-1
             R = dv/di
@@ -83,17 +88,46 @@ def make_stat(G):
     avg=avg/n
     lavg=lavg/n
     return msd,holes,avg,lavg
+
+def get_last_iteration(filenames):
+    subset=[]
+    position_list=[]
+    count_list=[]
+    for filename in filenames: 
+        try:
+            position,count=filename.split("_0")
+        except:
+            continue
+        if (position in position_list):
+            #position_index = [i for i,pos in enumerate(position_list) if pos = position]
+            index = position_list.index(position)
+            if ( count_list[index] < count): 
+                subset[index] = filename
+                count_list[index] = count
+        else:
+            subset.append(filename)
+            position_list.append(position)
+            count_list.append(count)
+        
+#    return subset
+    return [subset[0]]
+
+
     
 
 #######################
 def main():
     sample_name,no = get_sample_name()
     files=get_files(sample_name)
+    files=get_last_iteration(files)
+#    print(files)
     Gs=[]
     for filename in files:
         G=get_conductance(filename)
+    #    print(G)
         Gs.append(G)
     msd,holes,avg,lavg=make_stat(Gs)
+    #print(msd,holes,avg,lavg)
     print(f"{sample_name:s}\t{no:s}\t{msd:.5f}\t{holes:.5f}\t{avg:.5f}\t{lavg:.5f}")
 
 if __name__ == "__main__":

### 2021-12-12 Code/Input_DOE/make_exps.py
changed from python2 to python3

@@ -1,4 +1,4 @@
-#!/usr/bin/python2
+#!/usr/bin/python3
 import pyDOE as p
 import get_exps as get
 import numpy as np

### 2021-12-12 Thesis/chapter/aims-and-objectives.tex
thesis split into chapters

The aim of this work is to develop a non-conducting layer on steel based on  non-toxic materials like aluminium or zirconium via doctor blading. 
This layer can then be used as insulator for CIGS modules on steel sheets.
Doctor blading - or tape casting - is a widely used precision coating method to apply thin films on large area surfaces\cite{Berni2004}.
%The method of doctor blading, which is in principle a sol-gel process, 
This sol-gel process was chosen over spin coating because of the availability to the 
industrial partner.
In order to optimize the resulting layer the multitude of parameters was optimized with an particle swarm optimization ansatz. %machine learning 
The conductivity (dependent variable), the number of layers and calcination time (both independent variables) should be minimized.
%The conductivity should be as small as possible.
%The number of layers should be held small and the calcination heating rate should be maximized. 
\iffalse
Defensio: Argumente in der Arbeit noch mal sichten, Feedback von Betreuungsperson im Kopf haben - da könnten Fragen kommen, 
sich selbst aufnehmen

Präsentieren: Visualisierungen sinnvoll? 
Antworten überlegen/Argumente überlegen
Limitation, Rahmen der Arbeit
Begründung für die eigene Vorgehensweise
\fi

### 2021-12-12 Thesis/chapter/experimental.tex
thesis split into chapters

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec:exp}
%\subsection{finding a solution}
%\subsection{finding process variables}
In this section the used chemicals and substrates, experimental procedures and any used 
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
The experiments can be split into three sections: 
In the first section the base recipe and the base process were sought. 
In the pre-optimisation section the boundaries for the optimisation were investigated. 
And during the third and final step the experiments for the optimisation were performed.
\subsection{Substrate Preparation}
Five different substrates were used throughout this work: 
microscope glass slides (\cm{2.5}\x\cm{7.5})\ds{ from Sigma Aldrich},\ds{ thinner,} squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squwares fo the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Solutions}
%Two main recipes were used and their compositions were varied. 
All recipes for solutions can be divided into two categories:
the first recipe - adopted from Anwar et. al. \cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water}.
The second recipe - adopted from Hu et. al. \cite{Hu2016} - was based on \gls{zrpro} in \gls{buoh}.

\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[height=0.8\textwidth]{Pics/sol-aq.png}
		\label{fig:sol-aq}
		\caption{Aquatic solution}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[height=0.8\textwidth]{Pics/sol-bu.png}
		\label{fig:sol-bu}
		\caption{Buthanolic solution}
	\end{subfigure}
	\label{fig:sol}
	\caption{Aquatic and buthanolic solution with magnetic stirring bars in beaker glass sealed with Parafilm} 
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Aquatic solution}
\gls{zrpro} was added to \gls{acac} while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to \gls{ipo} and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the resulting layer.
The \gls{water}-\gls{ipo} mixture was added to the other solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
Unfortunately, this solution failed to produce anything near homogeneous solutions. 
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aquatic solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Buthanolic solution}
\label{sec:sol}
Five different concentrations of the buthanolic solutions were prepared. 
The \gls{1f} was closest to the recipe proposed by Hu et. al. \cite{Hu2016}. 
The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar with 
higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
Not all chemicals mentioned in \cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
%\td{p34}
Different solvents (Butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before the 
\gls{pso} started - the stabilisation compound (\gls{acoh}) was changed to \gls{ipo}.
The most promissing combination of solvent, chelating agent and stabilisation reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, which was used for the final optimisation.
The main differences between the used recipe and mentioned by \cite{Hu2016} were 
precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
complex aluminium isopropoxide), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%DB          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[h]
	\centering
	\caption{}
	\label{tab:rec2}
	\begin{tabular}{rlllll}
		\hline
		recipe	&1F		&2F		&3F		&4F		&5F		\\
		\hline
		\gls{buoh} [\ml{}]		&4.95	&4.9	&4.85	&4.8	&4.75	\\
		\gls{zrpro} [\ml{}]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
		\gls{acac} [\ml{}]		&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
		\gls{ipo}/\gls{acoh} [\ml{}]		&2		&2		&2		&2		&2		\\
		\hline
	\end{tabular}
\end{table}

The solvent (\gls{buoh}) was put into a beaker glass (or similar, preferably with an 
air-tight cap) with a magnetic stirring bar and \gls{zrpro} was added while stirring. After 
stirring \minutes{\ds{10 to }15} one mole equivalent chelating agent (\gls{acac}) was 
added and stirred for another \minutes{\ds{10 to }15}. Finally, the stabilisation 
solvent\cite{Hu2016} (\gls{ipo} or \gls{acoh}) was added to the mixture and stirred for 
additional \minutes{\ds{20-}30}. 
In order to make a \gls{2f} solution, the volume of \gls{zrpro} and \gls{acac} was 
doubled and the volume of \gls{buoh} was decreased by the increase of volume of \gls{zrpro}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Doctor blading}
\label{sec:DB}
All glass substrates were doctor bladed manually with a smooth stainless steel wire bar 
coater. On two opposing edges adhesive tape was applied to create a valley in between. After the 
layer was applied and dried the tape was removed and the substrate treated with heat.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} wasn't altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

%Most steel substrates (all pre-optimisation and optimisation samples) 
All steel substrates 
were doctor bladed with 
an Erichsen Coatmaster 510 film applicator with a heatable plate.
The rest was doctor bladed on a glass plate, fixed with double sided adhesive tape and 
partially heated with a heat gun.
The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in 
\SI{0.05}{\milli\meter} steps and did not substantially alter the results.
For the rest of the experiments a blade height of \SI{0.02}{\milli\meter} was used.
The heatable vacuum plate 
had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where 
underpressure could be applied to keep substrate in place (see 
figure~\ref{fig:eric}). Most of them were covered with tape to increase the suction at the remaining ones. After setting the temperature of the heating plate to 
\SI{200}{\celsius}, the vacuum plate temperature (room temperature, \SI{40}{\celsius}, 
\SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) and the 
\gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}) were set, 
the blade was put into position, the sample was placed on the vacuum plate and the vacuum 
was switched on. 
During pre-optimisation samples, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
\mmps{1}, \mmps{2} and \mmps{5}) were tested. 
\ul{100} of solution were 
applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the 
liquid evenly. After evaporation of the solution, the vacuum was turned off, the 'blade 
pusher' was put into initial position, the blade was removed and excess solution on the plate 
was removed with a 
wipe. The doctor bladed substrate was transferred to the \SI{200}{\celsius} heating plate and 
rested on there for \minutes{5}. 
This process of applying a \gls{zro} layer was repeated as many times as needed.
\begin{figure}
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsen1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsendb1.png}
		\caption{}
	\end{subfigure}
	\caption{
		(a)
		Temperature regulator (1) on the left,
		vacuum pump (2) in the background and 
		Erichsen Coatmaster 510 film applicator (3) with heatable vacuum plate.
        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\micro\meter}.
		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
	}
	\label{fig:eric}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calcination}
A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate 
the doctor bladed samples. 
The heating plate could hold temperature for a certain amount of time, but heated with a 
fixed rate of circa \oc{10}/\minutes{}.
%The heating plate heated with a steady rate of \td{\oc{5}/\minutes{}}.
In order to achieve a lower overall heating rate several temperature ramps and plateaus 
were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
This procedure was called HP1.
The HP1 procedure was optimized for the available hardware by a colleague working on the 
project prior to the author.

\begin{table}[h]
	\centering
	%\caption{Time the temperature was held constant at certain temperatures on the heating plate}
    \caption{Heating programs}
    \subcaption{Heating program HP1 used with the Labtech EH45C heating plate}
	\label{tab:labtech}
	\begin{tabular}{rl ll ll ll ll ll ll }%ll ll ll ll ll ll ll}
		\hline
		\hline
		T [\oc{}]	    &80		&100	&150	&160	&170 	&180	&190	&200	&250	&300	&350	&400	\\
		t [\minutes{}]	&10 	&10		&5 		&5 		&5 		&5 &5 &10 &10 &10 &10 &60 \\
		\hline
		\hline
	\end{tabular}
%%%%%%%%%%%%
    \subcaption{Heating programs NT1 - NT6 used with the Naberterm LB410 muffle furnace}
	\label{tab:nt}
	\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
		\hline\hline
		Name	&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
		\hline
		NT1		&2					&1					&2				&400	&60  \\
		NT2		&2					&2					&2				&400	&60  \\
		NT3		&3					&3					&3				&400	&60  \\
		NT4		&4					&4					&4				&400	&60  \\
		NT5		&4					&4					&4				&500	&60  \\
		NT6		&1					&1					&1				&400	&60  \\
%		NT7		&max				&max				&max			&600	&60  \\
		\hline\hline
	\end{tabular}
\end{table}
%
%\clearpage
The NT1 heating program was used to mimic the HP1 heating procedure from the heating 
plate in the Naberterm muffle furnace. 
NT2 is an simplification of NT1 and programs NT3~-~NT6 are the same as NT2 with altered 
heating rate and 
NT5 additionally used a calcination temperature T$_{\textrm{Cal}}$ of \SI{500}{\celsius}.
NT2-NT6 had 2 variables (heating rate and calcination temperature) in contrast to 
NT1 which had 4 (three different heating rates and calcination temperature). 
All heating programs were held at the calcination temperature for one hour.
%In figure \ref{fig:heat} the different heating curves are depicted. 
%
%\begin{figure}
%	\centering
%	\includegraphics[width=.7\textwidth]{../Data/Graphs/hp1.png}
%	\caption{Different heatings curves}
%	\label{fig:heat}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Characterisation}
All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
\Gls{ft} \gls{ir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter} - \SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a Silicon detector for visual and \gls{ir} light 
(\SI{500}{\nano\meter} - \SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The UV and VIS+IR spectra were merged 
in Opus software. % included in the spectrometer. 
%\td{IR around page 45
%REFLECTIVITY? can also be used for determination of thickness p47
%}
\Gls{xrd} spectra were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.

The \gls{iv} curves were measured with Agilent 4156C Precision Semiconductor 
Parameter Analyzer from \SI{-0.5}{\volt} to \SI{0.5}{\volt} with steps of 
\SI{10}{\milli\volt}.
%
Prior to \gls{iv} measurements the samples were sputtered with aluminium 
through a mask to produce a multitude of equidistant contacts with a Leybold 
UNIVEX450C Sputter System.
%https://en.wikipedia.org/wiki/Sputter_deposition
Directional current sputtering was used with Argon as inert gas at \SI{0.005}{\milli\bar} 
and with a power of \SI{40}{\watt} for \SI{700}{\second}.
Between sputtering and \gls{iv} measurements 
direct contacts to the steel subtrate were created by removing the \gls{zro} layer with 
sand paper on two opposing edges of a sample and then by applying silver paste.
%\td{scratched until short circuit was produced (aka the steel foil was reached under the \gls{zro} layer).  }
See figure~\ref{fig:circuit} for a sketch of the connectivity.

\begin{figure}[hbt]
    \centering
    \begin{circuitikz} \draw
        (0,0) to[european voltage source] (0,2)
        to[ammeter] (2,2) 
        to[generic,l=W] (4,2) 
        to[generic,l=Au] (6,2) 
        to[generic,l=Al] (8,2)
        -- (8,2)
        to[generic,l=ZrO$_2$] (8,0)
        -- (8,0)
        to[generic,l=steel] (6,0)
        to[generic,l=Ag] (4,0)
        to[generic,l=Au] (2,0) 
        to[generic,l=W] (0,0) 
            ;
    \end{circuitikz}
    \caption{Sketch of circuit, from the source clockwise: varibale voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.}
    \label{fig:circuit}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREOPTIMISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Preparatory Experiments/series (Pro-optimisation/Finding base process/Preliminary study)}
\subsection{Pre-optimisation}
%Initially, glass plates were doctor bladed manually with aquatic solution and calcinated 
%via HP1. 
%Glass was used because of its availability and in order to be able to make IR 
%\td{transmission} spectra.
%In order to measure the resistivity of the produced layer \gls{fto} and \gls{ito} layered 
%glass plates (both conductive) were used as substrate.
%Conducting substrates were also needed to produce \gls{sem} micrographs. 
%\td{should maybe put this into beginning of section \ref{sec:exp}?}
%otherwise the sample would charge and can't be pictured anymore. 
%this means if the produced layer is thick and homogeneous enough, it's difficult to see in sem
%Different additives were included in the recipe (see table \ref{tab:rec1}) and the resistance was checked with a multimeter. 
%\todo{different additives, heating programs (NT1-NT5 and HP1), blade distances (distance between blade and substrate) and layer counts were tried}
Composition of the aquatic solution, heating program, blade distance (distance between 
blade and substrate) and layer count were varied but no homogeneous layers resulted. 
Thus, 
the buthanolic recipe was introduced, which gave rise to more homogeneous films.
After the blade moved over the substrate the remaining liquid needed about a minute 
to evaporate. 
%\td{
The then current procedure produced clear and continuous films, but was plagued from 
inhomogeneities due to drying stains. 
The drying stains could be circumvented by using a heat gun, but the results were not 
reproducible. 
The glass plate of the film applicator was therefore exchanged with a metal plate which 
allowed to hold the sample in place through underpressure and heat it to a certain 
temperature. The bounds of the process variables were then explored in a preliminary study 
using the Plackett-Burman \cite{Plackett1946} design implemented in the \texttt{python3} 
library \texttt{pyDOE}. With 
(1,5), (4,10), (400,500), (120,480), (0.1,5) and  (20,80) 
as nominal and extreme values for 
relative concentration $conc$, number of layers $layers$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively. 
After testing the first samples, the \gls{db} velocities altered to 1 and 5 (see table \ref{tab:pre-opt1}).
\begin{table}[htb]
	\centering
	\begin{subtable}{0.5\linewidth}
		\begin{tabular}{cccccc}
			\hline
			\hline
	%		&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
	conc	&layers	&$v_{\textrm{DB}}$	&$T_{\textrm{DB}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\
			\hline
	1	&10	&5	&20	&120	&400	\\
	1	&4	&0.1	&20	&120	&500	\\
	5	&10	&0.1	&20	&120	&500	\\
	5	&4	&5	&20	&480	&400	\\
	1	&5	&5	&80	&120	&500	\\
	1	&10	&1	&80	&480	&400	\\
	5	&5	&1	&80	&120	&400	\\
	5	&10	&5	&80	&480	&500	\\
			\hline\hline
		\end{tabular}
		\subcaption{Placket-Burman style experiments}
		\label{tab:pre-opt1}
	\end{subtable}%
	\begin{subtable}{0.5\linewidth}
		\begin{tabular}{cccccc}
	%conc	&layers	&vDOC	&TDOC	&vCal	&Tcal		\\
			\hline\hline
	conc	&layers	&$v_{\textrm{DB}}$	&$T_{\textrm{DB}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\
			\hline
	2	&8	&0.5	&40	&360	&470	\\
	2	&6	&2	&40	&360	&430	\\
	1	&4	&12	&70	&120	&500	\\
	1	&9	&18	&80	&240	&400	\\
	4	&6	&14	&60	&240	&500	\\
	4	&6	&14	&60	&240	&500	\\
	4	&6	&14	&60	&240	&500	\\
\\
			\hline
			\hline
		\end{tabular}
		\subcaption{Hand picked experiments}
		\label{tab:pre-opt2}
	\end{subtable}
	\caption{}
	\label{tab:pre-opt}
\end{table}

%$T_{DB}$[\oc{}]
%$v_{DB}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a DB machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Shortly before the \gls{pso} the stabilisation agent was changed from \gls{acoh} to 
\gls{ipo} because of much better soltion stability.
After 
%a fitting recipe was found and 
the boundaries were fixed the process variables to 
produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
See table \ref{tab:space} for the space spanned for the optimisation.
\begin{table}[ht!]
    \caption{}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}

\ds{The final boundaries were
conc 2 - 5 (1) ,
layers 4 - 12 (2),
\gls{db} velocity 10 - 20 (2),
\gls{db} temperature 20 - 80 (20),
heating rate 120 - 1080 (240),
calcination temp 300 - 500 (100),
.
}

### 2021-12-12 Thesis/chapter/results-and-discussion.tex
thesis split into chapters

\td{base/best sample was somewhot 150, 5 layers 3F 2K/min 400C} what was the best result?
\td{
double calcination (2x400C) was tried instead of pyrolization (4x200 then 400C),p49
so higher concentration of zro2 leads to less stable solution
5F ca 100min
4F ca 140min
3F ca 420min (7h)
}
\td{if i would plan the optimisation again, I would take less input variables (fokus on 
conc,vdoc and tdoc or even only vdoc and tdoc) which may or may not have multiple maxima.}
\td{adding a extra variable to optimize was to optimistic and ich hab mir damit eindeutig 
(im nachhinein) steine in den Weg gelegt.}
\td{instead of changing the stabilisation agent before optimisation, could change after pso}
\td{varied doctor blading velocity: 10, 5, 1, 0.5, 0.2, 0.1. Slower less layer}
\todo{Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
The space seems to be too big for the small sample size.
Look at relation of space size and sample size here and in Hu2016.
\td{p68 iPrOH to milky solution and solution becomes clear!!!! checked how much 
is needed. 5F solution milky over night ~2ml, added 1ml IPO and clear.}
\td{extra PB-design with conc(2-4), layers(6-8), tcal(430-470), tvel(4-6),
vdoc(0.5-2), tdoc(40-60). low vdoc very homogenuous but actually nearly no 
deposition because miniscus is pulling liquid off the substrate.}
\td{IPO influence on "stability" p74: 600ul IPO makes clear, 4000 ul BuOH not clear with 
same base solution (1ml of 4F), added extra 400ul to BuOH sol and after 5min clear. 
of 1:5 is unacceptable Dilution }
21.8 (1F) from 15.02. 13:30 bis 
26.3 (1ml iPO to ca2ml of 5f) from 16.02. 16:30 bis 18.02.++
18.02 4F in 80min milky
      2F in ca 24h (stabilization AcOH)
\td{In example of documentation 2 input variables and 1-2 responses initial population=10
, subsequent population=5, but 10 iterations. Clearly more input varibles and less 
iterations (as in actual experiments) lead to suboptimal results.
When plotting input vars  against the response variables, no trend
The exploration-vs-exploitation parameters of the model were also not set accordingly.}
see \href{https://search.r-project.org/CRAN/refmans/emma/html/emma.html}{source}

Would be easier to fit with single factor at a time variation or latin hyper cuber?
Would it also be easier for PSO or ML to find fitting function?
Every output var is independent of each other, so $v_{cal}$ can act as test

plot predictions from EMMA and ML.
the data has a lot of error, but because the production process takes so long nad the limited time and the chosen optimisation method, the experiments weren't weiderholt
how much variance is in data?

The most time consuming part was definitively the prelaminary studies.
this time could have been verkürzt by testing a wide array of diverse recipes from the literature

The data is spread across the datenraum, such that it is not trivial to (1) find the variable with the most variance and (2) to fit in order to understand to impact of noise on the data. 
Dimension reduction bietet sich stark an bei solcher Datenlage. 
Welche methode funktioniert bei relativ vielen variablen, wenig datenpunkten und Noise. 
Am besten waere feature extraction (variable x1 hat am meisten einfluss. ginge auch wenn man bei pca den einfluss von verschiedenen

heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the GA performes
It doesn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset

first recipe tried to improve to achieve more restisting layer. by pH value, surface 
tensionand solution ratios (only 10\% change because it was assumed, that the recipe is 
good and should be improved, but the recipe should be altered thoroughly.
two layers were also tried but didn't even pass the visual examination/test/inspection. 
A curst was produced. 
At this point in time everything was doctor bladed by hand. The hight was varied (with tape).
When the switch to the erichsen was made. The height was kept constant in order to keep 
the variables to optimize ueberschuabar, but could have been even less variables.
If the movement was to slow the resluting  layer would be very inhomogenuous, thus the
velocity wasn't varied.

aquatic vs buthanolic
aquatic immidiately milky

\td{p75 tested various vDOC (10,15,20) with TDOC (40,60,70,80) variations with only visual 
inspection of evaporation process. Ideally solution evaporate shortly after DB but not 
before} 
n-BuOH has boiling point of ca 117C 
\href{https://pubchem.ncbi.nlm.nih.gov/compound/1-butanol#section=Boiling-Point}{source}
\td{p74 146,150,151,152,153,154,156,157,158,160,161,186,187,188,190,194,195,198 
all sputtered with Ag silver on 19.02.2021.}
EMMA was finished on 23.02.2021
first experiments generated, but trashed because 1F solution neglected, contraints 
tightened
p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation
look at visualisation in code/pca/ folder and maybe use sort -n 3 
which values were actually used in EMMA and how were they calculated
from 145 to 160 what was changed, large increase of G
small better!!!
p82 test to what extend AcOH can be replaced with iPOH
192 was first with IPOH
use Kernel ridge regression, in PSO the distance of response variables is 
preparation before measuring the i-v: removing layer by scratching in order to to the 
steel subtrate. measure resistance if very low (around 10-1) apply paste and let dry
why different output with ptyhon 3.6 (work laptop) and 3.8 personal
discussion: 
why is IPO satbilizing? 
what are reasons for instability? 
IV aufbau p 103 
TODO: check which software versions
check if output of 
check if outputs provided by all-stat.sh is same as in R  (p 100)
look at last pages of notebook
\td{maybe the observable/sumofsquareddistanceoflogofconductance is not a good metric.
I should have a look at the raw data. maybe try to verarbeiten different and then fit 
with KRR or SVM, is phd a sigmoid function? }

\td{for 1F c(Zr) = 44.6 mmol/L
if n is number of samples, and p is number of input variables, then n >> p 
In this case n\~50 and p\~6 which give n/p=8+1/3
in EMMA documentation example n=55and p=1-2, n/p=55-22.5
plot x vs G and hold all other vars const
write script to do that}

\todo{make sample time line with ipo vs acoh, al vs ag, hg vs doc, ...}

\td{
acceptable layer was produced by buthanolic solution, but very unstable (short lived) how long? p41 
extra AcOH stabilzed but needed so much that dilution too large...
The stirring time was untersucht, but not much difference so shortest was used because 
short time can produces faster and the resulting solution is longer stable 
(after finishing mixing)
10 layers were tried of short stiring and gave good results? samples 130,131,134,135 (p43)
}

%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
\subsection{XRD}

\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra}
	\label{fig:xrd}
\end{figure}

### 2021-12-12 Thesis/chapter/theoretical-background.tex
thesis split into chapters

%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\subsection{Sputtering}
\subsection{SEM}
\url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
\subsection{Infrared absorption}
\subsection{X-Ray Diffraction}
\url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
\url{https://chem.libretexts.org/Courses/Franklin_and_Marshall_College/Introduction_to_Materials_Characterization__CHM_412_Collaborative_Text/Diffraction_Techniques/X-ray_diffraction_(XRD)_basics_and_application}\\
\subsection{Particle Swarm Optimization}
\subsection{Machine Learning}
\subsubsection{History}
\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
\subsection{Princlipal Component Analysis}
reinforcement learning could also have been a nice option

### 2022-02-28 Thesis/chapter/01-introduction.tex
renamed chapter with numbers

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\td{describe everything what is mentioned in \ref{sec:exp}}
\Gls{pv} is one big hope when trying to become carbon neutral as it uses the energy provided by sun directly in contrast to renewable energy sources (e.g. wind and water) or even carbon based sources.
One sort of \gls{pv} are \gls{cigs} \cite{Vasekar2010} cells. % https://doi.org/10.1016/j.tsf.2009.09.033}
\td{was sind vorteile?}
In order to make a module, multiple cells are operated in series. 
The cells must be applied to a non-conducting surface.
Glass is a good non-conducting substrate, but very rigid and brittle. 
An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
An insulating layer must therefore be applied to the steel substrate before any \gls{cigs} cells can be applied.
A non-toxic material which is suitable for this application is \gls{zro}. 
An economic and scalable method is doctor blading via a \gls{sg} process. 
\gls{sg} processes often produce porous layers. 
In this work a dense, insulating and homogeneous layer is pursued. 
\Gls{ml} can help to uncover complex non-linear relations, such as the influence of the 
production factors on the thickness and resistance of the resulting layer.
The optimisation of the conductance if performed with a particle swarm optimization 
algorithm. 
The resulting optimum is compared with other optimisation methods.

### 2022-02-28 Thesis/chapter/03-theoretical-background.tex
renamed chapter with numbers

--- 2021-12-12 Thesis/chapter/theoretical-background.tex
@@
 %\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
+\todo{Structure: Free writing} 
+Ueber das Material, also PV und speziell CIGS (copper indium gallium sulfide) 
+ueber den MC prozess berichten, also DB, i-v curven, sputtering, sem, ir, xrd
+ueber den it ml stuff und statistisch, also ML algemein, pso im speziellen 
+perfekt fuer intro einfach mal erwaehnen was wo in diesem capitel zu finden sein wird. 
+Books PV, analytic otto? 
+\subsection{Photovoltaik and CSGI}
+The grundlage for all pvs is the photovoltaik effect which was entdeckt by Albert Einstein adn for which he got the nobel price. 
+The Prinziple is easy: When the energy (E = hv) of the light is \td{large,strong,big,high}er than the binding energy of an electron the electron is ejected with the remaining energy as kinetic energy 
+\begin{math}
+	E_{kin}=hv - Eb
+\end{math}
+Different Materials have different binding energies. Metalls do have in general lower binding energies than covalent bound material and halbleiter do have even lowers E_b. 
+Thats Silica is in a lot of PVs. 
+The next generation of PVs. 
+CIGS has in contrast to silicium based PV a direct band gap\td{source and what does that mean?}
+duennschicht pv, haben eine effeftivitaet von 7-16\% vs 15-22\% \cite{Mertens2018}
+\subsection{Zirconium oxide}
 \subsection{Sputtering}
+%https://en.wikipedia.org/wiki/Sputter_deposition
 \subsection{SEM}
@@
 \subsection{Infrared absorption}
+\td{IR around page 45;
+REFLECTIVITY? can also be used for determination of thickness p47
+}
 \subsection{X-Ray Diffraction}

### 2022-02-28 Thesis/chapter/04-experimental.tex
renamed chapter with numbers

--- 2021-12-12 Thesis/chapter/experimental.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\label{sec:exp}
-%\subsection{finding a solution}
-%\subsection{finding process variables}
 In this section the used chemicals and substrates, experimental procedures and any used 
@@
 \subsection{Solutions}
-%Two main recipes were used and their compositions were varied. 
 All recipes for solutions can be divided into two categories:
@@
 	\centering
-	\caption{}
+	\caption{Composition of different buthanolic solutions}
 	\label{tab:rec2}
@@
 fixed rate of circa \oc{10}/\minutes{}.
-%The heating plate heated with a steady rate of \td{\oc{5}/\minutes{}}.
 In order to achieve a lower overall heating rate several temperature ramps and plateaus 
@@
 	\centering
-	%\caption{Time the temperature was held constant at certain temperatures on the heating plate}
     \caption{Heating programs}
+	\label{tab:heating}
     \subcaption{Heating program HP1 used with the Labtech EH45C heating plate}
@@
 in Opus software. % included in the spectrometer. 
-%\td{IR around page 45
-%REFLECTIVITY? can also be used for determination of thickness p47
-%}
 \Gls{xrd} spectra were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
@@
 \SI{10}{\milli\volt}.
-%
 Prior to \gls{iv} measurements the samples were sputtered with aluminium 
@@
 UNIVEX450C Sputter System.
-%https://en.wikipedia.org/wiki/Sputter_deposition
 Directional current sputtering was used with Argon as inert gas at \SI{0.005}{\milli\bar} 
@@
 Between sputtering and \gls{iv} measurements 
-direct contacts to the steel subtrate were created by removing the \gls{zro} layer with 
+direct contacts to the steel substrate were created by removing a patch the \gls{zro}
+layer with 
 sand paper on two opposing edges of a sample and then by applying silver paste.
-%\td{scratched until short circuit was produced (aka the steel foil was reached under the \gls{zro} layer).  }
 See figure~\ref{fig:circuit} for a sketch of the connectivity.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Preparatory Experiments/series (Pro-optimisation/Finding base process/Preliminary study)}
 \subsection{Pre-optimisation}
@@
 %\td{
-The then current procedure produced clear and continuous films, but was plagued from 
+The then current procedure resulted in clear and continuous films, but was plagued from 
 inhomogeneities due to drying stains. 
@@
 The glass plate of the film applicator was therefore exchanged with a metal plate which 
-allowed to hold the sample in place through underpressure and heat it to a certain 
+allowed to hold the sample in place through underpressure and simultaneously heat it to a certain 
 temperature. The bounds of the process variables were then explored in a preliminary study 
@@
 as nominal and extreme values for 
-relative concentration $conc$, number of layers $layers$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively.
-After testing the first samples, the \gls{db} velocities altered to 1 and 5 (see table \ref{tab:pre-opt1}).
-\begin{table}[htb]
+relative concentration of Zr $c_{Zr}$, number of layers $n_{l}$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively.
+After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see table \ref{tab:pre-opt1}).
+\begin{table}[hbt]
 	\centering
+	\caption{Pre-optimization experiments}
+	\label{tab:pre-opt}
 	\begin{subtable}{0.5\linewidth}
+		\centering
+		\subcaption{Placket-Burman style experiments}
+		\label{tab:pre-opt1}
 		\begin{tabular}{cccccc}
@@
 	%		&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
-	conc	&layers	&$v_{\textrm{DB}}$	&$T_{\textrm{DB}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\
+			$c_{Zr}$	&$n_l$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
 			\hline
@@
 		\end{tabular}
-		\subcaption{Placket-Burman style experiments}
-		\label{tab:pre-opt1}
 	\end{subtable}%
 	\begin{subtable}{0.5\linewidth}
+		\centering
+		\subcaption{Hand picked experiments}
+		\label{tab:pre-opt2}
 		\begin{tabular}{cccccc}
@@
 			\hline\hline
-	conc	&layers	&$v_{\textrm{DB}}$	&$T_{\textrm{DB}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\
+			$c_{Zr}$	&$n_l$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
+	%conc	&layers	&$v_{\textrm{DB}}$	&$T_{\textrm{DB}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\
 			\hline
@@
 	1	&9	&18	&80	&240	&400	\\
-	4	&6	&14	&60	&240	&500	\\
-	4	&6	&14	&60	&240	&500	\\
-	4	&6	&14	&60	&240	&500	\\
-\\
+	4*	&6	&14	&60	&240	&500	\\
+	4*	&6	&14	&60	&240	&500	\\
+	4*	&6	&14	&60	&240	&500	\\
 			\hline
 			\hline
+			\\
+%			\multicolumn{6}{c}{*different stabilisation reagent compositions}\\
 		\end{tabular}
-		\subcaption{Hand picked experiments}
-		\label{tab:pre-opt2}
 	\end{subtable}
-	\caption{}
-	\label{tab:pre-opt}
 \end{table}
@@
 Shortly before the \gls{pso} the stabilisation agent was changed from \gls{acoh} to 
-\gls{ipo} because of much better soltion stability.
+\gls{ipo} because of much better solution stability.
+The up to this moment best process was chosen to be tested with \ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
+%\td{As the sample showed the best all ex were proceeded with ipo as stabilatin agent. }
+The sample produced with \gls{ipo} as stabilization agent showed comparable passivation results and better stability. Therefore \gls{ipo} was used  as stabilisation in further experiments.
 After 
@@
 \begin{table}[ht!]
-    \caption{}
+	\centering
+	\caption{Final values used in the \gls{pso}.}
     \label{tab:space}
@@
         \hline\hline
-        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
+		$c_{Zr}$	&$n_l$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
+%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
         \hline

### 2022-02-28 Thesis/chapter/05-computational-details.tex
renamed chapter with numbers

--- 2021-04-18 Thesis/article.tex
@@
-\documentclass[a4paper]{article}
-\usepackage[margin=3cm]{geometry}
-\usepackage{xcolor}
-\usepackage{graphicx}
-\usepackage{lipsum}
-\usepackage{amsmath}
-\usepackage{pdfpages}
-\usepackage{url}
-\usepackage{hyperref}
-\hypersetup{
-	colorlinks = true,
-	colorlinks = false,
-	linkbordercolor = {white},
-	urlcolor = {blue},
-	linkcolor = {blue},
-	citecolor = {blue}
-}
-\usepackage{acronym}
-\usepackage[acronym,nomain]{glossaries}
-\makeglossaries
-\newcommand{\todo}[1]{\textbf{\textcolor{red}{#1}}}
-\newcommand{\td}[1]{\textbf{\textcolor{red}{#1}}}
-\newcommand{\me}[1]{\textbf{\textcolor{gray}{#1}}}
-\newcommand{\ds}[1]{}
-\newcommand{\oc}{$^o$C}
+\subsection{Data Processing}
+\label{sec:eval}
+%\td{describe problem and solution found}
+For every sample multiple \gls{iv} curves were measured. 
+The main difficulty faced in processing the data was to present the measurements obtain 
+from a sample in one representative number. 
+The average of each conductance would be an obvious choice but difficult to represent a 
+sample correctly since the possible values of conductance span accross several magnitudes.
+So the average of logarithms of conductances is the next nearby ansatz.
+\todo{why didn't i just take this?}
+\td{L2 norm because it might be easier to compare to other methods. }
+\td{inspired by euclidean norm/L2 distance from ideal case} 
+\td{wanted to put more weight on bad shunts}
+\td{plot avg, avg(log), avg(log-13)}
 
-\title{Functional oxide layers for electrical isolation and chemical passivation of steel substrates}
-\author{Johann Dorn}
+For every I-V curve (aluminium dot) the gradient $g$ at $V=0$ is calculated by taking 
+each $n=5$ points after and before the origin at least $d=2$ points distance (which boils
+down to the values from \SI{0.02}{\volt} to \SI{0.07}{\volt}) , averaging their V and I values 
+and calculating
+\begin{equation}
+    g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
+\end{equation}
+As a measure of conductance a distance D from an ideal non-conducting case. The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
+\begin{equation}
+	D = \sum_i^N \frac{ -log_{10}(g_i) - 13}{N}
+	\label{eq:D}
+\end{equation}
+Another measure is the density of shorted species $\rho_{s}$ is calculated in following way:
+\begin{equation}
+	s_i = \begin{cases}
+	1 &\text{if} \quad -log(g_i) < 5 \\
+	0 &\text{if} \quad -log(g_i) \geq 5 \\
+	\end{cases}
+\end{equation}
+\begin{equation}
+	\rho_s = \sum_i^N \frac{s_i}{N}
+	\label{eq:rho}
+\end{equation}
+Other estimates of the conductance are the averages:
+\begin{equation}
+	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
+\end{equation}
 
-\begin{document}
-\maketitle
-\iffalse
-my notes
-\fi
-%\begin{acronym}
-%	\newacronym{nemo}{amat}{dolorem}
-	\newacronym{zrpro}{Zr(PrO)$_4$}{zirconium(IV)propoxide}
-	\newacronym{acac}{Hacac}{acetylacetone}
-	\newacronym{acoh}{AcOH}{acetic acid}
-	\newacronym{buoh}{BuOH}{1-buthanol}
-	\newacronym{ipo}{IPO}{2-Propanol}
-	\newacronym{ito}{ITO}{indium doped tin oxide}
-	\newacronym{fto}{FTO}{fluorine doped tin oxide}
-	\newacronym{n2}{N$_2$}{nitrogen}
-	\newacronym{water}{H$_2$O}{deionized water}
-	\newacronym{sds}{SDS}{sodium dodecyl sulfate}
-	\newacronym{hcl}{HCl}{hydrochloric acid}
-	\newacronym{h2so4}{H$_2$SO$_4$}{sulfuric acid}
-	\newacronym{naoh}{NaOH}{sodium hydroxide}
-	\newacronym{zro}{ZrO$_2$}{zirconium dioxide}
-	\newacronym{1f}{1F}{one-fold concentrated solution}
-	\newacronym{2f}{2F}{two-fold concentrated solution}
-	\newacronym{3f}{3F}{three-fold concentrated solution}
-	\newacronym{4f}{4F}{four-fold concentrated solution}
-	\newacronym{5f}{5F}{five-fold concentrated solution}
-	\newacronym{db}{DB}{doctor blading}
-%\end{acronym}
+\begin{equation}
+	G_2 =  \sum_i^N \frac{log(g_i)}{N}
+\end{equation}
 
-%\clearpage
-\printglossaries
-%\clearpage
-%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Preface}
-%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\td{describe everything what is meantioned in \ref{sec:exp}}
-%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Aims and Objectives}
-was hab ich gemacht, warum? 
-Defensio: Argumente in der Arbeit noch mal sichten, Feedback von Betreuungsperson im Kopf haben - da könnten Fragen kommen, 
-sich selbst aufnehmen
-
-Präsentieren: Visualisierungen sinnvoll? 
-Antworten überlegen/Argumente überlegen
-Limitation, Rahmen der Arbeit
-Begründung für die eigene Vorgehensweise
-%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIMENTAL
-\section{Experimental}
-\label{sec:exp}
-In this section the used chemicals and substrates, experimental procedures and any used equipment are described. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Substrate Preparation}
-Five different substrates were used throughout this work: 
-microscope glass slides (2.5~cm~x~7.5~cm) \td{from where}, thinner, squared glass plates (2.5~cm~x~2.5~cm) \td{from where}, \gls{ito} glass plates (2.5~cm~x 2.5~cm) \td{from where}, \gls{fto} glass plates (5~cm~x~5~cm) from \td{Sigma Aldrich} and steel foil (10~cm~x~10~cm) \td{provided by Sunplugged GmbH (\url{http://sunplugged.at/)}}.
-The glass slides and \gls{fto} were cut\td{/scratched} with a \td{diamond scratcher/scraper} and broken with a \td{glass breaker} into pieces of dimensions 2.5~cm~x~2.5~cm.
-The steel foil was cut with a foil cutter\me{, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting slides)}.
-All substrates were cleaned in three steps before usage:
-\begin{enumerate}
-	\item 15 minutes in 50 ml \gls{water} and 1 ml of Hellmanex III in a sonic bath
-	\item 15 minutes in \gls{water} in a sonic bath
-	\item 15 minutes in \gls{ipo} in a sonic bath 
-\end{enumerate}
-After the last cleaning step, the samples were dry blown with dry \gls{n2} gas.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\iffalse
-\subsection{Cutting of the steel foil}
-\label{sec:cut}
-There is a red foil cutter in the vacuum room, which cuts the foil without much bending.
-Alternatively, the foil can be cut without bending by cutting repeatedly with a cutter knife.
-The foil is cut into 2.5 x 2.7 mm plates.
-The small plates are marked with an diamond cutter pen.
-The plates are cleaned with 1ml of Hellmanex III in 50-100 ml \gls{water} in the sonic bath for 15 min, then in \gls{water} for 15 min and finally in \gls{ipo} for 15 min. 
-The samples are dry blown with dry N$_2$ and stored until doctor blading.
-\fi
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Solution}
-Two main recipes were used and their \td{ingredients/compositions} were varied. 
-The first recipe - adopted from Anwar et. al. \cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} 
-and the second recipe - 
-adopted from Hu et. al. \cite{Hu2016} -
-was based on \gls{zrpro} in \gls{buoh}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Aquatic solution}
-\me{The procedure for the aquatic solution is as follows:}
-While stirring \gls{zrpro} is added to \gls{acac} and \gls{water} (including any additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) is added to \gls{ipo} in two separate vessels and stirred for 1 hour.
-The \gls{water}-\gls{ipo} mixture is added to the other solution and stirred over night. 
-The exact volumes can be taken from table \ref{tab:rec1}.
-\begin{table}[h]
+\subsection{Sample Selection}
+\label{sec:ss}
+An evolutionary approach was chosen, namely a multi-objective Particle Swarm Optimization (PSO) with a multi-response
+Multivariate Adaptive Regression Splines (MARS) model\cite{Villanova2010,Kennedy1995,Breiman1997,Carta2011}.
+%
+"PSO is a population based heuristic inspired by the flocking behavior of birds. 
+To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{Villanova2010}
+%
+Initially the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
+Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
+%
+%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
+\begin{table}[htb]
 	\centering
-	\caption{}
-	\label{tab:rec1}
-	\begin{tabular}{llllllll}
+	\begin{tabular}{cc cc cc}
 		\hline
-		recipe				&1		&2		&3		&4		&5		&6		&7\\
-%		\hline
-%		conc. [a.u.]	&1		&1.7	&2.6	&3.5	&4.4	\\
+		Zr(PrO)$_4$ conc. [21 g/L]	&layers	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
 		\hline
-		\gls{zrpro} [ml]	&8		&8		&8		&8		&8		&8		&8\\
-		\gls{acac} [ml]		&8		&8		&8		&8		&8		&8		&8\\
-		\gls{ipo} [ml]		&2		&2		&2		&2		&2		&2		&2\\
-		\gls{water} [ml]		&2.6	&2.6	&2.5	&2		&2		&2		&2\\
-		\gls{sds} [mg]		&-		&5.9	&-		&-		&-		&-		&-\\
-		\gls{hcl} [ml]		&-		&-		&-		&-		&0.5	&-		&-\\
-		\gls{h2so4} [ml]	&-		&-		&-		&-		&-		&0.5	&-\\
-		\gls{naoh} [ml] 	&-		&-		&-		&-		&-		&-		&0.5\\
+		2				&4		&40					&10				&300				&120	\\
+		3				&6		&50					&12				&400				&360	\\
+		4				&8		&60					&14				&500				&600	\\
+		5				&10		&70					&16				&					&840	\\
+						&12		&80					&18				&					&1080	\\
+						&		&					&20				&					&		\\
 		\hline
 	\end{tabular}
-\end{table}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Buthanolic solution}
-\label{sec:sol}
-\td{make recipe general}
-%The recipe for the solution was adapted from ref \cite{Hu2016}.
-Five different concentration were prepared. 
-%The first solution \td{(standard concentration/ one fold/ 1F)} 
-%followed the recipe loosely, which is described by Hu et al. \cite{Hu2016}.
-%In order to obtain thicker \gls{zro} layers the \gls{zrpro} concentration in the starting solution was raised.
-The \gls{1f} \td{(one fold (1F) solution /or/ one fold solution (1F))}
-%one-fold concentrated solution (1F) 
-was closest to the recipe proposed by Hu et. al. \cite{Hu2016}. 
-The other four solutions (\gls{2f}, \gls{3f}, \gls{4f}, \gls{5f}) were similar with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2}).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\iffalse
-The procedure for obtaining the \gls{1f} solution will be explained in detail: \td{maybe just keep it general}
-%
-%was closely on the basis of ref \cite{Hu2016}. 
-%The standard concentration will be described first and then the differences of higher concentrated solutions:
-4.9 ml of solvent (\gls{buoh}) are put into a beaker glass (or similar, preferably with \td{an air-tight} cap) with a stirrer. 
-0.1 ml of \gls{zrpro} are added while stirring.  
-After 10 to 15 minutes 0.05 ml (\ds{approximately }one mole equivalent of \gls{zrpro}) chelating agent (\gls{acac}) is added and stirred for another 10 to 15 minutes. 
-Finally, 1 ml of stabilisation solvent (\gls{ipo} or \gls{acoh}) is added to the mixture and stirred for additional 20-30 minutes. 
-\fi
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The solvent (\gls{buoh}) is put into a beaker glass (or similar, preferably with \td{an air-tight} cap) with a stirrer and \gls{zrpro} is added while stirring.  
-After 10 to 15 minutes one mole equivalent chelating agent (\gls{acac}) is added and stirred for another 10 to 15 minutes. 
-Finally, the stabilisation solvent (\gls{ipo} or \gls{acoh}) is added to the mixture and stirred for additional 20-30 minutes. 
-Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In order to make a \gls{2f} solution, the volume of \gls{zrpro} and \gls{acac} is doubled and \gls{buoh} is decreased by the volume of \gls{zrpro}. 
-The real concentration is not double of the original, though, but rather 1.7 fold because volume of \gls{ipo} is kept constant.
-
-\begin{table}[h]
-	\centering
-	\caption{}
-	\label{tab:rec2}
-	\begin{tabular}{rlllll}
-		\hline
-				&1F		&2F		&3F		&4F		&5F		\\
-		\hline
-		conc. [a.u.]	&1		&1.7	&2.6	&3.5	&4.4	\\
-		\hline
-		\gls{buoh} [ml]		&4.95	&4.9	&4.85	&4.8	&4.75	\\
-		\gls{zrpro} [ml]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
-		\gls{acac} [ml]		&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
-		\gls{ipo}/\gls{acoh} [ml]		&2		&2		&2		&2		&2		\\
-		\hline
-	\end{tabular}
+	\caption{Discrete levels of each input parameter \td{are concentrations correct?}}
+	\label{tab:input}
 \end{table}
 
-\subsection{Doctor blading}
-\label{sec:DB}
-\begin{figure}
-	\centering
-	\includegraphics[width=.8\textwidth]{Pics/erichsen.png}
-	\caption{Erichsen Coatmaster 510 
-		%Doctor blading machine 
-		with vacuum pump in the background and temperature regulator on the left.}
-	\label{fig:eric}
-\end{figure}
-\td{picture of the machine, and name of the machine}
-The temperature of the heating plate is set to 200 $^o$C.
-The temperature of the vacuum plate is set and waited until reached.
-The sample is placed on the vacuum plate and tested if it can be \td{held/retained} by the underpressure.
-The velocity of the \gls{db} blade is set and a mini test run is performed. 
-The blade is put in position. 
-100-125 $\mu$l of solution is applied with an 10-1000 $\mu$l pipette and the doctor blading is started immediately. 
-After evaporation of the solution, the vacuum is turned of, the 'blade pusher' put into initial position, the blade removed and excess solution removed with a wipe. 
-The small metal plate is transferred to the hot heating plate and rests on there for 3-5 min. 
-The process is repeated as wished.
+The first step is to select an initial population (ensemble of experiments), which is chosen randomly from the population space. 
+The samples are made, measured and evaluated according to section \ref{sec:exp} and the distance $D$ (see eq.
+\ref{eq:D}), $\rho_s$ (see eq.
+\ref{eq:rho}), $n_{layers}$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program.
+The program uses this data to estimate a response for each output variable (and to choose a fraction of the initial population which is allowed to propagate).
+The response variables for the entire population space is calculated. 
+The current population - each of the particles independently - moves towards the optimum solution.
+The population for the next time step is outputted and the experiments are again executed, measured and evaluated.
 
-\subsection{Calcination}
-A LabTech EH45 C heating plate and a Naberterm \td{L B410} furnace were used to calcinate the doctor bladed samples. 
-The heating plate heated with a steady rate of \td{2} $^o$C/min. 
-In order to achieve a lower overall heating rate several temperature ramps and plateaus were \todo{used}. See table~\ref{tab:labtech}
-
-\begin{table}[h]
-	\centering
-	\begin{tabular}{rl ll ll ll ll ll ll }%ll ll ll ll ll ll ll}
-%			&temp [\oc]	&time/rate &temp [\oc]	&time/rate	&temp [\oc]\\
-		HP1		&&&&&&&&&&&&&\\
-		\hline
-		T [\oc]	&80		&100	&150	&160	&170 	&180	&190	&200	&250	&300	&350	&400	\\
-		t [min]	&10 	&10		&5 		&5 		&5 		&5 &5 &10 &10 &10 &10 &60 \\
-		\hline
-	\end{tabular}
-	\caption{Time the temperature was held constant at certain temperatures on the heatingplate}
-	\label{tab:labtech}
-\end{table}
-
-\begin{table}[h]
-	\centering
-	\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
-%			&temp [\oc]	&time/rate &temp [\oc]	&time/rate	&temp [\oc]\\
-		HP1		&&&&&\\%&&&&&&&&\\
-		\hline
-		T [\oc]				&80		&150	&200	&400	&400 	\\
-		$\theta$ [\oc/min]	&10 	&10		&5 		&5		& 		\\
-		\hline
-		name	&80-150 [\oc/min]	&150-200 [\oc/min]	&200-T$_{max}$ [\oc/min]	&T$_{max}$ [min]	&T$_{max}$ [\oc] \\
-		NT1		&2					&1					&2					&60 &400 \\
-		NT2		&2					&2					&2					&60 &400 \\
-		NT3		&3					&3					&3					&60 &400 \\
-		NT4		&4					&4					&4					&60 &400 \\
-		NT5		&4					&4					&4					&60 &500 \\
-		NT6		&1					&1					&1					&60 &400 \\
-		NT7		&max				&max				&max				&60 &600 \\
-		\hline
-	\end{tabular}
-	\caption{Heating rates and constant temperature times. \td{Macht dieser Graph ueberhaupt sinn? }}
-	\label{tab:nt}
-\end{table}
-
-\subsection{EMMA Propagation}
-\begin{table}
+%\subsection{EMMA Propagation}
+\begin{table}[htb]
 	\centering
@@
 
-\section{Evaluation and Computational Details}
-\subsection{Evaluation of Samples}
-\label{sec:eval}
-For every I-V curve (aluminium dot) the gradient $g$ at V=0 is calculated by taking 5 points after the origin and 5 points before the origin, averaging their V and I values and calculating i
-\begin{equation}
-	g = \frac{I_{n+1} - I_n}{V_{n+1} - V_n}.
-\end{equation}
-As a measure of conductance a distance D from an ideal non-conducting case. The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
-\begin{equation}
-	D = \sum_i^N \frac{ -log_{10}(g_i) - 13}{N}
-	\label{eq:D}
-\end{equation}
-Another measure is the density of shorted species $\rho_{s}$ is calculated in following way:
-\begin{equation}
-	s_i = \begin{cases}
-	1 &\text{if} \quad -log(g_i) < 5 \\
-	0 &\text{if} \quad -log(g_i) \geq 5 \\
-	\end{cases}
-\end{equation}
-\begin{equation}
-	\rho_s = \sum_i^N \frac{s_i}{N}
-	\label{eq:rho}
-\end{equation}
-Other estimates of the conductance are the averages:
-\begin{equation}
-	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
-\end{equation}
+\subsection{Fitting via Machine Learning}
+\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
+Python and sci-kit learn \td{cite} was used to implement a linear fit model, and SVR with the kernels polynomial, rbf and sigmoid. 
+The space of hyper parameters C, the degree (in case of polynomial), epsilon and gamma was scaned.
 
-\begin{equation}
-	G_2 =  \sum_i^N \frac{log(g_i)}{N}
-\end{equation}
-
-\subsection{Sample Selection}
-\label{sec:ss}
-An evolutionary approach was chosen, namely a multi-objective Particle Swarm Optimization (PSO) with a multi-response
-Multivariate Adaptive Regression Splines (MARS) model\cite{Villanova2010,Kennedy1995,Breiman1997,Carta2011}.
-%
-"PSO is a population based heuristic inspired by the flocking behavior of birds. 
-To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{Villanova2010}
-%
-Initially the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
-Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
-%
-%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
-\begin{table}[htb]
-	\centering
-	\begin{tabular}{cc cc cc}
-		\hline
-		Zr(PrO)$_4$ conc. [21 g/L]	&layers	&$T_{DB}$[$^o$C]	&$v_{DB}$[mm/s]	&$T_{cal}$[$^o$C]	&$v_{cal}$[$^o$C/hour]	\\
-		\hline
-		2				&4		&40					&10				&300				&120	\\
-		3				&6		&50					&12				&400				&360	\\
-		4				&8		&60					&14				&500				&600	\\
-		5				&10		&70					&16				&					&840	\\
-						&12		&80					&18				&					&1080	\\
-						&		&					&20				&					&		\\
-		\hline
-	\end{tabular}
-	\caption{Discrete levels of each input parameter \td{are concentrations correct?}}
-	\label{tab:input}
-\end{table}
-
-The first step is to select an initial population (ensemble of experiments), which is chosen randomly from the population space. 
-The samples are made, measured and evaluated according to section \ref{sec:exp} and the distance $D$ (see eq.
-\ref{eq:D}), $\rho_s$ (see eq.
-\ref{eq:rho}), $n_{layers}$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in $^o$C/min) are supplied to the program.
-The program uses this data to estimate a response for each output variable (and to choose a fraction of the initial population which is allowed to propagate).
-The response variables for the entire population space is calculated. 
-The current population - each of the particles independently - moves towards the optimum solution.
-The population for the next time step is outputted and the experiments are again executed, measured and evaluated.
-
-scarce data may lead to overfitting\cite{Lecun1995conv}
-\section{Results and Discussion}
-The space seems to be too big for the small sample size.
-Look at relation of space size and sample size here and in Hu2016.
-\section{Outlook}
-
-Making of the solution for the sol-gel process:
-For a single concentrated solution 0.05 ml of \gls{zrpro} are added while stirring to 4.95 ml of \gls{buoh} and stirred for 15 minutes. 
-0.013 ml (or one molar equvilent of Zr) of \gls{acac} is added to the stirring solution. 
-After another 15 minutes 1 ml of acetic acid is added and stirred for 30 minutes to stabilize the solution up to 24h.
-
-The concentration can be increased up to 5 times being stable for a minimum of 4 hours. 
-The sol-gel process produces am homogeneous transparent crystalline zirconia oxide layer. 
-homogeneity can be mainly controlled via blade velocity and temperature and layers can be stacked.
-
-%\clearpage
-\bibliographystyle{ieeetr}
-\bibliography{int}
-\end{document}
+The independent variables are located on a partially irregular grid.

### 2022-02-28 Thesis/chapter/07-outlook.tex
renamed chapter with numbers

Making of the solution for the sol-gel process:
For a single concentrated solution \ml{0.05} of \gls{zrpro} are added while stirring to \ml{4.95} of \gls{buoh} and stirred for \minutes{15}. 
\ml{0.013} (or one molar equvilent of Zr) of \gls{acac} is added to the stirring solution. 
After another \minutes{15} \ml{1} of acetic acid is added and stirred for \minutes{30} to stabilize the solution up to \h{24}.

The concentration can be increased up to 5 times being stable for a minimum of \h{4}. 
The sol-gel process produces am homogeneous transparent crystalline zirconia oxide layer. 
homogeneity can be mainly controlled via blade velocity and temperature and layers can be stacked.

It should have been alos verglichen with grid search with comparable size
but most time was used to find a vernuenfig base recipe and process

It is still very human 
Der process is - as it the case with all ML and most fitting processes - is very abhaengig von hyper parameters, 
In the current work population size, number of generations, and most importantly boundaries (grenzen).

### 2022-02-28 Thesis/chapter/03-theoretical-background.tex
zusammenfassung von PV buch digitalisieren + some lit

@@
 Books PV, analytic otto? 
-\subsection{Photovoltaik and CSGI}
+\subsection{Photovoltaic and CSGI}
+\iffalse
 The grundlage for all pvs is the photovoltaik effect which was entdeckt by Albert Einstein adn for which he got the nobel price. 
@@
 duennschicht pv, haben eine effeftivitaet von 7-16\% vs 15-22\% \cite{Mertens2018}
+\fi
+\subsubsection{Problems of current energy supply}
+The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
+will be exhausted within the next 100 years. 
+%This time period must of course taken with a grain of salt as it can happen that even though the resource are being exhausted they can rise from one year to another as new reserves are being discovered and explored.
+Even though this time period is not exact and highly dependent on external factors, this number is rather small and brings us in zugzwang
+
+\subsubsection{History of Photovoltaics}
+The photoelectric effect was discovered in 1839 by french scientist Alexandre Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel. 
+With the discovery of the correlatio
+aenderung von widestand vonhalbleiter selen von bit ing willouhgby smith und ass joseph may fuer pv relevanten innere photoeket
+1876 william adam und richard Day zeigten mit Selenstab mit platin elektroden dass festkörper Lichenergie direkt in elekt energie umwalndeln 
+1905 erklaertle die physiklischen hinterdr'ünde mit seinem lichtquantentheorie einstein 
+die ersten solarzellen wurden in den 1950s in Nieschen anwendungen wie der Raumfahrt mit einem wirkungsgrad unter 10 prozent 
+durch die oelkriese 1973 stieg das interesse an pv und alternativen energiequellen und 1977 das erste salor...? 
+K5
+Neben der g"ngigen kristallienen Siliziem Zelle gibt es auch Duennnschichtzellen
+wegen dem hohen Absorptionskoeffizenten und der geringen Eindringtiefe von veispielsweise amorphem Silizium oder auch CIS (siehe table p 84) wird nur wenig Material benötigt und flexible Zellen konnen hergestellt werden
+CIGS 
+Materialien aus der Grupper der Chalkopyrite wisen allesamt eine XXX Gitterstruktur auf genauso wie Namengeber der Gruppe, das Chalkopyrit (CuFeS2).
+Meist wird ein Material mit der Summenformel CuIn_XGA_{(1-x)}Se_2 verwendet.
+Durch den hohen Unterschied der Bandabstaedne von CuInSe2 und CuGaSe2 kamnn durch entsprechende Mischverhaeltnisse von In und Ga der Bandabstand eingestellt werden (Tablep 142) Abbildung Bild 5.22 p143) beschreiben und bild für Modul
+Um ein Modul flexibel zu machen kann statt Glas Stahl als stbstrat verwendet werden. Allerdings wird ein Isolater zwischen Stahsubstrat und CIGS Zelle benötigt
+
 \subsection{Zirconium oxide}

### 2022-03-03 Thesis/chapter/03-theoretical-background.tex
PV book zrk gegebn

--- 2022-02-28 Thesis/chapter/03-theoretical-background.tex
@@
 duennschicht pv, haben eine effeftivitaet von 7-16\% vs 15-22\% \cite{Mertens2018}
+\fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Problems of current energy supply}
+The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
+will be exhausted within the next 100 years. 
+%This time period must of course taken with a grain of salt as it can happen that even though the resource are being exhausted they can rise from one year to another as new reserves are being discovered and explored.
+Even though this time period is not exact and highly dependent on external factors, this number is rather small and brings us in zugzwang
+
+\subsubsection{History of Photovoltaics}
+%aenderung von widestand vonhalbleiter selen von bit ing willouhgby smith und ass joseph may fuer pv relevanten innere photoeket
+The photoelectric effect was first decribed in 1839 by french scientist Alexandre Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel. 
+%1876 william adam und richard Day zeigten mit Selenstab mit platin elektroden dass festkörper Lichenergie direkt in elekt energie umwalndeln 
+With the discovery of the correlation between the {change of the }resistance and the irradiating light by british engineer Willouhgby Smith and his assistant Joseph May another relevant piece of the PV jigsaw was discovered.
+In 1876 William Adam and Richard Day showed that with a bar of selenium attached with platin electrodes the energy of light can be directly converted into electrical energy.
+%1905 erklaertle die physiklischen hinterdr'ünde mit seinem lichtquantentheorie einstein 
+And finally, in 1905 Einstein described the physical background of the photoelectric effect with his light quantum theory\cite{einstein1905erzeugung}.
+
+%die ersten solarzellen wurden in den 1950s in Nieschen anwendungen wie der Raumfahrt mit einem wirkungsgrad unter 10 prozent 
+The first solar cells were used in the 1950s in niche applications such as the space flight with efficiencies under 10 percent. 
+%durch die oelkriese 1973 stieg das interesse an pv und alternativen energiequellen und 1977 das erste salor...? 
+Though, fuelled by the oil crisis in 1973 the interest in photovoltaic and alternative energy sources in general rose and the development of mass product was boosted. \\
+consumer market
+\\
+K5\\
+%Neben der g"ngigen kristallienen Siliziem Zelle gibt es auch Duennnschichtzellen wegen dem hohen Absorptionskoeffizenten und der geringen Eindringtiefe von veispielsweise amorphem Silizium oder auch CIS (siehe table p 84) wird nur wenig Material benötigt und flexible Zellen konnen hergestellt werden
+Besides the common crystalline silicon cells there are thin film cells which because of their high absorption coefficient of light and therefore shallow penetration depth of light
+need less material and can be used to create/produce flexible cells \\
+of amorph silicon or CIS (see table p84)
+
+\begin{table}
+    \begin{tabular}{cccccc}
+        \hline
+        \hline
+        Material&   Art&    Bandluecke [eV]&    Wavelenght [nm]&    Absorptionskoeffizent alpha&    Eindringtiefe [um]\\
+        \hline
+        c-Si&   indirect&   1.12&   600&    4000/cm&    2.5\\
+        c-Si&   indirect&   1.12&   1000&    64/cm&    150\\
+        c-Si&   indirect&   1.12&   1100&    3.5/cm&    290\\
+        a-Si&   direct&      1.7&    600&    40,000/cm&  0.25\\
+        CdTe&   direct&      1.45&    600&    37,000/cm&  0.3\\
+        a-Si&   direct&      1.42&    600&    40,000/cm&  0.2\\
+        \hline
+        \hline
+
+    \end{tabular}
+\end{table}
+
+CIGS\\ 
+%Materialien aus der Grupper der Chalkopyrite wisen allesamt eine XXX Gitterstruktur auf genauso wie Namengeber der Gruppe, das Chalkopyrit (CuFeS2). 
+Materials from the chalcopyrite group (tetranogal crystal system) (eg CuInGaSe) can be used as absorber in such thin film cells.
+Meist wird ein Material mit der Summenformel $CuIn_XGA_{(1-x)}Se_2$ verwendet. 
+Durch den hohen Unterschied der Bandabstaedne von CuInSe2 und CuGaSe2 kamnn durch entsprechende Mischverhaeltnisse von In und Ga der Bandabstand eingestellt werden (Tablep 142) Abbildung Bild 5.22 p143) beschreiben und bild für Modul
+
+{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glas substrat} 
+\begin{table}
+    \begin{tabular}{cccc}
+        \hline\hline
+        Materialkombination&    Name&   Bandabstand&    Kürzel\\
+        \hline
+        CuInSe2&        copper indium di selenide&  1&  CISe\\
+        CuInS2&        copper indium di sulfide&  1.5&  CIS\\
+        CuGaSe2&        copper gallium di selenide&  1.7&  CIGSe\\
+        CuGaS2&        copper gallium di sulfide&  1.55&  CIGS\\
+        \hline\hline
+    \end{tabular}
+\end{table}
+
+Um ein Modul flexibel zu machen kann statt Glas Stahl als stbstrat verwendet werden. 
+Allerdings wird ein Isolater zwischen Stahsubstrat und CIGS Zelle benötigt
+
 \subsection{Zirconium oxide}

### 2022-03-08 Thesis/chapter/03-theoretical-background.tex
translate from PV book

@@
 \end{math}
-Different Materials have different binding energies. Metalls do have in general lower binding energies than covalent bound material and halbleiter do have even lowers E_b. 
-Thats Silica is in a lot of PVs. 
+Different Materials have different binding energies. 
+Metals do have in general lower binding energies than covalent bound material and semiconductors do have even lowers E_b. Really? 
+That's Silica is in a lot of PVs. 
 The next generation of PVs. 
-CIGS has in contrast to silicium based PV a direct band gap\td{source and what does that mean?}
+CIGS has in contrast to silicon based PV a direct band gap\td{source and what does that mean?}
 duennschicht pv, haben eine effeftivitaet von 7-16\% vs 15-22\% \cite{Mertens2018}
@@
 %aenderung von widestand vonhalbleiter selen von bit ing willouhgby smith und ass joseph may fuer pv relevanten innere photoeket
-The photoelectric effect was first decribed in 1839 by french scientist Alexandre Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel. 
 %1876 william adam und richard Day zeigten mit Selenstab mit platin elektroden dass festkörper Lichenergie direkt in elekt energie umwalndeln 
-With the discovery of the correlation between the {change of the }resistance and the irradiating light by british engineer Willouhgby Smith and his assistant Joseph May another relevant piece of the PV jigsaw was discovered.
-In 1876 William Adam and Richard Day showed that with a bar of selenium attached with platin electrodes the energy of light can be directly converted into electrical energy.
 %1905 erklaertle die physiklischen hinterdr'ünde mit seinem lichtquantentheorie einstein 
+%die ersten solarzellen wurden in den 1950s in Nieschen anwendungen wie der Raumfahrt mit einem wirkungsgrad unter 10 prozent 
+%durch die oelkriese 1973 stieg das interesse an pv und alternativen energiequellen und 1977 das erste salor...? 
+The photoelectric effect was first described in 1839 by french scientist Alexandre Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel. 
+With the discovery of 
+photo conductivity of selenium
+%the correlation between the {change of the }resistance and the irradiating light 
+by British engineer Willouhgby Smith and his assistant Joseph May another relevant piece of the photovoltaic jigsaw was discovered. 
+In 1876 William Adam and Richard Day showed that 
+the energy of light can be directly converted into electrical energy by a bar of selenium with attached platinum electrodes.
 And finally, in 1905 Einstein described the physical background of the photoelectric effect with his light quantum theory\cite{einstein1905erzeugung}.
+In the 1950s the first solar cells were used in niche applications such as the space flight with efficiencies under 10 percent. 
+Eventually, the interest in photovoltaic and alternative energy sources in general rose fuelled by the oil crisis in 1973 
+and the development of photovoltaic for the consumer market was boosted. \\
 
-%die ersten solarzellen wurden in den 1950s in Nieschen anwendungen wie der Raumfahrt mit einem wirkungsgrad unter 10 prozent 
-The first solar cells were used in the 1950s in niche applications such as the space flight with efficiencies under 10 percent. 
-%durch die oelkriese 1973 stieg das interesse an pv und alternativen energiequellen und 1977 das erste salor...? 
-Though, fuelled by the oil crisis in 1973 the interest in photovoltaic and alternative energy sources in general rose and the development of mass product was boosted. \\
-consumer market
-\\
 K5\\
 %Neben der g"ngigen kristallienen Siliziem Zelle gibt es auch Duennnschichtzellen wegen dem hohen Absorptionskoeffizenten und der geringen Eindringtiefe von veispielsweise amorphem Silizium oder auch CIS (siehe table p 84) wird nur wenig Material benötigt und flexible Zellen konnen hergestellt werden
-Besides the common crystalline silicon cells there are thin film cells which because of their high absorption coefficient of light and therefore shallow penetration depth of light
-need less material and can be used to create/produce flexible cells \\
-of amorph silicon or CIS (see table p84)
+Besides the common crystalline silicon cells 
+there are thin film cells 
+which have a higher absorption coefficient that classical crystalline silicon cell. 
+Therefore, the penetration depth of light is more shallow and less material is needed to produce a cell which can be flexible.
+%which because of their high absorption coefficient of light 
+%and therefore shallow penetration depth of light
+%need less material and can be used to produce flexible cells \\
+%of amorph silicon or CIS (see table p84)
 
@@
         CdTe&   direct&      1.45&    600&    37,000/cm&  0.3\\
-        a-Si&   direct&      1.42&    600&    40,000/cm&  0.2\\
+		\td{a-Si}&   direct&      1.42&    600&    40,000/cm&  0.2\\
         \hline
         \hline
-
     \end{tabular}
@@
 %Materialien aus der Grupper der Chalkopyrite wisen allesamt eine XXX Gitterstruktur auf genauso wie Namengeber der Gruppe, das Chalkopyrit (CuFeS2). 
-Materials from the chalcopyrite group (tetranogal crystal system) (eg CuInGaSe) can be used as absorber in such thin film cells.
-Meist wird ein Material mit der Summenformel $CuIn_XGA_{(1-x)}Se_2$ verwendet. 
+%Meist wird ein Material mit der Summenformel $CuIn_XGA_{(1-x)}Se_2$ verwendet. 
+Materials from the chalcopyrite group (tetragonal crystal system) (eg CuInGaSe(CIGS)) can be used as absorber in such thin film cells.
+Mostly a Material with the chemical formula  $\text{CuIn}_\text{x}\text{Ga}_{\text{(1-x)}}\text{Se}_2$ (CIGS).
+The awesome thing about CIGS is that the band gap can be varied by between 1eV and 1.7eV by varying the inidum gallium ratio accordingly. 
 Durch den hohen Unterschied der Bandabstaedne von CuInSe2 und CuGaSe2 kamnn durch entsprechende Mischverhaeltnisse von In und Ga der Bandabstand eingestellt werden (Tablep 142) Abbildung Bild 5.22 p143) beschreiben und bild für Modul
+Because of the large difference of band gaps of CuInSe2 and CuGaSe2 the band gap can be configured by mixing ratio of inidum and gallium (see table \ref{tab:cigs}).
 
@@
     \end{tabular}
+	\caption{band gaps of different chalcopyrites}
+	\label{tab:cigs}
 \end{table}

### 2022-03-14 Thesis/chapter/03-theoretical-background.tex
CIGS

@@
 Books PV, analytic otto? 
-\subsection{Photovoltaic and CSGI}
+\subsection{Photovoltaic and CIGS}
 \iffalse
@@
 The photoelectric effect was first described in 1839 by french scientist Alexandre Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel. 
-With the discovery of 
-photo conductivity of selenium
+With the discovery of photo conductivity of selenium
 %the correlation between the {change of the }resistance and the irradiating light 
-by British engineer Willouhgby Smith and his assistant Joseph May another relevant piece of the photovoltaic jigsaw was discovered. 
-In 1876 William Adam and Richard Day showed that 
+by British engineer Willouhgby Smith\cite{Smith1873Selenium} 
+%and his assistant Joseph May 
+another relevant piece of the photovoltaic jigsaw was discovered. 
+In 1876 William Adams and Richard Day\cite{Adams1876Selenium} showed that 
 the energy of light can be directly converted into electrical energy by a bar of selenium with attached platinum electrodes.
@@
 
-K5\\
+\subsection{CIGS}
 %Neben der g"ngigen kristallienen Siliziem Zelle gibt es auch Duennnschichtzellen wegen dem hohen Absorptionskoeffizenten und der geringen Eindringtiefe von veispielsweise amorphem Silizium oder auch CIS (siehe table p 84) wird nur wenig Material benötigt und flexible Zellen konnen hergestellt werden
-Besides the common crystalline silicon cells 
-there are thin film cells 
-which have a higher absorption coefficient that classical crystalline silicon cell. 
+Amorphous silicon and copper indium selenide (CIS) \td{(see next chapter)} have much higher absorption coefficients of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}) and can therefore be much thinner and use less material.
+Another vorteil of thin film cells is that they can be flexible. 
+%which because of their high absorption coefficient of light %and therefore shallow penetration depth of light%need less material and can be used to produce flexible cells \\%of amorph silicon or CIS (see table p84)
+Besides the common crystalline silicon cells there are thin film cells which have a higher absorption coefficient that classical crystalline silicon cell. 
 Therefore, the penetration depth of light is more shallow and less material is needed to produce a cell which can be flexible.
-%which because of their high absorption coefficient of light 
-%and therefore shallow penetration depth of light
-%need less material and can be used to produce flexible cells \\
-%of amorph silicon or CIS (see table p84)
 
-\begin{table}
+\begin{table}[htb]
+	\small
     \begin{tabular}{cccccc}
@@
         CdTe&   direct&      1.45&    600&    37,000/cm&  0.3\\
-		\td{a-Si}&   direct&      1.42&    600&    40,000/cm&  0.2\\
+		GaAs&   direct&      1.42&    600&    40,000/cm&  0.2\\
         \hline
@@
     \end{tabular}
+	\caption{\td{citeauthor(mertens)}}
+	\label{tab:cigs:alpha}
 \end{table}
@@
 {Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glas substrat} 
-\begin{table}
+\begin{table}[htb]
     \begin{tabular}{cccc}

### 2022-04-12 Thesis/chapter/03-theoretical-background.tex
behind

@@
 Books PV, analytic otto? 
-\subsection{Photovoltaic and CIGS}
+\subsection{Photovoltaics}
 \iffalse
@@
 Amorphous silicon and copper indium selenide (CIS) \td{(see next chapter)} have much higher absorption coefficients of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}) and can therefore be much thinner and use less material.
-Another vorteil of thin film cells is that they can be flexible. 
+Another advantage of thin film cells is that they can be used in flexible applications. 
 %which because of their high absorption coefficient of light %and therefore shallow penetration depth of light%need less material and can be used to produce flexible cells \\%of amorph silicon or CIS (see table p84)
-Besides the common crystalline silicon cells there are thin film cells which have a higher absorption coefficient that classical crystalline silicon cell. 
-Therefore, the penetration depth of light is more shallow and less material is needed to produce a cell which can be flexible.
+
+%Besides the common crystalline silicon cells there are thin film cells which have a higher absorption coefficient that classical crystalline silicon cell. 
+%Therefore, the penetration depth of light is more shallow and less material is needed to produce a cell which can be flexible.
 
@@
     \end{tabular}
-	\caption{\td{citeauthor(mertens)}}
+	\caption{data from \cite{mertens2015photovoltaik}}
 	\label{tab:cigs:alpha}

### 2022-04-26 Thesis/chapter/03-theoretical-background.tex
write on ZrO2

@@
 Books PV, analytic otto? 
+\\
+This chapter aims to shine light on the evolution of PV and 
+give some introduction on methods used during experimental and \td{analytical} phase of this work. 
 \subsection{Photovoltaics}
@@
 The grundlage for all pvs is the photovoltaik effect which was entdeckt by Albert Einstein adn for which he got the nobel price. 
-The Prinziple is easy: When the energy (E = hv) of the light is \td{large,strong,big,high}er than the binding energy of an electron the electron is ejected with the remaining energy as kinetic energy 
+The Prinziple is easy: When the energy (E = hv) of the light is \td{large,strong,high}er 
+than the binding energy of an electron the electron is ejected with the remaining energy as kinetic energy 
 \begin{math}
@@
 \subsubsection{Problems of current energy supply}
-The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
+The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
+and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
 will be exhausted within the next 100 years. 
 %This time period must of course taken with a grain of salt as it can happen that even though the resource are being exhausted they can rise from one year to another as new reserves are being discovered and explored.
-Even though this time period is not exact and highly dependent on external factors, this number is rather small and brings us in zugzwang
+Even though this time period is not exact and highly dependent on detection methods, 
+this number is rather small and brings us in zugzwang.
 
@@
 In 1876 William Adams and Richard Day\cite{Adams1876Selenium} showed that 
-the energy of light can be directly converted into electrical energy by a bar of selenium with attached platinum electrodes.
-And finally, in 1905 Einstein described the physical background of the photoelectric effect with his light quantum theory\cite{einstein1905erzeugung}.
-In the 1950s the first solar cells were used in niche applications such as the space flight with efficiencies under 10 percent. 
-Eventually, the interest in photovoltaic and alternative energy sources in general rose fuelled by the oil crisis in 1973 
+the energy of light can be directly converted into electrical energy by a bar of 
+selenium with attached platinum electrodes.
+And finally, in 1905 Einstein described the physical background of the photoelectric 
+effect with his light quantum theory\cite{einstein1905erzeugung}.
+In the 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space flight. 
+Eventually, the interest in photovoltaic and other alternative energy sources 
+rose - fuelled by the oil crisis in 1973 - 
 and the development of photovoltaic for the consumer market was boosted. \\
@@
 \subsection{CIGS}
-%Neben der g"ngigen kristallienen Siliziem Zelle gibt es auch Duennnschichtzellen wegen dem hohen Absorptionskoeffizenten und der geringen Eindringtiefe von veispielsweise amorphem Silizium oder auch CIS (siehe table p 84) wird nur wenig Material benötigt und flexible Zellen konnen hergestellt werden
-Amorphous silicon and copper indium selenide (CIS) \td{(see next chapter)} have much higher absorption coefficients of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}) and can therefore be much thinner and use less material.
-Another advantage of thin film cells is that they can be used in flexible applications. 
+%%%
+%Materials from the chalcopyrite group (tetragonal crystal system) (eg CuInGaSe(CIGS)) can be used as absorber in such thin film cells.
+CIGS ($\text{CuIn}_\text{x}\text{Ga}_{\text{(1-x)}}\text{Se}_2$) is of the chalcopyrite group (tetragonal crystal system) and can be used as thin film PV. 
+Just like CdTe, GaAs and amorphoous silicon CIGS have much higher absorption coeffiecients 
+(lower penetration depth) of visible light than crystlline silicon (see table \ref{tab:cigs:alpha}). 
+These thin film PVs not only use less material, but also can be used in flexible applications. 
+%%%
+%Amorphous silicon and copper indium selenide (CIS) \td{(see next chapter)} have much higher absorption coefficients of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}) and can therefore be much thinner and use less material.
+%Another advantage of thin film cells is that they can be used in flexible applications. 
 %which because of their high absorption coefficient of light %and therefore shallow penetration depth of light%need less material and can be used to produce flexible cells \\%of amorph silicon or CIS (see table p84)
-
-%Besides the common crystalline silicon cells there are thin film cells which have a higher absorption coefficient that classical crystalline silicon cell. 
-%Therefore, the penetration depth of light is more shallow and less material is needed to produce a cell which can be flexible.
 
@@
         \hline
-        Material&   Art&    Bandluecke [eV]&    Wavelenght [nm]&    Absorptionskoeffizent alpha&    Eindringtiefe [um]\\
+        Material&   Type&    Band Gap [eV]&    Wavelenght [nm]&    sbsortption coef. alpha&    penetration depth [um]\\
         \hline
@@
 %Meist wird ein Material mit der Summenformel $CuIn_XGA_{(1-x)}Se_2$ verwendet. 
-Materials from the chalcopyrite group (tetragonal crystal system) (eg CuInGaSe(CIGS)) can be used as absorber in such thin film cells.
-Mostly a Material with the chemical formula  $\text{CuIn}_\text{x}\text{Ga}_{\text{(1-x)}}\text{Se}_2$ (CIGS).
-The awesome thing about CIGS is that the band gap can be varied by between 1eV and 1.7eV by varying the inidum gallium ratio accordingly. 
-Durch den hohen Unterschied der Bandabstaedne von CuInSe2 und CuGaSe2 kamnn durch entsprechende Mischverhaeltnisse von In und Ga der Bandabstand eingestellt werden (Tablep 142) Abbildung Bild 5.22 p143) beschreiben und bild für Modul
-Because of the large difference of band gaps of CuInSe2 and CuGaSe2 the band gap can be configured by mixing ratio of inidum and gallium (see table \ref{tab:cigs}).
+%Materials from the chalcopyrite group (tetragonal crystal system) (eg CuInGaSe(CIGS)) can be used as absorber in such thin film cells.
+%Mostly a Material with the chemical formula  $\text{CuIn}_\text{x}\text{Ga}_{\text{(1-x)}}\text{Se}_2$ (CIGS).
+%The awesome thing about CIGS is that the band gap can be varied by between 1eV and 1.7eV by varying the inidum gallium ratio accordingly. 
+The band gap of CIGS can be varied by between 1eV and 1.7eV by varying the inidum gallium 
+ratio, accordingly.
+This is a result of the large difference of band gaps of CuInSe2 and CuGaSe2 (see table \ref{tab:cigs}). 
+%Durch den hohen Unterschied der Bandabstaedne von CuInSe2 und CuGaSe2 kamnn durch entsprechende Mischverhaeltnisse von In und Ga der Bandabstand eingestellt werden (Tablep 142) Abbildung Bild 5.22 p143) beschreiben und bild für Modul
+%Because of the large difference of band gaps of CuInSe2 and CuGaSe2 the band gap can be configured by mixing ratio of inidum and gallium (see table \ref{tab:cigs}).
 
@@
         \hline\hline
-        Materialkombination&    Name&   Bandabstand&    Kürzel\\
+        Empirical Formula&    Name&   Band Gap&    Abbreviation\\
         \hline
@@
 \subsection{Zirconium oxide}
+Zirconium oxide \td{(Zr02)} is ceramic with a bandgap of 5-7 eV and dielectric constant of 15-22\cite{Anwar2017}. 
+This makes it attractive as an insulator for semiconductor and \td{PV} industry. 
+It is monoclinic below 1170 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C. \td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
+%Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
+\td{COMMENT: solution age was not accounted for}
+what is important properites of zro2? 
 \subsection{Sputtering}
 %https://en.wikipedia.org/wiki/Sputter_deposition
+what is the principle behind sputtering
+what is sputtering, how does it work, what different kinds of sputtering is there, 
+what is is used for? 
+what was it used for in this work? 
 \subsection{SEM}
 \url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
+what is sputtering, how does it work, what different kinds of sputtering is there, what is is used for? 
 \subsection{Infrared absorption}
@@
 reinforcement learning could also have been a nice option
+\subsection{Linear Regression}

### 2022-05-02 Thesis/chapter/03-theoretical-background.tex
Sputtering first attempt

@@
 	\small
+    \center
     \begin{tabular}{cccccc}
@@
 
-CIGS\\ 
+%CIGS\\ 
 %Materialien aus der Grupper der Chalkopyrite wisen allesamt eine XXX Gitterstruktur auf genauso wie Namengeber der Gruppe, das Chalkopyrit (CuFeS2). 
@@
 %The awesome thing about CIGS is that the band gap can be varied by between 1eV and 1.7eV by varying the inidum gallium ratio accordingly. 
-The band gap of CIGS can be varied by between 1eV and 1.7eV by varying the inidum gallium 
-ratio, accordingly.
+The band gap of CIGS can be varied by between 1eV and 1.7eV by varying the inidum gallium ratio.
 This is a result of the large difference of band gaps of CuInSe2 and CuGaSe2 (see table \ref{tab:cigs}). 
@@
 
-{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glas substrat} 
+{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glas substrat, borrow book} 
+The standard substrate is glass \td{why?}. A flexible substrate is needed for a flexible module. 
+Plastics have a very low metling points and metals are conducting, but can be coated with a non conducting material such as \td{ZrO2}.
 \begin{table}[htb]
+    \center
     \begin{tabular}{cccc}
@@
 
-Um ein Modul flexibel zu machen kann statt Glas Stahl als stbstrat verwendet werden. 
-Allerdings wird ein Isolater zwischen Stahsubstrat und CIGS Zelle benötigt
+%Um ein Modul flexibel zu machen kann statt Glas Stahl als stbstrat verwendet werden. 
+%Allerdings wird ein Isolater zwischen Stahsubstrat und CIGS Zelle benötigt
 
@@
 %Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
-\td{COMMENT: solution age was not accounted for}
 what is important properites of zro2? 
 \subsection{Sputtering}
-%https://en.wikipedia.org/wiki/Sputter_deposition
-what is the principle behind sputtering
+% https://en.wikipedia.org/wiki/Sputter_deposition
+\td{what is the principle behind sputtering
 what is sputtering, how does it work, what different kinds of sputtering is there, 
@@
 what was it used for in this work? 
+}
+%Sputtering is a physical deposition method. 
+Sputtering describes the process when highly energetic particles collide with a surface 
+and through a cascade of momentum transfers surface particles are depleted and sputter from the surface.
+This process occurs naturally in outer space and is used in science and technology for 
+sputter cleaning, thin film deposition, analysis or etching. 
+The phenomenon was discovered in the middle of the 20th century\cite{Sigmund1987} and is
+a field of research with its own subfields, such as. 
+1.5h
+
+\td{A high voltage is angelegt at the source (a metal waffer). 
+Electrons with a high kinetic energy bump into the source and herausschießen metal atoms, 
+which will deposit on a target. 
+By ausrüsten the target with a mask, arbitrary musters can be obtained (e.g. contact arrays).
+}
+How are the electrons erzeugt? 
+\td{With a magnetron (a micro wave erzeuging high vacuum bauteil) a plasma is sustained. 
+}
+Find source
 \subsection{SEM}

### 2022-05-05 Thesis/chapter/03-theoretical-background.tex
sputtering 2nd attempt

@@
 what is important properites of zro2?
+
 \subsection{Sputtering}
@@
 %Sputtering is a physical deposition method. 
-Sputtering describes the process when highly energetic particles collide with a surface 
-and through a cascade of momentum transfers surface particles are depleted and sputter from the surface.
-This process occurs naturally in outer space and is used in science and technology for 
+Sputtering describes the process of particles being sputtered from a surface after 
+impact of highly energetic particles.
+These high energy particles start cascades of momentum transfers. 
+If a path of a cascade reaches back to the surface and the kinetic energy of a surface 
+particle exceeds the binding energy, it is ejected (or sputtered).
+
+%Sputtering describes the process when highly energetic particles collide with a surface 
+%and through a cascade of momentum transfers surface particles are depleted and sputter from the surface.
+This process occurs naturally in outer space (through alpha particles, electrons etc.) 
+and is used in science and technology for 
 sputter cleaning, thin film deposition, analysis or etching. 
-The phenomenon was discovered in the middle of the 20th century\cite{Sigmund1987} and is
-a field of research with its own subfields, such as. 
+The phenomenon was discovered and identified as an atomic collision phenomenon in the 
+middle of the 20th century and now is a field of research with its own niche subfields 
+(e.g. sputtering of exotic materials (such as condensed gases, planetary
+atmospheres, lunar dust grains, proteins and viruses), high density cascades and 
+linear cascades, which could be called classical sputtering)
+%sputtering of insulators and biomolecular material)
+\cite{Sigmund1987}.
+%
+In this work it was used to deposit thin gold contacts through a mask. 
+A directional current sputtering machine was used. 
+\td{describe the machine}
+A argon plasma in a strong electrical field (some kV) provides the highly energetic particles. 
+Argon ions are accelerated through the field to the source (a metal wafer), which acts as cathode, and start cascades. 
+In order to maximise the yield (sputtering speed) a magnet is used to trap the plasma close to source. 
+Plasma sputtering with a strong magnet to 
 1.5h 
-
-\td{A high voltage is angelegt at the source (a metal waffer). 
+\\
+\td{A high voltage is angelegt at the source (a metal wafer). 
 Electrons with a high kinetic energy bump into the source and herausschießen metal atoms, 
@@
 Find source
+
 \subsection{SEM}

### 2022-05-09 Thesis/chapter/03-theoretical-background.tex
comment Swann1988 sputtering

@@
 \subsection{Zirconium oxide}
-Zirconium oxide \td{(Zr02)} is ceramic with a bandgap of 5-7 eV and dielectric constant of 15-22\cite{Anwar2017}. 
+Zirconium oxide \td{(ZrO2)} is ceramic with a bandgap of 5-7 eV and dielectric constant of 15-22\cite{Anwar2017}. 
 This makes it attractive as an insulator for semiconductor and \td{PV} industry. 
-It is monoclinic below 1170 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C. \td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
+It is monoclinic below 1170 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Stevens1986}.
+%\td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
 %Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
-what is important properites of zro2?
+\td{what is important properites of zro2? }
 
@@
 what was it used for in this work? 
+}
+\td{
+- phenomon of high energy particle bombardement know off particles from a source\\
+- options to create high energy particles: electron gun, thermal evaporation or cathode? 
+- vorteile sind: Swann p 67(2)
+- need low pressure bcs of MFP but plasma needs gas to sustain
+- source is target and target is substrate
+
 }

### 2022-05-11 Thesis/chapter/03-theoretical-background.tex
400 words sputtering freewriting

@@
 \td{
-- phenomon of high energy particle bombardement know off particles from a source\\
+- phenomon of high energy particle bombardement know off particles from a source
 - options to create high energy particles: electron gun, thermal evaporation or cathode? 
@@
 - source is target and target is substrate
-
 }
@@
 }
-Find source
+Find source\\\\
+
+SPUTTERING FREEWRITING: 
+what is sputtering? \\
+sputtering is the processes of highly energetic ions (only ions?) hitting a surface and atoms or molecules being expelled. 
+This is a physical vapor deposition technique (PVD).
+PVD can be unterteils in thermal and highly energetic activated.
+Sputtering is part of HEA, which hast the convenience, that some substrates don't withstand high temperatures.
+what can it be used for?\\
+Sputtering moved from being a curious experiment to having multi anwendungen in science (forschung) and engineering, becuase the sputtered materials can be deposited on  substrate. 
+anwendungen reichen from, thin films for PV, electrical circuits, storage media such as CDs and DVDs etc. 
+Vorteile of sputtering are also a good adherent to the substrate and good step coverage and what else? 
+different styles\\
+The most successful durchgesetzte kind of sputtering devices are magnetron sputtering devices, which wiederum can be unterteilt in DC (directional current) RF (radio frequency) sputtering and reactive sputtering.
+how does it work? \\
+A high voltage is applied to the source (make skizze), which acts as a cathode. 
+The cathode, then, emits electrons which collide with XXX gas (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
+The argon may get ionized by electron and the argon cation will be accelerated to the cathode. If the cation has enough energy it will bump off a target atom or molecule. 
+This happens by a cascade of momentum transfers, which can reach the surface again. 
+If the suface particle gets momentum pointing from the surface and the remaining kinetic energy is higher then the binding energy, the particle is sputtered. 
+The pressure should be small, such that the sputtered particle has a moeglichst long mean free path (MFP), but on the other hand there is a minimum pressure to keep the plasma going. 
+Usual pressures are around (1 mPa?).
+\td{mention the substrate parallel to the target}
+
+A magnetron can be placed behind the cathode (target) in order to trap ejected ions close to the electron source. 
+This prevents high energy electrons from reaching the target and undoing the deposited layer and increasing the probability of an electron colliding with an argon atom and ionizing it
 

### 2022-05-12 Thesis/chapter/03-theoretical-background.tex
03-theoretical background intro finished

@@
 %\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
+\ds{
 \todo{Structure: Free writing} 
@@
 Books PV, analytic otto? 
-\\
-This chapter aims to shine light on the evolution of PV and 
-give some introduction on methods used during experimental and \td{analytical} phase of this work. 
+}
+This chapter can be broken down into three section. 
+The first chapter tries to shine light on the evolution of PV and give some background on \gls{cigs}.
+The second chapter reads about material-scientific methods which were used during the practical part of this work. 
+The last and third part focuses on the information technological, algorithmic and analytics methods used to optimize and predict material properties. 
+%This chapter aims to shine light on the evolution of PV and on CIGSand 
+%give some introduction on methods used during experimental and \td{analytical} phase of this work. 
 \subsection{Photovoltaics}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Problems of current energy supply}
+The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
+and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
+will be exhausted within the next 100 years. 
+%This time period must of course taken with a grain of salt as it can happen that even though the resource are being exhausted they can rise from one year to another as new reserves are being discovered and explored.
+Even though this time period is not exact and highly dependent on detection methods, 
+this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
+One viable options is \gls{pv}.
+
 \iffalse
-The grundlage for all pvs is the photovoltaik effect which was entdeckt by Albert Einstein adn for which he got the nobel price. 
+The basis for all pvs is the photovoltaik effect which was entdeckt by Albert Einstein adn for which he got the Nobel price. 
 The Prinziple is easy: When the energy (E = hv) of the light is \td{large,strong,high}er 
@@
 \fi
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Problems of current energy supply}
-The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
-and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
-will be exhausted within the next 100 years. 
-%This time period must of course taken with a grain of salt as it can happen that even though the resource are being exhausted they can rise from one year to another as new reserves are being discovered and explored.
-Even though this time period is not exact and highly dependent on detection methods, 
-this number is rather small and brings us in zugzwang.
-
 \subsubsection{History of Photovoltaics}
@@
 The photoelectric effect was first described in 1839 by french scientist Alexandre Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel. 
-With the discovery of photo conductivity of selenium
-%the correlation between the {change of the }resistance and the irradiating light 
-by British engineer Willouhgby Smith\cite{Smith1873Selenium} 
-%and his assistant Joseph May 
-another relevant piece of the photovoltaic jigsaw was discovered. 
+Another relevant piece of the photovoltaic jigsaw was discovered 
+with the discovery of photo conductivity of selenium
+by British engineer Willouhgby Smith\cite{Smith1873Selenium}.
 In 1876 William Adams and Richard Day\cite{Adams1876Selenium} showed that 
@@
 
-\subsection{CIGS}
+\subsubsection{Crystalline Silicon Photovoltaics}
+The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
+
+\td{
+what is it? 
+What is it used for? 
+How does it work? 
+What different kinds are there? 
+}
+
+\subsubsection{CIGS}
 %%%
 %Materials from the chalcopyrite group (tetragonal crystal system) (eg CuInGaSe(CIGS)) can be used as absorber in such thin film cells.
-CIGS ($\text{CuIn}_\text{x}\text{Ga}_{\text{(1-x)}}\text{Se}_2$) is of the chalcopyrite group (tetragonal crystal system) and can be used as thin film PV. 
-Just like CdTe, GaAs and amorphoous silicon CIGS have much higher absorption coeffiecients 
-(lower penetration depth) of visible light than crystlline silicon (see table \ref{tab:cigs:alpha}). 
-These thin film PVs not only use less material, but also can be used in flexible applications. 
+CIGS ($\text{CuIn}_\text{x}\text{Ga}_{\text{(1-x)}}\text{Se}_2$) is of the chalcopyrite group (tetragonal crystal system) and can be used as thin film \gls{pv}. 
+Just like CdTe, GaAs and amorphous silicon CIGS have much higher absorption coefficients 
+(lower penetration depth) of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}). 
+These thin film \gls{pv}s not only use less material, but also can be used in flexible applications. 
 %%%
@@
         \hline
-        Material&   Type&    Band Gap [eV]&    Wavelenght [nm]&    sbsortption coef. alpha&    penetration depth [um]\\
+		Material&   Type&    Band Gap [\ev{}]&    Wavelength [\nm{}]&    Absorption coef. $\alpha$    &Penetration Depth [\um{}]\\
         \hline
@@
 
-%CIGS\\ 
-%Materialien aus der Grupper der Chalkopyrite wisen allesamt eine XXX Gitterstruktur auf genauso wie Namengeber der Gruppe, das Chalkopyrit (CuFeS2). 
-%Meist wird ein Material mit der Summenformel $CuIn_XGA_{(1-x)}Se_2$ verwendet. 
-%Materials from the chalcopyrite group (tetragonal crystal system) (eg CuInGaSe(CIGS)) can be used as absorber in such thin film cells.
-%Mostly a Material with the chemical formula  $\text{CuIn}_\text{x}\text{Ga}_{\text{(1-x)}}\text{Se}_2$ (CIGS).
-%The awesome thing about CIGS is that the band gap can be varied by between 1eV and 1.7eV by varying the inidum gallium ratio accordingly. 
-The band gap of CIGS can be varied by between 1eV and 1.7eV by varying the inidum gallium ratio.
+Amazingly, the band gap of CIGS can be varied by between 1eV and 1.7eV by varying the indium gallium ratio.
 This is a result of the large difference of band gaps of CuInSe2 and CuGaSe2 (see table \ref{tab:cigs}). 
@@
 
-{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glas substrat, borrow book} 
+{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book} 
 The standard substrate is glass \td{why?}. A flexible substrate is needed for a flexible module. 
-Plastics have a very low metling points and metals are conducting, but can be coated with a non conducting material such as \td{ZrO2}.
+Plastics have a very low melting points and metals are conducting, but can be coated with a non conducting material such as \td{\gls{zro}}.
 \begin{table}[htb]
@@
 \url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
-what is sputtering, how does it work, what different kinds of sputtering is there, what is is used for? 
+what is sputtering, 
+how does it work, 
+what different kinds of sputtering is there, 
+what is is used for? 
+\cite{McMullan1995}
+\cite{Vernon2000}
+\cite{Kaliva2020}
+
 \subsection{Infrared absorption}

### 2022-05-12 Thesis/chapter/03-theoretical-background.tex
ZrO2 ramble

@@
 %\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
+\ds{what is it? What is it used for? How does it work? What different kinds are there? }
 \ds{
@@
 The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
-
-\td{
-what is it? 
-What is it used for? 
-How does it work? 
-What different kinds are there? 
-}
+\td{what is it? What is it used for? How does it work? What different kinds are there? }
 
@@
 
-{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book} 
-The standard substrate is glass \td{why?}. A flexible substrate is needed for a flexible module. 
-Plastics have a very low melting points and metals are conducting, but can be coated with a non conducting material such as \td{\gls{zro}}.
+\td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book} 
+The standard substrate is glass 
+because of it's high thermal stability, resistance and hardness. 
+A flexible substrate is needed for a flexible module, though. 
+Plastics have a very low melting points and metals are conducting, but can be coated with a non conducting material such as \gls{zro}.
 \begin{table}[htb]
@@
         \hline
-        CuInSe2&       copper indium di selenide&  1&  CISe\\
-        CuInS2&        copper indium di sulfide&  1.5&  CIS\\
-        CuGaSe2&       copper gallium di selenide&  1.7&  CIGSe\\
-        CuGaS2&        copper gallium di sulfide&  1.55&  CIGS\\
+		\ch{CuInSe2}&       copper indium di selenide&  1&  CISe\\
+		\ch{CuInS2}&        copper indium di sulfide&  1.5&  CIS\\
+		\ch{CuGaSe2}&       copper gallium di selenide&  1.7&  CIGSe\\
+		\ch{CuGaS2}&        copper gallium di sulfide&  1.55&  CIGS\\
         \hline\hline
@@
 
-%Um ein Modul flexibel zu machen kann statt Glas Stahl als stbstrat verwendet werden. 
-%Allerdings wird ein Isolater zwischen Stahsubstrat und CIGS Zelle benötigt
-
-\subsection{Zirconium oxide}
-Zirconium oxide \td{(ZrO2)} is ceramic with a bandgap of 5-7 eV and dielectric constant of 15-22\cite{Anwar2017}. 
-This makes it attractive as an insulator for semiconductor and \td{PV} industry. 
-It is monoclinic below 1170 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Stevens1986}.
+\subsubsection{Zirconium oxide}
+Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
+This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
+It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
+The cubic phase can be stabilzed down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage due to phase transition\cite{Nielsen2005}.
 %\td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
 %Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
+It is not poisonous. \td{cite?}
+It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
+See ref \cite{Nielsen2005} for 2.3 Hydrous Zirconium Oxide 2.3 and 2.20 Zirconium Alkoxides.
+
 \td{what is important properites of zro2? }
+\td{what is it? What is it used for? How does it work? What different kinds are there? }
+
+\subsubsection{Sol-Gel}
+\td{what is it? What is it used for? How does it work? What different kinds are there? }
+One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
 

### 2022-05-12 Thesis/chapter/04-experimental.tex
experimental comment

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\td{COMMENT: solution age was not accounted for}
 In this section the used chemicals and substrates, experimental procedures and any used 
@@
 was added to \gls{ipo} and both were stirred for one hour. 
-These additives were added to influence pH and surface tension with the goal to influence the resulting layer.
+These additives were added to influence pH and surface tension with the goal to influence the resulting layer \td{see Parvulescu2015}
 The \gls{water}-\gls{ipo} mixture was added to the other solution and stirred over night. 

### 2022-05-13 Thesis/chapter/05-computational-details.tex
add ML wikis

@@
 \label{sec:eval}
+Reading list
+\begin{itemize}
+    \item https://de.wikipedia.org/wiki/Globaler_F-Test
+    \item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
+    \item Curse of dimensionality scholar
+    \item linear regression von ungar 
+    \item ridge regression + support vector machine
+    \item correlation vs covariance
+    \item https://en.wikipedia.org/wiki/Regression_analysis
+    \item https://en.wikipedia.org/wiki/Noise_reduction
+    \item https://en.wikipedia.org/wiki/Feature_extraction
+    \item https://en.wikipedia.org/wiki/Feature_selection
+    \item https://en.wikipedia.org/wiki/Dimensionality_reduction
+    \item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
+    \item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
+    \item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
+    \item 
+    \item 
+    \item 
+\end{itemize}
 %\td{describe problem and solution found}

### 2022-05-14 Thesis/chapter/03-theoretical-background.tex
wiki thesis
refine sputtering

@@
 \ds{what is it? What is it used for? How does it work? What different kinds are there? }
+\ds{what? how? why?}
 \ds{
@@
 It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
-The cubic phase can be stabilzed down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage due to phase transition\cite{Nielsen2005}.
+The cubic phase can be stabilzed down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
+when cooling and undergoing phase transistion\cite{Nielsen2005}.
+%due to phase transition\cite{Nielsen2005}.
 %\td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
 %Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
-It is not poisonous. \td{cite?}
+%It is not poisonous. \td{cite?}
 It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
-See ref \cite{Nielsen2005} for 2.3 Hydrous Zirconium Oxide 2.3 and 2.20 Zirconium Alkoxides.
+%See ref \cite{Nielsen2005} for 2.3 Hydrous Zirconium Oxide 2.3 and 2.20 Zirconium Alkoxides.
+Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3}). 
+"Zirconium alkoxides hyrdolize quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.
 
-\td{what is important properites of zro2? }
-\td{what is it? What is it used for? How does it work? What different kinds are there? }
+%\td{what is important properites of zro2? }
+%\td{what is it? What is it used for? How does it work? What different kinds are there? }
 
@@
 % https://en.wikipedia.org/wiki/Sputter_deposition
+\iffalse
 \td{what is the principle behind sputtering
@@
 impact of highly energetic particles.
-These high energy particles start cascades of momentum transfers. 
-If a path of a cascade reaches back to the surface and the kinetic energy of a surface 
+These high energy particles start cascades of momentum transfers (see figure \td{cp sigmund 1969}). 
+If a path of such a momentum transfer cascade reaches back to the surface and the kinetic energy of a surface 
 particle exceeds the binding energy, it is ejected (or sputtered).
@@
 The phenomenon was discovered and identified as an atomic collision phenomenon in the 
-middle of the 20th century and now is a field of research with its own niche subfields 
+middle of the 20th century and is now a field of research with its own niche subfields 
 (e.g. sputtering of exotic materials (such as condensed gases, planetary
@@
 \td{describe the machine}
-A argon plasma in a strong electrical field (some kV) provides the highly energetic particles. 
+An argon plasma in a strong electrical field (some kV) provides the highly energetic particles. 
 Argon ions are accelerated through the field to the source (a metal wafer), which acts as cathode, and start cascades. 
@@
 Find source\\\\
+\fi
 
-SPUTTERING FREEWRITING: 
-what is sputtering? \\
-sputtering is the processes of highly energetic ions (only ions?) hitting a surface and atoms or molecules being expelled. 
-This is a physical vapor deposition technique (PVD).
-PVD can be unterteils in thermal and highly energetic activated.
-Sputtering is part of HEA, which hast the convenience, that some substrates don't withstand high temperatures.
-what can it be used for?\\
-Sputtering moved from being a curious experiment to having multi anwendungen in science (forschung) and engineering, becuase the sputtered materials can be deposited on  substrate. 
-anwendungen reichen from, thin films for PV, electrical circuits, storage media such as CDs and DVDs etc. 
-Vorteile of sputtering are also a good adherent to the substrate and good step coverage and what else? 
-different styles\\
-The most successful durchgesetzte kind of sputtering devices are magnetron sputtering devices, which wiederum can be unterteilt in DC (directional current) RF (radio frequency) sputtering and reactive sputtering.
-how does it work? \\
-A high voltage is applied to the source (make skizze), which acts as a cathode. 
-The cathode, then, emits electrons which collide with XXX gas (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
-The argon may get ionized by electron and the argon cation will be accelerated to the cathode. If the cation has enough energy it will bump off a target atom or molecule. 
-This happens by a cascade of momentum transfers, which can reach the surface again. 
-If the suface particle gets momentum pointing from the surface and the remaining kinetic energy is higher then the binding energy, the particle is sputtered. 
-The pressure should be small, such that the sputtered particle has a moeglichst long mean free path (MFP), but on the other hand there is a minimum pressure to keep the plasma going. 
-Usual pressures are around (1 mPa?).
-\td{mention the substrate parallel to the target}
+%SPUTTERING FREEWRITING: 
+%what is sputtering? \\
+Sputtering is the processes of highly energetic ions hitting a surface and atoms or molecules being expelled. 
+This is called a physical vapor deposition (PVD) technique. 
+PVD can be divided into activation by thermal energy and activation by energetic particle bombardment. %\td{high-energy particles}.
+%thermal and highly energetic particles activated. 
+Sputtering is of the latter, which 
+is advantageous if substrates can't withstand high temperatures.
+%has the convenience, that some substrates can't withstand high temperatures. 
+%\td{what can it be used for?}\\
+Sputtering evolved from being a curious experiment in the middle of the 20th century to having various applications in research and engineering.
+Use cases vary from thin films depositions for \gls{pv}, for electrical circuits or for storage media such as CDs and DVDs 
+over sputter cleaning and etching to analysis.
+Advantages of 
+sputtered thin films include good adhesion to the substrate and good step coverage. 
+%sputtering are also a good adherent to the substrate and good step coverage and what else?
 
-A magnetron can be placed behind the cathode (target) in order to trap ejected ions close to the electron source. 
-This prevents high energy electrons from reaching the target and undoing the deposited layer and increasing the probability of an electron colliding with an argon atom and ionizing it
+%\td{how does it work?}\\
+A high voltage is applied to 
+two parallel electrode with low pressure gas in between. 
+The target acts as cathode and the substrate (holder) as anode (see \td{fig}).
+%the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
+%(the substrate represents the anode). 
+The cathode, then, emits electrons which collide with a gas particle (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
+Some gas particles may get ionized by the collision and the gas cation is accelerated to the cathode. 
+If the cation has enough energy it will bump off a target atom or molecule from the surface. 
+This happens by a cascade of momentum transfers, which can reach the surface again (see fig \td{cp sigmund69}). 
+If the surface particle gets momentum pointing away from the bulk and the remaining kinetic energy is higher then the binding energy, the particle is sputtered. 
+The pressure should be small, such that the sputtered particle has a long mean free path (MFP), but on the other hand there is a minimum pressure to keep the plasma going. 
+Usual pressures are around 1 mPa (1 mbar) or lower\cite{Swann}.
+
+A magnetron can be placed behind the cathode (target) in order to trap ejected electrons close to the source. 
+This prevents high energy electrons from reaching the target and undoing the deposited layer and this also increases the probability of an electron colliding with an argon atom and ionizing it.
+
+When oxygen or nitrogen are added to the  gas this is called reactive sputtering.
+Sputtered atoms will react with the gas and result in oxide or nitrides layers, respectively.
+The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning\td{cite? What is poisoned?}.
+
+The limitation of only being able to use conducting materials as targets can be circumvented by using a radio frequency electrical field. 
+This prevents a charge building up on the target. \td{why is a charge?}
+Although RF sputtering is more versatile, DC sputtering is more common because of it's simpler system and economical reasons.
+%Through this method only conducting materials can be sputtered, be
+\td{sputtered particles are neutral and not influenced by the electrical field}
+%\td{different styles}\\
+%The most successful/common/established type of sputtering devices are magnetron sputtering machines, which 
+%Sputtering devices can be separated in DC (directional current) and RF (radio frequency) sputtering and reactive sputtering. 
+%During RF sputtering, the voltage is wobbling which prevents charge accumulation on the target and thus also non conduction targets can be sputtered.
 

### 2022-05-17 Thesis/chapter/03-theoretical-background.tex
cleaning and SEM

@@
 %\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
+\td{https://en.wikipedia.org/wiki/Thesis}
 \ds{what is it? What is it used for? How does it work? What different kinds are there? }
@@
 The last and third part focuses on the information technological, algorithmic and analytics methods used to optimize and predict material properties.
-%This chapter aims to shine light on the evolution of PV and on CIGSand 
-%give some introduction on methods used during experimental and \td{analytical} phase of this work. 
+
 \subsection{Photovoltaics}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Materials and Their Analysis}
 \subsubsection{Zirconium oxide}
@@
 
-\subsection{Sputtering}
-% https://en.wikipedia.org/wiki/Sputter_deposition
-\iffalse
-\td{what is the principle behind sputtering
-what is sputtering, how does it work, what different kinds of sputtering is there, 
-what is is used for? 
-what was it used for in this work? 
-}
-\td{
-- phenomon of high energy particle bombardement know off particles from a source
-- options to create high energy particles: electron gun, thermal evaporation or cathode? 
-- vorteile sind: Swann p 67(2)
-- need low pressure bcs of MFP but plasma needs gas to sustain
-- source is target and target is substrate
-}
-%Sputtering is a physical deposition method. 
-Sputtering describes the process of particles being sputtered from a surface after 
-impact of highly energetic particles.
-These high energy particles start cascades of momentum transfers (see figure \td{cp sigmund 1969}). 
-If a path of such a momentum transfer cascade reaches back to the surface and the kinetic energy of a surface 
-particle exceeds the binding energy, it is ejected (or sputtered).
-
-%Sputtering describes the process when highly energetic particles collide with a surface 
-%and through a cascade of momentum transfers surface particles are depleted and sputter from the surface.
-This process occurs naturally in outer space (through alpha particles, electrons etc.) 
-and is used in science and technology for 
-sputter cleaning, thin film deposition, analysis or etching. 
-The phenomenon was discovered and identified as an atomic collision phenomenon in the 
-middle of the 20th century and is now a field of research with its own niche subfields 
-(e.g. sputtering of exotic materials (such as condensed gases, planetary
-atmospheres, lunar dust grains, proteins and viruses), high density cascades and 
-linear cascades, which could be called classical sputtering)
-%sputtering of insulators and biomolecular material)
-\cite{Sigmund1987}.
-%
-In this work it was used to deposit thin gold contacts through a mask. 
-A directional current sputtering machine was used. 
-\td{describe the machine}
-An argon plasma in a strong electrical field (some kV) provides the highly energetic particles. 
-Argon ions are accelerated through the field to the source (a metal wafer), which acts as cathode, and start cascades. 
-In order to maximise the yield (sputtering speed) a magnet is used to trap the plasma close to source. 
-Plasma sputtering with a strong magnet to 
-1.5h 
-\\
-\td{A high voltage is angelegt at the source (a metal wafer). 
-Electrons with a high kinetic energy bump into the source and herausschießen metal atoms, 
-which will deposit on a target. 
-By ausrüsten the target with a mask, arbitrary musters can be obtained (e.g. contact arrays).
-}
-How are the electrons erzeugt? 
-\td{With a magnetron (a micro wave erzeuging high vacuum bauteil) a plasma is sustained. 
-}
-Find source\\\\
-\fi
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Sputtering}
 %SPUTTERING FREEWRITING: 
@@
 This is called a physical vapor deposition (PVD) technique. 
-PVD can be divided into activation by thermal energy and activation by energetic particle bombardment. %\td{high-energy particles}.
-%thermal and highly energetic particles activated. 
+PVD can be divided into activation by thermal energy and activation by energetic particle bombardment. 
 Sputtering is of the latter, which 
 is advantageous if substrates can't withstand high temperatures.
-%has the convenience, that some substrates can't withstand high temperatures. 
 %\td{what can it be used for?}\\
@@
 sputtered thin films include good adhesion to the substrate and good step coverage.
-%sputtering are also a good adherent to the substrate and good step coverage and what else?
 
@@
 %the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
-%(the substrate represents the anode). 
 The cathode, then, emits electrons which collide with a gas particle (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
@@
 If the surface particle gets momentum pointing away from the bulk and the remaining kinetic energy is higher then the binding energy, the particle is sputtered. 
-The pressure should be small, such that the sputtered particle has a long mean free path (MFP), but on the other hand there is a minimum pressure to keep the plasma going. 
-Usual pressures are around 1 mPa (1 mbar) or lower\cite{Swann}.
+The pressure should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand there is a minimum pressure to keep the plasma going. 
+Usual pressures are around 1 Pa ($10^{-2}$ mbar) or lower\cite{Swann1988}.
 
@@
 Although RF sputtering is more versatile, DC sputtering is more common because of it's simpler system and economical reasons.
-%Through this method only conducting materials can be sputtered, be
 \td{sputtered particles are neutral and not influenced by the electrical field}
-%\td{different styles}\\
-%The most successful/common/established type of sputtering devices are magnetron sputtering machines, which 
-%Sputtering devices can be separated in DC (directional current) and RF (radio frequency) sputtering and reactive sputtering. 
-%During RF sputtering, the voltage is wobbling which prevents charge accumulation on the target and thus also non conduction targets can be sputtered.
 
-\subsection{SEM}
+\subsubsection{Scanning electron Microscopy}
 \url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
+\Gls{sem} is a microscopical technique which allows visualisation of surfaces with features in the nano meter regime. 
+While optical microscopes use visible light and optical lenses the \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
+%Instead of light, it uses electrons with shorter wavelengths. zum abbilden
+This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to light\cite{Kaliva2020}.
+The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons. 
+Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
+Electrons are \td{created} by either \gls{feg}, where are strong electrical field rips electrons from the bulk and thermionic guns where the filament (tungsten W or \ch{LaB6} (brigther and longer lasting but more expensive)) is heated until electrons are emitted.
+Electrons are then accelerated by a voltage of 2 to 40 kV and bundled into narrow beams\cite{Vernon2000} by lenses.
+\td{A high \gls{mfp} is needed for electrons to travel from the source to the sample and to the detector. Thus, a very low pressure is in the inside.}
+It was used as a preliminary way of checking the surface condition. 
+%This allows greater detail. 
+why? 
+\td{what? how? why?}
 what is sputtering, 
@@
 
-\subsection{Infrared absorption}
+\subsubsection{Infrared absorption}
 \td{IR around page 45;
@@
 }
-\subsection{X-Ray Diffraction}
-\url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
+\subsubsection{X-Ray Diffraction}
+\gls{xrd} is used to study the crystalline strucutre of materlias since X-rays wavelengths (between 0.2 and \nm{10}) are comparable to the interatomic spacing of crystalline solids.
+\cite{Kaliva2020}.
+Each crystalline material has discreet atomc structure, which upon irradiation with X-rays causes constructive and destructive interference and generates unique diffraction patterns. 
+XRD \td{spectra} of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad cruve with a maximum extending over several degrees (2$\theta$).
+
 \url{https://chem.libretexts.org/Courses/Franklin_and_Marshall_College/Introduction_to_Materials_Characterization__CHM_412_Collaborative_Text/Diffraction_Techniques/X-ray_diffraction_(XRD)_basics_and_application}\\
-\subsection{Particle Swarm Optimization}
+
 \subsection{Machine Learning}
-\subsubsection{History}
-\subsubsection{different kinds} 
+\paragraph{History}
+some text to test
+\paragraph{different kinds} 
 supervised vs unsupervised
 classification (discrete) vs regression
-\subsection{Princlipal Component Analysis}
+\paragraph{Particle Swarm Optimization}
+\paragraph{Princlipal Component Analysis}
 reinforcement learning could also have been a nice option
-\subsection{Linear Regression}
+\paragraph{Linear Regression}

### 2022-05-17 Thesis/chapter/03-theoretical-background.tex
IR freewriting of chapter from schwedt

@@
 }
+\td{what, how, why?}
+\Gls{ir} spectroscopy is molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between $10^{-3}$ and $10^{-6}$ \nm{}) with molecules. \cite{Schwedt2008}
+\td{FREE WRITING:}
+light is described as periodic electro magnetic wave which moves. 
+All \gls{em} waves move with the speed of light c = 300k km /s in vacuum. 
+talk about $E=h\cdot v$ and $\nu=c/\lambda$ and $\bar{\nu}=1/\lambda$
+shorter wavelengths (higher frequencies) carry more energy. 
+In practice the spectrum \gls{em} waves are unterteilt in different things. 
+from high to low energie: Xray, \gls{uv}, vis, (near, middle and far) \gls{ir}, microwaves and radiowaves. 
+Xrays interact with core electrons, \gls{uv} and vis with valence electrons, ir with schwingungne mol rot and translation, microwaves with rotation and radio with electron and nuclear spin. 
+molecular vibrations are unterteilt in valenz and deformation vibration.
+absorbance pre din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
+The absorbance intensity is abhaengig von wave length and molecule structure. 
+Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum.
+
+Ein molekule hat $F=3N$ (N anzahl der atome) freiheitsgrade, wobei $F_T=3$ translation und $F_R=3$ (2 für lineare molecules) wodurch sich die anzahl der vibration reduces to $F_V=3N-6$ ($3N-5$) for vibrations.
+vibrations are unterteils in valence vibrations (change of bond length) and deformation (change of bindungs angle). 
+only vibrations with change in dipole momemnt are \gls{ir} active.
+
+differences to UVVis: transmission instead of absorbance, higher energy left instead right, base line on top instead of bottom.
+\paragraph{(Fourier Transform) Infrared spectrometer}
+ A ceramic material (Nernst glower) is heated to \oc{1600} as light source. 
+ In the two strahlen spectrometer the light is split, send through the sample and a reference, combined and send through a monochromator to a detector. 
+ In the \gls{ft}\gls{ir} spectrometer the beam is send thourhg the sample, split and reflected from a static and from a moving mirror, recombined and detected by a photo multiplier (a bauteil which transforms photons into electircal signals).
+
 \subsubsection{X-Ray Diffraction}

### 2022-05-20 Thesis/chapter/03-theoretical-background.tex
clean unneeded text

@@
-%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
 \td{https://en.wikipedia.org/wiki/Thesis}
@@
 \ds{what? how? why?}
-\ds{
-\todo{Structure: Free writing} 
-Ueber das Material, also PV und speziell CIGS (copper indium gallium sulfide) 
-ueber den MC prozess berichten, also DB, i-v curven, sputtering, sem, ir, xrd
-ueber den it ml stuff und statistisch, also ML algemein, pso im speziellen 
-perfekt fuer intro einfach mal erwaehnen was wo in diesem capitel zu finden sein wird. 
-Books PV, analytic otto? 
-}
 This chapter can be broken down into three section. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Problems of current energy supply}
@@
 will be exhausted within the next 100 years. 
-%This time period must of course taken with a grain of salt as it can happen that even though the resource are being exhausted they can rise from one year to another as new reserves are being discovered and explored.
 Even though this time period is not exact and highly dependent on detection methods, 
@@
 
-\iffalse
-The basis for all pvs is the photovoltaik effect which was entdeckt by Albert Einstein adn for which he got the Nobel price. 
-The Prinziple is easy: When the energy (E = hv) of the light is \td{large,strong,high}er 
-than the binding energy of an electron the electron is ejected with the remaining energy as kinetic energy 
-\begin{math}
-	E_{kin}=hv - Eb
-\end{math}
-Different Materials have different binding energies. 
-Metals do have in general lower binding energies than covalent bound material and semiconductors do have even lowers E_b. Really? 
-That's Silica is in a lot of PVs. 
-The next generation of PVs. 
-CIGS has in contrast to silicon based PV a direct band gap\td{source and what does that mean?}
-duennschicht pv, haben eine effeftivitaet von 7-16\% vs 15-22\% \cite{Mertens2018}
-\fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{History of Photovoltaics}
-%aenderung von widestand vonhalbleiter selen von bit ing willouhgby smith und ass joseph may fuer pv relevanten innere photoeket
-%1876 william adam und richard Day zeigten mit Selenstab mit platin elektroden dass festkörper Lichenergie direkt in elekt energie umwalndeln 
-%1905 erklaertle die physiklischen hinterdr'ünde mit seinem lichtquantentheorie einstein 
-%die ersten solarzellen wurden in den 1950s in Nieschen anwendungen wie der Raumfahrt mit einem wirkungsgrad unter 10 prozent 
-%durch die oelkriese 1973 stieg das interesse an pv und alternativen energiequellen und 1977 das erste salor...? 
-The photoelectric effect was first described in 1839 by french scientist Alexandre Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel. 
+The photoelectric effect was first described in 1839 by french scientist Alexandre 
+Edmond Becquerel, the father of Henri Becquerel\cite{becquerel1839memoire}. 
 Another relevant piece of the photovoltaic jigsaw was discovered 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Crystalline Silicon Photovoltaics}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{CIGS}
-%%%
-%Materials from the chalcopyrite group (tetragonal crystal system) (eg CuInGaSe(CIGS)) can be used as absorber in such thin film cells.
 CIGS ($\text{CuIn}_\text{x}\text{Ga}_{\text{(1-x)}}\text{Se}_2$) is of the chalcopyrite group (tetragonal crystal system) and can be used as thin film \gls{pv}. 
@@
 These thin film \gls{pv}s not only use less material, but also can be used in flexible applications.
-%%%
-%Amorphous silicon and copper indium selenide (CIS) \td{(see next chapter)} have much higher absorption coefficients of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}) and can therefore be much thinner and use less material.
-%Another advantage of thin film cells is that they can be used in flexible applications. 
-%which because of their high absorption coefficient of light %and therefore shallow penetration depth of light%need less material and can be used to produce flexible cells \\%of amorph silicon or CIS (see table p84)
 
@@
 This is a result of the large difference of band gaps of CuInSe2 and CuGaSe2 (see table \ref{tab:cigs}).
-%Durch den hohen Unterschied der Bandabstaedne von CuInSe2 und CuGaSe2 kamnn durch entsprechende Mischverhaeltnisse von In und Ga der Bandabstand eingestellt werden (Tablep 142) Abbildung Bild 5.22 p143) beschreiben und bild für Modul
-%Because of the large difference of band gaps of CuInSe2 and CuGaSe2 the band gap can be configured by mixing ratio of inidum and gallium (see table \ref{tab:cigs}).
 
@@
 when cooling and undergoing phase transistion\cite{Nielsen2005}.
-%due to phase transition\cite{Nielsen2005}.
-%\td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
-%Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
-%It is not poisonous. \td{cite?}
 It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
-%See ref \cite{Nielsen2005} for 2.3 Hydrous Zirconium Oxide 2.3 and 2.20 Zirconium Alkoxides.
 Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3}). 
@@
 
-%\td{what is important properites of zro2? }
-%\td{what is it? What is it used for? How does it work? What different kinds are there? }
-
-\subsubsection{Sol-Gel}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Sol-Gel and Doctor Blading}
 \td{what is it? What is it used for? How does it work? What different kinds are there? }
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Scanning electron Microscopy}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Infrared absorption}
@@
 \td{what, how, why?}
-\Gls{ir} spectroscopy is molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between $10^{-3}$ and $10^{-6}$ \nm{}) with molecules. \cite{Schwedt2008}
+
+\Gls{ir} spectroscopy is molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between $10^{-3}$ and $10^{-6}$ \m{}) with molecules. \cite{Schwedt2008}
 \td{FREE WRITING:}
@@
 talk about $E=h\cdot v$ and $\nu=c/\lambda$ and $\bar{\nu}=1/\lambda$
-shorter wavelengths (higher frequencies) carry more energy. 
+shorter wavelength (higher frequencies) carry more energy. 
 In practice the spectrum \gls{em} waves are unterteilt in different things. 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{X-Ray Diffraction}
+%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
 \gls{xrd} is used to study the crystalline strucutre of materlias since X-rays wavelengths (between 0.2 and \nm{10}) are comparable to the interatomic spacing of crystalline solids.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Machine Learning}
-\paragraph{History}
+\subsubsection{History}
 some text to test
-\paragraph{different kinds} 
+\subsubsection{different kinds} 
 supervised vs unsupervised
 classification (discrete) vs regression
-\paragraph{Particle Swarm Optimization}
-\paragraph{Princlipal Component Analysis}
+\subsubsection{Particle Swarm Optimization}
+\subsubsection{Princlipal Component Analysis}
 reinforcement learning could also have been a nice option
-\paragraph{Linear Regression}
+\subsubsection{Linear Regression}

### 2022-05-20 Thesis/makefile.sh
real Makefile

@@ -1,6 +1,0 @@
-#!/bin/bash
-
-basename=thesis
-pdflatex $basename.tex
-bibtex $basename.aux
-makeglossaries $basename

### 2022-05-21 Thesis/chapter/03-theoretical-background.tex
SEM finished

@@
 \subsubsection{Scanning electron Microscopy}
-\url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
+The history of \gls{sem} can be traced back to 1843 when Scottish clockmaker Alexander Bain filed a patent for dissecting an image by scanning.
+A detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}.
 \Gls{sem} is a microscopical technique which allows visualisation of surfaces with features in the nano meter regime. 
-While optical microscopes use visible light and optical lenses the \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
-%Instead of light, it uses electrons with shorter wavelengths. zum abbilden
+While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
 This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to light\cite{Kaliva2020}.
@@
 Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
-Electrons are \td{created} by either \gls{feg}, where are strong electrical field rips electrons from the bulk and thermionic guns where the filament (tungsten W or \ch{LaB6} (brigther and longer lasting but more expensive)) is heated until electrons are emitted.
+Electrons originate from either \gls{feg}, where are strong electrical field rips electrons from the bulk, or from thermionic guns where the filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted.
 Electrons are then accelerated by a voltage of 2 to 40 kV and bundled into narrow beams\cite{Vernon2000} by lenses.
-\td{A high \gls{mfp} is needed for electrons to travel from the source to the sample and to the detector. Thus, a very low pressure is in the inside.}
-It was used as a preliminary way of checking the surface condition. 
-%This allows greater detail. 
-why? 
-\td{what? how? why?}
-what is sputtering, 
-how does it work, 
-what different kinds of sputtering is there, 
-what is is used for? 
-\cite{McMullan1995}
-\cite{Vernon2000}
-\cite{Kaliva2020}
+A high \gls{mfp} is needed for electrons to travel from the source to the sample (and to the detector). 
+Thus, a very low pressure is in the inside. 
+In this work \gls{sem} was used as a preliminary way of checking the surface condition.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Infrared absorption}
+\subsubsection{Infrared Absorption and Spectroscopy}
 \td{IR around page 45;
@@
 \td{what, how, why?}
+\td{QUESTIONS: 
+	how does a IR spectr work? monochromator or FT 
+	how does FT work 
+	how does a beam splitter work? 
+	how does detector work? two different for UVVis and MIR
+}
 
-\Gls{ir} spectroscopy is molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between $10^{-3}$ and $10^{-6}$ \m{}) with molecules. \cite{Schwedt2008}
+\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between $10^{-3}$ and $10^{-6}$\m{} or wave numbers of 500 to \pcm{4000} ) with molecules.
+\cite{Schwedt2008}
+In general, light is described as periodic \gls{em} wave 
+which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
+The relation of energy $E$ of a photon, its frequency $\nu$, wavelength $\lambda$ and wave number $\bar{\nu}$ are as follows:
+\begin{align*}
+	E &= h \cdot \nu \\
+	\nu &= c/ \lambda \\
+	\bar{\nu} &= 1/\lambda,
+\end{align*}
+where $h$ is the Planck's constant.
+%In words: shorter wavelength (higher frequency) photons are more energetic.
+In practice the spectrum of \gls{em} waves is sectioned in different ranges; 
+\td{see figure?}
+from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
+\td{with number?}
+X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
+Molecular vibrations can be separated in valence and deformation vibrations.
+
 \td{FREE WRITING:}
-light is described as periodic electro magnetic wave which moves. 
-All \gls{em} waves move with the speed of light c = 300k km /s in vacuum. 
-talk about $E=h\cdot v$ and $\nu=c/\lambda$ and $\bar{\nu}=1/\lambda$
-shorter wavelength (higher frequencies) carry more energy. 
-In practice the spectrum \gls{em} waves are unterteilt in different things. 
-from high to low energie: Xray, \gls{uv}, vis, (near, middle and far) \gls{ir}, microwaves and radiowaves. 
-Xrays interact with core electrons, \gls{uv} and vis with valence electrons, ir with schwingungne mol rot and translation, microwaves with rotation and radio with electron and nuclear spin. 
-molecular vibrations are unterteilt in valenz and deformation vibration.
-absorbance pre din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
-The absorbance intensity is abhaengig von wave length and molecule structure. 
-Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum.
+Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
+The absorbance intensity is dependent on wave length and molecule structure. 
+%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
 
-Ein molekule hat $F=3N$ (N anzahl der atome) freiheitsgrade, wobei $F_T=3$ translation und $F_R=3$ (2 für lineare molecules) wodurch sich die anzahl der vibration reduces to $F_V=3N-6$ ($3N-5$) for vibrations.
-vibrations are unterteils in valence vibrations (change of bond length) and deformation (change of bindungs angle). 
-only vibrations with change in dipole momemnt are \gls{ir} active.
+A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translation $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements.
 
-differences to UVVis: transmission instead of absorbance, higher energy left instead right, base line on top instead of bottom.
+The number of vibrations can therefore calculated as 
+\begin{align*}
+	F_V &= 3N - F_T - F_R = 3N - 6 \\
+	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
+\end{align*}
+%wodurch sich die anzahl der vibration reduces to $F_V=3N-6$ ($3N-5$) for vibrations. 
+Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bindungs angle). 
+Only vibrations that change the dipole moment of the molecule are \gls{ir} active.
+
+%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
+\td{describe simple IR with monochromator}
 \paragraph{(Fourier Transform) Infrared spectrometer}

### 2022-05-21 Thesis/chapter/03-theoretical-background.tex
siunitx

@@
         \hline
-		Material&   Type&    Band Gap [\ev{}]&    Wavelength [\nm{}]&    Absorption coef. $\alpha$    &Penetration Depth [\um{}]\\
+		Material&   Type&    Band Gap [\ev{}]&    Wavelength [\nm{}]&    Absorption coef. $\alpha$ [\pcm{}]    &Penetration Depth [\um{}]\\
         \hline
-        c-Si&   indirect&   1.12&   600&    4000/cm&    2.5\\
-        c-Si&   indirect&   1.12&   1000&    64/cm&    150\\
-        c-Si&   indirect&   1.12&   1100&    3.5/cm&    290\\
-        a-Si&   direct&      1.7&    600&    40,000/cm&  0.25\\
-        CdTe&   direct&      1.45&    600&    37,000/cm&  0.3\\
-		GaAs&   direct&      1.42&    600&    40,000/cm&  0.2\\
+		c-Si&   indirect&   1.12&   600&    \num{4000}&    2.5\\
+		c-Si&   indirect&   1.12&   1000&    \num{64}&    150\\
+		c-Si&   indirect&   1.12&   1100&    \num{3.5}&    290\\
+		a-Si&   direct&      1.7&    600&    \num{40000}&  0.25\\
+		CdTe&   direct&      1.45&    600&    \num{37000}&  0.3\\
+		GaAs&   direct&      1.42&    600&    \num{40000}&  0.2\\
         \hline
@@
 Advantages of 
-sputtered thin films include good adhesion to the substrate and good step coverage.
+sputtered thin films include good adhesion to the substrate and good step coverage\cite{Swann1988}.
 
@@
 A high voltage is applied to 
-two parallel electrode with low pressure gas in between. 
+two parallel electrodes with low pressure gas in between. 
 The target acts as cathode and the substrate (holder) as anode (see \td{fig}).
 %the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
-The cathode, then, emits electrons which collide with a gas particle (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
-Some gas particles may get ionized by the collision and the gas cation is accelerated to the cathode. 
-If the cation has enough energy it will bump off a target atom or molecule from the surface. 
+The cathode, then, emits electrons which collide with a gas particles (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
+Some gas particles may get ionized by the collision and the gas cations are accelerated to the cathode. 
+If a cation has enough energy it will bump off one or more atoms or molecules from the surface. 
 This happens by a cascade of momentum transfers, which can reach the surface again (see fig \td{cp sigmund69}). 
-If the surface particle gets momentum pointing away from the bulk and the remaining kinetic energy is higher then the binding energy, the particle is sputtered. 
-The pressure should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand there is a minimum pressure to keep the plasma going. 
-Usual pressures are around 1 Pa ($10^{-2}$ mbar) or lower\cite{Swann1988}.
+If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
+This sputtered particle travels unaffected by the electrical field perpendicular to the surface towards the substrate and condenses with other particles to form a layer.
+The pressure should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand 
+a minimum pressure is needed to keep the plasma "alive". 
+Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
 
 A magnetron can be placed behind the cathode (target) in order to trap ejected electrons close to the source. 
-This prevents high energy electrons from reaching the target and undoing the deposited layer and this also increases the probability of an electron colliding with an argon atom and ionizing it.
+This prevents high energy electrons from reaching the target and undoing the deposited layer and this also increases the probability of an electron colliding with an argon atom and ionizing it, increasing the yield.
 
@@
 Sputtered atoms will react with the gas and result in oxide or nitrides layers, respectively.
-The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning\td{cite? What is poisoned?}.
+The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning. 
+Meaning the target begin covered by an insulating layers which can lead to defects in the growing film\cite{Kelly2000}.
 
 The limitation of only being able to use conducting materials as targets can be circumvented by using a radio frequency electrical field. 
-This prevents a charge building up on the target. \td{why is a charge?}
+This prevents a charge building up on the target. %\td{why is a charge?}
 Although RF sputtering is more versatile, DC sputtering is more common because of it's simpler system and economical reasons.
-\td{sputtered particles are neutral and not influenced by the electrical field}
+%\td{sputtered particles are neutral and not influenced by the electrical field}
 
@@
 
-\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between $10^{-3}$ and $10^{-6}$\m{} or wave numbers of 500 to \pcm{4000} ) with molecules.
-\cite{Schwedt2008}
+%%% WHAT? 
+\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between \num{e-3} and \num{e-6}\m{}
+or wave numbers of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
 In general, light is described as periodic \gls{em} wave 
 which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
-The relation of energy $E$ of a photon, its frequency $\nu$, wavelength $\lambda$ and wave number $\bar{\nu}$ are as follows:
+The relation of energy~$E$ of a photon, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
 \begin{align*}
@@
 %In words: shorter wavelength (higher frequency) photons are more energetic.
-In practice the spectrum of \gls{em} waves is sectioned in different ranges; 
-\td{see figure?}
+In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?});
 from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
@@
 X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
-Molecular vibrations can be separated in valence and deformation vibrations.
-
-\td{FREE WRITING:}
-Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
-The absorbance intensity is dependent on wave length and molecule structure. 
-%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
-
-A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translation $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements.
-
+%Molecular vibrations can be separated in valence and deformation vibrations.
+%
+A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
+%
 The number of vibrations can therefore calculated as 
@@
 %wodurch sich die anzahl der vibration reduces to $F_V=3N-6$ ($3N-5$) for vibrations. 
-Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bindungs angle). 
+Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bindungs angle) vibrations\cite{Melker2006}. 
 Only vibrations that change the dipole moment of the molecule are \gls{ir} active.
 
-%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
-\td{describe simple IR with monochromator}
+%\td{describe simple IR with monochromator}
+%\paragraph{\Gls{IR} Spectrometer}
+
 \paragraph{(Fourier Transform) Infrared spectrometer}
  A ceramic material (Nernst glower) is heated to \oc{1600} as light source. 
- In the two strahlen spectrometer the light is split, send through the sample and a reference, combined and send through a monochromator to a detector. 
- In the \gls{ft}\gls{ir} spectrometer the beam is send thourhg the sample, split and reflected from a static and from a moving mirror, recombined and detected by a photo multiplier (a bauteil which transforms photons into electircal signals).
+ In the two beam spectrometer the light is split, send through the sample and a reference and alternately send through a monochromator to a detector (thermocouple). 
+In the \gls{ft}\gls{ir} spectrometer the beam is send through the sample, split and reflected from a static and from a moving mirror, recombined and detected by a photo multiplier (a device which transforms photons into electrical signals).
+\td{In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample, individually}
+
+\td{FREE WRITING:}
+Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
+The absorbance intensity is dependent on wave length and molecule structure. 
+%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
+%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
 

### 2022-05-22 Thesis/chapter/03-theoretical-background.tex
IR fast

@@
 \td{IR around page 45;
-REFLECTIVITY? can also be used for determination of thickness p47
+REFLECTIVITY? can also be used for determination of thickness p47\cite{Dumin1967}
 }
-\td{what, how, why?}
 \td{QUESTIONS: 
-	how does a IR spectr work? monochromator or FT 
-	how does FT work 
 	how does a beam splitter work? 
@@
 %%% WHAT? 
-\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between \num{e-3} and \num{e-6}\m{}
-or wave numbers of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
+\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of \num{e-3} to \num{e-6}\m{}
+or wave numbers $\bar{\nu}$ of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
 In general, light is described as periodic \gls{em} wave 
@@
 \end{align*}
-%wodurch sich die anzahl der vibration reduces to $F_V=3N-6$ ($3N-5$) for vibrations. 
-Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bindungs angle) vibrations\cite{Melker2006}. 
+Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
 Only vibrations that change the dipole moment of the molecule are \gls{ir} active.
@@
 %\td{describe simple IR with monochromator}
-%\paragraph{\Gls{IR} Spectrometer}
 
 \paragraph{(Fourier Transform) Infrared spectrometer}
- A ceramic material (Nernst glower) is heated to \oc{1600} as light source. 
- In the two beam spectrometer the light is split, send through the sample and a reference and alternately send through a monochromator to a detector (thermocouple). 
-In the \gls{ft}\gls{ir} spectrometer the beam is send through the sample, split and reflected from a static and from a moving mirror, recombined and detected by a photo multiplier (a device which transforms photons into electrical signals).
+ A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
+ In the two-beam-spectrometer the light is split, sent through the sample and a reference and alternately sent through a monochromator to a detector (thermocouple). 
+%
+In the \gls{ft}\gls{ir} spectrometer the beam is sent through the sample, split and 
+reflected from a static and from a moving mirror, recombined and detected by a photo 
+multiplier (a device which transforms photons into electrical signals). 
+How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams.
 \td{In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample, individually}
@@
 %differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
+When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967}.
 
@@
 %\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
-\gls{xrd} is used to study the crystalline strucutre of materlias since X-rays wavelengths (between 0.2 and \nm{10}) are comparable to the interatomic spacing of crystalline solids.
-\cite{Kaliva2020}.
-Each crystalline material has discreet atomc structure, which upon irradiation with X-rays causes constructive and destructive interference and generates unique diffraction patterns. 
-XRD \td{spectra} of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad cruve with a maximum extending over several degrees (2$\theta$).
+\gls{xrd} is used to study the crystalline structure of materials.
+Since X-rays wavelengths (\num{0.2} to \nm{10}) are comparable to the interatomic spacing of crystalline solids the beams get reflected and contain information about the structure\cite{Kaliva2020}.
+Each crystalline material has a discreet atomic structure, which upon irradiation with 
+X-rays causes constructive and destructive interference according to Bragg's law and generates unique diffraction patterns. 
+\Gls{xrd} diffraction plots of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad curve with a maximum extending over several degrees (2$\theta$).
 
-\url{https://chem.libretexts.org/Courses/Franklin_and_Marshall_College/Introduction_to_Materials_Characterization__CHM_412_Collaborative_Text/Diffraction_Techniques/X-ray_diffraction_(XRD)_basics_and_application}\\
+%\url{https://chem.libretexts.org/Courses/Franklin_and_Marshall_College/Introduction_to_Materials_Characterization__CHM_412_Collaborative_Text/Diffraction_Techniques/X-ray_diffraction_(XRD)_basics_and_application}\\
 

### 2022-05-22 Thesis/chapter/06-results-and-discussion.tex
thoughts on literature research: intro, lit review, methodology

--- 2021-12-12 Thesis/chapter/results-and-discussion.tex
@@
 
+\td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, 
+could have been verhindert durch lesen the docu and more papers more thoughoughly. 
+Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}
 %\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer.
@@
 \end{figure}
+
+\td{show results between 1ml acoh (199), acoh+ipo 1:1 (201) and ipo (192). Show graph of the three vs log pondus G and pinhole density and maybe distribution of single point measurements? 
+\texttt{set boxwidth 2; set xtics 5; p "stat.dat" u 1:3 with boxes} 
+}

### 2022-05-24 Thesis/chapter/03-theoretical-background.tex
start with ML

@@
 \subsubsection{Infrared Absorption and Spectroscopy}
-\td{IR around page 45;
-REFLECTIVITY? can also be used for determination of thickness p47\cite{Dumin1967}
-}
-\td{QUESTIONS: 
-	how does a beam splitter work? 
-	how does detector work? two different for UVVis and MIR
-}
-
 %%% WHAT? 
@@
  A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
- In the two-beam-spectrometer the light is split, sent through the sample and a reference and alternately sent through a monochromator to a detector (thermocouple). 
+ In the two-beam-spectrometer the light is split, sent through the sample and a reference and one of the two beams is alternately sent through a monochromator to a detector (\td{thermocouple}). 
 %
@@
 multiplier (a device which transforms photons into electrical signals). 
-How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams.
-\td{In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample, individually}
+How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
+In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample.
+%
+When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967} of optical less dense material.
 
-\td{FREE WRITING:}
-Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
-The absorbance intensity is dependent on wave length and molecule structure. 
 %\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
 %differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
-When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967}.
+
+\td{QUESTIONS: 
+	how does detector work? two different for UVVis and MIR
+	IR around page 45;
+The absorbance intensity is dependent on wave length and molecule structure. 
+Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
+}
 
@@
 \subsubsection{History}
-some text to test
+find cool examples like in https://pubs.rsc.org/en/content/articlehtml/2019/sc/c9sc01742a
+noteable mentions: GAN, language processing, self driving cars, image recognition, playing board games (and beating humans). 
+See protocoll
+dall-e 2 \cite{Marcus2022}
 \subsubsection{different kinds} 

### 2022-06-03 Thesis/chapter/03-theoretical-background.tex
AI freewriting

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Machine Learning}
+\subsection{Artificial Inteligence}
 \subsubsection{History}
-find cool examples like in https://pubs.rsc.org/en/content/articlehtml/2019/sc/c9sc01742a
-noteable mentions: GAN, language processing, self driving cars, image recognition, playing board games (and beating humans). 
-See protocoll
-dall-e 2 \cite{Marcus2022}
+
+\todo{freewrinting}: The history of AI goes back to the middle of the 20th century.
+At the dartmouth conference researchers from the emerging field came to gether and the begriff of ai was coined.
+Important people are Alan Turing, who thought alot about how to define and how to test and how to implement ai.
+One example is to measure against the human in playing chess.
+which was managed to, the human was besiegt by a computer in the early 2000.
+But fear not.
+That doesn't mean that computers are more intelligent than humans and certainly not that research is over.
+AI is still a young field, strongly growing and gaining ubiquitous status.
+Slowly creeping into every human things just like electricity hundred years ago.
+Now we cant - it's hard to - imagine to live without electricity.
+Another test ingeniused by alan turing, is that a human must communicate with a unknown entity (in written form) and guess or better ableiten if they are dealing with a machine or a human being.
+It is easy for humans to come up with question to bring AI out of concept, but when reading AI written articles (see GPT), it's easy to see this test being passed in the near future.
+Realms in which AI is gaining traction are: 
+An interesting effect is the so called AI effect: certain fields get incorporated into AI research and practical and after some time of general use are no more considered AI such as spam filter, web searches and and.
+which fields will be incorporated by AI in the near future? 
+which questions have to be answered? philosophical and ethical questions. 
+Humans, now, must mit sich selbst auseinaner setzen
+
+ETC 
+ - playing board games (and beating humans). alpha go 
+ - image recognition
+ - \href{https://pubs.rsc.org/en/content/articlehtml/2019/sc/c9sc01742a}{[src]}
+ - medicine (early erkennen of krakheiten like cancer) \href{https://med.stanford.edu/radiology/news/2020/smart-toilet.html}{[src]}
+ - pig operation \href{https://www.science.org/doi/10.1126/scirobotics.abj2908}{[src]}
+ - haushaltshilfen 
+ - See protocoll
+ - cyber security\cite{Sarker2021}
+ - analysis by synthesis openAI iGPT-2 \href{https://openai.com/blog/image-gpt/}{[src]}
+ - using similar input data to start training instead of random starting weights
+ - Sundar Pichai (google ceo): impact of ai will be greater than fire and electricity
+ - TPUs used in google and alpha go 
+ - NN + computational power made a lot of advances possible
+ - computer learned to see, 
+ - Google's Jeff Dean generalize over thousands of tasks AI
+ - Thomas Oxley Neurologist TEDx
+ - catching and throwing stuff 
+ - trivial spam filters, image
+ - dr alan d thompson
+ - fly brain 100k neurons \cite{Zheng2018} \href{https://en.wikipedia.org/wiki/List\_of\_animals\_by\_number\_of\_neurons{[wiki]}}
+ - better if similar task before \href{https://www.cs.ubc.ca/~amuham01/LING530/papers/radford2018improving.pdf}{[src]}
+ - In concrete terms, these capabilities lie at the heart of modern technologies such as smartphone voice recognition, autopilot in planes, driverless cars, translation software, new marketing techniques, investment fund managing, advances in security and surveillance software, facial recognition and autonomous drones, amongst other wide-ranging uses.
+ \href{https://onlinelibrary.wiley.com/doi/full/10.1111/1467-923X.12794}{[src]}\cite{Hassan2020}
+ - weaponry and war \href{https://futureoflife.org/data/documents/research\_priorities.pdf}{[src]}
+ - "AI (like any powerful new technology) enables both great new benefits
+ and novel pitfalls to be avoided"
+ - embodied systems such as robots (futureoflife)
+ - random thought: build AI (unsupervised) to train a supervised leanrning AI (learning in generations
+ - AI open letter \cite{Russel2015}
+ - AI100 \href{https://ai100.stanford.edu/gathering-strength-gathering-storms-one-hundred-year-study-artificial-intelligence-ai100-2021-study}{[src]}, 
+ - it's looking as if AI will become ubiquituous and permeate all facetes of life.
+Zeichen dafür are the \td{infamous} zitat from google ceo, "ai fire electricity", eimrates building a AI centered city named Neom and the stanford AI100 report \cite{Littman2021}
+ - datasets can be augumented with GAN created data [\href{https://arxiv.org/abs/1711.04340}{src}]
+ - facial recognition to prevent theft of toilet paper \cite{Andrews2017}.
+ - financial: lending and financial planing ie investing (so called robo-advisors)\cite{Littman2021}\href{https://ai100.stanford.edu/2021-report/standing-questions-and-responses/sq2-what-are-most-important-advances-ai}{[src]}
+ - Discussion: "Of course, applying recommendation to multiple tasks simultaneously raises the challenging question of how best to make tradeoffs among these different objectives."\cite{Littman2021}
+ - AI effect \href{https://ai100.stanford.edu/2016-report/section-i-what-artificial-intelligence/defining-ai#\_ftnref3}{[src]} \cite{McCorduck1982} (e.g. spam filter or web search) 
+ - history: Norbert Wiener, Alan Turing, John von Neumann, Dartmouth conference 1956, team of Newell, Simon and Shaw. then: fields, then arten of AI 
+ - beautiful review of McCorduck1982\cite{McCorduck1982} was written by Apter in sthe same year\cite{Apter1982}
+\td{Lanuage: }
+ - language processing
+ - natural language turn into computer code 
+ - GPT-3 by openAI language model 
+ - writing an article \url{https://www.theguardian.com/commentisfree/2020/sep/08/robot-wrote-this-article-gpt-3}
+ - google translate 
+ - sophia \url{https://link.springer.com/article/10.1007/s00146-020-01104-w}
+ - speach recognition
+ - \href{https://ai100.stanford.edu/2021-report/standing-questions-and-responses/sq2-what-are-most-important-advances-ai#_2021SQ2ref3}{srouces}
+
+autonomous vehicles:
+ - self driving cars
+ - tesla, goolge, General Motors, Ford
+ - mayflower autonomous shiop uk to US
+
+ creative: 
+ - make headlines for articles, design info graphics
+ - google picture search
+ - Brand mark (create logo)
+ - Hidrelet Diao: simpsons to real world 
+ - VQGAN + CLIP (openAI?)
+ - Neuraldivergent : AI generated art
+ - https://openai.com/blog/image-gpt/
+ - animating photos, deep fakes
+ - dall-e 2 \cite{Marcus2022}
+ - this person does not exist, dalle 2 
+ - GAN
+ - make video games \cite{Guzdial2016}
+
+ discussion: ein nachteil ist, dass bei EMMA im vornhinein festgelegt wurde welche parameter und danach konnte man entweder die parameter nicht aendern oder einen winzigen Bruchteil der Daten verwenden.
+whereas a human would (not unlike a GAN) extrapolate unusable data into the usable regime per bauchgefühl
+
 \subsubsection{different kinds} 
@@
 classification (discrete) vs regression
+%
 \subsubsection{Particle Swarm Optimization}
+%
 \subsubsection{Princlipal Component Analysis}
 reinforcement learning could also have been a nice option
+%
 \subsubsection{Linear Regression}
+%

### 2022-06-04 Thesis/chapter/03-theoretical-background.tex
ir?

--- 2022-05-24 Thesis/chapter/03-theoretical-background.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Machine Learning}
+\subsection{Statistics, Regressin and Machine Learning}
 \subsubsection{History}
-find cool examples like in https://pubs.rsc.org/en/content/articlehtml/2019/sc/c9sc01742a
+find cool examples like in \url{https://pubs.rsc.org/en/content/articlehtml/2019/sc/c9sc01742a}  \\
+\url{https://medium.com/@LightOnIO/beyond-overfitting-and-beyond-silicon-the-double-descent-curve-18b6d9810e1b}  \\
+\url{https://www.nature.com/articles/427297a}\\
+\url{https://www.sciencedirect.com/science/article/abs/pii/S0040609001015164} \\
+\url{https://ieeexplore.ieee.org/abstract/document/6656789}\\
+\url{https://www.sciencedirect.com/science/article/abs/pii/S0038092X04000854}\\
+\url{https://www.sciencedirect.com/science/article/abs/pii/S007964251930101X}\\
+
 noteable mentions: GAN, language processing, self driving cars, image recognition, playing board games (and beating humans). 
 See protocoll
-dall-e 2 \cite{Marcus2022}
+Chapters to read from "UNDERSTANDING MACHINE LEARNING from theory to algorithms" 1,5,9,11,12,14,15,16,20,23,25
+dall-e 2 \cite{Marcus2022}\\
+vNeumann 4 param elephant \cite{Dyson2004}\\
+4 param elephant \cite{Mayer2010}\\
+"All models are wrong but some are useful" \cite{Box1979}\\
+"THE NEED FOR SIMPLE SCIENTIFIC MODELS - PARSIMONY" \cite{Box1979}\\
+"Breakthroughs in machine learning are rapidly changing science and society, yet our fundamental understanding of this technology has lagged far behind." \cite{Belkin2018}\\
 \subsubsection{different kinds} 
@@
 classification (discrete) vs regression
+\subsubsection{Design of Experiment}
 \subsubsection{Particle Swarm Optimization}

### 2022-06-04 Thesis/chapter/03-theoretical-background.tex

--- 2022-06-03 Thesis/chapter/03-theoretical-background.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Statistics, Regressin and Machine Learning}
+\subsubsection{History}
+find cool examples like in \url{https://pubs.rsc.org/en/content/articlehtml/2019/sc/c9sc01742a}  \\
+\url{https://medium.com/@LightOnIO/beyond-overfitting-and-beyond-silicon-the-double-descent-curve-18b6d9810e1b}  \\
+\url{https://www.nature.com/articles/427297a}\\
+\url{https://www.sciencedirect.com/science/article/abs/pii/S0040609001015164} \\
+\url{https://ieeexplore.ieee.org/abstract/document/6656789}\\
+\url{https://www.sciencedirect.com/science/article/abs/pii/S0038092X04000854}\\
+\url{https://www.sciencedirect.com/science/article/abs/pii/S007964251930101X}\\
+
+noteable mentions: GAN, language processing, self driving cars, image recognition, playing board games (and beating humans). 
+See protocoll
+Chapters to read from "UNDERSTANDING MACHINE LEARNING from theory to algorithms" 1,5,9,11,12,14,15,16,20,23,25
+dall-e 2 \cite{Marcus2022}\\
+vNeumann 4 param elephant \cite{Dyson2004}\\
+4 param elephant \cite{Mayer2010}\\
+"All models are wrong but some are useful" \cite{Box1979}\\
+"THE NEED FOR SIMPLE SCIENTIFIC MODELS - PARSIMONY" \cite{Box1979}\\
+"Breakthroughs in machine learning are rapidly changing science and society, yet our fundamental understanding of this technology has lagged far behind." \cite{Belkin2018}\\
+\subsubsection{different kinds} 
+supervised vs unsupervised
+classification (discrete) vs regression
+\subsubsection{Design of Experiment}
+=======
 \subsection{Artificial Inteligence}

### 2022-06-11 Thesis/chapter/03-theoretical-background.tex
ML sources

--- 2022-06-04 Thesis/chapter/03-theoretical-background.tex
@@
 
-\td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book} 
+\td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book (Recreated based on\cite{mertens2015photovoltaik}) or (Image source:\cite{mertens2015photovoltaik})}
+
 The standard substrate is glass 
@@
 \subsubsection{Design of Experiment}
+=======
+\subsection{Artificial Inteligence}
+\subsubsection{History}
+
+\todo{freewrinting}: The history of AI goes back to the middle of the 20th century.
+At the dartmouth conference researchers from the emerging field came to gether and the begriff of ai was coined.
+Important people are Alan Turing, who thought alot about how to define and how to test and how to implement ai.
+One example is to measure against the human in playing chess.
+which was managed to, the human was besiegt by a computer in the early 2000.
+But fear not.
+That doesn't mean that computers are more intelligent than humans and certainly not that research is over.
+AI is still a young field, strongly growing and gaining ubiquitous status.
+Slowly creeping into every human things just like electricity hundred years ago.
+Now we cant - it's hard to - imagine to live without electricity.
+Another test ingeniused by alan turing, is that a human must communicate with a unknown entity (in written form) and guess or better ableiten if they are dealing with a machine or a human being.
+It is easy for humans to come up with question to bring AI out of concept, but when reading AI written articles (see GPT), it's easy to see this test being passed in the near future.
+Realms in which AI is gaining traction are: 
+An interesting effect is the so called AI effect: certain fields get incorporated into AI research and practical and after some time of general use are no more considered AI such as spam filter, web searches and and.
+which fields will be incorporated by AI in the near future? 
+which questions have to be answered? philosophical and ethical questions. 
+Humans, now, must mit sich selbst auseinaner setzen 
+%
+\clearpage
+%
+\todo{ETC}\\
+ - playing board games (and beating humans). alpha go zero \cite{Silver2017}\\
+ - image recognition for medicine\cite{Li2020,Deo2015,Topol2019}, autonomous driving \cite{Fujiyoshi2019}\\
+ - simulating molecules \cite{Westermayr2019}\\
+ - medicine (early erkennen of krakheiten like cancer) \href{https://med.stanford.edu/radiology/news/2020/smart-toilet.html}{[src]}\\
+ - pig operation \href{https://www.science.org/doi/10.1126/scirobotics.abj2908}{[src]}\\
+ - haushaltshilfen \\
+ - See protocoll\\
+ - cyber security\cite{Sarker2021}\\
+ - analysis by synthesis openAI iGPT-2 \href{https://openai.com/blog/image-gpt/}{[src]}\\
+ - using similar input data to start training instead of random starting weights\\
+ - Sundar Pichai (google ceo): impact of ai will be greater than fire and electricity\\
+ - TPUs used in google and alpha go \\
+ - NN + computational power made a lot of advances possible\\
+ - computer learned to see, \\
+ - Google's Jeff Dean generalize over thousands of tasks AI\\
+ - Thomas Oxley Neurologist TEDx\\
+ - catching and throwing stuff \\
+ - trivial spam filters, image\\
+ - dr alan d thompson\\
+ - fly brain 100k neurons \cite{Zheng2018} \href{https://en.wikipedia.org/wiki/List\_of\_animals\_by\_number\_of\_neurons{[wiki]}}\\
+ - better if similar task before \href{https://www.cs.ubc.ca/~amuham01/LING530/papers/radford2018improving.pdf}{[src]}\\
+ - In concrete terms, these capabilities lie at the heart of modern technologies such as smartphone voice recognition, autopilot in planes, driverless cars, translation software, new marketing techniques, investment fund managing, advances in security and surveillance software, facial recognition and autonomous drones, amongst other wide-ranging uses.\\
+ \href{https://onlinelibrary.wiley.com/doi/full/10.1111/1467-923X.12794}{[src]}\cite{Hassan2020}\\
+ - weaponry and war \href{https://futureoflife.org/data/documents/research\_priorities.pdf}{[src]}\\
+ - "AI (like any powerful new technology) enables both great new benefits\\
+ and novel pitfalls to be avoided"\\
+ - embodied systems such as robots (futureoflife)\\
+ - random thought: build AI (unsupervised) to train a supervised leanrning AI (learning in generations\\
+ - AI open letter \cite{Russel2015}\\
+ - AI100 \href{https://ai100.stanford.edu/gathering-strength-gathering-storms-one-hundred-year-study-artificial-intelligence-ai100-2021-study}{[src]}, \\
+ - it's looking as if AI will become ubiquituous and permeate all facetes of life.
+Zeichen dafür are the \td{infamous} zitat from google ceo, "ai fire electricity", eimrates building a AI centered city named Neom and the stanford AI100 report \cite{Littman2021}\\
+ - datasets can be augumented with GAN created data [\href{https://arxiv.org/abs/1711.04340}{src}]\\
+ - facial recognition to prevent theft of toilet paper \cite{Andrews2017}.\\
+ - financial: lending and financial planing ie investing (so called robo-advisors)\cite{Littman2021}\href{https://ai100.stanford.edu/2021-report/standing-questions-and-responses/sq2-what-are-most-important-advances-ai}{[src]}\\
+ - Discussion: "Of course, applying recommendation to multiple tasks simultaneously raises the challenging question of how best to make tradeoffs among these different objectives."\cite{Littman2021}\\
+ - AI effect \href{https://ai100.stanford.edu/2016-report/section-i-what-artificial-intelligence/defining-ai#\_ftnref3}{[src]} \cite{McCorduck1982} (e.g. spam filter or web search) \\
+ - history: Norbert Wiener, Alan Turing, John von Neumann, Dartmouth conference 1956, team of Newell, Simon and Shaw. then: fields, then arten of AI \\
+ - beautiful review of McCorduck1982\cite{McCorduck1982} was written by Apter in sthe same year\cite{Apter1982}\\
+ - idea: when train supersived, also train unsupervised and see if similar results
+
+\todo{Lanuage: }\\
+ - language processing\\
+ - natural language turn into computer code \\
+ - GPT-3 by openAI language model \\
+ - writing an article \url{https://www.theguardian.com/commentisfree/2020/sep/08/robot-wrote-this-article-gpt-3}\\
+ - google translate \\
+ - sophia \url{https://link.springer.com/article/10.1007/s00146-020-01104-w}\\
+ - speach recognition\\
+ - \href{https://ai100.stanford.edu/2021-report/standing-questions-and-responses/sq2-what-are-most-important-advances-ai#_2021SQ2ref3}{srouces}\\
+
+\todo{autonomous vehicles:}\\
+ - self driving cars\\
+ - tesla, goolge, General Motors, Ford\\
+ - mayflower autonomous shiop uk to US\\
+
+\todo{creative: }\\
+ - make headlines for articles, design info graphics\\
+ - google picture search\\
+ - Brand mark (create logo)\\
+ - Hidrelet Diao: simpsons to real world \\
+ - VQGAN + CLIP (openAI?)\\
+ - Neuraldivergent : AI generated art\\
+ - https://openai.com/blog/image-gpt/\\
+ - animating photos, deep fakes\\
+ - dall-e 2 \cite{Marcus2022}\\
+ - this person does not exist, dalle 2 \\
+ - GAN\\
+ - make video games \cite{Guzdial2016}\\
+
+ discussion: ein nachteil ist, dass bei EMMA im vornhinein festgelegt wurde welche parameter und danach konnte man entweder die parameter nicht aendern oder einen winzigen Bruchteil der Daten verwenden.
+whereas a human would (not unlike a GAN) extrapolate unusable data into the usable regime per bauchgefühl
+
+\subsubsection{different kinds} 
+supervised vs unsupervised
+classification (discrete) vs regression
+%
 \subsubsection{Particle Swarm Optimization}
+%
 \subsubsection{Princlipal Component Analysis}
 reinforcement learning could also have been a nice option
+%
 \subsubsection{Linear Regression}
+%

### 2022-06-12 Thesis/chapter/03-theoretical-background.tex
AI free write 1st edit

@@
 
-\todo{freewrinting}: The history of AI goes back to the middle of the 20th century.
-At the dartmouth conference researchers from the emerging field came to gether and the begriff of ai was coined.
-Important people are Alan Turing, who thought alot about how to define and how to test and how to implement ai.
-One example is to measure against the human in playing chess.
-which was managed to, the human was besiegt by a computer in the early 2000.
-But fear not.
-That doesn't mean that computers are more intelligent than humans and certainly not that research is over.
+\todo{freewrinting}: The history of AI goes back to the middle of the \nth{20} century. 
+Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined. 
+Pioneers like Alan Turing thought a lot about how to define and how to test and how to implement \gls{ai}. 
+One example how to measure \gls{ai} is to let it play chess against a human, which was managed to, the human was defeated by a computer in the early 2000. 
+But fear not, that doesn't mean that computers are more intelligent than humans and certainly not that research is over. 
 AI is still a young field, strongly growing and gaining ubiquitous status. 
-Slowly creeping into every human things just like electricity hundred years ago.
+Slowly creeping into every human aspect just like electricity around one hundred years ago. 
 Now we cant - it's hard to - imagine to live without electricity. 
-Another test ingeniused by alan turing, is that a human must communicate with a unknown entity (in written form) and guess or better ableiten if they are dealing with a machine or a human being.
+Another test ingenioused by Alan Turing, is that a human must communicate with a unknown entity (in written form) and judge if they are dealing with a machine or a human being. 
 It is easy for humans to come up with question to bring AI out of concept, but when reading AI written articles (see GPT), it's easy to see this test being passed in the near future. 
 Realms in which AI is gaining traction are: 
-An interesting effect is the so called AI effect: certain fields get incorporated into AI research and practical and after some time of general use are no more considered AI such as spam filter, web searches and and.
+An interesting effect is the so called \gls{ai} effect:
+
+effect \cite{McCorduck1982,ai100} (e.g. spam filter or web search) \\
+
+certain fields get incorporated into AI research and practical and after some time of general use are no more considered AI such as spam filter, web searches and and. 
 which fields will be incorporated by AI in the near future? 

### 2022-06-14 Thesis/chapter/03-theoretical-background.tex
AI history and intro

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Statistics, Regressin and Machine Learning}
-\subsubsection{History}
-find cool examples like in \url{https://pubs.rsc.org/en/content/articlehtml/2019/sc/c9sc01742a}  \\
-\url{https://medium.com/@LightOnIO/beyond-overfitting-and-beyond-silicon-the-double-descent-curve-18b6d9810e1b}  \\
-\url{https://www.nature.com/articles/427297a}\\
-\url{https://www.sciencedirect.com/science/article/abs/pii/S0040609001015164} \\
-\url{https://ieeexplore.ieee.org/abstract/document/6656789}\\
-\url{https://www.sciencedirect.com/science/article/abs/pii/S0038092X04000854}\\
-\url{https://www.sciencedirect.com/science/article/abs/pii/S007964251930101X}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Statistics, Regression and Machine Learning}
+\subsection{Artificial Inteligence}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-noteable mentions: GAN, language processing, self driving cars, image recognition, playing board games (and beating humans). 
-See protocoll
-Chapters to read from "UNDERSTANDING MACHINE LEARNING from theory to algorithms" 1,5,9,11,12,14,15,16,20,23,25
-dall-e 2 \cite{Marcus2022}\\
-vNeumann 4 param elephant \cite{Dyson2004}\\
-4 param elephant \cite{Mayer2010}\\
-"All models are wrong but some are useful" \cite{Box1979}\\
-"THE NEED FOR SIMPLE SCIENTIFIC MODELS - PARSIMONY" \cite{Box1979}\\
-"Breakthroughs in machine learning are rapidly changing science and society, yet our fundamental understanding of this technology has lagged far behind." \cite{Belkin2018}\\
+The history of \gls{ai} goes back to the middle of the \nth{20} century. 
+Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
+For a more in depth dive into the history of AI consult the beautifully written review\cite{Apter1982} of McCorduck's 1982 book "Machines Who Think"\cite{McCorduck1982}, which focuses also on the great minds behind advances of \gls{ai}.
+Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{Howard2019}. 
+One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
+(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
+%the best humans don't stand a chance against the best computers since \td{early 2000s}).\cite{Silver2017}
+Another test ingenioussed by Alan Turing, is that a human who communicates with a unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
+It is easy for humans to come up with question to detect and AI, 
+but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future.
+
+But fear not, that doesn't mean that computers are more intelligent than humans and certainly not that research is over. 
+AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
+it is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
+Now, we can't - it's hard to - imagine to live without electricity. 
+Realms in which AI is gaining traction are: 
+%
+playing board games (and beating humans)\cite{Silver2017}, 
+image recognition (in medicine)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
+in chemistry\cite{Westermayr2019,goh2017chemception,jha2018elemnet}, 
+cyber security\cite{Sarker2021},
+facial recognition to prevent theft of toilet paper \cite{Andrews2017},
+financial sector (as robo-advisors)\cite{Littman2021}
+natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021}
+and even creative tasks like 
+creating non existing faces\cite{Mansourifar2020}, 
+create artwork (DALL-E 2)\cite{Marcus2022} or 
+making video games \cite{Guzdial2016}
+.
+It is nearly hard to find a field where \gls{ai} isn't used in some way. 
+This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
+certain fields get incorporated into \gls{ai} research and practice and after some time of general use are no more considered \gls{ai} (e.g. spam filter or web searches).
+Google CEO Sundar Pichai (Google CEO) even goes as far and said: 
+"AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}
+
+%which fields will be incorporated by AI in the near future? 
+%which questions have to be answered? philosophical and ethical questions. 
+%Humans, now, must mit sich selbst auseinaner setzen 
+%
+
+\subsubsection{AI vs statistics}
 \subsubsection{different kinds} 
@@
 \subsubsection{Design of Experiment}
-=======
-\subsection{Artificial Inteligence}
-\subsubsection{History}
 
-\todo{freewrinting}: The history of AI goes back to the middle of the \nth{20} century. 
-Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined. 
-Pioneers like Alan Turing thought a lot about how to define and how to test and how to implement \gls{ai}. 
-One example how to measure \gls{ai} is to let it play chess against a human, which was managed to, the human was defeated by a computer in the early 2000. 
-But fear not, that doesn't mean that computers are more intelligent than humans and certainly not that research is over. 
-AI is still a young field, strongly growing and gaining ubiquitous status. 
-Slowly creeping into every human aspect just like electricity around one hundred years ago. 
-Now we cant - it's hard to - imagine to live without electricity. 
-Another test ingenioused by Alan Turing, is that a human must communicate with a unknown entity (in written form) and judge if they are dealing with a machine or a human being. 
-It is easy for humans to come up with question to bring AI out of concept, but when reading AI written articles (see GPT), it's easy to see this test being passed in the near future. 
-Realms in which AI is gaining traction are: 
-An interesting effect is the so called \gls{ai} effect:
-
-effect \cite{McCorduck1982,ai100} (e.g. spam filter or web search) \\
-
-certain fields get incorporated into AI research and practical and after some time of general use are no more considered AI such as spam filter, web searches and and. 
-which fields will be incorporated by AI in the near future? 
-which questions have to be answered? philosophical and ethical questions. 
-Humans, now, must mit sich selbst auseinaner setzen 
+\subsubsection{different kinds} 
+supervised vs unsupervised
+classification (discrete) vs regression
 %
+\subsubsection{Particle Swarm Optimization}
+%
+\subsubsection{Princlipal Component Analysis}
+reinforcement learning could also have been a nice option
+%
+\subsubsection{Linear Regression}
+%
+\iffalse
 \clearpage
@@
 
-\subsubsection{different kinds} 
-supervised vs unsupervised
-classification (discrete) vs regression
-%
-\subsubsection{Particle Swarm Optimization}
-%
-\subsubsection{Princlipal Component Analysis}
-reinforcement learning could also have been a nice option
-%
-\subsubsection{Linear Regression}
-%
+noteable mentions: GAN, language processing, self driving cars, image recognition, playing board games (and beating humans). 
+See protocoll
+Chapters to read from "UNDERSTANDING MACHINE LEARNING from theory to algorithms" 1,5,9,11,12,14,15,16,20,23,25
+dall-e 2 \cite{Marcus2022}\\
+vNeumann 4 param elephant \cite{Dyson2004}\\
+4 param elephant \cite{Mayer2010}\\
+"All models are wrong but some are useful" \cite{Box1979}\\
+"THE NEED FOR SIMPLE SCIENTIFIC MODELS - PARSIMONY" \cite{Box1979}\\
+"Breakthroughs in machine learning are rapidly changing science and society, yet our fundamental understanding of this technology has lagged far behind." \cite{Belkin2018}\\
+\fi

### 2022-06-19 Thesis/chapter/03-theoretical-background.tex
delete massive AI sources

@@
 %
-\iffalse
-\clearpage
-%
-\todo{ETC}\\
- - playing board games (and beating humans). alpha go zero \cite{Silver2017}\\
- - image recognition for medicine\cite{Li2020,Deo2015,Topol2019}, autonomous driving \cite{Fujiyoshi2019}\\
- - simulating molecules \cite{Westermayr2019}\\
- - medicine (early erkennen of krakheiten like cancer) \href{https://med.stanford.edu/radiology/news/2020/smart-toilet.html}{[src]}\\
- - pig operation \href{https://www.science.org/doi/10.1126/scirobotics.abj2908}{[src]}\\
- - haushaltshilfen \\
- - See protocoll\\
- - cyber security\cite{Sarker2021}\\
- - analysis by synthesis openAI iGPT-2 \href{https://openai.com/blog/image-gpt/}{[src]}\\
- - using similar input data to start training instead of random starting weights\\
- - Sundar Pichai (google ceo): impact of ai will be greater than fire and electricity\\
- - TPUs used in google and alpha go \\
- - NN + computational power made a lot of advances possible\\
- - computer learned to see, \\
- - Google's Jeff Dean generalize over thousands of tasks AI\\
- - Thomas Oxley Neurologist TEDx\\
- - catching and throwing stuff \\
- - trivial spam filters, image\\
- - dr alan d thompson\\
- - fly brain 100k neurons \cite{Zheng2018} \href{https://en.wikipedia.org/wiki/List\_of\_animals\_by\_number\_of\_neurons{[wiki]}}\\
- - better if similar task before \href{https://www.cs.ubc.ca/~amuham01/LING530/papers/radford2018improving.pdf}{[src]}\\
- - In concrete terms, these capabilities lie at the heart of modern technologies such as smartphone voice recognition, autopilot in planes, driverless cars, translation software, new marketing techniques, investment fund managing, advances in security and surveillance software, facial recognition and autonomous drones, amongst other wide-ranging uses.\\
- \href{https://onlinelibrary.wiley.com/doi/full/10.1111/1467-923X.12794}{[src]}\cite{Hassan2020}\\
- - weaponry and war \href{https://futureoflife.org/data/documents/research\_priorities.pdf}{[src]}\\
- - "AI (like any powerful new technology) enables both great new benefits\\
- and novel pitfalls to be avoided"\\
- - embodied systems such as robots (futureoflife)\\
- - random thought: build AI (unsupervised) to train a supervised leanrning AI (learning in generations\\
- - AI open letter \cite{Russel2015}\\
- - AI100 \href{https://ai100.stanford.edu/gathering-strength-gathering-storms-one-hundred-year-study-artificial-intelligence-ai100-2021-study}{[src]}, \\
- - it's looking as if AI will become ubiquituous and permeate all facetes of life.
-Zeichen dafür are the \td{infamous} zitat from google ceo, "ai fire electricity", eimrates building a AI centered city named Neom and the stanford AI100 report \cite{Littman2021}\\
- - datasets can be augumented with GAN created data [\href{https://arxiv.org/abs/1711.04340}{src}]\\
- - facial recognition to prevent theft of toilet paper \cite{Andrews2017}.\\
- - financial: lending and financial planing ie investing (so called robo-advisors)\cite{Littman2021}\href{https://ai100.stanford.edu/2021-report/standing-questions-and-responses/sq2-what-are-most-important-advances-ai}{[src]}\\
- - Discussion: "Of course, applying recommendation to multiple tasks simultaneously raises the challenging question of how best to make tradeoffs among these different objectives."\cite{Littman2021}\\
- - AI effect \href{https://ai100.stanford.edu/2016-report/section-i-what-artificial-intelligence/defining-ai#\_ftnref3}{[src]} \cite{McCorduck1982} (e.g. spam filter or web search) \\
- - history: Norbert Wiener, Alan Turing, John von Neumann, Dartmouth conference 1956, team of Newell, Simon and Shaw. then: fields, then arten of AI \\
- - beautiful review of McCorduck1982\cite{McCorduck1982} was written by Apter in sthe same year\cite{Apter1982}\\
- - idea: when train supersived, also train unsupervised and see if similar results
-
-\todo{Lanuage: }\\
- - language processing\\
- - natural language turn into computer code \\
- - GPT-3 by openAI language model \\
- - writing an article \url{https://www.theguardian.com/commentisfree/2020/sep/08/robot-wrote-this-article-gpt-3}\\
- - google translate \\
- - sophia \url{https://link.springer.com/article/10.1007/s00146-020-01104-w}\\
- - speach recognition\\
- - \href{https://ai100.stanford.edu/2021-report/standing-questions-and-responses/sq2-what-are-most-important-advances-ai#_2021SQ2ref3}{srouces}\\
-
-\todo{autonomous vehicles:}\\
- - self driving cars\\
- - tesla, goolge, General Motors, Ford\\
- - mayflower autonomous shiop uk to US\\
-
-\todo{creative: }\\
- - make headlines for articles, design info graphics\\
- - google picture search\\
- - Brand mark (create logo)\\
- - Hidrelet Diao: simpsons to real world \\
- - VQGAN + CLIP (openAI?)\\
- - Neuraldivergent : AI generated art\\
- - https://openai.com/blog/image-gpt/\\
- - animating photos, deep fakes\\
- - dall-e 2 \cite{Marcus2022}\\
- - this person does not exist, dalle 2 \\
- - GAN\\
- - make video games \cite{Guzdial2016}\\
-
- discussion: ein nachteil ist, dass bei EMMA im vornhinein festgelegt wurde welche parameter und danach konnte man entweder die parameter nicht aendern oder einen winzigen Bruchteil der Daten verwenden.
-whereas a human would (not unlike a GAN) extrapolate unusable data into the usable regime per bauchgefühl
-
-noteable mentions: GAN, language processing, self driving cars, image recognition, playing board games (and beating humans). 
-See protocoll
-Chapters to read from "UNDERSTANDING MACHINE LEARNING from theory to algorithms" 1,5,9,11,12,14,15,16,20,23,25
-dall-e 2 \cite{Marcus2022}\\
-vNeumann 4 param elephant \cite{Dyson2004}\\
-4 param elephant \cite{Mayer2010}\\
-"All models are wrong but some are useful" \cite{Box1979}\\
-"THE NEED FOR SIMPLE SCIENTIFIC MODELS - PARSIMONY" \cite{Box1979}\\
-"Breakthroughs in machine learning are rapidly changing science and society, yet our fundamental understanding of this technology has lagged far behind." \cite{Belkin2018}\\
-\fi

### 2022-06-19 Thesis/chapter/03-theoretical-background.tex
DOE

@@
 %
+\subsubsection{2022-06-19-Free-Writing}
+The problem which presents it self is in principle a search problem.
+A large space of possible combinations of experimental anordnungen presents it self
+and out of these we want to find the optimial parameter combination. 
+The best way with unlimitied resources would be the brute-force approach to try every possibility. 
+But due to limited time this is unfeasable. 
+But a new questions arises: how should the ausmasse of the search space be eingeschraenkt? 
+What are the upper and lower limits and which intervals/step size/grid size should be used. 
+Also even before, we have to answer which dimensions/parameters should we include in the search? 
+Which parameters should we keep constant and at which value? 
+And finally which features should we use to measure the goodness of an experiment?
+
+I tried different methods to answer the first X questions: Latin square and Plackett-Burman design.
+Unfortunately, I was faced with similar questions. How many levels and which end points? 
+latin squares are about orthogonality 
+PB is a factorial experiment desing in contrast to one-fator-at-a-time methods.
+reliability and validity are low due to experiments not replicated
+
+https://en.wikipedia.org/wiki/Design_of_experiments
+https://en.wikipedia.org/wiki/The_Design_of_Experiments
+https://en.wikipedia.org/wiki/Response_surface_methodology
+https://en.wikipedia.org/wiki/Optimal_design
+https://sci-hub.st/https://doi.org/10.2307/2332195
+https://en.wikipedia.org/wiki/Latin_square
+https://en.wikipedia.org/wiki/Outline_of_artificial_intelligence
+https://en.wikipedia.org/wiki/Evolutionary_algorithm
+https://en.wikipedia.org/wiki/Particle_swarm_optimization
+EMMA doesn't allow for reproducibility

### 2022-06-20 Thesis/chapter/03-theoretical-background.tex
freewriting AI

--- 2022-06-14 Thesis/chapter/03-theoretical-background.tex
@@
 %the best humans don't stand a chance against the best computers since \td{early 2000s}).\cite{Silver2017}
-Another test ingenioussed by Alan Turing, is that a human who communicates with a unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
-It is easy for humans to come up with question to detect and AI, 
+Another test ingenioused by Alan Turing, is that a human who communicates with a unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
+It is easy for humans to come up with question to detect an AI, 
 but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future.
 
-But fear not, that doesn't mean that computers are more intelligent than humans and certainly not that research is over. 
+But fear not, that doesn't mean that computers are more intelligent than humans\cite{searle1999married,searle1980} and certainly not that research is over. 
 AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
-it is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
-Now, we can't - it's hard to - imagine to live without electricity. 
+It is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
+%Now, we can't - it's hard to - imagine to live without electricity. 
 Realms in which AI is gaining traction are: 
@@
 %
+\subsubsection{Free writing about AI}
+I chose an evolutionary algorithm which is - i think - also part of machine learning, 
+which is a part of AI. 
+There are many different types of AI. what are the most haeufig sub domains of the AI field? 
+(natural) language processing, image erkennung, and prediction which can be geteilt in 
+classification (discrete) and continuous prediction. 
+These are mainly machine learning algos. other machine learning tasks are EA, PSO,
 
 \subsubsection{AI vs statistics}
+let GPT-3 write 
+check out links at \url{https://yewtu.be/watch?v=PqbB07n_uQ4}
 \subsubsection{different kinds} 

### 2022-06-21 Thesis/chapter/03-theoretical-background.tex
Machine learning chapter alot

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Statistics, Regression and Machine Learning}
-\subsection{Artificial Inteligence}
+\subsection{Statistics and Machine Learning}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Design of Experiment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Statistics vs Regression}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{AI vs statistics}
+\td{let GPT-3 write}
+check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
+see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Artificial Inteligence and Machine Learning}
 
@@
 %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Machine Learning Methods}
+There is a platitude of different machine learning methods: 
+they can be divided into supervised (there is a known solution) and unsupervised (exploratory).  
+An orthogonal division can be made by regression (continuous) versus classification (discrete). 
+Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
+%One which is really popular now a days is neural networks (NN) and deep learning. 
+\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
+%
+Artificial neurons (also called nodes), which are arranged in layers, 
+are connected to each of the neurons of previous and next layers
+and the weights (parameters), with which the data is routed from one neuron to another, 
+are optimised during training. 
+%
+%There are of course many more \gls{ml} designs for different tasks. 
+%Although, mainly \gls{nn} are in the media and take up a lot of space in the field 
+%DL shines when it is used for complex data with massive data sets. 
+Convolutional-layer neural networks excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
+%One architecture which distinguishes itself for picture recognition is a convolutional networks.\td{cite some}
+Other common architectures are linear regression, kernel ridge regression, support vector regression.
+There are also lesser know algorithms like \gls{ga} (part of evolutionary algorithms) and \gls{pso}. 
+One advantage of the last two is that they start with a small data set
+%don't require the massive amount of data like \gls{dl} 
+and periodically request new data and try to solve the problem iteratively.
+
+"A genetic algorithm (GA) is a search algorithm that uses principles of natural selection and genetics to optimize a search space.
+A GA starts with a population of randomly generated solutions, or chromosomes, and then proceeds to breed them together to create new solutions.
+The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes.
+This process is repeated until a satisfactory solution is found."
+
+\Gls{ga} uses a starting population of size $p$ ($p \in$ \td{N$^+$}) where each experiment (or data point) 
+is represented by a fixed size genome of 0's and 1's in most cases. 
+Each individual is then given a fitness value. 
+New genomes are added and discarded from the population using 
+selection, mutation and crossover operations.
+%The best n ($n \in$ \td{N}) will be selected to produce offspring, 
+%whose genome is a combination of both genomes with potential mutations 
+%and a (mostly) random c
+
+\Gls{pso} also uses a starting population of particles of size $p$ where each experiment 
+is represented by its independent and dependent variables. 
+It was originally inspired by the behaviour of bird flocks and fish school.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Free writing about AI}
@@
 
-\subsubsection{AI vs statistics}
-let GPT-3 write 
-check out links at \url{https://yewtu.be/watch?v=PqbB07n_uQ4}
-\subsubsection{different kinds} 
-supervised vs unsupervised
-classification (discrete) vs regression
-\subsubsection{Design of Experiment}
-
-\subsubsection{different kinds} 
-supervised vs unsupervised
-classification (discrete) vs regression
-%
-\subsubsection{Particle Swarm Optimization}
-%
-\subsubsection{Princlipal Component Analysis}
-reinforcement learning could also have been a nice option
-%
-\subsubsection{Linear Regression}
-%
 \subsubsection{2022-06-19-Free-Writing}
@@
 
-https://en.wikipedia.org/wiki/Design_of_experiments
-https://en.wikipedia.org/wiki/The_Design_of_Experiments
-https://en.wikipedia.org/wiki/Response_surface_methodology
-https://en.wikipedia.org/wiki/Optimal_design
-https://sci-hub.st/https://doi.org/10.2307/2332195
-https://en.wikipedia.org/wiki/Latin_square
-https://en.wikipedia.org/wiki/Outline_of_artificial_intelligence
-https://en.wikipedia.org/wiki/Evolutionary_algorithm
-https://en.wikipedia.org/wiki/Particle_swarm_optimization
-EMMA doesn't allow for reproducibility
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Particle Swarm Optimization}
+%
+%\subsubsection{Princlipal Component Analysis}
+\textbf{things I should try if they work:}
+\begin{itemize}
+    \item what is reinforcement learning? 
+    \item PCA
+    \item linear regression
+    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
+    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
+    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
+\end{itemize}
+
+%    https://en.wikipedia.org/wiki/Design_of_experiments
+%    https://en.wikipedia.org/wiki/The_Design_of_Experiments
+%    https://en.wikipedia.org/wiki/Response_surface_methodology
+%    https://en.wikipedia.org/wiki/Optimal_design
+%    https://sci-hub.st/https://doi.org/10.2307/2332195
+%    https://en.wikipedia.org/wiki/Latin_square
+%    https://en.wikipedia.org/wiki/Outline_of_artificial_intelligence
+%    https://en.wikipedia.org/wiki/Evolutionary_algorithm
+%    https://en.wikipedia.org/wiki/Particle_swarm_optimization
+%    EMMA doesn't allow for reproducibility
+
+\td{
+\url{https://stats.stackexchange.com/questions/5026/what-is-the-difference-between-data-mining-statistics-machine-learning-and-ai}
+In principle both AI and stat use math to get information out of data. 
+AI might use machine learning to create "intelligent" acting (playing a game or driving a  car).
+machine learning tries to predict unseen data points  and statistics is a subfield of maths which tries to get insight into a given data.
+For example, in a statistical model, it is desirable to reduce the number of inputs.
+This allows the statistician to better study how a change in the input variable can be directly affected by the output variable.\cite{gontcharov2019}
+pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
+    }
+\begin{itemize}
+    \item[( )] machine learning and diff fields in ML
+    \item[( )] Genetical algorithm 
+    \item[( )] particle swarm optimisation
+\end{itemize}

### 2022-06-28 Thesis/chapter/03-theoretical-background.tex
cleaned ML chapter

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Statistics and Machine Learning}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Design of Experiment}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Statistics vs Regression}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{AI vs statistics}
-\td{let GPT-3 write}
-check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
-see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
+\subsection{Machine Learning and Statistics}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 (in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
-%the best humans don't stand a chance against the best computers since \td{early 2000s}).\cite{Silver2017}
-Another test ingenioused by Alan Turing, is that a human who communicates with a unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
+Another test ingenioused by Alan Turing, is that a human communicates with an unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
 It is easy for humans to come up with question to detect an AI, 
@@
 
-But fear not, that doesn't mean that computers are more intelligent than humans\cite{searle1999married,searle1980} and certainly not that research is over. 
+But fear not, that doesn't mean that computers are sentient or more intelligent than humans\cite{searle1980,searle1999married} and certainly not that research is over. 
 AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
@@
 %
-playing board games (and beating humans)\cite{Silver2017}, 
+playing board games (and beating humans)\cite{Silver2017,Feng1999,Campbell2002}, 
 image recognition (in medicine)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
@@
 cyber security\cite{Sarker2021},
-facial recognition to prevent theft of toilet paper \cite{Andrews2017},
-financial sector (as robo-advisors)\cite{Littman2021}
-natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021}
+facial recognition (to prevent theft of toilet paper \cite{Andrews2017}),
+financial sector (as robo-advisors)\cite{Littman2021},
+natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021} (which can also create pictures through scalable vector graphics (SVG) and code)
 and even creative tasks like 
@@
 create artwork (DALL-E 2)\cite{Marcus2022} or 
-making video games \cite{Guzdial2016}
-.
+making video games\cite{Guzdial2016}.
+%
 It is nearly hard to find a field where \gls{ai} isn't used in some way. 
@@
 certain fields get incorporated into \gls{ai} research and practice and after some time of general use are no more considered \gls{ai} (e.g. spam filter or web searches).
-Google CEO Sundar Pichai (Google CEO) even goes as far and said: 
+Google CEO Sundar Pichai even goes as far and said: 
 "AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}
 
-%which fields will be incorporated by AI in the near future? 
-%which questions have to be answered? philosophical and ethical questions. 
-%Humans, now, must mit sich selbst auseinaner setzen 
 %
@@
 There is a platitude of different machine learning methods: 
-they can be divided into supervised (there is a known solution) and unsupervised (exploratory).  
+they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
 An orthogonal division can be made by regression (continuous) versus classification (discrete). 
 Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
-%One which is really popular now a days is neural networks (NN) and deep learning. 
 \Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
@@
 are connected to each of the neurons of previous and next layers
-and the weights (parameters), with which the data is routed from one neuron to another, 
+and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
 are optimised during training. 
 %
-%There are of course many more \gls{ml} designs for different tasks. 
-%Although, mainly \gls{nn} are in the media and take up a lot of space in the field 
-%DL shines when it is used for complex data with massive data sets. 
-Convolutional-layer neural networks excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
-%One architecture which distinguishes itself for picture recognition is a convolutional networks.\td{cite some}
-Other common architectures are linear regression, kernel ridge regression, support vector regression.
-There are also lesser know algorithms like \gls{ga} (part of evolutionary algorithms) and \gls{pso}. 
-One advantage of the last two is that they start with a small data set
-%don't require the massive amount of data like \gls{dl} 
-and periodically request new data and try to solve the problem iteratively.
+Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
+Other common \td{architectures} are linear regression, kernel ridge regression, support vector regression.
+There are also lesser know algorithms like 
+evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
+%
+One advantage of evolutionary algorithms is that they start with a small data set
+and periodically request new data in order to solve the problem iteratively.
 
-"A genetic algorithm (GA) is a search algorithm that uses principles of natural selection and genetics to optimize a search space.
+A genetic algorithm (GA) is a search algorithm that uses principles of natural selection and genetics to optimize a search space.
 A GA starts with a population of randomly generated solutions, or chromosomes, and then proceeds to breed them together to create new solutions.
 The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes.
-This process is repeated until a satisfactory solution is found."
+This process is repeated until a satisfactory solution is found.\footnote{This paragraph was written by GPT\cite{Liu2021gpt} providing the input "Introduction to genetic algorithms: "}
 
+\iffalse
 \Gls{ga} uses a starting population of size $p$ ($p \in$ \td{N$^+$}) where each experiment (or data point) 
@@
 %and a (mostly) random c
+\fi
 
@@
 \subsubsection{Particle Swarm Optimization}
+it has been shown that \gls{pso} works well on problems wher \gls{ga}s work well\cite{Kennedy1995}. 
+It can be seen as in the middle of \gls{ga} (taking eons) and \gls{nn} taking seconds regarding time scale\cite{Kennedy1995}.
+it is a stochastic process
+are there iterative optimisation processes without stochastic? 
 %
-%\subsubsection{Princlipal Component Analysis}
-\textbf{things I should try if they work:}
+\subsubsection{things I should try if they work:}
 \begin{itemize}
+    \item GA 
     \item what is reinforcement learning? 
@@
     }
-\begin{itemize}
-    \item[( )] machine learning and diff fields in ML
-    \item[( )] Genetical algorithm 
-    \item[( )] particle swarm optimisation
-\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Design of Experiment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Linear Regression}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{AI vs statistics}
+\td{let GPT-3 write}
+check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
+see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
+\url{https://journals.sagepub.com/doi/pdf/10.1177/1352458520978648}
+\url{https://journals.sagepub.com/doi/full/10.1177/1352458520978648}

### 2022-07-15 Thesis/chapter/01-introduction.tex
ueberarbeitet

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\td{describe everything what is mentioned in \ref{sec:exp}}
-\Gls{pv} is one big hope when trying to become carbon neutral as it uses the energy provided by sun directly in contrast to renewable energy sources (e.g. wind and water) or even carbon based sources.
-One sort of \gls{pv} are \gls{cigs} \cite{Vasekar2010} cells. % https://doi.org/10.1016/j.tsf.2009.09.033}
-\td{was sind vorteile?}
+\Gls{pv} is one viable option when becoming carbon neutral. 
+Furthermore, 
+it uses the suns energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
+it is fit to be used in futuristic Dyson spheres\cite{dyson1960search} which harness the power output of the whole sun.
+%
+One sort of \gls{pv} are \gls{cigs}\cite{Vasekar2010} cells. 
+Due to their large absorption coefficient, less material is needed and they can be made thinner and flexible. 
+%\td{was sind vorteile?}
 In order to make a module, multiple cells are operated in series. 
@@
 An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
-An insulating layer must therefore be applied to the steel substrate before any \gls{cigs} cells can be applied.
+An insulating layer must therefore be applied to the steel substrate before any \gls{cigs} cells can be \td{applied}.
 A non-toxic material which is suitable for this application is \gls{zro}. 
@@
 In this work a dense, insulating and homogeneous layer is pursued. 
-\Gls{ml} can help to uncover complex non-linear relations, such as the influence of the 
+\Gls{ml} can help to uncover complex non-linear relations, such as the \td{influence} of the 
 production factors on the thickness and resistance of the resulting layer.
-The optimisation of the conductance if performed with a particle swarm optimization 
+The minimization of the conductance is performed with a particle swarm optimization 
 algorithm. 

### 2022-07-15 Thesis/chapter/03-theoretical-background.tex
ueberarbeitet

@@
-\td{https://en.wikipedia.org/wiki/Thesis}
+%\td{https://en.wikipedia.org/wiki/Thesis}
 \ds{what is it? What is it used for? How does it work? What different kinds are there? }
 \ds{what? how? why?}
-This chapter can be broken down into three section. 
-The first chapter tries to shine light on the evolution of PV and give some background on \gls{cigs}.
-The second chapter reads about material-scientific methods which were used during the practical part of this work. 
+This chapter can be broken down into three sections. 
+The first section tries to shine light on the evolution of PV and give some background on \gls{cigs}.
+The middle section reads about material-scientific methods which were used during the practical part of this work. 
 The last and third part focuses on the information technological, algorithmic and analytics methods used to optimize and predict material properties.
@@
 will be exhausted within the next 100 years. 
-Even though this time period is not exact and highly dependent on detection methods, 
+Even though this time period is not exact and highly dependent on detection methods of resources, 
 this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
@@
 The photoelectric effect was first described in 1839 by french scientist Alexandre 
-Edmond Becquerel, the father of Henri Becquerel\cite{becquerel1839memoire}. 
-Another relevant piece of the photovoltaic jigsaw was discovered 
+Edmond Becquerel, the father of Henri Becquerel\cite{becquerel1839memoire} (the person after whom the unit is named).
+Another relevant piece of the \gls{pv} jigsaw was discovered 
 with the discovery of photo conductivity of selenium
@@
 rose - fuelled by the oil crisis in 1973 - 
-and the development of photovoltaic for the consumer market was boosted. \\
+and the development of photovoltaic for the consumer market was boosted. 
+This development lead to a drop in 
+average price for \gls{pv} module from \$ 100 per watt in 1975 to \$ 4 per watt in 2007\cite{pagliaro2008flexible}.
 
@@
 \subsubsection{Crystalline Silicon Photovoltaics}
+\td{aka PV basics}
+The vorgang of conversion of photons into voltaic energy can be broken down into two essential steps ( egal ob in silicon based or in plants): the creation of an electron hole pair and then their separation by the structure of the device.
+This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction.
+\td{stop}
 The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
 \td{what is it? What is it used for? How does it work? What different kinds are there? }
+\cite{markvart2013principles}
+\td{CIGS has higher absorption coefficient because of direct band gap in contrast to crystalline silicon which has an indirect band gap and therefore less absorption probability.}
 
@@
 
-Amazingly, the band gap of CIGS can be varied by between 1eV and 1.7eV by varying the indium gallium ratio.
-This is a result of the large difference of band gaps of CuInSe2 and CuGaSe2 (see table \ref{tab:cigs}).
+Amazingly, the band gap of CIGS can be varied between 1eV and 1.7eV by varying the indium gallium ratio.
+This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}).
 

### 2022-07-16 Thesis/chapter/03-theoretical-background.tex
PV basics

@@
 \td{aka PV basics}
-The vorgang of conversion of photons into voltaic energy can be broken down into two essential steps ( egal ob in silicon based or in plants): the creation of an electron hole pair and then their separation by the structure of the device.
+The proecess of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
+the creation of an electron hole pair and then their separation by the structure of the device. 
 This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction.

### 2022-07-19 Thesis/chapter/03-theoretical-background.tex
cigs figure from Markvart Principles
theory overarbeitet

--- 2022-07-15 Thesis/chapter/03-theoretical-background.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Crystalline Silicon Photovoltaics}
-\td{aka PV basics}
-The vorgang of conversion of photons into voltaic energy can be broken down into two essential steps ( egal ob in silicon based or in plants): the creation of an electron hole pair and then their separation by the structure of the device.
+wer penetration depth) of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}).
+
+\subsubsection{Photovoltaics Basics}
+The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
+the creation of an electron hole pair and then its separation by the structure of the device.\cite{markvart2013principles}
 This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction.
-\td{stop}
+This is mainly achieved through a p-n junction.\td{cite a good source} 
+%
 The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
-\td{what is it? What is it used for? How does it work? What different kinds are there? }
-\cite{markvart2013principles}
-\td{CIGS has higher absorption coefficient because of direct band gap in contrast to crystalline silicon which has an indirect band gap and therefore less absorption probability.}
+Together with amorphous silicon 2020 80\% of all sold \gls{pv} where made of silicon.
+A comprehensive overview over different \gls{pv} technologies can be found in \cite{markvart2013principles}.
+\td{What different kinds are there? }
 
@@
 \subsubsection{CIGS}
-CIGS ($\text{CuIn}_\text{x}\text{Ga}_{\text{(1-x)}}\text{Se}_2$) is of the chalcopyrite group (tetragonal crystal system) and can be used as thin film \gls{pv}. 
-Just like CdTe, GaAs and amorphous silicon CIGS have much higher absorption coefficients 
+\gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
+It was first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen} 
+and it's potential use as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
+Just like CdTe, GaAs and amorphous silicon CIGS has much higher absorption coefficients 
 (lower penetration depth) of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}). 
+This is due to a direct band gap rather than an indirect band gap (like crystalline silicon). 
 These thin film \gls{pv}s not only use less material, but also can be used in flexible applications.

### 2022-07-19 Thesis/chapter/03-theoretical-background.tex
theory overarbeitet agin

--- 2022-07-15 Thesis/chapter/03-theoretical-background.tex
@@
 The middle section reads about material-scientific methods which were used during the practical part of this work. 
-The last and third part focuses on the information technological, algorithmic and analytics methods used to optimize and predict material properties.
+The last and third part focuses on the information technological, algorithmic and analytical methods used to optimize and predict material properties.
 
@@
 this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
-One viable options is \gls{pv}.
+One viable option is \gls{pv}.
 
@@
 The photoelectric effect was first described in 1839 by french scientist Alexandre 
-Edmond Becquerel, the father of Henri Becquerel\cite{becquerel1839memoire} (the person after whom the unit is named).
-Another relevant piece of the \gls{pv} jigsaw was discovered 
+Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel (the person after whom the unit is named).
+Another relevant piece of the \gls{pv} jigsaw was brought to light
+%discovered
 with the discovery of photo conductivity of selenium
@@
 \td{aka PV basics}
-The vorgang of conversion of photons into voltaic energy can be broken down into two essential steps ( egal ob in silicon based or in plants): the creation of an electron hole pair and then their separation by the structure of the device.
+The proecess of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
+the creation of an electron-hole pair and then its separation by the structure of the material.
 This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction.
@@
 \td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book (Recreated based on\cite{mertens2015photovoltaik}) or (Image source:\cite{mertens2015photovoltaik})}
+\begin{figure}
+	\includegraphics[width=\textwidth]{./Pics/cigs.png}
+	\caption{Schematic layer sequence of a standard \ch{ZnO}/\ch{CdS}/\ch{Cu(In,Ga)Se2} thin-film solar cell.}
+	\label{fig:cigs}
+\end{figure}
 
@@
 \subsubsection{Sol-Gel and Doctor Blading}
-\td{what is it? What is it used for? How does it work? What different kinds are there? }
-One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
+%\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
+%
+\Gls{dbc} Doctor blade coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing, and ceramic industries.
+The roll to roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
+A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
+In roll-to-roll processes the substrate moves instead of the blade.
 

### 2022-07-19 Thesis/chapter/03-theoretical-background.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Crystalline Silicon Photovoltaics}
-\td{aka PV basics}
-The proecess of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
-the creation of an electron-hole pair and then its separation by the structure of the material.
+\subsubsection{Photovoltaics Basics}
+The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
+the creation of an electron-hole pair and then its separation by the structure of the material.\cite{markvart2013principles}
 This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction.
-\td{stop}
+This is mainly achieved through a p-n junction.\td{cite a good source} 
+%
 The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
-\td{what is it? What is it used for? How does it work? What different kinds are there? }
-\cite{markvart2013principles}
-\td{CIGS has higher absorption coefficient because of direct band gap in contrast to crystalline silicon which has an indirect band gap and therefore less absorption probability.}
+Together with amorphous silicon 2020 80\% of all sold \gls{pv} where made of silicon.
+A comprehensive overview over different \gls{pv} technologies can be found in \cite{markvart2013principles}.
+\td{What different kinds are there? }
 

### 2022-07-21 Thesis/chapter/03-theoretical-background.tex
CIGS history

@@
 the creation of an electron-hole pair and then its separation by the structure of the material.\cite{markvart2013principles}
-This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction.
-This is mainly achieved through a p-n junction.\td{cite a good source} 
+This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. Diodes are also 
+This is often achieved through a p-n junction.\cite{breitenstein2013understanding}
 %
 The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
-Together with amorphous silicon 2020 80\% of all sold \gls{pv} where made of silicon.
+Together with amorphous silicon 2010 over 88\% of all sold \gls{pv} where made of silicon\cite{breitenstein2013understanding}.
 A comprehensive overview over different \gls{pv} technologies can be found in \cite{markvart2013principles}.
-\td{What different kinds are there? }
 
@@
 \gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
-It was first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen} 
-and it's potential use as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
+%It was 
+\ch{CuInSe2} and \ch{CuGaSe2} were first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen} 
+and potential use of \ch{CuInSe2} as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
+\td{Already in 1975 efficiencies of over 10\% were achieved.\cite{kazmerski1976thin}}
 Just like CdTe, GaAs and amorphous silicon CIGS has much higher absorption coefficients 
@@
 
-\td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book (Recreated based on\cite{mertens2015photovoltaik}) or (Image source:\cite{mertens2015photovoltaik})}
 \begin{figure}
@@
 
-The standard substrate is glass 
-because of it's high thermal stability, resistance and hardness. 
+\td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book (Recreated based on\cite{mertens2015photovoltaik}) or (Image source:\cite{mertens2015photovoltaik})}
+\td{On the top of a \gls{cigs} cell there is a conducting and durchsichtige layer of \ch{ZnO}. 
+Why is there this doped \ch{ZnO} layer? 
+Why is there this \ch{CdS} layer? (n-material)
+\gls{cigs} is p-material.
+}
+The glass substrate is located under the molybdenum electrode. 
+It is the standard substrate because of it's high thermal stability, electrical resistance and mechanical hardness. 
 A flexible substrate is needed for a flexible module, though. 

### 2022-07-21 Thesis/chapter/03-theoretical-background.tex
CIGS finish

--- 2022-07-19 Thesis/chapter/03-theoretical-background.tex
@@
 the creation of an electron-hole pair and then its separation by the structure of the material.\cite{markvart2013principles}
-This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction.
-This is mainly achieved through a p-n junction.\td{cite a good source} 
+This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. Diodes are also 
+%This is often achieved through a p-n junction.\cite{breitenstein2013understanding}
+This is often achieved through a p-n junction.
+The n-type side has excess electrons and p-type side has excess electron holes. 
+If the n- and p-type are of the same basis material, they are called homojunctions (silicon); if not, heterojunctions e.g. \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}.\cite{breitenstein2013understanding}
 %
 The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
-Together with amorphous silicon 2020 80\% of all sold \gls{pv} where made of silicon.
+Together with amorphous silicon 2010 over 88\% of all sold \gls{pv} where made of silicon\cite{breitenstein2013understanding}.
 A comprehensive overview over different \gls{pv} technologies can be found in \cite{markvart2013principles}.
-\td{What different kinds are there? }
 
@@
 \gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
-It was first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen} 
-and it's potential use as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
+%It was 
+\ch{CuInSe2} and \ch{CuGaSe2} were first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen}.
+The potential use of \ch{CuInSe2} as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
+%Already in 1975 efficiencies of cells of over 10\% were achieved.\cite{kazmerski1976thin}
+Cells with efficiencies of over 10\% were achieved already by 1975.\cite{kazmerski1976thin}
+Today, 
+\gls{cigs} modules (multiple \gls{pv} cells in series) 
+reach efficiencies of up to 16\%\cite{feurer2017cigs},
+monocrystalline silicon \gls{pv} modules reach efficiencies of 14-20\%
+and polycrystalline silicon \gls{pv} modules 12-17\%\cite{mcevoy2011practical}.
+
 Just like CdTe, GaAs and amorphous silicon CIGS has much higher absorption coefficients 
@@
 
-\begin{table}[htb]
+\begin{table}[tbh]
 	\small
@@
 	\label{tab:cigs:alpha}
-\end{table}
-
-Amazingly, the band gap of CIGS can be varied between 1eV and 1.7eV by varying the indium gallium ratio.
-This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}).
-
-\td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book (Recreated based on\cite{mertens2015photovoltaik}) or (Image source:\cite{mertens2015photovoltaik})}
-\begin{figure}
-	\includegraphics[width=\textwidth]{./Pics/cigs.png}
-	\caption{Schematic layer sequence of a standard \ch{ZnO}/\ch{CdS}/\ch{Cu(In,Ga)Se2} thin-film solar cell.}
-	\label{fig:cigs}
-\end{figure}
-
-The standard substrate is glass 
-because of it's high thermal stability, resistance and hardness. 
-A flexible substrate is needed for a flexible module, though. 
-Plastics have a very low melting points and metals are conducting, but can be coated with a non conducting material such as \gls{zro}.
-\begin{table}[htb]
-    \center
+%
+	\vspace{1cm}
     \begin{tabular}{cccc}
         \hline\hline
-        Empirical Formula&    Name&   Band Gap&    Abbreviation\\
+		Empirical Formula&    Name&   Band Gap [\si{eV}{}]&    Abbreviation\\
         \hline
-		\ch{CuInSe2}&       copper indium di selenide&  1&  CISe\\
+		\ch{CuInSe2}&       copper indium di selenide&  1.04&  CISe\\
 		\ch{CuInS2}&        copper indium di sulfide&  1.5&  CIS\\
@@
 
+\begin{figure}
+	\includegraphics[width=\textwidth]{./Pics/cigs.png}
+	\caption{Schematic layer sequence of a standard \ch{ZnO}/\ch{CdS}/\ch{Cu(In,Ga)Se2} thin-film solar cell.}
+	\label{fig:cigs}
+\end{figure}
+
+%\td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book (Recreated based on\cite{mertens2015photovoltaik}) or (Image source:\cite{mertens2015photovoltaik})}
+%\td{On the top of a \gls{cigs} cell there is a conducting and durchsichtige layer of \ch{ZnO}. 
+%Why is there this doped \ch{ZnO} layer?
+
+Amazingly, the band gap of CIGS can be varied between \ev{1} and \ev{1.7} by varying the indium gallium ratio.
+This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}). 
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In figure \ref{fig:cigs} the schematic layer sequence of a standard \gls{cigs} thin film cell is shown. 
+Typically a \um{1} thick molybdenum layer is deposited on soda lime glass. 
+The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in 112 direction\cite{hedstrom1993cigs}.
+A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporated from elemental sources controlled by a mass spectrometer.\cite{hedstrom1993cigs}
+The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
+The heterojunction is then completed by deposition of \ch{CdS} (typically \nm{50} thick).
+\ch{CdS} was earlier used as front contact, but now only acts as n-type wide-gap window and buffer. 
+\ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
+The \ch{ZnO} window layer (usually of thickness 50-\nm{70} is highly conductive (especially the \ch{Al} doped layer) and acts as front contact.
+
+%
+Instead of glass as substrate, steel and plastics (e.g. polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
+They both come with their own inconveniences. 
+Plastics generally have very low melting points which restrict preparation temperatures.
+Steel, on the other hand, is temperature resistant enough, but is an electric conductor. 
+The conductance of steel can be masked by a insulator layer (e.g. \ch{ZrO2}, \ch{Al2O3}).
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
-The cubic phase can be stabilzed down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
-when cooling and undergoing phase transistion\cite{Nielsen2005}.
+The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
+when cooling and undergoing phase transition\cite{Nielsen2005}.
 It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
 Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3}). 
-"Zirconium alkoxides hyrdolize quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.
+"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.
 

### 2022-07-24 Thesis/chapter/01-introduction.tex
OED/DOE source found

@@
 The resulting optimum is compared with other optimisation methods.
+
+\td{
+This work used a rather unconventional approach. 
+Firstly, a problem was posed. Then, some minor literature research was done and the problem was tackled. 
+Finally, the engineering problem was solved within the limits of acceptability, but not aussreichend for the author. 
+The larger bulk of literature research was done after the practical work has been finished in order to solve the secondary scientific problem of predicting outputs and approximate dependencies. 
+}

### 2022-07-24 Thesis/chapter/03-theoretical-background.tex
OED/DOE source found

@@
 \subsubsection{Design of Experiment}
+In two cases a deliberate design of experiment makes sense. 
+If the query of a new data point is very expensive it favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
+If the query space is so vast, that randomly querying might lead to information about uninteresting part of the domain.
+Continuous state spaces must be accommodated by arbitrary discretization.
+\cite{cohn1996neural}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsubsection{AI vs statistics}
+General experimental procedure from Cherkassky and Mulier\cite{cherkassky1998learning}
+\begin{enumerate}
+	\item State the problem 
+	\item Formulate the hypothesis
+	\item Design the experiment/generate the data
+	\item Collect the data and perform preprocessing
+	\item Estimate the model 
+	\item Interpret the model/draw the conclusions
+\end{enumerate}
+\textbf{1.
+Statement of the Problem} There was no clear statement of the problem.
+Now I would formulate it: "How to produce most insulating layer with least energy?
+How do we define most insulating?" That's why there are two output variables rather than one.
+\textbf{2. Hypothesis Formulation} formulate an unknown dependency and define input and output variables.
+\textbf{3.
+Data Generation and Experiment Design} can be either in control of the modeler (designed experiment) or in an observational setting.
+The data collection can affect the sampling distribution and influence the next steps.
+\textbf{4.
+Collect the Data and Perform Preprocessing} here outliers are detected and data preprocessing/encoding/feature selection.
+Scaling by standard deviation might be a good idea, but independent scaling of variables can lead to suboptimal representation for the learning task.
+Feature selection: A small number of informative features make the task of estimating dependencies easier.
+\textbf{5. Model Estimation} The main goal is to construct a model for accurate prediction of future outputs
+\textbf{6.
+Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete.
+In classical statistics such as linearly parametrized function will suit both requirements.
+More complex and flexible models might lead to better estimates with less interpretability.
+Identifying the most important input variables.
+
+There are not only \textbf{x}(input) and y(output) variables, but also \textbf{z}(uncontrolled/unobserved input variables).
+Issues of methods for learning from data: 
+\begin{itemize}
+	\item How to incorporate a priori assumptions into learning? 
+	\item How to measure model complexity (i.e. flexibility to fit the training data)?
+	\item How to find a optimal balance between the data and a priori knowledge? 
+\end{itemize}
+
+\cite{cherkassky1998learning}
+%%
 \td{let GPT-3 write}

### 2022-07-24 Thesis/chapter/06-results-and-discussion.tex
AI history and intro
OED/DOE source found

@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{XRD}
+\begin{figure}
+	\centering
+	\includegraphics[width=\picwidth]{Pics/xrd.png}
+	\caption{XRD spectra}
+	\label{fig:xrd}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{SEM}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{V-I and PSO//Optimization}
+\td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}
+\td{too much data as input, dimensionality reduction (PCA) and optimization}
+
+\td{show results between 1ml acoh (199), acoh+ipo 1:1 (201) and ipo (192). Show graph of the three vs log pondus G and pinhole density and maybe distribution of single point measurements? 
+\texttt{set boxwidth 2; set xtics 5; p "stat.dat" u 1:3 with boxes} 
+}
+
 \td{base/best sample was somewhot 150, 5 layers 3F 2K/min 400C} what was the best result?
@@
 if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
-\subsection{XRD}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\picwidth]{Pics/xrd.png}
-	\caption{XRD spectra}
-	\label{fig:xrd}
-\end{figure}
-
-\td{show results between 1ml acoh (199), acoh+ipo 1:1 (201) and ipo (192). Show graph of the three vs log pondus G and pinhole density and maybe distribution of single point measurements? 
-\texttt{set boxwidth 2; set xtics 5; p "stat.dat" u 1:3 with boxes} 
-}
+\td{I wanted to exhaust the possibilities of EA (not having enough data).
+i should have rather einengen the search raum as much as possible (spreading the search room too much) and then do optimisation: fix layer count to 3 fix conc to 3F and fix calc temp and rate (or only use two extreme values)}

### 2022-07-26 Thesis/chapter/03-theoretical-background.tex
learning from data 1

@@
 \subsubsection{AI vs statistics}
+\begin{itemize}
+	\item \td{let GPT-3 write}
+	\item check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
+	\item see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
+	\item 
+		\href
+		{https://doi.org/10.1177\%2F1352458520978648}
+		{Machine and deep learning in MS research are just powerful statistics – No}
+\end{itemize}
+
+\subsubsection{Learning from Data}
 General experimental procedure from Cherkassky and Mulier\cite{cherkassky1998learning}
@@
 Identifying the most important input variables.
+\cite{cherkassky1998learning}
 
@@
 \end{itemize}
+\cite{cherkassky1998learning}
 
-\cite{cherkassky1998learning}
+"Learning is the process of estimating an unkown (input,output) dependency of structure of a system using a limit number of observations."\cite{cherkassky1998learning}
+
+The process informal part of selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} (page 25)
+
+"Do not attempt to solve a specified problem by indirectly solving a harder general problem as an intermediate step."\cite{cherkassky1998learning}(p33)
+
+"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)
+
+Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
+Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps.
+
+Any learning process requires the following(p40): 
+\begin{itemize}
+	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
+	\item A priori knowledge to impose contrains
+	\item An inductive principle (what needs to be done)
+		\begin{itemize}
+			\item penalizeation (regularization) inductive principle
+			\item early stopping rules (with ANN, difficult to control and interpret)
+			\item structural risk minimization (SRM) (order according to complexity)
+			\item Bayesian Inference (add subjectivity to learning machine)
+			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
+		\end{itemize}
+	\item A learning method (how does it need to be done,implementation)
+\end{itemize}
+
+\textbf{Curse and Complexity of Dimensionality}
+goal is to estimate function with finite samples, so it's always inaccurate (biased). 
+meaning full estimate only possible with high sampling density, which is difficult for high dimensional functions.
+\begin{enumerate}
+	\item Sample sizes yielding the same denisty increse exponentially with dimension .
+	\item A large radius is needed to enclose a fraction of the data points in a high-dimensional space.
+	\item Almost every point is closer to an edge than to another point.
+	\item Almost every point  is an outlier in its own projection.
+\end{enumerate}
+
 %%
-\td{let GPT-3 write}
-check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
-see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
-\url{https://journals.sagepub.com/doi/pdf/10.1177/1352458520978648}
-\url{https://journals.sagepub.com/doi/full/10.1177/1352458520978648}
+Further Literature: 
+\begin{itemize}
+	\item 
+		\href
+		{https://doi.org/10.1016/0893-6080(94)90066-3}
+		{Pedagogical pattern selection strategies}
+	\item 
+		\href
+		{https://doi.org/10.1016/0893-6080(95)00137-9}
+		{Neural Network Exploration Using Optimal Experiment Design}
+	\item 
+		\href
+		{https://doi.org/10.1016/S0076-5392(08)63235-X} 
+		{Chapter 6 Experiment Design}
+	\item 
+		\href
+		{https://doi.org/10.1177\%2F1352458520978648}
+		{Machine and deep learning in MS research are just powerful statistics – No}
+\end{itemize}

### 2022-07-29 Thesis/chapter/03-theoretical-background.tex
DOE research

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Design of Experiment}
+\subsubsection{Design of Experiment} %DOE
+"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."\cite{goodwin1977experiment}
+Contstraints might include range constraints of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
+"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
+
 In two cases a deliberate design of experiment makes sense. 
@@
 \cite{cohn1996neural}
+
+DOEs: randomization, latin square
+\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}
+\url{https://rss.onlinelibrary.wiley.com/doi/abs/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}
+maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{enumerate}
-	\item Sample sizes yielding the same denisty increse exponentially with dimension .
+	\item Sample sizes yielding the same density increse exponentially with dimension.
 	\item A large radius is needed to enclose a fraction of the data points in a high-dimensional space.
@@
 		\href
-		{https://doi.org/10.1016/S0076-5392(08)63235-X} 
-		{Chapter 6 Experiment Design}
+		{hArticlettps://doi.org/10.1016/S0076-5392(08)63235-X} 
+        {Chapter 6 Experiment Design}\cite{goodwin1977experiment}
 	\item 

### 2022-07-31 Thesis/chapter/03-theoretical-background.tex
ANOVA

@@
 
-DOEs: randomization, latin square
+DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, 
 \url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}
@@
 maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Analysis of Variance} % ANOVA
+The statistical significance of the experiment is determined by a ratio of two variances.
+This ratio is independent of several possible alterations to the experimental observations: Adding a constant to all observations does not alter significance.
+Multiplying all observations by a constant does not alter significance.
+So ANOVA statistical significance result is independent of constant bias and scaling errors as well as the units used in expressing observations.
+%https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions
+\td{make analysis with EMMA dataset and EMMA+DOE}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-08-08 Thesis/chapter/03-theoretical-background.tex
stat

@@
 \td{make analysis with EMMA dataset and EMMA+DOE}
+\url{https://www.scribbr.com/statistics/anova-in-r/} just make input categorical
+\url{https://pypi.org/project/pynova/}
+\textbf{Assumptions of ANOVA}
+from \url{https://statsandr.com/blog/anova-in-r/}
+\begin{itemize}
+    \item variable type: continuous dependent variable and categorial qualitative independent variable (also called treatments or levels).
+The input variables are discretized an can therefore be seen as categorial.
+    \item Independence: groups and levels should be independent
+    \item Normality: the residual (that is the durchschnittliche dependance of uncontrollable variables ,like room temperature or humidity) should approximately follow a normal distribution. 
+    \item Equality of variance: variance in differenct groups should be equal (compare with homoscedasticity).
+    \item No outliers
+\end{itemize}
+
+\textbf{Other statistics}
+\begin{itemize}
+    \item f-test 
+    \item p-value 
+    \item t-test
+\end{itemize}
 

### 2022-08-10 Thesis/chapter/03-theoretical-background.tex
basic statistics + plotting

@@
     \item f-test 
-    \item p-value 
-    \item t-test
+    \item p-value: Is the probability that a data point is observed under the null hypothesis. A small value argues against the null hypothesis. 
+    \item t-test: will tell you if a variable is statistically significant. 
+    \item f-test: will tell you if a group of variables is jointly significant
 \end{itemize}
+
+let's rule out different input variables: \\
+does the heating temperature influence the resistance?  no \\
+does the heating velocity influence the resistance?  hardly\\
+do conc and layers number influence resistance? linear \\
+do db velocity and db temperautre influence resistance? how\\
+
+somebody very wise (my superviser) once said: we need to able to predict it otherwise it is just an engineering problem \td{(look at mail)}
 

### 2022-08-11 Thesis/chapter/03-theoretical-background.tex
further stats: gisela Haertler

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\ds{
+introduction 
+    why I chose this practicum, 
+        bcs wanted to check if lab is for me 
+    why i chose to include ml 
+        bcs I wanted what i learned during undergrad courses help me find a good solution and 
+        wanted to dive deeper into the ml field as it is very interesting for 
+what is ML? 
+what kind of ML techniques? 
+statistics:
+what is the difference between ml and stat? 
+    superficially very similar but different goals and diff rahmenbedingungen 
+DOE is a very old, much information less experiments 
+    how to design experiment: already many insights for next time 
+statistics: 
+    help me find insight from data 
+    ANOVA 
+    linear regression 
+}
+
 \subsection{Machine Learning and Statistics}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Why introduce machine learning to this project? 
+I wanted to apply and delve into what I've been studying during my undergrad courses. 
+This seemed like the perfect oppurtunity.
+
 \subsubsection{Artificial Inteligence and Machine Learning}
-
+%How can \gls{ai} and \gls{ml} be defined? 
 The history of \gls{ai} goes back to the middle of the \nth{20} century. 
 Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
-For a more in depth dive into the history of AI consult the beautifully written review\cite{Apter1982} of McCorduck's 1982 book "Machines Who Think"\cite{McCorduck1982}, which focuses also on the great minds behind advances of \gls{ai}.
+\Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
+%For a more in depth dive into the history of AI consult the beautifully written review\cite{Apter1982} of McCorduck's 1982 book "Machines Who Think"\cite{McCorduck1982}, which focuses also on the great minds behind advances of \gls{ai}.
 Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{Howard2019}. 
@@
 creating non existing faces\cite{Mansourifar2020}, 
-create artwork (DALL-E 2)\cite{Marcus2022} or 
+create graphic artwork (DALL-E 2)\cite{Marcus2022} or 
 making video games\cite{Guzdial2016}.
@@
 \subsubsection{Machine Learning Methods}
+%
+\Gls{ml} is at the base of most \gls{ai}s.
+It is a umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
+%
 There is a platitude of different machine learning methods: 
@@
 and periodically request new data in order to solve the problem iteratively.
+\td{This is exactly what I needed because every experiment is very time intensive.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Free writing about AI}
-I chose an evolutionary algorithm which is - i think - also part of machine learning, 
-which is a part of AI. 
-There are many different types of AI. what are the most haeufig sub domains of the AI field? 
-(natural) language processing, image erkennung, and prediction which can be geteilt in 
-classification (discrete) and continuous prediction. 
-These are mainly machine learning algos. other machine learning tasks are EA, PSO,
+\subsubsection{Particle Swarm Optimization}
 
-\subsubsection{2022-06-19-Free-Writing}
-The problem which presents it self is in principle a search problem.
-A large space of possible combinations of experimental anordnungen presents it self
-and out of these we want to find the optimial parameter combination. 
-The best way with unlimitied resources would be the brute-force approach to try every possibility. 
-But due to limited time this is unfeasable. 
-But a new questions arises: how should the ausmasse of the search space be eingeschraenkt? 
-What are the upper and lower limits and which intervals/step size/grid size should be used. 
-Also even before, we have to answer which dimensions/parameters should we include in the search? 
-Which parameters should we keep constant and at which value? 
-And finally which features should we use to measure the goodness of an experiment?
-
-I tried different methods to answer the first X questions: Latin square and Plackett-Burman design.
-Unfortunately, I was faced with similar questions. How many levels and which end points? 
-latin squares are about orthogonality 
-PB is a factorial experiment desing in contrast to one-fator-at-a-time methods.
-reliability and validity are low due to experiments not replicated
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Particle Swarm Optimization}
 it has been shown that \gls{pso} works well on problems wher \gls{ga}s work well\cite{Kennedy1995}. 
@@
 %
-\subsubsection{things I should try if they work:}
-\begin{itemize}
-    \item GA 
-    \item what is reinforcement learning? 
-    \item PCA
-    \item linear regression
-    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
-    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
-    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
-\end{itemize}
-
-%    https://en.wikipedia.org/wiki/Design_of_experiments
-%    https://en.wikipedia.org/wiki/The_Design_of_Experiments
-%    https://en.wikipedia.org/wiki/Response_surface_methodology
-%    https://en.wikipedia.org/wiki/Optimal_design
-%    https://sci-hub.st/https://doi.org/10.2307/2332195
-%    https://en.wikipedia.org/wiki/Latin_square
-%    https://en.wikipedia.org/wiki/Outline_of_artificial_intelligence
-%    https://en.wikipedia.org/wiki/Evolutionary_algorithm
-%    https://en.wikipedia.org/wiki/Particle_swarm_optimization
-%    EMMA doesn't allow for reproducibility
-
-\td{
-\url{https://stats.stackexchange.com/questions/5026/what-is-the-difference-between-data-mining-statistics-machine-learning-and-ai}
-In principle both AI and stat use math to get information out of data. 
-AI might use machine learning to create "intelligent" acting (playing a game or driving a  car).
-machine learning tries to predict unseen data points  and statistics is a subfield of maths which tries to get insight into a given data.
-For example, in a statistical model, it is desirable to reduce the number of inputs.
-This allows the statistician to better study how a change in the input variable can be directly affected by the output variable.\cite{gontcharov2019}
-pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
-    }
 
@@
 maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The statistical significance of the experiment is determined by a ratio of two variances. 
-This ratio is independent of several possible alterations to the experimental observations: Adding a constant to all observations does not alter significance.
+This ratio is independent of several possible alterations to the experimental observations: 
+Adding a constant to all observations does not alter significance. 
 Multiplying all observations by a constant does not alter significance. 
-So ANOVA statistical significance result is independent of constant bias and scaling errors as well as the units used in expressing observations.
-%https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions
+So ANOVA statistical significance result is independent of constant bias and scaling errors 
+as well as the units used in expressing observations. %https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions
 \td{make analysis with EMMA dataset and EMMA+DOE}
@@
 \subsubsection{AI vs statistics}
+As \gls{ml} failed me or rather I failed in \gls{ml} (see Learning from Data) I tried to extract as much insight as possible using statistics. 
+What is statistics, though and what seperates it from \gls{ml}? 
 \begin{itemize}
@@
 \end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Free writing about AI}
+I chose an evolutionary algorithm which is - i think - also part of machine learning, 
+which is a part of AI. 
+There are many different types of AI. what are the most haeufig sub domains of the AI field? 
+(natural) language processing, image erkennung, and prediction which can be geteilt in 
+classification (discrete) and continuous prediction. 
+These are mainly machine learning algos. other machine learning tasks are EA, PSO,
+
+\subsubsection{2022-06-19-Free-Writing}
+The problem which presents it self is in principle a search problem.
+A large space of possible combinations of experimental anordnungen presents it self
+and out of these we want to find the optimial parameter combination. 
+The best way with unlimitied resources would be the brute-force approach to try every possibility. 
+But due to limited time this is unfeasable. 
+But a new questions arises: how should the ausmasse of the search space be eingeschraenkt? 
+What are the upper and lower limits and which intervals/step size/grid size should be used. 
+Also even before, we have to answer which dimensions/parameters should we include in the search? 
+Which parameters should we keep constant and at which value? 
+And finally which features should we use to measure the goodness of an experiment?
+
+I tried different methods to answer the first X questions: Latin square and Plackett-Burman design.
+Unfortunately, I was faced with similar questions. How many levels and which end points? 
+latin squares are about orthogonality 
+PB is a factorial experiment desing in contrast to one-fator-at-a-time methods.
+reliability and validity are low due to experiments not replicated
+
+\subsubsection{things I should try if they work:}
+\begin{itemize}
+    \item GA 
+    \item what is reinforcement learning? 
+    \item PCA
+    \item linear regression
+    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
+    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
+    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
+\end{itemize}
+
+%    https://en.wikipedia.org/wiki/Design_of_experiments
+%    https://en.wikipedia.org/wiki/The_Design_of_Experiments
+%    https://en.wikipedia.org/wiki/Response_surface_methodology
+%    https://en.wikipedia.org/wiki/Optimal_design
+%    https://sci-hub.st/https://doi.org/10.2307/2332195
+%    https://en.wikipedia.org/wiki/Latin_square
+%    https://en.wikipedia.org/wiki/Outline_of_artificial_intelligence
+%    https://en.wikipedia.org/wiki/Evolutionary_algorithm
+%    https://en.wikipedia.org/wiki/Particle_swarm_optimization
+%    EMMA doesn't allow for reproducibility
+
+\td{
+\url{https://stats.stackexchange.com/questions/5026/what-is-the-difference-between-data-mining-statistics-machine-learning-and-ai}
+In principle both AI and stat use math to get information out of data. 
+AI might use machine learning to create "intelligent" acting (playing a game or driving a  car).
+machine learning tries to predict unseen data points  and statistics is a subfield of maths which tries to get insight into a given data.
+For example, in a statistical model, it is desirable to reduce the number of inputs.
+This allows the statistician to better study how a change in the input variable can be directly affected by the output variable.\cite{gontcharov2019}
+pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
+    }

### 2022-08-19 Thesis/chapter/03-theoretical-background.tex
Goodwin quote

@@
 Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
-Other common \td{architectures} are linear regression, kernel ridge regression, support vector regression.
+Other common architectures include linear regression, kernel ridge regression, support vector regression.
 There are also lesser know algorithms like 
@@
 The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes.
-This process is repeated until a satisfactory solution is found.\footnote{This paragraph was written by GPT\cite{Liu2021gpt} providing the input "Introduction to genetic algorithms: "}
+This process is repeated until a satisfactory solution is found.\footnote{This paragraph was written by GPT\cite{Liu2021gpt} given the input "Introduction to genetic algorithms: "}
 
@@
 \subsubsection{Design of Experiment} %DOE
-"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."\cite{goodwin1977experiment}
+%\epigraph{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}{Grahem C.
+Goodwin\cite{goodwin1977experiment}}
+%
+\begin{quote}
+	{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}
+	- {Grahem C. Goodwin\cite{goodwin1977experiment}}
+\end{quote}
+%
 Contstraints might include range constraints of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
@@
 In two cases a deliberate design of experiment makes sense. 
-If the query of a new data point is very expensive it favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
+If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
 If the query space is so vast, that randomly querying might lead to information about uninteresting part of the domain.
@@
 
+"Je grösser nämlich die Anzahl freier Parameter im Modell ist, umso grösser ist der erforderliche Datenumfang und umso ungenauer wir die statistisch gewonnene Aussgae bei gleichem Datenumfang." - Gisela Härtler\cite{haertler2014statistisch}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 What is statistics, though and what seperates it from \gls{ml}? 
+more genau mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of of \td{finding correlation from data, finding mathematical models to describe the data} where as (classical) statistics is the domain of representing the data.
 \begin{itemize}

### 2022-08-22 Thesis/chapter/03-theoretical-background.tex
aestetic

@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %\td{https://en.wikipedia.org/wiki/Thesis}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Photovoltaics}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
 \subsubsection{Problems of current energy supply}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Materials and Their Analysis}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Zirconium oxide}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Machine Learning and Statistics}
 \ds{
@@
 
-\subsection{Machine Learning and Statistics}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Artificial Inteligence and Machine Learning}
@@
 DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, 
-\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}
-\url{https://rss.onlinelibrary.wiley.com/doi/abs/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}
+\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}\\
+\url{https://doi.org/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}
 maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Learning from Data}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{2022-06-19-Free-Writing}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{things I should try if they work:}
@@
 }
+
+am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
+ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell \cite{haertler2014statistisch}
+Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
+Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}

### 2022-08-24 Thesis/chapter/03-theoretical-background.tex
DOE und PSO

@@
 playing board games (and beating humans)\cite{Silver2017,Feng1999,Campbell2002}, 
-image recognition (in medicine)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
-in chemistry\cite{Westermayr2019,goh2017chemception,jha2018elemnet}, 
+image recognition (very popular for medical diagnosis)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
+chemistry\cite{Westermayr2019,goh2017chemception,jha2018elemnet}, 
 cyber security\cite{Sarker2021},
@@
 financial sector (as robo-advisors)\cite{Littman2021},
-natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021} (which can also create pictures through scalable vector graphics (SVG) and code)
+natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021} 
+(which can also create code and pictures through scalable vector graphics (SVG))
 and even creative tasks like 
@@
 This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
-certain fields get incorporated into \gls{ai} research and practice and after some time of general use are no more considered \gls{ai} (e.g. spam filter or web searches).
+certain fields get incorporated into \gls{ai} research and practice.
+Such that, after some time of general use it is no more considered \gls{ai} (e.g. spam filter or web searches).
 Google CEO Sundar Pichai even goes as far and said: 
@@
 they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
-An orthogonal division can be made by regression (continuous) versus classification (discrete). 
+An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
 Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
@@
 
-\Gls{pso} also uses a starting population of particles of size $p$ where each experiment 
+\Gls{pso} also uses a starting population of particles where each experiment (particle) 
 is represented by its independent and dependent variables. 
-It was originally inspired by the behaviour of bird flocks and fish school.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Particle Swarm Optimization}
-
-it has been shown that \gls{pso} works well on problems wher \gls{ga}s work well\cite{Kennedy1995}. 
-It can be seen as in the middle of \gls{ga} (taking eons) and \gls{nn} taking seconds regarding time scale\cite{Kennedy1995}.
-it is a stochastic process
-are there iterative optimisation processes without stochastic? 
-%
+It was originally inspired by the behaviour of bird flocks and fish schools.
+Each particle has an associated position and velocity. 
+Every movement across the search space is stochastic and influenced by its particle velocity and position as well as its and the swarm's best known position.
 
@@
 %
-Contstraints might include range constraints of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
-"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
-
-In two cases a deliberate design of experiment makes sense. 
+In two cases a deliberate design of experiment is beneficial.
 If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
 If the query space is so vast, that randomly querying might lead to information about uninteresting part of the domain.
-Continuous state spaces must be accommodated by arbitrary discretization.
+% 
+At the beginning of an experiment its constraints must be determined. 
+%
+Constraints for a given experiment might include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
+%
+
+A naive approach to an experiment design is the full factorial \gls{doe}.
+Each possible combination of discrete values is tested. 
+While this is the best design it will more often than not be infeasible due the curse of dimensionality.
+The 2-level factorial design provides an alternative with $2^d$ (where d is the dimensionality of the problem) experiments. 
+Drawbacks of 2-level factorial include no data about the inside of the search space and infeasibility for moderate dimensional problems.
+
+The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of the two level fractional factorial design, 
+where the number of needed experiments is smaller than $d+2$ and 
+each combination of levels for any pair of factors appears the same number of times. 
+In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
+%A straight forward design can be to randomly chose a certain number of experiments from the search space. 
+A drawback of randomization is that sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
+The Hammersley design\cite{viana2016tutorial,diwekar1997efficient} is based on the Hammersley sequence and produces space filling data points. 
+The Latin hypercube \gls{doe}\cite{viana2016tutorial,diwekar1997efficient} is a type of orthogonal \gls{doe}, 
+which has the advantage that 
+each level for each variable will be tested only once. 
+A Latin hypercube \gls{doe} can be also created such that data points more uniformly distribute over the search space. 
+%"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
+%
+%Continuous state spaces must be accommodated by arbitrary discretization.
 \cite{cohn1996neural}
+%
+At
 
 DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, 
-\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}\\
-\url{https://doi.org/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}
+\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal} very math intensive  \\
+\url{https://doi.org/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}  \\
 maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}

### 2022-08-24 Thesis/chapter/06-results-and-discussion.tex
learning from data 1
DOE und PSO

@@
 \subsection{V-I and PSO//Optimization}
-\td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}
-\td{too much data as input, dimensionality reduction (PCA) and optimization}
+\td{ideal objective is to create response surface approximation}\\
+\td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}\\
+\td{too much data as input, dimensionality reduction (PCA) and optimization}\\
+\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}
+\td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
+The primary goal of a screening experiment is to identify the active factors. 
+A secondary goal is to provide a simple model that captures the essential features of the 
+relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}
 
@@
 i should have rather einengen the search raum as much as possible (spreading the search room too much) and then do optimisation: fix layer count to 3 fix conc to 3F and fix calc temp and rate (or only use two extreme values)}
+
+\td{I wanted to let the algorithm show what I already knew instead of letting my a priori knowledge constrain the model before starting.}
+
+\subsection{DOE}
+factorial design (classical \gls{doe} is more robust at feature extraction for error laden data \cite{giunta2003overview}

### 2022-08-26 Thesis/chapter/03-theoretical-background.tex
DOE edit

@@
 %
-In two cases a deliberate design of experiment is beneficial.
+In two cases a deliberate \gls{doe} is beneficial.
 If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
-If the query space is so vast, that randomly querying might lead to information about uninteresting part of the domain.
+If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.
 % 
@@
 Each possible combination of discrete values is tested. 
-While this is the best design it will more often than not be infeasible due the curse of dimensionality.
-The 2-level factorial design provides an alternative with $2^d$ (where d is the dimensionality of the problem) experiments. 
+While this is the most informative design it will more often than not be infeasible due the curse of dimensionality\cite{cherkassky1998learning}.
+The 2-level factorial design provides an alternative with $2^d$ (where $d$ is the number of independent variables) experiments. 
 Drawbacks of 2-level factorial include no data about the inside of the search space and infeasibility for moderate dimensional problems.
+In a full factorial or 2-level factorial design most experiments are redundant and most resources will be spent exploring high-order interaction effects\cite{gunst2009fractional}.
+In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
+%A straight forward design can be to randomly chose a certain number of experiments from the search space.
 
-The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of the two level fractional factorial design, 
+The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 
 where the number of needed experiments is smaller than $d+2$ and 
 each combination of levels for any pair of factors appears the same number of times. 
-In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
-%A straight forward design can be to randomly chose a certain number of experiments from the search space. 
-A drawback of randomization is that sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
+A drawback of randomization and 2-level factorial designs is that the sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
 The Hammersley design\cite{viana2016tutorial,diwekar1997efficient} is based on the Hammersley sequence and produces space filling data points. 
 The Latin hypercube \gls{doe}\cite{viana2016tutorial,diwekar1997efficient} is a type of orthogonal \gls{doe}, 
-which has the advantage that 
-each level for each variable will be tested only once. 
+which has the advantage that each level for each variable will be tested only once. 
 A Latin hypercube \gls{doe} can be also created such that data points more uniformly distribute over the search space. 
@@
 %
-At
+\td{For a 2-level factorial applies: "The effect of any factor main effect (A, B, C) or interaction (AB, AC, BC, ABC) is the difference of two averages, the average of the responses correpsonding to +1 levels and the average of the responses corresponding to -1 levels.
+" - from Gunst2009\cite{gunst2009fractional}}
 
@@
 am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
-ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell \cite{haertler2014statistisch}
+"ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell" \cite{haertler2014statistisch}
 Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
 Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}
+
+\td{if i want to learn about support vector machine, read chapter 4,7,8 from "Learning from Data" by Cherkassky\cite{cherkassky1998learning} (TUBib 726-1998)}

### 2022-08-26 Thesis/chapter/06-results-and-discussion.tex
DOE edit

@@
 factorial design (classical \gls{doe} is more robust at feature extraction for error laden data \cite{giunta2003overview}
+
+\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest.
+Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2007
+but on the other hand 
+If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?

### 2022-08-29 Thesis/chapter/03-theoretical-background.tex
pyDOE

@@
 \ds{
-introduction 
-    why I chose this practicum, 
-        bcs wanted to check if lab is for me 
-    why i chose to include ml 
-        bcs I wanted what i learned during undergrad courses help me find a good solution and 
-        wanted to dive deeper into the ml field as it is very interesting for 
-what is ML? 
-what kind of ML techniques? 
 statistics:
@@
 		superficially very similar but different goals and diff rahmenbedingungen 
-DOE is a very old, much information less experiments 
-    how to design experiment: already many insights for next time 
-statistics: 
-    help me find insight from data 
-    ANOVA 
+    how can i usee ANOVA 
     linear regression 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Why introduce machine learning to this project? 
-I wanted to apply and delve into what I've been studying during my undergrad courses. 
-This seemed like the perfect oppurtunity.
+%Why introduce machine learning to this project? 
+%I wanted to apply and delve into what I've been studying during my undergrad courses. 
+%This seemed like the perfect oppurtunity. 
+Is machine learning just hyped statistics? No! 
+Although machine learning uses several statistical methods, their goal and frame conditions are different. 
+\td{The goal of machine learning is to ???}
 
@@
 \Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
-%For a more in depth dive into the history of AI consult the beautifully written review\cite{Apter1982} of McCorduck's 1982 book "Machines Who Think"\cite{McCorduck1982}, which focuses also on the great minds behind advances of \gls{ai}.
 Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{Howard2019}. 
@@
 \Gls{ml} is at the base of most \gls{ai}s.
-It is a umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
+It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
 %
@@
 An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
-Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
+Independent from these $2\cdot2$ categories there are multiple ways to let machines learn from data.
+%
 \Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
-%
 Artificial neurons (also called nodes), which are arranged in layers, 
@@
 Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
-Other common architectures include linear regression, kernel ridge regression, support vector regression.
+Other common architectures include linear regression, kernel ridge regression and support vector regression.
 There are also lesser know algorithms like 
@@
 is represented by its independent and dependent variables. 
-It was originally inspired by the behaviour of bird flocks and fish schools.
+It was originally inspired by the behaviour of bird flocks and fish schools\cite{Kennedy1995}.
 Each particle has an associated position and velocity. 
@@
 % 
-At the beginning of an experiment its constraints must be determined. 
+At the beginning of any experiment its constraints must be determined. 
 %
-Constraints for a given experiment might include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
+Constraints for a given experiment include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
 %
 
+%FULL FACTORIAL
 A naive approach to an experiment design is the full factorial \gls{doe}.
@@
 While this is the most informative design it will more often than not be infeasible due the curse of dimensionality\cite{cherkassky1998learning}.
+% 2-LVL FACTORIAL
 The 2-level factorial design provides an alternative with $2^d$ (where $d$ is the number of independent variables) experiments. 
-Drawbacks of 2-level factorial include no data about the inside of the search space and infeasibility for moderate dimensional problems.
-In a full factorial or 2-level factorial design most experiments are redundant and most resources will be spent exploring high-order interaction effects\cite{gunst2009fractional}.
+Drawbacks of 2-level factorial \gls{doe}s include no data about the inside of the search space and infeasibility for high dimensional problems.
+In a full factorial or 2-level factorial design most experiments are redundant and most resources will be spent exploring high-order interaction effects\cite{gunst2009fractional}, which are often minimal to non-existent.
+% RANDOM 
 In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
+%
 %A straight forward design can be to randomly chose a certain number of experiments from the search space. 
-
+%Alternatively, a subset of from the 2-level factorial design can be chosen, which is called a fractional factorial design. 
+When a subset is chosen from the factorial design, it is called a fractional factorial design. 
+% PLACKETT_BURMAN
 The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 
-where the number of needed experiments is smaller than $d+2$ and 
-each combination of levels for any pair of factors appears the same number of times. 
-A drawback of randomization and 2-level factorial designs is that the sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
+where the number of needed experiments $n$ is $n<d+4$ 
+(more precisely $n=(\lfloor d\div4\rfloor+1)\cdot4$, where $\lfloor x\rfloor$ denotes the floor function on $x$) 
+and each combination of levels for any pair of factors appears the same number of times. 
+% HAMMERSLEY 
+A drawback of 2-level factorial and random fractional designs is that the sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
 The Hammersley design\cite{viana2016tutorial,diwekar1997efficient} is based on the Hammersley sequence and produces space filling data points. 
+% LATIN HYPER CUBE
 The Latin hypercube \gls{doe}\cite{viana2016tutorial,diwekar1997efficient} is a type of orthogonal \gls{doe}, 
@@
 A Latin hypercube \gls{doe} can be also created such that data points more uniformly distribute over the search space. 
+Latin hypercube \gls{doe}s are mainly used in computer simulations which are purely deterministic and therefore have no error. 
 %"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
@@
 %
-\td{For a 2-level factorial applies: "The effect of any factor main effect (A, B, C) or interaction (AB, AC, BC, ABC) is the difference of two averages, the average of the responses correpsonding to +1 levels and the average of the responses corresponding to -1 levels.
+\td{For any 2-level factorial DOE applies: "The effect of any factor main effect (A, B, C) or interaction (AB, AC, BC, ABC) is the difference of two averages, the average of the responses correpsonding to +1 levels and the average of the responses corresponding to -1 levels.
 " - from Gunst2009\cite{gunst2009fractional}}
 
-DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, 
-\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal} very math intensive  \\
+DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, \\
 \url{https://doi.org/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}  \\

### 2022-08-29 Code/Statistics/pydoe.sh

@@ -1,0 +1,14 @@
+#!/usr/bin/env sh
+[ -z "$1" ] && echo "USAGE: $0 <INTEGER>" && exit 
+factors=$1
+dirname=`mktemp -d`
+#echo "This will take about 1 minutes"
+python3 -m venv $dirname
+source ${dirname}/bin/activate 
+#set -x 
+pip install --upgrade pip wheel > /dev/null
+pip install pydoe > /dev/null
+#set +x
+python3 -c "import pyDOE as pd; print(pd.doe_plackett_burman.pbdesign($factors))"
+deactivate
+rm -rf $dirname

### 2022-09-05 Thesis/chapter/03-theoretical-background.tex
anova0

--- 2022-08-26 Thesis/chapter/03-theoretical-background.tex
@@
 An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
+%Two architecture which don't quite fit into this classification are Generative Adversarial Network (GAN) and jk
 Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
@@
 If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.
+%Both encompass nearly all cases. 
 % 
@@
 In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
+%, a fractional factorial \gls{doe}. 
 %A straight forward design can be to randomly chose a certain number of experiments from the search space. 
-
+%
+%
 The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 
@@
 %Continuous state spaces must be accommodated by arbitrary discretization.
-\cite{cohn1996neural}
+%\cite{cohn1996neural}
+\iffalse
 %
@@
 maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}
+\fi
 
@@
 \subsubsection{Analysis of Variance} % ANOVA
+\Gls{anova} analyses the means by means of mincing variances.
+%of of the continuous outputs where inputs are categories. 
+The inputs of the model should be categorical and the outputs continuous. 
 The statistical significance of the experiment is determined by a ratio of two variances. 
-This ratio is independent of several possible alterations to the experimental observations: 
-Adding a constant to all observations does not alter significance. 
-Multiplying all observations by a constant does not alter significance. 
-So ANOVA statistical significance result is independent of constant bias and scaling errors 
-as well as the units used in expressing observations. %https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions
-\td{make analysis with EMMA dataset and EMMA+DOE}
-\url{https://www.scribbr.com/statistics/anova-in-r/} just make input categorical
-\url{https://pypi.org/project/pynova/}
+%This ratio is independent of several possible alterations to the experimental observations: 
+%Adding a constant to all observations does not alter significance. 
+%Multiplying all observations by a constant does not alter significance. 
+\Gls{anova} statistical significance results are independent of constant bias and 
+scaling errors as well as the units used in expressing observations. 
+\href{https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions}{(click here)}
+Addiitonal assumptions of \gls{anova}: groups and levels should be independent, 
+residual error should follow normal distribution, variance of groups should be equal. 
+\href{https://statsandr.com/blog/anova-in-r/}{(click here)}
+
+\textbf{Links}
+\url{https://www.scribbr.com/statistics/anova-in-r/} just make input categorical\\
+\url{https://pypi.org/project/pynova/}\\
+
+\iffalse
 \textbf{Assumptions of ANOVA}
@@
 \end{itemize}
+\fi
 
@@
 \begin{itemize}
-    \item f-test 
+    \item f-test (include to ANOVA \url{https://quantifyinghealth.com/f-statistic-in-linear-regression/})
     \item p-value: Is the probability that a data point is observed under the null hypothesis. A small value argues against the null hypothesis. 
@@
     \item f-test: will tell you if a group of variables is jointly significant
+    \item T-test (signal-noise-ratio \href{https://statisticsbyjim.com/hypothesis-testing/t-tests-1-sample-2-sample-paired-t-tests/}{(click here)}): if variable are stat. significant; 
+    \item F-test (ratio of variances \href{https://statisticsbyjim.com/anova/f-tests-anova/}{click here}): if group of vars stat.
+sig \url{https://quantifyinghealth.com/f-statistic-in-linear-regression/}
 \end{itemize}
 
-let's rule out different input variables: \\
-does the heating temperature influence the resistance?  no \\
-does the heating velocity influence the resistance?  hardly\\
-do conc and layers number influence resistance? linear \\
-do db velocity and db temperautre influence resistance? how\\
-
-somebody very wise (my superviser) once said: we need to able to predict it otherwise it is just an engineering problem \td{(look at mail)}
-
-"Je grösser nämlich die Anzahl freier Parameter im Modell ist, umso grösser ist der erforderliche Datenumfang und umso ungenauer wir die statistisch gewonnene Aussgae bei gleichem Datenumfang." - Gisela Härtler\cite{haertler2014statistisch}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Linear Regression}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 As \gls{ml} failed me or rather I failed in \gls{ml} (see Learning from Data) I tried to extract as much insight as possible using statistics. 
-What is statistics, though and what seperates it from \gls{ml}? 
+What is statistics, though, and what seperates it from \gls{ml}? 
 more genau mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of of \td{finding correlation from data, finding mathematical models to describe the data} where as (classical) statistics is the domain of representing the data.

### 2022-09-05 Thesis/chapter/06-results-and-discussion.tex
anova0

@@
 If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
+
+let's rule out different input variables: \\
+does the heating temperature influence the resistance?  no \\
+does the heating velocity influence the resistance?  hardly\\
+do conc and layers number influence resistance? linear \\
+do db velocity and db temperautre influence resistance? how\\
+
+somebody very wise (my superviser) once said: we need to able to predict it otherwise it is just an engineering problem \td{(look at mail)}
+
+"Je grösser nämlich die Anzahl freier Parameter im Modell ist, umso grösser ist der erforderliche Datenumfang und umso ungenauer wir die statistisch gewonnene Aussgae bei gleichem Datenumfang." - Gisela Härtler\cite{haertler2014statistisch}
+
+\td{make analysis with EMMA dataset and EMMA+DOE}
+\td{talk about the switch of recipe before emma: makes experiments hard/impossible to compare, but more practical and proof that it works weell}

### 2022-09-08 Code/Statistics/stat.R
R statistics basics

@@ -1,0 +1,11 @@
+dat<-read.delim("./db_final.tsv") 
+summary(dat)
+hist(dat$G)
+str(dat)
+boxplot(dat$G)
+boxplot(dat$G ~ dat$TCal )
+boxplot(dat$G ~ dat$TCal, xlab="Calcination Temp [C]", ylab="Resistance") 
+library("vioplot") 
+library("ggplot2")
+mod<-lm(dat$G ~ dat$TCal)
+plot(dat$G ~ dat$TCal)

### 2022-09-08 Thesis/chapter/03-theoretical-background.tex
minor

--- 2022-08-29 Thesis/chapter/03-theoretical-background.tex
@@
 %How can \gls{ai} and \gls{ml} be defined? 
+\Gls{ai} is a trans-disciplinary field with roots in logic, statistics, cognitive psychology, decision theory, neuroscience, linguistics, cybernetics, and computer engineering.\cite{howard2019artificial}
 The history of \gls{ai} goes back to the middle of the \nth{20} century. 
@@
 \Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
-Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{Howard2019}. 
+Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{howard2019artificial}. 
 One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
@@
     \item linear regression
+	\item t-test and anova but on what? 
     \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 

### 2022-09-08 Thesis/chapter/03-theoretical-background.tex

@@
 An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
-Independent from these $2\cdot2$ categories there are multiple ways to let machines learn from data.
+%Two architecture which don't quite fit into this classification are Generative Adversarial Network (GAN) and jk
+Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
 %
@@
 % PLACKETT_BURMAN
+%, a fractional factorial \gls{doe}. 
+%A straight forward design can be to randomly chose a certain number of experiments from the search space. 
+%
+%
 The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 

### 2022-10-05 Thesis/chapter/03-theoretical-background.tex
Turing Test

@@
 (in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
-Another test ingenioused by Alan Turing, is that a human communicates with an unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
-It is easy for humans to come up with question to detect an AI, 
-but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future.
+%Another test ingenioused by Alan Turing, is that a human communicates with an unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
+Another test ingenioused by Alan Turing, is the imitation game\cite{turing1950imitation}, now a days known as Turing test.
+An interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
+\textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is in the interrogators side.
+The question is if \textbf{A} is replaced with an computer how the ratio of outcomes would deviate from the original ratio. 
+%
+%(in written form) and must judge who is the 
+%if they are dealing with a machine or a human being. 
+%
+\td{It is easy for humans to come up with question to detect an AI, 
+but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future.}
 
@@
 \td{if i want to learn about support vector machine, read chapter 4,7,8 from "Learning from Data" by Cherkassky\cite{cherkassky1998learning} (TUBib 726-1998)}
+
+%$\mathcal{Y}(Y)= E$

### 2022-10-16 Thesis/chapter/03-theoretical-background.tex
sputter figure version 0

@@
 
+\begin{figure}[htb]
+	\includegraphics[width=\textwidth]{./Pics/sputter0.png}
+    \caption{Propagation of energy in a dense cascade. Left graph: "Primary" shockwave. Right graph: "Thermal" pulse or "secondary" shockwave. Figure taken from Sigmund 1987\cite{sigmund1987}}
+	\label{fig:sputter}
+\end{figure}
+
 %\td{how does it work?}\\
@@
 two parallel electrodes with low pressure gas in between. 
-The target acts as cathode and the substrate (holder) as anode (see \td{fig}).
+The target acts as cathode and the substrate (holder) as anode (see figure \ref{fig:sputter}).
 %the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
@@
 If a cation has enough energy it will bump off one or more atoms or molecules from the surface. 
-This happens by a cascade of momentum transfers, which can reach the surface again (see fig \td{cp sigmund69}). 
+This happens by a cascade of momentum transfers, which can reach the surface again (see fig \td{from \cite{sigmund1987}}). 
 If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
@@
 %In words: shorter wavelength (higher frequency) photons are more energetic.
-In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?});
+In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?+table});
 from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
-\td{with number?}
 X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
@@
  A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
- In the two-beam-spectrometer the light is split, sent through the sample and a reference and one of the two beams is alternately sent through a monochromator to a detector (\td{thermocouple}). 
+ In the two-beam-spectrometer the light is split, sent through the sample and a reference and one of the two beams is alternately sent through a monochromator to a detector (often a thermopile).
 %
@@
 
-\td{QUESTIONS: 
-	how does detector work? two different for UVVis and MIR
+\td{
 	IR around page 45;
@@
 An interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
-\textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is in the interrogators side.
-The question is if \textbf{A} is replaced with an computer how the ratio of outcomes would deviate from the original ratio. 
+\textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is on the interrogators side.
+The question is if \textbf{A} is replaced with a computer how the ratio of outcomes would deviate from the original ratio. 
 %
@@
 %
-\td{It is easy for humans to come up with question to detect an AI, 
-but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future.}
+%
+%\ds{It is easy for humans to come up with question to detect an AI, 
+%but when reading AI written articles\cite{gpt2020}, 
+%it's easy to see this test being passed in the near future.}
+%
+At the moment it's hard to imagine a computer getting a higher ratio than a human
+but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the future.
 
@@
 evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
+\gls{pso} algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simulta- neously\cite{Villannova2010}.
 %

### 2022-10-16 Code/Statistics/stat.R

@@ -9,3 +9,8 @@ library("vioplot")
 library("ggplot2")
 mod<-lm(dat$G ~ dat$TCal)
 plot(dat$G ~ dat$TCal)
+
+# TODO 
+# small data set 
+# fit with earth 
+# plot earth fit

### 2022-10-16 Thesis/chapter/02-aims-and-objectives.tex
ueberarbeitet
free writing einarbeiten

--- 2021-12-12 Thesis/chapter/aims-and-objectives.tex
@@
 %The method of doctor blading, which is in principle a sol-gel process, 
-This sol-gel process was chosen over spin coating because of the availability to the 
-industrial partner.
+This sol-gel process was chosen over spin coating because of 
+its scalability.
+%the availability to the industrial partner.
 In order to optimize the resulting layer the multitude of parameters was optimized with an particle swarm optimization ansatz. %machine learning 
@@
 \fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{2022-06-19-Free-Writing}
+The problem which presents it self is in principle a search problem.
+A large space of possible combinations of experimental anordnungen presents it self
+and out of these we want to find the optimial parameter combination. 
+The best way with unlimitied resources would be the brute-force approach to try every possibility. 
+But due to limited time this is unfeasable. 
+But a new questions arises: how should the ausmasse of the search space be eingeschraenkt? 
+What are the upper and lower limits and which intervals/step size/grid size should be used. 
+Also even before, we have to answer which dimensions/parameters should we include in the search? 
+Which parameters should we keep constant and at which value? 
+And finally which features should we use to measure the goodness of an experiment?
+
+I tried different methods to answer the first X questions: Latin square and Plackett-Burman design.
+Unfortunately, I was faced with similar questions. How many levels and which end points? 
+latin squares are about orthogonality 
+PB is a factorial experiment desing in contrast to one-fator-at-a-time methods.
+reliability and validity are low due to experiments not replicated
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-10-16 Thesis/chapter/03-theoretical-background.tex
free writing einarbeiten

@@
 		superficially very similar but different goals and diff rahmenbedingungen 
-    how can i usee ANOVA 
+    how can i use ANOVA 
     linear regression 
@@
 %This seemed like the perfect oppurtunity. 
-Is machine learning just hyped statistics? No! 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Is machine learning just hyped statistics? No! 
+		%\href
+		%{https://doi.org/10.1177\%2F1352458520978648}
+		%{Machine and deep learning in MS research are just powerful statistics – No}
 Although machine learning uses several statistical methods, their goal and frame conditions are different. 
-\td{The goal of machine learning is to ???}
+%\td{The goal of machine learning is to ???}
+
+%\begin{itemize}
+%	\item \td{let GPT-3 write}
+%	\item check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
+%	\item see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
+%	\item 
+%		\href
+%		{https://doi.org/10.1177\%2F1352458520978648}
+%		{Machine and deep learning in MS research are just powerful statistics – No}
+%\end{itemize}
+
+%\td{
+%\url{https://stats.stackexchange.com/questions/5026/what-is-the-difference-between-data-mining-statistics-machine-learning-and-ai}
+%In principle both \gls{ml} and statistics use math to get information out of data. 
+%AI might use machine learning to create "intelligent" acting (playing a game or driving a  car). 
+\Gls{ml} tries to predict unseen data points and statistics is a subfield of maths 
+which tries to get insight into a given data. 
+For example, in a statistical model, it is desirable to reduce the number of inputs. 
+This allows the statistician to better study how a change in the input variable can be 
+directly affected by the output variable.\cite{gontcharov2019}
+%pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
+%}
+%What is statistics, though, and what seperates it from \gls{ml}? 
+More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of of 
+\td{finding correlation from data, finding mathematical models to describe the data} 
+where as (classical) statistics is the domain of representing the data. 
+\td{talk about statistics, then the difference to Ml} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\td{if i want to learn about support vector machine, read chapter 4,7,8 from "Learning from Data" by Cherkassky\cite{cherkassky1998learning} (TUBib 726-1998)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %
+%\todo{check out SVM and KRR}
+%
 \Gls{ml} is at the base of most \gls{ai}s.
@@
 evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
-\gls{pso} algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simulta- neously\cite{Villannova2010}.
+\gls{pso} algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simulta- neously\cite{Villanova2010}.
 %
@@
 and periodically request new data in order to solve the problem iteratively.
-\td{This is exactly what I needed because every experiment is very time intensive.}
+%\td{This is exactly what I needed because every experiment is very time intensive.}
 
@@
 Every movement across the search space is stochastic and influenced by its particle velocity and position as well as its and the swarm's best known position.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{EMMA}
+\Gls{emma} and \gls{mars}
 
@@
 \Gls{anova} analyses the means by means of mincing variances.
+\td{at the basis of anova lies the F-test.}
 %of of the continuous outputs where inputs are categories. 
@@
 \fi
-
-\textbf{Other statistics}
-\begin{itemize}
-    \item f-test (include to ANOVA \url{https://quantifyinghealth.com/f-statistic-in-linear-regression/})
-    \item p-value: Is the probability that a data point is observed under the null hypothesis. A small value argues against the null hypothesis. 
-    \item t-test: will tell you if a variable is statistically significant. 
-    \item f-test: will tell you if a group of variables is jointly significant
-    \item T-test (signal-noise-ratio \href{https://statisticsbyjim.com/hypothesis-testing/t-tests-1-sample-2-sample-paired-t-tests/}{(click here)}): if variable are stat. significant; 
-    \item F-test (ratio of variances \href{https://statisticsbyjim.com/anova/f-tests-anova/}{click here}): if group of vars stat.
-sig \url{https://quantifyinghealth.com/f-statistic-in-linear-regression/}
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{AI vs statistics}
-As \gls{ml} failed me or rather I failed in \gls{ml} (see Learning from Data) I tried to extract as much insight as possible using statistics. 
-What is statistics, though, and what seperates it from \gls{ml}? 
-more genau mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of of \td{finding correlation from data, finding mathematical models to describe the data} where as (classical) statistics is the domain of representing the data.
-\begin{itemize}
-	\item \td{let GPT-3 write}
-	\item check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
-	\item see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
-	\item 
-		\href
-		{https://doi.org/10.1177\%2F1352458520978648}
-		{Machine and deep learning in MS research are just powerful statistics – No}
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Learning from Data}
-General experimental procedure from Cherkassky and Mulier\cite{cherkassky1998learning}
-\begin{enumerate}
-	\item State the problem 
-	\item Formulate the hypothesis
-	\item Design the experiment/generate the data
-	\item Collect the data and perform preprocessing
-	\item Estimate the model 
-	\item Interpret the model/draw the conclusions
-\end{enumerate}
-\textbf{1.
-Statement of the Problem} There was no clear statement of the problem.
-Now I would formulate it: "How to produce most insulating layer with least energy?
-How do we define most insulating?" That's why there are two output variables rather than one.
-\textbf{2. Hypothesis Formulation} formulate an unknown dependency and define input and output variables.
-\textbf{3.
-Data Generation and Experiment Design} can be either in control of the modeler (designed experiment) or in an observational setting.
-The data collection can affect the sampling distribution and influence the next steps.
-\textbf{4.
-Collect the Data and Perform Preprocessing} here outliers are detected and data preprocessing/encoding/feature selection.
-Scaling by standard deviation might be a good idea, but independent scaling of variables can lead to suboptimal representation for the learning task.
-Feature selection: A small number of informative features make the task of estimating dependencies easier.
-\textbf{5. Model Estimation} The main goal is to construct a model for accurate prediction of future outputs
-\textbf{6.
-Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete.
-In classical statistics such as linearly parametrized function will suit both requirements.
-More complex and flexible models might lead to better estimates with less interpretability.
-Identifying the most important input variables.
-\cite{cherkassky1998learning}
-
-There are not only \textbf{x}(input) and y(output) variables, but also \textbf{z}(uncontrolled/unobserved input variables).
-Issues of methods for learning from data: 
-\begin{itemize}
-	\item How to incorporate a priori assumptions into learning? 
-	\item How to measure model complexity (i.e. flexibility to fit the training data)?
-	\item How to find a optimal balance between the data and a priori knowledge? 
-\end{itemize}
-\cite{cherkassky1998learning}
-
-"Learning is the process of estimating an unkown (input,output) dependency of structure of a system using a limit number of observations."\cite{cherkassky1998learning}
-
-The process informal part of selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} (page 25)
-
-"Do not attempt to solve a specified problem by indirectly solving a harder general problem as an intermediate step."\cite{cherkassky1998learning}(p33)
-
-"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)
-
-Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
-Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps.
-
-Any learning process requires the following(p40): 
-\begin{itemize}
-	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
-	\item A priori knowledge to impose contrains
-	\item An inductive principle (what needs to be done)
-		\begin{itemize}
-			\item penalizeation (regularization) inductive principle
-			\item early stopping rules (with ANN, difficult to control and interpret)
-			\item structural risk minimization (SRM) (order according to complexity)
-			\item Bayesian Inference (add subjectivity to learning machine)
-			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
-		\end{itemize}
-	\item A learning method (how does it need to be done,implementation)
-\end{itemize}
-
-\textbf{Curse and Complexity of Dimensionality}
-goal is to estimate function with finite samples, so it's always inaccurate (biased). 
-meaning full estimate only possible with high sampling density, which is difficult for high dimensional functions.
-\begin{enumerate}
-	\item Sample sizes yielding the same density increse exponentially with dimension.
-	\item A large radius is needed to enclose a fraction of the data points in a high-dimensional space.
-	\item Almost every point is closer to an edge than to another point.
-	\item Almost every point  is an outlier in its own projection.
-\end{enumerate}
-
-%%
-Further Literature: 
-\begin{itemize}
-	\item 
-		\href
-		{https://doi.org/10.1016/0893-6080(94)90066-3}
-		{Pedagogical pattern selection strategies}
-	\item 
-		\href
-		{https://doi.org/10.1016/0893-6080(95)00137-9}
-		{Neural Network Exploration Using Optimal Experiment Design}
-	\item 
-		\href
-		{hArticlettps://doi.org/10.1016/S0076-5392(08)63235-X} 
-        {Chapter 6 Experiment Design}\cite{goodwin1977experiment}
-	\item 
-		\href
-		{https://doi.org/10.1177\%2F1352458520978648}
-		{Machine and deep learning in MS research are just powerful statistics – No}
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Free writing about AI}
-I chose an evolutionary algorithm which is - i think - also part of machine learning, 
-which is a part of AI. 
-There are many different types of AI. what are the most haeufig sub domains of the AI field? 
-(natural) language processing, image erkennung, and prediction which can be geteilt in 
-classification (discrete) and continuous prediction. 
-These are mainly machine learning algos. other machine learning tasks are EA, PSO,
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{2022-06-19-Free-Writing}
-The problem which presents it self is in principle a search problem.
-A large space of possible combinations of experimental anordnungen presents it self
-and out of these we want to find the optimial parameter combination. 
-The best way with unlimitied resources would be the brute-force approach to try every possibility. 
-But due to limited time this is unfeasable. 
-But a new questions arises: how should the ausmasse of the search space be eingeschraenkt? 
-What are the upper and lower limits and which intervals/step size/grid size should be used. 
-Also even before, we have to answer which dimensions/parameters should we include in the search? 
-Which parameters should we keep constant and at which value? 
-And finally which features should we use to measure the goodness of an experiment?
-
-I tried different methods to answer the first X questions: Latin square and Plackett-Burman design.
-Unfortunately, I was faced with similar questions. How many levels and which end points? 
-latin squares are about orthogonality 
-PB is a factorial experiment desing in contrast to one-fator-at-a-time methods.
-reliability and validity are low due to experiments not replicated
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{things I should try if they work:}
-\begin{itemize}
-    \item GA 
-    \item what is reinforcement learning? 
-    \item PCA
-    \item linear regression
-	\item t-test and anova but on what? 
-    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
-    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
-    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
-\end{itemize}
-
-%    https://en.wikipedia.org/wiki/Design_of_experiments
-%    https://en.wikipedia.org/wiki/The_Design_of_Experiments
-%    https://en.wikipedia.org/wiki/Response_surface_methodology
-%    https://en.wikipedia.org/wiki/Optimal_design
-%    https://sci-hub.st/https://doi.org/10.2307/2332195
-%    https://en.wikipedia.org/wiki/Latin_square
-%    https://en.wikipedia.org/wiki/Outline_of_artificial_intelligence
-%    https://en.wikipedia.org/wiki/Evolutionary_algorithm
-%    https://en.wikipedia.org/wiki/Particle_swarm_optimization
-%    EMMA doesn't allow for reproducibility
-
-\td{
-\url{https://stats.stackexchange.com/questions/5026/what-is-the-difference-between-data-mining-statistics-machine-learning-and-ai}
-In principle both AI and stat use math to get information out of data. 
-AI might use machine learning to create "intelligent" acting (playing a game or driving a  car).
-machine learning tries to predict unseen data points  and statistics is a subfield of maths which tries to get insight into a given data.
-For example, in a statistical model, it is desirable to reduce the number of inputs.
-This allows the statistician to better study how a change in the input variable can be directly affected by the output variable.\cite{gontcharov2019}
-pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
-}
-
-am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
-"ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell" \cite{haertler2014statistisch}
-Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
-Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}
-
-\td{if i want to learn about support vector machine, read chapter 4,7,8 from "Learning from Data" by Cherkassky\cite{cherkassky1998learning} (TUBib 726-1998)}
-
-%$\mathcal{Y}(Y)= E$

### 2022-10-16 Thesis/chapter/06-results-and-discussion.tex
Turing Test
free writing einarbeiten

@@
 \td{talk about the switch of recipe before emma: makes experiments hard/impossible to compare, but more practical and proof that it works weell}
+
+\td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
+
+% https://journals-sagepub-com.uaccess.univie.ac.at/doi/pdf/10.1177/0013164495055004001
+% https://www.researchgate.net/profile/Barbara-Tabachnick/publication/259465542_Experimental_Designs_Using_ANOVA/links/5e6bb05f92851c6ba70085db/Experimental-Designs-Using-ANOVA.pdf
+% https://stats.stackexchange.com/questions/137631/is-it-appropriate-to-do-an-anova-on-a-feature-selected-via-inspecting-pca-result
+% https://link.springer.com/chapter/10.1007/978-3-642-32639-4_15
+
+plot generation against conductivity
+
+comparison of size: 
+see Notes/ga_from_lit_summary.txt 
+what is the minimum of population*generation and what is 10*5
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Learning from Data}
+General experimental procedure from Cherkassky and Mulier\cite{cherkassky1998learning}
+\begin{enumerate}
+	\item State the problem 
+	\item Formulate the hypothesis
+	\item Design the experiment/generate the data
+	\item Collect the data and perform preprocessing
+	\item Estimate the model 
+	\item Interpret the model/draw the conclusions
+\end{enumerate}
+\textbf{1.
+Statement of the Problem} There was no clear statement of the problem.
+Now I would formulate it: "How to produce most insulating layer with least energy?
+How do we define most insulating?" That's why there are two output variables rather than one.
+\textbf{2. Hypothesis Formulation} formulate an unknown dependency and define input and output variables.
+\textbf{3.
+Data Generation and Experiment Design} can be either in control of the modeler (designed experiment) or in an observational setting.
+The data collection can affect the sampling distribution and influence the next steps.
+\textbf{4.
+Collect the Data and Perform Preprocessing} here outliers are detected and data preprocessing/encoding/feature selection.
+Scaling by standard deviation might be a good idea, but independent scaling of variables can lead to suboptimal representation for the learning task.
+Feature selection: A small number of informative features make the task of estimating dependencies easier.
+\textbf{5. Model Estimation} The main goal is to construct a model for accurate prediction of future outputs
+\textbf{6.
+Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete.
+In classical statistics such as linearly parametrized function will suit both requirements.
+More complex and flexible models might lead to better estimates with less interpretability.
+Identifying the most important input variables.
+\cite{cherkassky1998learning}
+
+There are not only \textbf{x}(input) and y(output) variables, but also \textbf{z}(uncontrolled/unobserved input variables).
+Issues of methods for learning from data: 
+\begin{itemize}
+	\item How to incorporate a priori assumptions into learning? 
+	\item How to measure model complexity (i.e. flexibility to fit the training data)?
+	\item How to find a optimal balance between the data and a priori knowledge? 
+\end{itemize}
+\cite{cherkassky1998learning}
+
+"Learning is the process of estimating an unkown (input,output) dependency of structure of a system using a limit number of observations."\cite{cherkassky1998learning}
+
+The process informal part of selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} (page 25)
+
+"Do not attempt to solve a specified problem by indirectly solving a harder general problem as an intermediate step."\cite{cherkassky1998learning}(p33)
+
+"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)
+
+Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
+Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps.
+
+Any learning process requires the following(p40): 
+\begin{itemize}
+	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
+	\item A priori knowledge to impose contrains
+	\item An inductive principle (what needs to be done)
+		\begin{itemize}
+			\item penalizeation (regularization) inductive principle
+			\item early stopping rules (with ANN, difficult to control and interpret)
+			\item structural risk minimization (SRM) (order according to complexity)
+			\item Bayesian Inference (add subjectivity to learning machine)
+			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
+		\end{itemize}
+	\item A learning method (how does it need to be done,implementation)
+\end{itemize}
+\cite{cherkassky1998learning}
+
+\textbf{Curse and Complexity of Dimensionality}
+goal is to estimate function with finite samples, so it's always inaccurate (biased). 
+meaning full estimate only possible with high sampling density, which is difficult for high dimensional functions.
+\begin{enumerate}
+	\item Sample sizes yielding the same density increse exponentially with dimension.
+	\item A large radius is needed to enclose a fraction of the data points in a high-dimensional space.
+	\item Almost every point is closer to an edge than to another point.
+	\item Almost every point  is an outlier in its own projection.
+\end{enumerate}
+\textbf{Other statistics}
+\begin{itemize}
+    \item f-test (include to ANOVA \url{https://quantifyinghealth.com/f-statistic-in-linear-regression/})
+    \item p-value: Is the probability that a data point is observed under the null hypothesis. A small value argues against the null hypothesis. 
+    \item t-test: will tell you if a variable is statistically significant. 
+    \item f-test: will tell you if a group of variables is jointly significant
+    \item T-test (signal-noise-ratio \href{https://statisticsbyjim.com/hypothesis-testing/t-tests-1-sample-2-sample-paired-t-tests/}{(click here)}): if variable are stat. significant; 
+    \item F-test (ratio of variances \href{https://statisticsbyjim.com/anova/f-tests-anova/}{click here}): if group of vars stat.
+sig \url{https://quantifyinghealth.com/f-statistic-in-linear-regression/}
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{things I should try if they work:}
+\begin{itemize}
+    \item GA 
+    \item what is reinforcement learning? 
+    \item PCA
+    \item linear regression
+	\item t-test and anova but on what? 
+    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
+    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
+    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
+\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
+"ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell" \cite{haertler2014statistisch}
+Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
+Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-10-17 Code/Statistics/stat.R
R earth/mars

@@ -5,12 +5,31 @@ str(dat)
 boxplot(dat$G)
 boxplot(dat$G ~ dat$TCal )
 boxplot(dat$G ~ dat$TCal, xlab="Calcination Temp [C]", ylab="Resistance") 
-library("vioplot") 
-library("ggplot2")
+#library("vioplot") 
+#library("ggplot2")
 mod<-lm(dat$G ~ dat$TCal)
 plot(dat$G ~ dat$TCal)
 
+# https://www.rdocumentation.org/packages/dplyr/versions/1.0.10
+d.all <- dat %>% select ( ! avg1.G.:avg2.G.) 
+x.all <- d.all %>% select(conc:TCal)
+y.all <- d.all %>% select( G:phd)
+mars.all <- earth ( x.all, y.all)
+format(mars.all)
+
+d.emma <- d.all %>% filter ( enr != 0 ) 
+x.emma <- d.emma %>% select(conc:TCal)
+y.emma <- d.emma %>% select( G:phd)
+mars.emma <- earth ( x.emma, y.emma)
+format(mars.emma)
+
+d.hot <- d.all %>% filter ( TCal != 300 ) 
+x.hot <- d.hot %>% select(conc:TCal)
+y.hot <- d.hot %>% select( G:phd)
+mars.hot <- earth ( x.hot, y.hot)
+format(mars.hot)
+
 # TODO 
-# small data set 
-# fit with earth 
 # plot earth fit
+# plot a curve
+# curve((x-1)/(x^2),from=0, to=20,ylab="y")

### 2022-10-17 Thesis/chapter/03-theoretical-background.tex
theory draft finished

@@
 Sputtering is the processes of highly energetic ions hitting a surface and atoms or molecules being expelled. 
-This is called a physical vapor deposition (PVD) technique. 
-PVD can be divided into activation by thermal energy and activation by energetic particle bombardment. 
+This is called a \gls{pvd} technique in contrast to chemical vapor deposition. 
+\Gls{pvd} can be divided into activation by thermal energy and activation by energetic particle bombardment. 
 Sputtering is of the latter, which 
@@
 %\td{what can it be used for?}\\
-Sputtering evolved from being a curious experiment in the middle of the 20th century to having various applications in research and engineering.
-Use cases vary from thin films depositions for \gls{pv}, for electrical circuits or for storage media such as CDs and DVDs 
+Sputtering evolved from being a curious experiment in the middle of the 20th century to 
+having various applications in research and engineering.
+Use cases vary from thin films depositions for \gls{pv}, 
+for electrical circuits or for storage media such as CDs and DVDs 
 over sputter cleaning and etching to analysis.
-Advantages of 
-sputtered thin films include good adhesion to the substrate and good step coverage\cite{Swann1988}.
+Advantages of sputtered thin films include good adhesion to the substrate 
+and good step coverage\cite{Swann1988}.
 
 \begin{figure}[htb]
-	\includegraphics[width=\textwidth]{./Pics/sputter0.png}
-    \caption{Propagation of energy in a dense cascade. Left graph: "Primary" shockwave. Right graph: "Thermal" pulse or "secondary" shockwave. Figure taken from Sigmund 1987\cite{sigmund1987}}
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \includegraphics[width=\textwidth]{./Pics/sputter1.png}
+        \caption{}
+        \label{fig:sputter0}
+    \end{subfigure}
+    \hspace{1cm}
+    \begin{subfigure}[t]{.3\textwidth}
+        \includegraphics[width=\textwidth]{./Pics/sputter2.png}
+        \caption{}
+        \label{fig:sputter1}
+    \end{subfigure}
+%    \caption{Propagation of energy in a dense cascade. Left graph: "Primary" shockwave. Right graph: "Thermal" pulse or "secondary" shockwave. Figure taken from Sigmund 1987\cite{sigmund1969}}
+    \caption{Schematic representation of the creation of sputter particles during sputter deposition. 
+    (a) creation of ions in the chamber: 
+        the top rectangle depicts the source/cathode/target, 
+        the bottom rectangle the anode/substrate holder and 
+        the lower rectangle the substrate to be sputtered. 
+    (b) example series of collision processes leading to sputtering of atoms: 
+        horizontal line represents the target surface, 
+        the small circle a high energetic ion and 
+        the large circles target particles. 
+    }
 	\label{fig:sputter}
@@
 two parallel electrodes with low pressure gas in between. 
-The target acts as cathode and the substrate (holder) as anode (see figure \ref{fig:sputter}).
+The target acts as anode and the substrate (holder) as cathode (see \td{figure \ref{fig:sputter}}).
 %the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
-The cathode, then, emits electrons which collide with a gas particles (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
-Some gas particles may get ionized by the collision and the gas cations are accelerated to the cathode. 
+The anode, then, emits electrons which collide with a gas particles (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
+Some gas particles may get ionized by the collision and the gas cations are accelerated to the anode. 
 If a cation has enough energy it will bump off one or more atoms or molecules from the surface. 
-This happens by a cascade of momentum transfers, which can reach the surface again (see fig \td{from \cite{sigmund1987}}). 
+This happens by a cascade of momentum transfers, which can reach the surface again (see figure \ref{fig:sputter}). 
 If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
-This sputtered particle travels unaffected by the electrical field perpendicular to the surface towards the substrate and condenses with other particles to form a layer.
+This neutral sputtered particle travels unaffected by the electrical field perpendicular to the surface towards the substrate and condenses with other particles to form a layer.
 The pressure should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand 
@@
 
-A magnetron can be placed behind the cathode (target) in order to trap ejected electrons close to the source. 
-This prevents high energy electrons from reaching the target and undoing the deposited layer and this also increases the probability of an electron colliding with an argon atom and ionizing it, increasing the yield.
+A magnetron can be placed behind the cathode (target) in order to trap the plasma close to the source. 
+This lowers the pressure needed to keep the plasma alive. 
+Furthermore, magnetrons prevent high energy electrons from reaching the substrate and 
+undoing the deposited layer and this also increases the probability of an electron 
+colliding with an argon atom and ionizing it, increasing the yield.
 
@@
 evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
-\gls{pso} algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simulta- neously\cite{Villanova2010}.
+\gls{pso} algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simulta- neously\cite{villanova2010function}.
 %
@@
 \subsubsection{EMMA}
-\Gls{emma} and \gls{mars}
+%\Gls{emma} and \gls{mars}
+\Gls{emma} is an implementation of the \gls{pso} in the \texttt{R} programming language. 
+Each time step the dependent variables for all possible input variable combinations
+are predicted with the help of \gls{mars}. 
+\Gls{mars} is a regression method introduced by Friedman's 1991 paper 
+"Multivariate Adaptive Regression Splines"\cite{friedman1991mutlivariate}. 
+The \texttt{CRAN} package which implements \gls{mars} is called \texttt{earth} due to \gls{mars} being trade marked\cite{mars}.
+%by the \texttt{earth} package (available from CRAN). 
+%The name \texttt{earth} was chosen as \texttt{mars} has been trade marked\cite{mars}. 
+Advantages of \gls{mars} are its easy interpretability and flexibility to model non-linearity and of course ability to cope with high dimensional data\cite{villanova2010function}.
 
@@
 \subsubsection{Analysis of Variance} % ANOVA
-\Gls{anova} analyses the means by means of mincing variances.
-\td{at the basis of anova lies the F-test.}
+\Gls{anova} is a statistical test for estimating the influence of multiple categorical independent variables on a dependent numerical variable. 
+At the heart of \gls{anova} lies the F-test. 
+The F-test was ingeniused by Ronald Fisher, an important figure in modern statistics. 
+The F-test uses a ratio of variances to determine if a null-hypothesis (observed difference is due to chance alone) is true. 
+The variance in the enumerator measures the "between-group variability" and the denominator measures the "within-group variability".
+%This ratio is unaltered by adding constants to all observations or scaling errors. 
+This ratio is unaffected by units, scaling errors and constant bias. 
+%
+%\Gls{anova} analyses the means by means of mincing variances.
 %of of the continuous outputs where inputs are categories. 
-The inputs of the model should be categorical and the outputs continuous. 
-The statistical significance of the experiment is determined by a ratio of two variances. 
+%The statistical significance of the experiment is determined by a ratio of two variances. 
 %This ratio is independent of several possible alterations to the experimental observations: 
@@
 %Multiplying all observations by a constant does not alter significance. 
-\Gls{anova} statistical significance results are independent of constant bias and 
-scaling errors as well as the units used in expressing observations. 
-\href{https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions}{(click here)}
-Addiitonal assumptions of \gls{anova}: groups and levels should be independent, 
+%\Gls{anova} statistical significance results are independent of constant bias and 
+%scaling errors as well as the units used in expressing observations. 
+%\href{https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions}{(click here)}
+Additional assumptions of \gls{anova} include: groups and levels should be independent, 
 residual error should follow normal distribution, variance of groups should be equal. 
-\href{https://statsandr.com/blog/anova-in-r/}{(click here)}
+%\href{https://statsandr.com/blog/anova-in-r/}{(click here)}
 
-\textbf{Links}
-\url{https://www.scribbr.com/statistics/anova-in-r/} just make input categorical\\
-\url{https://pypi.org/project/pynova/}\\
+%\textbf{Links}
+%\url{https://www.scribbr.com/statistics/anova-in-r/} just make input categorical\\
+%\url{https://pypi.org/project/pynova/}\\
 

### 2022-10-18 Code/ML/fit2.py
old python code comments

@@ -1,3 +1,4 @@
+#!/usr/bin/env python3
 import math
 import numpy as np 
 #import sklearn.svm  as skl
@@ -8,15 +9,22 @@ from sklearn.pipeline import make_pipeline
 from sklearn.utils import shuffle
 import pandas as pd
 
+# INPUT FILE
 infile="stat2.dat"
+# HEADER
 names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
+# LOAD FILE
 df=pd.read_csv(infile, skiprows=1, delim_whitespace=True, names = names)
+# SHUFFLE DATA
 df= shuffle(df)
+# DEFINE MEAN AVERAGE ERROR 
 def get_MAE(y,ypred):
     return (np.average(np.absolute(y-ypred)))
+    
 def get_sets(df,nr):
     names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
-    df=pd.read_csv(infile, skiprows=1, delim_whitespace=True, names = names)
+#    df=pd.read_csv(infile, skiprows=1, delim_whitespace=True, names = names)
+    # DEFINITIONS
     conc = df.conc
     layr = df.layers
     vDoc = df.vDOC
@@ -28,12 +36,15 @@ def get_sets(df,nr):
     layers = df.layers
     Cal_vel = df.vCal
     
+    # NUMBER OF DATA POINTS
     ndatapoints=len(conc)
     tmin=0                      # train minimum index
     tmax=int(ndatapoints*4/5)
     ttmin = tmax                   # test  minimum index
     ttmax=ndatapoints
 
+    # SPLIT DATA IN TRAINING AND TEST
+    # DEFINE TRAINING SET
     trainx1 = conc[tmin:tmax].to_numpy()
     trainx2 = layr[tmin:tmax].to_numpy()
     trainx3 = vDoc[tmin:tmax].to_numpy()
@@ -45,6 +56,7 @@ def get_sets(df,nr):
     trainy3 = layr[tmin:tmax].to_numpy()
     trainy4 = vCal[tmin:tmax].to_numpy()
 
+    # DEFINE VALIDATION SET
[…]

### 2022-10-18 Code/ML/gridsearch.py

@@ -1,7 +1,7 @@
-import math
+#!/usr/bin/env python3
+
 import numpy as np 
-#import sklearn.svm  as skl
-from sklearn.svm import SVR
+from sklearn.svm import SVR # Epsilon-support Vector Regression
 from sklearn.kernel_ridge import KernelRidge as KRR
 import pandas as pd
 
@@ -82,7 +82,7 @@ for g in gamma:
                     for nr in range(1,n+1):
                         varia=str(d)
                         trainx,testx,trainy,testy = get_sets(df,nr)
-                        ML = SVR(kernel='poly', C=0.1, degree=3, epsilon=0.1)
+#                        ML = SVR(kernel='poly', C=0.1, degree=3, epsilon=0.1)
                         ML = SVR(kernel=k, C=c, degree=d, epsilon=e)
                         ML.fit(trainx,trainy)
                         pred_testy = ML.predict(testx)

### 2022-10-18 Code/ML/pred/fit.py

@@ -66,6 +66,8 @@ e=1
 trainx,trainy=get_sets(df,nr)
 testx=get_x(df2)
 ML = SVR(kernel=k, C=c, degree=d, epsilon=e)
+print(trainx)
+print(trainy)
 ML.fit(trainx,trainy)
 pred = ML.predict(testx)
 print(names[nr+7])

### 2022-10-18 Code/PCA/linreg.py

@@ -11,10 +11,11 @@ X=data[:,6:]
 X_names=names[6:]
 y=data[:,2].reshape(len(data[:,2]),1)
 #y=data[:,3].reshape(len(data[:,3]),1)
-newdata=np.concatenate((X,y),1)
+#newdata=np.concatenate((X,y),1)
 reg = LinearRegression().fit(X,y)
 y_pred = reg.predict(X)
 print("Reg score", reg.score(X,y))
+print("Reg coef", X_names)
 print("Reg coef", reg.coef_)
 #print(X_names)
 #print(y)

### 2022-10-18 Code/Statistics/sub/anova.R
clean prediction analysis code

@@ -1,0 +1,22 @@
+#!/usr/bin/env Rscript
+#
+# USAGE: execute script from within the folder
+
+library("dplyr") 
+
+n="numeric"
+f="factor"
+dat<-read.delim("../db_final.tsv", colClasses=c(n,n,n,n,n,n,f,f,f,f,f,f))
+d.all <- dat %>% select (! avg1.G.:avg2.G.)
+d.emma <- d.all %>% filter ( enr != 0 ) 
+
+G.TCal.all.aov<-aov(G ~ TCal, data = d.all)
+print("ANOVA with all samples")
+summary(G.TCal.all.aov)
+
+G.TCal.emma.aov<-aov(G ~ TCal, data = d.emma)
+print("ANOVA with EMMA samples")
+summary(G.TCal.emma.aov)
+
+
+

### 2022-10-18 Code/Statistics/sub/create_pyvenv.sh

@@ -1,0 +1,10 @@
+#!/usr/bin/env bash
+
+[ -z "$1" ] && echo "Please call this script with an INSTALLATION DIR (e.g. bash $0 ~/Documents/mypyvenv)" && exit 1
+PREFIX="$1"
+
+python3 -m venv $PREFIX 
+source $PREFXI/bin/activate 
+pip install --update pip 
+pip install wheel 
+pip install numpy pandas sklearn dfply

### 2022-10-18 Code/Statistics/sub/linreg.py

@@ -1,0 +1,21 @@
+#!/usr/bin/env python3
+
+import numpy as np 
+import pandas as pd
+from sklearn.linear_model import LinearRegression
+
+infile="../db_final.tsv"
+names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
+df=pd.read_csv(infile, skiprows=1, names = names,delimiter="\t")
+data=np.array(df)
+X=data[:,6:]
+X_names=names[6:]
+y=data[:,2].reshape(len(data[:,2]),1)
+reg = LinearRegression().fit(X,y)
+y_pred = reg.predict(X)
+print("Reg score", reg.score(X,y))
+print("Reg coef", X_names)
+print("Reg coef", reg.coef_)
+exit()
+
+

### 2022-10-18 Code/Statistics/sub/mars.R

@@ -1,0 +1,29 @@
+#!/usr/bin/env Rscript
+#
+# USAGE: execute script from within the folder
+
+library("dplyr")
+library("earth")
+
+dat<-read.delim("../db_final.tsv") 
+d.all <- dat %>% select ( ! avg1.G.:avg2.G.) 
+x.all <- d.all %>% select(conc:TCal)
+y.all <- d.all %>% select( G:phd)
+mars.all <- earth ( x.all, y.all)
+print("MARS model for all samples") 
+format(mars.all)
+
+d.emma <- d.all %>% filter ( enr != 0 ) 
+x.emma <- d.emma %>% select(conc:TCal)
+y.emma <- d.emma %>% select( G:phd)
+mars.emma <- earth ( x.emma, y.emma)
+print("MARS model for EMMA samples")
+format(mars.emma)
+
+d.hot <- d.all %>% filter ( TCal != 300 ) 
+x.hot <- d.hot %>% select(conc:TCal)
+y.hot <- d.hot %>% select( G:phd)
+mars.hot <- earth ( x.hot, y.hot)
+print("MARS model for all samles with TCal>300")
+format(mars.hot)
+

### 2022-10-18 Code/Statistics/sub/ml_gridsearch.py

@@ -1,0 +1,122 @@
+#!/usr/bin/env python3
+
+import numpy as np 
+from simport SVR # Epsilon-support Vector Regression
+from sklearn.kernel_ridge import KernelRidge as KRR
+from sklearn.utils import shuffle
+import pandas as pd
+import dfply
+
+# INPUT FILE
+infile = "../db_final.tsv"
+# HEADER
+names = ["nr", "enr", "G", "phd", "avg1G", "avg2G", "conc", "layr", "vDOC", "TDOC", "vCal", "TCal" ]
+names_short = ["nr", "enr", "G", "phd", "conc", "layr", "vDOC", "TDOC", "vCal", "TCal" ]
+# LOAD FILE
+dat = pd.read_csv(infile, skiprows=1, delim_whitespace=True, names = names)
+# FILTER DATA FRAME
+df = dat >> dfply.drop("avg1G", "avg2G") >> dfply.mask(df.enr > 300)
+
+# GET MEAN AVERAGE ERROR 
+def get_MAE(y,ypred):
+    return (np.average(np.absolute(y-ypred)))
+# K-FOLD CROSS VALIDATION
+def get_sets(df,nr,kfold):
+    # DEFINITIONS
+    conc = df.conc
+    layr = df.layr
+    vDoc = df.vDOC
+    TDoc = df.TDOC
+    vCal = df.vCal
+    TCal = df.TCal
+    G = df.G
+    phd = df.phd
+    
+    # NUMBER OF DATA POINTS
+    ndatapoints=len(conc)
+    tmin=0                      # train minimum index
+    tmax=int(ndatapoints*(kfold-1)/kfold)
+    ttmin = tmax                   # test  minimum index
+    ttmax=ndatapoints
+
+    # SPLIT DATA IN TRAINING AND TEST
+    # DEFINE TRAINING SET
+    trainx1 = conc[tmin:tmax].to_numpy()
+    trainx2 = layr[tmin:tmax].to_numpy()
+    trainx3 = vDoc[tmin:tmax].to_numpy()
+    trainx4 = TDoc[tmin:tmax].to_numpy()
+    trainx5 = vCal[tmin:tmax].to_numpy()
+    trainx6 = TCal[tmin:tmax].to_numpy()
+    trainy1 = G[tmin:tmax].to_numpy()
+    trainy2 = phd[tmin:tmax].to_numpy()
+    trainy3 = layr[tmin:tmax].to_numpy()
[…]

### 2022-10-18 Thesis/chapter/060-results-material.tex
split RESULTS AND DISCUSSION

--- 2021-12-12 Thesis/chapter/results-and-discussion.tex
@@
-\td{base/best sample was somewhot 150, 5 layers 3F 2K/min 400C} what was the best result?
-\td{
-double calcination (2x400C) was tried instead of pyrolization (4x200 then 400C),p49
-so higher concentration of zro2 leads to less stable solution
-5F ca 100min
-4F ca 140min
-3F ca 420min (7h)
-}
-\td{if i would plan the optimisation again, I would take less input variables (fokus on 
-conc,vdoc and tdoc or even only vdoc and tdoc) which may or may not have multiple maxima.}
-\td{adding a extra variable to optimize was to optimistic and ich hab mir damit eindeutig 
-(im nachhinein) steine in den Weg gelegt.}
-\td{instead of changing the stabilisation agent before optimisation, could change after pso}
-\td{varied doctor blading velocity: 10, 5, 1, 0.5, 0.2, 0.1. Slower less layer}
-\todo{Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
-The space seems to be too big for the small sample size.
-Look at relation of space size and sample size here and in Hu2016.
-\td{p68 iPrOH to milky solution and solution becomes clear!!!! checked how much 
-is needed. 5F solution milky over night ~2ml, added 1ml IPO and clear.}
-\td{extra PB-design with conc(2-4), layers(6-8), tcal(430-470), tvel(4-6),
-vdoc(0.5-2), tdoc(40-60). low vdoc very homogenuous but actually nearly no 
-deposition because miniscus is pulling liquid off the substrate.}
-\td{IPO influence on "stability" p74: 600ul IPO makes clear, 4000 ul BuOH not clear with 
-same base solution (1ml of 4F), added extra 400ul to BuOH sol and after 5min clear. 
-of 1:5 is unacceptable Dilution }
-21.8 (1F) from 15.02. 13:30 bis 
-26.3 (1ml iPO to ca2ml of 5f) from 16.02. 16:30 bis 18.02.++
-18.02 4F in 80min milky
-      2F in ca 24h (stabilization AcOH)
-\td{In example of documentation 2 input variables and 1-2 responses initial population=10
-, subsequent population=5, but 10 iterations. Clearly more input varibles and less 
-iterations (as in actual experiments) lead to suboptimal results.
-When plotting input vars  against the response variables, no trend
-The exploration-vs-exploitation parameters of the model were also not set accordingly.}
-see \href{https://search.r-project.org/CRAN/refmans/emma/html/emma.html}{source}
-
-Would be easier to fit with single factor at a time variation or latin hyper cuber?
-Would it also be easier for PSO or ML to find fitting function?
-Every output var is independent of each other, so $v_{cal}$ can act as test
-
-plot predictions from EMMA and ML.
-the data has a lot of error, but because the production process takes so long nad the limited time and the chosen optimisation method, the experiments weren't weiderholt
-how much variance is in data?
-
-The most time consuming part was definitively the prelaminary studies.
-this time could have been verkürzt by testing a wide array of diverse recipes from the literature
-
-The data is spread across the datenraum, such that it is not trivial to (1) find the variable with the most variance and (2) to fit in order to understand to impact of noise on the data. 
-Dimension reduction bietet sich stark an bei solcher Datenlage. 
-Welche methode funktioniert bei relativ vielen variablen, wenig datenpunkten und Noise. 
-Am besten waere feature extraction (variable x1 hat am meisten einfluss. ginge auch wenn man bei pca den einfluss von verschiedenen
-
-heating rate was one of the dependent variables with the intention of minimizing the variable. 
-It can also be used as test to see how well the GA performes
-It doesn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
-Overall there were too many variables involved for such a small dataset
-
-first recipe tried to improve to achieve more restisting layer. by pH value, surface 
-tensionand solution ratios (only 10\% change because it was assumed, that the recipe is 
-good and should be improved, but the recipe should be altered thoroughly.
-two layers were also tried but didn't even pass the visual examination/test/inspection. 
-A curst was produced. 
-At this point in time everything was doctor bladed by hand. The hight was varied (with tape).
-When the switch to the erichsen was made. The height was kept constant in order to keep 
-the variables to optimize ueberschuabar, but could have been even less variables.
-If the movement was to slow the resluting  layer would be very inhomogenuous, thus the
-velocity wasn't varied.
-
-aquatic vs buthanolic
-aquatic immidiately milky
-
-\td{p75 tested various vDOC (10,15,20) with TDOC (40,60,70,80) variations with only visual 
-inspection of evaporation process. Ideally solution evaporate shortly after DB but not 
-before} 
-n-BuOH has boiling point of ca 117C 
-\href{https://pubchem.ncbi.nlm.nih.gov/compound/1-butanol#section=Boiling-Point}{source}
-\td{p74 146,150,151,152,153,154,156,157,158,160,161,186,187,188,190,194,195,198 
-all sputtered with Ag silver on 19.02.2021.}
-EMMA was finished on 23.02.2021
-first experiments generated, but trashed because 1F solution neglected, contraints 
-tightened
-p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation
-look at visualisation in code/pca/ folder and maybe use sort -n 3 
-which values were actually used in EMMA and how were they calculated
-from 145 to 160 what was changed, large increase of G
-small better!!!
-p82 test to what extend AcOH can be replaced with iPOH
-192 was first with IPOH
-use Kernel ridge regression, in PSO the distance of response variables is 
-preparation before measuring the i-v: removing layer by scratching in order to to the 
-steel subtrate. measure resistance if very low (around 10-1) apply paste and let dry
-why different output with ptyhon 3.6 (work laptop) and 3.8 personal
-discussion: 
-why is IPO satbilizing? 
-what are reasons for instability? 
-IV aufbau p 103 
-TODO: check which software versions
-check if output of 
-check if outputs provided by all-stat.sh is same as in R  (p 100)
-look at last pages of notebook
-\td{maybe the observable/sumofsquareddistanceoflogofconductance is not a good metric.
-I should have a look at the raw data. maybe try to verarbeiten different and then fit 
-with KRR or SVM, is phd a sigmoid function? }
-
-\td{for 1F c(Zr) = 44.6 mmol/L
-if n is number of samples, and p is number of input variables, then n >> p 
-In this case n\~50 and p\~6 which give n/p=8+1/3
-in EMMA documentation example n=55and p=1-2, n/p=55-22.5
-plot x vs G and hold all other vars const
-write script to do that}
-
-\todo{make sample time line with ipo vs acoh, al vs ag, hg vs doc, ...}
-
-\td{
-acceptable layer was produced by buthanolic solution, but very unstable (short lived) how long? p41 
-extra AcOH stabilzed but needed so much that dilution too large...
-The stirring time was untersucht, but not much difference so shortest was used because 
-short time can produces faster and the resulting solution is longer stable 
-(after finishing mixing)
-10 layers were tried of short stiring and gave good results? samples 130,131,134,135 (p43)
-}
-
-%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer.
-resistance of steel is neglectable.
-In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold.
-if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{XRD}
-
 \begin{figure}
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{SEM}

### 2022-10-18 Thesis/chapter/061-results-emma.tex
split RESULTS AND DISCUSSION

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{EMMA}
\todo{make figure with G over time}
\begin{itemize}
    \item DOE (only experiment planing)
    \item EMMA/MARS (influence of TCal) \texttt{Code/Statistics/sub/mars.R}
    \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
    \item grid search 
    \item KRR (???)
    \item SVM (???)
\end{itemize}

### 2022-10-18 Thesis/chapter/06-results-and-discussion.tex
split RESULTS AND DISCUSSION
split finish

--- 2022-08-26 Thesis/chapter/06-results-and-discussion.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{XRD}
-\begin{figure}
-	\centering
-	\includegraphics[width=\picwidth]{Pics/xrd.png}
-	\caption{XRD spectra}
-	\label{fig:xrd}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{SEM}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{V-I and PSO//Optimization}
-\td{ideal objective is to create response surface approximation}\\
-\td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}\\
-\td{too much data as input, dimensionality reduction (PCA) and optimization}\\
-\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}
-\td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
-The primary goal of a screening experiment is to identify the active factors. 
-A secondary goal is to provide a simple model that captures the essential features of the 
-relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}
-
-\td{show results between 1ml acoh (199), acoh+ipo 1:1 (201) and ipo (192). Show graph of the three vs log pondus G and pinhole density and maybe distribution of single point measurements? 
-\texttt{set boxwidth 2; set xtics 5; p "stat.dat" u 1:3 with boxes} 
-}
-
-\td{base/best sample was somewhot 150, 5 layers 3F 2K/min 400C} what was the best result?
-\td{
-double calcination (2x400C) was tried instead of pyrolization (4x200 then 400C),p49
-so higher concentration of zro2 leads to less stable solution
-5F ca 100min
-4F ca 140min
-3F ca 420min (7h)
-}
-\td{if i would plan the optimisation again, I would take less input variables (fokus on 
-conc,vdoc and tdoc or even only vdoc and tdoc) which may or may not have multiple maxima.}
-\td{adding a extra variable to optimize was to optimistic and ich hab mir damit eindeutig 
-(im nachhinein) steine in den Weg gelegt.}
-\td{instead of changing the stabilisation agent before optimisation, could change after pso}
-\td{varied doctor blading velocity: 10, 5, 1, 0.5, 0.2, 0.1. Slower less layer}
-\todo{Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
-The space seems to be too big for the small sample size.
-Look at relation of space size and sample size here and in Hu2016.
-\td{p68 iPrOH to milky solution and solution becomes clear!!!! checked how much 
-is needed. 5F solution milky over night ~2ml, added 1ml IPO and clear.}
-\td{extra PB-design with conc(2-4), layers(6-8), tcal(430-470), tvel(4-6),
-vdoc(0.5-2), tdoc(40-60). low vdoc very homogenuous but actually nearly no 
-deposition because miniscus is pulling liquid off the substrate.}
-\td{IPO influence on "stability" p74: 600ul IPO makes clear, 4000 ul BuOH not clear with 
-same base solution (1ml of 4F), added extra 400ul to BuOH sol and after 5min clear. 
-of 1:5 is unacceptable Dilution }
-21.8 (1F) from 15.02. 13:30 bis 
-26.3 (1ml iPO to ca2ml of 5f) from 16.02. 16:30 bis 18.02.++
-18.02 4F in 80min milky
-      2F in ca 24h (stabilization AcOH)
-\td{In example of documentation 2 input variables and 1-2 responses initial population=10
-, subsequent population=5, but 10 iterations. Clearly more input varibles and less 
-iterations (as in actual experiments) lead to suboptimal results.
-When plotting input vars  against the response variables, no trend
-The exploration-vs-exploitation parameters of the model were also not set accordingly.}
-see \href{https://search.r-project.org/CRAN/refmans/emma/html/emma.html}{source}
-
-Would be easier to fit with single factor at a time variation or latin hyper cuber?
-Would it also be easier for PSO or ML to find fitting function?
-Every output var is independent of each other, so $v_{cal}$ can act as test
-
-plot predictions from EMMA and ML.
-the data has a lot of error, but because the production process takes so long nad the limited time and the chosen optimisation method, the experiments weren't weiderholt
-how much variance is in data?
-
-The most time consuming part was definitively the prelaminary studies.
-this time could have been verkürzt by testing a wide array of diverse recipes from the literature
-
-The data is spread across the datenraum, such that it is not trivial to (1) find the variable with the most variance and (2) to fit in order to understand to impact of noise on the data. 
-Dimension reduction bietet sich stark an bei solcher Datenlage. 
-Welche methode funktioniert bei relativ vielen variablen, wenig datenpunkten und Noise. 
-Am besten waere feature extraction (variable x1 hat am meisten einfluss. ginge auch wenn man bei pca den einfluss von verschiedenen
-
+\subsection{emma and Analysis}
+\begin{itemize}
+    \item what was the best result? 
+    \item discuss layers: less layers are better in prediction of? 
+    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
 heating rate was one of the dependent variables with the intention of minimizing the variable. 
-It can also be used as test to see how well the GA performes
+It can also be used as test to see how well the EMMA performes (or rather, more precisely MARS)
 It doesn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
 Overall there were too many variables involved for such a small dataset
+    \item plot G vs nr or boxplot (see also \texttt{/Code/PCA/overview.gp} maybe sort -k3) 
+    \item which values were actually used in EMMA and how were they calculated?
+        G, phd, vCal and layers
+    \item plot generation against conductivity
+\end{itemize}
 
-first recipe tried to improve to achieve more restisting layer. by pH value, surface 
-tensionand solution ratios (only 10\% change because it was assumed, that the recipe is 
-good and should be improved, but the recipe should be altered thoroughly.
-two layers were also tried but didn't even pass the visual examination/test/inspection. 
-A curst was produced. 
-At this point in time everything was doctor bladed by hand. The hight was varied (with tape).
-When the switch to the erichsen was made. The height was kept constant in order to keep 
-the variables to optimize ueberschuabar, but could have been even less variables.
-If the movement was to slow the resluting  layer would be very inhomogenuous, thus the
-velocity wasn't varied.
-
-aquatic vs buthanolic
-aquatic immidiately milky
-
-\td{p75 tested various vDOC (10,15,20) with TDOC (40,60,70,80) variations with only visual 
-inspection of evaporation process. Ideally solution evaporate shortly after DB but not 
-before} 
-n-BuOH has boiling point of ca 117C 
-\href{https://pubchem.ncbi.nlm.nih.gov/compound/1-butanol#section=Boiling-Point}{source}
-\td{p74 146,150,151,152,153,154,156,157,158,160,161,186,187,188,190,194,195,198 
-all sputtered with Ag silver on 19.02.2021.}
-EMMA was finished on 23.02.2021
-first experiments generated, but trashed because 1F solution neglected, contraints 
-tightened
-p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation
-look at visualisation in code/pca/ folder and maybe use sort -n 3 
-which values were actually used in EMMA and how were they calculated
-from 145 to 160 what was changed, large increase of G
-small better!!!
-p82 test to what extend AcOH can be replaced with iPOH
-192 was first with IPOH
-use Kernel ridge regression, in PSO the distance of response variables is 
-preparation before measuring the i-v: removing layer by scratching in order to to the 
-steel subtrate. measure resistance if very low (around 10-1) apply paste and let dry
-why different output with ptyhon 3.6 (work laptop) and 3.8 personal
-discussion: 
-why is IPO satbilizing? 
-what are reasons for instability? 
-IV aufbau p 103 
-TODO: check which software versions
-check if output of 
-check if outputs provided by all-stat.sh is same as in R  (p 100)
-look at last pages of notebook
-\td{maybe the observable/sumofsquareddistanceoflogofconductance is not a good metric.
-I should have a look at the raw data. maybe try to verarbeiten different and then fit 
-with KRR or SVM, is phd a sigmoid function? }
-
-\td{for 1F c(Zr) = 44.6 mmol/L
-if n is number of samples, and p is number of input variables, then n >> p 
-In this case n\~50 and p\~6 which give n/p=8+1/3
-in EMMA documentation example n=55and p=1-2, n/p=55-22.5
-plot x vs G and hold all other vars const
-write script to do that}
-
-\todo{make sample time line with ipo vs acoh, al vs ag, hg vs doc, ...}
-
-\td{
-acceptable layer was produced by buthanolic solution, but very unstable (short lived) how long? p41 
-extra AcOH stabilzed but needed so much that dilution too large...
-The stirring time was untersucht, but not much difference so shortest was used because 
-short time can produces faster and the resulting solution is longer stable 
-(after finishing mixing)
-10 layers were tried of short stiring and gave good results? samples 130,131,134,135 (p43)
-}
-
-\td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, 
-could have been verhindert durch lesen the docu and more papers more thoughoughly. 
-Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}
-%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer.
-resistance of steel is neglectable.
-In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold.
-if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
-\td{I wanted to exhaust the possibilities of EA (not having enough data).
-i should have rather einengen the search raum as much as possible (spreading the search room too much) and then do optimisation: fix layer count to 3 fix conc to 3F and fix calc temp and rate (or only use two extreme values)}
-
-\td{I wanted to let the algorithm show what I already knew instead of letting my a priori knowledge constrain the model before starting.}
-
-\subsection{DOE}
-factorial design (classical \gls{doe} is more robust at feature extraction for error laden data \cite{giunta2003overview}
-
-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest.
-Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2007
-but on the other hand 
-If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
+and cite something pro forma \cite{ncbi1butanol}

### 2022-10-18 Thesis/chapter/060-results-material.tex
split finish

@@
 \subsection{SEM}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Material Scientific}
+\subsubsection{First recipe} 
+alteration of pH etc no improvement
+
+\subsubsection{Stability of the Solution}
+\begin{itemize}
+    \item compare AcOH vs AcOH+IPO 1:1 vs IPO (via boxplot) also G and phd? 
+    \item p68 solution became clear after being milky 
+    \item p74 
+    \item why does IPO stabilize? 
+    \item what is the reason for instability? 
+    \item why does increased Zr conc decrease stability
+    \item initial stirring time no influence on stability (and resulting layer?)
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Material}
+\td{show results between 1ml acoh (199), acoh+ipo 1:1 (201) and ipo (192). Show graph of the three vs log pondus G and pinhole density and maybe distribution of single point measurements?}
+\td{p68 iPrOH to milky solution and solution becomes clear!!!! checked how much 
+is needed. 5F solution milky over night ~2ml, added 1ml IPO and clear.}
+\td{instead of changing the stabilisation agent before optimisation, could change after pso, was vor und nachteile?}
+\td{
+so higher concentration of zro2 leads to less stable solution
+5F ca 100min
+4F ca 140min
+3F ca 420min (7h)
+}
+- aquatic vs buthanolic: aquatic immidiately milky
+\texttt{set boxwidth 2; set xtics 5; p "stat.dat" u 1:3 with boxes} 
+\begin{itemize}
+    \item double calcination (2x400C) was tried instead of pyrolization (4x200 then 400C),p49
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{V-I and preoptimization}
+\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}
+\td{varied doctor blading velocity: 10, 5, 1, 0.5, 0.2, 0.1. Slower less layer}
+\todo{Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
+\td{extra PB-design with conc(2-4), layers(6-8), tcal(430-470), tvel(4-6),
+vdoc(0.5-2), tdoc(40-60). low vdoc very homogenuous but actually nearly no 
+deposition because miniscus is pulling liquid off the substrate.}
+\td{IPO influence on "stability" p74: 600ul IPO makes clear, 4000 ul BuOH not clear with 
+same base solution (1ml of 4F), added extra 400ul to BuOH sol and after 5min clear. 
+of 1:5 is unacceptable Dilution }
+- 21.8 (1F) from 15.02. 13:30 bis 
+26.3 (1ml iPO to ca2ml of 5f) from 16.02. 16:30 bis 18.02.++
+18.02 4F in 80min milky
+      2F in ca 24h (stabilization AcOH)
+- first recipe tried to improve to achieve more restisting layer. by pH value, surface 
+tensionand solution ratios (only 10\% change because it was assumed, that the recipe is 
+good and should be improved, but the recipe should be altered thoroughly.
+two layers were also tried but didn't even pass the visual examination/test/inspection. 
+A curst was produced. 
+- At this point in time everything was doctor bladed by hand. The hight was varied (with tape).
+When the switch to the erichsen was made. The height was kept constant in order to keep 
+the variables to optimize ueberschuabar, but could have been even less variables.
+If the movement was to slow the resluting  layer would be very inhomogenuous, thus the
+velocity wasn't varied.
+\td{p75 tested various vDOC (10,15,20) with TDOC (40,60,70,80) variations with only visual 
+inspection of evaporation process. Ideally solution evaporate shortly after DB but not 
+before} 
+n-BuOH has boiling point of ca 117C\td{\cite{ncbi1butanol} look at source}
+- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation
+- first experiments generated, but trashed because 1F solution neglected, contraints tightened
+- p82 test to what extend AcOH can be replaced with iPOH
+- 192 was first with IPOH
+- why is IPO satbilizing? what are reasons for instability? 
+\td{
+acceptable layer was produced by buthanolic solution, but very unstable (short lived) how long? p41 
+extra AcOH stabilzed but needed so much that dilution too large...
+The stirring time was untersucht, but not much difference so shortest was used because 
+short time can produces faster and the resulting solution is longer stable 
+(after finishing mixing)
+10 layers were tried of short stiring and gave good results? samples 130,131,134,135 (p43)
+}
+- \td{talk about the switch of recipe before emma: makes experiments hard/impossible to compare, but more practical and proof that it works weell}

### 2022-10-18 Thesis/chapter/062-discussion.tex
split finish

\td{ideal objective is to create response surface approximation}\\
\td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}\\
\td{too much data as input, dimensionality reduction (PCA) and optimization}\\
\td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
{The primary goal of a screening experiment is to identify the active factors.
A secondary goal is to provide a simple model that captures the essential features of the 
relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{diskussion and outlook}
\td{if i would plan the optimisation again, I would take less input variables (fokus on 
conc,vdoc and tdoc or even only vdoc and tdoc) which may or may not have multiple maxima.}
\td{adding a extra variable to optimize was to optimistic and ich hab mir damit eindeutig 
(im nachhinein) steine in den Weg gelegt.}
The space seems to be too big for the small sample size.
Look at relation of space size and sample size here and in Hu2016.
\td{In example of documentation 2 input variables and 1-2 responses initial population=10
, subsequent population=5, but 10 iterations. Clearly more input varibles and less 
iterations (as in actual experiments) lead to suboptimal results.
When plotting input vars  against the response variables, no trend
- The exploration-vs-exploitation parameters of the model were also not set accordingly.}
see \href{https://search.r-project.org/CRAN/refmans/emma/html/emma.html}{source}
Would be easier to fit with single factor at a time variation or latin hyper cuber? 
with same search-space to actual-data ratio
- Would it also be easier for MARS or ML to find fitting function?
plot predictions from EMMA and ML. or rather compare MAE
- the data has a lot of error, but because the production process takes so long and the 
limited time and the chosen optimisation method, the experiments weren't weiderholt
how much variance is in data? 
- The most time consuming part was definitively the prelaminary studies.
this time could have been verkürzt by testing a wide array of diverse recipes from the literature
- The data is spread across the datenraum, such that it is not trivial to 
(1) find the variable with the most variance and 
(2) to fit in order to understand to impact of noise on the data. 
- Dimension reduction bietet sich stark an bei solcher Datenlage. 
Welche methode funktioniert bei relativ vielen variablen, wenig datenpunkten und Noise. 
Am besten waere feature extraction (variable x1 hat am meisten einfluss) 
ginge auch wenn man bei pca den einfluss von verschiedenen 
I stand in front of this problem where the solution is to not use as many indep vars von vorne herein. 
- EMMA was finished on 23.02.2021 (make timeline?)
- TODO: check which software versions
-\td{for 1F c(Zr) = 44.6 mmol/L
if n is number of samples, and p is number of input variables, then n >> p 
In this case n\~50 and p\~6 which give n/p=8+1/3
in EMMA documentation example n=55and p=1-2, n/p=55-22.5
plot x vs G and hold all other vars const
write script to do that}
\todo{make sample time line with ipo vs acoh, al vs ag, hg vs doc, ...}
\td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, 
could have been verhindert durch lesen the docu and more papers more thoughoughly. 
Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
- \td{I wanted to exhaust the possibilities of EA (not having enough data). i should have rather einengen the search raum as much as possible (spreading the search room too much) and then do optimisation: fix layer count to 3 fix conc to 3F and fix calc temp and rate (or only use two extreme values)}
- \td{I wanted to let the algorithm show what I already knew instead of letting my a priori knowledge constrain the model before starting.}
- factorial design (classical \gls{doe} is more robust at feature extraction for error laden data \cite{giunta2003overview}
-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest. Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2007}
but on the other hand: If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
- let's rule out different input variables: \\
does the heating temperature influence the resistance?  no \\
does the heating velocity influence the resistance?  hardly\\
do conc and layers number influence resistance? linear \\
do db velocity and db temperautre influence resistance? how\\
- somebody very wise (my superviser) once said: we need to able to predict it otherwise it is just an engineering problem \td{(look at mail)}
- "Je grösser nämlich die Anzahl freier Parameter im Modell ist, umso grösser ist der erforderliche Datenumfang und umso ungenauer wir die statistisch gewonnene Aussgae bei gleichem Datenumfang." - Gisela Härtler\cite{haertler2014statistisch}
- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
-comparison of population size: 
\verb|see Notes/ga_from_lit_summarj.txt|
what is the minimum of population*generation and what is 10*5

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Learning from Data}
General experimental procedure from Cherkassky and Mulier\cite{cherkassky1998learning}
\begin{enumerate}
	\item State the problem 
	\item Formulate the hypothesis
	\item Design the experiment/generate the data
	\item Collect the data and perform preprocessing
	\item Estimate the model 
	\item Interpret the model/draw the conclusions
\end{enumerate}
\textbf{1. Statement of the Problem} There was no clear statement of the problem. Now I would formulate it: "How to produce most insulating layer with least energy? How do we define most insulating?" That's why there are two output variables rather than one.
\textbf{2. Hypothesis Formulation} formulate an unknown dependency and define input and output variables.
\textbf{3. Data Generation and Experiment Design} can be either in control of the modeler (designed experiment) or in an observational setting. The data collection can affect the sampling distribution and influence the next steps. 
\textbf{4. Collect the Data and Perform Preprocessing} here outliers are detected and data preprocessing/encoding/feature selection. Scaling by standard deviation might be a good idea, but independent scaling of variables can lead to suboptimal representation for the learning task. Feature selection: A small number of informative features make the task of estimating dependencies easier. 
\textbf{5. Model Estimation} The main goal is to construct a model for accurate prediction of future outputs
\textbf{6. Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete. In classical statistics such as linearly parametrized function will suit both requirements. More complex and flexible models might lead to better estimates with less interpretability. Identifying the most important input variables. \cite{cherkassky1998learning}

There are not only \textbf{x}(input) and y(output) variables, but also \textbf{z}(uncontrolled/unobserved input variables).
Issues of methods for learning from data: 
\begin{itemize}
	\item How to incorporate a priori assumptions into learning? 
	\item How to measure model complexity (i.e. flexibility to fit the training data)?
	\item How to find a optimal balance between the data and a priori knowledge? 
\end{itemize}
\cite{cherkassky1998learning}

"Learning is the process of estimating an unkown (input,output) dependency of structure of a system using a limit number of observations."\cite{cherkassky1998learning}

The process informal part of selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} (page 25)

"Do not attempt to solve a specified problem by indirectly solving a harder general problem as an intermediate step."\cite{cherkassky1998learning}(p33)

"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)

Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps.

Any learning process requires the following(p40): 
\begin{itemize}
	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
	\item A priori knowledge to impose contrains
	\item An inductive principle (what needs to be done)
		\begin{itemize}
			\item penalizeation (regularization) inductive principle
			\item early stopping rules (with ANN, difficult to control and interpret)
			\item structural risk minimization (SRM) (order according to complexity)
			\item Bayesian Inference (add subjectivity to learning machine)
			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
		\end{itemize}
	\item A learning method (how does it need to be done,implementation)
\end{itemize}
\cite{cherkassky1998learning}

\textbf{Curse and Complexity of Dimensionality}
goal is to estimate function with finite samples, so it's always inaccurate (biased). 
meaning full estimate only possible with high sampling density, which is difficult for high dimensional functions.
\begin{enumerate}
	\item Sample sizes yielding the same density increse exponentially with dimension.
	\item A large radius is needed to enclose a fraction of the data points in a high-dimensional space.
	\item Almost every point is closer to an edge than to another point.
	\item Almost every point  is an outlier in its own projection.
\end{enumerate}
\textbf{Other statistics}
\begin{itemize}
    \item f-test (include to ANOVA \url{https://quantifyinghealth.com/f-statistic-in-linear-regression/})
    \item p-value: Is the probability that a data point is observed under the null hypothesis. A small value argues against the null hypothesis. 
    \item t-test: will tell you if a variable is statistically significant. 
    \item f-test: will tell you if a group of variables is jointly significant
    \item T-test (signal-noise-ratio \href{https://statisticsbyjim.com/hypothesis-testing/t-tests-1-sample-2-sample-paired-t-tests/}{(click here)}): if variable are stat. significant; 
    \item F-test (ratio of variances \href{https://statisticsbyjim.com/anova/f-tests-anova/}{click here}): if group of vars stat. sig \url{https://quantifyinghealth.com/f-statistic-in-linear-regression/}
\end{itemize}

am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
"ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell" \cite{haertler2014statistisch}
Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LINKS}
\begin{itemize}
    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-10-19 Thesis/chapter/06-results-and-discussion.tex
R&D: preoptimisation

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{emma and Analysis}
-\begin{itemize}
-    \item what was the best result? 
-    \item discuss layers: less layers are better in prediction of? 
-    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
-heating rate was one of the dependent variables with the intention of minimizing the variable. 
-It can also be used as test to see how well the EMMA performes (or rather, more precisely MARS)
-It doesn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
-Overall there were too many variables involved for such a small dataset
-    \item plot G vs nr or boxplot (see also \texttt{/Code/PCA/overview.gp} maybe sort -k3) 
-    \item which values were actually used in EMMA and how were they calculated?
-        G, phd, vCal and layers
-    \item plot generation against conductivity
-\end{itemize}
-
 and cite something pro forma \cite{ncbi1butanol}
+\input{chapter/060-results-material.tex}
+%\input{chapter/061-results-emma.tex}
+%\input{chapter/062-discussion.tex}

### 2022-10-19 Thesis/chapter/060-results-material.tex
R&D: preoptimisation

@@
 \subsection{SEM}
+\begin{figure}
+    \centering
+    \begin{subfigure}{.4\textwidth}
+        \includegraphics[width=\textwidth]{Pics/sem/071_fto_old_1x.png}
+        \caption{sem1}
+        \label{fig:sem1}
+    \end{subfigure}
+    \begin{subfigure}{.4\textwidth}
+        \includegraphics[width=\textwidth]{Pics/sem/071_fto_old_2x.png}
+        \caption{sem2}
+        \label{fig:sem2}
+    \end{subfigure}
+    \caption{sem}
+    \label{fig:sem}
+\end{figure}
 
@@
 \subsubsection{First recipe} 
-alteration of pH etc no improvement
+As already indicated in the experimental section the recipe adopted from \cite{Anwar2017} didn't produce any \td{good} results. 
+The solution was milky/cloudy and didn't produce homogeneous films. 
+Altering the composition, pH etc. didn't improve the resulting layers.
 
-\subsubsection{Stability of the Solution}
-\begin{itemize}
-    \item compare AcOH vs AcOH+IPO 1:1 vs IPO (via boxplot) also G and phd? 
-    \item p68 solution became clear after being milky 
-    \item p74 
-    \item why does IPO stabilize? 
-    \item what is the reason for instability? 
-    \item why does increased Zr conc decrease stability
-    \item initial stirring time no influence on stability (and resulting layer?)
-\end{itemize}
+The sol-gel recipe optimized by \cite{Hu2016} for \ch{Al2O3} worked splendidly for our use even after (not so) minor changes.
+%An substantial improvement could be achieved by
+The stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
+The stability was inspected visually. 
+As soon as the solution showed initial cloudiness, it was declared as unstable. 
+The regular solution was stable for approximately \td{24h} sealed with Parafilm. 
+A solution with \gls{ipo} as stabilizing agent stayed stable for \td{72h}. 
+As an increase of the \gls{zrpro} concentration decreased the \td{stable time}. 
+%5F ca 100min
+%4F ca 140min
+%3F ca 420min (7h)
+\Gls{ipo} solution allowed to even reuse high concentrated solution, which would otherwise become cloudy under 60 minutes. 
+Multiple question still need to be answered: 
+What causes the cloudiness (as stability increased through sealing probably \ch{H2O} from the air or \ch{O2}) and what's the mechanism? 
+How does \gls{ipo} increase the stability? 
+Does it do so because it "fits" better with the solvent. 
+As the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}. 
+It was even observed that the addition of \td{some drops of} \gls{ipo} to an acetic solution can clear the solution.
+5F acetic solution milky over night 5:1 dilution with \gls{ipo} and clear after one minute of stirring and stayed clear over 5 nights.
+% more details on pages 68ff
+No effect on the solution or the resulting layer was noticed \td{from the initial stirring}
+\todo{Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Material}
-\td{show results between 1ml acoh (199), acoh+ipo 1:1 (201) and ipo (192). Show graph of the three vs log pondus G and pinhole density and maybe distribution of single point measurements?}
-\td{p68 iPrOH to milky solution and solution becomes clear!!!! checked how much 
-is needed. 5F solution milky over night ~2ml, added 1ml IPO and clear.}
-\td{instead of changing the stabilisation agent before optimisation, could change after pso, was vor und nachteile?}
-\td{
-so higher concentration of zro2 leads to less stable solution
-5F ca 100min
-4F ca 140min
-3F ca 420min (7h)
-}
-- aquatic vs buthanolic: aquatic immidiately milky
-\texttt{set boxwidth 2; set xtics 5; p "stat.dat" u 1:3 with boxes} 
-\begin{itemize}
-    \item double calcination (2x400C) was tried instead of pyrolization (4x200 then 400C),p49
-\end{itemize}
+%\td{instead of changing the stabilisation agent before optimisation, could change after pso, was vor und nachteile?}
+after realizing the improved effectiveness of \gls{ipo} for experimentation, 
+it was decided that EMMA will be executed with \gls{ipo} solution.
+\begin{figure}
+    \centering
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/iv-199-acoh.png}
+        \caption{iv acoh} \label{fig:iv-acoh}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/iv-201-acoh-ipo.png}
+        \caption{iv acoh ipo} \label{fig:iv-acoh-ipo}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/iv-192-ipo.png}
+        \caption{ipo} \label{fig:ipo}
+    \end{subfigure}
+    \caption{iv of 6x4F} \label{fig:iv}
+\end{figure}
 
@@
 \subsection{V-I and preoptimization}
-\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}
 \td{varied doctor blading velocity: 10, 5, 1, 0.5, 0.2, 0.1. Slower less layer}
-\todo{Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
 \td{extra PB-design with conc(2-4), layers(6-8), tcal(430-470), tvel(4-6),

### 2022-10-19 Thesis/chapter/061-results-emma.tex
R&D: preoptimisation

@@
 \subsection{EMMA}
-\todo{make figure with G over time}
 \begin{itemize}
+    \item what was the best result? 
+    \item discuss layers: less layers are better in prediction of? 
+    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
+heating rate was one of the dependent variables with the intention of minimizing the variable. 
+It can also be used as test to see how well the EMMA performes (or rather, more precisely MARS)
+It doesn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
+Overall there were too many variables involved for such a small dataset
+    \item plot G vs nr or boxplot (see also \texttt{/Code/PCA/overview.gp} maybe sort -k3) 
+    \item which values were actually used in EMMA and how were they calculated?
+        G, phd, vCal and layers
+    \item plot generation against conductivity
+    \item \todo{make figure with G over time}
     \item DOE (only experiment planing)
@@
 \end{itemize}
+
+and cite something pro forma \cite{ncbi1butanol}
+\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}

### 2022-10-19 Thesis/chapter/060-results-material.tex
rd: material first rough draft

@@
 The solution was milky/cloudy and didn't produce homogeneous films. 
-Altering the composition, pH etc. didn't improve the resulting layers.
+Altering the composition, pH, surfactant etc. didn't improve the resulting layers. 
+%- first recipe tried to improve to achieve more restisting layer.
+by pH value, surface tension and solution ratios (only 10\% change because it was assumed, that the recipe is good and should be improved, but the recipe should be altered thoroughly.
+two layers were also tried but didn't even pass the visual examination/test/inspection.
+A curst was produced.
 
@@
 The regular solution was stable for approximately \td{24h} sealed with Parafilm. 
+%192 was first with IPOH
 A solution with \gls{ipo} as stabilizing agent stayed stable for \td{72h}. 
@@
 %3F ca 420min (7h)
+%extra AcOH stabilzed but needed so much that dilution too large...
+%\td{IPO influence on "stability" p74: 600ul IPO makes clear, 4000 ul BuOH not clear with 
+%same base solution (1ml of 4F), added extra 400ul to BuOH sol and after 5min clear. 
+%of 1:5 is unacceptable Dilution }
+%- 21.8 (1F) from 15.02. 13:30 bis 
+%26.3 (1ml iPO to ca2ml of 5f) from 16.02. 16:30 bis 18.02.++
+%18.02 4F in 80min milky
+%      2F in ca 24h (stabilization AcOH)
+%
+%acceptable layer was produced by buthanolic solution, but very unstable (short lived) how long? p41 
 \Gls{ipo} solution allowed to even reuse high concentrated solution, which would otherwise become cloudy under 60 minutes. 
@@
 \todo{Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
+%The stirring time was untersucht, but not much difference so shortest was used because 
+%short time can produces faster and the resulting solution is longer stable 
+%(after finishing mixing)
 
@@
 \subsection{V-I and preoptimization}
-\td{varied doctor blading velocity: 10, 5, 1, 0.5, 0.2, 0.1. Slower less layer}
-\td{extra PB-design with conc(2-4), layers(6-8), tcal(430-470), tvel(4-6),
-vdoc(0.5-2), tdoc(40-60). low vdoc very homogenuous but actually nearly no 
-deposition because miniscus is pulling liquid off the substrate.}
-\td{IPO influence on "stability" p74: 600ul IPO makes clear, 4000 ul BuOH not clear with 
-same base solution (1ml of 4F), added extra 400ul to BuOH sol and after 5min clear. 
-of 1:5 is unacceptable Dilution }
-- 21.8 (1F) from 15.02. 13:30 bis 
-26.3 (1ml iPO to ca2ml of 5f) from 16.02. 16:30 bis 18.02.++
-18.02 4F in 80min milky
-      2F in ca 24h (stabilization AcOH)
-- first recipe tried to improve to achieve more restisting layer. by pH value, surface 
-tensionand solution ratios (only 10\% change because it was assumed, that the recipe is 
-good and should be improved, but the recipe should be altered thoroughly.
-two layers were also tried but didn't even pass the visual examination/test/inspection. 
-A curst was produced. 
-- At this point in time everything was doctor bladed by hand. The hight was varied (with tape).
-When the switch to the erichsen was made. The height was kept constant in order to keep 
-the variables to optimize ueberschuabar, but could have been even less variables.
-If the movement was to slow the resluting  layer would be very inhomogenuous, thus the
-velocity wasn't varied.
-\td{p75 tested various vDOC (10,15,20) with TDOC (40,60,70,80) variations with only visual 
-inspection of evaporation process. Ideally solution evaporate shortly after DB but not 
-before} 
-n-BuOH has boiling point of ca 117C\td{\cite{ncbi1butanol} look at source}
+The doctor blading velocity (i.e. the velocity with which the blade moves and spreads the sol over the sample) 
+was varied during preoptimization. 
+The slower the \gls{db} velocity the more \td{homogeneously} the solution evaporated. 
+If the \gls{db} was \td{too slow (lt 1 mm/s)} the surface tension pulled solvent over the sample without \td{leaving was zurk/forming a gel.}
+\td{deposition because miniscus is pulling liquid off the substrate.}
+Additionally the temperature while doctor blading affects the resulting layer together with the \gls{db} velocity.
+
+\td{Assumption: Ideally solution evaporate shortly after DB but not before}
+due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
 - p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation
-- first experiments generated, but trashed because 1F solution neglected, contraints tightened
-- p82 test to what extend AcOH can be replaced with iPOH
-- 192 was first with IPOH
-- why is IPO satbilizing? what are reasons for instability? 
-\td{
-acceptable layer was produced by buthanolic solution, but very unstable (short lived) how long? p41 
-extra AcOH stabilzed but needed so much that dilution too large...
-The stirring time was untersucht, but not much difference so shortest was used because 
-short time can produces faster and the resulting solution is longer stable 
-(after finishing mixing)
-10 layers were tried of short stiring and gave good results? samples 130,131,134,135 (p43)
-}
-- \td{talk about the switch of recipe before emma: makes experiments hard/impossible to compare, but more practical and proof that it works weell}
+\begin{figure}
+    \centering
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/log-146-good-10x1F.png}
+        \caption{log} \label{fig:log1}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/log-154-okay-3x4F.png}
+        \caption{log} \label{fig:log2}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
+        \caption{log} \label{fig:log3}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
+        \caption{stat} \label{fig:stat1}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
+        \caption{stat} \label{fig:stat2}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
+        \caption{stat} \label{fig:stat3}
+    \end{subfigure}
+    \caption{maybe remove 146 and make 154 good AND set yrange [E-1:E-14]} \label{fig:sem}
+\end{figure}

### 2022-10-21 Code/Statistics/scripts/anova.R
edit scripts

@@ -10,13 +10,37 @@ dat<-read.delim("../db_final.tsv", colClasses=c(n,n,n,n,n,n,f,f,f,f,f,f))
 d.all <- dat %>% select (! avg1.G.:avg2.G.)
 d.emma <- d.all %>% filter ( enr != 0 ) 
 
+G.TCal.emma.aov<-aov(G ~ TCal, data = d.emma)
+print("ANOVA with EMMA samples: G ~ TCal")
+summary(G.TCal.emma.aov)
+
 G.TCal.all.aov<-aov(G ~ TCal, data = d.all)
-print("ANOVA with all samples")
+print("ANOVA with all samples: G ~ TCal")
 summary(G.TCal.all.aov)
 
-G.TCal.emma.aov<-aov(G ~ TCal, data = d.emma)
-print("ANOVA with EMMA samples")
-summary(G.TCal.emma.aov)
+G.layr.emma.aov<-aov(G ~ layr, data = d.emma)
+print("ANOVA with EMMA samples: G ~ layr")
+summary(G.layr.emma.aov)
+
+G.layr.all.aov<-aov(G ~ layr, data = d.all)
+print("ANOVA with all samples: G ~ layr")
+summary(G.layr.all.aov)
+
+G.TDOC.emma.aov<-aov(G ~ TDOC, data = d.emma)
+print("ANOVA with EMMA samples: G ~ TDOC")
+summary(G.TDOC.emma.aov)
+
+G.TDOC.all.aov<-aov(G ~ TDOC, data = d.all)
+print("ANOVA with all samples: G ~ TDOC")
+summary(G.TDOC.all.aov)
+
+G.TvDOC.emma.aov<-aov(G ~ TDOC:vDOC, data = d.emma)
+print("ANOVA with EMMA samples: G ~ TDOC:vDOC")
+summary(G.TvDOC.emma.aov)
+
+G.TvDOC.all.aov<-aov(G ~ TDOC:vDOC, data = d.all)
+print("ANOVA with all samples: G ~ TDOC:vDOC")
+summary(G.TvDOC.all.aov)
 
 
 

### 2022-10-21 Code/Statistics/scripts/emma.R

@@ -1,0 +1,25 @@
+#!/usr/bin/env Rscript
+#
+# USAGE: execute script from within the folder
+
+library("dplyr")
+load("../../EMMA/t5") 
+source("../../EMMA/inter.R") 
+#for (i in 1:4){
+#    emmacheck(t4,graph=1,eresp=i)
+#}
+#print("Global Best")
+#t5$Gb.arch
+#print("Personal Best")
+##matrix(t5$Pb.arch,nrow=5)
+##t5$xpop[:2] 
+
+x<-t4
+input <- cbind(x$xpop,x$ypop)
+fmla <- as.formula(paste(paste("data.matrix(input[,",ncol(x$xpop)+1,":",ncol(x$xpop)+ncol(x$ypop),"])"),"~", paste(colnames(x$xpop),collapse= "+")))
+mars.mod <- earth(fmla,degree=2,trace=0,minspan=1,data=input,keepxy=TRUE)
+head(x$ypop,1)
+format(mars.mod)
+
+
+

### 2022-10-21 Code/Statistics/scripts/mars.R

@@ -8,22 +8,24 @@ library("earth")
 dat<-read.delim("../db_final.tsv") 
 d.all <- dat %>% select ( ! avg1.G.:avg2.G.) 
 x.all <- d.all %>% select(conc:TCal)
-y.all <- d.all %>% select( G:phd)
-mars.all <- earth ( x.all, y.all)
+#y.all <- d.all %>% select( G:phd)
+#y.all <- d.all %>% mutate(vC6=vCal*60) %>% select(G,phd,layr,vC6)
+y.all <- d.all %>% select(G,phd,layr,vCal)
+mars.all <- earth ( x.all, y.all, degree=2)
 print("MARS model for all samples") 
 format(mars.all)
 
 d.emma <- d.all %>% filter ( enr != 0 ) 
 x.emma <- d.emma %>% select(conc:TCal)
-y.emma <- d.emma %>% select( G:phd)
-mars.emma <- earth ( x.emma, y.emma)
+y.emma <- d.emma %>% mutate(vC6=vCal*60) %>% select(G,phd,layr,vC6)
+mars.emma <- earth ( x.emma, y.emma, degree=2)
 print("MARS model for EMMA samples")
 format(mars.emma)
 
 d.hot <- d.all %>% filter ( TCal != 300 ) 
 x.hot <- d.hot %>% select(conc:TCal)
-y.hot <- d.hot %>% select( G:phd)
-mars.hot <- earth ( x.hot, y.hot)
+y.hot <- d.hot %>% mutate(vC6=vCal*60) %>% select(G,phd,layr,vC6)
+mars.hot <- earth ( x.hot, y.hot, degree=2)
 print("MARS model for all samles with TCal>300")
 format(mars.hot)
 

### 2022-10-21 Thesis/chapter/061-results-emma.tex
start results emma

--- 2022-10-18 Thesis/chapter/061-results-emma.tex
@@
 \subsection{EMMA}
-\todo{make figure with G over time}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{what is best}
+\begin{align}
+%    G    & = -3.7 + 0.18 * TCal +  8.1 * max(0,6-layr)\\
+%    \rho & = -0.78 + 0.0024 * TCal + 0.13 * max(0,6-layr)
+    G &=      -19 + 0.28 * TCal  - 0.022 * layr*TCal  +  0.16 * h(layr-6)*TDOC \\
+    \rho &=  -0.87 + 0.0047 * TCal  - 0.00036 * layr*TCal  +  0.0024 * h(layr-6)*TDOC \\
+    \lambda &=  6.8 - 0.014 * TCal  + 0.0018 * layr*TCal  + 0.0060 * h(layr-6)*TDOC \\
+    v_{cal} &= 29 - 0.052 * TCal  + 0.0011 * layr*TCal  -  0.011 * h(layr-6)*TDOC 
+\end{align}
+what was the best result? For each particle there is best and global best. 
+https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{how did evolve over time?}
+
+\begin{table}[h]
+	\centering
+    \caption{Global best per generation}
+	\label{tab:emma_gen}
+	\begin{tabular}{cccccccc}
+        \hline\hline
+    generation  &enr &conc &layr &vDOC &TDOC &vCal &TCal\\
+        \hline
+     1   &1       &2    &4   &10   &40  &120  &300\\
+     2   &5       &2    &6   &10   &40  &120  &300\\
+     3   &2947    &4    &6   &16   &80 &1080  &300\\
+     4   &2405    &2    &6   &10   &40 &1080  &300\\
+     5   &13      &2   &10   &10   &40  &120  &300\\
+    \hline\hline
+	\end{tabular}
+\end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.6\textwidth]{Pics/stats/G-t.png}
+    \caption{conductivity G [a.u.] against sample number (is this even correct?)}
+    \label{fig:G-t}
+\end{figure}
+
+\td{TODO: check if the sorted correctly? Make generation graph with boxplot }
+    \td{TODO: visualize} how the population moved across the space (with parallel coordinates? or see page 121)
+        \url{https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{how did model selection influence results}
 \begin{itemize}
-    \item DOE (only experiment planing)
-    \item EMMA/MARS (influence of TCal) \texttt{Code/Statistics/sub/mars.R}
+    \item MARS chooses same set from independent variables for predicting all dependent variables. 
+    \item flaws of MARS: all functions are dependent on same indep vars
+    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
+heating rate was one of the dependent variables with the intention of minimizing the variable. 
+It can also be used as test to see how well the EMMA performes (or rather, more precisely MARS)
+It doesn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
+Overall there were too many variables involved for such a small dataset
+        that means that adding dependent variables influences \td{previous variables}
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{analyse data with other methods post optimization}
+\begin{itemize}
     \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}

### 2022-10-21 Thesis/chapter/060-results-material.tex
XRD and SEM text frist draft

@@
 
+In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
+The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
+This wideness is is due to polycristalinity/amorphness of the material which is \td{erwartet due} to the sol-gel creation process.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \centering
-    \begin{subfigure}{.4\textwidth}
-        \includegraphics[width=\textwidth]{Pics/sem/071_fto_old_1x.png}
-        \caption{sem1}
-        \label{fig:sem1}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_1x.png}
+        \caption{71 fto old 1x} \label{fig:sem-old1}
     \end{subfigure}
-    \begin{subfigure}{.4\textwidth}
-        \includegraphics[width=\textwidth]{Pics/sem/071_fto_old_2x.png}
-        \caption{sem2}
-        \label{fig:sem2}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_2x.png}
+        \caption{71 fto old 2x} \label{fig:sem-old2}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
+        \caption{115 fto cs 1x} \label{fig:sem-cs1}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
+        \caption{147 steel ph? 10x} \label{fig:sem-ph}
     \end{subfigure}
@@
 \end{figure}
+
+The \gls{sem} pictures were not easy to take since we were trying to create an insulator 
+and the quality of the picture relies on the conductance of the material's surface. 
+This means that the better the quality of the resulting layer the more tedious it was to get/take a decent SEM image. 
+Figure \ref{fig:sem-old} shows ausschnitte of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
+These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
+Large cracks and inhomogenity were part of (ausmachen) all samples created with the Anwar recipe; 
+also/even after several/multiple/various alteration to the recipe.
+
+Figure \ref{fig:sem-cs1} shows the cross section of a single layers of \gls{zro} on \gls{fto} glass. 
+The large crystalline \td{range} which makes up most of the topper/top part of the image is \gls{fto}. 
+The úbergang to glass is gerade noch so zu sehen. 
+On the lower kante of the \gls{fto} a circa 100nm thick homogeneous layer can be observed, \gls{zro} produced by buthanolic recipe inspired by Hu et al..
+
+Figure \ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic layer on top of a steel substrate. 
+The large unregularity on the bottom left could darstellen a pin hole a (tiny) hole that reaches the substrate. 
+These unregularites are rather the ausnahme. 
+Alternatively, the small, hardly visible  irregularities verstreut across surface could darstellen such pin holes. 
+These - I think - eher only are one layer deep irregularities since they are so haeufig 
+and very little pin holes were observed on similar samples.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{V-I and preoptimization}
-The doctor blading velocity (i.e. the velocity with which the blade moves and spreads the sol over the sample) 
-was varied during preoptimization. 
-The slower the \gls{db} velocity the more \td{homogeneously} the solution evaporated. 
-If the \gls{db} was \td{too slow (lt 1 mm/s)} the surface tension pulled solvent over the sample without \td{leaving was zurk/forming a gel.}
-\td{deposition because miniscus is pulling liquid off the substrate.}
-Additionally the temperature while doctor blading affects the resulting layer together with the \gls{db} velocity.
-
-\td{Assumption: Ideally solution evaporate shortly after DB but not before}
-due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
-- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation
+\subsection{V-I}
 \begin{figure}
@@
     \end{subfigure}
-    \caption{maybe remove 146 and make 154 good AND set yrange [E-1:E-14]} \label{fig:sem}
+    \caption{maybe remove 146 and make 154 good AND set yrange [E-1:E-14]} \label{fig:iv}
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Preoptimization}
+The doctor blading velocity (i.e. the velocity with which the blade moves and spreads the sol over the sample) 
+was varied during preoptimization. 
+The slower the \gls{db} velocity the more \td{homogeneously} the solution evaporated. 
+If the \gls{db} was \td{too slow (lt 1 mm/s)} the surface tension pulled solvent over the sample without \td{leaving was zurk/forming a gel.}
+\td{deposition because miniscus is pulling liquid off the substrate.}
+Additionally the temperature while doctor blading affects the resulting layer together with the \gls{db} velocity.
+
+\td{Assumption: Ideally solution evaporate shortly after DB but not before}
+due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
+- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation

### 2022-10-21 Thesis/chapter/061-results-emma.tex
XRD and SEM text frist draft

@@
     v_{cal} &= 29 - 0.052 * TCal  + 0.0011 * layr*TCal  -  0.011 * h(layr-6)*TDOC 
+    \label{eq:emma}
 \end{align}
@@
 \subsubsection{how did model selection influence results}
+The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ were included as dependent variable with the objective to maximize with a relative weight of 0.05.
+The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
+Another thought behind including $v_{cal}$ and $\lambda$ was to test if the alogrithm would correctly predict those. 
+Two major flaws behind this flaws became obvious with time: 
+(1) The algorithm would be influenced by those values to choose samples, which potenitally optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
+Neben making the problem unnoetiger weise more complicate, important time (around 10\% of the samples) could have been replaced with more insighful samples. 
+(2) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ ($C/h$ instead of $C/min$) and $\lambda$, respectively. 
+The algorithm will tend to include thos values into the prediction function for all dependent variables and possibly exclude others which have more influence on $G$ and $\rho$ (see \ref{eq:emma}).
 \begin{itemize}
@@
 \subsubsection{analyse data with other methods post optimization}
+Anova shows that the influence of TCal is significant as shown by the F 
 \begin{itemize}

### 2022-10-24 Thesis/chapter/05-computational-details.tex
ueberarbeitet
include gen figures

--- 2022-02-28 Thesis/chapter/05-computational-details.tex
@@
 \label{sec:eval}
+Reading list
+\begin{itemize}
+    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
+    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
+    %\item Curse of dimensionality scholar
+    %\item linear regression von ungar 
+    %\item ridge regression + support vector machine
+    %\item correlation vs covariance
+    %\item https://en.wikipedia.org/wiki/Regression_analysis
+    %\item https://en.wikipedia.org/wiki/Noise_reduction
+    %\item https://en.wikipedia.org/wiki/Feature_extraction
+    %\item https://en.wikipedia.org/wiki/Feature_selection
+    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
+    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
+    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
+    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
+    \item 
+    \item 
+    \item 
+\end{itemize}
 %\td{describe problem and solution found}
@@
 
+\td{system behavior are discussed in Modeling the Results.
+Algorithm and Coating Features. The theoretical efficiency
+of the proposed approach has been verified using a simulation
+based on a preliminary experimental model (48 recipes evalu-
+ated, see the Supporting Information, S3). Then, 15 new experi-
+ments were selected for each subsequent time instant. Each time
+instant involves experiment identification, solution preparation,
+coating deposition, and spot analysis.
+Figure 2a presents the laser scanner measurement of a spot
+}\cite{Carta2011}
 %\subsection{EMMA Propagation}
-\begin{table}[htb]
-	\centering
-	\begin{tabular}{ccccccc}
-		\hline
-		\hline
-conc	&layers	&vDOC	&TDOC	&vCal	&Tcal	&	\\
-		\hline
-1	&10	&5	&20	&120	&400	&\\
-1	&4	&0.1	&20	&120	&500	&\\
-5	&10	&0.1	&20	&120	&500	&\\
-5	&4	&5	&20	&480	&400	&\\
-1	&5	&5	&80	&120	&500	&\\
-1	&10	&1	&80	&480	&400	&\\
-5	&5	&1	&80	&120	&400	&\\
-5	&10	&5	&80	&480	&500	&\\
-2	&8	&0.5	&40	&360	&470	&\\
-2	&6	&2	&40	&360	&430	&\\
-		\hline
-%4	&12	&-	&-	&-	&-&\\
-1	&4	&12	&70	&120	&500	&\\
-1	&9	&18	&80	&240	&400	&\\
-%2	&5	&18	&70	&-	&-		&\\
-4	&6	&14	&60	&240	&500	&\\
-4	&6	&14	&60	&240	&500	&\\
-4	&6	&14	&60	&240	&500	&\\
-		\hline
-2	&10	&20	&40	&120	&500	&6113\\
-3	&8	&18	&70	&1080	&300	&2850\\
-3	&6	&10	&50	&1080	&400	&5526	\\
-%3	&10	&14	&50	&600	&500	&-7374	\\
-3	&10	&16	&80	&120	&500	&6554	\\
-4	&6	&16	&80	&1080	&300	&2947	\\
-3	&12	&12	&80	&840	&500	&8318	\\
-3	&10	&14	&50	&600	&500	&7374	\\
-5	&6	&10	&60	&1080	&400	&5648	\\
-5	&10	&20	&60	&360	&300	&3956	\\
-5	&12	&14	&60	&1080	&300	&2700	\\
-		\hline
-%2	&2	&10	&40	&600	&300	&-7201	\\
-2	&4	&10	&80	&1080	&300	&6101	\\
-%2	&4	&10	&40	&600	&300	&-7201	\\
-2	&4	&10	&40	&600	&300	&7201	\\
-3	&4	&12	&60	&600	&300	&1462	\\
-4	&4	&10	&80	&1080	&300	&2883	\\
-5	&12	&20	&70	&600	&300	&1680	\\
-		\hline
-2	&4	&10	&40	&120	&300	&1	\\
-2	&4	&10	&40	&120	&500	&6001	\\
-3	&4	&10	&40	&120	&500	&6102	\\
-5	&4	&10	&80	&1080	&300	&2884	\\
-5	&12	&20	&60	&120	&300	&360	\\
-		\hline
-3	&4	&10	&40	&600	&400	&4202	\\
-2	&6	&20	&40	&120	&500	&6105	\\
-%4	&4	&14	&80	&1080	&300	&-2923	\\
-5	&12	&14	&60	&600	&300	&1500	\\
-3	&6	&14	&60	&600	&300	&1486	\\
-4	&4	&14	&80	&1080	&300	&2923	\\
-		\hline
-4	&8	&18	&80	&1080	&300	&2971	\\
-3	&8	&10	&50	&1080	&300	&2530	\\
-2	&12	&16	&40	&120	&400	&3077	\\
-2	&10	&18	&60	&1080	&300	&2733	\\
-4	&10	&10	&50	&1080	&300	&2535	\\
-		\hline
-		\hline
-	\end{tabular}
-	\caption{}
-	\label{tab:emma}
-\end{table}
+%\begin{table}[htb]
+%	\centering
+%	\begin{tabular}{ccccccc}
+%		\hline
+%		\hline
+%conc	&layers	&vDOC	&TDOC	&vCal	&Tcal	&	\\
+%		\hline
+%1	&10	&5	&20	&120	&400	&\\
+%1	&4	&0.1	&20	&120	&500	&\\
+%5	&10	&0.1	&20	&120	&500	&\\
+%5	&4	&5	&20	&480	&400	&\\
+%1	&5	&5	&80	&120	&500	&\\
+%1	&10	&1	&80	&480	&400	&\\
+%5	&5	&1	&80	&120	&400	&\\
+%5	&10	&5	&80	&480	&500	&\\
+%2	&8	&0.5	&40	&360	&470	&\\
+%2	&6	&2	&40	&360	&430	&\\
+%		\hline
+%%4	&12	&-	&-	&-	&-&\\
+%1	&4	&12	&70	&120	&500	&\\
+%1	&9	&18	&80	&240	&400	&\\
+%%2	&5	&18	&70	&-	&-		&\\
+%4	&6	&14	&60	&240	&500	&\\
+%4	&6	&14	&60	&240	&500	&\\
+%4	&6	&14	&60	&240	&500	&\\
+%		\hline
+%2	&10	&20	&40	&120	&500	&6113\\
+%3	&8	&18	&70	&1080	&300	&2850\\
+%3	&6	&10	&50	&1080	&400	&5526	\\
+%%3	&10	&14	&50	&600	&500	&-7374	\\
+%3	&10	&16	&80	&120	&500	&6554	\\
+%4	&6	&16	&80	&1080	&300	&2947	\\
+%3	&12	&12	&80	&840	&500	&8318	\\
+%3	&10	&14	&50	&600	&500	&7374	\\
+%5	&6	&10	&60	&1080	&400	&5648	\\
+%5	&10	&20	&60	&360	&300	&3956	\\
+%5	&12	&14	&60	&1080	&300	&2700	\\
+%		\hline
+%%2	&2	&10	&40	&600	&300	&-7201	\\
+%2	&4	&10	&80	&1080	&300	&6101	\\
+%%2	&4	&10	&40	&600	&300	&-7201	\\
+%2	&4	&10	&40	&600	&300	&7201	\\
+%3	&4	&12	&60	&600	&300	&1462	\\
+%4	&4	&10	&80	&1080	&300	&2883	\\
+%5	&12	&20	&70	&600	&300	&1680	\\
+%		\hline
+%2	&4	&10	&40	&120	&300	&1	\\
+%2	&4	&10	&40	&120	&500	&6001	\\
+%3	&4	&10	&40	&120	&500	&6102	\\
+%5	&4	&10	&80	&1080	&300	&2884	\\
+%5	&12	&20	&60	&120	&300	&360	\\
+%		\hline
+%3	&4	&10	&40	&600	&400	&4202	\\
+%2	&6	&20	&40	&120	&500	&6105	\\
+%%4	&4	&14	&80	&1080	&300	&-2923	\\
+%5	&12	&14	&60	&600	&300	&1500	\\
+%3	&6	&14	&60	&600	&300	&1486	\\
+%4	&4	&14	&80	&1080	&300	&2923	\\
+%		\hline
+%4	&8	&18	&80	&1080	&300	&2971	\\
+%3	&8	&10	&50	&1080	&300	&2530	\\
+%2	&12	&16	&40	&120	&400	&3077	\\
+%2	&10	&18	&60	&1080	&300	&2733	\\
+%4	&10	&10	&50	&1080	&300	&2535	\\
+%		\hline
+%		\hline
+%	\end{tabular}
+%	\caption{}
+%	\label{tab:emma}
+%\end{table}
+%
 

### 2022-10-24 Thesis/chapter/060-results-material.tex
include gen figures

@@
 This means that the better the quality of the resulting layer the more tedious it was to get/take a decent SEM image. 
-Figure \ref{fig:sem-old} shows ausschnitte of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
+Figures \ref{fig:sem-old1} and \ref{fig:sem-old2} shows ausschnitte of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
 These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
@@
     \end{subfigure}
-    \caption{iv of 6x4F} \label{fig:iv}
+    \caption{iv of 6x4F} \label{fig:iv-ipo}
 \end{figure}
@@
     \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/log-146-good-10x1F.png}
-        \caption{log} \label{fig:log1}
+        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
+        \caption{log good 3x4F} \label{fig:log2}
     \end{subfigure}
     \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/log-154-okay-3x4F.png}
-        \caption{log} \label{fig:log2}
+        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
+        \caption{log okay 10x1F} \label{fig:log1}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
-        \caption{log} \label{fig:log3}
+        \caption{log bad 3x3F} \label{fig:log3}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
+        \caption{stat good 3x4F} \label{fig:stat2}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
-        \caption{stat} \label{fig:stat1}
-    \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
-        \caption{stat} \label{fig:stat2}
+        \caption{stat okay 10x1F} \label{fig:stat1}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
-        \caption{stat} \label{fig:stat3}
+        \caption{stat bad 3x3F} \label{fig:stat3}
     \end{subfigure}
-    \caption{maybe remove 146 and make 154 good AND set yrange [E-1:E-14]} \label{fig:iv}
+    \caption{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold} \label{fig:iv}
 \end{figure}

### 2022-10-24 Thesis/chapter/061-results-emma.tex
include gen figures

@@
 \subsection{EMMA}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{what is best}
-\begin{align}
-%    G    & = -3.7 + 0.18 * TCal +  8.1 * max(0,6-layr)\\
-%    \rho & = -0.78 + 0.0024 * TCal + 0.13 * max(0,6-layr)
-    G &=      -19 + 0.28 * TCal  - 0.022 * layr*TCal  +  0.16 * h(layr-6)*TDOC \\
-    \rho &=  -0.87 + 0.0047 * TCal  - 0.00036 * layr*TCal  +  0.0024 * h(layr-6)*TDOC \\
-    \lambda &=  6.8 - 0.014 * TCal  + 0.0018 * layr*TCal  + 0.0060 * h(layr-6)*TDOC \\
-    v_{cal} &= 29 - 0.052 * TCal  + 0.0011 * layr*TCal  -  0.011 * h(layr-6)*TDOC 
-    \label{eq:emma}
-\end{align}
-what was the best result? For each particle there is best and global best. 
-https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation
+\subsubsection{all samples}
+%\input{chapter/emma.table.tex}
+A total of 30 recipes have been investigated in 
+five iterations of the algorithm ($t = 0, \dots,4$). 
+%The best recipe identified by the EMMA algorithm is as follows: 
+The best recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
+The calcinatino heating $v_{cal}$ rate has been predicted perfectly 
+\td{even though $v_{cal}$ doesn't appear in the prediction function, how is this possible?}
+The number of layers $\lambda$ on the other hand was predicted poorly 
+even though the conversion factor wsa 1 and the prediction function dependent on $\lambda$.
 
@@
 
+\begin{figure}
+    \centering
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[width=.8\textwidth]{Pics/stats/gen-G.png}
+        \caption{emma G gen } \label{fig:emma-G-gen}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[width=.8\textwidth]{Pics/stats/gen-phd.png}
+        \caption{emma phd gen} \label{fig:emma-phd-gen}
+    \end{subfigure}
+    \caption{emma gen} \label{fig:emma-gen}
+\end{figure}
+
+In figure \ref{fig:emma-gen} we can see the two main optimizables at each generation
+for each particle.
+It shows a clear trend which indicates that the optimization worked even though 
+the predicted function and the chosen samples where not exactly as expected. 
+This might be due to the high error of samples.
+
 \begin{table}[h]
@@
     \caption{Global best per generation}
-	\label{tab:emma_gen}
+	\label{tab:emma-Gb}
 	\begin{tabular}{cccccccc}
@@
 	\end{tabular}
+\begin{tabular}{cccccc}
+    \hline\hline
+enr     &1st gen     &2nd gen        &3rd gen        &4th gen        &5th gen\\
+    \hline
+1       &1.214185    &       &       &       &38.7962       \\
+5       &       &4.196626       &       &       &25.47335       \\
+2947    &       &       &10.9594    &       &10.9594       \\
+2405    &       &       &       &20.04962   &25.47335       \\
+13      &       &       &       &       &24.87178   \\
+    \hline\hline
+\end{tabular}
 \end{table}
 
+%\iffalse
+%\fi
+
+%\iffalse
 \begin{figure}
@@
 \url{https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation}
+%\fi
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{what is best}
+\begin{align}
+    G &=      -19 + 0.28 * TCal  - 0.022 * layr*TCal  +  0.16 * h(layr-6)*TDOC \\
+    \rho &=  -0.87 + 0.0047 * TCal  - 0.00036 * layr*TCal  +  0.0024 * h(layr-6)*TDOC \\
+    \lambda &=  6.8 - 0.014 * TCal  + 0.0018 * layr*TCal  + 0.0060 * h(layr-6)*TDOC \\
+    v_{cal} &= 29 - 0.052 * TCal  + 0.0011 * layr*TCal  -  0.011 * h(layr-6)*TDOC 
+    \label{eq:emma}
+\end{align}
+%what was the best result? For each particle there is best and global best. 
+https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation
 
@@
 \end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{analyse data with other methods post optimization}
-Anova shows that the influence of TCal is significant as shown by the F 
-\begin{itemize}
-    \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
-    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
-    \item grid search 
-    \item KRR (???)
-    \item SVM (???)
-\end{itemize}
-
-and cite something pro forma \cite{ncbi1butanol}
-\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}

### 2022-10-24 Thesis/chapter/062-post-emma.tex
include gen figures

\subsection{Post-EMMA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{analyse data with other methods post optimization}
Anova shows that the influence of TCal is significant as shown by the F 
\begin{itemize}
    \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
    \item grid search 
    \item KRR (???)
    \item SVM (???)
\end{itemize}

\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}

### 2022-10-24 Code/EMMA/inter.R
quietly load R packages

@@ -33,7 +33,7 @@
 
 
 
-library("emma")
+suppressMessages(suppressWarnings(library("emma")))
 ### META PARAMETERS
 in.name <- 	c("conc",	"layr",	"vDOC",	"TDOC",	"vCal",	"TCal")
 nlev <- 	c(4,		5,		6,		5,		5,		3)

### 2022-10-24 Code/Statistics/scripts/anova.R

@@ -2,45 +2,50 @@
 #
 # USAGE: execute script from within the folder
 
-library("dplyr") 
+#library("dplyr",quietly=1) 
+suppressMessages(suppressWarnings(library("dplyr")))
 
+only_emma=1
 n="numeric"
 f="factor"
 dat<-read.delim("../db_final.tsv", colClasses=c(n,n,n,n,n,n,f,f,f,f,f,f))
 d.all <- dat %>% select (! avg1.G.:avg2.G.)
 d.emma <- d.all %>% filter ( enr != 0 ) 
 
-G.TCal.emma.aov<-aov(G ~ TCal, data = d.emma)
-print("ANOVA with EMMA samples: G ~ TCal")
-summary(G.TCal.emma.aov)
+if (only_emma==0)
+{
+    G.TCal.emma.aov<-aov(G ~ TCal, data = d.emma)
+    print("ANOVA with EMMA samples: G ~ TCal")
+    summary(G.TCal.emma.aov)
 
-G.TCal.all.aov<-aov(G ~ TCal, data = d.all)
-print("ANOVA with all samples: G ~ TCal")
-summary(G.TCal.all.aov)
+    G.layr.emma.aov<-aov(G ~ layr, data = d.emma)
+    print("ANOVA with EMMA samples: G ~ layr")
+    summary(G.layr.emma.aov)
 
-G.layr.emma.aov<-aov(G ~ layr, data = d.emma)
-print("ANOVA with EMMA samples: G ~ layr")
-summary(G.layr.emma.aov)
+    G.TDOC.emma.aov<-aov(G ~ TDOC, data = d.emma)
+    print("ANOVA with EMMA samples: G ~ TDOC")
+    summary(G.TDOC.emma.aov)
 
-G.layr.all.aov<-aov(G ~ layr, data = d.all)
-print("ANOVA with all samples: G ~ layr")
-summary(G.layr.all.aov)
+    G.TvDOC.emma.aov<-aov(G ~ TDOC:vDOC, data = d.emma)
+    print("ANOVA with EMMA samples: G ~ TDOC:vDOC")
+    summary(G.TvDOC.emma.aov)
+}else{
+    G.TCal.all.aov<-aov(G ~ TCal, data = d.all)
+    print("ANOVA with all samples: G ~ TCal")
+    summary(G.TCal.all.aov)
 
[…]

### 2022-10-24 Code/Statistics/scripts/emma.R

@@ -2,7 +2,7 @@
 #
 # USAGE: execute script from within the folder
 
-library("dplyr")
+suppressMessages(suppressWarnings(library("dplyr")))
 load("../../EMMA/t5") 
 source("../../EMMA/inter.R") 
 #for (i in 1:4){

### 2022-10-24 Code/Statistics/scripts/mars.R

@@ -2,8 +2,8 @@
 #
 # USAGE: execute script from within the folder
 
-library("dplyr")
-library("earth")
+suppressMessages(suppressWarnings(library("dplyr")))
+suppressMessages(suppressWarnings(library("earth")))
 
 dat<-read.delim("../db_final.tsv") 
 d.all <- dat %>% select ( ! avg1.G.:avg2.G.) 

### 2022-10-24 Code/Statistics/scripts/anova-phd.R
only emma data set

@@ -1,0 +1,46 @@
+#!/usr/bin/env Rscript
+#
+# USAGE: execute script from within the folder
+
+library("dplyr") 
+
+n="numeric"
+f="factor"
+dat<-read.delim("../db_final.tsv", colClasses=c(n,n,n,n,n,n,f,f,f,f,f,f))
+d.all <- dat %>% select (! avg1.G.:avg2.G.)
+d.emma <- d.all %>% filter ( enr != 0 ) 
+
+phd.TCal.emma.aov<-aov(phd ~ TCal, data = d.emma)
+print("ANOVA with EMMA samples: phd ~ TCal")
+summary(phd.TCal.emma.aov)
+
+phd.layr.emma.aov<-aov(phd ~ layr, data = d.emma)
+print("ANOVA with EMMA samples: phd ~ layr")
+summary(phd.layr.emma.aov)
+
+phd.TDOC.emma.aov<-aov(phd ~ TDOC, data = d.emma)
+print("ANOVA with EMMA samples: phd ~ TDOC")
+summary(phd.TDOC.emma.aov)
+
+phd.TvDOC.emma.aov<-aov(phd ~ TDOC:vDOC, data = d.emma)
+print("ANOVA with EMMA samples: phd ~ TDOC:vDOC")
+summary(phd.TvDOC.emma.aov)
+
+phd.TCal.all.aov<-aov(phd ~ TCal, data = d.all)
+print("ANOVA with all samples: phd ~ TCal")
+summary(phd.TCal.all.aov)
+
+phd.layr.all.aov<-aov(phd ~ layr, data = d.all)
+print("ANOVA with all samples: phd ~ layr")
+summary(phd.layr.all.aov)
+
+phd.TDOC.all.aov<-aov(phd ~ TDOC, data = d.all)
+print("ANOVA with all samples: phd ~ TDOC")
+summary(phd.TDOC.all.aov)
+
+phd.TvDOC.all.aov<-aov(phd ~ TDOC:vDOC, data = d.all)
+print("ANOVA with all samples: phd ~ TDOC:vDOC")
+summary(phd.TvDOC.all.aov)
+
+
+

### 2022-10-24 Code/Statistics/scripts/anova.R

@@ -5,18 +5,23 @@
 #library("dplyr",quietly=1) 
 suppressMessages(suppressWarnings(library("dplyr")))
 
-only_emma=1
+only_emma<-1
 n="numeric"
 f="factor"
 dat<-read.delim("../db_final.tsv", colClasses=c(n,n,n,n,n,n,f,f,f,f,f,f))
 d.all <- dat %>% select (! avg1.G.:avg2.G.)
-d.emma <- d.all %>% filter ( enr != 0 ) 
+d.emma <- d.all %>% filter ( enr != 0 )
+#summary(d.emma)
 
-if (only_emma==0)
-{
+#if (only_emma==1)
+#{
     G.TCal.emma.aov<-aov(G ~ TCal, data = d.emma)
     print("ANOVA with EMMA samples: G ~ TCal")
     summary(G.TCal.emma.aov)
+
+    G.vCal.emma.aov<-aov(G ~ vCal, data = d.emma)
+    print("ANOVA with EMMA samples: G ~ vCal")
+    summary(G.vCal.emma.aov)
 
     G.layr.emma.aov<-aov(G ~ layr, data = d.emma)
     print("ANOVA with EMMA samples: G ~ layr")
@@ -29,10 +34,15 @@ if (only_emma==0)
     G.TvDOC.emma.aov<-aov(G ~ TDOC:vDOC, data = d.emma)
     print("ANOVA with EMMA samples: G ~ TDOC:vDOC")
     summary(G.TvDOC.emma.aov)
-}else{
+#}else{
+    print("#######################################################3") 
     G.TCal.all.aov<-aov(G ~ TCal, data = d.all)
     print("ANOVA with all samples: G ~ TCal")
     summary(G.TCal.all.aov)
+
+    G.vCal.all.aov<-aov(G ~ vCal, data = d.all)
+    print("ANOVA with all samples: G ~ vCal")
+    summary(G.vCal.all.aov)
 
     G.layr.all.aov<-aov(G ~ layr, data = d.all)
     print("ANOVA with all samples: G ~ layr")
@@ -45,7 +55,7 @@ if (only_emma==0)
     G.TvDOC.all.aov<-aov(G ~ TDOC:vDOC, data = d.all)
     print("ANOVA with all samples: G ~ TDOC:vDOC")
     summary(G.TvDOC.all.aov)
-}
+#}
 
 
 

### 2022-10-24 Code/Statistics/scripts/linreg.py

@@ -2,20 +2,44 @@
 
 import numpy as np 
 import pandas as pd
+import dfply
 from sklearn.linear_model import LinearRegression
 
+print_influence=1
+only_emma=1
+y_index=3 # 2=G; 3=phd; 7=layers; 10=vCal 
 infile="../db_final.tsv"
 names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
 df=pd.read_csv(infile, skiprows=1, names = names,delimiter="\t")
+if only_emma:
+    df = df >>dfply.mask(df.enr !=0)
 data=np.array(df)
 X=data[:,6:]
 X_names=names[6:]
-y=data[:,2].reshape(len(data[:,2]),1)
+if (y_index == 10) : 
+    y=data[:,y_index].reshape(len(data[:,y_index]),1)*60
+else:           
+    y=data[:,y_index].reshape(len(data[:,y_index]),1)
 reg = LinearRegression().fit(X,y)
 y_pred = reg.predict(X)
+y_name = names[y_index]
+print("Lin regression for", y_name, "\tOnly EMMA data used:", only_emma)
 print("Reg score", reg.score(X,y))
 print("Reg coef", X_names)
 print("Reg coef", reg.coef_)
-exit()
+print("Reg intercept: ", reg.intercept_)
 
+if print_influence:
+    for i in range(6): 
+        #print( "influence:",names[6+i], reg.coef_[6+i]*max(X[:,6+i]) ) 
+        #print( "influence:",names[6+i], reg.coef_[0,i], reg.coef_[0,i]*max(X[:,i]) , sep="\t") 
+        print( 
+              names[6+i], 
+              "coef:",
+              reg.coef_[0,i], 
+              "influence:",
+              reg.coef_[0,i]*max(X[:,i]), 
+              sep="\t") 
+
+exit()
 

### 2022-10-24 Thesis/chapter/062-post-emma.tex
post-emma bad first draft

@@
     \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
-    \item grid search 
+    \item grid search ???
     \item KRR (???)
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{Linear Regressin}
+I thought that the influnce of $conc$ and $\lambda$ are the biggest, but they are just the smalles absolute values. 
+Thus, eventhough $T_{cal}$ might have a smaller coefficient for lin reg, the influence on the dependent variable might be larger. 
+The biggest influece on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{doc}$. 
+Both $T_{cal}$ and $T_{doc}$ have positive coefficients, i.e. a negative influence on the resistance. 
+Then both $\lambda$ and $v_{doc}$ both have about a fift ob the largest influence and a negative influence. 
+An indication that the data is strongly tainted by error (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41, 
+which is (sad but true) even unterboten by the $R^2$ of lin fit of $G$, 0.34. 
+The coefficients, though share the signs. 
+This is only true if the extended data set is used and therefore again rather by chance. 
+It is even more \td{erstaunlich} that EMMA managed to decrease the average of $pG$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}. 
+Or was is only luck?
+
+$v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality. 
+Was zu erwarten war.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{ANOVA}\label{sec:res-anova}
+\Gls{anova} doesn't provide a lot of extra information. 
+It bestaetigt that TCal has influence on both G and phd. 
+It seems that the probability of getting such data per chance that Tcal has no influence 
+(null hypothesis is true) is less then 5\% (even less than 1\%). 
+wrong the second is not for phd but for extended data set
+but for phd even lower than 0.1 \%
+
+\iffalse
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{Grid Search}
+For \gls{krr} and {svm} I had to find out what the ideal hyper parameters were. 
+So, I anstellen a grid search with the following hyperparameters: 
+%kernel=["poly","rbf"]#,"sigmoid"]
+%C= np.array(range(1,20))*0.05
+%degree=range(1,6)
+%epsilon= np.array(range(1,20))*0.2
+%gamma=[0.0,0.1,1.0,10.0]
+%#param = {"kernel":kernel, "C":C, "degree":degree, "epsilon":epsilon, "gamma":gamma }
+%C=[1,0.1]; degree=[3]; epsilon=[1,2]; gamma=['scale']
+Now what are C,epsilon and gamma?
+
+Since the data set was very small, I could be generous with the grid search even on relatively humble hardware (intel i7-8550U).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{KRR}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{SVM}
 \td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}
+\fi

### 2022-10-25 Thesis/chapter/063-discussion.tex
include gen figures
results and discussion planned

--- 2022-10-18 Thesis/chapter/062-discussion.tex
@@
-\td{ideal objective is to create response surface approximation}\\
+\subsection{Diskussion}
+\subsubsection{Mistakes and Solutions}
+This chapter is structured as a letter 
+which my present self thinks that would have helped my past self 
+if recieved before the start of the practical part of my master practikum:\\
+
+to discuss: results from EMMA or rather which the data present are counter intuitive. 
+why lowest conductivity with lowest TCal and why is there a minimum for layers? 
+low TDOC results in lower conductivity... okay
+
+Dear Johann,
+
+I know that you (I) won't believe this but I'm you in the future. 
+So you are me in the past and I have a few hints on how to avoid some stone in your way 
+and how to hopefully be more successful in you master thesis. 
+"I make a plan. I break a plan. But I'm never without a plan." - a nice quote which I couln't zuschreiben, but which holds a lot of truth. 
+Planning can give you the chance to zoom out and force yourself to get an overview. 
+It let's you decide how much time you want to spend on each todo.
+
+The next tip is that at the beginning of a project the research phase shouldn't be underestimated. 
+Take time to dig into the basics and discuss with collegues if you have the chance. 
+Try to understand the methods you'll use as well as possible. 
+Most importantly, high light advantages and disadvantages of the methods and competeing/alternatives. 
+Like in a design project. Lay out as many as diverse solutions as possible, 
+compare, and ick the best parts.
+The research phase let's you learn from other's mistakes and saves a lot of time.
+
+Another important task which preceeds/anti-follows above mentioned is to define the objective as clear as possible.  
+%\td{ideal objective is to create response surface approximation}\\
+It will help to set a clear goal for each todo, e.g. 
+the primary goal of a screening experiment is to identify the active factors.\cite{miller2001using}
+Which question should be answered and aufstellen a null Hypothesis. 
+This is often very trivial, but let's you focus on the correct path.
+
+The mistake which I regret the most is that I overestimated the vereinfachenden factor of reducing the splits (or discrete points between two extrems, which a variable can take) instead of the reduction of dimensions which eleminates a whole degree of freedom.
+I expected my algorithm of choice to perform magic. 
+A measurement to compare different algorithms could be, dimension and ratio of measured sampled to sample space. 
+Im vergleich to other algo I used a lot of dimensions and a low ratio.
+A low ratio gives rise to a high probability of the data being statistically insignificant, especially if the error is realtively large.
+
+All the best and stay persistent, \\  
+Johann \\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Mistakes} 
 \td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}\\
@@
 \td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
+\td{adding a extra variable to optimize was to optimistic and ich hab mir damit eindeutig 
+(im nachhinein) steine in den Weg gelegt.}
+The space seems to be too big for the small sample size.
+%-
+Look at relation of space size and sample size here and in Hu2016.:
+\td{In example of documentation 2 input variables and 1-2 responses initial population=10
+, subsequent population=5, but 10 iterations. Clearly more input varibles and less 
+iterations (as in actual experiments) lead to suboptimal results.}
+%
+- The exploration-vs-exploitation parameters of the model were also not set accordingly.
+see \href{https://search.r-project.org/CRAN/refmans/emma/html/emma.html}{source}
+%
+- the data has a lot of error, but because the production process takes so long and the 
+limited time and the chosen optimisation method, the experiments weren't weiderholt
+how much variance is in data? 
+%
+data-points-to-indep-vars ratio as measurement
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Next time better}
 {The primary goal of a screening experiment is to identify the active factors.
@@
 relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}}
+%
+\td{if i would plan the optimisation again, I would take less input variables (fokus on 
+conc,vdoc and tdoc or even only vdoc and tdoc) which may or may not have multiple maxima.}
+%
+- The most time consuming part was definitively the prelaminary studies.
+this time could have been verkürzt by testing a wide array of diverse recipes from the literature
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Next steps}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{diskussion and outlook}
-\td{if i would plan the optimisation again, I would take less input variables (fokus on 
-conc,vdoc and tdoc or even only vdoc and tdoc) which may or may not have multiple maxima.}
-\td{adding a extra variable to optimize was to optimistic and ich hab mir damit eindeutig 
-(im nachhinein) steine in den Weg gelegt.}
-The space seems to be too big for the small sample size.
-Look at relation of space size and sample size here and in Hu2016.
-\td{In example of documentation 2 input variables and 1-2 responses initial population=10
-, subsequent population=5, but 10 iterations. Clearly more input varibles and less 
-iterations (as in actual experiments) lead to suboptimal results.
-When plotting input vars  against the response variables, no trend
-- The exploration-vs-exploitation parameters of the model were also not set accordingly.}
-see \href{https://search.r-project.org/CRAN/refmans/emma/html/emma.html}{source}
-Would be easier to fit with single factor at a time variation or latin hyper cuber? 
-with same search-space to actual-data ratio
-- Would it also be easier for MARS or ML to find fitting function?
-plot predictions from EMMA and ML. or rather compare MAE
-- the data has a lot of error, but because the production process takes so long and the 
-limited time and the chosen optimisation method, the experiments weren't weiderholt
-how much variance is in data? 
-- The most time consuming part was definitively the prelaminary studies.
-this time could have been verkürzt by testing a wide array of diverse recipes from the literature
+
 - The data is spread across the datenraum, such that it is not trivial to 
@@
 (2) to fit in order to understand to impact of noise on the data.
+
 - Dimension reduction bietet sich stark an bei solcher Datenlage.
+
 Welche methode funktioniert bei relativ vielen variablen, wenig datenpunkten und Noise.
+
 Am besten waere feature extraction (variable x1 hat am meisten einfluss) 
@@
 I stand in front of this problem where the solution is to not use as many indep vars von vorne herein.
-- EMMA was finished on 23.02.2021 (make timeline?)
-- TODO: check which software versions
+
 -\td{for 1F c(Zr) = 44.6 mmol/L
@@
 in EMMA documentation example n=55and p=1-2, n/p=55-22.5
-plot x vs G and hold all other vars const
-write script to do that}
-\todo{make sample time line with ipo vs acoh, al vs ag, hg vs doc, ...}
+}
 \td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, 
@@
 Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}
+
 %\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer.
@@
 if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
+
 - \td{I wanted to exhaust the possibilities of EA (not having enough data).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Would be easier to fit with single factor at a time variation or latin hyper cuber? 
+%with same search-space to actual-data ratio
+%- Would it also be easier for MARS or ML to find fitting function?
+%plot predictions from EMMA and ML. or rather compare MAE

### 2022-10-27 Thesis/chapter/060-results-material.tex
ir figures included

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{XRD}
-\begin{figure}
-	\centering
-	\includegraphics[width=\picwidth]{Pics/xrd.png}
-	\caption{XRD spectra}
-	\label{fig:xrd}
-\end{figure}
-
-In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
-The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
-This wideness is is due to polycristalinity/amorphness of the material which is \td{erwartet due} to the sol-gel creation process.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{SEM}
-\begin{figure}
-    \centering
-    \begin{subfigure}{.45\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_1x.png}
-        \caption{71 fto old 1x} \label{fig:sem-old1}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_2x.png}
-        \caption{71 fto old 2x} \label{fig:sem-old2}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
-        \caption{115 fto cs 1x} \label{fig:sem-cs1}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
-        \caption{147 steel ph? 10x} \label{fig:sem-ph}
-    \end{subfigure}
-    \caption{sem}
-    \label{fig:sem}
-\end{figure}
-
-The \gls{sem} pictures were not easy to take since we were trying to create an insulator 
-and the quality of the picture relies on the conductance of the material's surface. 
-This means that the better the quality of the resulting layer the more tedious it was to get/take a decent SEM image. 
-Figures \ref{fig:sem-old1} and \ref{fig:sem-old2} shows ausschnitte of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
-These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
-Large cracks and inhomogenity were part of (ausmachen) all samples created with the Anwar recipe; 
-also/even after several/multiple/various alteration to the recipe.
-
-Figure \ref{fig:sem-cs1} shows the cross section of a single layers of \gls{zro} on \gls{fto} glass. 
-The large crystalline \td{range} which makes up most of the topper/top part of the image is \gls{fto}. 
-The úbergang to glass is gerade noch so zu sehen. 
-On the lower kante of the \gls{fto} a circa 100nm thick homogeneous layer can be observed, \gls{zro} produced by buthanolic recipe inspired by Hu et al..
-
-Figure \ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic layer on top of a steel substrate. 
-The large unregularity on the bottom left could darstellen a pin hole a (tiny) hole that reaches the substrate. 
-These unregularites are rather the ausnahme. 
-Alternatively, the small, hardly visible  irregularities verstreut across surface could darstellen such pin holes. 
-These - I think - eher only are one layer deep irregularities since they are so haeufig 
-and very little pin holes were observed on similar samples.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Material Scientific}
-\subsubsection{First recipe} 
+\subsubsection{Solution}
 As already indicated in the experimental section the recipe adopted from \cite{Anwar2017} didn't produce any \td{good} results. 
 The solution was milky/cloudy and didn't produce homogeneous films. 
-Altering the composition, pH, surfactant etc. didn't improve the resulting layers. 
+Altering the composition, pH, surfactant etc. didn't improve the resulting \gls{zro} layers. 
 %- first recipe tried to improve to achieve more restisting layer.
@@
 
+%\iffalse
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Infra Red}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}{.49\textwidth}
+        \centering
+        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
+        \caption{Transmittance of \gls{zro} on glass} \label{fig:ir-gt}
+    \end{subfigure}
+    \begin{subfigure}{.49\textwidth}
+        \centering
+        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
+        \caption{reflectance of \gls{zro} on glass} \label{fig:ir-gr}
+    \end{subfigure}
+    \caption{IR} \label{fig:ir}
+\end{figure}
+
+In figure \ref{fig:ir-gt} transmission spectra of visible and \gls{nir} light can be seen. 
+Each sample had different numbers of layers. 
+The incident angle was 0 degree for each sample.
+differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
+The more layers the more of the light is absorbed (800nm) by the \gls{zro} layers. 
+%The trend is not monotone due to 
+The thicker the layer is the more wavy the graph, which can be most likely be attributed to interferrence. 
+This trend can also be observed in figure \ref{fig:ir-gr}
+Figure \ref{fig:ir-gr} shows reflectance spectra of visible and \gls{nir} at an angle of 45 degrees. 
+%\fi
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{SEM}
+\begin{figure}
+    \centering
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_1x.png}
+        \caption{71 fto old 1x} \label{fig:sem-old1}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_2x.png}
+        \caption{71 fto old 2x} \label{fig:sem-old2}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
+        \caption{115 fto cs 1x} \label{fig:sem-cs1}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
+        \caption{147 steel ph? 10x} \label{fig:sem-ph}
+    \end{subfigure}
+    \caption{sem}
+    \label{fig:sem}
+\end{figure}
+
+The \gls{sem} pictures were not easy to take since we were trying to create an insulator 
+and the quality of the picture relies on the conductance of the material's surface. 
+This means that the better the quality of the resulting layer the more tedious it was to get/take a decent SEM image. 
+Figures \ref{fig:sem-old1} and \ref{fig:sem-old2} shows ausschnitte of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
+These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
+Large cracks and inhomogenity were part of (ausmachen) all samples created with the Anwar recipe; 
+also/even after several/multiple/various alteration to the recipe.
+
+Figure \ref{fig:sem-cs1} shows the cross section of a single layers of \gls{zro} on \gls{fto} glass. 
+The large crystalline \td{range} which makes up most of the topper/top part of the image is \gls{fto}. 
+The úbergang to glass is gerade noch so zu sehen. 
+On the lower kante of the \gls{fto} a circa 100nm thick homogeneous layer can be observed, \gls{zro} produced by buthanolic recipe inspired by Hu et al..
+
+Figure \ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic layer on top of a steel substrate. 
+The large unregularity on the bottom left could darstellen a pin hole a (tiny) hole that reaches the substrate. 
+These unregularites are rather the ausnahme. 
+Alternatively, the small, hardly visible  irregularities verstreut across surface could darstellen such pin holes. 
+These - I think - eher only are one layer deep irregularities since they are so haeufig 
+and very little pin holes were observed on similar samples.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{XRD}
+\begin{figure}
+	\centering
+	\includegraphics[width=\picwidth]{Pics/xrd.png}
+	\caption{XRD spectra}
+	\label{fig:xrd}
+\end{figure}
+
+In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
+The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
+This wideness is is due to polycristalinity/amorphness of the material which is \td{erwartet due} to the sol-gel creation process.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Preoptimization}

### 2022-10-28 Data/I-V/make_log_i-v.sh
iv figures with x/y labels

@@ -8,6 +8,8 @@ png=1
 #### SETTINGS HEAD
 echo "set xrange [-0.5:0.5]"
 echo "set logscale y"
+echo 'set xlabel "voltage [V]"'
+echo 'set ylabel "current [I]"'
 if [ $png -eq 1 ]; then 
 	echo "set term pngcairo"
 	echo "set out \"log-i-v.png\""

### 2022-10-28 Thesis/chapter/060-results-material.tex
minor change results

@@
 The more layers the more of the light is absorbed (800nm) by the \gls{zro} layers. 
-%The trend is not monotone due to 
+%The trend is not monotonic due to inhomogenities in the sample???b
 The thicker the layer is the more wavy the graph, which can be most likely be attributed to interferrence. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{V-I}
+\subsubsection{Current Voltage Curves} 
 \begin{figure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
-        \caption{log good 3x4F} \label{fig:log2}
+        \caption{log good 3x4F} \label{fig:iv-log-good}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
-        \caption{log okay 10x1F} \label{fig:log1}
+        \caption{log okay 10x1F} \label{fig:iv-log-okay}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
-        \caption{log bad 3x3F} \label{fig:log3}
+        \caption{log bad 3x3F} \label{fig:iv-log-bad}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
-        \caption{stat good 3x4F} \label{fig:stat2}
+        \caption{stat good 3x4F} \label{fig:iv-stat-good}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
-        \caption{stat okay 10x1F} \label{fig:stat1}
+        \caption{stat okay 10x1F} \label{fig:iv-stat-okay}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
-        \caption{stat bad 3x3F} \label{fig:stat3}
+        \caption{stat bad 3x3F} \label{fig:iv-stat-bad}
     \end{subfigure}
@@
 \end{figure}
+
+%Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
+Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of a good sample. 
+Each line represents a I-V measurement at a distinct contact 
+The highest voltages are around 
+All of the curves show a max voltage of under \num{e-6} \SI{}{\volt}. 
+And quite a few show hardly any current which is the ideal. 
+For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section \ref{sec:eval}). 
+Figure \ref{fig:iv-stat-good} shows the distribution of gradients.
+
+Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements from moderate sample. 
+Most of the \gls{iv}s have a maximum voltage of under \num{e-6} V, but there are some so called pin holes.
+
+Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample where all 
+measurement exhibit relatively high voltages. Which indicates a bad overall \gls{zro} layer.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Preoptimization}
+\subsubsection{Preoptimization}
 The doctor blading velocity (i.e. the velocity with which the blade moves and spreads the sol over the sample) 

### 2022-10-28 Thesis/chapter/063-discussion.tex
minor change results

@@
 
+\iffalse
 Dear Johann,
@@
 The next tip is that at the beginning of a project the research phase shouldn't be underestimated. 
-Take time to dig into the basics and discuss with collegues if you have the chance. 
+Take time to dig into the basics and discuss with colleagues if you have the chance. 
 Try to understand the methods you'll use as well as possible. 
-Most importantly, high light advantages and disadvantages of the methods and competeing/alternatives. 
+Most importantly, high light advantages and disadvantages of the methods and competing/alternatives. 
 Like in a design project. Lay out as many as diverse solutions as possible, 
@@
 Johann \\
+\fi
 

### 2022-10-30 Thesis/chapter/04-experimental.tex
DOE und PSO
added lables to experimental subsections

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Solutions}
+\subsection{Solutions}\label{sec:exp-sol}
 All recipes for solutions can be divided into two categories:
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Aquatic solution}
+\subsubsection{Aquatic solution}\label{sec:exp-sol-aq}
 \gls{zrpro} was added to \gls{acac} while stirring and in a separate vessel \gls{water} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Buthanolic solution}
-\label{sec:sol}
+\subsubsection{Buthanolic solution}\label{sec:exp-sol-bu}
 Five different concentrations of the buthanolic solutions were prepared. 
@@
 \subsection{Doctor blading}
-\label{sec:DB}
+\label{sec:exp-db}
 All glass substrates were doctor bladed manually with a smooth stainless steel wire bar 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Calcination}
+\subsection{Calcination}\label{sec:exp-calc}
 A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pre-optimisation}
+\subsection{Pre-optimisation}\label{sec:exp-preopt}
+\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
+\td{Screening}
 %Initially, glass plates were doctor bladed manually with aquatic solution and calcinated 

### 2022-10-30 Thesis/chapter/060-results-material.tex
good draft results materials/pre-opt

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Material Scientific}
-\subsubsection{Solution}
-As already indicated in the experimental section the recipe adopted from \cite{Anwar2017} didn't produce any \td{good} results. 
-The solution was milky/cloudy and didn't produce homogeneous films. 
-Altering the composition, pH, surfactant etc. didn't improve the resulting \gls{zro} layers. 
-%- first recipe tried to improve to achieve more restisting layer.
-by pH value, surface tension and solution ratios (only 10\% change because it was assumed, that the recipe is good and should be improved, but the recipe should be altered thoroughly.
-two layers were also tried but didn't even pass the visual examination/test/inspection.
-A curst was produced.
+\subsection{Material Scientific and Pre-optimization}
+%\subsubsection{Solution}
+%%%%%%%% AQUATIC 
+As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.\cite{Anwar2017} failed to produce a homogeneous layer. 
+The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure \ref{fig:sem-old}). 
+Altering the ratios of ingredients, adjusting pH (by adding \gls{naoh}, \ch{H2SO4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't improve the resulting \gls{zro} layers. 
+% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
+% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
+Even after the consecutive application of two layers there was no clear improvement and the results reminded rather of a sparse crust than of a film. 
+%It is assumed that the solution was far from the optimum for a sol-gel process. 
+%
+Figure \ref{fig:sem-old} shows a typical details of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
+%These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
+Large cracks, non coated areas and inhomogeneity were 
+%part of (ausmachen) 
+shared characteristics among 
+all samples created with the aquatic recipe. 
+%even after several/multiple/various alteration to the recipe.
 
-The sol-gel recipe optimized by \cite{Hu2016} for \ch{Al2O3} worked splendidly for our use even after (not so) minor changes.
-%An substantial improvement could be achieved by
-The stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
-The stability was inspected visually. 
+The sol-gel recipe optimized by Hu et al.\cite{Hu2016} for \ch{Al2O3} worked splendidly for our use case even after (not so) minor changes (see section \ref{sec:exp-sol-bu}). 
+%
+Figure \ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
+%%%% PIN HOLES
+The large irregularity on the bottom left could depict a pin hole, a (tiny) hole that reaches to the substrate. 
+These irregularities are rather the exception. 
+Alternatively, the small, hardly visible slits spread across the surface could depict such pin holes. 
+These - I think - are rather only one layer deep irregularities since they are so prevalent
+and hardly any pin holes were electrically observed on similar samples.
+
+%%%%%% STABILITY
 As soon as the solution showed initial cloudiness, it was declared as unstable. 
-The regular solution was stable for approximately \td{24h} sealed with Parafilm. 
+The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
+A solution with \gls{acoh} was stable for approximately \td{24h} sealed with Parafilm. 
 %192 was first with IPOH
-A solution with \gls{ipo} as stabilizing agent stayed stable for \td{72h}. 
-As an increase of the \gls{zrpro} concentration decreased the \td{stable time}. 
+Whereas a solution with \gls{ipo} as stabilizing agent stayed stable for circa \td{72h}. 
+An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
+%
+Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
+as they could be stored until the next time needed instead of producing a separate solution for each sample.
+It was discovered that after a \gls{acoh} solution has aged beyond cloudiness 
+the addition of a small amount of \gls{ipo} can even reversed the aging effect. % for \td{respectable} amount of time. 
+This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
+even after 5 fold dilution. 
+%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
+%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.
+
+\begin{figure}[htb]
+    \centering
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
+        \caption{SEM picture of \gls{zro} produces by H2O solution} \label{fig:sem-old}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.79\textwidth]{Pics/sem/147_steel_ph_10x.png}
+        \caption{SEM picture of \gls{zro} produced by buoh solution} \label{fig:sem-ph}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
+        \caption{115 fto cs 1x} \label{fig:sem-cs1}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
+        \includegraphics[width=.8\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
+        \caption{150 steel 2Fx5} \label{fig:sem-cs2}
+    \end{subfigure}
+    \caption{SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d)} \label{fig:sem}
+\end{figure}
+
+%%%%%%%%% CROSS SECTION
+Figure \ref{fig:sem-cs1} shows the cross section of a single layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
+The large crystalline part which makes up most of the image is \gls{fto}. 
+The boundary to glass is visible at the very top. 
+%On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
+On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer of \gls{zro} (produced with buthanolic recipe)  can be observed.
+%
+Measuring the cross section on steel was not as straight forward because of the ductility of steel. 
+The only way to get an insight into the thickness of the layer via \gls{sem} was through 
+scratching the surface with an diamond glass cutter. 
+The result can be seen in figure \ref{fig:sem-cs2}. 
+5 layers of double concentrated solution were applied to this sample. 
+Assuming that the raised structure resembling a tentacle is \gls{zro}, 
+the thickness of the layer can be estimated to be around \um{1}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsubsection{SEM}
+
+%The \gls{sem} pictures were not easy to take since 
+%it has been tried to create an insulator 
+%and the quality of the picture relies on the conductance of the material's surface. 
+%This means that the better the quality of the resulting layer the more tedious it was to take a decent SEM image.
+
+%
 %5F ca 100min
@@
 %acceptable layer was produced by buthanolic solution, but very unstable (short lived) how long? p41 
-\Gls{ipo} solution allowed to even reuse high concentrated solution, which would otherwise become cloudy under 60 minutes. 
-Multiple question still need to be answered: 
-What causes the cloudiness (as stability increased through sealing probably \ch{H2O} from the air or \ch{O2}) and what's the mechanism? 
-How does \gls{ipo} increase the stability? 
-Does it do so because it "fits" better with the solvent. 
-As the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}. 
-It was even observed that the addition of \td{some drops of} \gls{ipo} to an acetic solution can clear the solution.
-5F acetic solution milky over night 5:1 dilution with \gls{ipo} and clear after one minute of stirring and stayed clear over 5 nights.
+%\Gls{ipo} solution allowed to even reuse high concentrated solution, which would otherwise become cloudy under 60 minutes. 
+%Multiple question still need to be answered: 
+%What causes the cloudiness (as stability increased through sealing probably \ch{H2O} from the air or \ch{O2}) and what's the mechanism? 
+%How does \gls{ipo} increase the stability? 
+%Does it do so because it "fits" better with the solvent. 
+%As the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}. 
+%It was even observed that the addition of \td{some drops of} \gls{ipo} to an acetic solution can clear the solution.
+%5F acetic solution milky over night 5:1 dilution with \gls{ipo} and clear after one minute of stirring and stayed clear over 5 nights.
 % more details on pages 68ff
-No effect on the solution or the resulting layer was noticed \td{from the initial stirring}
-\todo{Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
+%No effect on the solution or the resulting layer was noticed \td{from the initial stirring}
+%\todo{Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
 %The stirring time was untersucht, but not much difference so shortest was used because 
@@
 %\td{instead of changing the stabilisation agent before optimisation, could change after pso, was vor und nachteile?}
-after realizing the improved effectiveness of \gls{ipo} for experimentation, 
-it was decided that EMMA will be executed with \gls{ipo} solution.
-\begin{figure}
-    \centering
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/iv-199-acoh.png}
-        \caption{iv acoh} \label{fig:iv-acoh}
-    \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/iv-201-acoh-ipo.png}
-        \caption{iv acoh ipo} \label{fig:iv-acoh-ipo}
-    \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/iv-192-ipo.png}
-        \caption{ipo} \label{fig:ipo}
-    \end{subfigure}
-    \caption{iv of 6x4F} \label{fig:iv-ipo}
-\end{figure}
+%after realizing the improved effectiveness of \gls{ipo} for experimentation, 
+%it was decided that EMMA will be executed with \gls{ipo} solution.
+
+%- first recipe tried to improve to achieve more resisting layer. 
+%by pH value, surface tension and solution ratios 
+%(only 10\% change because it was assumed, that the recipe is good and should be improved, 
+%but the recipe should be altered thoroughly. 
+%two layers were also tried but didn't even pass the visual examination/test/inspection. 
+%A curst was produced. 
+%It is assumed
+
+%\iffalse
+%\begin{figure}
+%    \centering
+%    \begin{subfigure}{.45\textwidth}
+%        \centering
+%        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_1x.png}
+%        \caption{71 fto old 1x} \label{fig:sem-old1}
+%    \end{subfigure}
+%    \begin{subfigure}{.45\textwidth}
+%        \centering
+%        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_2x.png}
+%        \caption{71 fto old 2x} \label{fig:sem-old2}
+%    \end{subfigure}
+%    \begin{subfigure}{.45\textwidth}
+%        \centering
+%        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
+%        \caption{115 fto cs 1x} \label{fig:sem-cs1}
+%    \end{subfigure}
+%    \begin{subfigure}{.45\textwidth}
+%        \centering
+%        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
+%        \includegraphics[width=.8\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
+%        \caption{150 steel 2Fx5} \label{fig:sem-cs2}
+%    \end{subfigure}
+%    \caption{cross section}
+%    \label{fig:sem}
+%\end{figure}
+%\fi
 
@@
 
-\begin{figure}
+\begin{figure}[htb]
     \centering
@@
 The incident angle was 0 degree for each sample.
-differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
-The more layers the more of the light is absorbed (800nm) by the \gls{zro} layers. 
+%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
+The more layers the more of the light is absorbed (1000nm) by the \gls{zro} layers. 
 %The trend is not monotonic due to inhomogenities in the sample???b
-The thicker the layer is the more wavy the graph, which can be most likely be attributed to interferrence. 
-This trend can also be observed in figure \ref{fig:ir-gr}
-Figure \ref{fig:ir-gr} shows reflectance spectra of visible and \gls{nir} at an angle of 45 degrees. 
+The thicker the layer is the more wavy the graph, which most likely can be attributed to interference.
+This trend can also be observed in figure \ref{fig:ir-gr}.
+The light interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film}. 
+Figure \ref{fig:ir-gr} shows reflectance spectra of visible and \gls{nir} at an incident angle of 45 degrees. 
+The shift of the wavy part of the spectra (comparing reflectance with transmittance) 
+can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
 %\fi
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{SEM}
-\begin{figure}
-    \centering
-    \begin{subfigure}{.45\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_1x.png}
-        \caption{71 fto old 1x} \label{fig:sem-old1}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_2x.png}
-        \caption{71 fto old 2x} \label{fig:sem-old2}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
-        \caption{115 fto cs 1x} \label{fig:sem-cs1}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
-        \caption{147 steel ph? 10x} \label{fig:sem-ph}
-    \end{subfigure}
-    \caption{sem}
-    \label{fig:sem}
-\end{figure}
-
-The \gls{sem} pictures were not easy to take since we were trying to create an insulator 
-and the quality of the picture relies on the conductance of the material's surface. 
-This means that the better the quality of the resulting layer the more tedious it was to get/take a decent SEM image. 
-Figures \ref{fig:sem-old1} and \ref{fig:sem-old2} shows ausschnitte of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
-These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
-Large cracks and inhomogenity were part of (ausmachen) all samples created with the Anwar recipe; 
-also/even after several/multiple/various alteration to the recipe.
-
-Figure \ref{fig:sem-cs1} shows the cross section of a single layers of \gls{zro} on \gls{fto} glass. 
-The large crystalline \td{range} which makes up most of the topper/top part of the image is \gls{fto}. 
-The úbergang to glass is gerade noch so zu sehen. 
-On the lower kante of the \gls{fto} a circa 100nm thick homogeneous layer can be observed, \gls{zro} produced by buthanolic recipe inspired by Hu et al..
-
-Figure \ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic layer on top of a steel substrate. 
-The large unregularity on the bottom left could darstellen a pin hole a (tiny) hole that reaches the substrate. 
-These unregularites are rather the ausnahme. 
-Alternatively, the small, hardly visible  irregularities verstreut across surface could darstellen such pin holes. 
-These - I think - eher only are one layer deep irregularities since they are so haeufig 
-and very little pin holes were observed on similar samples.
 
@@
 %Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
-Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of a good sample. 
-Each line represents a I-V measurement at a distinct contact 
-The highest voltages are around 
-All of the curves show a max voltage of under \num{e-6} \SI{}{\volt}. 
-And quite a few show hardly any current which is the ideal. 
-For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section \ref{sec:eval}). 
-Figure \ref{fig:iv-stat-good} shows the distribution of gradients.
-
+Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of a insulating sample. 
+Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
+All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
+and quite a few show hardly any current which is the ideal. 
+For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section \ref{sec:exp-eval}). 
+Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample as in \ref{fig:iv-log-good}.
+%
 Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements from moderate sample. 
-Most of the \gls{iv}s have a maximum voltage of under \num{e-6} V, but there are some so called pin holes.
-
-Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample where all 
-measurement exhibit relatively high voltages. Which indicates a bad overall \gls{zro} layer.
+Most of the \gls{iv}s have a maximum voltage of under \num{e-6} V, 
+but there are some so called pin holes with conductance above this threshold. %\num{e-6} V. 
+%
+In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of the functions 
+is not at \SI{0}{\volt}, which means that the function does not cross the origin. 
+This deviation is similar to the deviation because of the photo-currents\cite{perez2018solar}, 
+but was not investigated further. 
+Though, the photo-current is compelling, it is most likely not zutreffend because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
+%
+Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample 
+where all measurement exhibit relatively high voltages and high calculated conductances. 
+This indicates a overall bad condition of the \gls{zro} layer for insulating.
 
@@
 
-In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
-The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
-This wideness is is due to polycristalinity/amorphness of the material which is \td{erwartet due} to the sol-gel creation process.
+Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate, steel, and 
+the substrate with ten layers of double concentrated solution (experiment number 6113, see \td{appendix}).
+In addition two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108).
+The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ clearly stand out against the noise from the experimental spectrum. %can be clearly seen in the experimental spectra.
+%In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
+%The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
+%This wideness is is due to polycrystalline form of the material which is expected 
+%due to the sol-gel creation process and multiple applications of layers. 
+%Nonetheless, the \gls{xrd} spectra shows clearly that the produced layer is \gls{zro}.
 
@@
 \subsubsection{Preoptimization}
-The doctor blading velocity (i.e. the velocity with which the blade moves and spreads the sol over the sample) 
-was varied during preoptimization. 
-The slower the \gls{db} velocity the more \td{homogeneously} the solution evaporated. 
-If the \gls{db} was \td{too slow (lt 1 mm/s)} the surface tension pulled solvent over the sample without \td{leaving was zurk/forming a gel.}
-\td{deposition because miniscus is pulling liquid off the substrate.}
-Additionally the temperature while doctor blading affects the resulting layer together with the \gls{db} velocity.
+Before the optimization with the \gls{emma} algorithm, 
+the boundaries of the input variables were explored. 
+Especially, the \gls{db} velocity (i.e. the velocity with which the blade moves and spreads the solution over the sample)
+was varied and examined during pre-optimization. 
+The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
+If the \gls{db} velocity was too slow (less than \mmps{1}), no layer was formed. 
+With the reason that the force exerted by the blade on the liquid not being strong enough to overcome surface tension. 
+This means that behind the blade a meniscus would pull the liquid without leaving any for the gelling process. 
+Additionally, the temperature while \gls{db} affects the resulting layer together with the \gls{db} velocity.
 
-\td{Assumption: Ideally solution evaporate shortly after DB but not before}
-due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
-- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation
+%\td{Assumption: Ideally solution evaporate shortly after DB but not before}
+%due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
+%- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation

### 2022-10-30 Thesis/chapter/060-results-material.tex
add appendix

@@
 Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate, steel, and 
-the substrate with ten layers of double concentrated solution (experiment number 6113, see \td{appendix}).
+the substrate with ten layers of double concentrated solution (experiment number 6113, see Appendix \ref{sec:app-emma}).
 In addition two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108).

### 2022-10-30 Thesis/chapter/061-results-emma.tex
post-emma bad first draft
minor change results
good draft results materials/pre-opt
add appendix

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{all samples}
-%\input{chapter/emma.table.tex}
-A total of 30 recipes have been investigated in 
-five iterations of the algorithm ($t = 0, \dots,4$). 
+%\subsubsection{all samples}
+A total of 30 recipes (see \ref{sec:app-emma}) have been investigated in 
+five iterations of the algorithm ($t = 0, \dots, 4$). 
 %The best recipe identified by the EMMA algorithm is as follows: 
 The best recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
-The calcinatino heating $v_{cal}$ rate has been predicted perfectly 
+The calcination heating $v_{cal}$ rate has been predicted perfectly 
 \td{even though $v_{cal}$ doesn't appear in the prediction function, how is this possible?}
@@
 
-\begin{figure}
+\begin{figure}[htb]
     \centering
     \begin{subfigure}{.45\textwidth}
+        \centering
         \includegraphics[width=.8\textwidth]{Pics/stats/gen-G.png}
@@
     \begin{subfigure}{.45\textwidth}
+        \centering
         \includegraphics[width=.8\textwidth]{Pics/stats/gen-phd.png}
@@
 
-\begin{table}[h]
+\begin{table}[htb]
 	\centering
@@
 
-%\iffalse
+\iffalse
 \begin{figure}
@@
 \url{https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation}
-%\fi
+\fi
 
@@
 %what was the best result? For each particle there is best and global best.
-https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation
 
@@
 \end{itemize}
+
+\td{look at emma papers}

### 2022-11-02 Thesis/chapter/061-results-emma.tex
EMMA/MARS equations, begin describe

@@
 %\subsubsection{all samples}
-A total of 30 recipes (see \ref{sec:app-emma}) have been investigated in 
-five iterations of the algorithm ($t = 0, \dots, 4$). 
-%The best recipe identified by the EMMA algorithm is as follows: 
+A total of 30 recipes (see appendix \ref{sec:app-emma}) have been investigated in 
+five iterations ($t = 0, \dots, 4$) of the algorithm. 
+Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
 The best recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
-The calcination heating $v_{cal}$ rate has been predicted perfectly 
-\td{even though $v_{cal}$ doesn't appear in the prediction function, how is this possible?}
-The number of layers $\lambda$ on the other hand was predicted poorly 
-even though the conversion factor wsa 1 and the prediction function dependent on $\lambda$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{how did evolve over time?}
-
-\begin{figure}[htb]
-    \centering
-    \begin{subfigure}{.45\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{Pics/stats/gen-G.png}
-        \caption{emma G gen } \label{fig:emma-G-gen}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{Pics/stats/gen-phd.png}
-        \caption{emma phd gen} \label{fig:emma-phd-gen}
-    \end{subfigure}
-    \caption{emma gen} \label{fig:emma-gen}
-\end{figure}
-
-In figure \ref{fig:emma-gen} we can see the two main optimizables at each generation
-for each particle.
-It shows a clear trend which indicates that the optimization worked even though 
-the predicted function and the chosen samples where not exactly as expected. 
-This might be due to the high error of samples.
+The experiments for generation 5 where not executed but 
+predictions were alread made
+with the information from the previous generations. 
+%%% BEST
+The best sample predicted by the algorithm is experiment number 13 with 
+lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
+and lowest calcination heating rate and temperature.
 
@@
         \hline\hline
-    generation  &enr &conc &layr &vDOC &TDOC &vCal &TCal\\
+        generation  &enr &conc &layr &$v_{DB}$ &$T_{DB}$ &$v_{cal}$ &$T_{cal}$\\
         \hline
@@
 	\end{tabular}
+\end{table}
+
+\begin{table}
+	\centering
+    \caption{Predicted G} 
+    \label{tab:emma-pred-G}
     \begin{tabular}{cccccc}
@@
 \end{table}
+
+%%% OVER TIME 
+The only clear trend from table \ref{tab:emma-Gb} is the layer count, which rises with the generations. 
+The remaining input variables remained more or less the same except for the 3rd generation. 
+%
+In table \ref{tab:emma-pred-G} it can be seen that $G$ as predicted 
+by the 5th generation by the prediction function lowered with each iteration, 
+except for sample 2947, which wasn't predicted but measured. 
+This shows that the easiest part of the algorithm, the selection of the optimum 
+from predicted values works as expected. 
+% and that the predictions included more lower values over time
+%
+The predicted $G$ for each generation's best as predicted 
+by the very generation would increase with each iteration (see table \ref{tab:emma-pred-G}). 
+This indicates an underestimation of the $G$ at the beginning and a correction with time. 
+%The reason for is probably a 
+The underestimation probably stems from a lucky selection of initial experiments.
+
+In figure \ref{fig:emma-gen} we can see the two measured main target dependent variables, $\gamma$ and $\rho$, of each particle at generations 1 to 4. 
+%for each particle included in the optimization. 
+%It shows a clear trend which indicates that the optimization worked even though 
+Both variables were to be minimized and show a clear trend towards low values indicating 
+that the optimization worked even though 
+the prediction functions (see equations \ref{eq:emma-G3} - \ref{eq:emma-vcal4}) 
+and the chosen samples where not exactly as expected. 
+Neither were the measurements for these samples, which might be due to the high measuring error of samples and variation of quality due to uncontrolled independent variables like room temperature or humidity.
+
+\begin{figure}[hb]
+    \centering
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{Pics/stats/gen-G.png}
+        \caption{} \label{fig:emma-G-gen}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{Pics/stats/gen-phd.png}
+        \caption{} \label{fig:emma-phd-gen}
+    \end{subfigure}
+    \caption{Each $\gamma$ (a) and $\rho$ (b) of each particle and each generation after initial selection process} 
+    \label{fig:emma-gen}
+\end{figure}
+
+%%% EQUATION 
+Equations \ref{eq:emma-G3}-\ref{eq:emma-vcal3} and \ref{eq:emma-G4}-\ref{eq:emma-vcal4} represent the prediction functions at $t=3$ and $t=4$ rounded to 2 significant digits, respectively.
+$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
+The expression $h(\lambda-6)$ translates into layer count only has an influence if larger than 6 
+and $h(6-\lambda)$ into layer count influential only if under 6.
+%
+The first thing to notice is that every prediction function of a generation depends on the same variables. 
+%This means that the algorithm must decide on the variables which explain the most variance independent of optimization weights.
+This stems from the fact that the algorithm must chose a single minimal set of basis functions to predict all dependent variables. 
+%
+Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as dependent variables rather unfortunate. %highly questionable. 
+%As the \gls{mars} algorithm is gready,
+Different independent variables compete to be in the prediction functions because of the greediness of the \gls{mars} algorithm. 
+%\td{This makes including $\lambda$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
+In equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} the coefficient have the same signs and differ by a factor of roughly 100.
+This fits the data well, but the positive influence of the layer count/number is counter intuitive 
+as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of pin holes going all the way trough the \gls{zro} layer. %pin hole density. 
+The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} 
+seem low, but considering the minimum value of the inter action of \num{36000} should not be under estimated. 
+%It's positive the hinge
+It is astonishing that the knot of the hinge function for equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} was chosen so low; 
+basically only including the influence of $\lambda=4$.
+On the positive site the calcination heating rate $v_{cal}$ (see equation \ref{eq:emma-vcal}) has been predicted perfectly within numerical precision.
+
+It is interesting that measured 
+%%% MAIN INFLUENCE 
+%Even without considering the large maximum of $T_{cal}$,
+
+\iffalse
+The coefficient for $T_{cal}$ is the largest for all equations. 
+Factoring in the large maximum value of $T_{cal}$ in contrast the other independent variables, 
+$T_{cal}$ has the by far the largest influence on the dependent variables. 
+The coefficient of the interaction of $layr$ and $T_{cal}$ is about a tenth in size, %interaction between?H
+but has the extra factor of $layr$ of up to 12, resulting in the products being in the same order of magnitude.
+I can be noted that the coefficient of the $layr\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient. 
+%%% EXPECTATION
+It should be doubted, though, that the $layr$ only appears as interaction term 
+together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
+\fi
+
+\begin{align}
+%
+    \label{eq:emma-phd1}
+    \hat{\rho}_1 &= -26  + 0.0025 \cdot T_{DB}\cdot T{Cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{Cal} \\
+    \label{eq:emma-G1}
+    \hat{\gamma}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{DB}\cdot T_{Cal} + 0.00080 \cdot h(6-layr)\cdot T_{cal}\\
+    \label{eq:emma-layr1}
+    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{DB}\cdot T_{cal} -  0.0056 \cdot  h(6-layr)\cdot T_{cal}\\
+    \label{eq:emma-vcal1}
+    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{DB}\cdot T_{cal} - 0.0055 \cdot  h(6-layr)\cdot T_{cal}\\
+%
+    \label{eq:emma-phd2}
+    \hat{\rho}_2 &= 47\\
+    \label{eq:emma-G2}
+    \hat{\gamma}_2 &= 0.23\\
+    \label{eq:emma-layr2}
+    \hat{\lambda}_2 &= 7.3\\
+    \label{eq:emma-vcal2}
+    \hat{v}_{cal,2} &= 10\\
+%
+    \label{eq:emma-phd3}
+    \hat{\rho}_3 &= 0.075  -   0.0014 \cdot  v_{cal}  +    0.18 \cdot  h(6-\lambda)  + 3.9\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
+    \label{eq:emma-G3}
+    \hat{\gamma}_3 &= 43  -   0.097 \cdot  v_{cal}  +     10 \cdot  h(6-\lambda)  + 0.00026 \cdot  v_{cal}\cdot T_{cal} \\
+    \label{eq:emma-layr3}
+    \hat{\lambda}_3 &= 9.9  - 0.00064 \cdot  v_{cal}  -     2.7 \cdot  h(6-\lambda)  - 1.3\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
+    \label{eq:emma-vcal3}
+    \hat{v}_{cal,3} &= -5.2\cdot 10^{-15}  +   0.016 \cdot  v_{Cal}  + 1.3\cdot 10^{-15} \cdot  h(6-\lambda)  + 3.9\cdot 10^{-21} \cdot  v_{Cal}\cdot T_{cal} \\
+%
+    \label{eq:emma-phd4}
+    \hat{\rho}_4 &=  -0.87 + 0.0047 \cdot  T_{cal} - 0.00036 \cdot  \lambda\cdot T_{cal}  +  0.0024 \cdot  h(\lambda-6)\cdot T_{DB} \\
+    \label{eq:emma-G4}
+    \hat{\gamma}_4 &=     -19 + 0.28 \cdot  T_{cal}  - 0.022 \cdot  \lambda\cdot T_{cal}  +  0.16 \cdot  h(\lambda-6)\cdot T_{DB} \\
+    \label{eq:emma-layr4}
+    \hat{\lambda}_4 &=  6.8 - 0.014 \cdot  T_{cal}  + 0.0018 \cdot  \lambda\cdot T_{cal}  + 0.0060 \cdot  h(\lambda-6)\cdot T_{DB} \\
+    \label{eq:emma-vcal4}
+    \hat{v}_{cal,4} &=  29 - 0.052 \cdot  T_{cal}  + 0.0011 \cdot  \lambda\cdot T_{cal}  -  0.011 \cdot  h(\lambda-6)\cdot T_{DB} 
+\end{align}
+%\fi
+%what was the best result? For each particle there is best and global best.
+
+%The calcination heating $v_{cal}$ rate has been predicted perfectly. 
+%\td{even though $v_{cal}$ doesn't appear in the prediction function, how is this possible?}
+%The number of layers $\lambda$ on the other hand was predicted poorly 
+%even though the conversion factor was $1$ and the prediction function dependent on $\lambda$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%\subsubsection{how did evolve over time?}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{what is best}
-\begin{align}
-    G &=      -19 + 0.28 * TCal  - 0.022 * layr*TCal  +  0.16 * h(layr-6)*TDOC \\
-    \rho &=  -0.87 + 0.0047 * TCal  - 0.00036 * layr*TCal  +  0.0024 * h(layr-6)*TDOC \\
-    \lambda &=  6.8 - 0.014 * TCal  + 0.0018 * layr*TCal  + 0.0060 * h(layr-6)*TDOC \\
-    v_{cal} &= 29 - 0.052 * TCal  + 0.0011 * layr*TCal  -  0.011 * h(layr-6)*TDOC 
-    \label{eq:emma}
-\end{align}
-%what was the best result? For each particle there is best and global best.
-
+%\subsubsection{what is best}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{how did model selection influence results}
-The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ were included as dependent variable with the objective to maximize with a relative weight of 0.05.
+\subsubsection{influence of variable selection on outcome}
+The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ were included as dependent variable with the objective to maximize with a relative weight of 0.05 each.
 The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
-Another thought behind including $v_{cal}$ and $\lambda$ was to test if the alogrithm would correctly predict those. 
-Two major flaws behind this flaws became obvious with time: 
-(1) The algorithm would be influenced by those values to choose samples, which potenitally optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
-Neben making the problem unnoetiger weise more complicate, important time (around 10\% of the samples) could have been replaced with more insighful samples. 
-(2) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ ($C/h$ instead of $C/min$) and $\lambda$, respectively. 
-The algorithm will tend to include thos values into the prediction function for all dependent variables and possibly exclude others which have more influence on $G$ and $\rho$ (see \ref{eq:emma}).
+Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
+%
+Three major flaws behind this consideration became obvious with time: 
+%
+\todo{
+(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ ($C/h$ instead of $C/min$) and $\lambda$, respectively. 
+The algorithm will tend to include those values into the prediction function for 
+all dependent variables and possibly exclude others which have more influence 
+on $\gamma$ and $\rho$ (see equations \ref{eq:emma-G} and \ref{eq:emma-phd}).
+%
+(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
+%
+(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
 \begin{itemize}
     \item MARS chooses same set from independent variables for predicting all dependent variables. 
-    \item flaws of MARS: all functions are dependent on same indep vars
+    \item flaws of MARS: all functions are dependent on same independent vars
     \item Every output var is independent of each other, so $v_{cal}$ can act as test 
 heating rate was one of the dependent variables with the intention of minimizing the variable. 
-It can also be used as test to see how well the EMMA performes (or rather, more precisely MARS)
+It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS)
 It doesn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
@@
 \end{itemize}
+}
 
 \td{look at emma papers}
+\td{change G to gamma and write enr to every figure}
+\td{calculate MSE for predictions}

### 2022-11-02 Code/Statistics/scripts/emma.R

@@ -2,23 +2,22 @@
 #
 # USAGE: execute script from within the folder
 
+
+# 
+# emmacheck(t4,graph="yes",nresp={1,2,3,4})
+# wget https://cran.r-project.org/src/contrib/Archive/emma/emma_0.1-0.tar.gz
+# tar xf emma_0.1-0.tar.gz 
+# vim emma/R/emmacheck.R 
+
 suppressMessages(suppressWarnings(library("dplyr")))
 load("../../EMMA/t5") 
 source("../../EMMA/inter.R") 
-#for (i in 1:4){
-#    emmacheck(t4,graph=1,eresp=i)
-#}
-#print("Global Best")
-#t5$Gb.arch
-#print("Personal Best")
-##matrix(t5$Pb.arch,nrow=5)
-##t5$xpop[:2] 
 
 x<-t4
 input <- cbind(x$xpop,x$ypop)
 fmla <- as.formula(paste(paste("data.matrix(input[,",ncol(x$xpop)+1,":",ncol(x$xpop)+ncol(x$ypop),"])"),"~", paste(colnames(x$xpop),collapse= "+")))
 mars.mod <- earth(fmla,degree=2,trace=0,minspan=1,data=input,keepxy=TRUE)
-head(x$ypop,1)
+sprintf("t%i",x$time)
 format(mars.mod)
 
 

### 2022-11-02 Code/Statistics/scripts/mars.R

@@ -1,31 +1,37 @@
 #!/usr/bin/env Rscript
 #
 # USAGE: execute script from within the folder
+# GET MARS fuctions from db_final.emma.tsv
 
 suppressMessages(suppressWarnings(library("dplyr")))
 suppressMessages(suppressWarnings(library("earth")))
+only_emma=1
 
+dat<-read.delim("../db_final.emma.tsv") 
 dat<-read.delim("../db_final.tsv") 
 d.all <- dat %>% select ( ! avg1.G.:avg2.G.) 
-x.all <- d.all %>% select(conc:TCal)
-#y.all <- d.all %>% select( G:phd)
-#y.all <- d.all %>% mutate(vC6=vCal*60) %>% select(G,phd,layr,vC6)
+if (! only_emma){
+x.all <- d.all %>% mutate(vC6=vCal*60) %>% select(conc:layr,vDOC,TDOC,vC6,TCal)
 y.all <- d.all %>% select(G,phd,layr,vCal)
 mars.all <- earth ( x.all, y.all, degree=2)
 print("MARS model for all samples") 
 format(mars.all)
+}
 
 d.emma <- d.all %>% filter ( enr != 0 ) 
-x.emma <- d.emma %>% select(conc:TCal)
-y.emma <- d.emma %>% mutate(vC6=vCal*60) %>% select(G,phd,layr,vC6)
-mars.emma <- earth ( x.emma, y.emma, degree=2)
+x.emma <- d.emma %>% mutate(vC6=vCal*60) %>% select(conc:layr,vDOC,TDOC,vC6,TCal)
+y.emma <- d.emma %>% select(G,phd,layr,vCal)
+input <- cbind(x.emma,y.emma)
+fmla <- as.formula(paste(paste("data.matrix(input[,",ncol(x.emma)+1,":",ncol(x.emma)+ncol(y.emma),"])"),"~", paste(colnames(x.emma),collapse= "+")))
+mars.emma <- earth(fmla,degree=2,trace=0,minspan=1,data=input,keepxy=TRUE)
 print("MARS model for EMMA samples")
 format(mars.emma)
 
+if (! only_emma){
 d.hot <- d.all %>% filter ( TCal != 300 ) 
 x.hot <- d.hot %>% select(conc:TCal)
 y.hot <- d.hot %>% mutate(vC6=vCal*60) %>% select(G,phd,layr,vC6)
 mars.hot <- earth ( x.hot, y.hot, degree=2)
[…]

### 2022-11-02 Code/Statistics/scripts/mse-gen-4-5.R

@@ -1,0 +1,36 @@
+#!/usr/bin/env Rscript
+#
+# USAGE: execute script from within the folder
+
+# 
+# emmacheck(t4,graph="yes",nresp={1,2,3,4})
+# wget https://cran.r-project.org/src/contrib/Archive/emma/emma_0.1-0.tar.gz
+# tar xf emma_0.1-0.tar.gz 
+# vim emma/R/emmacheck.R 
+
+suppressMessages(suppressWarnings(library("dplyr")))
+load("../../EMMA/t5") 
+source("../../EMMA/inter.R") 
+source("../../../../emma.src/emma/R/estimateModel.R")
+
+mse<- function(x){
+    g3.pred <- estimateModel(x,"no")[x$tested,]
+    g3.measured <- x$ypop
+    g3.diff <- g3.pred - g3.measured
+    g3.se <- g3.diff * g3.diff
+    g3.sum <- 0
+    g3.n <- 0
+    for (i in 1:ncol(g3.se)){
+        for (j in 1:nrow(g3.se)){
+            g3.sum <- g3.sum + g3.se[j,i]
+            g3.n <- g3.n + 1 
+        }
+    }
+    g3.mse<- g3.sum/g3.n
+    return (g3.mse)
+}
+#sprintf("MSE_t0: %f",mse(t0))
+sprintf("MSE_t1: %i %f",length(t1$tested),mse(t1))
+sprintf("MSE_t2: %i %f",length(t2$tested),mse(t2))
+sprintf("MSE_t3: %i %f",length(t3$tested),mse(t3))
+sprintf("MSE_t4: %i %f",length(t4$tested),mse(t4))

### 2022-11-02 Code/Statistics/scripts/polyreg.py

@@ -1,0 +1,35 @@
+#!/usr/bin/env python3
+
+import numpy as np 
+import pandas as pd
+from sklearn.preprocessing import PolynomialFeatures
+from sklearn.linear_model import LinearRegression
+
+# DATA PREPARATION
+y_index=2 # 2=G; 3=phd; 7=layers; 10=vCal 
+infile="../db_final.tsv"
+names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
+df=pd.read_csv(infile, skiprows=1, names = names,delimiter="\t")
+data=np.array(df)
+X=data[:,6:]
+X_names=names[6:]
+if (y_index == 10) : 
+    y=data[:,y_index].reshape(len(data[:,y_index]),1)*60
+else:           
+    y=data[:,y_index].reshape(len(data[:,y_index]),1)
+
+#REGRESSION 
+poly_reg=PolynomialFeatures(interaction_only=True)
+X_poly=poly_reg.fit_transform(X)
+reg = LinearRegression().fit(X_poly,y)
+poly_reg.fit(X_poly,y)
+y_pred = reg.predict(X_poly)
+y_name = names[y_index]
+
+print("Lin regression for", y_name)
+print("Reg score", reg.score(X_poly,y))
+print("Reg coef", X_names)
+print("Reg coef", reg.coef_)
+print("Reg intercept: ", reg.intercept_)
+exit()
+

### 2022-11-02 Thesis/chapter/061-results-emma.tex
MSE for t=1,2,3,4, pre-opt too

@@
 
-It is interesting that measured 
+For each generation the \gls{mse} was calculated such that only samples were used which were available at that time. 
+It is 64, 158, 54 and 50 for $t=1,2,3,4$, respectively. 
+The high \gls{mse} can be explained because the prediction function is only a constant at $t=2$. 
+Appart from the second generation the \gls{mse} falls over time, which might be attributed to overfitting.
+The \gls{mse} for each generation was calculated between predicted values for pre-optimisation samples to check for overfitting, 
+but the the error sank with each generation (except for the second gen): 102, 118, 58, 50, respectively for $t=1,2,3,4$.
+
+It is interesting that although prediction functions for $t=3$ perfectly predicted $v_{cal}$ 
+the combined \gls{mse} for $t=4$ is lower. 
 %%% MAIN INFLUENCE 
@@
 %
-    \label{eq:emma-phd1}
-    \hat{\rho}_1 &= -26  + 0.0025 \cdot T_{DB}\cdot T{Cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{Cal} \\
-    \label{eq:emma-G1}
-    \hat{\gamma}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{DB}\cdot T_{Cal} + 0.00080 \cdot h(6-layr)\cdot T_{cal}\\
-    \label{eq:emma-layr1}
-    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{DB}\cdot T_{cal} -  0.0056 \cdot  h(6-layr)\cdot T_{cal}\\
-    \label{eq:emma-vcal1}
-    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{DB}\cdot T_{cal} - 0.0055 \cdot  h(6-layr)\cdot T_{cal}\\
+%    \label{eq:emma-phd1}
+%    \hat{\rho}_1 &= -26  + 0.0025 \cdot T_{DB}\cdot T{Cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{Cal} \\
+%    \label{eq:emma-G1}
+%    \hat{\gamma}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{DB}\cdot T_{Cal} + 0.00080 \cdot h(6-layr)\cdot T_{cal}\\
+%    \label{eq:emma-layr1}
+%    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{DB}\cdot T_{cal} -  0.0056 \cdot  h(6-layr)\cdot T_{cal}\\
+%    \label{eq:emma-vcal1}
+%    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{DB}\cdot T_{cal} - 0.0055 \cdot  h(6-layr)\cdot T_{cal}\\
 %
-    \label{eq:emma-phd2}
-    \hat{\rho}_2 &= 47\\
-    \label{eq:emma-G2}
-    \hat{\gamma}_2 &= 0.23\\
-    \label{eq:emma-layr2}
-    \hat{\lambda}_2 &= 7.3\\
-    \label{eq:emma-vcal2}
-    \hat{v}_{cal,2} &= 10\\
+%    \label{eq:emma-phd2}
+%    \hat{\rho}_2 &= 47\\
+%    \label{eq:emma-G2}
+%    \hat{\gamma}_2 &= 0.23\\
+%    \label{eq:emma-layr2}
+%    \hat{\lambda}_2 &= 7.3\\
+%    \label{eq:emma-vcal2}
+%    \hat{v}_{cal,2} &= 10\\
 %

### 2022-11-02 Code/Statistics/scripts/mars.R

@@ -7,7 +7,6 @@ suppressMessages(suppressWarnings(library("dplyr")))
 suppressMessages(suppressWarnings(library("earth")))
 only_emma=1
 
-dat<-read.delim("../db_final.emma.tsv") 
 dat<-read.delim("../db_final.tsv") 
 d.all <- dat %>% select ( ! avg1.G.:avg2.G.) 
 if (! only_emma){

### 2022-11-02 Code/Statistics/scripts/mse-gen-4-5.R

@@ -1,36 +1,0 @@
-#!/usr/bin/env Rscript
-#
-# USAGE: execute script from within the folder
-
-# 
-# emmacheck(t4,graph="yes",nresp={1,2,3,4})
-# wget https://cran.r-project.org/src/contrib/Archive/emma/emma_0.1-0.tar.gz
-# tar xf emma_0.1-0.tar.gz 
-# vim emma/R/emmacheck.R 
-
-suppressMessages(suppressWarnings(library("dplyr")))
-load("../../EMMA/t5") 
-source("../../EMMA/inter.R") 
-source("../../../../emma.src/emma/R/estimateModel.R")
-
-mse<- function(x){
-    g3.pred <- estimateModel(x,"no")[x$tested,]
-    g3.measured <- x$ypop
-    g3.diff <- g3.pred - g3.measured
-    g3.se <- g3.diff * g3.diff
-    g3.sum <- 0
-    g3.n <- 0
-    for (i in 1:ncol(g3.se)){
-        for (j in 1:nrow(g3.se)){
-            g3.sum <- g3.sum + g3.se[j,i]
-            g3.n <- g3.n + 1 
-        }
-    }
-    g3.mse<- g3.sum/g3.n
-    return (g3.mse)
-}
-#sprintf("MSE_t0: %f",mse(t0))
-sprintf("MSE_t1: %i %f",length(t1$tested),mse(t1))
-sprintf("MSE_t2: %i %f",length(t2$tested),mse(t2))
-sprintf("MSE_t3: %i %f",length(t3$tested),mse(t3))
-sprintf("MSE_t4: %i %f",length(t4$tested),mse(t4))

### 2022-11-02 Code/Statistics/scripts/mse-t.R

@@ -1,0 +1,74 @@
+#!/usr/bin/env Rscript
+#
+# USAGE: execute script from within the folder
+# measure the MSE of predictions for t=1,2,3,4
+
+# 
+# emmacheck(t4,graph="yes")
+# wget https://cran.r-project.org/src/contrib/Archive/emma/emma_0.1-0.tar.gz
+# tar xf emma_0.1-0.tar.gz 
+# vim emma/R/estimateModel.R
+
+suppressMessages(suppressWarnings(library("dplyr")))
+load("../../EMMA/t5") 
+source("../../EMMA/inter.R") 
+source("../../../../emma.src/emma/R/estimateModel.R")
+
+test.overfit<-function(x){
+    dat<-read.delim("../db_final.sorted.tsv") 
+    d.all <- dat  %>% dplyr::select ( ! avg1.G.:avg2.G.) 
+    d.po <- d.all %>% filter ( enr != 0 ) 
+    x.po <- d.po %>% mutate(v6C=vCal*60) %>% dplyr::select(conc,layr,vDOC,TDOC,v6C,TCal)
+    x.po <- x.po %>% mutate(vCal=v6C*1) %>% dplyr::select(conc,layr,vDOC,TDOC,vCal,TCal)
+    y.po <- d.po %>% dplyr::select(G,phd,layr,vCal)
+    input <- cbind(x.po,y.po)
+    input <- cbind(x$xpop,x$ypop)
+    fmla <- as.formula(paste(paste("data.matrix(input[,",ncol(x$xpop)+1,":",ncol(x$xpop)+ncol(x$ypop),"])"),"~", paste(colnames(x$xpop),collapse= "+")))
+    mars.po <- earth(fmla,degree=2,trace=0,minspan=1,data=input,keepxy=TRUE)
+    forecast <- predict(mars.po,newdata=x.po)
+    predicted <- data.frame(forecast)
+    rownames(predicted) <- rownames(x.po)
+    colnames(predicted) <- colnames(x$yspace)
+    g3.pred<-predicted
+    g3.measured <- y.po
+    g3.diff <- g3.pred - g3.measured
+    g3.se <- g3.diff * g3.diff
+    g3.sum <- 0
+    g3.n <- 0
+    for (i in 1:ncol(g3.se)){
+        for (j in 1:nrow(g3.se)){
+            g3.sum <- g3.sum + g3.se[j,i]
[…]

### 2022-11-04 Code/Statistics/scripts/mars.R
G to gamma in generation graphs

@@ -19,7 +19,7 @@ format(mars.all)
 
 d.emma <- d.all %>% filter ( enr != 0 ) 
 x.emma <- d.emma %>% mutate(vC6=vCal*60) %>% select(conc:layr,vDOC,TDOC,vC6,TCal)
-y.emma <- d.emma %>% select(G,phd,layr,vCal)
+y.emma <- d.emma %>% select(G,phd,layr,vCal) # %>% select (vCal) 
 input <- cbind(x.emma,y.emma)
 fmla <- as.formula(paste(paste("data.matrix(input[,",ncol(x.emma)+1,":",ncol(x.emma)+ncol(y.emma),"])"),"~", paste(colnames(x.emma),collapse= "+")))
 mars.emma <- earth(fmla,degree=2,trace=0,minspan=1,data=input,keepxy=TRUE)

### 2022-11-04 Thesis/chapter/061-results-emma.tex
results emma first good draft

@@
     \end{subfigure}
-    \caption{Each $\gamma$ (a) and $\rho$ (b) of each particle and each generation after initial selection process} 
+    \caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process} 
     \label{fig:emma-gen}
@@
 %%% EQUATION 
-Equations \ref{eq:emma-G3}-\ref{eq:emma-vcal3} and \ref{eq:emma-G4}-\ref{eq:emma-vcal4} represent the prediction functions at $t=3$ and $t=4$ rounded to 2 significant digits, respectively.
+%\subsubsection{Equation}
+Equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} and \ref{eq:emma-phd4}-\ref{eq:emma-vcal4} represent the prediction functions at $t=3$ and $t=4$ rounded to 2 significant digits, respectively.
 $h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
@@
 %
-The first thing to notice is that every prediction function of a generation depends on the same variables. 
+The first thing to notice is that prediction functions of each generation depend on the same variables. 
 %This means that the algorithm must decide on the variables which explain the most variance independent of optimization weights.
-This stems from the fact that the algorithm must chose a single minimal set of basis functions to predict all dependent variables. 
+This stems from the fact that the algorithm must chose a single minimal set of \gls{bf} to predict all dependent variables. 
 %
-Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as dependent variables rather unfortunate. %highly questionable. 
-%As the \gls{mars} algorithm is gready,
-Different independent variables compete to be in the prediction functions because of the greediness of the \gls{mars} algorithm. 
+%\td{Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as \textit{optimizands} rather unfortunate. %highly questionable. 
 %\td{This makes including $\lambda$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
-In equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} the coefficient have the same signs and differ by a factor of roughly 100.
-This fits the data well, but the positive influence of the layer count/number is counter intuitive 
-as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of pin holes going all the way trough the \gls{zro} layer. %pin hole density. 
-The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} 
-seem low, but considering the minimum value of the inter action of \num{36000} should not be under estimated. 
-%It's positive the hinge
-It is astonishing that the knot of the hinge function for equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} was chosen so low; 
-basically only including the influence of $\lambda=4$.
-On the positive site the calcination heating rate $v_{cal}$ (see equation \ref{eq:emma-vcal}) has been predicted perfectly within numerical precision.
-
-For each generation the \gls{mse} was calculated such that only samples were used which were available at that time. 
-It is 64, 158, 54 and 50 for $t=1,2,3,4$, respectively. 
-The high \gls{mse} can be explained because the prediction function is only a constant at $t=2$. 
-Appart from the second generation the \gls{mse} falls over time, which might be attributed to overfitting.
-The \gls{mse} for each generation was calculated between predicted values for pre-optimisation samples to check for overfitting, 
-but the the error sank with each generation (except for the second gen): 102, 118, 58, 50, respectively for $t=1,2,3,4$.
-
-It is interesting that although prediction functions for $t=3$ perfectly predicted $v_{cal}$ 
-the combined \gls{mse} for $t=4$ is lower. 
-%%% MAIN INFLUENCE 
-%Even without considering the large maximum of $T_{cal}$,
-
-\iffalse
-The coefficient for $T_{cal}$ is the largest for all equations. 
-Factoring in the large maximum value of $T_{cal}$ in contrast the other independent variables, 
-$T_{cal}$ has the by far the largest influence on the dependent variables. 
-The coefficient of the interaction of $layr$ and $T_{cal}$ is about a tenth in size, %interaction between?H
-but has the extra factor of $layr$ of up to 12, resulting in the products being in the same order of magnitude.
-I can be noted that the coefficient of the $layr\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient. 
-%%% EXPECTATION
-It should be doubted, though, that the $layr$ only appears as interaction term 
-together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
-\fi
+%As the \gls{mars} algorithm is greedy,
+%Different independent variables compete to be used as \gls{bf} in the prediction functions because of the greediness of the \gls{mars} algorithm. 
+%}
 
@@
 \end{align}
-%\fi
-%what was the best result? For each particle there is best and global best.
 
-%The calcination heating $v_{cal}$ rate has been predicted perfectly. 
-%\td{even though $v_{cal}$ doesn't appear in the prediction function, how is this possible?}
-%The number of layers $\lambda$ on the other hand was predicted poorly 
-%even though the conversion factor was $1$ and the prediction function dependent on $\lambda$.
+The coefficients in equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} have the same signs and differ by a factor of roughly 100.
+This fits the data well, but the positive influence of the layer count/number is counter intuitive 
+as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
+The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} 
+seem low, but - considering the minimum value of the interaction of \num{36000} - have a higher influence on $\rho_3$ and $\gamma_3$ than $h(6 - \lambda)$. 
+%It's positive the hinge
+It is astonishing that the knot of the hinge function for equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} was chosen so low; 
+basically only including the influence of $\lambda=4$.
+Meaning for equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} that the lowest layer count produces worse samples which is intuitive, but more layers don't improve the insulation. 
+On the positive side the calcination heating rate $v_{cal}$ (see equation \ref{eq:emma-vcal3}) has been predicted perfectly within numerical precision.
+
+%%% T=4
+The coefficient of equations \ref{eq:emma-phd4} and \ref{eq:emma-G4} show the same pattern 
+as equations \ref{eq:emma-phd3} and \ref{eq:emma-G3}: identical signs and factor 100. 
+The choice of \gls{bf} in combination with their coefficient signs of 
+(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) seem more plausible than (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
+$\lambda$ decreases $G$ and $\rho$ and additionally the lowest $\lambda$ increases the two \textit{optimizands}. 
+Highly interesting is the influence of $T_{cal}$ on the conductance of the sample. 
+The conductance increases with higher calcination temperature, ergo the resistance decreases contrary to expectations.
+It was expected that under \oc{400} the calcination does not fully \td{ablaufen} and 
+that therefore the resulting layer does not insulate. 
+Furthermore, the influence of $T_{cal}$ is the larges of all \gls{bf} on $\rho$ and $\gamma$.
+%This becomes clear when looking at the data.
+The coefficient of the interaction of $layr$ and $T_{cal}$ is about a tenth in size, 
+but has the extra factor of $layr$ of up to 12, resulting in the products being in the same order of magnitude.
+It can be noted that the coefficient of the $layr\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient. 
+%It should be doubted, though, that the $layr$ only appears as interaction term 
+%together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
+It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
+with $T_{cal}$ and $T_{DB}$.
+
+%%% MSE
+For each generation the \gls{mse} was calculated such that only samples 
+from the optimisation were used which were available at the time of prediction. 
+The \gls{mse} is 64, 158, 54 and 50 for $t=1,2,3,4$, respectively. 
+It is interesting that although prediction functions for $t=3$ perfectly predicted $v_{cal}$ 
+the combined \gls{mse} for $t=4$ is lower. 
+The high \gls{mse} at $t=2$ can be explained because the prediction functions are only constant values. 
+Apart from the second generation the \gls{mse} falls over time, which shows that the algorithm works but might be attributed to overfitting.
+%The \gls{mse} for each generation was also calculated between predicted values for pre-optimisation samples to check for overfitting, 
+The \gls{mse} for each generation's prediction function was also calculated with pre-optimisation samples, which are unseen data. 
+The error sank again with each generation (except for the second generation): 102, 118, 58, 50, respectively for $t=1,2,3,4$. 
+This means that the regularization method of the \gls{mars} algorithm in principle works on investigated samples. 
+\td{It should be noted, that the validation \gls{mse} for $t=1$ is much higher.}
+The high validation \gls{mse} (nearly 1.5 fold instead of circa 1 fold) for $t=1$ shows the poor prediction ability which improved.
+\td{why is \gls{mse} higher with higher values? No homoscedasticity ( equality of variance)?
+Or rather \gls{mse} at $t=2$ high because \gls{rf}s at $t=2$ poor and gen=2 samples are chosen with help of \gls{rf} at $t=2$? 
+}
+
+%%% PROBLEMS 
+The two main problems were too many independent variables and too many dependent variables. 
+Both seem closely related and overcomplicate the optimization but both come with their own implications. 
+Too many independent variables make it harder to distinguish variance due to random error from variance due to dependency. 
+This is mainly because of the curse of dimensionality \td{cite} which makes it hard to collect enough data for each dimension. 
+The main problem about too many independent variables is that the same set of \gls{bf}s will be used to predict all \textit{optimizands}.
+This leads to competition between the \gls{bf}s as not all dependent variables may depend on the same independent variables. 
+This effect is reinforced by the choice of two independent variables as dependent variables (IVDV). 
+Independent variables as dependent variables will likely be chosen in \gls{bf}s, 
+for including them in the \gls{rf} is a easy way to reduce the \gls{mse}.
+These \gls{bf}s then "take places" \td{(cf. musical chairs)} of \gls{bf}s predicting other dependent variables in the \gls{rf}. 
+This in turn can lead to wrong predictions and therefore inefficient choice of future samples.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimizands}
+The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ 
+were included as dependent variables with the objective to maximize with a relative weight of 0.05 each.
+The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
+Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
+%
+%Three major flaws behind this consideration became obvious with time: 
+%
+\
+\ds{
+(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
+The algorithm will tend to include those values into the prediction function for 
+all dependent variables and possibly exclude others which have more influence 
+on $\gamma$ and $\rho$ (see equations \ref{eq:emma-G4}? and \ref{eq:emma-phd4}?).
+%
+(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
+%
+(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
+\begin{itemize}
+    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
+heating rate was one of the dependent variables with the intention of minimizing the variable. 
+It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
+Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
+Overall there were too many variables involved for such a small dataset
+        that means that adding dependent variables influences \td{previous variables}
+\end{itemize}
+}
+\td{look at emma papers}
+\td{change G to gamma and write enr to every figure}
 
@@
 %\subsubsection{how did evolve over time?}
-
-%\iffalse
-%\fi
 
@@
 \fi
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%\subsubsection{what is best}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{influence of variable selection on outcome}
-The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ were included as dependent variable with the objective to maximize with a relative weight of 0.05 each.
-The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
-Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
-%
-Three major flaws behind this consideration became obvious with time: 
-%
-\todo{
-(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ ($C/h$ instead of $C/min$) and $\lambda$, respectively. 
-The algorithm will tend to include those values into the prediction function for 
-all dependent variables and possibly exclude others which have more influence 
-on $\gamma$ and $\rho$ (see equations \ref{eq:emma-G} and \ref{eq:emma-phd}).
-%
-(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
-%
-(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
-\begin{itemize}
-    \item MARS chooses same set from independent variables for predicting all dependent variables. 
-    \item flaws of MARS: all functions are dependent on same independent vars
-    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
-heating rate was one of the dependent variables with the intention of minimizing the variable. 
-It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS)
-It doesn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
-Overall there were too many variables involved for such a small dataset
-        that means that adding dependent variables influences \td{previous variables}
-\end{itemize}
-}
-
-\td{look at emma papers}
-\td{change G to gamma and write enr to every figure}
-\td{calculate MSE for predictions}

### 2022-11-05 Thesis/chapter/03-theoretical-background.tex
results emma first good draft
write about mars

--- 2022-10-16 Thesis/chapter/03-theoretical-background.tex
@@
 
-%\td{https://en.wikipedia.org/wiki/Thesis}
-\ds{what is it? What is it used for? How does it work? What different kinds are there? }
-\ds{what? how? why?}
-This chapter can be broken down into three sections. 
-The first section tries to shine light on the evolution of PV and give some background on \gls{cigs}.
-The middle section reads about material-scientific methods which were used during the practical part of this work. 
-The last and third part focuses on the information technological, algorithmic and analytical methods used to optimize and predict material properties.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Photovoltaics}
-%
-\subsubsection{Problems of current energy supply}
-The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
-and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
-will be exhausted within the next 100 years. 
-Even though this time period is not exact and highly dependent on detection methods of resources, 
-this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
-One viable option is \gls{pv}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{History of Photovoltaics}
-The photoelectric effect was first described in 1839 by french scientist Alexandre 
-Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel (the person after whom the unit is named).
-Another relevant piece of the \gls{pv} jigsaw was brought to light
-%discovered
-with the discovery of photo conductivity of selenium
-by British engineer Willouhgby Smith\cite{Smith1873Selenium}.
-In 1876 William Adams and Richard Day\cite{Adams1876Selenium} showed that 
-the energy of light can be directly converted into electrical energy by a bar of 
-selenium with attached platinum electrodes.
-And finally, in 1905 Einstein described the physical background of the photoelectric 
-effect with his light quantum theory\cite{einstein1905erzeugung}.
-In the 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space flight. 
-Eventually, the interest in photovoltaic and other alternative energy sources 
-rose - fuelled by the oil crisis in 1973 - 
-and the development of photovoltaic for the consumer market was boosted. 
-This development lead to a drop in 
-average price for \gls{pv} module from \$ 100 per watt in 1975 to \$ 4 per watt in 2007\cite{pagliaro2008flexible}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Photovoltaics Basics}
-The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
-the creation of an electron-hole pair and then its separation by the structure of the material.\cite{markvart2013principles}
-This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. Diodes are also 
-%This is often achieved through a p-n junction.\cite{breitenstein2013understanding}
-This is often achieved through a p-n junction.
-The n-type side has excess electrons and p-type side has excess electron holes. 
-If the n- and p-type are of the same basis material, they are called homojunctions (silicon); if not, heterojunctions e.g. \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}.\cite{breitenstein2013understanding}
-%
-The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
-Together with amorphous silicon 2010 over 88\% of all sold \gls{pv} where made of silicon\cite{breitenstein2013understanding}.
-A comprehensive overview over different \gls{pv} technologies can be found in \cite{markvart2013principles}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CIGS}
-\gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
-%It was 
-\ch{CuInSe2} and \ch{CuGaSe2} were first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen}.
-The potential use of \ch{CuInSe2} as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
-%Already in 1975 efficiencies of cells of over 10\% were achieved.\cite{kazmerski1976thin}
-Cells with efficiencies of over 10\% were achieved already by 1975.\cite{kazmerski1976thin}
-Today, 
-\gls{cigs} modules (multiple \gls{pv} cells in series) 
-reach efficiencies of up to 16\%\cite{feurer2017cigs},
-monocrystalline silicon \gls{pv} modules reach efficiencies of 14-20\%
-and polycrystalline silicon \gls{pv} modules 12-17\%\cite{mcevoy2011practical}.
-
-Just like CdTe, GaAs and amorphous silicon CIGS has much higher absorption coefficients 
-(lower penetration depth) of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}). 
-This is due to a direct band gap rather than an indirect band gap (like crystalline silicon). 
-These thin film \gls{pv}s not only use less material, but also can be used in flexible applications.
-
-\begin{table}[tbh]
-	\small
-    \center
-    \begin{tabular}{cccccc}
-        \hline
-        \hline
-		Material&   Type&    Band Gap [\ev{}]&    Wavelength [\nm{}]&    Absorption coef. $\alpha$ [\pcm{}]    &Penetration Depth [\um{}]\\
-        \hline
-		c-Si&   indirect&   1.12&   600&    \num{4000}&    2.5\\
-		c-Si&   indirect&   1.12&   1000&    \num{64}&    150\\
-		c-Si&   indirect&   1.12&   1100&    \num{3.5}&    290\\
-		a-Si&   direct&      1.7&    600&    \num{40000}&  0.25\\
-		CdTe&   direct&      1.45&    600&    \num{37000}&  0.3\\
-		GaAs&   direct&      1.42&    600&    \num{40000}&  0.2\\
-        \hline
-        \hline
-    \end{tabular}
-	\caption{data from \cite{mertens2015photovoltaik}}
-	\label{tab:cigs:alpha}
-%
-	\vspace{1cm}
-    \begin{tabular}{cccc}
-        \hline\hline
-		Empirical Formula&    Name&   Band Gap [\si{eV}{}]&    Abbreviation\\
-        \hline
-		\ch{CuInSe2}&       copper indium di selenide&  1.04&  CISe\\
-		\ch{CuInS2}&        copper indium di sulfide&  1.5&  CIS\\
-		\ch{CuGaSe2}&       copper gallium di selenide&  1.7&  CIGSe\\
-		\ch{CuGaS2}&        copper gallium di sulfide&  1.55&  CIGS\\
-        \hline\hline
-    \end{tabular}
-	\caption{band gaps of different chalcopyrites}
-	\label{tab:cigs}
-\end{table}
-
-\begin{figure}
-	\includegraphics[width=\textwidth]{./Pics/cigs.png}
-	\caption{Schematic layer sequence of a standard \ch{ZnO}/\ch{CdS}/\ch{Cu(In,Ga)Se2} thin-film solar cell.}
-	\label{fig:cigs}
-\end{figure}
-
-%\td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book (Recreated based on\cite{mertens2015photovoltaik}) or (Image source:\cite{mertens2015photovoltaik})}
-%\td{On the top of a \gls{cigs} cell there is a conducting and durchsichtige layer of \ch{ZnO}. 
-%Why is there this doped \ch{ZnO} layer?
-
-Amazingly, the band gap of CIGS can be varied between \ev{1} and \ev{1.7} by varying the indium gallium ratio.
-This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}). 
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In figure \ref{fig:cigs} the schematic layer sequence of a standard \gls{cigs} thin film cell is shown. 
-Typically a \um{1} thick molybdenum layer is deposited on soda lime glass. 
-The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in 112 direction\cite{hedstrom1993cigs}.
-A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporated from elemental sources controlled by a mass spectrometer.\cite{hedstrom1993cigs}
-The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
-The heterojunction is then completed by deposition of \ch{CdS} (typically \nm{50} thick).
-\ch{CdS} was earlier used as front contact, but now only acts as n-type wide-gap window and buffer. 
-\ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
-The \ch{ZnO} window layer (usually of thickness 50-\nm{70} is highly conductive (especially the \ch{Al} doped layer) and acts as front contact.
-
-%
-Instead of glass as substrate, steel and plastics (e.g. polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
-They both come with their own inconveniences. 
-Plastics generally have very low melting points which restrict preparation temperatures.
-Steel, on the other hand, is temperature resistant enough, but is an electric conductor. 
-The conductance of steel can be masked by a insulator layer (e.g. \ch{ZrO2}, \ch{Al2O3}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Materials and Their Analysis}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Zirconium oxide}
-Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
-This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
-It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
-The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
-when cooling and undergoing phase transition\cite{Nielsen2005}.
-It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
-Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3}). 
-"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Sol-Gel and Doctor Blading}
-%\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
-%
-\Gls{dbc} Doctor blade coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing, and ceramic industries.
-The roll to roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
-A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
-In roll-to-roll processes the substrate moves instead of the blade.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Sputtering}
-%SPUTTERING FREEWRITING: 
-%what is sputtering? \\
-Sputtering is the processes of highly energetic ions hitting a surface and atoms or molecules being expelled. 
-This is called a physical vapor deposition (PVD) technique. 
-PVD can be divided into activation by thermal energy and activation by energetic particle bombardment. 
-Sputtering is of the latter, which 
-is advantageous if substrates can't withstand high temperatures.
-%\td{what can it be used for?}\\
-Sputtering evolved from being a curious experiment in the middle of the 20th century to having various applications in research and engineering.
-Use cases vary from thin films depositions for \gls{pv}, for electrical circuits or for storage media such as CDs and DVDs 
-over sputter cleaning and etching to analysis.
-Advantages of 
-sputtered thin films include good adhesion to the substrate and good step coverage\cite{Swann1988}.
-
-\begin{figure}[htb]
-	\includegraphics[width=\textwidth]{./Pics/sputter0.png}
-    \caption{Propagation of energy in a dense cascade. Left graph: "Primary" shockwave. Right graph: "Thermal" pulse or "secondary" shockwave. Figure taken from Sigmund 1987\cite{sigmund1987}}
-	\label{fig:sputter}
-\end{figure}
-
-%\td{how does it work?}\\
-A high voltage is applied to 
-two parallel electrodes with low pressure gas in between. 
-The target acts as cathode and the substrate (holder) as anode (see figure \ref{fig:sputter}).
-%the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
-The cathode, then, emits electrons which collide with a gas particles (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
-Some gas particles may get ionized by the collision and the gas cations are accelerated to the cathode. 
-If a cation has enough energy it will bump off one or more atoms or molecules from the surface. 
-This happens by a cascade of momentum transfers, which can reach the surface again (see fig \td{from \cite{sigmund1987}}). 
-If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
-This sputtered particle travels unaffected by the electrical field perpendicular to the surface towards the substrate and condenses with other particles to form a layer.
-The pressure should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand 
-a minimum pressure is needed to keep the plasma "alive". 
-Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
-
-A magnetron can be placed behind the cathode (target) in order to trap ejected electrons close to the source. 
-This prevents high energy electrons from reaching the target and undoing the deposited layer and this also increases the probability of an electron colliding with an argon atom and ionizing it, increasing the yield.
-
-When oxygen or nitrogen are added to the  gas this is called reactive sputtering.
-Sputtered atoms will react with the gas and result in oxide or nitrides layers, respectively.
-The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning. 
-Meaning the target begin covered by an insulating layers which can lead to defects in the growing film\cite{Kelly2000}.
-
-The limitation of only being able to use conducting materials as targets can be circumvented by using a radio frequency electrical field. 
-This prevents a charge building up on the target. %\td{why is a charge?}
-Although RF sputtering is more versatile, DC sputtering is more common because of it's simpler system and economical reasons.
-%\td{sputtered particles are neutral and not influenced by the electrical field}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Scanning electron Microscopy}
-The history of \gls{sem} can be traced back to 1843 when Scottish clockmaker Alexander Bain filed a patent for dissecting an image by scanning.
-A detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}.
-\Gls{sem} is a microscopical technique which allows visualisation of surfaces with features in the nano meter regime. 
-While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
-This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to light\cite{Kaliva2020}.
-The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons. 
-Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
-Electrons originate from either \gls{feg}, where are strong electrical field rips electrons from the bulk, or from thermionic guns where the filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted.
-Electrons are then accelerated by a voltage of 2 to 40 kV and bundled into narrow beams\cite{Vernon2000} by lenses.
-A high \gls{mfp} is needed for electrons to travel from the source to the sample (and to the detector). 
-Thus, a very low pressure is in the inside. 
-In this work \gls{sem} was used as a preliminary way of checking the surface condition.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Infrared Absorption and Spectroscopy}
-%%% WHAT? 
-\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of \num{e-3} to \num{e-6}\m{}
-or wave numbers $\bar{\nu}$ of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
-In general, light is described as periodic \gls{em} wave 
-which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
-The relation of energy~$E$ of a photon, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
-\begin{align*}
-	E &= h \cdot \nu \\
-	\nu &= c/ \lambda \\
-	\bar{\nu} &= 1/\lambda,
-\end{align*}
-where $h$ is the Planck's constant.
-%In words: shorter wavelength (higher frequency) photons are more energetic.
-In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?+table});
-from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
-X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
-%Molecular vibrations can be separated in valence and deformation vibrations.
-%
-A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
-%
-The number of vibrations can therefore calculated as 
-\begin{align*}
-	F_V &= 3N - F_T - F_R = 3N - 6 \\
-	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
-\end{align*}
-Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
-Only vibrations that change the dipole moment of the molecule are \gls{ir} active.
-
-%\td{describe simple IR with monochromator}
-
-\paragraph{(Fourier Transform) Infrared spectrometer}
- A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
- In the two-beam-spectrometer the light is split, sent through the sample and a reference and one of the two beams is alternately sent through a monochromator to a detector (often a thermopile).
-%
-In the \gls{ft}\gls{ir} spectrometer the beam is sent through the sample, split and 
-reflected from a static and from a moving mirror, recombined and detected by a photo 
-multiplier (a device which transforms photons into electrical signals). 
-How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
-In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample.
-%
-When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967} of optical less dense material.
-
-%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
-%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
-
-\td{
-	IR around page 45;
-The absorbance intensity is dependent on wave length and molecule structure. 
-Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{X-Ray Diffraction}
-%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
-\gls{xrd} is used to study the crystalline structure of materials.
-Since X-rays wavelengths (\num{0.2} to \nm{10}) are comparable to the interatomic spacing of crystalline solids the beams get reflected and contain information about the structure\cite{Kaliva2020}.
-Each crystalline material has a discreet atomic structure, which upon irradiation with 
-X-rays causes constructive and destructive interference according to Bragg's law and generates unique diffraction patterns. 
-\Gls{xrd} diffraction plots of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad curve with a maximum extending over several degrees (2$\theta$).
-
-%\url{https://chem.libretexts.org/Courses/Franklin_and_Marshall_College/Introduction_to_Materials_Characterization__CHM_412_Collaborative_Text/Diffraction_Techniques/X-ray_diffraction_(XRD)_basics_and_application}\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Machine Learning and Statistics}
-\ds{
-statistics:
-	what is the difference between ml and stat? 
-		superficially very similar but different goals and diff rahmenbedingungen 
-    how can i use ANOVA 
-    linear regression 
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Why introduce machine learning to this project? 
-%I wanted to apply and delve into what I've been studying during my undergrad courses. 
-%This seemed like the perfect oppurtunity. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Is machine learning just hyped statistics? No! 
-		%\href
-		%{https://doi.org/10.1177\%2F1352458520978648}
-		%{Machine and deep learning in MS research are just powerful statistics – No}
-Although machine learning uses several statistical methods, their goal and frame conditions are different. 
-%\td{The goal of machine learning is to ???}
-
-%\begin{itemize}
-%	\item \td{let GPT-3 write}
-%	\item check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
-%	\item see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
-%	\item 
-%		\href
-%		{https://doi.org/10.1177\%2F1352458520978648}
-%		{Machine and deep learning in MS research are just powerful statistics – No}
-%\end{itemize}
-
-%\td{
-%\url{https://stats.stackexchange.com/questions/5026/what-is-the-difference-between-data-mining-statistics-machine-learning-and-ai}
-%In principle both \gls{ml} and statistics use math to get information out of data. 
-%AI might use machine learning to create "intelligent" acting (playing a game or driving a  car). 
-\Gls{ml} tries to predict unseen data points and statistics is a subfield of maths 
-which tries to get insight into a given data. 
-For example, in a statistical model, it is desirable to reduce the number of inputs. 
-This allows the statistician to better study how a change in the input variable can be 
-directly affected by the output variable.\cite{gontcharov2019}
-%pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
-%}
-%What is statistics, though, and what seperates it from \gls{ml}? 
-More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of of 
-\td{finding correlation from data, finding mathematical models to describe the data} 
-where as (classical) statistics is the domain of representing the data. 
-\td{talk about statistics, then the difference to Ml} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\td{if i want to learn about support vector machine, read chapter 4,7,8 from "Learning from Data" by Cherkassky\cite{cherkassky1998learning} (TUBib 726-1998)}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Artificial Inteligence and Machine Learning}
-%How can \gls{ai} and \gls{ml} be defined? 
-\Gls{ai} is a trans-disciplinary field with roots in logic, statistics, cognitive psychology, decision theory, neuroscience, linguistics, cybernetics, and computer engineering.\cite{howard2019artificial}
-The history of \gls{ai} goes back to the middle of the \nth{20} century. 
-Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
-\Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
-Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{howard2019artificial}. 
-One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
-(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
-%Another test ingenioused by Alan Turing, is that a human communicates with an unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
-Another test ingenioused by Alan Turing, is the imitation game\cite{turing1950imitation}, now a days known as Turing test.
-An interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
-\textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is on the interrogators side.
-The question is if \textbf{A} is replaced with a computer how the ratio of outcomes would deviate from the original ratio. 
-%
-%(in written form) and must judge who is the 
-%if they are dealing with a machine or a human being. 
-%
-%
-%\ds{It is easy for humans to come up with question to detect an AI, 
-%but when reading AI written articles\cite{gpt2020}, 
-%it's easy to see this test being passed in the near future.}
-%
-At the moment it's hard to imagine a computer getting a higher ratio than a human
-but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the future.
-
-But fear not, that doesn't mean that computers are sentient or more intelligent than humans\cite{searle1980,searle1999married} and certainly not that research is over. 
-AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
-It is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
-%Now, we can't - it's hard to - imagine to live without electricity. 
-Realms in which AI is gaining traction are: 
-%
-playing board games (and beating humans)\cite{Silver2017,Feng1999,Campbell2002}, 
-image recognition (very popular for medical diagnosis)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
-chemistry\cite{Westermayr2019,goh2017chemception,jha2018elemnet}, 
-cyber security\cite{Sarker2021},
-facial recognition (to prevent theft of toilet paper \cite{Andrews2017}),
-financial sector (as robo-advisors)\cite{Littman2021},
-natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021} 
-(which can also create code and pictures through scalable vector graphics (SVG))
-and even creative tasks like 
-creating non existing faces\cite{Mansourifar2020}, 
-create graphic artwork (DALL-E 2)\cite{Marcus2022} or 
-making video games\cite{Guzdial2016}.
-%
-It is nearly hard to find a field where \gls{ai} isn't used in some way. 
-This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
-certain fields get incorporated into \gls{ai} research and practice.
-Such that, after some time of general use it is no more considered \gls{ai} (e.g. spam filter or web searches).
-Google CEO Sundar Pichai even goes as far and said: 
-"AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}
-
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Machine Learning Methods}
-%
-%\todo{check out SVM and KRR}
-%
-\Gls{ml} is at the base of most \gls{ai}s.
-It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
-%
-There is a platitude of different machine learning methods: 
-they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
-An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
-%Two architecture which don't quite fit into this classification are Generative Adversarial Network (GAN) and jk
-Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
-%
-\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
-Artificial neurons (also called nodes), which are arranged in layers, 
-are connected to each of the neurons of previous and next layers
-and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
-are optimised during training. 
-%
-Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
-Other common architectures include linear regression, kernel ridge regression and support vector regression.
-There are also lesser know algorithms like 
-evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
-\gls{pso} algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simulta- neously\cite{Villanova2010}.
-%
-One advantage of evolutionary algorithms is that they start with a small data set
-and periodically request new data in order to solve the problem iteratively.
-%\td{This is exactly what I needed because every experiment is very time intensive.}
-
-A genetic algorithm (GA) is a search algorithm that uses principles of natural selection and genetics to optimize a search space.
-A GA starts with a population of randomly generated solutions, or chromosomes, and then proceeds to breed them together to create new solutions.
-The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes.
-This process is repeated until a satisfactory solution is found.\footnote{This paragraph was written by GPT\cite{Liu2021gpt} given the input "Introduction to genetic algorithms: "}
-
-\iffalse
-\Gls{ga} uses a starting population of size $p$ ($p \in$ \td{N$^+$}) where each experiment (or data point) 
-is represented by a fixed size genome of 0's and 1's in most cases. 
-Each individual is then given a fitness value. 
-New genomes are added and discarded from the population using 
-selection, mutation and crossover operations.
-%The best n ($n \in$ \td{N}) will be selected to produce offspring, 
-%whose genome is a combination of both genomes with potential mutations 
-%and a (mostly) random c
-\fi
-
-\Gls{pso} also uses a starting population of particles where each experiment (particle) 
-is represented by its independent and dependent variables. 
-It was originally inspired by the behaviour of bird flocks and fish schools\cite{Kennedy1995}.
-Each particle has an associated position and velocity. 
-Every movement across the search space is stochastic and influenced by its particle velocity and position as well as its and the swarm's best known position.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{EMMA}
-\Gls{emma} and \gls{mars}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Design of Experiment} %DOE
-%\epigraph{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}{Grahem C.
-Goodwin\cite{goodwin1977experiment}}
-%
-\begin{quote}
-	{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}
-	- {Grahem C. Goodwin\cite{goodwin1977experiment}}
-\end{quote}
-%
-In two cases a deliberate \gls{doe} is beneficial.
-If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
-If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.
-%Both encompass nearly all cases. 
-% 
-At the beginning of any experiment its constraints must be determined. 
-%
-Constraints for a given experiment include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
-%
-
-%FULL FACTORIAL
-A naive approach to an experiment design is the full factorial \gls{doe}.
-Each possible combination of discrete values is tested. 
-While this is the most informative design it will more often than not be infeasible due the curse of dimensionality\cite{cherkassky1998learning}.
-% 2-LVL FACTORIAL
-The 2-level factorial design provides an alternative with $2^d$ (where $d$ is the number of independent variables) experiments. 
-Drawbacks of 2-level factorial \gls{doe}s include no data about the inside of the search space and infeasibility for high dimensional problems.
-In a full factorial or 2-level factorial design most experiments are redundant and most resources will be spent exploring high-order interaction effects\cite{gunst2009fractional}, which are often minimal to non-existent.
-% RANDOM 
-In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
-%
-%A straight forward design can be to randomly chose a certain number of experiments from the search space. 
-%Alternatively, a subset of from the 2-level factorial design can be chosen, which is called a fractional factorial design. 
-When a subset is chosen from the factorial design, it is called a fractional factorial design. 
-% PLACKETT_BURMAN
-%, a fractional factorial \gls{doe}. 
-%A straight forward design can be to randomly chose a certain number of experiments from the search space. 
-%
-%
-The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 
-where the number of needed experiments $n$ is $n<d+4$ 
-(more precisely $n=(\lfloor d\div4\rfloor+1)\cdot4$, where $\lfloor x\rfloor$ denotes the floor function on $x$) 
-and each combination of levels for any pair of factors appears the same number of times. 
-% HAMMERSLEY 
-A drawback of 2-level factorial and random fractional designs is that the sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
-The Hammersley design\cite{viana2016tutorial,diwekar1997efficient} is based on the Hammersley sequence and produces space filling data points. 
-% LATIN HYPER CUBE
-The Latin hypercube \gls{doe}\cite{viana2016tutorial,diwekar1997efficient} is a type of orthogonal \gls{doe}, 
-which has the advantage that each level for each variable will be tested only once. 
-A Latin hypercube \gls{doe} can be also created such that data points more uniformly distribute over the search space. 
-Latin hypercube \gls{doe}s are mainly used in computer simulations which are purely deterministic and therefore have no error. 
-%"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
-%
-%Continuous state spaces must be accommodated by arbitrary discretization.
-%\cite{cohn1996neural}
-\iffalse
-%
-\td{For any 2-level factorial DOE applies: "The effect of any factor main effect (A, B, C) or interaction (AB, AC, BC, ABC) is the difference of two averages, the average of the responses correpsonding to +1 levels and the average of the responses corresponding to -1 levels.
-" - from Gunst2009\cite{gunst2009fractional}}
-
-DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, \\
-\url{https://doi.org/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}  \\
-maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}
-\fi
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Analysis of Variance} % ANOVA
-\Gls{anova} analyses the means by means of mincing variances.
-\td{at the basis of anova lies the F-test.}
-%of of the continuous outputs where inputs are categories. 
-The inputs of the model should be categorical and the outputs continuous. 
-The statistical significance of the experiment is determined by a ratio of two variances. 
-%This ratio is independent of several possible alterations to the experimental observations: 
-%Adding a constant to all observations does not alter significance. 
-%Multiplying all observations by a constant does not alter significance. 
-\Gls{anova} statistical significance results are independent of constant bias and 
-scaling errors as well as the units used in expressing observations. 
-\href{https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions}{(click here)}
-Addiitonal assumptions of \gls{anova}: groups and levels should be independent, 
-residual error should follow normal distribution, variance of groups should be equal. 
-\href{https://statsandr.com/blog/anova-in-r/}{(click here)}
-
-\textbf{Links}
-\url{https://www.scribbr.com/statistics/anova-in-r/} just make input categorical\\
-\url{https://pypi.org/project/pynova/}\\
-
-\iffalse
-\textbf{Assumptions of ANOVA}
-from \url{https://statsandr.com/blog/anova-in-r/}
-\begin{itemize}
-    \item variable type: continuous dependent variable and categorial qualitative independent variable (also called treatments or levels).
-The input variables are discretized an can therefore be seen as categorial.
-    \item Independence: groups and levels should be independent
-    \item Normality: the residual (that is the durchschnittliche dependance of uncontrollable variables ,like room temperature or humidity) should approximately follow a normal distribution. 
-    \item Equality of variance: variance in differenct groups should be equal (compare with homoscedasticity).
-    \item No outliers
-\end{itemize}
-\fi
+\input{chapter/030-theory-materials.tex}
+\input{chapter/031-theory-calculations.tex}

### 2022-11-05 Thesis/chapter/030-theory-materials.tex
write about mars

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\td{https://en.wikipedia.org/wiki/Thesis}
\ds{what is it? What is it used for? How does it work? What different kinds are there? }
\ds{what? how? why?}
This chapter can be broken down into three sections. 
The first section tries to shine light on the evolution of PV and give some background on \gls{cigs}.
The middle section reads about material-scientific methods which were used during the practical part of this work. 
The last and third part focuses on the information technological, algorithmic and analytical methods used to optimize and predict material properties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics}
%
\subsubsection{Problems of current energy supply}
The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
will be exhausted within the next 100 years. 
Even though this time period is not exact and highly dependent on detection methods of resources, 
this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
One viable option is \gls{pv}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{History of Photovoltaics}
The photoelectric effect was first described in 1839 by french scientist Alexandre 
Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel (the person after whom the unit is named).
Another relevant piece of the \gls{pv} jigsaw was brought to light
%discovered
with the discovery of photo conductivity of selenium
by British engineer Willouhgby Smith\cite{Smith1873Selenium}.
In 1876 William Adams and Richard Day\cite{Adams1876Selenium} showed that 
the energy of light can be directly converted into electrical energy by a bar of 
selenium with attached platinum electrodes.
And finally, in 1905 Einstein described the physical background of the photoelectric 
effect with his light quantum theory\cite{einstein1905erzeugung}.
In the 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space flight. 
Eventually, the interest in photovoltaic and other alternative energy sources 
rose - fuelled by the oil crisis in 1973 - 
and the development of photovoltaic for the consumer market was boosted. 
This development lead to a drop in 
average price for \gls{pv} module from \$ 100 per watt in 1975 to \$ 4 per watt in 2007\cite{pagliaro2008flexible}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Photovoltaics Basics}
The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
the creation of an electron-hole pair and then its separation by the structure of the material.\cite{markvart2013principles}
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. Diodes are also 
%This is often achieved through a p-n junction.\cite{breitenstein2013understanding}
This is often achieved through a p-n junction.
The n-type side has excess electrons and p-type side has excess electron holes. 
If the n- and p-type are of the same basis material, they are called homojunctions (silicon); if not, heterojunctions e.g. \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}.\cite{breitenstein2013understanding}
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
Together with amorphous silicon 2010 over 88\% of all sold \gls{pv} where made of silicon\cite{breitenstein2013understanding}.
A comprehensive overview over different \gls{pv} technologies can be found in \cite{markvart2013principles}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CIGS}
\gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
%It was 
\ch{CuInSe2} and \ch{CuGaSe2} were first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen}.
The potential use of \ch{CuInSe2} as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
%Already in 1975 efficiencies of cells of over 10\% were achieved.\cite{kazmerski1976thin}
Cells with efficiencies of over 10\% were achieved already by 1975.\cite{kazmerski1976thin}
Today, 
\gls{cigs} modules (multiple \gls{pv} cells in series) 
reach efficiencies of up to 16\%\cite{feurer2017cigs},
monocrystalline silicon \gls{pv} modules reach efficiencies of 14-20\%
and polycrystalline silicon \gls{pv} modules 12-17\%\cite{mcevoy2011practical}.

Just like CdTe, GaAs and amorphous silicon CIGS has much higher absorption coefficients 
(lower penetration depth) of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}). 
This is due to a direct band gap rather than an indirect band gap (like crystalline silicon). 
These thin film \gls{pv}s not only use less material, but also can be used in flexible applications.

\begin{table}[tbh]
	\small
    \center
    \begin{tabular}{cccccc}
        \hline
        \hline
		Material&   Type&    Band Gap [\ev{}]&    Wavelength [\nm{}]&    Absorption coef. $\alpha$ [\pcm{}]    &Penetration Depth [\um{}]\\
        \hline
		c-Si&   indirect&   1.12&   600&    \num{4000}&    2.5\\
		c-Si&   indirect&   1.12&   1000&    \num{64}&    150\\
		c-Si&   indirect&   1.12&   1100&    \num{3.5}&    290\\
		a-Si&   direct&      1.7&    600&    \num{40000}&  0.25\\
		CdTe&   direct&      1.45&    600&    \num{37000}&  0.3\\
		GaAs&   direct&      1.42&    600&    \num{40000}&  0.2\\
        \hline
        \hline
    \end{tabular}
	\caption{data from \cite{mertens2015photovoltaik}}
	\label{tab:cigs:alpha}
%
	\vspace{1cm}
    \begin{tabular}{cccc}
        \hline\hline
		Empirical Formula&    Name&   Band Gap [\si{eV}{}]&    Abbreviation\\
        \hline
		\ch{CuInSe2}&       copper indium di selenide&  1.04&  CISe\\
		\ch{CuInS2}&        copper indium di sulfide&  1.5&  CIS\\
		\ch{CuGaSe2}&       copper gallium di selenide&  1.7&  CIGSe\\
		\ch{CuGaS2}&        copper gallium di sulfide&  1.55&  CIGS\\
        \hline\hline
    \end{tabular}
	\caption{band gaps of different chalcopyrites}
	\label{tab:cigs}
\end{table}

\begin{figure}
	\includegraphics[width=\textwidth]{./Pics/cigs.png}
	\caption{Schematic layer sequence of a standard \ch{ZnO}/\ch{CdS}/\ch{Cu(In,Ga)Se2} thin-film solar cell.}
	\label{fig:cigs}
\end{figure}

%\td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book (Recreated based on\cite{mertens2015photovoltaik}) or (Image source:\cite{mertens2015photovoltaik})}
%\td{On the top of a \gls{cigs} cell there is a conducting and durchsichtige layer of \ch{ZnO}. 
%Why is there this doped \ch{ZnO} layer?

Amazingly, the band gap of CIGS can be varied between \ev{1} and \ev{1.7} by varying the indium gallium ratio.
This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}). 
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In figure \ref{fig:cigs} the schematic layer sequence of a standard \gls{cigs} thin film cell is shown. 
Typically a \um{1} thick molybdenum layer is deposited on soda lime glass. 
The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in 112 direction\cite{hedstrom1993cigs}.
A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporated from elemental sources controlled by a mass spectrometer.\cite{hedstrom1993cigs}
The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
The heterojunction is then completed by deposition of \ch{CdS} (typically \nm{50} thick).
\ch{CdS} was earlier used as front contact, but now only acts as n-type wide-gap window and buffer. 
\ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
The \ch{ZnO} window layer (usually of thickness 50-\nm{70} is highly conductive (especially the \ch{Al} doped layer) and acts as front contact.

%
Instead of glass as substrate, steel and plastics (e.g. polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
They both come with their own inconveniences. 
Plastics generally have very low melting points which restrict preparation temperatures.
Steel, on the other hand, is temperature resistant enough, but is an electric conductor. 
The conductance of steel can be masked by a insulator layer (e.g. \ch{ZrO2}, \ch{Al2O3}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Materials and Their Analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Zirconium oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
when cooling and undergoing phase transition\cite{Nielsen2005}.
It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3}). 
"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Sol-Gel and Doctor Blading}
%\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
%
\Gls{dbc} Doctor blade coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing, and ceramic industries.
The roll to roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
In roll-to-roll processes the substrate moves instead of the blade.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Sputtering}
%SPUTTERING FREEWRITING: 
%what is sputtering? \\
Sputtering is the processes of highly energetic ions hitting a surface and atoms or molecules being expelled. 
This is called a \gls{pvd} technique in contrast to chemical vapor deposition. 
\Gls{pvd} can be divided into activation by thermal energy and activation by energetic particle bombardment. 
Sputtering is of the latter, which 
is advantageous if substrates can't withstand high temperatures.
%\td{what can it be used for?}\\
Sputtering evolved from being a curious experiment in the middle of the 20th century to 
having various applications in research and engineering.
Use cases vary from thin films depositions for \gls{pv}, 
for electrical circuits or for storage media such as CDs and DVDs 
over sputter cleaning and etching to analysis.
Advantages of sputtered thin films include good adhesion to the substrate 
and good step coverage\cite{Swann1988}.

\begin{figure}[htb]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \includegraphics[width=\textwidth]{./Pics/sputter1.png}
        \caption{}
        \label{fig:sputter0}
    \end{subfigure}
    \hspace{1cm}
    \begin{subfigure}[t]{.3\textwidth}
        \includegraphics[width=\textwidth]{./Pics/sputter2.png}
        \caption{}
        \label{fig:sputter1}
    \end{subfigure}
%    \caption{Propagation of energy in a dense cascade. Left graph: "Primary" shockwave. Right graph: "Thermal" pulse or "secondary" shockwave. Figure taken from Sigmund 1987\cite{sigmund1969}}
    \caption{Schematic representation of the creation of sputter particles during sputter deposition. 
    (a) creation of ions in the chamber: 
        the top rectangle depicts the source/cathode/target, 
        the bottom rectangle the anode/substrate holder and 
        the lower rectangle the substrate to be sputtered. 
    (b) example series of collision processes leading to sputtering of atoms: 
        horizontal line represents the target surface, 
        the small circle a high energetic ion and 
        the large circles target particles. 
    }
	\label{fig:sputter}
\end{figure}

%\td{how does it work?}\\
A high voltage is applied to 
two parallel electrodes with low pressure gas in between. 
The target acts as anode and the substrate (holder) as cathode (see \td{figure \ref{fig:sputter}}).
%the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
The anode, then, emits electrons which collide with a gas particles (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
Some gas particles may get ionized by the collision and the gas cations are accelerated to the anode. 
If a cation has enough energy it will bump off one or more atoms or molecules from the surface. 
This happens by a cascade of momentum transfers, which can reach the surface again (see figure \ref{fig:sputter}). 
If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
This neutral sputtered particle travels unaffected by the electrical field perpendicular to the surface towards the substrate and condenses with other particles to form a layer.
The pressure should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand 
a minimum pressure is needed to keep the plasma "alive". 
Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.

A magnetron can be placed behind the cathode (target) in order to trap the plasma close to the source. 
This lowers the pressure needed to keep the plasma alive. 
Furthermore, magnetrons prevent high energy electrons from reaching the substrate and 
undoing the deposited layer and this also increases the probability of an electron 
colliding with an argon atom and ionizing it, increasing the yield.

When oxygen or nitrogen are added to the gas this is called reactive sputtering.
Sputtered atoms will react with the gas and result in oxide or nitrides layers, respectively.
The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning. 
Meaning the target begin covered by an insulating layers which can lead to defects in the growing film\cite{Kelly2000}.

The limitation of only being able to use conducting materials as targets can be circumvented by using a radio frequency electrical field. 
This prevents a charge building up on the target. %\td{why is a charge?}
Although RF sputtering is more versatile, DC sputtering is more common because of it's simpler system and economical reasons.
%\td{sputtered particles are neutral and not influenced by the electrical field}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Scanning electron Microscopy}
The history of \gls{sem} can be traced back to 1843 when Scottish clockmaker Alexander Bain filed a patent for dissecting an image by scanning. A detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}. 
\Gls{sem} is a microscopical technique which allows visualisation of surfaces with features in the nano meter regime. 
While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to light\cite{Kaliva2020}.
The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons. 
Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
Electrons originate from either \gls{feg}, where are strong electrical field rips electrons from the bulk, or from thermionic guns where the filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted. 
Electrons are then accelerated by a voltage of 2 to 40 kV and bundled into narrow beams\cite{Vernon2000} by lenses.
A high \gls{mfp} is needed for electrons to travel from the source to the sample (and to the detector). 
Thus, a very low pressure is in the inside. 
In this work \gls{sem} was used as a preliminary way of checking the surface condition.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Infrared Absorption and Spectroscopy}
%%% WHAT? 
\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of \num{e-3} to \num{e-6}\m{}
or wave numbers $\bar{\nu}$ of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
The relation of energy~$E$ of a photon, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is the Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?+table});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
%Molecular vibrations can be separated in valence and deformation vibrations.
%
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active.

%\td{describe simple IR with monochromator}

\paragraph{(Fourier Transform) Infrared spectrometer}
 A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
 In the two-beam-spectrometer the light is split, sent through the sample and a reference and one of the two beams is alternately sent through a monochromator to a detector (often a thermopile).
%
In the \gls{ft}\gls{ir} spectrometer the beam is sent through the sample, split and 
reflected from a static and from a moving mirror, recombined and detected by a photo 
multiplier (a device which transforms photons into electrical signals). 
How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample.
%
When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967} of optical less dense material.

%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.

\td{
	IR around page 45;
The absorbance intensity is dependent on wave length and molecule structure. 
Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{X-Ray Diffraction}
%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\gls{xrd} is used to study the crystalline structure of materials.
Since X-rays wavelengths (\num{0.2} to \nm{10}) are comparable to the interatomic spacing of crystalline solids the beams get reflected and contain information about the structure\cite{Kaliva2020}.
Each crystalline material has a discreet atomic structure, which upon irradiation with 
X-rays causes constructive and destructive interference according to Bragg's law and generates unique diffraction patterns. 
\Gls{xrd} diffraction plots of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad curve with a maximum extending over several degrees (2$\theta$).

%\url{https://chem.libretexts.org/Courses/Franklin_and_Marshall_College/Introduction_to_Materials_Characterization__CHM_412_Collaborative_Text/Diffraction_Techniques/X-ray_diffraction_(XRD)_basics_and_application}\\

### 2022-11-05 Thesis/chapter/031-theory-calculations.tex
write about mars

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Machine Learning and Statistics}
\ds{
statistics:
	what is the difference between ml and stat? 
		superficially very similar but different goals and diff rahmenbedingungen 
    how can i use ANOVA 
    linear regression 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Why introduce machine learning to this project? 
%I wanted to apply and delve into what I've been studying during my undergrad courses. 
%This seemed like the perfect oppurtunity. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Is machine learning just hyped statistics? No! 
		%\href
		%{https://doi.org/10.1177\%2F1352458520978648}
		%{Machine and deep learning in MS research are just powerful statistics – No}
Although machine learning uses several statistical methods, their goal and frame conditions are different. 
%\td{The goal of machine learning is to ???}

%\begin{itemize}
%	\item \td{let GPT-3 write}
%	\item check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
%	\item see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
%	\item 
%		\href
%		{https://doi.org/10.1177\%2F1352458520978648}
%		{Machine and deep learning in MS research are just powerful statistics – No}
%\end{itemize}

%\td{
%\url{https://stats.stackexchange.com/questions/5026/what-is-the-difference-between-data-mining-statistics-machine-learning-and-ai}
%In principle both \gls{ml} and statistics use math to get information out of data. 
%AI might use machine learning to create "intelligent" acting (playing a game or driving a  car). 
\Gls{ml} tries to predict unseen data points and statistics is a subfield of maths 
which tries to get insight into a given data. 
For example, in a statistical model, it is desirable to reduce the number of inputs. 
This allows the statistician to better study how a change in the input variable can be 
directly affected by the output variable.\cite{gontcharov2019}
%pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
%}
%What is statistics, though, and what seperates it from \gls{ml}? 
More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of of 
\td{finding correlation from data, finding mathematical models to describe the data} 
where as (classical) statistics is the domain of representing the data. 
\td{talk about statistics, then the difference to Ml} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\td{if i want to learn about support vector machine, read chapter 4,7,8 from "Learning from Data" by Cherkassky\cite{cherkassky1998learning} (TUBib 726-1998)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Artificial Inteligence and Machine Learning}
%How can \gls{ai} and \gls{ml} be defined? 
\Gls{ai} is a trans-disciplinary field with roots in logic, statistics, cognitive psychology, decision theory, neuroscience, linguistics, cybernetics, and computer engineering.\cite{howard2019artificial}
The history of \gls{ai} goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
\Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{howard2019artificial}. 
One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
%Another test ingenioused by Alan Turing, is that a human communicates with an unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
Another test ingenioused by Alan Turing, is the imitation game\cite{turing1950imitation}, now a days known as Turing test.
An interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
\textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is on the interrogators side.
The question is if \textbf{A} is replaced with a computer how the ratio of outcomes would deviate from the original ratio. 
%
%(in written form) and must judge who is the 
%if they are dealing with a machine or a human being. 
%
%
%\ds{It is easy for humans to come up with question to detect an AI, 
%but when reading AI written articles\cite{gpt2020}, 
%it's easy to see this test being passed in the near future.}
%
At the moment it's hard to imagine a computer getting a higher ratio than a human
but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the future.

But fear not, that doesn't mean that computers are sentient or more intelligent than humans\cite{searle1980,searle1999married} and certainly not that research is over. 
AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
It is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
%Now, we can't - it's hard to - imagine to live without electricity. 
Realms in which AI is gaining traction are: 
%
playing board games (and beating humans)\cite{Silver2017,Feng1999,Campbell2002}, 
image recognition (very popular for medical diagnosis)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
chemistry\cite{Westermayr2019,goh2017chemception,jha2018elemnet}, 
cyber security\cite{Sarker2021},
facial recognition (to prevent theft of toilet paper \cite{Andrews2017}),
financial sector (as robo-advisors)\cite{Littman2021},
natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021} 
(which can also create code and pictures through scalable vector graphics (SVG))
and even creative tasks like 
creating non existing faces\cite{Mansourifar2020}, 
create graphic artwork (DALL-E 2)\cite{Marcus2022} or 
making video games\cite{Guzdial2016}.
%
It is nearly hard to find a field where \gls{ai} isn't used in some way. 
This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
certain fields get incorporated into \gls{ai} research and practice.
Such that, after some time of general use it is no more considered \gls{ai} (e.g. spam filter or web searches).
Google CEO Sundar Pichai even goes as far and said: 
"AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Machine Learning Methods}
%
%\todo{check out SVM and KRR}
%
\Gls{ml} is at the base of most \gls{ai}s.
It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
%
There is a platitude of different machine learning methods: 
they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
%Two architecture which don't quite fit into this classification are Generative Adversarial Network (GAN) and jk
Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
%
\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
Artificial neurons (also called nodes), which are arranged in layers, 
are connected to each of the neurons of previous and next layers
and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
are optimised during training. 
%
Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
Other common architectures include linear regression, kernel ridge regression and support vector regression.
There are also lesser know algorithms like 
evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
\gls{pso} algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simulta- neously\cite{villanova2010function}.
%
One advantage of evolutionary algorithms is that they start with a small data set
and periodically request new data in order to solve the problem iteratively.
%\td{This is exactly what I needed because every experiment is very time intensive.}

A genetic algorithm (GA) is a search algorithm that uses principles of natural selection and genetics to optimize a search space. A GA starts with a population of randomly generated solutions, or chromosomes, and then proceeds to breed them together to create new solutions. The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes. This process is repeated until a satisfactory solution is found.\footnote{This paragraph was written by GPT\cite{Liu2021gpt} given the input "Introduction to genetic algorithms: "}

\iffalse
\Gls{ga} uses a starting population of size $p$ ($p \in$ \td{N$^+$}) where each experiment (or data point) 
is represented by a fixed size genome of 0's and 1's in most cases. 
Each individual is then given a fitness value. 
New genomes are added and discarded from the population using 
selection, mutation and crossover operations.
%The best n ($n \in$ \td{N}) will be selected to produce offspring, 
%whose genome is a combination of both genomes with potential mutations 
%and a (mostly) random c
\fi

\Gls{pso} also uses a starting population of particles where each experiment (particle) 
is represented by its independent and dependent variables. 
It was originally inspired by the behaviour of bird flocks and fish schools\cite{Kennedy1995}.
Each particle has an associated position and velocity. 
Every movement across the search space is stochastic and influenced by its particle velocity and position as well as its and the swarm's best known position.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{EMMA}
%\Gls{emma} and \gls{mars}
\Gls{emma} is an implementation of the \gls{pso} in the \texttt{R} programming language. 
Each time step the dependent variables for all possible input variable combinations
are predicted with the help of \gls{mars}. 
\Gls{mars} is a regression method introduced by Friedman's 1991 paper 
"Multivariate Adaptive Regression Splines"\cite{friedman1991multivariate}. 
The \texttt{CRAN} package which implements \gls{mars} is called \texttt{earth} due to \gls{mars} being trade marked\cite{mars}.
%%% MARS 
\gls{mars} is an extension of multivariate linear regression.
Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g. kernel functions), whose number of parameter quickly exceeds the practical for moderate dimensions (n>5). 
%to higher dimensions (n > 2) is straightforward in principle but difficult in practice. 
"These difficulties are related to the so-called “curse-of-dimensionality”, a phrase coined by Bellman (1961) to express the fact that exponentially increasing numbers of points are needed to densely populate Euclidean spaces of increasing dimension."\cite{friedman1988fitting}
The main advancements are the ability to fit (possible complex) interactions and non-linearities. 
%- "The key ingredient that advances this approach to general settings is the ability to fit (possibly complex) interactions among the variables through the product terms that are permitted to enter the approximation (9), if required by the fit."\cite{friedman1988fitting}
%% MARS MODEL SELECTION
%- "The approximation is developed in a forward/backwards stepwise recursive manner in analogy with the recursive partitioning approach. "\cite{friedman1988fitting}
The \gls{rf} is developed in a forward/backward stepwise recursive manner. 
During the forward recursion basis functions are added in pairs until a certain number of terms is reached. 
Then, the backwards algorithm regularizes the function by removing terms. 
The metric which decides if a term should be removed is called \gls{gcv} and was introduced by Wahba and Cravenin 1969\cite{wahba1979smoothing}.

- "Choosing a previous term for multiplication (10) is analogous to choosing a (previous) region to split in (7). The optimization over 2, and t in (10) is quite similar to finding the optimal splitting variable and split point for partitioning a region. "\cite{friedman1988fitting}

\begin{equation}
    GCV(M) = \frac{1}{N} \sum_{i=1}^{N} \frac{ \left(y_i - \hat{f}(x_i) \right)^2 } {\left( 1- \frac{C(M)}{N}\right)^2 }
\end{equation}
with $M$ being the number of terms, $N$ the number of data points, $d$ the degrees of freedom and
\begin{equation}
    C(M) = (d + 1)M + 1
\end{equation}

%%Advantages of \gls{mars} are its easy interpretability and flexibility to model non-linearity and of course ability to cope with high dimensional data\cite{villanova2010function}.

- the interpretability of $\hat{f}(x)$ is important to understand $f(x)$ spaces of increasing dimension."\cite{friedman1988fitting}
%
- the error is due to unmeasured and uncontrolled

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Design of Experiment} %DOE
%\epigraph{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}{Grahem C. Goodwin\cite{goodwin1977experiment}}
%
\begin{quote}
	{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}
	- {Grahem C. Goodwin\cite{goodwin1977experiment}}
\end{quote}
%
In two cases a deliberate \gls{doe} is beneficial.
If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.
%Both encompass nearly all cases. 
% 
At the beginning of any experiment its constraints must be determined. 
%
Constraints for a given experiment include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
%

%FULL FACTORIAL
A naive approach to an experiment design is the full factorial \gls{doe}.
Each possible combination of discrete values is tested. 
While this is the most informative design it will more often than not be infeasible due the curse of dimensionality\cite{cherkassky1998learning}.
% 2-LVL FACTORIAL
The 2-level factorial design provides an alternative with $2^d$ (where $d$ is the number of independent variables) experiments. 
Drawbacks of 2-level factorial \gls{doe}s include no data about the inside of the search space and infeasibility for high dimensional problems.
In a full factorial or 2-level factorial design most experiments are redundant and most resources will be spent exploring high-order interaction effects\cite{gunst2009fractional}, which are often minimal to non-existent.
% RANDOM 
In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
%
%A straight forward design can be to randomly chose a certain number of experiments from the search space. 
%Alternatively, a subset of from the 2-level factorial design can be chosen, which is called a fractional factorial design. 
When a subset is chosen from the factorial design, it is called a fractional factorial design. 
% PLACKETT_BURMAN
%, a fractional factorial \gls{doe}. 
%A straight forward design can be to randomly chose a certain number of experiments from the search space. 
%
%
The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 
where the number of needed experiments $n$ is $n<d+4$ 
(more precisely $n=(\lfloor d\div4\rfloor+1)\cdot4$, where $\lfloor x\rfloor$ denotes the floor function on $x$) 
and each combination of levels for any pair of factors appears the same number of times. 
% HAMMERSLEY 
A drawback of 2-level factorial and random fractional designs is that the sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
The Hammersley design\cite{viana2016tutorial,diwekar1997efficient} is based on the Hammersley sequence and produces space filling data points. 
% LATIN HYPER CUBE
The Latin hypercube \gls{doe}\cite{viana2016tutorial,diwekar1997efficient} is a type of orthogonal \gls{doe}, 
which has the advantage that each level for each variable will be tested only once. 
A Latin hypercube \gls{doe} can be also created such that data points more uniformly distribute over the search space. 
Latin hypercube \gls{doe}s are mainly used in computer simulations which are purely deterministic and therefore have no error. 
%"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
%
%Continuous state spaces must be accommodated by arbitrary discretization.
%\cite{cohn1996neural}
\iffalse
%
\td{For any 2-level factorial DOE applies: "The effect of any factor main effect (A, B, C) or interaction (AB, AC, BC, ABC) is the difference of two averages, the average of the responses correpsonding to +1 levels and the average of the responses corresponding to -1 levels. " - from Gunst2009\cite{gunst2009fractional}}

DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, \\
\url{https://doi.org/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}  \\
maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Analysis of Variance} % ANOVA
\Gls{anova} is a statistical test for estimating the influence of multiple categorical independent variables on a dependent numerical variable. 
At the heart of \gls{anova} lies the F-test. 
The F-test was ingeniused by Ronald Fisher, an important figure in modern statistics. 
The F-test uses a ratio of variances to determine if a null-hypothesis (observed difference is due to chance alone) is true. 
The variance in the enumerator measures the "between-group variability" and the denominator measures the "within-group variability".
%This ratio is unaltered by adding constants to all observations or scaling errors. 
This ratio is unaffected by units, scaling errors and constant bias. 
%
%\Gls{anova} analyses the means by means of mincing variances.
%of of the continuous outputs where inputs are categories. 
%The statistical significance of the experiment is determined by a ratio of two variances. 
%This ratio is independent of several possible alterations to the experimental observations: 
%Adding a constant to all observations does not alter significance. 
%Multiplying all observations by a constant does not alter significance. 
%\Gls{anova} statistical significance results are independent of constant bias and 
%scaling errors as well as the units used in expressing observations. 
%\href{https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions}{(click here)}
Additional assumptions of \gls{anova} include: groups and levels should be independent, 
residual error should follow normal distribution, variance of groups should be equal. 
%\href{https://statsandr.com/blog/anova-in-r/}{(click here)}

%\textbf{Links}
%\url{https://www.scribbr.com/statistics/anova-in-r/} just make input categorical\\
%\url{https://pypi.org/project/pynova/}\\

\iffalse
\textbf{Assumptions of ANOVA}
from \url{https://statsandr.com/blog/anova-in-r/}
\begin{itemize}
    \item variable type: continuous dependent variable and categorial qualitative independent variable (also called treatments or levels). The input variables are discretized an can therefore be seen as categorial.
    \item Independence: groups and levels should be independent
    \item Normality: the residual (that is the durchschnittliche dependance of uncontrollable variables ,like room temperature or humidity) should approximately follow a normal distribution. 
    \item Equality of variance: variance in differenct groups should be equal (compare with homoscedasticity).
    \item No outliers
\end{itemize}
\fi

### 2022-11-05 Thesis/chapter/061-results-emma.tex
write about mars

@@
 \td{change G to gamma and write enr to every figure}
+\td{in \cite{friedman1991multivariate} the model is said to work well on $\frac{N}{n}$ ratios (aka events per predictor varibale (EPV)) of 20-50. 
+EPV is around 5 for this model.
+Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
+Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
+"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
+}
 

### 2022-11-06 Thesis/chapter/031-theory-calculations.tex
MARS included to EMMA theory

@@
 \Gls{emma} is an implementation of the \gls{pso} in the \texttt{R} programming language. 
-Each time step the dependent variables for all possible input variable combinations
+Each time step the dependent variables for all possible input variable combinations %$\mathbf{x} = \{x_1,\cdots ,x_N\}$ 
 are predicted with the help of \gls{mars}. 
+The \gls{mars} \gls{rf} is then used to chose the next position for each particle.
 \Gls{mars} is a regression method introduced by Friedman's 1991 paper 
@@
 Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g.
-kernel functions), whose number of parameter quickly exceeds the practical for moderate dimensions (n>5).
+kernel functions), whose number of parameter quickly exceeds the practical for moderate dimensions ($n>5$).
+%
 %to higher dimensions (n > 2) is straightforward in principle but difficult in practice. 
-"These difficulties are related to the so-called “curse-of-dimensionality”, a phrase coined by Bellman (1961) to express the fact that exponentially increasing numbers of points are needed to densely populate Euclidean spaces of increasing dimension."\cite{friedman1988fitting}
+%"These difficulties are related to the so-called “curse-of-dimensionality”, a phrase coined by Bellman (1961) to express the fact that exponentially increasing numbers of points are needed to densely populate Euclidean spaces of increasing dimension."\cite{friedman1988fitting}
+%
 The main advancements are the ability to fit (possible complex) interactions and non-linearities. 
+%
 %- "The key ingredient that advances this approach to general settings is the ability to fit (possibly complex) interactions among the variables through the product terms that are permitted to enter the approximation (9), if required by the fit."\cite{friedman1988fitting}
@@
 %- "The approximation is developed in a forward/backwards stepwise recursive manner in analogy with the recursive partitioning approach. "\cite{friedman1988fitting}
+%
+%%% FORWARD MARS
 The \gls{rf} is developed in a forward/backward stepwise recursive manner. 
 During the forward recursion basis functions are added in pairs until a certain number of terms is reached. 
-Then, the backwards algorithm regularizes the function by removing terms. 
+Each pair consists of two hinge functions (also called rectifier functions) multiplied with a term already part of the \gls{rf} including the constant term.
+The maximum degree of interaction is 2 for \gls{emma}, but can be varied. 
+This means that only two basis functions can be multiplied (excluding the constant term) to form a subsequent term.
+Pairwise added hinge functions are of the simple form $h(x-c)$ and $h(c-x)$ where $h(a)= max(0,a)$ and with $x$ being an independent variable, $c$ being a constant and $a$ being any expression. 
+%%% BACKWARD EMMA
+Then, the backwards algorithm regularizes the function by removing individual terms. 
 The metric which decides if a term should be removed is called \gls{gcv} and was introduced by Wahba and Cravenin 1969\cite{wahba1979smoothing}.
-
-- "Choosing a previous term for multiplication (10) is analogous to choosing a (previous) region to split in (7).
-The optimization over 2, and t in (10) is quite similar to finding the optimal splitting variable and split point for partitioning a region.
-"\cite{friedman1988fitting}
 
@@
 \end{equation}
-with $M$ being the number of terms, $N$ the number of data points, $d$ the degrees of freedom and
+with $M$ being the number of terms, $N$ the number of data points, a correction term
 \begin{equation}
@@
 \end{equation}
+and penalty is $d=3$ for interactions larger than 1 and $d=2$ otherwise.
+The variable of the hinge functions and its knot location at the forward step and which terms to delete 
+at the backwards step are selected by minimizing \gls{gcv}. 
+The coefficients for each term are then chosen via regular \gls{mse} minimisation\cite{friedman1988fitting}.
 
 %%Advantages of \gls{mars} are its easy interpretability and flexibility to model non-linearity and of course ability to cope with high dimensional data\cite{villanova2010function}. 
-
-- the interpretability of $\hat{f}(x)$ is important to understand $f(x)$ spaces of increasing dimension."\cite{friedman1988fitting}
-%
-- the error is due to unmeasured and uncontrolled
+%- the interpretability of $\hat{f}(x)$ is important to understand $f(x)$ spaces of increasing dimension."\cite{friedman1988fitting}
 

### 2022-11-06 Thesis/chapter/061-results-emma.tex
MARS included to EMMA theory

@@
 Equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} and \ref{eq:emma-phd4}-\ref{eq:emma-vcal4} represent the prediction functions at $t=3$ and $t=4$ rounded to 2 significant digits, respectively.
-$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
+%$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
 The expression $h(\lambda-6)$ translates into layer count only has an influence if larger than 6 
@@
 Both seem closely related and overcomplicate the optimization but both come with their own implications. 
-Too many independent variables make it harder to distinguish variance due to random error from variance due to dependency. 
+Too many independent variables make it harder to distinguish variance due to random error (due to unmeasured and uncontrolled variables) from variance due to dependency of chosen dependent varibales. 
 This is mainly because of the curse of dimensionality \td{cite} which makes it hard to collect enough data for each dimension. 

### 2022-11-06 Code/Statistics/scripts/linreg.py
linreg add argparse

@@ -4,32 +4,59 @@ import numpy as np
 import pandas as pd
 import dfply
 from sklearn.linear_model import LinearRegression
+import argparse
 
-print_influence=1
-only_emma=1
-y_index=3 # 2=G; 3=phd; 7=layers; 10=vCal 
+parser = argparse.ArgumentParser(description ='Search some files')
+parser.add_argument('-i', '--influence',dest ='print_influence',action ='store_true', help ='print influence')
+parser.add_argument('-e', '--emma', dest ='only_emma',action ='store_true', help ='only use emma data')
+parser.add_argument('-y', '--yindex', dest ='y_index',action ='store', choices={'0','2','3','7','10'}, default='0', help ='y to fit: 0=all; 2=G; 3=phd; 7=layers; 10=vCal [default=0]')
+args = parser.parse_args()
+
 infile="../db_final.tsv"
 names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
+#
+def MSE(predicted,measured):
+    pred=np.array(predicted)
+    real=np.array(measured)
+    mse=np.square(pred-real).mean()
+    return mse
+#
 df=pd.read_csv(infile, skiprows=1, names = names,delimiter="\t")
-if only_emma:
+if args.only_emma:
     df = df >>dfply.mask(df.enr !=0)
 data=np.array(df)
 X=data[:,6:]
+X[4]=X[4]*60
 X_names=names[6:]
-if (y_index == 10) : 
-    y=data[:,y_index].reshape(len(data[:,y_index]),1)*60
+if (int(args.y_index) == 0):
+    y=data[:,[2,3,7,10]].reshape(len(data[:,[2,3,7,10]]),4)
+#elif (int(args.y_index) == 10) : 
+#    y=data[:,int(args.y_index)].reshape(len(data[:,int(args.y_index)]),1)*60
 else:           
-    y=data[:,y_index].reshape(len(data[:,y_index]),1)
+    y=data[:,int(args.y_index)].reshape(len(data[:,int(args.y_index)]),1)
+# try all Y
+#print(y)
+#exit()
+
 reg = LinearRegression().fit(X,y)
 y_pred = reg.predict(X)
-y_name = names[y_index]
-print("Lin regression for", y_name, "\tOnly EMMA data used:", only_emma)
+if args.y_index == 0: 
+    y_name = "all"
[…]

### 2022-11-06 Thesis/chapter/062-post-emma.tex
results and discussion planned
minor change results
results emma first good draft
minor text

@@
 \subsubsection{analyse data with other methods post optimization}
-Anova shows that the influence of TCal is significant as shown by the F 
 \begin{itemize}
     \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
-    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
-    \item grid search ???
-    \item KRR (???)
-    \item SVM (???)
+    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py
+    \item grid search
+    \item KRR (start with grid search) (???)
+    \item SVM (start with grid search) (???)
 \end{itemize}
@@
 
+Do multi linear reg like in Peprah et al. 2017\cite{peprah2017appraisal}.
+
+%MSE(data=all) =427
+%MSE(data=emma)=250
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
@@
 but for phd even lower than 0.1 \%
+Anova shows that the influence of TCal is significant as shown by the F
 
@@
 \subsubsection{KRR}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
@@
 \td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{PCR?}
+
 \fi
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsubsection{Comparison} 
+compare all methods. 
+How should I compare them? 
+What are the measurables.

### 2022-11-08 Thesis/chapter/01-introduction.tex
DOE und PSO
drueber lesen bis excl 04 characterization

@@
 it uses the suns energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
-it is fit to be used in futuristic Dyson spheres\cite{dyson1960search} which harness the power output of the whole sun.
+it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
 %
@@
 An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
-An insulating layer must therefore be applied to the steel substrate before any \gls{cigs} cells can be \td{applied}.
-A non-toxic material which is suitable for this application is \gls{zro}. 
+An insulating layer must therefore be applied to the steel substrate before any \gls{cigs} cells can be synthesised on top.
+A non-toxic material which is suitable for the insulation is \gls{zro}. 
 An economic and scalable method is doctor blading via a \gls{sg} process. 
@@
 In this work a dense, insulating and homogeneous layer is pursued. 
-\Gls{ml} can help to uncover complex non-linear relations, such as the \td{influence} of the 
-production factors on the thickness and resistance of the resulting layer.
+\Gls{ml} can help to uncover complex non-linear relations, such as the 
+dependence of the thickness and resistance of the resulting layer on production factors.
+%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
 The minimization of the conductance is performed with a particle swarm optimization 
@@
 
-\td{
+\ds{
 This work used a rather unconventional approach. 
@@
 }
+
+The remainder of this work is organized with section 
+%\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
+\ref{sec:theoretical} giving 
+some background on topics of \gls{pv}, material science and computational science which were used in this work.
+In sections \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
+Section \ref{sec:results} is split into three subsections: material specific results are presented in section \ref{sec:res-mat}, results regarding \gls{pso} in \label{sec:res-emma} and further analysis in section \ref{sec:res-post}.
+\td{Finally, section \ref{sec:outlook} discusses the outlook and next steps}

### 2022-11-08 Thesis/chapter/030-theory-materials.tex
drueber lesen bis excl 04 characterization

@@
 The middle section reads about material-scientific methods which were used during the practical part of this work. 
-The last and third part focuses on the information technological, algorithmic and analytical methods used to optimize and predict material properties.
+The last and third part focuses on the algorithmic, statistical and analytical methods used to optimize and predict material properties.
 
@@
 \subsection{Photovoltaics}
-%
-\subsubsection{Problems of current energy supply}
+%\subsubsection{Problems of current energy supply}
 The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
@@
 Even though this time period is not exact and highly dependent on detection methods of resources, 
-this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
+this number is rather small and brings us in \textit{zugzwang} to develop sustainable energy sources. 
 One viable option is \gls{pv}.
@@
 the creation of an electron-hole pair and then its separation by the structure of the material.\cite{markvart2013principles}
-This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. Diodes are also 
-%This is often achieved through a p-n junction.\cite{breitenstein2013understanding}
+This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
 This is often achieved through a p-n junction.
 The n-type side has excess electrons and p-type side has excess electron holes. 
-If the n- and p-type are of the same basis material, they are called homojunctions (silicon); if not, heterojunctions e.g. \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}.\cite{breitenstein2013understanding}
+If the n- and p-type are of the same basis material, they are called homojunctions (e.g.
+silicon); if not, heterojunctions e.g.
+\ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}.\cite{breitenstein2013understanding}
 %
-The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
-Together with amorphous silicon 2010 over 88\% of all sold \gls{pv} where made of silicon\cite{breitenstein2013understanding}.
-A comprehensive overview over different \gls{pv} technologies can be found in \cite{markvart2013principles}.
+The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still 
+have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
+In 2022 
+over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon).\cite{breitenstein2013understanding}
+%
+A comprehensive overview on different \gls{pv} technologies can be found in \cite{markvart2013principles}.
 
@@
     \end{tabular}
-	\caption{data from \cite{mertens2015photovoltaik}}
+    \caption{Photonic properties of several established \gls{pv} materials (data from \cite{mertens2020photovoltaik})}
 	\label{tab:cigs:alpha}
@@
     \end{tabular}
-	\caption{band gaps of different chalcopyrites}
+    \caption{Band gaps of different chalcopyrites (data from \cite{mertens2020photovoltaik})}
 	\label{tab:cigs}
@@
 	\includegraphics[width=\textwidth]{./Pics/cigs.png}
-	\caption{Schematic layer sequence of a standard \ch{ZnO}/\ch{CdS}/\ch{Cu(In,Ga)Se2} thin-film solar cell.}
+    \caption{Schematic layer sequence of a standard \ch{ZnO}/\ch{CdS}/\ch{Cu(In,Ga)Se2} thin-film solar cell.\cite{rau2013cigs}}
 	\label{fig:cigs}
 \end{figure}
-
-%\td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book (Recreated based on\cite{mertens2015photovoltaik}) or (Image source:\cite{mertens2015photovoltaik})}
-%\td{On the top of a \gls{cigs} cell there is a conducting and durchsichtige layer of \ch{ZnO}. 
-%Why is there this doped \ch{ZnO} layer?
 
@@
 It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
-Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3}). 
-"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.
+Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3})\cite{Nielsen2005}.
+%"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.
 
@@
 %
-\Gls{dbc} Doctor blade coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing, and ceramic industries.
-The roll to roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
+\Gls{db} coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing, and ceramic industries.
+The roll-to-roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
 A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
@@
 over sputter cleaning and etching to analysis.
-Advantages of sputtered thin films include good adhesion to the substrate 
+Advantages of sputter-deposited thin films include good adhesion to the substrate 
 and good step coverage\cite{Swann1988}.
@@
     \caption{Schematic representation of the creation of sputter particles during sputter deposition. 
-    (a) creation of ions in the chamber: 
+    (a)~creation of ions in the chamber: 
         the top rectangle depicts the source/cathode/target, 
-        the bottom rectangle the anode/substrate holder and 
-        the lower rectangle the substrate to be sputtered. 
+        the lower rectangle the anode/substrate holder and 
+        the bottom rectangle the substrate to be sputtered. 
     (b) example series of collision processes leading to sputtering of atoms: 
@@
 two parallel electrodes with low pressure gas in between. 
-The target acts as anode and the substrate (holder) as cathode (see \td{figure \ref{fig:sputter}}).
+The target acts as anode and the substrate (holder) as cathode (see figure \ref{fig:sputter0}).
 %the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
@@
 If a cation has enough energy it will bump off one or more atoms or molecules from the surface. 
-This happens by a cascade of momentum transfers, which can reach the surface again (see figure \ref{fig:sputter}). 
+This happens by a cascade of momentum transfers, which can reach the surface again (see figure \ref{fig:sputter1}). 
 If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
 This neutral sputtered particle travels unaffected by the electrical field perpendicular to the surface towards the substrate and condenses with other particles to form a layer.
-The pressure should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand 
+The pressure in the chamber should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand 
 a minimum pressure is needed to keep the plasma "alive". 
@@
 A magnetron can be placed behind the cathode (target) in order to trap the plasma close to the source. 
-This lowers the pressure needed to keep the plasma alive. 
+This lowers the pressure needed to keep the plasma "alive". 
 Furthermore, magnetrons prevent high energy electrons from reaching the substrate and 
-undoing the deposited layer and this also increases the probability of an electron 
+undoing the deposited layer.
+This also increases the probability of an electron 
 colliding with an argon atom and ionizing it, increasing the yield.
@@
 When oxygen or nitrogen are added to the gas this is called reactive sputtering.
-Sputtered atoms will react with the gas and result in oxide or nitrides layers, respectively.
-The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning. 
-Meaning the target begin covered by an insulating layers which can lead to defects in the growing film\cite{Kelly2000}.
+Sputtered atoms will react with the gas and result in oxide or nitride layers, respectively.
+The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning;
+meaning the target begin covered by an insulating layers which can lead to defects in the growing film\cite{Kelly2000}.
 
 The limitation of only being able to use conducting materials as targets can be circumvented by using a radio frequency electrical field. 
-This prevents a charge building up on the target. %\td{why is a charge?}
-Although RF sputtering is more versatile, DC sputtering is more common because of it's simpler system and economical reasons.
+This prevents charge from building up on the target. 
+Although radio frequency sputtering is more versatile, directional current sputtering is more common because of it's simpler system and economical reasons.
 %\td{sputtered particles are neutral and not influenced by the electrical field}
@@
 Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
-Electrons originate from either \gls{feg}, where are strong electrical field rips electrons from the bulk, or from thermionic guns where the filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted.
-Electrons are then accelerated by a voltage of 2 to 40 kV and bundled into narrow beams\cite{Vernon2000} by lenses.
+Electrons originate from either a \gls{feg}, where a strong electrical field rips electrons from the bulk, or from thermionic guns where the filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted.
+Electrons are then accelerated by a voltage of 2 to 40 kV and bundled into narrow beams by lenses\cite{Vernon2000}.
 A high \gls{mfp} is needed for electrons to travel from the source to the sample (and to the detector). 
@@
 \Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of \num{e-3} to \num{e-6}\m{}
-or wave numbers $\bar{\nu}$ of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
+or wave numbers $\bar{\nu}$ of 500 to \pcm{4000}) with molecules\cite{Schwedt2008}.
 In general, light is described as periodic \gls{em} wave 
 which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
+In other materials light moves with the velocity $v=\frac{c}{n(\lambda)}$, where $n(\lambda)$ is the refractive index which is a function of the wavelength. 
 The relation of energy~$E$ of a photon, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
@@
 %
-The number of vibrations can therefore calculated as 
+The number of vibrations can therefore be calculated as 
 \begin{align*}
@@
 
-\paragraph{(Fourier Transform) Infrared spectrometer}
+\paragraph{Fourier Transform Infrared Spectrometer}
  A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
@@
 %
-When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967} of optical less dense material.
+When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967} of the optical less dense material.
 
@@
 
-\td{
+\ds{
 	IR around page 45;

### 2022-11-08 Thesis/chapter/031-theory-calculations.tex
drueber lesen bis excl 04 characterization

@@
 		%{Machine and deep learning in MS research are just powerful statistics – No}
-Although machine learning uses several statistical methods, their goal and frame conditions are different. 
+Although \gls{ml} uses several statistical methods, their goal and frame conditions are different. 
 %\td{The goal of machine learning is to ???}
-
+%
 %\begin{itemize}
@@
 %\end{itemize}
-
+%
 %\td{
@@
 More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of of 
-\td{finding correlation from data, finding mathematical models to describe the data} 
-where as (classical) statistics is the domain of representing the data. 
+finding mathematical models to describe the data 
+whereas (classical) statistics is the domain of representing the data. 
 \td{talk about statistics, then the difference to Ml} 
@@
 %How can \gls{ai} and \gls{ml} be defined? 
-\Gls{ai} is a trans-disciplinary field with roots in logic, statistics, cognitive psychology, decision theory, neuroscience, linguistics, cybernetics, and computer engineering.\cite{howard2019artificial}
+\Gls{ai} is a trans-disciplinary field with roots in logic, statistics, cognitive psychology, decision theory, neuroscience, linguistics, cybernetics, and computer engineering\cite{howard2019artificial}.
 The history of \gls{ai} goes back to the middle of the \nth{20} century. 
@@
 %Another test ingenioused by Alan Turing, is that a human communicates with an unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
-Another test ingenioused by Alan Turing, is the imitation game\cite{turing1950imitation}, now a days known as Turing test.
+Another test \textit{ingenioused} by Alan Turing, is the imitation game\cite{turing1950imitation}, nowadays known as Turing test.
 An interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
@@
 This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
-certain fields get incorporated into \gls{ai} research and practice.
-Such that, after some time of general use it is no more considered \gls{ai} (e.g. spam filter or web searches).
+certain fields get incorporated into \gls{ai} research and practice,
+such that, after some time of general use it is no more considered \gls{ai} (e.g. spam filter or web searches).
 Google CEO Sundar Pichai even goes as far and said: 
@@
 %
-Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
+Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and are useful in quantum mechanics too\cite{westermayr2020combining}.
 Other common architectures include linear regression, kernel ridge regression and support vector regression.
@@
 Each particle has an associated position and velocity. 
-Every movement across the search space is stochastic and influenced by its particle velocity and position as well as its and the swarm's best known position.
+Every movement across the search space is 
+additionally to a stochastic term
+%stochastic and 
+influenced by its particle velocity and position as well as its and the swarm's best visited position.
 
@@
 Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g.
-kernel functions), whose number of parameter quickly exceeds the practical for moderate dimensions ($n>5$).
+kernel functions), whose number of parameter quickly exceeds the practical for moderate dimensional problems ($n>5$).
 %
@@
 %
-The main advancements are the ability to fit (possible complex) interactions and non-linearities. 
+The main advancements of \gls{mars} are the ability to fit (possibly complex) interactions and non-linearities. 
 %
@@
 The \gls{rf} is developed in a forward/backward stepwise recursive manner. 
-During the forward recursion basis functions are added in pairs until a certain number of terms is reached. 
-Each pair consists of two hinge functions (also called rectifier functions) multiplied with a term already part of the \gls{rf} including the constant term.
+During the forward recursion terms are added in pairs until a certain number of terms is reached. 
+Each pair consists of two hinge functions (also called rectifier functions) multiplied with a term already part of the \gls{rf} (including the constant term).
 The maximum degree of interaction is 2 for \gls{emma}, but can be varied. 
@@
 % 2-LVL FACTORIAL
-The 2-level factorial design provides an alternative with $2^d$ (where $d$ is the number of independent variables) experiments. 
+The 2-level factorial design provides an alternative with $2^d$ experiments (where $d$ is the number of independent variables). 
 Drawbacks of 2-level factorial \gls{doe}s include no data about the inside of the search space and infeasibility for high dimensional problems.
@@
 %
-The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 
+The \gls{pb}\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 
 where the number of needed experiments $n$ is $n<d+4$ 
-(more precisely $n=(\lfloor d\div4\rfloor+1)\cdot4$, where $\lfloor x\rfloor$ denotes the floor function on $x$) 
-and each combination of levels for any pair of factors appears the same number of times. 
+(more precisely $n=(\lfloor d\div4\rfloor+1)\cdot4$, where $\lfloor x\rfloor$ denotes the floor function on $x$).
+The \gls{pb} design ensures that each combination of levels for any pair of factors appears the same number of times. 
 % HAMMERSLEY 
-A drawback of 2-level factorial and random fractional designs is that the sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
+A drawback of 2-level factorial (incl. \gls{pb}) and random fractional designs is that the sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
 The Hammersley design\cite{viana2016tutorial,diwekar1997efficient} is based on the Hammersley sequence and produces space filling data points. 
@@
 which has the advantage that each level for each variable will be tested only once. 
-A Latin hypercube \gls{doe} can be also created such that data points more uniformly distribute over the search space. 
-Latin hypercube \gls{doe}s are mainly used in computer simulations which are purely deterministic and therefore have no error. 
+A Latin hypercube \gls{doe} can be also created such that data points distribute more uniformly over the search space. 
+Latin hypercube \gls{doe}s are mainly used in computer simulations which are purely deterministic and therefore are very precise.
 %"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
@@
 At the heart of \gls{anova} lies the F-test. 
-The F-test was ingeniused by Ronald Fisher, an important figure in modern statistics. 
+The F-test was \textit{ingeniused} by Ronald Fisher\cite{fisher1921on}, an important figure in modern statistics. 
 The F-test uses a ratio of variances to determine if a null-hypothesis (observed difference is due to chance alone) is true. 
 The variance in the enumerator measures the "between-group variability" and the denominator measures the "within-group variability".
-%This ratio is unaltered by adding constants to all observations or scaling errors. 
 This ratio is unaffected by units, scaling errors and constant bias. 
@@
 Additional assumptions of \gls{anova} include: groups and levels should be independent, 
-residual error should follow normal distribution, variance of groups should be equal. 
+residual error should follow normal distribution and variance within groups should be equal (homoscedasticity). 
 %\href{https://statsandr.com/blog/anova-in-r/}{(click here)}

### 2022-11-08 Thesis/chapter/04-experimental.tex
drueber lesen bis excl 04 characterization

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\td{COMMENT: solution age was not accounted for}
 In this section the used chemicals and substrates, experimental procedures and any used 
@@
 The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
-The steel foil was cut with a foil cutter into squwares fo the same dimensions. 
+The steel foil was cut with a foil cutter into squares of the same dimensions. 
 %, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
@@
 was added to \gls{ipo} and both were stirred for one hour. 
-These additives were added to influence pH and surface tension with the goal to influence the resulting layer \td{see Parvulescu2015}
+These additives were added to influence pH and surface tension with the goal to influence the resulting layer. % \td{see Parvulescu2015}
 The \gls{water}-\gls{ipo} mixture was added to the other solution and stirred over night. 
 The exact volumes can be taken from table~\ref{tab:rec1}.
-Unfortunately, this solution failed to produce anything near homogeneous solutions. 
+Unfortunately, this solution failed to produce anything near homogeneous layers. 
 Thus, an alternative solution was found.
@@
 \gls{pso} started - the stabilisation compound (\gls{acoh}) was changed to \gls{ipo}.
-The most promissing combination of solvent, chelating agent and stabilisation reagent was 
-\gls{buoh}, \gls{acac} and \gls{ipo}, which was used for the final optimisation.
-The main differences between the used recipe and mentioned by \cite{Hu2016} were 
+The most promising combination of solvent, chelating agent and stabilisation reagent was 
+\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimisation.
+The main differences between the used recipe and the recipe mentioned by \cite{Hu2016} were 
 precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
@@
 an Erichsen Coatmaster 510 film applicator with a heatable plate.
-The rest was doctor bladed on a glass plate, fixed with double sided adhesive tape and 
+The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
 partially heated with a heat gun.
@@
 \SI{0.05}{\milli\meter} steps and did not substantially alter the results.
-For the rest of the experiments a blade height of \SI{0.02}{\milli\meter} was used.
-The heatable vacuum plate 
+For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
+%
+Eventually, a heatable vacuum plate was used. It 
 had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where 
-underpressure could be applied to keep substrate in place (see 
-figure~\ref{fig:eric}). Most of them were covered with tape to increase the suction at the remaining ones. After setting the temperature of the heating plate to 
+underpressure could be applied to keep the substrate in place (see 
+figure~\ref{fig:eric}). 
+Most of them were covered with tape to increase the suction at the remaining ones. 
+After setting the temperature of the heating plate to 
 \SI{200}{\celsius}, the vacuum plate temperature (room temperature, \SI{40}{\celsius}, 
 \SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) and the 
-\gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}) were set, 
-the blade was put into position, the sample was placed on the vacuum plate and the vacuum 
+\gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
+the blade was put into its original position, the sample was placed on the vacuum plate and the vacuum 
 was switched on. 
@@
 liquid evenly. After evaporation of the solution, the vacuum was turned off, the 'blade 
-pusher' was put into initial position, the blade was removed and excess solution on the plate 
-was removed with a 
-wipe. The doctor bladed substrate was transferred to the \SI{200}{\celsius} heating plate and 
+pusher' was put into initial position, the blade was removed and excess solution 
+was removed from the plate with a wipe. 
+The doctor bladed substrate was transferred to the \SI{200}{\celsius} heating plate and 
 rested on there for \minutes{5}. 
@@
 were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
-This procedure was called HP1.
+This heating procedure was called HP1.
 The HP1 procedure was optimized for the available hardware by a colleague working on the 
@@
 All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
-\Gls{ft} \gls{ir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
+\Gls{ft}\gls{uv}\gls{vis}\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
 angle) were recorded with a Bruker Vertex 70 

### 2022-11-08 Thesis/chapter/05-computational-details.tex
drueber lesen bis excl 04 characterization

@@
 An evolutionary approach was chosen, namely a multi-objective Particle Swarm Optimization (PSO) with a multi-response
-Multivariate Adaptive Regression Splines (MARS) model\cite{Villanova2010,Kennedy1995,Breiman1997,Carta2011}.
+Multivariate Adaptive Regression Splines (MARS) model\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
 %
 "PSO is a population based heuristic inspired by the flocking behavior of birds. 
-To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{Villanova2010}
+To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
 %

### 2022-11-08 Thesis/chapter/063-discussion.tex
good draft results materials/pre-opt
drueber lesen bis excl 04 characterization

@@
 low TDOC results in lower conductivity... okay
+
+\td{"An important concept in inferential statistics is that the amount of information you can learn about a population is limited by the sample size.
+The more you want to learn, the larger your sample size must be." - by \url{https://blog.minitab.com/en/adventures-in-statistics-2/the-danger-of-overfitting-regression-models} }
+\td{"overfitting a regression model occurs when you attempt to estimate too many parameters from a sample that is too small." - same source}
+\td{"However, if the effect size is small or there is high multicollinearity, you may need more observations per term." -same source}
 
@@
 %plot predictions from EMMA and ML. or rather compare MAE
+
+\td{what are the reasons for large error?} 
+\begin{itemize} 
+    \item ageing of solution 
+    \item varying humidity
+    \item varying room temperature 
+    \item impurities in solutions
+    \item inhomogeneity of film 
+    \item measuring error
+    \item 
+\end{itemize}
+
+What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
+Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
+As the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
+
+\href{https://pubs.acs.org/doi/10.1021/ci0342472}{overfitting}
+\td{COMMENT: solution age was not accounted for}

### 2022-11-08 Thesis/chapter/030-theory-materials.tex
FTIR to FTUVVisIR

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Infrared Absorption and Spectroscopy}
+\subsubsection{UV/Vis/NIR Spectroscopy}
 %%% WHAT? 
-\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of \num{e-3} to \num{e-6}\m{}
-or wave numbers $\bar{\nu}$ of 500 to \pcm{4000}) with molecules\cite{Schwedt2008}.
+\Gls{uv}/\gls{vis}/\gls{nir} spectroscopy is a molecular spectroscopic method using 
+interactions of \gls{uv}, \gls{vis} and \gls{nir} light 
+(wavelengths $\lambda$ of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
 In general, light is described as periodic \gls{em} wave 
@@
 %In words: shorter wavelength (higher frequency) photons are more energetic.
-In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?+table});
+In practice the spectrum of \gls{em} waves is sectioned into different ranges; % (\td{see figure?+table});
 from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
@@
 %Molecular vibrations can be separated in valence and deformation vibrations.
-%
+
+% UVVis
+Two prerequisites need to be fulfilled in order for a \gls{uv}\gls{vis} photon to be 
+absorbed by a molecule or atom.
+Firstly, the energy must be the same as the difference between two electronic states, a lower populated and a higher empty orbital. 
+The electron will then be excited into a energetically higher orbital.
+Secondly, the spin state of both states has to be the same otherwise the transition is "forbidden" and the absorption is extremely unlikely.
+
+% IR
+\Gls{ir} photons interact with molecular vibrations, which is only a part of the degrees of freedom of a molecule.
 A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
@@
 Only vibrations that change the dipole moment of the molecule are \gls{ir} active. 
+The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes. 
+These transition are mostly "forbidden" quantum mechanically and allow analysis of bulk matter without extensive preparation
+due to the deep penetration depth of \gls{nir} light\cite{bec2019breakthrough}.
 
@@
 
-\paragraph{Fourier Transform Infrared Spectrometer}
- A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
- In the two-beam-spectrometer the light is split, sent through the sample and a reference and one of the two beams is alternately sent through a monochromator to a detector (often a thermopile).
+\paragraph{Fourier Transform Spectrometer}
+ %A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
+In the two-beam-spectrometer the light emitted from the light source is split, 
+sent through the sample and the reference and one of the two beams is alternately 
+sent through a monochromator to a detector (often a thermopile).
 %
-In the \gls{ft}\gls{ir} spectrometer the beam is sent through the sample, split and 
+In the \gls{ft} spectrometer the beam is sent through the sample, split and 
 reflected from a static and from a moving mirror, recombined and detected by a photo 
@@
 How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
-In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample.
+In a \gls{ft} spectrometer the reference has to be measured before the sample.
 %
-When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967} of the optical less dense material.
+When the refractive index of two layers differ, light can be used to measure the thickness\cite{Dumin1967} of the optical less dense material.
 

### 2022-11-08 Thesis/chapter/04-experimental.tex
experiment fertig druebergelesen

@@
 All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
-\Gls{ft}\gls{uv}\gls{vis}\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
+\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
 angle) were recorded with a Bruker Vertex 70 
@@
 \subsection{Pre-optimisation}\label{sec:exp-preopt}
-\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
-\td{Screening}
+%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
+%\td{Screening}
+%The main part of the screening pre-optimisation samples were optimized via biotic reinforcement learning (i.e. my brain). 
+The main part of all samples (around 90\%) were pre-optimization samples, 
+from which the bulk were screening experiments optimized via biotic reinforcement learning 
+(i.e. my brain) in order to obtain reasonable constraints for pre-optimization. 
 %Initially, glass plates were doctor bladed manually with aquatic solution and calcinated 
@@
 temperature. The bounds of the process variables were then explored in a preliminary study 
-using the Plackett-Burman \cite{Plackett1946} design implemented in the \texttt{python3} 
+using the Plackett-Burman\cite{Plackett1946} design implemented in the \texttt{python3} 
 library \texttt{pyDOE}. With 
@@
 as nominal and extreme values for 
-relative concentration of Zr $c_{Zr}$, number of layers $n_{l}$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively.
+relative concentration of Zr $c_{zr}$, number of layers $\lambda$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively.
 After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see table \ref{tab:pre-opt1}).
@@
 	%		&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
-			$c_{Zr}$	&$n_l$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
+			$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
 			\hline
@@
 		\centering
-		\subcaption{Hand picked experiments}
+        \subcaption{Hand picked experiments; $^*$varied stabilisation agent}
 		\label{tab:pre-opt2}
@@
 			\hline\hline
-			$c_{Zr}$	&$n_l$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
+			$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
 	%conc	&layers	&$v_{\textrm{DB}}$	&$T_{\textrm{DB}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\
@@
 	1	&9	&18	&80	&240	&400	\\
-	4*	&6	&14	&60	&240	&500	\\
-	4*	&6	&14	&60	&240	&500	\\
-	4*	&6	&14	&60	&240	&500	\\
+	4$^*$	&6	&14	&60	&240	&500	\\
+%	4$^\dagger$	&6	&14	&60	&240	&500	\\
+%	4$^\ddagger$	&6	&14	&60	&240	&500	\\
 			\hline
@@
 \gls{ipo} because of much better solution stability.
-The up to this moment best process was chosen to be tested with \ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
-%\td{As the sample showed the best all ex were proceeded with ipo as stabilatin agent. }
-The sample produced with \gls{ipo} as stabilization agent showed comparable passivation results and better stability. Therefore \gls{ipo} was used  as stabilisation in further experiments.
-After 
-%a fitting recipe was found and 
-the boundaries were fixed the process variables to 
-produce an insulating layer was examined. 
+The - up to this moment - best process was chosen to be tested with 
+\ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
+%\td{As the sample showed the best all ex were proceeded with ipo as stabilisation agent. }
+The sample produced with \gls{ipo} as stabilization agent 
+showed comparable passivization results and better stability. 
+Therefore \gls{ipo} was used  as stabilisation in further experiments.
+After the boundaries of the solution were fixed 
+the process variables to produce an insulating layer was examined. 
 %There were many variables which had to be taken into account. 
@@
         \hline\hline
-		$c_{Zr}$	&$n_l$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
+		$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
 %        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\

### 2022-11-08 Thesis/chapter/05-computational-details.tex
experiment fertig druebergelesen

--- 2022-10-24 Thesis/chapter/05-computational-details.tex
@@
 \label{sec:eval}
-Reading list
-\begin{itemize}
+%Reading list
+%\begin{itemize}
     %\item https://de.wikipedia.org/wiki/Globaler_F-Test
@@
     %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
-    \item 
-    \item 
-    \item 
-\end{itemize}
+%    \item 
+%\end{itemize}
 %\td{describe problem and solution found}
@@
 from a sample in one representative number. 
-The average of each conductance would be an obvious choice but difficult to represent a 
-sample correctly since the possible values of conductance span accross several magnitudes.
-So the average of logarithms of conductances is the next nearby ansatz.
-\todo{why didn't i just take this?}
-\td{L2 norm because it might be easier to compare to other methods. }
-\td{inspired by euclidean norm/L2 distance from ideal case} 
-\td{wanted to put more weight on bad shunts}
-\td{plot avg, avg(log), avg(log-13)}
-
+%
+%\todo{why didn't i just take this?}
+%\td{L2 norm because it might be easier to compare to other methods. }
+%\td{inspired by euclidean norm/L2 distance from ideal case} 
+%\td{wanted to put more weight on bad shunts}
+%\td{plot avg, avg(log), avg(log-13)}
+%
 For every I-V curve (aluminium dot) the gradient $g$ at $V=0$ is calculated by taking 
 each $n=5$ points after and before the origin at least $d=2$ points distance (which boils
-down to the values from \SI{0.02}{\volt} to \SI{0.07}{\volt}) , averaging their V and I values 
-and calculating
+down to the values from \SI{0.02}{\volt} to \SI{0.07}{\volt}), 
+averaging their V and I values and calculating
 \begin{equation}
@@
 \end{equation}
-As a measure of conductance a distance D from an ideal non-conducting case. The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
+%
+The average of each conductance would be an easy and naive choice but difficult to represent a 
+sample correctly since the possible values of conductance span across several magnitudes.
+So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
+%
+In order to make the metric closer and better comparable to the \gls{mse} the average of the squared difference 
+to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms. 
+%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
+%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
+%and the mean of all conductances was taken
+%
 \begin{equation}
-	D = \sum_i^N \frac{ -log_{10}(g_i) - 13}{N}
-	\label{eq:D}
+    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
+	\label{eq:gamma}
 \end{equation}
-Another measure is the density of shorted species $\rho_{s}$ is calculated in following way:
+Another measure is the density of shorted species $\rho$, calculated in following way:
 \begin{equation}
@@
 \begin{equation}
-	\rho_s = \sum_i^N \frac{s_i}{N}
+	\rho = \sum_i^N \frac{s_i}{N}
 	\label{eq:rho}
 \end{equation}
-Other estimates of the conductance are the averages:
-\begin{equation}
-	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
-\end{equation}
-
-\begin{equation}
-	G_2 =  \sum_i^N \frac{log(g_i)}{N}
-\end{equation}
+%Other estimates of the conductance are the averages:
+%\begin{equation}
+%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
+%\end{equation}
+%
+%\begin{equation}
+%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
+%%\end{equation}
 
@@
 \label{sec:ss}
-An evolutionary approach was chosen, namely a multi-objective Particle Swarm Optimization (PSO) with a multi-response
-Multivariate Adaptive Regression Splines (MARS) model\cite{Villanova2010,Kennedy1995,Breiman1997,Carta2011}.
+An evolutionary approach was chosen, namely a multi-objective 
+\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
 %
-"PSO is a population based heuristic inspired by the flocking behavior of birds. 
-To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{Villanova2010}
+%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
+%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
 %
-Initially the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
+Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
 Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
@@
 		\hline
-		Zr(PrO)$_4$ conc. [21 g/L]	&layers	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
+        $c_{zr}$ [21 g/L]	&$\lambda$	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
 		\hline
@@
 
-The first step is to select an initial population (ensemble of experiments), which is chosen randomly from the population space. 
-The samples are made, measured and evaluated according to section \ref{sec:exp} and the distance $D$ (see eq.
-\ref{eq:D}), $\rho_s$ (see eq.
+The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $\lambda$ and $v_{cal}$, which all should be minimized except $v_{cal}$.
+The next step is to select an initial population (ensemble of experiments), which is chosen randomly from the population space. 
+The experiments are executed, measured and evaluated according to section \ref{sec:exp} and $\gamma$ (see eq.
+\ref{eq:gamma}), $\rho_s$ (see eq.
 \ref{eq:rho}), $n_{layers}$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program.
-The program uses this data to estimate a response for each output variable (and to choose a fraction of the initial population which is allowed to propagate).
+\td{The program, then, uses this data to estimate a response for each output variable (and to choose a fraction of the initial population which is allowed to propagate).
 The response variables for the entire population space is calculated. 
+}
 The current population - each of the particles independently - moves towards the optimum solution.

### 2022-11-09 Thesis/chapter/05-computational-details.tex
first draft comp details

@@
 		\hline
-        $c_{zr}$ [21 g/L]	&$\lambda$	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
+        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$\lambda$	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
 		\hline
@@
 	\end{tabular}
-	\caption{Discrete levels of each input parameter \td{are concentrations correct?}}
+	\caption{Discrete levels of each input parameter }
 	\label{tab:input}
@@
 
-The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $\lambda$ and $v_{cal}$, which all should be minimized except $v_{cal}$.
-The next step is to select an initial population (ensemble of experiments), which is chosen randomly from the population space. 
-The experiments are executed, measured and evaluated according to section \ref{sec:exp} and $\gamma$ (see eq.
-\ref{eq:gamma}), $\rho_s$ (see eq.
-\ref{eq:rho}), $n_{layers}$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program.
-\td{The program, then, uses this data to estimate a response for each output variable (and to choose a fraction of the initial population which is allowed to propagate).
-The response variables for the entire population space is calculated. 
+The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $\lambda$ and $v_{cal}$, 
+where $\gamma$, $\rho$ and $\lambda$ are to be minimized and $v_{cal}$ to be maximized.
+%which all should be minimized except for $v_{cal}$.
+The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
+The experiments are executed, measured and evaluated according to section 
+\ref{sec:exp} and the responses $\gamma$ (see eq. \ref{eq:gamma}), $\rho_s$ (see eq. \ref{eq:rho}), 
+$n_{layers}$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in 
+\oc{}/\minutes{}) are supplied to the program. 
+The program, then, uses this data to estimate a response for each output variable 
+for the entire population space.
+(and to choose a fraction of the initial population which is allowed to propagate).
+\td{
+%The response variables for the entire population space is calculated. 
 }
-The current population - each of the particles independently - moves towards the optimum solution.
-The population for the next time step is outputted and the experiments are again executed, measured and evaluated.
+The current population - each of the particles independently - 
+have random velocity vector associated to them which is directed to the best predicted sample. 
+%moves towards the optimum solution.
+The population for the next time step is generated and the experiments are again executed, measured and evaluated.
+Each time step thus includes experiment identification, solution preparation, coating deposition and layer analysis.
 
-\td{system behavior are discussed in Modeling the Results.
+\ds{system behavior are discussed in Modeling the Results.
 Algorithm and Coating Features. The theoretical efficiency
@@
 coating deposition, and spot analysis.
-Figure 2a presents the laser scanner measurement of a spot
-}\cite{Carta2011}
-%\subsection{EMMA Propagation}
-%\begin{table}[htb]
-%	\centering
-%	\begin{tabular}{ccccccc}
-%		\hline
-%		\hline
-%conc	&layers	&vDOC	&TDOC	&vCal	&Tcal	&	\\
-%		\hline
-%1	&10	&5	&20	&120	&400	&\\
-%1	&4	&0.1	&20	&120	&500	&\\
-%5	&10	&0.1	&20	&120	&500	&\\
-%5	&4	&5	&20	&480	&400	&\\
-%1	&5	&5	&80	&120	&500	&\\
-%1	&10	&1	&80	&480	&400	&\\
-%5	&5	&1	&80	&120	&400	&\\
-%5	&10	&5	&80	&480	&500	&\\
-%2	&8	&0.5	&40	&360	&470	&\\
-%2	&6	&2	&40	&360	&430	&\\
-%		\hline
-%%4	&12	&-	&-	&-	&-&\\
-%1	&4	&12	&70	&120	&500	&\\
-%1	&9	&18	&80	&240	&400	&\\
-%%2	&5	&18	&70	&-	&-		&\\
-%4	&6	&14	&60	&240	&500	&\\
-%4	&6	&14	&60	&240	&500	&\\
-%4	&6	&14	&60	&240	&500	&\\
-%		\hline
-%2	&10	&20	&40	&120	&500	&6113\\
-%3	&8	&18	&70	&1080	&300	&2850\\
-%3	&6	&10	&50	&1080	&400	&5526	\\
-%%3	&10	&14	&50	&600	&500	&-7374	\\
-%3	&10	&16	&80	&120	&500	&6554	\\
-%4	&6	&16	&80	&1080	&300	&2947	\\
-%3	&12	&12	&80	&840	&500	&8318	\\
-%3	&10	&14	&50	&600	&500	&7374	\\
-%5	&6	&10	&60	&1080	&400	&5648	\\
-%5	&10	&20	&60	&360	&300	&3956	\\
-%5	&12	&14	&60	&1080	&300	&2700	\\
-%		\hline
-%%2	&2	&10	&40	&600	&300	&-7201	\\
-%2	&4	&10	&80	&1080	&300	&6101	\\
-%%2	&4	&10	&40	&600	&300	&-7201	\\
-%2	&4	&10	&40	&600	&300	&7201	\\
-%3	&4	&12	&60	&600	&300	&1462	\\
-%4	&4	&10	&80	&1080	&300	&2883	\\
-%5	&12	&20	&70	&600	&300	&1680	\\
-%		\hline
-%2	&4	&10	&40	&120	&300	&1	\\
-%2	&4	&10	&40	&120	&500	&6001	\\
-%3	&4	&10	&40	&120	&500	&6102	\\
-%5	&4	&10	&80	&1080	&300	&2884	\\
-%5	&12	&20	&60	&120	&300	&360	\\
-%		\hline
-%3	&4	&10	&40	&600	&400	&4202	\\
-%2	&6	&20	&40	&120	&500	&6105	\\
-%%4	&4	&14	&80	&1080	&300	&-2923	\\
-%5	&12	&14	&60	&600	&300	&1500	\\
-%3	&6	&14	&60	&600	&300	&1486	\\
-%4	&4	&14	&80	&1080	&300	&2923	\\
-%		\hline
-%4	&8	&18	&80	&1080	&300	&2971	\\
-%3	&8	&10	&50	&1080	&300	&2530	\\
-%2	&12	&16	&40	&120	&400	&3077	\\
-%2	&10	&18	&60	&1080	&300	&2733	\\
-%4	&10	&10	&50	&1080	&300	&2535	\\
-%		\hline
-%		\hline
-%	\end{tabular}
-%	\caption{}
-%	\label{tab:emma}
-%\end{table}
-%
+}%\cite{Carta2011}
 
+\iffalse 
 \subsection{Fitting via Machine Learning}
@@
 The independent variables are located on a partially irregular grid.  
+\fi

### 2022-11-12 Thesis/chapter/01-introduction.tex
First Draft (NO POST-EMMA)

@@
 In sections \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
-Section \ref{sec:results} is split into three subsections: material specific results are presented in section \ref{sec:res-mat}, results regarding \gls{pso} in \label{sec:res-emma} and further analysis in section \ref{sec:res-post}.
+Section \ref{sec:results} is split into three subsections: material specific results are presented in section \ref{sec:res-mat}, results regarding \gls{pso} in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
 \td{Finally, section \ref{sec:outlook} discusses the outlook and next steps}

### 2022-11-12 Thesis/chapter/05-computational-details.tex
First Draft (NO POST-EMMA)

@@
 For every I-V curve (aluminium dot) the gradient $g$ at $V=0$ is calculated by taking 
-each $n=5$ points after and before the origin at least $d=2$ points distance (which boils
-down to the values from \SI{0.02}{\volt} to \SI{0.07}{\volt}), 
-averaging their V and I values and calculating
+each 5 points before and after the origin with at least 2 points distance (which boils
+down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
+calculating averages of each point cloud $\overline{V}$ and $\overline{I}$ and taking the ratio of differences 
+%averaging their V and I values and calculating
 \begin{equation}
-    g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
+    %g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
+    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}.
 \end{equation}
@@
 %
-In order to make the metric closer and better comparable to the \gls{mse} the average of the squared difference 
+In order to make the metric closer and better comparable to the \gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
 to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms. 

### 2022-11-12 Thesis/chapter/060-results-material.tex
drueber lesen bis excl 04 characterization
First Draft (NO POST-EMMA)

--- 2022-10-30 Thesis/chapter/060-results-material.tex
@@
 \subsection{Material Scientific and Pre-optimization}
+\label{sec:res-mat}
 %\subsubsection{Solution}
@@
 %
-Figure \ref{fig:sem-old} shows a typical details of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
+Figure \ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
 %These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
@@
 The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
-A solution with \gls{acoh} was stable for approximately \td{24h} sealed with Parafilm. 
+A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
 %192 was first with IPOH
-Whereas a solution with \gls{ipo} as stabilizing agent stayed stable for circa \td{72h}. 
+Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
 An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
-%
 Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
 as they could be stored until the next time needed instead of producing a separate solution for each sample.
-It was discovered that after a \gls{acoh} solution has aged beyond cloudiness 
-the addition of a small amount of \gls{ipo} can even reversed the aging effect. % for \td{respectable} amount of time. 
+%
+It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness 
+the addition 50\% of the volume in \gls{ipo} can even reversed the aging effect for a respectable amount of time. 
 This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
@@
 Figure \ref{fig:sem-cs1} shows the cross section of a single layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
-The large crystalline part which makes up most of the image is \gls{fto}. 
+The large crystalline structure which makes up most of the upper part of the image is \gls{fto}. 
 The boundary to glass is visible at the very top. 
 %On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
-On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer of \gls{zro} (produced with buthanolic recipe)  can be observed.
+On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe)  can be observed.
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Infra Red}
+\subsubsection{Spectrometry}
 
@@
         \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
-        \caption{reflectance of \gls{zro} on glass} \label{fig:ir-gr}
+        \caption{Reflectance of \gls{zro} on glass} \label{fig:ir-gr}
     \end{subfigure}
-    \caption{IR} \label{fig:ir}
+    \caption{\td{UVVisIR}} \label{fig:ir}
 \end{figure}
 
-In figure \ref{fig:ir-gt} transmission spectra of visible and \gls{nir} light can be seen. 
+In figure \ref{fig:ir-gt} transmission spectra of \gls{uv}/\gls{vis}/\gls{nir} light can be seen. 
 Each sample had different numbers of layers. 
@@
 The light interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film}. 
-Figure \ref{fig:ir-gr} shows reflectance spectra of visible and \gls{nir} at an incident angle of 45 degrees. 
+Figure \ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 degrees. 
 The shift of the wavy part of the spectra (comparing reflectance with transmittance) 
@@
     \end{subfigure}
-    \caption{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold} \label{fig:iv}
+%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
+    \caption{Current-voltage curves and the distribution of gradients for three representative samples, \td{include $\rho$ threshold}}  
+    \label{fig:iv}
 \end{figure}
@@
 %Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
-Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of a insulating sample. 
+%Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
+Figure \ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where ordinate shows the logarithm to the base of 10 of the absolute value of the current. 
 Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
@@
 and quite a few show hardly any current which is the ideal. 
-For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section \ref{sec:exp-eval}). 
-Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample as in \ref{fig:iv-log-good}.
+For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}). 
+Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample depicted in \ref{fig:iv-log-good}.
 %
-Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements from moderate sample. 
-Most of the \gls{iv}s have a maximum voltage of under \num{e-6} V, 
-but there are some so called pin holes with conductance above this threshold. %\num{e-6} V. 
+Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
+Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
+but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
 %
-In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of the functions 
+In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of some curves 
 is not at \SI{0}{\volt}, which means that the function does not cross the origin. 
@@
 This indicates a overall bad condition of the \gls{zro} layer for insulating. 
+%
+\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
 
@@
 
-Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate, steel, and 
-the substrate with ten layers of double concentrated solution (experiment number 6113, see \td{appendix}).
-In addition two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108).
+Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate (steel) and 
+the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix \ref{sec:app-emma}).
+In addition two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
 The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ clearly stand out against the noise from the experimental spectrum. %can be clearly seen in the experimental spectra.
+\td{why cubic \gls{zro} when cubic stable above 2270C? todo: find xrd of monoclinic and tetragonal}
 %In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
@@
 the boundaries of the input variables were explored. 
-Especially, the \gls{db} velocity (i.e. the velocity with which the blade moves and spreads the solution over the sample)
+Especially, the \gls{db} velocity $v_{DB}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
 was varied and examined during pre-optimization. 
 The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
-If the \gls{db} velocity was too slow (less than \mmps{1}), no layer was formed. 
+If the $v_{DB}$ was too slow (less than \mmps{1}), no layer was formed. 
 With the reason that the force exerted by the blade on the liquid not being strong enough to overcome surface tension. 
 This means that behind the blade a meniscus would pull the liquid without leaving any for the gelling process. 
-Additionally, the temperature while \gls{db} affects the resulting layer together with the \gls{db} velocity.
+Additionally, the temperature while \gls{db} $T_{DB}$ affects the evaporation process together with the \gls{db} velocity $v_{DB}$.
 

### 2022-11-12 Thesis/chapter/061-results-emma.tex
drueber lesen bis excl 04 characterization
First Draft (NO POST-EMMA)

@@
 \subsection{EMMA}
-
+\label{sec:res-emma}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%\subsubsection{all samples}
+%%% ALL SAMPLES
 A total of 30 recipes (see appendix \ref{sec:app-emma}) have been investigated in 
@@
 The experiments for generation 5 where not executed but 
-predictions were alread made
+predictions were already made
 with the information from the previous generations. 
@@
 The best sample predicted by the algorithm is experiment number 13 with 
-lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
-and lowest calcination heating rate and temperature.
+%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
+%and lowest calcination heating rate and temperature. 
+lowest $c_{zr}$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$ and second highest $\lambda$. 
+%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
+%and lowest calcination heating rate and temperature.
 
@@
         \hline\hline
-        generation  &enr &conc &layr &$v_{DB}$ &$T_{DB}$ &$v_{cal}$ &$T_{cal}$\\
+        generation  &enr &$c_{zr}$ &$\lambda$ &$v_{DB}$ &$T_{DB}$ &$v_{cal}$ &$T_{cal}$\\
         \hline
@@
 	\centering
-    \caption{Predicted G} 
+    \caption{Predicted $\hat{\gamma}$} 
     \label{tab:emma-pred-G}
@@
         \hline\hline
-    enr     &1st gen     &2nd gen        &3rd gen        &4th gen        &5th gen\\
+    enr &1st gen \gls{rf}   &2nd gen \gls{rf} &3rd gen \gls{rf}    &4th gen \gls{rf}   &5th gen \gls{rf}\\
         \hline
@@
 %
-In table \ref{tab:emma-pred-G} it can be seen that $G$ as predicted 
-by the 5th generation by the prediction function lowered with each iteration, 
+In table \ref{tab:emma-pred-G} it can be seen that the predicted $\hat{\gamma}$ 
+(predicted with 5th generation \gls{rf}) lowered with each iteration, 
 except for sample 2947, which wasn't predicted but measured. 
-This shows that the easiest part of the algorithm, the selection of the optimum 
-from predicted values works as expected. 
+This shows that the easiest part of the algorithm - the selection of the optimum 
+from predicted values - works as expected. 
 % and that the predictions included more lower values over time
 %
-The predicted $G$ for each generation's best as predicted 
-by the very generation would increase with each iteration (see table \ref{tab:emma-pred-G}). 
-This indicates an underestimation of the $G$ at the beginning and a correction with time. 
+Contrarily, the predicted $\hat{\gamma}$ for each generation's best 
+(predicted by the very generation's \gls{rf}) does increase with each iteration 
+(see diagonal in table~\ref{tab:emma-pred-G}). 
+This indicates an underestimation of $\gamma$ at the beginning and a correction with time. 
 %The reason for is probably a 
-The underestimation probably stems from a lucky selection of initial experiments.
+The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements.
 
-In figure \ref{fig:emma-gen} we can see the two measured main target dependent variables, $\gamma$ and $\rho$, of each particle at generations 1 to 4. 
+In figure \ref{fig:emma-gen} we can see the two measured main \textit{optimizands}, 
+$\gamma$ and $\rho$, of each particle at generations 1 to 4. 
 %for each particle included in the optimization. 
 %It shows a clear trend which indicates that the optimization worked even though 
-Both variables were to be minimized and show a clear trend towards low values indicating 
-that the optimization worked even though 
-the prediction functions (see equations \ref{eq:emma-G3} - \ref{eq:emma-vcal4}) 
+Both variables were to be minimized and show a clear trend towards low values, 
+indicating that the optimization worked even though 
+the prediction functions (see equations (\ref{eq:emma-phd3}) - (\ref{eq:emma-vcal4})) 
 and the chosen samples where not exactly as expected. 
@@
 %\subsubsection{Equation}
-Equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} and \ref{eq:emma-phd4}-\ref{eq:emma-vcal4} represent the prediction functions at $t=3$ and $t=4$ rounded to 2 significant digits, respectively.
+Equations (\ref{eq:emma-phd3})-(\ref{eq:emma-vcal3}) and (\ref{eq:emma-phd4})-(\ref{eq:emma-vcal4}) represent the \gls{rf}s at $t=3$ and $t=4$, respsectively, rounded to 2 significant digits.
 %$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
@@
 %This means that the algorithm must decide on the variables which explain the most variance independent of optimization weights.
-This stems from the fact that the algorithm must chose a single minimal set of \gls{bf} to predict all dependent variables. 
+This stems from the fact that the algorithm choses a single minimal set of \gls{bf} to predict all dependent variables. 
 %
@@
 
-The coefficients in equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} have the same signs and differ by a factor of roughly 100.
-This fits the data well, but the positive influence of the layer count/number is counter intuitive 
+The coefficients in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) have the same signs and differ by a factor of roughly 100.
+This fits the data well, but the positive influence of the layer count $\lambda$ is counter intuitive 
 as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
-The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} 
-seem low, but - considering the minimum value of the interaction of \num{36000} - have a higher influence on $\rho_3$ and $\gamma_3$ than $h(6 - \lambda)$. 
+The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) 
+seem low, but - considering the minimum value of the interaction of \num{36000} - have a higher influence on $\rho_3$ and $\gamma_3$ than the $h(6-\lambda)$ term. 
 %It's positive the hinge
-It is astonishing that the knot of the hinge function for equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} was chosen so low; 
+It is astonishing that the knot of the hinge function for equations (\ref{eq:emma-phd3})-(\ref{eq:emma-vcal3}) was chosen so low; 
 basically only including the influence of $\lambda=4$.
-Meaning for equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} that the lowest layer count produces worse samples which is intuitive, but more layers don't improve the insulation. 
-On the positive side the calcination heating rate $v_{cal}$ (see equation \ref{eq:emma-vcal3}) has been predicted perfectly within numerical precision.
+Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) that the lowest layer count produces worse samples which is intuitive, but more than 6 layers don't improve the insulation. 
+On the positive side, the calcination heating rate $v_{cal}$ (see equation (\ref{eq:emma-vcal3})) has been predicted perfectly within numerical precision.
 
 %%% T=4
-The coefficient of equations \ref{eq:emma-phd4} and \ref{eq:emma-G4} show the same pattern 
-as equations \ref{eq:emma-phd3} and \ref{eq:emma-G3}: identical signs and factor 100. 
-The choice of \gls{bf} in combination with their coefficient signs of 
-(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) seem more plausible than (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
-$\lambda$ decreases $G$ and $\rho$ and additionally the lowest $\lambda$ increases the two \textit{optimizands}. 
-Highly interesting is the influence of $T_{cal}$ on the conductance of the sample. 
-The conductance increases with higher calcination temperature, ergo the resistance decreases contrary to expectations.
-It was expected that under \oc{400} the calcination does not fully \td{ablaufen} and 
-that therefore the resulting layer does not insulate. 
-Furthermore, the influence of $T_{cal}$ is the larges of all \gls{bf} on $\rho$ and $\gamma$.
+The coefficients of equations (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) show the same pattern 
+as equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}): identical signs and factor 100. 
+The choice of \gls{bf}s in combination with their coefficient signs seems more plausibel
+for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
+$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally the lowest $\lambda$ increases the two \textit{optimizands}. 
+Highly interesting is the influence of $T_{cal}$ on the measure of conductance of a sample. 
+The optimzand $\hat{\gamma}$ increases with higher calcination temperature, 
+ergo the resistance decreases contrary to expectations.
+It was expected that 
+%under \oc{400} the calcination does not fully \td{ablaufen} and 
+calcination under \oc{400} does not suffice and 
+that therefore the resulting layer does not insulate as well. 
+Furthermore, the influence of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$.
 %This becomes clear when looking at the data.
-The coefficient of the interaction of $layr$ and $T_{cal}$ is about a tenth in size, 
-but has the extra factor of $layr$ of up to 12, resulting in the products being in the same order of magnitude.
-It can be noted that the coefficient of the $layr\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient. 
+The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size, 
+but has the extra factor of $\lambda$ of up to 12, resulting in the products being in the same order of magnitude.
+It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient. 
+This could hint a compensation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
 %It should be doubted, though, that the $layr$ only appears as interaction term 
@@
 %%% MSE
-For each generation the \gls{mse} was calculated such that only samples 
+For each generation the \gls{mse} was calculated for which only samples 
 from the optimisation were used which were available at the time of prediction. 
+That means 15 samples for $t=1$ and 30 sampes for $t=4$ were used to calculate respective \gls{mse}s. 
 The \gls{mse} is 64, 158, 54 and 50 for $t=1,2,3,4$, respectively. 
@@
 the combined \gls{mse} for $t=4$ is lower. 
-The high \gls{mse} at $t=2$ can be explained because the prediction functions are only constant values. 
-Apart from the second generation the \gls{mse} falls over time, which shows that the algorithm works but might be attributed to overfitting.
+The high \gls{mse} at $t=2$ can be explained by the prediction functions being only constant values. 
+Apart from the second generation the \gls{mse} decreases  over time, 
+which shows that the algorithm works. 
+This decrease in \gls{mse} might be attributed to overfitting, though. 
 %The \gls{mse} for each generation was also calculated between predicted values for pre-optimisation samples to check for overfitting, 
@@
 The error sank again with each generation (except for the second generation): 102, 118, 58, 50, respectively for $t=1,2,3,4$. 
-This means that the regularization method of the \gls{mars} algorithm in principle works on investigated samples. 
-\td{It should be noted, that the validation \gls{mse} for $t=1$ is much higher.}
-The high validation \gls{mse} (nearly 1.5 fold instead of circa 1 fold) for $t=1$ shows the poor prediction ability which improved.
-\td{why is \gls{mse} higher with higher values? No homoscedasticity ( equality of variance)?
-Or rather \gls{mse} at $t=2$ high because \gls{rf}s at $t=2$ poor and gen=2 samples are chosen with help of \gls{rf} at $t=2$? 
-}
+%This shows 
+The decrease of \gls{mse} with out-of-sample data shows that the regularization method 
+of the \gls{mars} algorithm in principle works on investigated samples.
+
+%\td{It should be noted, that the validation \gls{mse} for $t=1$ is much higher.}
+The high validation \gls{mse} (nearly 1.5 fold instead of circa 1 fold of \gls{mse}) 
+for $t=1$ shows the poor prediction ability at the beginning which improved with generations.
+This decrease in validation \gls{mse} supports the hypothesis stated at the beginning of this section: 
+the measure of conductance was underestimated and improved over time.
+%\td{why is \gls{mse} higher with higher values? No homoscedasticity ( equality of variance)?
+%Or rather \gls{mse} at $t=2$ high because \gls{rf}s at $t=2$ poor and gen=2 samples are chosen with help of \gls{rf} at $t=2$? 
+%}
 
 %%% PROBLEMS 
+Even though the main \textit{optimizands} were minimized as required, the \gls{rf}s were not satisfactory. 
 The two main problems were too many independent variables and too many dependent variables. 
-Both seem closely related and overcomplicate the optimization but both come with their own implications. 
+Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
 Too many independent variables make it harder to distinguish variance due to random error (due to unmeasured and uncontrolled variables) from variance due to dependency of chosen dependent varibales. 
-This is mainly because of the curse of dimensionality \td{cite} which makes it hard to collect enough data for each dimension. 
-The main problem about too many independent variables is that the same set of \gls{bf}s will be used to predict all \textit{optimizands}.
+This is mainly because of the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
+%
+In the here presented optimisation model the data points per independent variable 
+(events per predictor variable EPV) are as low as 5. 
+By eliminating three independent variables the EVP could rise to 10, which is stated 
+as rule of tumb for mulitvariate regression\cite{vittinghoff2007relaxing}. 
+The results obtained with limited sample number deliver some insightfulness %are quite respectable. 
+considering an EPV of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
+and an EVP of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
+%In the original \gls{emma} paper\cite{villanova2010function} the EVP is 20.
+%\td{In the original \gls{mars} paper\cite{friedman1991multivariate} the model is said 
+%to work well on 20-50 events per predictor varibale.
+%In the current model EPV are around 5, which is even low for a conservative 
+%rule of thumbs of 10-15 EPV\cite{vittinghoff2007relaxing}.
+%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
+%Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
+%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
+%}
+%
+The main problem about too many independent variables specific to this optimisation procedure 
+is that the same set of \gls{bf}s will be used to predict all \textit{optimizands}.
 This leads to competition between the \gls{bf}s as not all dependent variables may depend on the same independent variables. 
-This effect is reinforced by the choice of two independent variables as dependent variables (IVDV). 
+This effect is reinforced by the choice of two independent variables as dependent variables. % (IVDV). 
 Independent variables as dependent variables will likely be chosen in \gls{bf}s, 
-for including them in the \gls{rf} is a easy way to reduce the \gls{mse}.
-These \gls{bf}s then "take places" \td{(cf. musical chairs)} of \gls{bf}s predicting other dependent variables in the \gls{rf}. 
+for including them in the \gls{rf}s is an easy way to reduce the \gls{mse}.
+These \gls{bf}s then "take away places" of \gls{bf}s predicting other dependent variables in the \gls{rf}. %\td{(cf. musical chairs)} 
 This in turn can lead to wrong predictions and therefore inefficient choice of future samples.
 
+\td{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
+}
 %
@@
 all dependent variables and possibly exclude others which have more influence 
-on $\gamma$ and $\rho$ (see equations \ref{eq:emma-G4}? and \ref{eq:emma-phd4}?).
+on $\gamma$ and $\rho$ (see equations (\ref{eq:emma-G4})? and (\ref{eq:emma-phd4})?).
 %

### 2022-11-12 Thesis/chapter/062-post-emma.tex
drueber lesen bis excl 04 characterization
First Draft (NO POST-EMMA)

@@
 \subsection{Post-EMMA}
+\label{sec:res-post-emma}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
@@
     \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
-    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py
+    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
     \item grid search
@@
     \item SVM (start with grid search) (???)
+    \item \url{https://blog.minitab.com/en/adventures-in-statistics-2/regression-smackdown-stepwise-versus-best-subsets}
+    \item \url{https://blog.minitab.com/en/how-to-choose-the-best-regression-model}
 \end{itemize}
@@
 (null hypothesis is true) is less then 5\% (even less than 1\%). 
+\td{why 0.5?\cite{hoffman2020concept}}
 wrong the second is not for phd but for extended data set

### 2022-11-15 Code/Statistics/scripts/anova.sh
anova only G and phd

@@ -2,7 +2,7 @@
 #
 #USAGE: ./anova.sh [--all] 
 
-for dep in G phd layr vcal 
+for dep in G phd # layr vcal 
 do 
     echo $dep
     ./anova-${dep}.R $1 | grep -A1 --no-group-separator -e "F val" | grep "*" 2> /dev/null

### 2022-11-15 Thesis/chapter/062-post-emma.tex
anova subsection structure

@@
-\subsection{Post-EMMA}
 \label{sec:res-post-emma}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{analyse data with other methods post optimization}
-\begin{itemize}
-    \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
-    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
-    \item grid search
-    \item KRR (start with grid search) (???)
-    \item SVM (start with grid search) (???)
-    \item \url{https://blog.minitab.com/en/adventures-in-statistics-2/regression-smackdown-stepwise-versus-best-subsets}
-    \item \url{https://blog.minitab.com/en/how-to-choose-the-best-regression-model}
-\end{itemize}
+\subsubsection{ANOVA}\label{sec:res-anova}
+\textbf{EMMA}
+The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance} 
+on the calcination temperature $T_{cal}$. 
+Now \gls{anova} can be used to check if the data 
+From emma we saw that TCal seems to hav the biggest influence on 
+both gamma and rho.
+
+\textbf{What can/did we test?}
+With anova we can check if the probability of arriving at these results was by pure chance or not. 
+With the null hypothesis that we arrive at results by pure chance and of that the probability. 
+We tested for each input variable the influence on rho and gamma 
+and also as a test on vcal and $\lambda$. 
+We used an alpha value of 0.05 which means that 1 out of 20 times this result could be 
+produced by pure chance. 
+If the f-value is below that value, then we choose to accept, that the data is not due to
+chance but due to the influence of the independent variables on the dependent variables. 
+Usually, the alpha-value is choosen to be 0.01-0.05\cite{hoffman2020concept,sellke2001pvalues}
+The choice of a relatively high alpha-value is gerechetfertigt by the rather small amount of data and \td{evn}.
+\td{could test anova on difference generation data sets}
+
+\textbf{What were the results?}
+\td{anova shows that for the mentioned indep and dep pairs, the means divieded by 
+indep groups are not equal and that there is at least one group that is different. 
+Important to mention, that anova uses categorical data for inputs, 
+where our data is numerical and thus information is lost}
+For both gamma and lambda (for both the emma dataset and the extended dataset) 
+the F values for Tcal were in all cases under 0.01, 
+indicating a real influence of Tcal on the conductance.
+Both datasets exhibit a $p(>F) < 0.05$ for the interaction Tcal:vcal on phd. 
+\td{why tcal:vcal on phd the same for both datasets?}
+And the extended data set has pF samll er than 0.01 of vcal on phd.
+
+\textbf{What do the results mean?} 
+Anova bestaetigt that TCal has influence on both G and phd. 
+\td{how to interpret p-values of 0.01 and 0.05? 
+They mean that under the assumption that the null hypothesis is correct, 
+there is a 1\% and 5\% chance of arriving at such data as observed.}
+It seems that the probability of getting such data per chance that Tcal has no influence 
+(null hypothesis is true) is less then 5\% (even less than 1\%). \td{NO bcs \cite{sellke2001pvalues}}
+
+%\textbf{Pre-writing:}
+%\Gls{anova} doesn't provide a lot of extra information. 
+%wrong the second is not for phd but for extended data set
+%but for phd even lower than 0.1 \%
+%Anova shows that the influence of TCal is significant as shown by the F
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{Linear Regressin}
+\subsubsection{Linear Regression}
 I thought that the influnce of $conc$ and $\lambda$ are the biggest, but they are just the smalles absolute values. 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{ANOVA}\label{sec:res-anova}
-\Gls{anova} doesn't provide a lot of extra information. 
-It bestaetigt that TCal has influence on both G and phd. 
-It seems that the probability of getting such data per chance that Tcal has no influence 
-(null hypothesis is true) is less then 5\% (even less than 1\%). 
-\td{why 0.5?\cite{hoffman2020concept}}
-wrong the second is not for phd but for extended data set
-but for phd even lower than 0.1 \%
-Anova shows that the influence of TCal is significant as shown by the F
-
-\iffalse
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%\iffalse
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
@@
 
-\fi
+%\fi
+
+\subsubsection{Further}
+\begin{itemize}
+    \item grid search
+    \item KRR (start with grid search) (???)
+    \item SVM (start with grid search) (???)
+    \item \url{https://blog.minitab.com/en/adventures-in-statistics-2/regression-smackdown-stepwise-versus-best-subsets}
+    \item \url{https://blog.minitab.com/en/how-to-choose-the-best-regression-model}
+\end{itemize}
 

### 2022-11-19 Thesis/chapter/062-post-emma.tex
anova first draft

@@
 The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance} 
-on the calcination temperature $T_{cal}$. 
-Now \gls{anova} can be used to check if the data 
-From emma we saw that TCal seems to hav the biggest influence on 
-both gamma and rho.
+on the calcination temperature $T_{cal}$ with regard to the \td{measurables} of the conductance. 
+\Gls{anova} is used to double check this. 
+%Now \gls{anova} can be used to check if the data
 
 \textbf{What can/did we test?}
-With anova we can check if the probability of arriving at these results was by pure chance or not. 
-With the null hypothesis that we arrive at results by pure chance and of that the probability. 
-We tested for each input variable the influence on rho and gamma 
-and also as a test on vcal and $\lambda$. 
-We used an alpha value of 0.05 which means that 1 out of 20 times this result could be 
-produced by pure chance. 
-If the f-value is below that value, then we choose to accept, that the data is not due to
-chance but due to the influence of the independent variables on the dependent variables. 
-Usually, the alpha-value is choosen to be 0.01-0.05\cite{hoffman2020concept,sellke2001pvalues}
-The choice of a relatively high alpha-value is gerechetfertigt by the rather small amount of data and \td{evn}.
+With \gls{anova} we can check if the probability of arriving at these results was by pure chance or not. 
+The null hypothesis is that the results were obtained by pure chance without any dependence of the insulation of a sample on the process variables.
+%We tested for each input variable the influence on rho and gamma 
+A one-way \gls{anova} was performed for every independent variable on $\rho$ and $\gamma$. 
+%and also as a test on vcal and $\lambda$. 
+We used an $\alpha$ value of 0.05 which means that 
+the null hypothesis is rejected if the p-value is under 0.05. 
+Usually, the $\alpha$-value is chosen to be 0.01 or 0.05\cite{hoffman2020concept,sellke2001pvalues}.
+The choice of a relatively high alpha-value is motivated by the rather small amount of data and low \td{EPV}.
+As mentioned by Sellke et al.\cite{sellke2001pvalues} a p-value of 0.05 might tempt 
+to guess that in 1 out of 20 cases the results could be false positives, 
+whereas the frequency is much higher. 
+%1 out of 20 times this result could be 
+%produced by pure chance given that the null hypothesis is true. 
+%If the p-value is below that value, then we choose to accept, that the data is not due to
+%chance but due to the influence of the independent variables on the dependent variables. 
 \td{could test anova on difference generation data sets}
@@
 \textbf{What were the results?}
-\td{anova shows that for the mentioned indep and dep pairs, the means divieded by 
-indep groups are not equal and that there is at least one group that is different. 
-Important to mention, that anova uses categorical data for inputs, 
-where our data is numerical and thus information is lost}
-For both gamma and lambda (for both the emma dataset and the extended dataset) 
-the F values for Tcal were in all cases under 0.01, 
-indicating a real influence of Tcal on the conductance.
-Both datasets exhibit a $p(>F) < 0.05$ for the interaction Tcal:vcal on phd. 
-\td{why tcal:vcal on phd the same for both datasets?}
-And the extended data set has pF samll er than 0.01 of vcal on phd.
+%\Gls{anova} shows that for the mentioned indep and dep pairs, the means divided by 
+%indep groups are not equal and that there is at least one group that is different. 
+For both $\rho$ and $\lambda$ (for both the \gls{emma} dataset and the extended dataset) 
+the F values for $T_{cal}$ were in all cases under 0.01, 
+indicating a real influence of $T_{cal}$ on the conductance.
+Both datasets exhibit a p-value $< 0.05$ for the interaction $T_{cal}$:$v_{cal}$ on $\rho$.
+\td{And the extended data set has p-value smaller than 0.01 of vcal on phd. 
+Whereas vcal on phd for \gls{emma} dataset has p-value of slightly over 0.05.}
+\td{why tcal:vcal on phd the same for both datasets? zufall}
 
@@
 (null hypothesis is true) is less then 5\% (even less than 1\%). \td{NO bcs \cite{sellke2001pvalues}}
+Important to mention, that anova uses categorical data for inputs, 
+where our data is numerical and thus information is lost
 

### 2022-11-19 Code/Statistics/scripts/linreg.py
add inline comments linreg.py

@@ -1,72 +1,92 @@
 #!/usr/bin/env python3
-
+#
 import numpy as np 
 import pandas as pd
 import dfply
 from sklearn.linear_model import LinearRegression
 import argparse
-
-parser = argparse.ArgumentParser(description ='Search some files')
-parser.add_argument('-i', '--influence',dest ='print_influence',action ='store_true', help ='print influence')
-parser.add_argument('-e', '--emma', dest ='only_emma',action ='store_true', help ='only use emma data')
-parser.add_argument('-y', '--yindex', dest ='y_index',action ='store', choices={'0','2','3','7','10'}, default='0', help ='y to fit: 0=all; 2=G; 3=phd; 7=layers; 10=vCal [default=0]')
-args = parser.parse_args()
-
-infile="../db_final.tsv"
-names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
 #
+# DEFINE MEAN SQUARED ERROR FUNCTION
 def MSE(predicted,measured):
     pred=np.array(predicted)
     real=np.array(measured)
     mse=np.square(pred-real).mean()
     return mse
 #
-df=pd.read_csv(infile, skiprows=1, names = names,delimiter="\t")
+# MAKE COMMAND LINE ARGUMENTS
+parser = argparse.ArgumentParser(description ='Search some files')
+parser.add_argument('-i', '--influence',dest ='print_influence',action ='store_true', help ='print influence')
+parser.add_argument('-e', '--emma', dest ='only_emma',action ='store_true', help ='only use emma data')
+parser.add_argument('-y', '--yindex', dest ='y_index',action ='store', choices={'0','2','3','7','10'}, default='0', help ='y to fit: 0=all; 2=G; 3=phd; 7=layers; 10=vCal [default=0]')
+args = parser.parse_args()
+#
+#LOAD DATA FROM FILE 
+infile="../db_final.tsv"
+names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
+df=pd.read_csv(infile, skiprows=1, names = names, delimiter="\t")
+#
+# CHECK IF ONLY USE EMMA DATA
[…]

### 2022-11-19 Code/Statistics/scripts/multivarlinreg.R
add multivar linreg R script

@@ -1,0 +1,20 @@
+#!/usr/bin/env Rscript
+#
+# USAGE: ./anova-G.R [--all] | grep -A1 -e "F value" --no-group-separator
+suppressMessages(suppressWarnings(library("dplyr")))
+only_emma<-1
+args = commandArgs(trailingOnly=TRUE)
+if ( length(args)==1 && (args[1]=="--all") ){only_emma<-0}
+n="numeric"
+f="factor"
+dat=read.delim("../db_final.tsv", colClasses=c(n,n,n,n,n,n,n,n,n,n,n,n))
+d.all = dat %>% select (! avg1.G.:avg2.G.)
+if (only_emma==1)
+{
+    d.all = d.all %>% filter ( enr != 0 )
+}
+X=d.all%>% select(conc,layr,vCal,TCal,vDOC,TDOC)
+
+lin.mod<- lm (cbind(d.all$G,d.all$phd) ~ conc+layr+vCal+TCal+vDOC+TDOC, data=d.all)
+summary(lin.mod)
+exit 0

### 2022-11-19 Code/ML/2022/gs_svm.py
add grid search svm py script

@@ -1,0 +1,103 @@
+#!/usr/bin/env python3
+
+import numpy as np 
+from sklearn.svm import SVR # Epsilon-support Vector Regression
+#from sklearn.kernel_ridge import KernelRidge as KRR
+import sklearn
+import pandas as pd
+import dfply
+import argparse
+#
+# MAKE COMMAND LINE ARGUMENTS
+parser = argparse.ArgumentParser(description ='Grid Search for hyper parameters')
+parser.add_argument('-e', '--emma', dest ='only_emma',action ='store_true', help ='only use emma data')
+parser.add_argument('-y', '--yindex', dest ='y_index',action ='store', choices={'2','3','7','10'}, default='2', help ='y to fit: 2=G; 3=phd; 7=layers; 10=vCal [default=2]')
+args = parser.parse_args()
+#
+# DATA PRE-PROCESSING WITH 5-fold script 
+def get_sets(df,names,args):
+    data=np.array(df)
+    X=data[:,6:]
+    # MUTLIply by 60 bcs C/h instead of C/min
+    X[4]=X[4]*60
+    X_names=names[6:]
+    Y=data[:,int(args.y_index)].reshape(-1)
+    return X,Y
+#
+# DO CROSS FOLD VALIDATION SPLIT 
+def cross_fold(X,Y,k,shuffle=True):
+    train_min=0             # train minimum index
+    train_max=int(len(df)/k*(k-1))
+    test_min = train_max    # test  minimum index
+    test_max=len(df)
+    #
+    # shuffle before cross validation
+    if shuffle:
+        X, Y = sklearn.utils.shuffle(X, Y, random_state=0)
+    #
+    X_train=X[train_min:train_max]
+    X_test=X[test_min:test_max]
+    Y_train=Y[train_min:train_max]
+    Y_test=Y[test_min:test_max]
+    return X_train,X_test,Y_train,Y_test
+#
+#LOAD DATA FROM FILE 
+infile="../../Statistics/db_final.tsv"
+names = ["nr", "enr", "conductivity", "phdensity", "avg1(G)", "avg2(G)", "conc", "layers", "vDOC", "TDOC", "vCal", "TCal"]
+#         0     1       2               3           4          5          6       7        8        9       10      11 
[…]

### 2022-11-19 Code/ML/pred/find_best.py

@@ -5,6 +5,7 @@ def get_goodness(g,phd, layers, vCal):
     w=weights=[0.4,0.5,0.05, 0.05]
     return w[0]*g+ w[1]*phd+ w[2]*layers+ w[3]*vCal
 
+# predicted from EMMA t=4? 
 infile="allspace.dat"
 names = ["nr", "conc", "layr", "vDOC", "TDOC", "vCal", "TCal", "G", "phd", "layers", "Cal_vel"]
 df=pd.read_csv(infile, skiprows=1, delim_whitespace=True, names = names)
@@ -17,11 +18,11 @@ for n in df.nr:
 #    print(n,i)
     v = values = [ df.G[i], df.phd[i], df.layers[i], df.Cal_vel[i] ] 
     measure = get_goodness(float(v[0]), float(v[1]), float(v[2]), float(v[3]) )
-    print(i,best_measure,bestvalues,measure)
     if measure < best_measure:
-        bestvalues=df.nr[i]
+        bestvalues=v #df.nr[i]
         best_measure = measure
-        print("yass")
+        print(i,best_measure,bestvalues,measure)
+#        print("yiss")
 
 #for line in f.readlines():
 #    values = line.split("\t")

### 2022-12-08 Code/Statistics/scripts/mars.R
mars prediction for all data

@@ -57,6 +57,12 @@ if (only_emma){
     print(get_MAE(y.inter,y.pred))
     print("MSE(inter)")
     print(get_MSE(y.inter,y.pred))
+    # PRINT MAE AND MSE FOR ALL DATA 
+    y.pred <- predict(mars.emma, newdata=x.all)
+    print("MAE(all)")
+    print(get_MAE(y.all,y.pred))
+    print("MSE(all)")
+    print(get_MSE(y.all,y.pred))
     # PRINT REGRESSION FORMULA 
     print("MARS model for EMMA samples")
     format(mars.emma)

### 2022-12-08 Thesis/chapter/062-post-emma.tex
post-emma table

@@
 
+\begin{table}[htb]
+	\centering
+    \caption{Post EMMA vergleich}
+	\label{tab:post-emma}
+	\begin{tabular}{c cc cc cc cc}
+    \hline\hline
+    G&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
+    \hline
+        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
+        lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
+        ML KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
+        ML SVM& 15  415&    26& 1050&   28& 1588&   19& 677\\
+    \hline\hline
+	\end{tabular}
+    %
+	\begin{tabular}{c cc cc cc cc}
+    \hline\hline
+    p&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
+    \hline
+        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
+        lin Reg&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
+        ML KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
+        ML SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
+    \hline\hline
+	\end{tabular}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

### 2022-12-08 Code/ML/2022/2_get_gshp.sh

@@ -1,0 +1,5 @@
+#!/bin/bash 
+#
+#GET HYPER PARAMETERS FOR GRID SEARCH 
+echo "Hyper parameter for grid search"
+grep --color=auto HPGS gs*py

### 2022-12-08 Code/ML/2022/get_gshp.sh

@@ -1,3 +1,0 @@
-#!/bin/bash 
-#
-grep --color=auto HPGS gs*py

### 2023-01-18 Thesis/chapter/060-results-material.tex
finished XRD

@@
+In this section the results will pe presented, explained and discussed. 
+Starting with physical measurements and material properties. 
+Followed by the presentation and exploration of the results obtain by optimisation/exploration  with the \gls{emma} method. 
+Finally, the results of alternative optimisation methods were let loose on the data and compared with the \gls{emma} method. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure \ref{fig:sem-old}). 
-Altering the ratios of ingredients, adjusting pH (by adding \gls{naoh}, \ch{H2SO4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't improve the resulting \gls{zro} layers. 
+Altering the ratios of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't improve the resulting \gls{zro} layers. 
 % ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
 % ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
-Even after the consecutive application of two layers there was no clear improvement and the results reminded rather of a sparse crust than of a film. 
+Even after the consecutive application of two layers, there was no improvement and the results reminded rather of a sparse crust than of a film. 
 %It is assumed that the solution was far from the optimum for a sol-gel process. 
@@
 
-The sol-gel recipe optimized by Hu et al.\cite{Hu2016} for \ch{Al2O3} worked splendidly for our use case even after (not so) minor changes (see section \ref{sec:exp-sol-bu}). 
-%
-Figure \ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
-%%%% PIN HOLES
-The large irregularity on the bottom left could depict a pin hole, a (tiny) hole that reaches to the substrate. 
-These irregularities are rather the exception. 
-Alternatively, the small, hardly visible slits spread across the surface could depict such pin holes. 
-These - I think - are rather only one layer deep irregularities since they are so prevalent
-and hardly any pin holes were electrically observed on similar samples.
-
-%%%%%% STABILITY
-As soon as the solution showed initial cloudiness, it was declared as unstable. 
-The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
-A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
-%192 was first with IPOH
-Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
-An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
-Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
-as they could be stored until the next time needed instead of producing a separate solution for each sample.
-%
-It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness 
-the addition 50\% of the volume in \gls{ipo} can even reversed the aging effect for a respectable amount of time. 
-This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
-even after 5 fold dilution. 
-%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
-%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.
-
-\begin{figure}[htb]
+\begin{figure}[bht]
     \centering
@@
         \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
-        \caption{115 fto cs 1x} \label{fig:sem-cs1}
+        \caption{115 fto cs 5x} \label{fig:sem-cs1}
     \end{subfigure}
@@
     \end{subfigure}
-    \caption{SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d)} \label{fig:sem}
+	\caption{SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} \label{fig:sem}
 \end{figure}
 
+The sol-gel recipe optimized by Hu et al.\cite{Hu2016} for \ch{Al2O3} worked splendidly for our use case even after (not so) minor changes (see section \ref{sec:exp-sol-bu}). 
+%
+Figure \ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
+%%%% PIN HOLES
+The large irregularity on the bottom left could depict a pin hole, a (tiny) hole that reaches to the substrate. 
+These irregularities are rather the exception. 
+Alternatively, the small, hardly visible slits spread across the surface could depict such pin holes. 
+These - I think - are rather only one layer deep irregularities since they are so prevalent
+and hardly any pin holes were electrically observed on similar samples.
+
+%%%%%% STABILITY
+As soon as the solution showed initial cloudiness, it was declared as unstable and no more used for \gls{db}. 
+The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
+A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
+%192 was first with IPOH
+Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
+An increase of the \gls{zrpro} concentration accelerates the aging process of the solution \td{what is this aging process chemically? oxidation, hydrolisation?}.
+Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
+as they could be stored until the next time needed, instead of producing a separate solution for each sample.
+%
+It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness 
+the addition 50\% of the volume in \gls{ipo} can even reversed the aging effect for a respectable amount of time. 
+This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
+even after 5 fold dilution. 
+%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
+%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.
+
 %%%%%%%%% CROSS SECTION
-Figure \ref{fig:sem-cs1} shows the cross section of a single layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
+Figure \ref{fig:sem-cs1} shows the cross section of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
 The large crystalline structure which makes up most of the upper part of the image is \gls{fto}. 
@@
 On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe)  can be observed.
+Measuring the cross section on steel was not as straight forward because the ductility of steel prevents fractures of the substrate. 
+Resorting to scratching the surface with an diamond glass cutter allowed us to get an insight into the thickness of the layer on steel substrate.
 %
-Measuring the cross section on steel was not as straight forward because of the ductility of steel. 
-The only way to get an insight into the thickness of the layer via \gls{sem} was through 
-scratching the surface with an diamond glass cutter. 
 The result can be seen in figure \ref{fig:sem-cs2}. 
@@
 Assuming that the raised structure resembling a tentacle is \gls{zro}, 
-the thickness of the layer can be estimated to be around \um{1}.
+the thickness of the layer can be estimated to be in the magnitude of \um{1}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{XRD}
+\begin{figure}
+	\centering
+	\includegraphics[width=\picwidth]{Pics/xrd.png}
+	\caption{XRD spectra}
+	\label{fig:xrd}
+\end{figure}
+
+\Gls{xrd} was used in order to confirm that the produced layer is indeed \gls{zro}. 
+Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate (steel) and 
+the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix \ref{sec:app-emma}).
+In addition, two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
+%
+The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ (highest to lowest intensity) clearly stand out against the noise from the experimental spectrum.
+%can be clearly seen in the experimental spectra.
+They confirm that the produced substance is \gls{zro}.
+To further clarify the phase Raman spectra are needed since cubic and tetragonal phases are difficult to distinguish from \gls{xrd} alone\cite{Purohit2006Combustion}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Spectrometry}
+
+\begin{figure}[htb]
+    \centering
+    \begin{subfigure}{.49\textwidth}
+        \centering
+        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
+        \caption{Transmission of \gls{zro} on glass} \label{fig:ir-gt}
+    \end{subfigure}
+    \begin{subfigure}{.49\textwidth}
+        \centering
+        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
+        \caption{Reflection of \gls{zro} on glass} \label{fig:ir-gr}
+    \end{subfigure}
+	\caption{\gls{uv}/\gls{vis}/\gls{nir}} Reflection vs Reflectance and Transmission vs Transmittance\label{fig:ir}
+\end{figure}
+
+In figure \ref{fig:ir-gt} transmission spectra of \gls{uv}/\gls{vis}/\gls{nir} light can be seen. 
+Each sample had different numbers of layers. 
+The incident angle was 0 degree for each sample.
+%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
+The more layers, the more of the light is absorbed (at 600-\nm{1100}) by the \gls{zro} layers. 
+%The trend is not monotonic due to inhomogenities in the sample???b
+The thicker, the layer is the more wavy the graph, which can be attributed to interference.
+This trend can also be observed in figure \ref{fig:ir-gr}.
+The weak interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film}. 
+%
+Figure \ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 degrees. 
+%The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
+Thicker layers reflect more light between approximately \nm{800} and \nm{1000}. 
+Again, this effect is most likely not observed across the whole spectrum because of interferences. 
+%It is interesting to note the shoulder at around \nm{850} present in every spectrum.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Current Voltage Curves} 
+\begin{figure}
+    \centering
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
+        \caption{log good 3x4F} \label{fig:iv-log-good}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
+        \caption{log okay 10x1F} \label{fig:iv-log-okay}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
+        \caption{log bad 3x3F} \label{fig:iv-log-bad}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
+        \caption{stat good 3x4F} \label{fig:iv-stat-good}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
+        \caption{stat okay 10x1F} \label{fig:iv-stat-okay}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
+        \caption{stat bad 3x3F} \label{fig:iv-stat-bad}
+    \end{subfigure}
+%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
+    \caption{Current-voltage curves and the distribution of gradients for three representative samples, \td{include $\rho$ threshold}}  
+    \label{fig:iv}
+\end{figure}
+
+%Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
+%Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
+Figure \ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the decimal logarithm of the absolute value of the current in Ampere.
+Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
+All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
+and quite a few show hardly any current which is the ideal. 
+For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}). 
+Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample depicted in \ref{fig:iv-log-good}.
+%
+Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
+Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
+but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
+%
+In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of some curves 
+is not at \SI{0}{\volt}, which means that the function does not cross the origin. 
+This deviation is similar to the deviation because of the photo-currents\cite{perez2018solar}, 
+but was not investigated further. 
+Though, the photo-current is compelling, it is most likely not zutreffend because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
+%
+Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample 
+where all measurement exhibit relatively high voltages and high calculated conductances. 
+This indicates a overall bad condition of the \gls{zro} layer for insulating. 
+%
+\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Preoptimization}
+Before the optimization with the \gls{emma} algorithm, 
+the boundaries of the input variables were explored. 
+Especially, the \gls{db} velocity $v_{DB}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
+was varied and examined during pre-optimization. 
+The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
+If the $v_{DB}$ was too slow (less than \mmps{1}), no layer was formed. 
+With the reason that the force exerted by the blade on the liquid not being strong enough to overcome surface tension. 
+This means that behind the blade a meniscus would pull the liquid without leaving any for the gelling process. 
+Additionally, the temperature while \gls{db} $T_{DB}$ affects the evaporation process together with the \gls{db} velocity $v_{DB}$.
+
+%\td{Assumption: Ideally solution evaporate shortly after DB but not before}
+%due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
+%- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\iffalse
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Spectrometry}
-
-\begin{figure}[htb]
-    \centering
-    \begin{subfigure}{.49\textwidth}
-        \centering
-        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
-        \caption{Transmittance of \gls{zro} on glass} \label{fig:ir-gt}
-    \end{subfigure}
-    \begin{subfigure}{.49\textwidth}
-        \centering
-        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
-        \caption{Reflectance of \gls{zro} on glass} \label{fig:ir-gr}
-    \end{subfigure}
-    \caption{\td{UVVisIR}} \label{fig:ir}
-\end{figure}
-
-In figure \ref{fig:ir-gt} transmission spectra of \gls{uv}/\gls{vis}/\gls{nir} light can be seen. 
-Each sample had different numbers of layers. 
-The incident angle was 0 degree for each sample.
-%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
-The more layers the more of the light is absorbed (1000nm) by the \gls{zro} layers. 
-%The trend is not monotonic due to inhomogenities in the sample???b
-The thicker the layer is the more wavy the graph, which most likely can be attributed to interference.
-This trend can also be observed in figure \ref{fig:ir-gr}.
-The light interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film}. 
-Figure \ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 degrees. 
-The shift of the wavy part of the spectra (comparing reflectance with transmittance) 
-can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
-%\fi
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Current Voltage Curves} 
-\begin{figure}
-    \centering
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
-        \caption{log good 3x4F} \label{fig:iv-log-good}
-    \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
-        \caption{log okay 10x1F} \label{fig:iv-log-okay}
-    \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
-        \caption{log bad 3x3F} \label{fig:iv-log-bad}
-    \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
-        \caption{stat good 3x4F} \label{fig:iv-stat-good}
-    \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
-        \caption{stat okay 10x1F} \label{fig:iv-stat-okay}
-    \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
-        \caption{stat bad 3x3F} \label{fig:iv-stat-bad}
-    \end{subfigure}
-%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
-    \caption{Current-voltage curves and the distribution of gradients for three representative samples, \td{include $\rho$ threshold}}  
-    \label{fig:iv}
-\end{figure}
-
-%Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
-%Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
-Figure \ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where ordinate shows the logarithm to the base of 10 of the absolute value of the current. 
-Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
-All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
-and quite a few show hardly any current which is the ideal. 
-For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}). 
-Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample depicted in \ref{fig:iv-log-good}.
-%
-Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
-Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
-but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
-%
-In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of some curves 
-is not at \SI{0}{\volt}, which means that the function does not cross the origin. 
-This deviation is similar to the deviation because of the photo-currents\cite{perez2018solar}, 
-but was not investigated further. 
-Though, the photo-current is compelling, it is most likely not zutreffend because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
-%
-Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample 
-where all measurement exhibit relatively high voltages and high calculated conductances. 
-This indicates a overall bad condition of the \gls{zro} layer for insulating. 
-%
-\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{XRD}
-\begin{figure}
-	\centering
-	\includegraphics[width=\picwidth]{Pics/xrd.png}
-	\caption{XRD spectra}
-	\label{fig:xrd}
-\end{figure}
-
-Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate (steel) and 
-the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix \ref{sec:app-emma}).
-In addition two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
-The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ clearly stand out against the noise from the experimental spectrum. %can be clearly seen in the experimental spectra.
-\td{why cubic \gls{zro} when cubic stable above 2270C? todo: find xrd of monoclinic and tetragonal}
-%In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
-%The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
-%This wideness is is due to polycrystalline form of the material which is expected 
-%due to the sol-gel creation process and multiple applications of layers. 
-%Nonetheless, the \gls{xrd} spectra shows clearly that the produced layer is \gls{zro}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Preoptimization}
-Before the optimization with the \gls{emma} algorithm, 
-the boundaries of the input variables were explored. 
-Especially, the \gls{db} velocity $v_{DB}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
-was varied and examined during pre-optimization. 
-The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
-If the $v_{DB}$ was too slow (less than \mmps{1}), no layer was formed. 
-With the reason that the force exerted by the blade on the liquid not being strong enough to overcome surface tension. 
-This means that behind the blade a meniscus would pull the liquid without leaving any for the gelling process. 
-Additionally, the temperature while \gls{db} $T_{DB}$ affects the evaporation process together with the \gls{db} velocity $v_{DB}$.
-
-%\td{Assumption: Ideally solution evaporate shortly after DB but not before}
-%due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
-%- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation

### 2023-01-18 Thesis/chapter/062-post-emma.tex
finished XRD

@@
 \label{sec:res-post-emma}
+%describe what awaits the reader in this chapter:
+in this section the experimental results are analyzed with different methods and compared with the original method EMMA which was integrated into the optimization. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
@@
 \textbf{EMMA}
-The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance} 
+The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance/effect/correlation} 
 on the calcination temperature $T_{cal}$ with regard to the \td{measurables} of the conductance. 
@@
 %chance but due to the influence of the independent variables on the dependent variables. 
-\td{could test anova on difference generation data sets}
+\td{could test anova on different generations data sets}
 

### 2023-01-19 Data/I-V/plot-single-ivs.sh
make final iv graphs

@@ -1,0 +1,21 @@
+#!/bin/bash 
+
+if [ "x" ==  "x$1" ] ; 
+then 
+	echo "USAGE: ./plot-single-iv.sh I-V_146_2021_02_03" ; exit 1  
+fi 
+pushd $1
+mkdir -p tmp 
+pushd tmp 
+for i in $(ls ../*L*C*) ; do 
+	echo "
+	set term pngcairo
+	set xlabel \"voltage [V]\"
+	set ylabel \"current [A]\"
+	set out \"$i.png\"
+	set xrange [-0.5:0.5]
+	plot \"$i\" w l notitle" > plot.gp ; 
+	gnuplot plot.gp ; 
+	mv $i.png . 
+done
+rm plot.gp ; 

### 2023-01-19 Thesis/chapter/060-results-material.tex
finish IV results

@@
 Finally, the results of alternative optimisation methods were let loose on the data and compared with the \gls{emma} method.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \centering
+	%
     \begin{subfigure}{.3\textwidth}
@@
     \end{subfigure}
+	%
     \begin{subfigure}{.3\textwidth}
@@
     \end{subfigure}
+	%
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/146-nocurrent.png}
+        \caption{no current} \label{fig:iv-nocurrent}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/146-diodic.png}
+        \caption{diodic} \label{fig:iv-diodic}
+    \end{subfigure}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{Pics/iv/146-ohmic.png}
+        \caption{ohmic} \label{fig:iv-ohmic}
+    \end{subfigure}
+	%
 %    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
@@
 %Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
-Figure \ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the decimal logarithm of the absolute value of the current in Ampere.
+Figure \ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
 Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
@@
 and quite a few show hardly any current which is the ideal. 
+An example for very low conductance measurement in non-logarithmic scale can be seen in figure \ref{fig:iv-nocurrent}.
 For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}). 
@@
 In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of some curves 
-is not at \SI{0}{\volt}, which means that the function does not cross the origin. 
-This deviation is similar to the deviation because of the photo-currents\cite{perez2018solar}, 
+is not at \SI{0}{\volt}, which means that the function does not cross the origin in non-logarithmic representation. 
+%
+This deviation (see figure \ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar}, 
 but was not investigated further. 
-Though, the photo-current is compelling, it is most likely not zutreffend because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
+Though, the explanation by photo-current is compelling, it does most likely not apply because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
+A better explanation would be the tunneling effect, whose \gls{iv} curves look very similar\cite{feenstra1994scanning,datta1997current}.
+%\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
 %
@@
 This indicates a overall bad condition of the \gls{zro} layer for insulating. 
+Figure \ref{fig:iv-ohmic} shows a graph circa following Ohm's law. 
 %
-\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
 

### 2023-01-20 Thesis/chapter/060-results-material.tex
finish EMMA coeff analysis

@@
 %
-This deviation (see figure \ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar}, 
-but was not investigated further. 
+This deviation (see figure \ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar} because of its non-zero current at $V=0$.
+%, but was not investigated further. 
 Though, the explanation by photo-current is compelling, it does most likely not apply because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
@@
 If the $v_{DB}$ was too slow (less than \mmps{1}), no layer was formed. 
-With the reason that the force exerted by the blade on the liquid not being strong enough to overcome surface tension. 
-This means that behind the blade a meniscus would pull the liquid without leaving any for the gelling process. 
+The reason is that the force exerted by the blade on the liquid is not strong enough to overcome surface tension. 
+This means that behind the blade a meniscus would pull the liquid without leaving behind any for the gelling process. 
 Additionally, the temperature while \gls{db} $T_{DB}$ affects the evaporation process together with the \gls{db} velocity $v_{DB}$.

### 2023-01-20 Thesis/chapter/061-results-emma.tex
finish EMMA coeff analysis

@@
 with the information from the previous generations. 
-%%% BEST
+%%% BEST PREDICTED RECIPE
 The best sample predicted by the algorithm is experiment number 13 with 
@@
 	\label{tab:emma-Gb}
-	\begin{tabular}{cccccccc}
+	\begin{tabular}{ccccccccc}
         \hline\hline
-        generation  &enr &$c_{zr}$ &$\lambda$ &$v_{DB}$ &$T_{DB}$ &$v_{cal}$ &$T_{cal}$\\
+		generation& measurements &enr &$c_{zr}$ &$\lambda$ &$v_{DB}$ &$T_{DB}$ &$v_{cal}$ &$T_{cal}$\\
         \hline
-     1   &1       &2    &4   &10   &40  &120  &300\\
-     2   &5       &2    &6   &10   &40  &120  &300\\
-     3   &2947    &4    &6   &16   &80 &1080  &300\\
-     4   &2405    &2    &6   &10   &40 &1080  &300\\
-     5   &13      &2   &10   &10   &40  &120  &300\\
+	1  &10	&1       &2    &4   &10   &40  &120  &300\\
+	2  &15	&5       &2    &6   &10   &40  &120  &300\\
+	3  &20	&2947    &4    &6   &16   &80 &1080  &300\\
+	4  &25	&2405    &2    &6   &10   &40 &1080  &300\\
+	5  &30	&13      &2   &10   &10   &40  &120  &300\\
     \hline\hline
@@
 The remaining input variables remained more or less the same except for the 3rd generation. 
+\td{why?}
 %
 In table \ref{tab:emma-pred-G} it can be seen that the predicted $\hat{\gamma}$ 
-(predicted with 5th generation \gls{rf}) lowered with each iteration, 
+(predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
 except for sample 2947, which wasn't predicted but measured. 
@@
 (see diagonal in table~\ref{tab:emma-pred-G}). 
-This indicates an underestimation of $\gamma$ at the beginning and a correction with time. 
+This indicates an underestimation of $\hat\gamma$ at the beginning and a correction with time. 
 %The reason for is probably a 
 The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
+Indeed, the samples with the lowest \textit{optimisands} are amoung the first generation (see appendix \ref{sec:app-emma}, \td{and maybe fig gen-g}).
 
-In figure \ref{fig:emma-gen} we can see the two measured main \textit{optimizands}, 
+In figure \ref{fig:emma-gen} we can see the two measured main \textit{optimisands}, 
 $\gamma$ and $\rho$, of each particle at generations 1 to 4. 
@@
 %It shows a clear trend which indicates that the optimization worked even though 
-Both variables were to be minimized and show a clear trend towards low values, 
+Both variables were to be minimized and show a clear trend towards low values with increasing generation, 
 indicating that the optimization worked even though 
@@
     \centering
-    \begin{subfigure}{.45\textwidth}
+    \begin{subfigure}{.24\textwidth}
         \centering
-        \includegraphics[width=.8\textwidth]{Pics/stats/gen-G.png}
+        \includegraphics[width=.98\textwidth]{Pics/stats/gen-G.png}
         \caption{} \label{fig:emma-G-gen}
     \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
+    \begin{subfigure}{.24\textwidth}
         \centering
-        \includegraphics[width=.8\textwidth]{Pics/stats/gen-phd.png}
+        \includegraphics[width=.98\textwidth]{Pics/stats/gen-phd.png}
         \caption{} \label{fig:emma-phd-gen}
     \end{subfigure}
-    \caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process} 
+    \begin{subfigure}{.24\textwidth}
+        \centering
+        \includegraphics[width=.98\textwidth]{Pics/stats/G-tcal.png}
+        \caption{} \label{fig:g-tcal}
+    \end{subfigure}
+    \begin{subfigure}{.24\textwidth}
+        \centering
+        \includegraphics[width=.98\textwidth]{Pics/stats/phd-tcal.png}
+        \caption{} \label{fig:phd-tcal}
+    \end{subfigure}
+	\caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process; \td{add caption for c and d. check if can plot with t=0}} 
     \label{fig:emma-gen}
@@
 %
-%\td{Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as \textit{optimizands} rather unfortunate. %highly questionable. 
+%\td{Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as \textit{optimisands} rather unfortunate. %highly questionable. 
 %\td{This makes including $\lambda$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
@@
 The coefficients in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) have the same signs and differ by a factor of roughly 100.
-This fits the data well, but the positive influence of the layer count $\lambda$ is counter intuitive 
+This fits the data well (see appendix \ref{sec:app-emma}), but the positive influence of the layer count $\lambda$ is counter intuitive 
 as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
@@
 for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
-$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally the lowest $\lambda$ increases the two \textit{optimizands}. 
-Highly interesting is the influence of $T_{cal}$ on the measure of conductance of a sample. 
-The optimzand $\hat{\gamma}$ increases with higher calcination temperature, 
-ergo the resistance decreases contrary to expectations.
+$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally the lowest $\lambda$ increases the two \textit{optimisands}. 
+% TCAL ON OPTIMIZANDS
+The influence of $T_{cal}$ on the measures of conductance ($\rho$ and $\gamma$) is higly interesting. 
 It was expected that 
-%under \oc{400} the calcination does not fully \td{ablaufen} and 
-calcination under \oc{400} does not suffice and 
+calcination temperatures under \oc{400} do not suffice to produce compact layers and 
 that therefore the resulting layer does not insulate as well. 
-Furthermore, the influence of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$.
-%This becomes clear when looking at the data.
-The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size, 
-but has the extra factor of $\lambda$ of up to 12, resulting in the products being in the same order of magnitude.
+%\td{xxx}
+\textit{Optimsands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
+according to equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}, 
+ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.
+% DESCRIBE COEFFEICIENTS
+Furthermore, the influence of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$ and also on $\hat\lambda$ and $\hat{v}_{cal}$.
+The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 
+but has the extra factor $\lambda$ of up to 12, resulting in the products of coefficients and independent variable being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$.
 It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient. 
-This could hint a compensation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
+This negative correlation could hint a compensation of the overestimated influence of $T_{cal}$ on the \textit{optimisands}.
 %It should be doubted, though, that the $layr$ only appears as interaction term 
 %together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
-It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
-with $T_{cal}$ and $T_{DB}$.
+%
+%It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
+%with $T_{cal}$ and $T_{DB}$. 
+From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_DB$ and then the rest of the independent variables. 
+I highly doubt though that the specific interactions proposed by EMMA are indeed meaningful.
 
@@
 
+\td{plot g and p vs TCal, calc avg of p and g for each gen, append pre-emma to appendix}
 %%% PROBLEMS 
-Even though the main \textit{optimizands} were minimized as required, the \gls{rf}s were not satisfactory. 
+Even though the main \textit{optimisands} were minimized as required, the \gls{rf}s were not satisfactory. 
 The two main problems were too many independent variables and too many dependent variables. 
@@
 The main problem about too many independent variables specific to this optimisation procedure 
-is that the same set of \gls{bf}s will be used to predict all \textit{optimizands}.
+is that the same set of \gls{bf}s will be used to predict all \textit{optimisands}.
 This leads to competition between the \gls{bf}s as not all dependent variables may depend on the same independent variables. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimizands}
+\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimisands}
 The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ 

### 2023-01-25 Code/Statistics/avg.py
generational average

@@ -1,0 +1,29 @@
+import numpy as np
+G_gen0=[
+        10.95940, 29.16378, 24.32170, 12.38955, 15.64646
+        , 
+        70.64908, 45.50493, 79.39680, 32.86985, 51.09902
+        ]
+G_gen1=[39.68027, 108.47050, 71.25290, 46.44359, 49.18166]
+G_gen2=[38.79620, 47.17184, 76.44246, 42.66628, 47.64474]
+G_gen3=[28.56022, 61.73920, 52.13835, 52.18121, 47.53164]
+G_gen4=[36.17699, 36.54716, 43.19611, 36.16643, 47.75640]
+G=[G_gen0, G_gen1, G_gen2, G_gen3, G_gen4]
+
+phd_gen0=[
+        0.00000, 0.02083, 0.00000, 0.00000, 0.03846
+        ,
+        0.78431, 0.02778, 0.86842, 0.00000, 0.03030
+        ]
+phd_gen1=[0.12500, 1.00000, 0.95652, 0.03030, 0.00000]
+phd_gen2=[0.05882, 0.33333, 1.00000, 0.00000, 0.00000]
+phd_gen3=[0.00000, 0.38710, 0.03571, 0.09091, 0.00000]
+phd_gen4=[0.06061, 0.04167, 0.00000, 0.04348, 0.00000]
+phd=[phd_gen0, phd_gen1, phd_gen2, phd_gen3, phd_gen4]
+
+a=5
+for i in range(5):
+#    print(G[i], G[i][5:9])
+#    print(i, np.average(G[i]), np.average(phd[i]), np.average(G[i][0:5]), np.average(phd[i][0:5])) 
+    print(f"{i:d}\t{np.average(G[i]):.4f}\t{np.average(phd[i]):.4f}\t{np.average(G[i][0:5]):.4f}\t{np.average(phd[i][0:5]):.4f}") 
+

### 2023-01-25 Thesis/chapter/061-results-emma.tex
add pre-emma table to appendix

@@
 The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
-Indeed, the samples with the lowest \textit{optimisands} are amoung the first generation (see appendix \ref{sec:app-emma}, \td{and maybe fig gen-g}).
+Indeed, the samples with the lowest \textit{optimisands} are amoung the first generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).
 
@@
     \end{subfigure}
-	\caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process; \td{add caption for c and d. check if can plot with t=0}} 
+	\caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process; \td{add caption for c and d.}} 
     \label{fig:emma-gen}

### 2023-01-27 Thesis/chapter/061-results-emma.tex
finish emma discusssion

@@
 
-\td{plot g and p vs TCal, calc avg of p and g for each gen, append pre-emma to appendix}
 %%% PROBLEMS 
@@
 Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
-Too many independent variables make it harder to distinguish variance due to random error (due to unmeasured and uncontrolled variables) from variance due to dependency of chosen dependent varibales. 
-This is mainly because of the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
+Too many independent variables make it harder to distinguish variance due to random error (due to unmeasured and uncontrolled variables) from variance due to dependency.
+% of chosen dependent varibales.
+The difficulty of identifying meaningful correlation is mainly owed to the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
 %
-In the here presented optimisation model the data points per independent variable 
-(events per predictor variable EPV) are as low as 5. 
-By eliminating three independent variables the EVP could rise to 10, which is stated 
-as rule of tumb for mulitvariate regression\cite{vittinghoff2007relaxing}. 
+%In the here presented optimisation model 
+%the data points per independent variable 
+%(events per predictor variable EPV) are as low as 5. 
+The \gls{epv} (data points per independent varible) are as low as 5 in the here presented optimisation model. % and data acquisition method
+By eliminating three independent variables the \gls{epv} could rise to 10, which is stated 
+as rule of thumb for mulitvariate regression\cite{vittinghoff2007relaxing}. 
 The results obtained with limited sample number deliver some insightfulness %are quite respectable. 
-considering an EPV of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
-and an EVP of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
-%In the original \gls{emma} paper\cite{villanova2010function} the EVP is 20.
+considering an \gls{epv} of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
+and an \gls{epv} of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
+%In the original \gls{emma} paper\cite{villanova2010function} the \gls{epv} is 20.
 %\td{In the original \gls{mars} paper\cite{friedman1991multivariate} the model is said 
@@
 %
-The main problem about too many independent variables specific to this optimisation procedure 
-is that the same set of \gls{bf}s will be used to predict all \textit{optimisands}.
-This leads to competition between the \gls{bf}s as not all dependent variables may depend on the same independent variables. 
+
+On the other side, the main problem about too many dependent variables specific to this optimisation procedure 
+is that the same set of \gls{bf}s will be used to predict \textbf{all} \textit{optimisands}.
+This leads to competition between the \gls{bf}s, as not all dependent variables may depend on the same independent variables. 
 This effect is reinforced by the choice of two independent variables as dependent variables. % (IVDV). 
 Independent variables as dependent variables will likely be chosen in \gls{bf}s, 
-for including them in the \gls{rf}s is an easy way to reduce the \gls{mse}.
+for including them in the \gls{rf}s is an easy way to reduce the \gls{mse} and improve prediction accuracy.
 These \gls{bf}s then "take away places" of \gls{bf}s predicting other dependent variables in the \gls{rf}. %\td{(cf. musical chairs)} 
 This in turn can lead to wrong predictions and therefore inefficient choice of future samples.
+
+The two independent variables $v{cal}$ and $\lambda$ were included as \textit{optimisands} for two reasons: 
+Maximizing the calcination velocity and minimizing the number of \td{layers/layer application iterations} leads to minimization of process time.
+This optimization would be better placed in a follow up study. 
+The second reason for including independent variables was to check if the model works. 
+This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimisands} and thus additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables.
+The second flaw is that there are obsiously better methods to assess the quality of a model that to make it more complex.
+Good alternatives would have been leave-one-out or cross validation.
 
@@
 }
-\td{look at emma papers}
-\td{change G to gamma and write enr to every figure}
-\td{in \cite{friedman1991multivariate} the model is said to work well on $\frac{N}{n}$ ratios (aka events per predictor varibale (EPV)) of 20-50. 
-EPV is around 5 for this model.
-Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
+%\td{look at emma papers}
+%\td{change G to gamma and write enr to every figure}
+
+%\td{in \cite{friedman1991multivariate} the model is said to work well on $\frac{N}{n}$ ratios (aka events per predictor varibale (EPV)) of 20-50. 
+%EPV is around 5 for this model.
+%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
 Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
-"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
-}
+%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
+%}
 

### 2023-01-27 Data/I-V/all_make.sh
change gp fontsize to 30

@@ -1,3 +1,4 @@
+#USAGE ./all_make.sh
 for dir in $(ls -1 | grep -e "I-V*"); do 
 #	echo $dir
 	cd $dir

### 2023-01-27 Data/I-V/make_log_i-v.sh

@@ -1,4 +1,5 @@
 #!/bin/bash
+# USAGE: bash ../make_log_i-v.sh . > i-v-log.gp
 pth=$1
 lines=($(echo $(ls -1 $pth/*L*C* ) | tr ";" "\n"))
 no_lines=${#lines[@]}
@@ -9,9 +10,9 @@ png=1
 echo "set xrange [-0.5:0.5]"
 echo "set logscale y"
 echo 'set xlabel "voltage [V]"'
-echo 'set ylabel "current [I]"'
+echo 'set ylabel "current [A]"'
 if [ $png -eq 1 ]; then 
-	echo "set term pngcairo"
+	echo "set term pngcairo size 1200, 900 font \",30\""
 	echo "set out \"log-i-v.png\""
 fi
 

### 2023-01-27 Data/I-V/plot-single-ivs.sh

@@ -9,7 +9,7 @@ mkdir -p tmp
 pushd tmp 
 for i in $(ls ../*L*C*) ; do 
 	echo "
-	set term pngcairo
+	set term pngcairo size 1200, 900 font \",30\"
 	set xlabel \"voltage [V]\"
 	set ylabel \"current [A]\"
 	set out \"$i.png\"

### 2023-01-27 Thesis/chapter/060-results-material.tex
finish emma discusssion
captions for results pre-emma and emma

@@
         \includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
-        \caption{SEM picture of \gls{zro} produces by H2O solution} \label{fig:sem-old}
+		\caption{}%SEM picture of \gls{zro} produces by H2O solution} 
+		\label{fig:sem-old}
     \end{subfigure}
@@
         \includegraphics[width=.79\textwidth]{Pics/sem/147_steel_ph_10x.png}
-        \caption{SEM picture of \gls{zro} produced by buoh solution} \label{fig:sem-ph}
+		\caption{}%SEM picture of \gls{zro} produced by buoh solution} 
+		\label{fig:sem-ph}
     \end{subfigure}
@@
         \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
-        \caption{115 fto cs 5x} \label{fig:sem-cs1}
+		\caption{}%115 fto cs 5x} 
+		\label{fig:sem-cs1}
     \end{subfigure}
@@
         \includegraphics[width=.8\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
-        \caption{150 steel 2Fx5} \label{fig:sem-cs2}
+		\caption{}%150 steel 2Fx5} 
+		\label{fig:sem-cs2}
     \end{subfigure}
-	\caption{SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} \label{fig:sem}
+	\caption{
+		SEM images of of \gls{zro}:
+		(a) \gls{zro} produces by aquatic solution on \gls{fto}
+		(b) 10 layers of \gls{zro} on steel substrate
+		(c) cross section of crack of 5 layers of \gls{zro} on fto 
+		(d) side view of scratched \gls{zro} on steel substrate
+		%SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} 
+		\label{fig:sem}
+	}
 \end{figure}
@@
 	\includegraphics[width=\picwidth]{Pics/xrd.png}
-	\caption{XRD spectra}
+	\caption{XRD spectra of steel substrate (yellow), \gls{zro} (blue), $\alpha$-Fe (green, idealized) and cubic-\gls{zro} (purple, idealized)\cite{gkatz1971xray}}
 	\label{fig:xrd}
+	% 207_6113_10x2F_v18T40_T500v2
 \end{figure}
@@
         \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
-        \caption{Transmission of \gls{zro} on glass} \label{fig:ir-gt}
+		\caption{}%Transmission of \gls{zro} on glass} 
+		\label{fig:ir-gt}
     \end{subfigure}
@@
         \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
-        \caption{Reflection of \gls{zro} on glass} \label{fig:ir-gr}
+		\caption{}%Reflection of \gls{zro} on glass} 
+		\label{fig:ir-gr}
     \end{subfigure}
-	\caption{\gls{uv}/\gls{vis}/\gls{nir}} Reflection vs Reflectance and Transmission vs Transmittance\label{fig:ir}
+	\label{fig:ir}
+	\caption{UV/Vis/NIR spectra of different \gls{zro} layer counts on glass 
+	(a)~transmission at \SI{0}{\degree} and (b)~reflection at \SI{45}{\degree} 
+	} 
+%	"138_g_00L_R.dpt"  w l t "0"  , \
+%	"118_g_03L_R.dpt"  w l t "3"  , \
+%	"114_g_05L_R.dpt"  w l t "5"  , \
+%	"130_g_10L_R2.dpt" w l t "10" , \
+%	"136_g_11L_R.dpt"  w l t "11"
+%	Reflection vs Reflectance and Transmission vs Transmittance
 \end{figure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
-        \caption{log good 3x4F} \label{fig:iv-log-good}
+		\caption{}%log good 3x4F} 
+		\label{fig:iv-log-good}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
-        \caption{log okay 10x1F} \label{fig:iv-log-okay}
+		\caption{}%log okay 10x1F} 
+		\label{fig:iv-log-okay}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
-        \caption{log bad 3x3F} \label{fig:iv-log-bad}
+		\caption{}%log bad 3x3F} 
+		\label{fig:iv-log-bad}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
-        \caption{stat good 3x4F} \label{fig:iv-stat-good}
+		\caption{}%stat good 3x4F} 
+		\label{fig:iv-stat-good}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
-        \caption{stat okay 10x1F} \label{fig:iv-stat-okay}
+		\caption{}%stat okay 10x1F} 
+		\label{fig:iv-stat-okay}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
-        \caption{stat bad 3x3F} \label{fig:iv-stat-bad}
+		\caption{}%stat bad 3x3F} 
+		\label{fig:iv-stat-bad}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/146-nocurrent.png}
-        \caption{no current} \label{fig:iv-nocurrent}
+		\caption{}%no current} 
+		\label{fig:iv-nocurrent}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/146-diodic.png}
-        \caption{diodic} \label{fig:iv-diodic}
+		\caption{}%diodic} 
+		\label{fig:iv-diodic}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{Pics/iv/146-ohmic.png}
-        \caption{ohmic} \label{fig:iv-ohmic}
+		\caption{}%ohmic} 
+		\label{fig:iv-ohmic}
     \end{subfigure}
@@
 %    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
-    \caption{Current-voltage curves and the distribution of gradients for three representative samples, \td{include $\rho$ threshold}}  
+	\caption{
+		Current-voltage curves and the distribution of gradients for three representative samples: insulating well (a),(d),(g), moderately (b),(e),(h), poorly (c),(f),(i); 
+		(a)-(c) I-V curves with log transformed current; 
+		(d)-(f) frequency histograms of the conductance with pin hole threshold marked as vertical line; 
+		(g)-(i) individual I-V measurements
+	}
     \label{fig:iv}

### 2023-01-27 Thesis/chapter/061-results-emma.tex
captions for results pre-emma and emma

@@
 	\centering
-    \caption{Global best per generation}
+    \caption{Global best per generation with experiment numbers and dependent variables/experiment conditions}
 	\label{tab:emma-Gb}
@@
 	5  &30	&13      &2   &10   &10   &40  &120  &300\\
-    \hline\hline
-	\end{tabular}
-\end{table}
-
-\begin{table}
-	\centering
-    \caption{Predicted $\hat{\gamma}$} 
-    \label{tab:emma-pred-G}
-    \begin{tabular}{cccccc}
-        \hline\hline
-    enr &1st gen \gls{rf}   &2nd gen \gls{rf} &3rd gen \gls{rf}    &4th gen \gls{rf}   &5th gen \gls{rf}\\
-        \hline
-    1       &1.214185    &       &       &       &38.7962       \\
-    5       &       &4.196626       &       &       &25.47335       \\
-    2947    &       &       &10.9594    &       &10.9594       \\
-    2405    &       &       &       &20.04962   &25.47335       \\
-    13      &       &       &       &       &24.87178   \\
     \hline\hline
@@
 % and that the predictions included more lower values over time
+\begin{table}
+	\centering
+    \caption{Predicted conductance measure $\hat{\gamma}$ for each generation by each generation's regression function}  
+    \label{tab:emma-pred-G}
+    \begin{tabular}{cccccc}
+        \hline\hline
+    enr &1st gen \gls{rf}   &2nd gen \gls{rf} &3rd gen \gls{rf}    &4th gen \gls{rf}   &5th gen \gls{rf}\\
+        \hline
+    1       &1.214185    &       &       &       &38.7962       \\
+    5       &       &4.196626       &       &       &25.47335       \\
+    2947    &       &       &10.9594    &       &10.9594       \\
+    2405    &       &       &       &20.04962   &25.47335       \\
+    13      &       &       &       &       &24.87178   \\
+        \hline\hline
+    \end{tabular}
+\end{table}
 %
@@
     \end{subfigure}
-	\caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process; \td{add caption for c and d.}} 
+	\caption{
+		(a)~calculated conductance measures~$\gamma$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation.
+		(b)~calculated pin hole density~$\rho$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation.
+		(c)~calculated conductance measures~$\gamma$ against calcination temperature $T_{cal}$
+		(d)~calculated pin hole density~$\rho$ against calcination temperature $T_{cal}$
+		\td{describe more in-depth in text}
+	}
+
     \label{fig:emma-gen}
@@
 \fi
+\td{TODO: find expression for $\gamma$: conductance measure, conducticity}

### 2023-01-29 Thesis/chapter/061-results-emma.tex
finsih res-emma add lin-reg functions

@@
 \td{
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%\subsubsection{how did evolve over time?}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimisands}
-The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ 
-were included as dependent variables with the objective to maximize with a relative weight of 0.05 each.
-The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
-Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
 }
@@
 \
-\ds{
+\td{
 (1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
@@
 }
-%\td{look at emma papers}
-%\td{change G to gamma and write enr to every figure}
 
-%\td{in \cite{friedman1991multivariate} the model is said to work well on $\frac{N}{n}$ ratios (aka events per predictor varibale (EPV)) of 20-50. 
-%EPV is around 5 for this model.
-%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
 Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%\subsubsection{how did evolve over time?}
-
-\iffalse
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{Pics/stats/G-t.png}
-    \caption{conductivity G [a.u.] against sample number (is this even correct?)}
-    \label{fig:G-t}
-\end{figure}
-
-\td{TODO: check if the sorted correctly? Make generation graph with boxplot }
-\td{TODO: visualize} how the population moved across the space (with parallel coordinates? or see page 121)
-\url{https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation}
-\fi
 \td{TODO: find expression for $\gamma$: conductance measure, conducticity}
+\td{when adding dep var to model this has two folgen: - beeinflusst the BF and the optimization, but bcs relatiev weight is only 0.05 for each, no big beeinflussung on optimization}

### 2023-01-29 Thesis/chapter/062-post-emma.tex
finsih res-emma add lin-reg functions

--- 2022-12-08 Thesis/chapter/062-post-emma.tex
@@
 \label{sec:res-post-emma}
+%describe what awaits the reader in this chapter:
+In this section the experimental results are analyzed with different methods and compared with the original method EMMA which was integrated into the experiment selection process. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 \subsubsection{ANOVA}\label{sec:res-anova}
-\textbf{EMMA}
-The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance} 
+%\textbf{EMMA}
+The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance/effect/correlation} 
 on the calcination temperature $T_{cal}$ with regard to the \td{measurables} of the conductance. 
@@
 Was zu erwarten war.
+
+\begin{align}
+	\begin{split}
+		\label{eq:linreg-phd}
+		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{DB} + 0.0058\cdot T_{DB} \\
+		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
+	\end{split}
+	\\
+	\begin{split}
+		\label{eq:linreg-G}
+		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot \lambda - 1.2\cdot v_{DB} + 0.2\cdot T_{DB} \\
+			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
+	\end{split}
+\end{align}
 
@@
 What are the measurables.
+
+\td{do regression for avg(-log(G)) instead of $\gamma$=avg( ( 13+log(G))**2)}

### 2023-02-01 Thesis/chapter/031-theory-calculations.tex
experiment fertig druebergelesen
post-emma table
start incorporate post-emma into theory

@@
 		%{Machine and deep learning in MS research are just powerful statistics – No}
+What is \gls{ml}? Some might argue that \gls{ml} is just overglorified statistics, but that's not the case. 
 Although \gls{ml} uses several statistical methods, their goal and frame conditions are different. 
@@
 is represented by its independent and dependent variables. 
-It was originally inspired by the behaviour of bird flocks and fish schools\cite{Kennedy1995}.
+It was originally inspired by the behaviour of bird flocks and fish schools\cite{Kennedy1995,villanova2010function}.
+%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
+%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
 Each particle has an associated position and velocity. 
@@
 \fi
+
+%%% FEATURE SELECTION 
+% https://stats.stackexchange.com/questions/39243/how-does-one-interpret-svm-feature-weights
+% gene (feature) selection with SVM https://link.springer.com/content/pdf/10.1023/A:1012487302797.pdf
+% Intro to feature selection https://axon.cs.byu.edu/Dan/778/papers/Feature%20Selection/guyon2.pdf
+
+\td{statistical methods to bewerten a model are: cross validation, leave-one-out validation ( special case of cross validation), correlation coefficient for linear fits, mean square error.
+methods to fit data are: lin reg, polynomial regression, ridge regression, KRR, SVM and?}

### 2023-02-01 Thesis/chapter/063-discussion.tex
finish EMMA coeff analysis
start incorporate post-emma into theory

@@
 \td{COMMENT: solution age was not accounted for}
+
+\td{two main problems: 1.
+too many input variables; 2.
+too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs.
+This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
+
+\td{The goal of introducing \gls{ml} to this project was to apply and delve/vertiefen into subject which I've been studying during my undergrad courses.
+This seemed like the perfect opputrunity.
+And indeed I learned a lot.
+Even if only although \gls{ml} is a hot topic at the moment, it can not solve every problem.
+Two important things have I learned regarding \gls{ml}:
+1.) The methods bringen sich nix if one doesn't know how to apply them which directly leads into my second erkenntnis
+2.) If one wants to use a tool, one should know how to use it and its innerlichkeiten in order to use it well.
+The second point is not the best comparison because one doesn't need to know how a light switch works in order to use it effectively use it.}

### 2023-02-03 Thesis/chapter/031-theory-calculations.tex
plan for theory calc

@@
 
+\subsubsection{Kernel Ridge Regression and Support Vector Machine}
+
+\textbf{goal}
+\begin{itemize}
+    \item intro to stat and ml 
+    \item say that although different will be abgehandelt in the same chapter 
+    \item basic statistics: MAE vs MSE, R, std, F-test 
+    \item lin reg 
+    \item ridge regression 
+    \item kernel ridge regression 
+    \item support vector machine 
+    \item anova (categorical), PCA, step wise regression
+    \item all previous ananlyse data to predict, but don't tell me which data point is needed next 
+    \item DOE (add data acquisition)
+    \item genetic algorithm and pso (they combine data gen with regression/prediction and optimisation, actually incorporate prediction into selection process but don't per se specify which pred and optimisation)
+    \item comment: always tradeoff between complexity and interpretability
+    \item quesiton: which paragraph by GPT2?? 
+\end{itemize}
+
+\textbf{current}
+\begin{itemize}
+    \item ML vs statistics
+    \item AI vs ML 
+    \item ML methods
+    \item EMMA 
+    \item KRR 
+    \item DOE
+    \item ANOVA
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%% STATISTICS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-02-05 Thesis/chapter/032-alt-theory-calculations.tex
start write alt cacl theory

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Machine Learning and Statistics}

\subsubsection{Introduction to AI, ML and statistics}
\textbf{What is AI?} It is the interdisciplinary field of making a artificial inteligent agent. 
What is intelligence though?
Intelligence is not easily defined. Some definitions I agree with is that intelligence 
includes learning from experience, finding solutions to new problems. 
Creativity is also substencial for intelligence. 
It is a goal in the field AI to immitate (and surpass) human intelligence. 
The turing tests aims to test a computers intelligience by testing if it can trick a person into believing that the computer is person while a person tries to make the person believe that they are in fact a person. 
Approaches range from knowledge based systems over hard coded intstructions to machine learning. 
%
\textbf{Machine Learning} is the art of telling a machine or computer how to gain knowlegde from data (aka experience). 
There are different problems and solutions. 
The problems include image recognition, voice recognition, natural language processing, data prediction, classification, recommendation systems and so on. 
%
In order to solve these problems machine learning resorts to statistical methods such as
linear regression, ridge regression. 
Further machine learning methods not regularly seen in statistics are the 
kernel trick, support vector machines, genetic algorithms and particle swarm algorithms. 
The last two are special in the sense that they don't provide a certain regression method,
but rather a frame work to choose the next sample which should be tested in a optimisation. 
%
\textbf{Statistics} is a subfield of mathematics and emerged from the aim to summerzie large data sets 
and extract information. In contrast to descriptive statistic, there is stochastic. 
Stochastic statistic aims on predicting data points with probabilities. 
%
\textbf{Linear regression} is one of the simplest methods to predict data. 
It besticht by its computational simplicity and easy interpretation. 
%Let's take this equation
\begin{equation}
\mathbf{y} = \mathbf{X} \mathbf{k} +c 
\end{equation}
Where $\mathbf{y}$ (size $\mathbb{R}^n$) is a vector of dependent variables and $\mathbf{X}$ (size $\mathbb{R}^{nxd}$) is a matrix of independent variables. 
The parameters $\mathbf{k}$ (size $\mathbb{R}^n$) and $c$ (size $\mathbb{R}$) are chosen by minimizing an objective function (loss function in \gls{ml} chargon).
A typical function to minimize are the L1 and L2 error, i.e. \gls{mae} and \gls{mse}, respectively.
\begin{align}
L_1&= \sum |y_i - \hat y_i| = \sum \sum |y_i - x_{i,j}\cdot k_i+c| \\
L_2&= \sum(y_i - \hat y_i)^2 = \sum (y_i - x_{i,j}\cdot k_i+c)^2
\end{align}
%
\textbf{Ridge Regression} is like linear regression but with an extra term which penalizes steep regression functions.
This extra term is scaled by a correction parameter $\lambda$. 
The larger $\lambda$ the larger regularisation and the flatter the regression functions. 
If $\lambda$ were infinite, then the regression function would be a flat line. 
The correction term avoids overfitting. 
\begin{equation}
    L_{RR} = L_2 + \lambda \sum k_i = \sum(y_i - \hat y_i)^2 + \lambda \sum k_i
\end{equation}
\textbf{Kernel Ridge Regression}
\gls{krr} combines ridge regression with the kernel method. 
A kernel transforms data in such a way that a linear hyperplane (a line in one dimension, 
a plane in two dimensions) can fit data in regression problem or seperate the data in classification problem. 
A kernel is some kind of similarity measure. 
The following equations show definitions for 
linear (eq.~\ref{eq:lin-kernel}), 
polynomial (eq.~\ref{eq:pol-kernel}), 
sigmoidal (eq.~\ref{eq:sig-kernel}) and 
radial basis functionial kernel~(eq. \ref{eq:rbf-kernel}).
\begin{align}
    \label{eq:lin-kernel}
    k_{lin}(\mathbf{x},\mathbf{y}) &= \mathbf{x}^{\top} \mathbf{y} \\
    \label{eq:pol-kernel}
    k_{pol}(\mathbf{x}, \mathbf{y}) &= (\gamma \mathbf{x}^{\top} \mathbf{y} + c_0)^d \\
    \label{eq:sig-kernel}
    k_{sig}(\mathbf{x}, \mathbf{y}) &= \text{tanh}(\gamma \mathbf{x}^{\top} \mathbf{y} + c_0) \\
    \label{eq:rbf-kernel}
    k_{rbf}(\mathbf{x}, \mathbf{y}) &= \text{exp}(- \gamma \| \mathbf{x} -  \mathbf{y} \|^2) 
\end{align}
These kernels fulfill the requirements of nonnegativity, symmetry, linearity\cite{rupp2015machine}.
% https://scikit-learn.org/stable/modules/metrics.html#polynomial-kernel
%
\textbf{Support vector machines} often use the kernel method to ...

\begin{itemize}
    \item \sout{intro to stat and ml}
    \item \sout{say that although different will be abgehandelt in the same chapter}
    \item \sout{basic statistics: MAE vs MSE, R, std, F-test} 
    \item \sout{lin reg}
    \item \sout{ridge regression}
    \item kernel ridge regression 
    \item support vector machine 
    \item anova (categorical), PCA, step wise regression
    \item all previous ananlyse data to predict, but don't tell me which data point is needed next 
    \item DOE (add data acquisition)
    \item genetic algorithm and pso (they combine data gen with regression/prediction and optimisation, actually incorporate prediction into selection process but don't per se specify which pred and optimisation)
    \item comment: always tradeoff between complexity and interpretability
    \item quesiton: which paragraph by GPT2?? 
\end{itemize}

### 2023-02-06 Thesis/chapter/032-alt-theory-calculations.tex
write up SVM and KRR

@@
 but rather a frame work to choose the next sample which should be tested in a optimisation. 
+\td{mention classification vs regression and supervised vs supervised}
 %
@@
 These kernels fulfill the requirements of nonnegativity, symmetry, linearity\cite{rupp2015machine}.
+\td{Note that when $\lambda$ tends to zero, the regularized loss function becomes the OLS loss function.
+When $\lambda$ tends to infinity, we get an intercept-only model}
+\td{A critique of ridge regression is that all the variables tend to end up in the model. The model only shrinks the coefficients.}
+% from https://medium.com/@zxr.nju/the-classical-linear-regression-model-is-good-why-do-we-need-regularization-c89dba10c8eb
+%
 % https://scikit-learn.org/stable/modules/metrics.html#polynomial-kernel
 %
-\textbf{Support vector machines} often use the kernel method to ...
+\textbf{Support vector machines} 
+\Gls{svm} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training}. 
+\Gls{svm} is mainly used for classification, but can also be used for regression. 
+Classifiction works by spanning a hyperplane between two categories in a way that the closest points from each category have the largest distance to the hyperplane. 
+The distance from the points to the hyperplane is called margin.
+These points are called support vectors and are used to define the hyperplane 
+A \gls{svm} avoids overfitting by only using a subset - the support vectors - to fit the model. 
+In the same manner as no data points are found within the margin for classification, 
+no data points should be found outside of the margin. 
+If the data is not seperable by a hyperplane the kernel trick can be used. 
+The downside of \gls{svm} is that it is very
 
@@
     \item \sout{ridge regression}
-    \item kernel ridge regression 
-    \item support vector machine 
+    \item \sout{kernel ridge regression}
+    \item \sout{support vector machine}
     \item anova (categorical), PCA, step wise regression

### 2023-02-10 Thesis/chapter/032-alt-theory-calculations.tex
svm chaos

@@
 \end{equation}
-Where $\mathbf{y}$ (size $\mathbb{R}^n$) is a vector of dependent variables and $\mathbf{X}$ (size $\mathbb{R}^{nxd}$) is a matrix of independent variables. 
-The parameters $\mathbf{k}$ (size $\mathbb{R}^n$) and $c$ (size $\mathbb{R}$) are chosen by minimizing an objective function (loss function in \gls{ml} chargon).
+Where $\mathbf{y}$ (size $\mathbb{R}^n$, where $n$ is the number of data points) is a vector of dependent variables and $\mathbf{X}$ (size $\mathbb{R}^{n\times d}$, where $d$ is the the number of independent variables) is a matrix of independent variables.
+The parameters $\mathbf{k}$ (size $\mathbb{R}^d$) and $c$ (size $\mathbb{R}$) are chosen by minimizing an objective function (loss function in \gls{ml} chargon).
 A typical function to minimize are the L1 and L2 error, i.e. \gls{mae} and \gls{mse}, respectively.
@@
 %
+
 \textbf{Ridge Regression} is like linear regression but with an extra term which penalizes steep regression functions.
@@
 \end{equation}
+
 \textbf{Kernel Ridge Regression}
@@
 %
+
 \textbf{Support vector machines} 
@@
 A \gls{svm} avoids overfitting by only using a subset - the support vectors - to fit the model. 
+\td{The goal is to fit $w$ and $b$ such that the margin (the distance from the descission boundary is maximal.
+As this the margin is inversely proportional to $\|w\|$, we aim to minimize $\|w\|$.
+With the contraint that all data points are correctly classified $y_i(x_iw-b)\geqslant1$.}
 In the same manner as no data points are found within the margin for classification, 
@@
 The downside of \gls{svm} is that it is very
+\td{$\text{min}\frac{1}{N} \sum_{i=1}^{N} max(0,1- y_i(\mathbf{x}x_i-b)) + \lambda \|w\|$
+The downside of \gls{svm} is that it is very sensitive to outliers.}
+
+$\min_{w,b} \|w\|$
+
+$ y_i(w \cdot x_i - b)\leqslant 1$
+
+Summary of SVM from Cherkassky's \textit{Learning from Data}\cite{cherkassky1998learning}
+The \gls{svm} was initially developed by V. Vapnik for the binary classification of seperable data, then improved to handle non-sperable data and eventually adapted to solve regression problems.
+The concepts of \gls{svm} will be discussed in the same chronological order.
+
+The decision boundary can be expressed as an hyperplane
+\begin{equation}
+	\hat{\mathbf{y}} = D(\mathbf{x}) = \mathbf{w} \cdot \mathbf{x} + w_0 
+\end{equation}
+with $
+\mathbf{y} \in \lbrace +1, -1 \rbrace^n ,\,
+\mathbf{w} \in \mathbb{R}^d ,\,
+\mathbf{x} \in \mathbb{R}^{n \times d} 
+$.
+A hyperplane which separate the data will satisfy the following equation: 
+\begin{equation}
+	\label{eq:svm01}
+	y_i(\mathbf{w} \cdot \mathbf{x}_i + w_0 ) \geqslant 1, \qquad i=1,\dots,n
+\end{equation}
+The distance from the decision boundary to the nearest points shall be denoted as $\tau$ and should be maximized. 
+Inequality \ref{eq:svm01} is an equation for the support vectors. 
+If we now take a vector from a positive support vector $x_+$ to a negative support vector $x_-$ and project it on to the unit vector of $w$ we get the width of the margin. 
+\begin{equation}
+	\label{eq:svm02}
+\begin{aligned} 
+	\text{width} &= (x_+ - x_-) \cdot \frac{w}{\|w\|} \\
+		&= ( (1-b)/w - (-1-b)/w ) ) \cdot \frac{w}{\|w\|} \\
+		&= \frac{2}{w} \cdot \frac{w}{\|w\|} = \frac{2}{\|w\|}
+\end{aligned}
+\end{equation}
+\td{draw sketch and make \ref{eq:svm02} on two lines}
+
+but before are the hyperplanes which go through the support vectors for positive sample: 
+\begin{equation}
+	y
+\end{equation}
 

### 2023-02-10 Thesis/chapter/032-alt-theory-calculations.tex
finsh SVM base

@@
 \Gls{svm} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training}. 
-\Gls{svm} is mainly used for classification, but can also be used for regression. 
-Classifiction works by spanning a hyperplane between two categories in a way that the closest points from each category have the largest distance to the hyperplane. 
-The distance from the points to the hyperplane is called margin.
-These points are called support vectors and are used to define the hyperplane 
-A \gls{svm} avoids overfitting by only using a subset - the support vectors - to fit the model. 
-\td{The goal is to fit $w$ and $b$ such that the margin (the distance from the descission boundary is maximal.
-As this the margin is inversely proportional to $\|w\|$, we aim to minimize $\|w\|$.
-With the contraint that all data points are correctly classified $y_i(x_iw-b)\geqslant1$.}
-In the same manner as no data points are found within the margin for classification, 
-no data points should be found outside of the margin. 
-If the data is not seperable by a hyperplane the kernel trick can be used. 
-The downside of \gls{svm} is that it is very
-\td{$\text{min}\frac{1}{N} \sum_{i=1}^{N} max(0,1- y_i(\mathbf{x}x_i-b)) + \lambda \|w\|$
-The downside of \gls{svm} is that it is very sensitive to outliers.}
-
-$\min_{w,b} \|w\|$
-
-$ y_i(w \cdot x_i - b)\leqslant 1$
-
-Summary of SVM from Cherkassky's \textit{Learning from Data}\cite{cherkassky1998learning}
+%
 The \gls{svm} was initially developed by V. Vapnik for the binary classification of seperable data, then improved to handle non-sperable data and eventually adapted to solve regression problems.
 The concepts of \gls{svm} will be discussed in the same chronological order. 
-
+%
+%\Gls{svm} is mainly used for classification, but can also be used for regression. 
+Classifiction works by spanning a hyperplane between two linearly separable categories in a way such that the closest points from each category have the largest distance to the hyperplane. 
+The distance from the points to the hyperplane is called margin $\tau$.
+These points are called support vectors and are used to define the hyperplane.
+A \gls{svm} avoids overfitting by only using a subset - the support vectors - to fit the model. 
+%Among the many advantages of \gls{svm} are the 
+%convex loss function, avoidance of overfitting by only using a subset of input vectors (the support vectors) to fit the model.
+The goal is to find the decision boundary which correctly classifies all samples with the biggest margin. 
+%\td{The goal is to fit $w$ and $b$ such that the margin (the distance from the descission boundary is maximal.
+%As this the margin is inversely proportional to $\|w\|$, we aim to minimize $\|w\|$.
+%With the contraint that all data points are correctly classified $y_i(x_iw-b)\geqslant1$.}
+%In the same manner as no data points are found within the margin for classification, 
+%no data points should be found outside of the margin. 
+%If the data is not seperable by a hyperplane the kernel trick can be used. 
+%\td{$\text{min}\frac{1}{N} \sum_{i=1}^{N} max(0,1- y_i(\mathbf{x}x_i-b)) + \lambda \|w\|$
+%The downside of \gls{svm} is that it is very sensitive to outliers.}
+%
+%$\min_{w,b} \|w\|$ 
+%
+%$ y_i(w \cdot x_i - b)\leqslant 1$ 
+%
+%Summary of SVM from Cherkassky's \textit{Learning from Data}\cite{cherkassky1998learning}
+%The \gls{svm} was initially developed by V. Vapnik for the binary classification of seperable data, then improved to handle non-sperable data and eventually adapted to solve regression problems.
+%The concepts of \gls{svm} will be discussed in the same chronological order. 
+%
 The decision boundary can be expressed as an hyperplane
 \begin{equation}
-	\hat{\mathbf{y}} = D(\mathbf{x}) = \mathbf{w} \cdot \mathbf{x} + w_0 
+	\hat{\mathbf{y}} = h(\mathbf{x}) = \mathbf{w} \cdot \mathbf{x} + b
 \end{equation}
@@
 \mathbf{y} \in \lbrace +1, -1 \rbrace^n ,\,
+\hat{\mathbf{y}} \in \mathbb{R}^n ,\,
 \mathbf{w} \in \mathbb{R}^d ,\,
@@
 $.
-A hyperplane which separate the data will satisfy the following equation: 
+The constraint of the positive and negative support vectors ($x^+$ and $x^-$, respectively) satisfying
+\begin{align}
+	\mathbf{w} \cdot x^+ + b &= 1 \\
+	\mathbf{w} \cdot x^- + b &= -1 
+\end{align}
+can be generalized to 
+%A hyperplane which separate the data will satisfy the following equation: 
 \begin{equation}
 	\label{eq:svm01}
-	y_i(\mathbf{w} \cdot \mathbf{x}_i + w_0 ) \geqslant 1, \qquad i=1,\dots,n
+	y_i(\mathbf{w} \cdot \mathbf{x}_i + b ) \geqslant 1 %\qquad i=1,\dots,n
 \end{equation}
-The distance from the decision boundary to the nearest points shall be denoted as $\tau$ and should be maximized. 
-Inequality \ref{eq:svm01} is an equation for the support vectors. 
-If we now take a vector from a positive support vector $x_+$ to a negative support vector $x_-$ and project it on to the unit vector of $w$ we get the width of the margin. 
+where $y_i$ being the labels of the training data. 
+The width of the margin can be inferred by projecting the vector spanning between two support vectors 
+on opposite sides of the decision boundary onto the unit vector perpendicular to the hyperplane. 
+%The distance from the decision boundary to the nearest points shall be denoted as $\tau$ and should be maximized. 
+%Inequality \ref{eq:svm01} is an equation for the support vectors. 
+If we now take a vector from a positive support vector $x^+$ to a negative support vector $x^-$ and project it on to the unit vector of $w$ (which is perpendicular to the hyperplane), 
+we get the width of the margin. 
 \begin{equation}
@@
 	\begin{aligned} 
-	\text{width} &= (x_+ - x_-) \cdot \frac{w}{\|w\|} \\
-		&= ( (1-b)/w - (-1-b)/w ) ) \cdot \frac{w}{\|w\|} \\
-		&= \frac{2}{w} \cdot \frac{w}{\|w\|} = \frac{2}{\|w\|}
+		2\tau &= (x^+ - x^-) \cdot \frac{\mathbf{w}}{\|\mathbf{w}\|} \\
+			&= (x^+ \cdot \mathbf{w} - x^-\cdot \mathbf{w} ) \cdot \frac{1}{\|\mathbf{w}\|} \\
+			&= ( (1-b) - (-1-b) ) \cdot \frac{1}{\|\mathbf{w}\|} \\
+			&= \frac{2}{\|w\|}
 	\end{aligned}
 \end{equation}
-\td{draw sketch and make \ref{eq:svm02} on two lines}
-
-but before are the hyperplanes which go through the support vectors for positive sample: 
+%\td{draw sketch and make \ref{eq:svm02} on two lines}
+Thus maximizing the margin is equivalent with minimizing $\|\mathbf{w}\|$. 
+By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we arrive at the loss function: 
 \begin{equation}
-	y
+	\label{eq:svm03}
+	\mathcal{L} = \frac{1}{2} \|\mathbf{w}\| - \sum_i^n \alpha_i [ y_i ( w_i \cdot x_i + b) -1 ] 
 \end{equation}
+which can be rewritten by some mathematical wizardry (setting the partial derivatives of the lagrangian 
+$\frac{\partial \mathcal{L}}{\partial \mathbf{w}}$ and $\frac{\partial \mathcal{L}}{\partial b}$ to zero and inserting into eq. (\ref{eq:svm03})): 
+\begin{equation}
+	\mathcal{L} = \sum_i^n \alpha_i - \frac{1}{2} \sum_i^n \sum_i^n \alpha_i \alpha_j y_i y_j \mathbf{x}_i \cdot \mathbf{x}_j 
+\end{equation}
+\td{write about kernel trick and non strick}
 

### 2023-02-12 Thesis/chapter/031-theory-calculations.tex
nearly finish theory

@@
 %What is statistics, though, and what seperates it from \gls{ml}? 
-More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of of 
+More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of 
 finding mathematical models to describe the data 
@@
 Other common architectures include linear regression, kernel ridge regression and support vector regression.
+
+\input{chapter/033-linreg-krr-svm.tex}
+
 There are also lesser know algorithms like 
 evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
-\gls{pso} algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simulta- neously\cite{villanova2010function}.
+\gls{pso} algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simultaneously\cite{villanova2010function}.
 %
@@
 
-A genetic algorithm (GA) is a search algorithm that uses principles of natural selection and genetics to optimize a search space.
+A \gls{ga} is a search algorithm that uses principles of natural selection and genetics to optimize a search space.
 A GA starts with a population of randomly generated solutions, or chromosomes, and then proceeds to breed them together to create new solutions.
@@
 
-\Gls{pso} also uses a starting population of particles where each experiment (particle) 
+A \gls{pso} also uses a starting population of particles where each experiment (particle) 
 is represented by its independent and dependent variables. 
-It was originally inspired by the behaviour of bird flocks and fish schools\cite{Kennedy1995,villanova2010function}.
+It was originally inspired by the behaviour of bird flocks and fish schools\cite{villanova2010function,Kennedy1995}.
 %"PSO is a population based heuristic inspired by the flocking behavior of birds. 
@@
 Each particle has an associated position and velocity. 
-Every movement across the search space is 
-additionally to a stochastic term
+Every movement across the search space is, 
+additionally to a stochastic term, 
 %stochastic and 
@@
 
+\iffalse
 \subsubsection{Kernel Ridge Regression and Support Vector Machine}
-
 \textbf{goal}
@@
 % Intro to feature selection https://axon.cs.byu.edu/Dan/778/papers/Feature%20Selection/guyon2.pdf
-
-\td{statistical methods to bewerten a model are: cross validation, leave-one-out validation ( special case of cross validation), correlation coefficient for linear fits, mean square error.
-methods to fit data are: lin reg, polynomial regression, ridge regression, KRR, SVM and?}
+\subsubsection{Validation}
+Validation is an important part of data analysis as it allows to estimate model errors. 
+Often used methods are cross validation, leave-
+statistical methods to bewerten a model are: 
+cross validation, leave-one-out validation ( special case of cross validation), correlation coefficient for linear fits, mean square error, mean absolute erro
+% https://www.researchgate.net/profile/Daniel-Berrar/publication/324701535_Cross-Validation/links/5cb4209c92851c8d22ec4349/Cross-Validation.pdf
+% https://www.sciencedirect.com/science/article/abs/pii/0304380093901052
+% https://www.eng.auburn.edu/~aesmith/files/janchap.pdf
+% https://www.sciencedirect.com/science/article/pii/S0379073806003239
+\td{cite from Hawkins 2004\cite{hawkins2004overfitting}}

### 2023-02-12 Thesis/chapter/032-alt-theory-calculations.tex
nearly finish theory

@@
 %\td{draw sketch and make \ref{eq:svm02} on two lines}
-Thus maximizing the margin is equivalent with minimizing $\|\mathbf{w}\|$. 
+Thus maximizing the margin is equivalent with minimizing $\|\mathbf{w}\|$ and minimizing $\frac{1}{2}\|\mathbf{w}\|^2$.
 By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we arrive at the loss function: 
@@
 \end{equation}
-which can be rewritten by some mathematical wizardry (setting the partial derivatives of the lagrangian 
-$\frac{\partial \mathcal{L}}{\partial \mathbf{w}}$ and $\frac{\partial \mathcal{L}}{\partial b}$ to zero and inserting into eq. (\ref{eq:svm03})): 
+which can be rewritten by some mathematical wizardry (setting the partial derivatives of the Lagrangian function
+$\frac{\partial \mathcal{L}}{\partial \mathbf{w}}$ and $\frac{\partial \mathcal{L}}{\partial b}$ 
+to zero and inserting into eq. (\ref{eq:svm03}))\cite{winston1992artificial,cherkassky1998learning}: 
 \begin{equation}
-	\mathcal{L} = \sum_i^n \alpha_i - \frac{1}{2} \sum_i^n \sum_i^n \alpha_i \alpha_j y_i y_j \mathbf{x}_i \cdot \mathbf{x}_j 
+	\mathcal{L} = \sum_i^n \alpha_i - \frac{1}{2} \sum_i^n \sum_j^n \alpha_i \alpha_j y_i y_j \mathbf{x}_i \cdot \mathbf{x}_j 
 \end{equation}

### 2023-02-12 Thesis/chapter/033-linreg-krr-svm.tex
nearly finish theory

--- 2023-02-12 Thesis/chapter/032-alt-theory-calculations.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Machine Learning and Statistics}
-
-\subsubsection{Introduction to AI, ML and statistics}
-\textbf{What is AI?} It is the interdisciplinary field of making a artificial inteligent agent. 
-What is intelligence though?
-Intelligence is not easily defined. Some definitions I agree with is that intelligence 
-includes learning from experience, finding solutions to new problems. 
-Creativity is also substencial for intelligence. 
-It is a goal in the field AI to immitate (and surpass) human intelligence. 
-The turing tests aims to test a computers intelligience by testing if it can trick a person into believing that the computer is person while a person tries to make the person believe that they are in fact a person.
-Approaches range from knowledge based systems over hard coded intstructions to machine learning. 
-%
-\textbf{Machine Learning} is the art of telling a machine or computer how to gain knowlegde from data (aka experience). 
-There are different problems and solutions. 
-The problems include image recognition, voice recognition, natural language processing, data prediction, classification, recommendation systems and so on. 
-%
-In order to solve these problems machine learning resorts to statistical methods such as
-linear regression, ridge regression. 
-Further machine learning methods not regularly seen in statistics are the 
-kernel trick, support vector machines, genetic algorithms and particle swarm algorithms. 
-The last two are special in the sense that they don't provide a certain regression method,
-but rather a frame work to choose the next sample which should be tested in a optimisation. 
-\td{mention classification vs regression and supervised vs supervised}
-%
-\textbf{Statistics} is a subfield of mathematics and emerged from the aim to summerzie large data sets 
-and extract information. In contrast to descriptive statistic, there is stochastic. 
-Stochastic statistic aims on predicting data points with probabilities. 
 %
 \textbf{Linear regression} is one of the simplest methods to predict data. 
-It besticht by its computational simplicity and easy interpretation. 
+It persuades by its computational simplicity and easy interpretation. 
 %Let's take this equation
@@
 \textbf{Ridge Regression} is like linear regression but with an extra term which penalizes steep regression functions.
-This extra term is scaled by a correction parameter $\lambda$. 
-The larger $\lambda$ the larger regularisation and the flatter the regression functions. 
-If $\lambda$ were infinite, then the regression function would be a flat line. 
-The correction term avoids overfitting. 
+This extra term which reduces overfitting is scaled by a correction parameter $\lambda$. 
+The larger, $\lambda$ the larger regularisation and the flatter the regression functions. 
+When $\lambda$ tends to infinity, we get an intercept-only model.
+When $\lambda$ is zero, the regularized loss function becomes the OLS loss function.
+%\td{A critique of ridge regression is that all the variables tend to end up in the model. The model only shrinks the coefficients.}
 \begin{equation}
@@
 
-\textbf{Kernel Ridge Regression}
-\gls{krr} combines ridge regression with the kernel method. 
-A kernel transforms data in such a way that a linear hyperplane (a line in one dimension, 
-a plane in two dimensions) can fit data in regression problem or seperate the data in classification problem. 
-A kernel is some kind of similarity measure. 
+%\textbf{Kernel Ridge Regression}
+\textbf{\gls{krr}} combines ridge regression with the kernel method. 
+A~kernel transforms data in such a way that a linear hyperplane (a line in one dimension, 
+a plane in two dimensions) can fit data in regression problems or seperate the data in classification problems. 
+A kernel is some kind of similarity measure 
+which fulfills the requirements of nonnegativity, symmetry, linearity\cite{rupp2015machine}.
 The following equations show definitions for 
@@
 sigmoidal (eq.~\ref{eq:sig-kernel}) and 
-radial basis functionial kernel~(eq. \ref{eq:rbf-kernel}).
+radial basis functionial kernel~(eq. \ref{eq:rbf-kernel}), with $\gamma$ as fixed hyperparameter and $c_0$ as parameter to optimize.
 \begin{align}
@@
 \end{align}
-These kernels fulfill the requirements of nonnegativity, symmetry, linearity\cite{rupp2015machine}.
-\td{Note that when $\lambda$ tends to zero, the regularized loss function becomes the OLS loss function.
-When $\lambda$ tends to infinity, we get an intercept-only model}
-\td{A critique of ridge regression is that all the variables tend to end up in the model. The model only shrinks the coefficients.}
-% from https://medium.com/@zxr.nju/the-classical-linear-regression-model-is-good-why-do-we-need-regularization-c89dba10c8eb
-%
-% https://scikit-learn.org/stable/modules/metrics.html#polynomial-kernel
-%
 
-\textbf{Support vector machines} 
-\Gls{svm} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training}. 
+%\textbf{Support vector machines} 
+\textbf{\Gls{svm}} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training}. 
 %
@@
 %
-%\Gls{svm} is mainly used for classification, but can also be used for regression. 
 Classifiction works by spanning a hyperplane between two linearly separable categories in a way such that the closest points from each category have the largest distance to the hyperplane. 
@@
 These points are called support vectors and are used to define the hyperplane.
-A \gls{svm} avoids overfitting by only using a subset - the support vectors - to fit the model. 
-%Among the many advantages of \gls{svm} are the 
-%convex loss function, avoidance of overfitting by only using a subset of input vectors (the support vectors) to fit the model.
+A \gls{svm} avoids overfitting by only using a subset of the data - the support vectors - to fit the model. 
 The goal is to find the decision boundary which correctly classifies all samples with the biggest margin. 
-%\td{The goal is to fit $w$ and $b$ such that the margin (the distance from the descission boundary is maximal.
-%As this the margin is inversely proportional to $\|w\|$, we aim to minimize $\|w\|$.
-%With the contraint that all data points are correctly classified $y_i(x_iw-b)\geqslant1$.}
-%In the same manner as no data points are found within the margin for classification, 
-%no data points should be found outside of the margin. 
-%If the data is not seperable by a hyperplane the kernel trick can be used. 
-%\td{$\text{min}\frac{1}{N} \sum_{i=1}^{N} max(0,1- y_i(\mathbf{x}x_i-b)) + \lambda \|w\|$
-%The downside of \gls{svm} is that it is very sensitive to outliers.}
-%
-%$\min_{w,b} \|w\|$ 
-%
-%$ y_i(w \cdot x_i - b)\leqslant 1$ 
-%
-%Summary of SVM from Cherkassky's \textit{Learning from Data}\cite{cherkassky1998learning}
-%The \gls{svm} was initially developed by V. Vapnik for the binary classification of seperable data, then improved to handle non-sperable data and eventually adapted to solve regression problems.
-%The concepts of \gls{svm} will be discussed in the same chronological order. 
 %
@@
 can be generalized to 
-%A hyperplane which separate the data will satisfy the following equation: 
 \begin{equation}
@@
 on opposite sides of the decision boundary onto the unit vector perpendicular to the hyperplane. 
-%The distance from the decision boundary to the nearest points shall be denoted as $\tau$ and should be maximized. 
-%Inequality \ref{eq:svm01} is an equation for the support vectors. 
 If we now take a vector from a positive support vector $x^+$ to a negative support vector $x^-$ and project it on to the unit vector of $w$ (which is perpendicular to the hyperplane), 
 we get the width of the margin. 
+\iffalse
 \begin{equation}
@@
 			&= \frac{2}{\|w\|}
+	\end{aligned}
+\end{equation}
+\fi
+\begin{equation}
+	\label{eq:svm02}
+	\begin{aligned} 
+		2\tau &= (x^+ - x^-) \cdot \frac{\mathbf{w}}{\|\mathbf{w}\|} 
+			= (x^+ \cdot \mathbf{w} - x^-\cdot \mathbf{w} ) \cdot \frac{1}{\|\mathbf{w}\|} \\
+			&= ( (1-b) - (-1-b) ) \cdot \frac{1}{\|\mathbf{w}\|} 
+			= \frac{2}{\|\mathbf{w}\|}
 	\end{aligned}
@@
 \end{equation}
+%
 \td{write about kernel trick and non strick}
-
-\begin{itemize}
-    \item \sout{intro to stat and ml}
-    \item \sout{say that although different will be abgehandelt in the same chapter}
-    \item \sout{basic statistics: MAE vs MSE, R, std, F-test} 
-    \item \sout{lin reg}
-    \item \sout{ridge regression}
-    \item \sout{kernel ridge regression}
-    \item \sout{support vector machine}
-    \item anova (categorical), PCA, step wise regression
-    \item all previous ananlyse data to predict, but don't tell me which data point is needed next 
-    \item DOE (add data acquisition)
-    \item genetic algorithm and pso (they combine data gen with regression/prediction and optimisation, actually incorporate prediction into selection process but don't per se specify which pred and optimisation)
-    \item comment: always tradeoff between complexity and interpretability
-    \item quesiton: which paragraph by GPT2?? 
-\end{itemize}

### 2023-02-12 Code/ML/2022/gs_krr.py

@@ -9,7 +9,7 @@ import dfply
 import argparse
 #
 #################
-# KERNEL FOR SVM
+# KERNEL FOR KRR
 kernel=["poly","rbf","sigmoid"] #HPGS
 # DEGREE OF POLYNOMIAL; ignored by rest
 degree=range(1,4) #HPGS

### 2023-02-13 Thesis/chapter/033-linreg-krr-svm.tex
start kernel

@@
 %\textbf{Kernel Ridge Regression}
+%%%%%%%%%%%%%%%%%%%%%%%%%%% { Kernel Ridge Regression } KRR %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \textbf{\gls{krr}} combines ridge regression with the kernel method. 
@@
 \end{align}
+A requirement for using kernels is having a dot product in the loss function. 
+This can be accomplished by expressing $\mathbf{k}$ with $\mathbf{X}$: $\mathbf{k}=\mathbf{X}^\top \mathbf{r}$
+\cite{rudin2020least}
 
-%\textbf{Support vector machines} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%% { Support vector machines } SVM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \textbf{\Gls{svm}} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training}. 
@@
 %
+\Gls{svm}s can handle non-perfect data by introducing a penalization for wrongly categorized samples. 
+\begin{equation}
+    L_H = sum_i^n max(0, 1- y_i ( \mathbf{w} \mathbf{x}_i + b ) 
+\end{equation}
+if the prediction and the true category don't agree, they have opposite signs and 
+their product will be a negative number.
+This is called a soft-margin \gls{svm} in contrast to the previously hard-margin \gls{svm}.
+
+A big advantage of \gls{svm} is that through the kernel trick non-linearly separable data 
+can be divided. 
 \td{write about kernel trick and non strick}

### 2023-02-14 Thesis/chapter/033-linreg-krr-svm.tex
finish kernel

@@
 \textbf{\gls{krr}} combines ridge regression with the kernel method. 
-A~kernel transforms data in such a way that a linear hyperplane (a line in one dimension, 
-a plane in two dimensions) can fit data in regression problems or seperate the data in classification problems. 
+A~kernel transforms data in such a way that a linear hyperplane (a line in two dimensions, 
+a plane in three dimensions) can fit data in regression problems or seperate the data in classification problems without actually doing the transormation for every data point. 
 A kernel is some kind of similarity measure 
@@
 This can be accomplished by expressing $\mathbf{k}$ with $\mathbf{X}$: $\mathbf{k}=\mathbf{X}^\top \mathbf{r}$
-\cite{rudin2020least}
+\cite{rudin2020least}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%% { Support vector machines } SVM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textbf{\Gls{svm}} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training}. 
+\textbf{\Gls{svm}} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training} . 
 %
@@
 Thus maximizing the margin is equivalent with minimizing $\|\mathbf{w}\|$ and minimizing $\frac{1}{2}\|\mathbf{w}\|^2$.
-By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we arrive at the loss function: 
+By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we arrive at the loss function which should be maximized: 
 \begin{equation}
 	\label{eq:svm03}
-	\mathcal{L} = \frac{1}{2} \|\mathbf{w}\| - \sum_i^n \alpha_i [ y_i ( w_i \cdot x_i + b) -1 ] 
+	\mathfrak{L} = \frac{1}{2} \|\mathbf{w}\|^2 - \sum_i^n \alpha_i [ y_i ( w_i \cdot x_i + b) -1 ] 
 \end{equation}
 which can be rewritten by some mathematical wizardry (setting the partial derivatives of the Lagrangian function
-$\frac{\partial \mathcal{L}}{\partial \mathbf{w}}$ and $\frac{\partial \mathcal{L}}{\partial b}$ 
+$\frac{\partial \mathfrak{L}}{\partial \mathbf{w}}$ and $\frac{\partial \mathfrak{L}}{\partial b}$ 
 to zero and inserting into eq. (\ref{eq:svm03}))\cite{winston1992artificial,cherkassky1998learning}: 
 \begin{equation}
-	\mathcal{L} = \sum_i^n \alpha_i - \frac{1}{2} \sum_i^n \sum_j^n \alpha_i \alpha_j y_i y_j \mathbf{x}_i \cdot \mathbf{x}_j 
+	\label{eq:svm04}
+	\mathfrak{L} = \sum_i^n \alpha_i - \frac{1}{2} \sum_i^n \sum_j^n \alpha_i \alpha_j y_i y_j \mathbf{x}_i \cdot \mathbf{x}_j 
 \end{equation}
 %
-\Gls{svm}s can handle non-perfect data by introducing a penalization for wrongly categorized samples. 
+%%%%%%%%%% SOFT MARGIN SVM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\textbf{Soft margin \gls{svm}} - in contrast to hard margin \gls{svm} is used if the data is non-seperable due to outliers\cite{cortes1995support}.
+Such data can be handeled by introducting a penalization term for wrongly categorized samples into the loss function. 
 \begin{equation}
-    L_H = sum_i^n max(0, 1- y_i ( \mathbf{w} \mathbf{x}_i + b ) 
+	\label{eq:svm-soft}
+	L_{SM} = \frac{2} {\|\mathbf{w}\|} + \sum_i^n max(0, 1- y_i ( \mathbf{w} \mathbf{x}_i + b ) 
 \end{equation}
-if the prediction and the true category don't agree, they have opposite signs and 
-their product will be a negative number.
-This is called a soft-margin \gls{svm} in contrast to the previously hard-margin \gls{svm}.
+If the prediction $\mathbf{w}\mathbf{x}_i+b$ and the true category $y_i$ don't agree, 
+they have opposite signs and their product will be a negative number.
+The substraction of a negative number will result in a positive penalizisation. 
+If the sample iis correctly predicted, the product will result in a positive number, 
+the substraction in a negative number and the maximum will be 0, if the sample is ousite of the margin.
 
-A big advantage of \gls{svm} is that through the kernel trick non-linearly separable data 
-can be divided. 
-\td{write about kernel trick and non strick}
+%%%%%%%%%%% KERNELS IN SVM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%A big advantage of \gls{svm} is that through the kernel trick non-linearly separable data can be divided. 
+%As mentioned before, a inner product is need to use the kernel trick. 
+The function we want to optimize (see eq. \ref{eq:svm04}) and its soft margin equivalent can both be expressed as inner products. 
+This allows us to seperate data not only with hyperplanes 
+but also with komplex decision boundaries due to the kernel trick. 
+Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the innerproduct of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper.
+\td{write about sv regrgession}
+%\td{write about kernel}

### 2023-02-15 Thesis/chapter/031-theory-calculations.tex
finish kernel
finish svm

@@
 whereas (classical) statistics is the domain of representing the data. 
-\td{talk about statistics, then the difference to Ml} 
+%\td{talk about statistics, then the difference to Ml} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \input{chapter/033-linreg-krr-svm.tex}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Population Based Optimisation Algorithms}
 
@@
 Validation is an important part of data analysis as it allows to estimate model errors. 
-Often used methods are cross validation, leave-
+Often used methods are analysis of residual error, cross validation and leave-one-out validation\cite{kartam1997artificial}.
+\td{to do read kartam}
 statistical methods to bewerten a model are: 
@@
 % https://www.sciencedirect.com/science/article/abs/pii/0304380093901052
-% https://www.eng.auburn.edu/~aesmith/files/janchap.pdf
 % https://www.sciencedirect.com/science/article/pii/S0379073806003239

### 2023-02-16 Thesis/chapter/031-theory-calculations.tex
finish theory

@@
 \subsection{Machine Learning and Statistics}
-\ds{
-statistics:
-	what is the difference between ml and stat? 
-		superficially very similar but different goals and diff rahmenbedingungen 
-    how can i use ANOVA 
-    linear regression 
-}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %Is machine learning just hyped statistics? No! 
-		%\href
 		%{https://doi.org/10.1177\%2F1352458520978648}
@@
 %
-%\begin{itemize}
-%	\item \td{let GPT-3 write}
-%	\item check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
-%	\item see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
-%	\item 
-%		\href
-%		{https://doi.org/10.1177\%2F1352458520978648}
-%		{Machine and deep learning in MS research are just powerful statistics – No}
-%\end{itemize}
-%
-%\td{
-%\url{https://stats.stackexchange.com/questions/5026/what-is-the-difference-between-data-mining-statistics-machine-learning-and-ai}
-%In principle both \gls{ml} and statistics use math to get information out of data. 
-%AI might use machine learning to create "intelligent" acting (playing a game or driving a  car). 
 \Gls{ml} tries to predict unseen data points and statistics is a subfield of maths 
@@
 %pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
-%}
-%What is statistics, though, and what seperates it from \gls{ml}? 
 More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of 
@@
 whereas (classical) statistics is the domain of representing the data.
-%\td{talk about statistics, then the difference to Ml} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\td{if i want to learn about support vector machine, read chapter 4,7,8 from "Learning from Data" by Cherkassky\cite{cherkassky1998learning} (TUBib 726-1998)}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 (in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
-%Another test ingenioused by Alan Turing, is that a human communicates with an unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
 Another test \textit{ingenioused} by Alan Turing, is the imitation game\cite{turing1950imitation}, nowadays known as Turing test.
@@
 The question is if \textbf{A} is replaced with a computer how the ratio of outcomes would deviate from the original ratio. 
-%
-%(in written form) and must judge who is the 
-%if they are dealing with a machine or a human being. 
-%
-%
-%\ds{It is easy for humans to come up with question to detect an AI, 
-%but when reading AI written articles\cite{gpt2020}, 
-%it's easy to see this test being passed in the near future.}
 %
@@
 It is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
-%Now, we can't - it's hard to - imagine to live without electricity. 
 Realms in which AI is gaining traction are: 
@@
 %
-%\todo{check out SVM and KRR}
-%
 \Gls{ml} is at the base of most \gls{ai}s.
@@
 An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
-%Two architecture which don't quite fit into this classification are Generative Adversarial Network (GAN) and jk
 Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
@@
 \subsubsection{EMMA}
-%\Gls{emma} and \gls{mars}
 \Gls{emma} is an implementation of the \gls{pso} in the \texttt{R} programming language. 
@@
 %
-The main advancements of \gls{mars} are the ability to fit (possibly complex) interactions and non-linearities. 
+The main advancements of \gls{mars} are the ability to fit (possibly complex) interactions and non-linearities without losing interpretability. 
 %
@@
 %%% FORWARD MARS
-The \gls{rf} is developed in a forward/backward stepwise recursive manner. 
+The \gls{rf} is developed in a forward/backward stepwise recursive manner\cite{friedman1988fitting}. 
 During the forward recursion terms are added in pairs until a certain number of terms is reached. 
@@
 Goodwin\cite{goodwin1977experiment}}
+%"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
 %
@@
 In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
-%
-%A straight forward design can be to randomly chose a certain number of experiments from the search space. 
-%Alternatively, a subset of from the 2-level factorial design can be chosen, which is called a fractional factorial design. 
 When a subset is chosen from the factorial design, it is called a fractional factorial design. 
 % PLACKETT_BURMAN
-%, a fractional factorial \gls{doe}. 
-%A straight forward design can be to randomly chose a certain number of experiments from the search space. 
-%
-%
 The \gls{pb}\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 
@@
 Latin hypercube \gls{doe}s are mainly used in computer simulations which are purely deterministic and therefore are very precise.
-%"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
 %
@@
 %
+Additional assumptions of \gls{anova} include: groups and levels should be independent, 
+residual error should follow normal distribution and variance within groups should be equal (homoscedasticity). 
 %\Gls{anova} analyses the means by means of mincing variances.
@@
 %\href{https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions}{(click here)}
-Additional assumptions of \gls{anova} include: groups and levels should be independent, 
-residual error should follow normal distribution and variance within groups should be equal (homoscedasticity). 
 %\href{https://statsandr.com/blog/anova-in-r/}{(click here)}
@@
 % Intro to feature selection https://axon.cs.byu.edu/Dan/778/papers/Feature%20Selection/guyon2.pdf
+\iffalse
+%%% VALIDATION 
 \subsubsection{Validation}
@@
 cross validation, leave-one-out validation ( special case of cross validation), correlation coefficient for linear fits, mean square error, mean absolute erro
-% https://www.researchgate.net/profile/Daniel-Berrar/publication/324701535_Cross-Validation/links/5cb4209c92851c8d22ec4349/Cross-Validation.pdf
-% https://www.sciencedirect.com/science/article/abs/pii/0304380093901052
-% https://www.sciencedirect.com/science/article/pii/S0379073806003239
 \td{cite from Hawkins 2004\cite{hawkins2004overfitting}}
+
+From Kartam1997: 
+Most Popular error measures are mean absolute error, mean squeared error and root mean squared error. 
+Different errors: 
+True error when tested with "an asymptotically large number of new data points that converge in the limit to the actual population distribution" (Weiss and Kulikowski 1991).
+Apparent error when tested with training data
+and 
+Testing error when tested with testing/validation error. 
+%
+Residual plots are a fast and easy way to analyze the model: $r_i = y_i - \hat y_i$. 
+Can check for systemic bias in general and residual distributions of training and test set.
+While the general bia for training set will be lower than for test set, they should obey the same distribution. 
+They allow to easily detect outliers and unsuitable regression functions. 
+%
+When dealing with \textbf{sparse data} the concept of resampling comes handy. 
+K-fold validation with two special cases. 
+k=n, then leave-one-out. 
+k=2, then train-and-test. 
+When $k\lln$, then $k/n$ samples are chosen randomly from the data set $x$-times. 
+\fi

### 2023-02-16 Thesis/chapter/060-results-material.tex
finish theory

@@
 Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
-An increase of the \gls{zrpro} concentration accelerates the aging process of the solution \td{what is this aging process chemically? oxidation, hydrolisation?}.
+An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
+%\td{what is this aging process chemically? oxidation, hydrolisation?}.
+The aging process was accelerated by being in contact with "fresh" air in contrast to being sealed. 
+It therefore dependent on the water or oxygen in the air corresponding to an oxidation or hyrolisation process.
+%
 Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 

### 2023-02-16 Thesis/chapter/061-results-emma.tex
finish theory

@@
 The best sample predicted by the algorithm is experiment number 13 with 
-%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
-%and lowest calcination heating rate and temperature. 
 lowest $c_{zr}$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$ and second highest $\lambda$. 
@@
 The remaining input variables remained more or less the same except for the 3rd generation. 
-\td{why?}
+%\td{why?}
 %
@@
 The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
-Indeed, the samples with the lowest \textit{optimisands} are amoung the first generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).
+Indeed, the samples with the lowest \textit{optimisands} are among the first generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).
 
-In figure \ref{fig:emma-gen} we can see the two measured main \textit{optimisands}, 
-$\gamma$ and $\rho$, of each particle at generations 1 to 4. 
-%for each particle included in the optimization. 
-%It shows a clear trend which indicates that the optimization worked even though 
+In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimisands}, 
+$\gamma$ and $\rho$, of each particle at each generation.
+They points at generation indicate particles which were not included to be propagated. 
+Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
+%
 Both variables were to be minimized and show a clear trend towards low values with increasing generation, 
@@
 and the chosen samples where not exactly as expected. 
-Neither were the measurements for these samples, which might be due to the high measuring error of samples and variation of quality due to uncontrolled independent variables like room temperature or humidity.
+Neither expected were the measurements for these samples, which might be due to the high measuring error of samples and variation of quality due to uncontrolled independent variables like room temperature or humidity.
+%
+Figures \ref{fig:g-tcal} and \ref{fig:phd-tcal} the correlation of calcination temperature $T_{cal}$ and $\gamma$ and $\rho$ can be seen clearly.
 
@@
 		(d)~calculated pin hole density~$\rho$ against calcination temperature $T_{cal}$
-		\td{describe more in-depth in text}
+		%\td{describe more in-depth in text}
 	}
@@
 The two independent variables $v{cal}$ and $\lambda$ were included as \textit{optimisands} for two reasons: 
-Maximizing the calcination velocity and minimizing the number of \td{layers/layer application iterations} leads to minimization of process time.
+Maximizing the calcination velocity and minimizing the number of layer application iterations leads to minimization of process time.
 This optimization would be better placed in a follow up study. 
@@
 This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimisands} and thus additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables.
-The second flaw is that there are obsiously better methods to assess the quality of a model that to make it more complex.
-Good alternatives would have been leave-one-out or cross validation.
+The second flaw is that there are obsiously better methods to assess the quality of a model than to make it more complex.
+%Good alternatives would have been leave-one-out or cross validation.
+Validation methods for sparse data include resampling vie k-fold cross validation\cite{kartam1997artificial}.
 
+\iffalse
 \td{
@@
 %}
+\fi
 

### 2023-02-16 Thesis/chapter/062-post-emma.tex
start incorporate post-emma into theory
finish theory

@@
+\subsection{Post-EMMA}
 \label{sec:res-post-emma}
@@
 %\textbf{EMMA}
-The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance/effect/correlation} 
-on the calcination temperature $T_{cal}$ with regard to the \td{measurables} of the conductance. 
+The \gls{rf} produced by the last iteration of \gls{emma} (see equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}) put a high significance
+%/effect/correlation
+on the calcination temperature $T_{cal}$ with regard to the 
+measures of the conductance. 
 \Gls{anova} is used to double check this. 
 %Now \gls{anova} can be used to check if the data 
+%\td{ANOVA was used to check if \gls{bf} identified by \gls{emma} are reasonable.}
 
 \textbf{What can/did we test?}
-With \gls{anova} we can check if the probability of arriving at these results was by pure chance or not. 
+the probability of arriving at these results was by pure chance can be checked with \gls{anova}. 
 The null hypothesis is that the results were obtained by pure chance without any dependence of the insulation of a sample on the process variables.
@@
 Usually, the $\alpha$-value is chosen to be 0.01 or 0.05\cite{hoffman2020concept,sellke2001pvalues}.
-The choice of a relatively high alpha-value is motivated by the rather small amount of data and low \td{EPV}.
+The choice of a relatively high $alpha$-value is motivated by the rather small amount of data and low events per varible ratio.
+\ds{
 As mentioned by Sellke et al.\cite{sellke2001pvalues} a p-value of 0.05 might tempt 
@@
 whereas the frequency is much higher. 
+A p-value of 0.01 and 0.05  mean that under the assumption that the null hypothesis is correct, 
+there is a 1\% and 5\% chance of arriving at such data as observed.
+%The results should thus be taken with a grain of salt. 
+}
 %1 out of 20 times this result could be 
@@
 %chance but due to the influence of the independent variables on the dependent variables. 
-\td{could test anova on different generations data sets}
+%\td{could test anova on different generations data sets}
 
@@
 %indep groups are not equal and that there is at least one group that is different. 
-For both $\rho$ and $\lambda$ (for both the \gls{emma} dataset and the extended dataset) 
-the F values for $T_{cal}$ were in all cases under 0.01, 
+For both $\rho$ and $\lambda$ (for both the \gls{emma} dataset and the extended dataset (=\gls{emma}+pre\gls{emma})) 
+the F-values for $T_{cal}$ were in all cases under 0.01, 
 indicating a real influence of $T_{cal}$ on the conductance.
-Both datasets exhibit a p-value $< 0.05$ for the interaction $T_{cal}$:$v_{cal}$ on $\rho$.
-\td{And the extended data set has p-value smaller than 0.01 of vcal on phd. 
-Whereas vcal on phd for \gls{emma} dataset has p-value of slightly over 0.05.}
-\td{why tcal:vcal on phd the same for both datasets? zufall}
+Furthermore, both datasets exhibit a p-value $< 0.05$ for the interaction $T_{cal}$:$v_{cal}$ on $\rho$
+and the extended data set has p-value smaller than 0.01 of $v_{cal}$ on $\rho$. 
+Whereas $v_{cal}$ on $\rho$ for \gls{emma} dataset has p-value of slightly over 0.05
+%\td{why tcal:vcal on phd the same for both datasets? zufall}
 
 \textbf{What do the results mean?} 
-Anova bestaetigt that TCal has influence on both G and phd. 
-\td{how to interpret p-values of 0.01 and 0.05? 
-They mean that under the assumption that the null hypothesis is correct, 
-there is a 1\% and 5\% chance of arriving at such data as observed.}
+\Gls{anova} confirms that $T_{cal}$ has influence on both $\gamma$ and $\rho$. 
 It seems that the probability of getting such data per chance that Tcal has no influence 
-(null hypothesis is true) is less then 5\% (even less than 1\%). \td{NO bcs \cite{sellke2001pvalues}}
-Important to mention, that anova uses categorical data for inputs, 
-where our data is numerical and thus information is lost
+(null hypothesis is true) is less then 5\% (even less than 1\%). 
+%\td{NO bcs \cite{sellke2001pvalues}}
+It is important to mention, that \gls{anova} assumes categorical data for inputs, 
+where our data is numerical and thus information is lost.
 
@@
 \subsubsection{Linear Regression}
-I thought that the influnce of $conc$ and $\lambda$ are the biggest, but they are just the smalles absolute values. 
-Thus, eventhough $T_{cal}$ might have a smaller coefficient for lin reg, the influence on the dependent variable might be larger. 
-The biggest influece on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{doc}$. 
-Both $T_{cal}$ and $T_{doc}$ have positive coefficients, i.e. a negative influence on the resistance. 
-Then both $\lambda$ and $v_{doc}$ both have about a fift ob the largest influence and a negative influence. 
+I thought that the influence of $c_{zr}$ and $\lambda$ are the biggest, but they are the smallest absolute values. 
+Thus, even though $T_{cal}$ might have a smaller coefficient for linear reg, the influence on the dependent variable might be larger. 
+The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
+Both $T_{cal}$ and $T_{DB}$ have positive coefficients, i.e. a negative influence on the resistance. 
+Then both $\lambda$ and $v_{DB}$ both have about a fifth ob the largest influence and a negative influence. 
 An indication that the data is strongly tainted by error (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41, 
-which is (sad but true) even unterboten by the $R^2$ of lin fit of $G$, 0.34. 
+which is (sad but true) even undercut by the $R^2$ of linear fit of $G$, 0.34. 
 The coefficients, though share the signs. 
 This is only true if the extended data set is used and therefore again rather by chance. 
-It is even more \td{erstaunlich} that EMMA managed to decrease the average of $pG$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}. 
-Or was is only luck?
+It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}.
 
 $v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality.
-Was zu erwarten war.
 

### 2023-02-17 Thesis/chapter/062-post-emma.tex
lin reg

@@
 %\textbf{EMMA}
-The \gls{rf} produced by the last iteration of \gls{emma} (see equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}) put a high significance
+The \gls{rf}s produced by the last iteration of \gls{emma} (see equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}) put a high significance
 %/effect/correlation
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%% LIN REG %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 \subsubsection{Linear Regression} 
-I thought that the influence of $c_{zr}$ and $\lambda$ are the biggest, but they are the smallest absolute values. 
-Thus, even though $T_{cal}$ might have a smaller coefficient for linear reg, the influence on the dependent variable might be larger. 
-The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
-Both $T_{cal}$ and $T_{DB}$ have positive coefficients, i.e. a negative influence on the resistance. 
-Then both $\lambda$ and $v_{DB}$ both have about a fifth ob the largest influence and a negative influence. 
-An indication that the data is strongly tainted by error (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41, 
-which is (sad but true) even undercut by the $R^2$ of linear fit of $G$, 0.34. 
-The coefficients, though share the signs. 
-This is only true if the extended data set is used and therefore again rather by chance. 
-It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}.
-
-$v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality.
-
+%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influennced by the Zirconium concentrain in the starting solution $c_{zr}$ and the number of layers applied $\lambda$, but their coefficients are the smallest in absolute values.
+The coefficients of
+the Zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$ are largest in value, but the values which are taken by $c_{zr}$ and $\lambda$ are the smallest among the input variables.
+%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influennced by
+%but their coefficients are the smallest in absolute values. 
+%
 \begin{align}
@@
 \end{align}
+%
+All terms have the same signs in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign except the intercept and $c_{zr}$. 
+$T_{cal}$ and $T_{DB}$ have positive coefficients, i.e. a negative influence on the resistance 
+and $\lambda$,$v_{DB}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
+An indication that the data is strongly tainted by error (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
+which is (sad but true) even undercut by the $R^2$ of linear fit of $\hat\gamma$, 0.34. 
+%The coefficients, though share the signs. 
+%This is only true if the extended data set is used and therefore again rather by chance. 
+When the linear regression is trained on the complete data set, all terms have the same sign. 
+%It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}. 
+%
+\begin{table}[htb]
+	\center
+	\begin{tabular}{cccccccc}
+		        & $c_{zr}$      & $\lambda$     & $v_{DB}$      & $T_{DB}$      & $v_{cal}$     & $T_{cal}$\\
+				\hline\hline
+				$\rho$          &2.04   &46.58  &1.15   &9.21   &13.50  &27.52\\
+				$\gamma$        &10.24  &7.10   &16.46  &10.97  &7.68   &47.55\\
+				\hline\hline
+	\end{tabular}
+	\label{tab:lin-reg-influence}
+	\caption{Influences of input variables on output variables in percent according to linear regression.}
+\end{table}
+%
+Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
+The influence was calculated by the formula: $I_i=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i$ is average value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression.
+%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
+The biggest influence on $\hat\rho$ and $\hat\gamma$ are $\lambda$ and $T_{cal}$. 
+While $T_{cal}$ is the second largest influence on $\hat\rho$ as well it is noteworthy that $\lambda$ contributes the least to $\hat\gamma$. 
+Furthermore the influence on $\hat\rho$ is dominated by $\lambda$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
+Different distributions were not expected. 
+This can have two reasons: 
+either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
+%
 
-Do multi linear reg like in Peprah et al. 2017\cite{peprah2017appraisal}.
+$v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality. 
+%Do multi linear reg like in Peprah et al. 2017\cite{peprah2017appraisal}.
+%
 

### 2023-02-17 Code/Statistics/scripts/linreg-influence.py

@@ -1,0 +1,52 @@
+#!/usr/bin/env python3
+
+import argparse
+
+# MAKE COMMAND LINE ARGUMENTS
+parser = argparse.ArgumentParser(description ='Check influence of individual terms with EMMA data set and complete data set and output as LaTeX tabular')
+parser.add_argument('--fe',dest ='fit_emma',action='store_true', help='fit with EMMA dataset [default]')
+parser.add_argument('--fa',dest ='fit_all',action='store_true', help='fit with complete dataset')
+args = parser.parse_args()
+
+if args.fit_all:
+    p_c_zr=0.017; p_l=0.22; p_v_db=0.013; p_t_db=0.0047; p_v_cal=0.00013; p_t_cal=0.0026    # complete data set
+    g_c_zr=2.7; g_l=0.69; g_v_db=1.4; g_t_db=0.43; g_v_cal=0.012; g_t_cal=0.14 # complete data set
+else:
+    p_c_zr=0.022; p_l=0.22; p_v_db=0.0029; p_t_db=0.0058; p_v_cal=0.00085; p_t_cal=0.0026  # EMMA data set
+    g_c_zr=3.2; g_l=0.97; g_v_db=1.2; g_t_db=0.2; g_v_cal=0.014; g_t_cal=0.13  # EMMA data set
+p=[p_c_zr, p_l, p_v_db, p_t_db, p_v_cal, p_t_cal]
+
+g=[g_c_zr, g_l, g_v_db, g_t_db, g_v_cal, g_t_cal]
+
+c_zr=(2+5)/2
+l=(4+12)/2
+v_db=(10+20)/2
+t_db=(40+80)/2
+v_cal=(120+1080)/2
+t_cal=(300+500)/2
+m=[c_zr, l, v_db, t_db, v_cal, t_cal]
+n=["c_zr", "l", "v_db", "t_db", "v_cal", "t_cal"]
+n=["$c_{zr}$", "$\\lambda$", "$v_{DB}$", "$T_{DB}$", "$v_{cal}$", "$T_{cal}$"]
+
+
+def get_influence(quantities,mean=m,names=n):
+    sum=0
+    for i in range(len(quantities)):
+        sum+= quantities[i]*mean[i]
+    for i in range(len(quantities)): 
+        print("\t&%.2f" %(quantities[i]*mean[i]/sum*100),end="")
+    print("\\\\")
+
+for i in n:
+    print("\t&",i,end="")
+    
[…]

### 2023-02-17 Code/Statistics/scripts/linreg.py

@@ -17,6 +17,8 @@ parser.add_argument('--pa',dest ='pred_all',action ='store_true', help ='predict
 parser.add_argument('--pe',dest ='pred_emma',action ='store_true', help ='predict Y values with EMMA dataset')
 parser.add_argument('--pi',dest ='pred_intra',action ='store_true', help ='predict Y values with pre-EMMA-intra dataset')
 parser.add_argument('--pp',dest ='pred_pre',action ='store_true', help ='predict Y values with pre-EMMA dataset')
+parser.add_argument('--fe',dest ='fit_emma',action='store_true', help='fit with EMMA dataset [default]')
+parser.add_argument('--fa',dest ='fit_all',action='store_true', help='fit with complete dataset')
 parser.add_argument('-r', '--regresssion',dest ='print_reg',action ='store_true', help ='print regression functions')
 parser.add_argument('-y', '--yindex', dest ='y_index',action ='store', choices={'0','2','3','7','10'}, default='0', help ='y to fit: 0=all; 2=G; 3=phd; 7=layers; 10=vCal [default=0]')
 args = parser.parse_args()
@@ -79,7 +81,12 @@ X_intra=get_x(data_intra)
 Y_intra=get_y(data_intra,args.y_index)
 #
 # DO LINEAR REGRESSION
-reg = LinearRegression().fit(X_emma,Y_emma)
+if args.fit_all : 
+    reg = LinearRegression().fit(X_all,Y_all)
+    train_dataset="complete dataset"
+else:
+    reg = LinearRegression().fit(X_emma,Y_emma)
+    train_dataset="EMMA dataset"
 Y_emma_pred = reg.predict(X_emma)
 Y_pre_pred = reg.predict(X_pre)
 Y_intra_pred = reg.predict(X_intra)
@@ -90,7 +97,8 @@ if args.y_index == "0":
     y_name = "all"
 else: 
     y_name = names[int(args.y_index)]
-print("Lin regression for", y_name)
+#print("Lin regression for", y_name)
+print("Lin regression trained with", train_dataset)
 print("Reg score", reg.score(X_emma,Y_emma))
 if args.print_mse: 
     print("MAE(emma): ",MAE(Y_emma_pred,Y_emma))

### 2023-02-18 Thesis/chapter/062-post-emma.tex
finish linreg

@@
 
-%%%%%%%%%%%%%%%%%%%% LIN REG %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%% LIN REG %% lin reg %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 \subsubsection{Linear Regression} 
 %Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influennced by the Zirconium concentrain in the starting solution $c_{zr}$ and the number of layers applied $\lambda$, but their coefficients are the smallest in absolute values.
-The coefficients of
-the Zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$ are largest in value, but the values which are taken by $c_{zr}$ and $\lambda$ are the smallest among the input variables.
-%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influennced by
+
+%\todo{what was fitted how?}
+The data obtained from the \gls{emma} optimisation was used to fit a linear model. 
+The biggest difference of the linear model to \gls{emma} is that all variables are included, that the \gls{bf}s are strictly linear and that there are no interaction terms. 
+The coefficients of the $\lambda$ term have the same sign in equations \ref{eq:emma-phd3},\ref{eq:emma-G3},\ref{eq:emma-phd4},\ref{eq:emma-G4} (\gls{emma} \gls{rf}s) and \ref{eq:linreg-phd},\ref{eq:linreg-G} and have comparable magnitudes too.
+%
+%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influenced by
 %but their coefficients are the smallest in absolute values. 
@@
 		\label{eq:linreg-phd}
-		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{DB} + 0.0058\cdot T_{DB} \\
+		\hat{\rho} &=  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{DB} + 0.0058\cdot T_{DB} \\
 		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
@@
 		\label{eq:linreg-G}
-		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot \lambda - 1.2\cdot v_{DB} + 0.2\cdot T_{DB} \\
-			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
+		\hat{\gamma} &={}  \qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot \lambda \,\,\quad - 1.2\cdot v_{DB} + \,\,\,\quad 0.2\cdot T_{DB} \\
+			& \qquad - 0.014\cdot v_{cal} \quad + 0.13\cdot T_{cal} + 7.2
+%		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot \lambda - 1.2\cdot v_{DB} + 0.2\cdot T_{DB} \\
+%			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
 	\end{split}
@@
 %
-All terms have the same signs in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign except the intercept and $c_{zr}$. 
-$T_{cal}$ and $T_{DB}$ have positive coefficients, i.e. a negative influence on the resistance 
-and $\lambda$,$v_{DB}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
-An indication that the data is strongly tainted by error (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
+All terms in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign except the intercept and $c_{zr}$. 
+%
+More particularly, $T_{cal}$ and $T_{DB}$ have positive coefficients, i.e. a negative influence on the resistance 
+and $\lambda$, $v_{DB}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
+An indication that the data is strongly tainted by noise (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
 which is (sad but true) even undercut by the $R^2$ of linear fit of $\hat\gamma$, 0.34. 
@@
 %This is only true if the extended data set is used and therefore again rather by chance. 
-When the linear regression is trained on the complete data set, all terms have the same sign. 
+When the linear regression is trained on the complete data set, all terms have the same sign compared to the \gls{emma} data set trained linear model. 
 %It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}.
+$v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality and thus are not displayed here. 
 %
@@
 				\hline\hline
-				$\rho$          &2.04   &46.58  &1.15   &9.21   &13.50  &27.52\\
-				$\gamma$        &10.24  &7.10   &16.46  &10.97  &7.68   &47.55\\
+				$\hat\rho$          &2.04   &46.58  &1.15   &9.21   &13.50  &27.52\\
+				$\hat\gamma$        &10.24  &7.10   &16.46  &10.97  &7.68   &47.55\\
 				\hline\hline
@@
 \end{table}
+
 %
+Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$ are largest in value, but the values which are taken by $c_{zr}$ and $\lambda$ itself are the smallest among the input variables.
 Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
-The influence was calculated by the formula: $I_i=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i$ is average value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression.
+In order to compare, the influence was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{min}+x_{max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression.
 %The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
-The biggest influence on $\hat\rho$ and $\hat\gamma$ are $\lambda$ and $T_{cal}$. 
+The biggest influence on $\hat\rho$ is  $\lambda$, followed by $T_{cal}$. 
 While $T_{cal}$ is the second largest influence on $\hat\rho$ as well it is noteworthy that $\lambda$ contributes the least to $\hat\gamma$. 
-Furthermore the influence on $\hat\rho$ is dominated by $\lambda$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
-Different distributions were not expected. 
-This can have two reasons: 
-either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
+That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
+Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artefact of the noise rather than a process property. 
+%Furthermore the influence on $\hat\rho$ is dominated by $\lambda$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
+%Different distributions were not expected. 
+The two very different distributions of influence among the input variables can have three reasons:
+%This can have two reasons: 
+(1) the linear function is not a suitable regression function for the data distribution.
+(2) the signal to noise ratio is so low that the noise rather than the signal was fitted.
+(3) the \textit{optimizands} indeed represent different properties of the material.
+%either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
 %
 
-$v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality. 
 %Do multi linear reg like in Peprah et al. 2017\cite{peprah2017appraisal}.
@@
 \subsubsection{Grid Search}
-For \gls{krr} and {svm} I had to find out what the ideal hyper parameters were. 
-So, I anstellen a grid search with the following hyperparameters: 
+The ideal hyper parameters have to be found for \gls{krr} and \gls{svm}.
+To do so a grid search over a set of hyper parameters was executed. 
+Both \gls{krr} and \gls{svm} following kernel: radial basis function, sigmoid, and polynomial with degree 1 to 4. 
+Gamma = {
+
+%KRR
+%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10] #HPGS
+%alpha=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2] #, 10, 50, 100] #HPGS
+
+%SVM
+%C= np.array(range(1,20))*0.05 # HPGS
+%epsilon= np.array(range(1,20))*0.2 # HPGS
+%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, "scale"] # HPGS
+
 %kernel=["poly","rbf"]#,"sigmoid"]

### 2023-02-19 Thesis/chapter/062-post-emma.tex
start Grid Seach

--- 2023-02-17 Thesis/chapter/062-post-emma.tex
@@
 %\iffalse
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 \subsubsection{Grid Search}
@@
 Now what are C,epsilon and gamma?
+
+\td{which parameters}
+The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
+The kernel took the form of \gls{rbf}, sigmoid and polynomial with degree 1--4.
+The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
+and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
+Note that $\gamma_{ml}$ is used differently in each kernel. 
+The kernels for \gls{svm} were the same and further hyper parameters were 
+$C$, $\varepsilon$ and $\gamma_{ml}$, where $C$ took the values 0.05--1 with 0.05 steps, $\varepsilon$ 0.02--4 with 0.2 steps and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
+Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
+and $\sigma(\mathbf{X})$ the variance of the input variables. 
+\td{how, every combination}
+Each grid search calculation was calculated with and without scaling the data before the optimisation. 
+For each optimisation \gls{mae}, \gls{mse}, $sigma(\mathbf{y})$ and $\sigma(\mathbf{\hat{y}})$ were calculated.
+
+\td{what were best results/hyper parameters}
+
+%# KRR
+%# some kind of scaling factor; can be set to auto/scale, include into list? 
+%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10] #HPGS
+%# alpha: bigger alpha, bigger regularisation 
+%alpha=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2] #, 10, 50, 100] #HPGS
+
+% SVM
+%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
+%https://scikit-learn.org/stable/modules/svm.html#svc
+%# regularization parameter
+%C= np.array(range(1,20))*0.05 # HPGS
+%# epsilon-tube size for no penalty; rather large 
+%epsilon= np.array(range(1,20))*0.2 # HPGS
+%# some kind of scaling factor; can be set to auto/scale, include into list?  
+%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, "scale"] # HPGS
 
@@
         lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
-        ML KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
-        ML SVM& 15  415&    26& 1050&   28& 1588&   19& 677\\
+        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
+        SVM& 15  415&    26& 1050&   28& 1588&   19& 677\\
     \hline\hline
@@
         lin Reg&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
-        ML KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
-        ML SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
+        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
+        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
     \hline\hline

### 2023-02-19 Code/ML/2022/gs_svm.py

@@ -10,10 +10,10 @@ import argparse
 #
 # KERNEL FOR SVM
 kernel=["poly","rbf","sigmoid"] # HPGS
-# regularization parameter
-C= np.array(range(1,20))*0.05 # HPGS
 # DEGREE OF POLYNOMIAL; ignored by rest
 degree=range(1,4) # HPGS
+# regularization parameter
+C= np.array(range(1,20))*0.05 # HPGS
 # epsilon-tube size for no penalty; rather large 
 epsilon= np.array(range(1,20))*0.2 # HPGS
 # some kind of scaling factor; can be set to auto/scale, include into list? 

### 2023-02-19 Thesis/chapter/062-post-emma.tex
grid search v2

@@
 %\iffalse
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
@@
 So, I anstellen a grid search with the following hyperparameters: 
-%kernel=["poly","rbf"]#,"sigmoid"]
-%C= np.array(range(1,20))*0.05
-%degree=range(1,6)
-%epsilon= np.array(range(1,20))*0.2
-%gamma=[0.0,0.1,1.0,10.0]
-%#param = {"kernel":kernel, "C":C, "degree":degree, "epsilon":epsilon, "gamma":gamma }
-%C=[1,0.1]; degree=[3]; epsilon=[1,2]; gamma=['scale']
-Now what are C,epsilon and gamma?
-
-\td{which parameters}
+%
+%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
+%https://scikit-learn.org/stable/modules/svm.html#svc
+%# KRR
+%# some kind of scaling factor; can be set to auto/scale, include into list? 
+%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10] #HPGS
+%# alpha: bigger alpha, bigger regularisation 
+%alpha=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2] #, 10, 50, 100] #HPGS
+%
+% SVM
+%# regularization parameter
+%C= np.array(range(1,20))*0.05 # HPGS
+%# epsilon-tube size for no penalty; rather large 
+%epsilon= np.array(range(1,20))*0.2 # HPGS
+%# some kind of scaling factor; can be set to auto/scale, include into list?  
+%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, "scale"] # HPGS 
+%
+\td{which parameters?}
 The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
@@
 The kernels for \gls{svm} were the same and further hyper parameters were 
-$C$, $\varepsilon$ and $\gamma_{ml}$, where $C$ took the values 0.05--1 with 0.05 steps, $\varepsilon$ 0.02--4 with 0.2 steps and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
+$C$, $\varepsilon$ and $\gamma_{ml}$, where $C$ took the values 0.05--0.95 with 0.05 steps, $\varepsilon$ 0.02--3.8 with 0.2 steps and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}.
 Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
 and $\sigma(\mathbf{X})$ the variance of the input variables.
-\td{how, every combination}
+
+\td{how and what?}
 Each grid search calculation was calculated with and without scaling the data before the optimisation. 
 For each optimisation \gls{mae}, \gls{mse}, $sigma(\mathbf{y})$ and $\sigma(\mathbf{\hat{y}})$ were calculated. 
+For each method (\gls{krr} and \gls{svm}) and each kernel the parameters with the lowest \gls{mae} were chosen.
 
@@
 
-%# KRR
-%# some kind of scaling factor; can be set to auto/scale, include into list? 
-%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10] #HPGS
-%# alpha: bigger alpha, bigger regularisation 
-%alpha=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2] #, 10, 50, 100] #HPGS
-
-% SVM
-%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
-%https://scikit-learn.org/stable/modules/svm.html#svc
-%# regularization parameter
-%C= np.array(range(1,20))*0.05 # HPGS
-%# epsilon-tube size for no penalty; rather large 
-%epsilon= np.array(range(1,20))*0.2 # HPGS
-%# some kind of scaling factor; can be set to auto/scale, include into list?  
-%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, "scale"] # HPGS
-
-Since the data set was very small, I could be generous with the grid search even on relatively humble hardware (intel i7-8550U).
+%Since the data set was very small, I could be generous with the grid search even on relatively humble hardware (intel i7-8550U).
 
@@
         KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
-        SVM& 15  415&    26& 1050&   28& 1588&   19& 677\\
+        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
     \hline\hline
@@
 
+%\fi
+
+\iffalse
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 \subsubsection{PCR?}
-
-%\fi
-
 \subsubsection{Further}
@@
 What are the measurables. 
+\fi
 

### 2023-02-19 Thesis/chapter/063-discussion.tex
start write alt cacl theory
finish theory
start Grid Seach
grid search v2

@@
-\subsection{Diskussion}
+\subsection{Discussion}
 \subsubsection{Mistakes and Solutions}
-This chapter is structured as a letter 
-which my present self thinks that would have helped my past self 
-if recieved before the start of the practical part of my master practikum:\\
+%This chapter is structured as a letter 
+%which my present self thinks that would have helped my past self 
+%if recieved before the start of the practical part of my master practikum:\\
 
-to discuss: results from EMMA or rather which the data present are counter intuitive. 
-why lowest conductivity with lowest TCal and why is there a minimum for layers? 
-low TDOC results in lower conductivity... okay
+%to discuss: results from EMMA or rather which the data present are counter intuitive. 
+%why lowest conductivity with lowest TCal and why is there a minimum for layers? 
+%low TDOC results in lower conductivity... okay 
+\subsubsection{ad results}
+why correlation $\gamma$?
+\subsubsection{tips for next time}
+\begin{itemize}
+    \item \textbf{planning} gives chance of zooming out, force oneself to get an overview and to decide how much time on each task
+    \item \textbf{research} phase is most important, dig into basics, discuss ideas with colleagues or go into detail about plan.
+Understand details of methods.
+Make a dummy run.
+Collect (dis-)advantages of different methods.
+Like in design project: do as many and as deverse solutions as possbile.
+Compare and combine the best parts.
+Reading will let learn from others mistakes.
+    \item \textbf{objective} should be defined as clear as possible.
+It will help to set a clear goal for each todo, e.g.
+the primary goal of a screening experiment is to identify the active factors.\cite{miller2001using} Which question should be answered and aufstellen a null Hypothesis.
+This is often very trivial, but let's you focus on the correct path.
+    \item \textbf{keep it simple}
+
+\end{itemize}
 
@@
 \td{"However, if the effect size is small or there is high multicollinearity, you may need more observations per term." -same source}
-
-\iffalse
-Dear Johann,
-
-I know that you (I) won't believe this but I'm you in the future. 
-So you are me in the past and I have a few hints on how to avoid some stone in your way 
-and how to hopefully be more successful in you master thesis. 
-"I make a plan. I break a plan. But I'm never without a plan." - a nice quote which I couln't zuschreiben, but which holds a lot of truth. 
-Planning can give you the chance to zoom out and force yourself to get an overview. 
-It let's you decide how much time you want to spend on each todo.
-
-The next tip is that at the beginning of a project the research phase shouldn't be underestimated. 
-Take time to dig into the basics and discuss with colleagues if you have the chance. 
-Try to understand the methods you'll use as well as possible. 
-Most importantly, high light advantages and disadvantages of the methods and competing/alternatives. 
-Like in a design project. Lay out as many as diverse solutions as possible, 
-compare, and ick the best parts.
-The research phase let's you learn from other's mistakes and saves a lot of time.
-
-Another important task which preceeds/anti-follows above mentioned is to define the objective as clear as possible.  
-%\td{ideal objective is to create response surface approximation}\\
-It will help to set a clear goal for each todo, e.g. 
-the primary goal of a screening experiment is to identify the active factors.\cite{miller2001using}
-Which question should be answered and aufstellen a null Hypothesis. 
-This is often very trivial, but let's you focus on the correct path.
 
@@
 The second point is not the best comparison because one doesn't need to know how a light switch works in order to use it effectively use it.}
+
+\td{don't try to solve a problem by solving a more general problem}
+\td{search i.e. and replace with i.e.\ }

### 2023-02-19 Code/ML/2022/0_cvgs.sh
grid search with CV

@@ -1,0 +1,65 @@
+#!/bin/bash 
+HELPTEXT="This program executes grid seach on hyper parameters
+\nUSAGE: $0 [-hrx] 
+\n\t-h\t print this help message and exit 
+\n\t-r\t recalculate everthing
+\n\t-x\t scale before fitting"
+recalculate="FALSE"
+scale="FALSE"
+help_bool="FALSE"
+
+for flag in "$@"
+do 
+    case $flag in 
+        -r) recalculate="TRUE";;
+        -x) scale="TRUE";;
+        -h) help_bool="TRUE";;
+    esac
+done 
+
+if [ $help_bool == "TRUE" ] 
+then 
+    echo -e $HELPTEXT
+    exit 0 
+fi 
+if  [ $scale == "TRUE" ] 
+then 
+    scaleflag="--scale"
+    scalename=".scale"
+fi 
+OUTFILE=cv_best$scalename.out
+
+if [ $recalculate == "TRUE" ] 
+then
+    source ../../../../int.venv/bin/activate
+    set -x 
+    ./cv_krr.py --emma -y2 $scaleflag 2>/dev/null > cs_krr.g$scalename.emma # grid search with only EMMA samples as data set
+    ./cv_krr.py --emma -y3 $scaleflag 2>/dev/null > cs_krr.p$scalename.emma # grid search with only EMMA samples as data set
+    ./cv_krr.py        -y2 $scaleflag 2>/dev/null > cs_krr.g$scalename.all # grid search with all samples as data set
+    ./cv_krr.py        -y3 $scaleflag 2>/dev/null > cs_krr.p$scalename.all # grid search with all samples as data set
+    ./cv_svm.py --emma -y2 $scaleflag 2>/dev/null > cs_svm.g$scalename.emma 
+    ./cv_svm.py --emma -y3 $scaleflag 2>/dev/null > cs_svm.p$scalename.emma 
+    ./cv_svm.py        -y2 $scaleflag 2>/dev/null > cs_svm.g$scalename.all
+    ./cv_svm.py        -y3 $scaleflag 2>/dev/null > cs_svm.p$scalename.all
+    set +x
+fi
+
+rm $OUTFILE
+echo $OUTFILE
+#echo -e "FILE\t\t MAE\t\t MSE\t\t sigma\t\t sigma_pred"
+if [ $scale == "TRUE" ] 
+then 
[…]

### 2023-02-19 Code/ML/2022/0_grid_search.sh

@@ -19,13 +19,17 @@ OUTFILE=gs_best$scalename.out
 
 if [ $recalculate == "TRUE" ] 
 then
-    source ../../../../pyvenv/bin/activate
+    source ../../../../int.venv/bin/activate
+    echo "start KRR emma data set"
     ./gs_krr.py --emma -y2 $scaleflag 2>/dev/null > gs_krr.g$scalename.emma # grid search with only EMMA samples as data set
     ./gs_krr.py --emma -y3 $scaleflag 2>/dev/null > gs_krr.p$scalename.emma # grid search with only EMMA samples as data set
+    echo "start KRR complete data set"
     ./gs_krr.py        -y2 $scaleflag 2>/dev/null > gs_krr.g$scalename.all # grid search with all samples as data set
     ./gs_krr.py        -y3 $scaleflag 2>/dev/null > gs_krr.p$scalename.all # grid search with all samples as data set
+    echo "start SVM emma data set"
     ./gs_svm.py --emma -y2 $scaleflag 2>/dev/null > gs_svm.g$scalename.emma 
     ./gs_svm.py --emma -y3 $scaleflag 2>/dev/null > gs_svm.p$scalename.emma 
+    echo "start SVM complete data set"
     ./gs_svm.py        -y2 $scaleflag 2>/dev/null > gs_svm.g$scalename.all
     ./gs_svm.py        -y3 $scaleflag 2>/dev/null > gs_svm.p$scalename.all
 fi
@@ -39,7 +43,7 @@ do
     for kernel in "deg=1" "deg=2" "deg=3" "rbf" "sigmoid"
     do 
         echo -ne "$file\t" | tee -a $OUTFILE
-        grep -e $kernel $file | sort -hr | tail -1 | tee -a $OUTFILE
+        grep -e $kernel $file | sort -hr -k1 | tail -1 | tee -a $OUTFILE
     done
     echo "-"
 done

### 2023-02-19 Code/ML/2022/cv_krr.py

@@ -8,14 +8,14 @@ import dfply
 import argparse
 #
 #################
-# KERNEL FOR SVM
-kernel=["poly","rbf","sigmoid"] #HPGS
+# KERNEL FOR KRR
+kernel=["poly","rbf","sigmoid"] # HPGS
 # DEGREE OF POLYNOMIAL; ignored by rest
-degree=range(1,4) #HPGS
-# some kind of scaling factor; can be set to auto/scale, include into list? 
-gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10] #HPGS
+degree=range(1,4) # HPGS
 # alpha: bigger alpha, bigger regularisation 
-alpha=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2] #, 10, 50, 100] #HPGS
+alpha=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5, 10] #, 10, 50, 100] # HPGS
+# some kind of scaling factor; can be set to auto/scale, include into list? 
+gamma=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5, 10] #, 10, 50, 100] # HPGS
 #
 # MAKE COMMAND LINE ARGUMENTS
 parser = argparse.ArgumentParser(description ='Grid Search for hyper parameters')
@@ -58,11 +58,14 @@ if args.scale : X=sklearn.preprocessing.StandardScaler().fit_transform(X)
 #
 # DUMMY RUN
 if args.test : 
-    degree=[1,2]; gamma=[0.01,0.1]; alpha=[0.5,0.1]; 
-n_exps=len(alpha)*(len(degree)+len(kernel)-1)*len(gamma)
+    degree=[1,2]; gamma=[0.01,0.1,1]; alpha=[0.5,0.1,1]; 
+#
+# CALCULATE NUMBER OF EXPERIMENTS
+n_exps=(len(degree)+len(kernel)-1)*len(gamma)*len(alpha)
 #
 # PRINT HEADER LINE 
-print("%s accuracy with standard deviation", names[int(args.y_index)])
+#print(f"%s accuracy with standard deviation", names[int(args.y_index)])
+print("mean(SCORE)\tvar(SCORE)\tparams")
 i=1
 #
 # PRINT SCORES

### 2023-02-19 Code/ML/2022/cv_svm.py

@@ -7,16 +7,17 @@ import pandas as pd
 import dfply
 import argparse
 #
+#################
 # KERNEL FOR SVM
 kernel=["poly","rbf","sigmoid"] # HPGS
-# regularization parameter
-C= np.array(range(1,20))*0.05 # HPGS
 # DEGREE OF POLYNOMIAL; ignored by rest
 degree=range(1,4) # HPGS
+# regularization parameter
+C= np.array(range(1,21))*0.05 # HPGS
 # epsilon-tube size for no penalty; rather large 
-epsilon= np.array(range(1,20))*0.2 # HPGS
+epsilon= np.array(range(1,21))*0.05 # HPGS
 # some kind of scaling factor; can be set to auto/scale, include into list? 
-gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, "scale"] # HPGS
+gamma=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5, 10, "scale"] # HPGS
 #
 # MAKE COMMAND LINE ARGUMENTS
 parser = argparse.ArgumentParser(description ='Grid Search for hyper parameters')
@@ -60,10 +61,13 @@ if args.scale : X=sklearn.preprocessing.StandardScaler().fit_transform(X)
 # DUMMY RUN
 if args.test : 
     C=[0.5,0.1]; degree=[1,2]; epsilon=[1,2]; gamma=["scale",0.1] # ,"auto"]
-n_exps=len(C)*(len(degree)+len(kernel)-1)*len(epsilon)*len(gamma)
+#
+# CALCULATE NUMBER OF EXPERIMENTS
+n_exps=(len(degree)+len(kernel)-1)*len(gamma)*len(C)*len(epsilon)
 #
 # PRINT HEADER LINE 
-print("%s accuracy with standard deviation", names[int(args.y_index)])
+#print(f"%s accuracy with standard deviation", names[int(args.y_index)])
+print("mean(SCORE)\tvar(SCORE)\tparams")
 i=1
 #
 # PRINT SCORES

### 2023-02-19 Code/ML/2022/gs_svm.py

@@ -28,7 +28,7 @@ parser.add_argument('-t', '--test', dest ='test',action ='store_true', help ='Te
 parser.add_argument('-x', '--scale', dest ='scale', action ='store_true', default=False, help='Scale input before fitting')
 args = parser.parse_args()
 #
-# DATA PRE-PROCESSING WITH 5-fold script 
+# DATA PRE-PROCESSING 
 def get_sets(df,names,args):
     data=np.array(df)
     X=data[:,6:]

### 2023-02-19 Thesis/chapter/063-discussion.tex
Grid search v3

@@
 %low TDOC results in lower conductivity... okay 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{ad results}
 why correlation $\gamma$?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{tips for next time}
@@
 Reading will let learn from others mistakes.
+\\ \td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, could have been verhindert durch lesen the docu and more papers more thoughoughly.
+Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}
     \item \textbf{objective} should be defined as clear as possible.
@@
 This is often very trivial, but let's you focus on the correct path.
-    \item \textbf{keep it simple}
-
+    \item \textbf{keep it simple}: include what you already know and reduce model size to minimum, such that \gls{epv} is high.
+Low \gls{epv} leads to low statistical significance, especially if the error is realtively large.
+(confere orig papers)
+%\td{In example of documentation 2 input variables and 1-2 responses initial population=10
+%, subsequent population=5, but 10 iterations. Clearly more input varibles and less 
+%iterations (as in actual experiments) lead to suboptimal results.}
+    \item \textbf{pre-optimisation}{The primary goal of a screening experiment is to identify the active factors.
+A secondary goal is to provide a simple model that captures the essential features of the relationship between these active factors and the response—that is, to identify the active effects.
+\cite{miller2001using}} But $2^6=64$ are too many for preliminary test so maybe check base and from there do $\cdot6=12$ experiments.
+Then focus on selected input vars, which might have mutliple maxima \\ \td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
+    \item factorial design (classical \gls{doe} is more robust at feature extraction for error laden data \cite{giunta2003overview}
+%
 \end{itemize}
-
-\td{"An important concept in inferential statistics is that the amount of information you can learn about a population is limited by the sample size.
-The more you want to learn, the larger your sample size must be." - by \url{https://blog.minitab.com/en/adventures-in-statistics-2/the-danger-of-overfitting-regression-models} }
-\td{"overfitting a regression model occurs when you attempt to estimate too many parameters from a sample that is too small." - same source}
-\td{"However, if the effect size is small or there is high multicollinearity, you may need more observations per term." -same source}
-
-The mistake which I regret the most is that I overestimated the vereinfachenden factor of reducing the splits (or discrete points between two extrems, which a variable can take) instead of the reduction of dimensions which eleminates a whole degree of freedom.
-I expected my algorithm of choice to perform magic. 
-A measurement to compare different algorithms could be, dimension and ratio of measured sampled to sample space. 
-Im vergleich to other algo I used a lot of dimensions and a low ratio.
-A low ratio gives rise to a high probability of the data being statistically insignificant, especially if the error is realtively large.
-
-All the best and stay persistent, \\  
-Johann \\
-\fi
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Mistakes} 
-\td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}\\
-\td{too much data as input, dimensionality reduction (PCA) and optimization}\\
-\td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
-\td{adding a extra variable to optimize was to optimistic and ich hab mir damit eindeutig 
-(im nachhinein) steine in den Weg gelegt.}
-The space seems to be too big for the small sample size.
-%-
-Look at relation of space size and sample size here and in Hu2016.:
-\td{In example of documentation 2 input variables and 1-2 responses initial population=10
-, subsequent population=5, but 10 iterations. Clearly more input varibles and less 
-iterations (as in actual experiments) lead to suboptimal results.}
-%
-- The exploration-vs-exploitation parameters of the model were also not set accordingly.
-see \href{https://search.r-project.org/CRAN/refmans/emma/html/emma.html}{source}
-%
-- the data has a lot of error, but because the production process takes so long and the 
-limited time and the chosen optimisation method, the experiments weren't weiderholt
-how much variance is in data? 
-%
-data-points-to-indep-vars ratio as measurement
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Next time better}
-{The primary goal of a screening experiment is to identify the active factors.
-A secondary goal is to provide a simple model that captures the essential features of the 
-relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}}
-%
-\td{if i would plan the optimisation again, I would take less input variables (fokus on 
-conc,vdoc and tdoc or even only vdoc and tdoc) which may or may not have multiple maxima.}
-%
-- The most time consuming part was definitively the prelaminary studies.
-this time could have been verkürzt by testing a wide array of diverse recipes from the literature
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Next steps}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{diskussion and outlook}
-
-- The data is spread across the datenraum, such that it is not trivial to 
-(1) find the variable with the most variance and 
-(2) to fit in order to understand to impact of noise on the data.
-
-- Dimension reduction bietet sich stark an bei solcher Datenlage.
-
-Welche methode funktioniert bei relativ vielen variablen, wenig datenpunkten und Noise.
-
-Am besten waere feature extraction (variable x1 hat am meisten einfluss) 
-ginge auch wenn man bei pca den einfluss von verschiedenen 
-I stand in front of this problem where the solution is to not use as many indep vars von vorne herein.
-
--\td{for 1F c(Zr) = 44.6 mmol/L
-if n is number of samples, and p is number of input variables, then n >> p 
-In this case n\~50 and p\~6 which give n/p=8+1/3
-in EMMA documentation example n=55and p=1-2, n/p=55-22.5
-}
-\td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, 
-could have been verhindert durch lesen the docu and more papers more thoughoughly. 
-Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}
-
-%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer.
-resistance of steel is neglectable.
-In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold.
-if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
-
-- \td{I wanted to exhaust the possibilities of EA (not having enough data).
-i should have rather einengen the search raum as much as possible (spreading the search room too much) and then do optimisation: fix layer count to 3 fix conc to 3F and fix calc temp and rate (or only use two extreme values)}
-- \td{I wanted to let the algorithm show what I already knew instead of letting my a priori knowledge constrain the model before starting.}
-- factorial design (classical \gls{doe} is more robust at feature extraction for error laden data \cite{giunta2003overview}
--\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest.
-Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2007}
-but on the other hand: If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
-- let's rule out different input variables: \\
-does the heating temperature influence the resistance?  no \\
-does the heating velocity influence the resistance?  hardly\\
-do conc and layers number influence resistance? linear \\
-do db velocity and db temperautre influence resistance? how\\
-- somebody very wise (my superviser) once said: we need to able to predict it otherwise it is just an engineering problem \td{(look at mail)}
-- "Je grösser nämlich die Anzahl freier Parameter im Modell ist, umso grösser ist der erforderliche Datenumfang und umso ungenauer wir die statistisch gewonnene Aussgae bei gleichem Datenumfang." - Gisela Härtler\cite{haertler2014statistisch}
-- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
--comparison of population size: 
-\verb|see Notes/ga_from_lit_summarj.txt|
-what is the minimum of population*generation and what is 10*5
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Learning from Data}
-General experimental procedure from Cherkassky and Mulier\cite{cherkassky1998learning}
+%%% 
+General experimental procedure from Cherkassky and Mulier Learning from Data\cite{cherkassky1998learning}
 \begin{enumerate}
@@
 \end{enumerate}
+\iffalse
 \textbf{1.
@@
 \cite{cherkassky1998learning}
+\fi
 
-There are not only \textbf{x}(input) and y(output) variables, but also \textbf{z}(uncontrolled/unobserved input variables).
-Issues of methods for learning from data: 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsectoin{discussion}
 \begin{itemize}
-	\item How to incorporate a priori assumptions into learning? 
-	\item How to measure model complexity (i.e. flexibility to fit the training data)?
-	\item How to find a optimal balance between the data and a priori knowledge? 
+    \item regularization
+    \item reproducability (random in code and repeat sample)
+    \item error of a sample 
 \end{itemize}
-\cite{cherkassky1998learning}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Mistakes} 
+- The most time consuming part was definitively the prelaminary studies.
+this time could have been verkürzt by testing a wide array of diverse recipes from the literature
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{diskussion and outlook}
+- Dimension reduction bietet sich stark an bei solcher Datenlage.
+
+%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer.
+resistance of steel is neglectable.
+In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold.
+if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
+
+%- \td{I wanted to exhaust the possibilities of EA (not having enough data).
+i should have rather einengen the search raum as much as possible (spreading the search room too much) and then do optimisation: fix layer count to 3 fix conc to 3F and fix calc temp and rate (or only use two extreme values)}
+%- \td{I wanted to let the algorithm show what I already knew instead of letting my a priori knowledge constrain the model before starting.}
+
+%-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest.
+Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2007}
+%but on the other hand: If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
+- let's rule out different input variables: \\
+does the heating temperature influence the resistance?  no \\
+does the heating velocity influence the resistance?  hardly\\
+do conc and layers number influence resistance? linear \\
+do db velocity and db temperautre influence resistance? how\\
+
+%- somebody very wise (my superviser) once said: we need to able to predict it otherwise it is just an engineering problem \td{(look at mail)}
+- "Je grösser nämlich die Anzahl freier Parameter im Modell ist, umso grösser ist der erforderliche Datenumfang und umso ungenauer wir die statistisch gewonnene Aussgae bei gleichem Datenumfang." - Gisela Härtler\cite{haertler2014statistisch}
+%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
+-comparison of population size: 
+\verb|see Notes/ga_from_lit_summarj.txt|
+%what is the minimum of population*generation and what is 10*5
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%Issues of methods for learning from data: 
+%\begin{itemize}
+%	\item How to incorporate a priori assumptions into learning? 
+%	\item How to measure model complexity (i.e. flexibility to fit the training data)?
+%	\item How to find a optimal balance between the data and a priori knowledge? 
+%\end{itemize}
+%\cite{cherkassky1998learning}
 
@@
 
-"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)
+%"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)
 
-Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
-Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps.
+%Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
+%Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps.
 
-Any learning process requires the following(p40): 
-\begin{itemize}
-	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
-	\item A priori knowledge to impose contrains
-	\item An inductive principle (what needs to be done)
-		\begin{itemize}
-			\item penalizeation (regularization) inductive principle
-			\item early stopping rules (with ANN, difficult to control and interpret)
-			\item structural risk minimization (SRM) (order according to complexity)
-			\item Bayesian Inference (add subjectivity to learning machine)
-			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
-		\end{itemize}
-	\item A learning method (how does it need to be done,implementation)
-\end{itemize}
-\cite{cherkassky1998learning}
+%Any learning process requires the following(p40): 
+%\begin{itemize}
+%	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
+%	\item A priori knowledge to impose contrains
+%	\item An inductive principle (what needs to be done)
+%		\begin{itemize}
+%			\item penalizeation (regularization) inductive principle
+%			\item early stopping rules (with ANN, difficult to control and interpret)
+%			\item structural risk minimization (SRM) (order according to complexity)
+%			\item Bayesian Inference (add subjectivity to learning machine)
+%			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
+%		\end{itemize}
+%	\item A learning method (how does it need to be done,implementation)
+%\end{itemize}
+%\cite{cherkassky1998learning}
 
@@
 \td{search i.e. and replace with i.e.\ }
+
+\td{"An important concept in inferential statistics is that the amount of information you can learn about a population is limited by the sample size.
+The more you want to learn, the larger your sample size must be." - by \url{https://blog.minitab.com/en/adventures-in-statistics-2/the-danger-of-overfitting-regression-models} }
+\td{"overfitting a regression model occurs when you attempt to estimate too many parameters from a sample that is too small." - same source}
+\td{"However, if the effect size is small or there is high multicollinearity, you may need more observations per term." -same source}

### 2023-02-19 Thesis/chapter/062-post-emma.tex

--- 2023-02-18 Thesis/chapter/062-post-emma.tex
@@
 %\iffalse
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 \subsubsection{Grid Search}
@@
 Both \gls{krr} and \gls{svm} following kernel: radial basis function, sigmoid, and polynomial with degree 1 to 4. 
-Gamma = {
+%
+%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
+%https://scikit-learn.org/stable/modules/svm.html#svc
+%
+\td{which parameters?}
+The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
+The kernel took the form of \gls{rbf}, sigmoid and polynomial with degree 1--4.
+The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
+and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
+Note that $\gamma_{ml}$ is used differently in each kernel. 
+The kernels for \gls{svm} were the same and further hyper parameters were 
+$C$, $\varepsilon$ and $\gamma_{ml}$, where $C$ took the values 0.05--0.95 with 0.05 steps, $\varepsilon$ 0.02--3.8 with 0.2 steps and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}.
+Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
+and $\sigma(\mathbf{X})$ the variance of the input variables. 
+%
+\td{how and what?}
+Each grid search calculation was calculated with and without scaling the data before the optimisation. 
+For each optimisation \gls{mae}, \gls{mse}, $sigma(\mathbf{y})$ and $\sigma(\mathbf{\hat{y}})$ were calculated. 
+For each method (\gls{krr} and \gls{svm}) and each kernel the parameters with the lowest \gls{mae} were chosen. 
+%
+\td{what were best results/hyper parameters}
 
-%KRR
-%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10] #HPGS
-%alpha=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2] #, 10, 50, 100] #HPGS
-
-%SVM
-%C= np.array(range(1,20))*0.05 # HPGS
-%epsilon= np.array(range(1,20))*0.2 # HPGS
-%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, "scale"] # HPGS
-
-%kernel=["poly","rbf"]#,"sigmoid"]
-%C= np.array(range(1,20))*0.05
-%degree=range(1,6)
-%epsilon= np.array(range(1,20))*0.2
-%gamma=[0.0,0.1,1.0,10.0]
-%#param = {"kernel":kernel, "C":C, "degree":degree, "epsilon":epsilon, "gamma":gamma }
-%C=[1,0.1]; degree=[3]; epsilon=[1,2]; gamma=['scale']
-Now what are C,epsilon and gamma?
-
-Since the data set was very small, I could be generous with the grid search even on relatively humble hardware (intel i7-8550U).
+%Since the data set was very small, I could be generous with the grid search even on relatively humble hardware (intel i7-8550U).
 
@@
         lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
-        ML KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
-        ML SVM& 15  415&    26& 1050&   28& 1588&   19& 677\\
+        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
+        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
     \hline\hline

### 2023-02-20 Thesis/chapter/05-computational-details.tex
comp details ML

@@
 
-\iffalse 
 \subsection{Fitting via Machine Learning}
-\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
-Python and sci-kit learn \td{cite} was used to implement a linear fit model, and SVR with the kernels polynomial, rbf and sigmoid. 
-The space of hyper parameters C, the degree (in case of polynomial), epsilon and gamma was scaned.
-
-The independent variables are located on a partially irregular grid.  
-\fi
+%\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
+Python and sci-kit learn \cite{pedregosa2011scikit} was used to implement a linear fit model, \gls{krr} and \gls{svm} with the kernels polynomial, \gls{rbf} and sigmoid. 
+%\subsubsection{Grid Search}
+A grid search over a set of hyper parameters was executed. 
+%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
+%https://scikit-learn.org/stable/modules/svm.html#svc
+% KRR 
+The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
+The kernel took the form of \gls{rbf}, sigmoid and polynomial with degree 1--4.
+The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
+and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
+Note that $\gamma_{ml}$ is used differently in each kernel. 
+% SVM
+The kernels for \gls{svm} were the same as for \gls{krr}. 
+Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$, 
+where $C$ took the values 0.05--0.95 with 0.05 steps, $\varepsilon$ 0.02--3.8 with 0.2 steps 
+and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
+Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
+and $\sigma(\mathbf{X})$ the variance of the input variables. 
+% GRID SEARCH 
+The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
+of the \gls{emma} data set were scaled before each calculation.
+For each calculation the \td{5-fold} cross validation score was calculated. 
+For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 
+the parameters with the highest score were noted.
+% 
+Finally, the different data sets were predicted for each model and \gls{mae} and \gls{mse} were calculated.
+These values were also calculated for \gls{emma} and the linear model in order to compare the different methods.

### 2023-02-20 Thesis/chapter/062-post-emma.tex
comp details ML

@@
 \subsubsection{Grid Search}
+\todo{reduce to results}
 The ideal hyper parameters have to be found for \gls{krr} and \gls{svm}.
@@
 \td{what were best results/hyper parameters}
+\td{procedure into diffferen capitel: choose hyperparaters, choose dataset (emma).
+Grid search over hyperparameters and score with default scorer with default cross validation settings, k-fold=5?
+chose lowest score for each optimizand and algo (svm/krr) combo.
+Fit model with emma-data and chosen hyper parameters, predict different data sets and calculate statistics (MAE+MSE) for each data set.}
 
@@
         lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
-        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
+%        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
+        KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
         SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
@@
         lin Reg&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
-        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
-        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
+%        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
+        KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
+%        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
+        SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
     \hline\hline
@@
 \subsubsection{KRR}
+
+\begin{verbatim}
+(int.venv) [pur@lithium 2022]$ ./01_show_best.sh
+cv_krr.g.scale.emma     -0.497302       0.252231        poly    deg=1   a=2.00  g=0.01  71/500
+cv_krr.p.scale.emma     -0.449674       0.517822        rbf     deg=0   a=10.00 g=0.2   395/500
+cv_svm.g.scale.emma     -0.368196       0.391125        poly    deg=2   C=0.7   e=1.0   g=0.5   7475/22000
+cv_svm.p.scale.emma     -0.948249       0.439029        poly    deg=3   C=0.1   e=0.1   g=0.01  8801/22000
+(int.venv) [pur@lithium 2022]$ ./3_calc_mse_of_best.sh -l
+krr g poly -d 1 a10.00 g0.01    &17.37 &548.36 &30.42 &1477.36 &34.78 &2167.38 &22.75 &931.00\\
+krr p rbf a2.00 g0.01   &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
+svm g poly -d 1 C0.7 e0.1 -g0.01        &14.55 &415.40 &25.68 &1049.23 &28.49 &1587.85 &19.13 &676.39\\
+svm p poly -d 1 C0.1 e0.1 -gscale       &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
+\end{verbatim}
 

### 2023-02-20 Thesis/chapter/063-discussion.tex
comp details ML

@@
 \subsubsection{Mistakes and Solutions}
-%This chapter is structured as a letter 
-%which my present self thinks that would have helped my past self 
-%if recieved before the start of the practical part of my master practikum:\\
-
-%to discuss: results from EMMA or rather which the data present are counter intuitive. 
 %why lowest conductivity with lowest TCal and why is there a minimum for layers? 
-%low TDOC results in lower conductivity... okay 
+%low TDOC results in lower conductivity... okay somehow 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{ad results}
-why correlation $\gamma$?
+\begin{itemize}
+    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
+    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
+\end{itemize}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{tips for next time}
+\subsubsection{Tips for next time}
 \begin{itemize}
-    \item \textbf{planning} gives chance of zooming out, force oneself to get an overview and to decide how much time on each task
+    \item \textbf{planning} gives chance of zooming out and force oneself to get an overview and to decide how much time on each task
     \item \textbf{research} phase is most important, dig into basics, discuss ideas with colleagues or go into detail about plan.
@@
 Collect (dis-)advantages of different methods.
-Like in design project: do as many and as deverse solutions as possbile.
+Like in design project: do as many and as diverse solutions as possbile.
 Compare and combine the best parts.
@@
 \begin{enumerate}
-	\item State the problem 
-	\item Formulate the hypothesis
-	\item Design the experiment/generate the data
-	\item Collect the data and perform preprocessing
-	\item Estimate the model 
-	\item Interpret the model/draw the conclusions
+    \item \textbf{State the problem}
+    \item \textbf{Formulate the hypothesi}
+    \item \textbf{Design the experiment/generate the dat}
+    \item \textbf{Collect the data and perform preprocessin}
+    \item \textbf{Estimate the model}
+    \item \textbf{Interpret the model/draw the conclusion}
 \end{enumerate}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsectoin{discussion}
+\subsubsection{discussion}
 \begin{itemize}

### 2023-02-22 Thesis/chapter/05-computational-details.tex
finish post-emma

@@
 	s_i = \begin{cases}
-	1 &\text{if} \quad -log(g_i) < 5 \\
-	0 &\text{if} \quad -log(g_i) \geq 5 \\
+        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
+        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
 	\end{cases}
@@
 (and to choose a fraction of the initial population which is allowed to propagate).
-\td{
 %The response variables for the entire population space is calculated. 
-}
 The current population - each of the particles independently - 
@@
 %\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
-Python and sci-kit learn \cite{pedregosa2011scikit} was used to implement a linear fit model, \gls{krr} and \gls{svm} with the kernels polynomial, \gls{rbf} and sigmoid. 
+Python 3.10.9 and sci-kit learn 1.1.2\cite{pedregosa2011scikit} were used to implement a linear fit model, \gls{krr} and \gls{svm} with the kernels polynomial, \gls{rbf} and sigmoid. 
 %\subsubsection{Grid Search}
@@
 of the \gls{emma} data set were scaled before each calculation.
-For each calculation the \td{5-fold} cross validation score was calculated. 
+% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
+% https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVR.html#sklearn.svm.SVR.score
+For each calculation the 5-fold cross validation score was calculated. 
+The score equals to the coefficient of determination $R^2$ which defined as 
+$1-\frac{\sum (y_i - \hat{y}_i)}{\sum (y_i - \bar{y}_i)}$.
 For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 

### 2023-02-22 Thesis/chapter/062-post-emma.tex
finish post-emma

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{Grid Search}
-\todo{reduce to results}
-The ideal hyper parameters have to be found for \gls{krr} and \gls{svm}.
-To do so a grid search over a set of hyper parameters was executed. 
-Both \gls{krr} and \gls{svm} following kernel: radial basis function, sigmoid, and polynomial with degree 1 to 4. 
+\subsubsection{Grid Search, KRR and SVM}
+The optimal parameters for each \textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 
+combination can be seen in table \ref{tab:grid-search}. 
+They parameters are often extrema.
+The hyperparameter $\gamma_{ml}$ took minimum value possibel twice. 
+In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
+The range of the hyperparameter $\alpha$ was 0.01--10 in the grid search. 
+So 2 and 10 are high values for the regularization parameter of \gls{krr}.
+The hyperparameter $\varepsilon$ specifies the size of the tube within which data does not contribute to the loss 
+and the value 1 is the maximum during the grid search. 
+%The value 1 for $\varepsilon$ is the highest possible, 
+%$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
+All these extreme values of hyperparameters stimulate regularisation and indicate noisy and difficult to fit data.
+\begin{table}
+    \center
+    \begin{tabular}{ccccccc}
+        \hline\hline
+        method  &kernel &degree &$\gamma_{ml}$   &$\alpha$    &$C$    &$\varepsilon$\\
+        \hline
+        KRR($\gamma$)   &poly   &1  &0.01   &2.00 &-&-\\
+        KRR($\rho  $)   &rbf    &-   &0.2    &10.00&-&-\\
+        SVM($\gamma$)   &poly   &2  &0.5    &-&0.7  &1.0  \\
+        SVM($\rho  $)   &poly   &3  &0.01   &-&0.1  &0.1  \\
+        \hline\hline
+    \end{tabular}
+    \caption{Best parameters for each \textit{optimisand}-method-combination}
+    \label{tab:grid-search}
+\end{table}
+% R2
+The $R^2$ values were calculated for each of the models using cross validation. 
+Resulting $R^2$ are all below zero (see equations \ref{eq:r2-krr-g}--\ref{eq:r2-svm-p}). 
+A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$.
+
+\begin{align}
+    \label{eq:r2-krr-g}
+    R^2(\gamma_{krr}) &= -0.50 \pm 0.25\\
+    \label{eq:r2-krr-p}
+    R^2(\rho_{krr})   &= -0.45 \pm 0.52\\
+    \label{eq:r2-svm-g}
+    R^2(\gamma_{svm}) &= -0.37 \pm 0.39\\
+    \label{eq:r2-svm-p}
+    R^2(\rho_{svm})   &= -0.95 \pm 0.44
+\end{align}
+
 %
-%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
-%https://scikit-learn.org/stable/modules/svm.html#svc
+Finally the \gls{mae} and \gls{mse} were calculated for different data sets with models 
+trained on the \gls{emma} data set (see table \ref{tab:post-emma}). 
+% EMMA 30 pts
+The first two columns show statistics for data the model was trained with and thus, 
+these columns contain the lowest numbers. 
+% pre-EMMA 21 pts 
+The next two columns were calculated with data obtained before the EMMA optimisation. 
+As the this pre-optimisation data set was mainly used to find appropriate boundaries for the input variables, 
+many data points are outside of the range of the \gls{emma} data set. 
+Thus, prediction for this data set are mainly extrapolations. 
+% inter/c/ pre-EMMA 5 pts
+The next two columns were produced by using pre-\gls{emma} data, 
+but only keeping points which sit inside the space spanned by the \gls{emma} constraints. 
+It should be expected that these statistics should be lower than in the previous two columns. 
+They are higher, though, because of the small sample size of 5 data points. 
+% all 51 
+The last two columns show data for prediction of all available data. 
+These statistics are lower because of the inclusion of the training set in the test set.
+
+In the self test of the first two columns \gls{mars} is the one method to rule them all.
+But as soon as unseen data enters the field, linear regression excels with its simplicity. 
+The linear regression method is only under cut by when calculatting the \gls{mae} of $\gamma$
+for the interpolating unseen data with \gls{svm}. 
 %
-\td{which parameters?}
-The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
-The kernel took the form of \gls{rbf}, sigmoid and polynomial with degree 1--4.
-The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
-and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
-Note that $\gamma_{ml}$ is used differently in each kernel. 
-The kernels for \gls{svm} were the same and further hyper parameters were 
-$C$, $\varepsilon$ and $\gamma_{ml}$, where $C$ took the values 0.05--0.95 with 0.05 steps, $\varepsilon$ 0.02--3.8 with 0.2 steps and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}.
-Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
-and $\sigma(\mathbf{X})$ the variance of the input variables. 
+%\todo{could use mean as prediction and compare}
+%\todo{could plot pred vs true}
+%\todo{pcr}
+%\todo{step wise regression}
+%\todo{why chose mae and mse}
+%\todo{talk about sigma(pred) vs sigma(true)}
+%\todo\url{https://blog.minitab.com/en/adventures-in-statistics-2/regression-smackdown-stepwise-versus-best-subsets}}
+%\todo{\url{https://blog.minitab.com/en/how-to-choose-the-best-regression-model}}
+%\todo{do regression for avg(-log(G)) instead of $\gamma$=avg( ( 13+log(G))**2)} 
 %
-\td{how and what?}
-Each grid search calculation was calculated with and without scaling the data before the optimisation. 
-For each optimisation \gls{mae}, \gls{mse}, $sigma(\mathbf{y})$ and $\sigma(\mathbf{\hat{y}})$ were calculated. 
-For each method (\gls{krr} and \gls{svm}) and each kernel the parameters with the lowest \gls{mae} were chosen. 
-%
-\td{what were best results/hyper parameters}
-\td{procedure into diffferen capitel: choose hyperparaters, choose dataset (emma).
-Grid search over hyperparameters and score with default scorer with default cross validation settings, k-fold=5?
-chose lowest score for each optimizand and algo (svm/krr) combo.
-Fit model with emma-data and chosen hyper parameters, predict different data sets and calculate statistics (MAE+MSE) for each data set.}
-
-%Since the data set was very small, I could be generous with the grid search even on relatively humble hardware (intel i7-8550U).
-
 \begin{table}[htb]
@@
     \hline\hline
-    G&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
+    $\gamma$&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
     \hline
@@
     \hline\hline
-    p&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
+    $\rho$&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
     \hline
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{KRR}
-
+\iffalse
 \begin{verbatim}
@@
 \end{verbatim}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{SVM}
-\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}
-
-%\fi
-
-\iffalse
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{PCR?}
-\subsubsection{Further}
-\begin{itemize}
-    \item grid search
-    \item KRR (start with grid search) (???)
-    \item SVM (start with grid search) (???)
-    \item \url{https://blog.minitab.com/en/adventures-in-statistics-2/regression-smackdown-stepwise-versus-best-subsets}
-    \item \url{https://blog.minitab.com/en/how-to-choose-the-best-regression-model}
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{Comparison} 
-compare all methods. 
-How should I compare them? 
-What are the measurables. 
 \fi
-
-\td{do regression for avg(-log(G)) instead of $\gamma$=avg( ( 13+log(G))**2)}

### 2023-02-22 Code/ML/2022/99_get_gshp.sh

@@ -2,4 +2,4 @@
 #
 #GET HYPER PARAMETERS FOR GRID SEARCH 
 echo "Hyper parameter for grid search"
-grep --color=auto HPGS gs*py
+grep --color=auto HPGS cv*py

### 2023-02-22 Thesis/chapter/063-discussion.tex
finish post-emma
clean free writing discussion

@@
 \subsection{Discussion}
-\subsubsection{Mistakes and Solutions}
-%why lowest conductivity with lowest TCal and why is there a minimum for layers? 
-%low TDOC results in lower conductivity... okay somehow 
+%\todo{search i.e. and replace with i.e.\ }
+%\todo{go to experimental and material (IV) discussion}
+%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer.
+resistance of steel is neglectable.
+In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold.
+if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
+%todo{go to anova discussion}
+%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Hindsight is easier than foresight}
+\begin{itemize}
+    \item The most time consuming part was definitively the prelaminary studies. this time could have been verkürzt by testing a wide array of diverse recipes from the literature
+    \item minimize prelaminary study time by testing a wide range of designs
+    \item Dimension reduction bietet sich stark an bei solcher Datenlage. in pre-optimisation!
+\end{itemize}
+%
+General experimental procedure from Cherkassky and Mulier Learning from Data\cite{cherkassky1998learning}:
+\begin{enumerate}
+    \item \textbf{State the problem}
+    \item \textbf{Formulate the hypothesis}
+    \item \textbf{Design the experiment/data generation process}
+    \item \textbf{Collect the data and perform preprocessing}
+    \item \textbf{Estimate the model}
+    \item \textbf{Interpret the model/draw the conclusion}
+\end{enumerate}
+\iffalse
+\textbf{1.
+Statement of the Problem} There was no clear statement of the problem.
+Now I would formulate it: "How to produce most insulating layer with least energy?
+How do we define most insulating?" That's why there are two output variables rather than one.
+\textbf{2. Hypothesis Formulation} formulate an unknown dependency and define input and output variables.
+\textbf{3.
+Data Generation and Experiment Design} can be either in control of the modeler (designed experiment) or in an observational setting.
+The data collection can affect the sampling distribution and influence the next steps.
+\textbf{4.
+Collect the Data and Perform Preprocessing} here outliers are detected and data preprocessing/encoding/feature selection.
+Scaling by standard deviation might be a good idea, but independent scaling of variables can lead to suboptimal representation for the learning task.
+Feature selection: A small number of informative features make the task of estimating dependencies easier.
+\textbf{5. Model Estimation} The main goal is to construct a model for accurate prediction of future outputs
+\textbf{6.
+Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete.
+In classical statistics such as linearly parametrized function will suit both requirements.
+More complex and flexible models might lead to better estimates with less interpretability.
+Identifying the most important input variables.
+\cite{cherkassky1998learning}
+\fi
+
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{itemize}
-
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Then focus on selected input vars, which might have mutliple maxima \\ \td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
-    \item factorial design (classical \gls{doe} is more robust at feature extraction for error laden data \cite{giunta2003overview}
+    \item factorial design (classical \gls{doe}) is more robust at feature extraction for error laden data \cite{giunta2003overview}
+\end{itemize}
 %
-\end{itemize}
-%%% 
-General experimental procedure from Cherkassky and Mulier Learning from Data\cite{cherkassky1998learning}
-\begin{enumerate}
-    \item \textbf{State the problem}
-    \item \textbf{Formulate the hypothesi}
-    \item \textbf{Design the experiment/generate the dat}
-    \item \textbf{Collect the data and perform preprocessin}
-    \item \textbf{Estimate the model}
-    \item \textbf{Interpret the model/draw the conclusion}
-\end{enumerate}
-\iffalse
-\textbf{1.
-Statement of the Problem} There was no clear statement of the problem.
-Now I would formulate it: "How to produce most insulating layer with least energy?
-How do we define most insulating?" That's why there are two output variables rather than one.
-\textbf{2. Hypothesis Formulation} formulate an unknown dependency and define input and output variables.
-\textbf{3.
-Data Generation and Experiment Design} can be either in control of the modeler (designed experiment) or in an observational setting.
-The data collection can affect the sampling distribution and influence the next steps.
-\textbf{4.
-Collect the Data and Perform Preprocessing} here outliers are detected and data preprocessing/encoding/feature selection.
-Scaling by standard deviation might be a good idea, but independent scaling of variables can lead to suboptimal representation for the learning task.
-Feature selection: A small number of informative features make the task of estimating dependencies easier.
-\textbf{5. Model Estimation} The main goal is to construct a model for accurate prediction of future outputs
-\textbf{6.
-Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete.
-In classical statistics such as linearly parametrized function will suit both requirements.
-More complex and flexible models might lead to better estimates with less interpretability.
-Identifying the most important input variables.
-\cite{cherkassky1998learning}
-\fi
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \item error of a sample 
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Mistakes} 
-- The most time consuming part was definitively the prelaminary studies.
-this time could have been verkürzt by testing a wide array of diverse recipes from the literature
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{diskussion and outlook}
-- Dimension reduction bietet sich stark an bei solcher Datenlage.
-
-%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer.
-resistance of steel is neglectable.
-In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold.
-if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
-
-%- \td{I wanted to exhaust the possibilities of EA (not having enough data).
-i should have rather einengen the search raum as much as possible (spreading the search room too much) and then do optimisation: fix layer count to 3 fix conc to 3F and fix calc temp and rate (or only use two extreme values)}
-%- \td{I wanted to let the algorithm show what I already knew instead of letting my a priori knowledge constrain the model before starting.}
-
+    \item only include relevant variables\cite{gunst2007fractional}, but include all variables which could contribute\cite{haertler2014statistisch}
 %-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest.
@@
 %but on the other hand: If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
-- let's rule out different input variables: \\
-does the heating temperature influence the resistance?  no \\
-does the heating velocity influence the resistance?  hardly\\
-do conc and layers number influence resistance? linear \\
-do db velocity and db temperautre influence resistance? how\\
-
-%- somebody very wise (my superviser) once said: we need to able to predict it otherwise it is just an engineering problem \td{(look at mail)}
-- "Je grösser nämlich die Anzahl freier Parameter im Modell ist, umso grösser ist der erforderliche Datenumfang und umso ungenauer wir die statistisch gewonnene Aussgae bei gleichem Datenumfang." - Gisela Härtler\cite{haertler2014statistisch}
-%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
--comparison of population size: 
-\verb|see Notes/ga_from_lit_summarj.txt|
-%what is the minimum of population*generation and what is 10*5
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%Issues of methods for learning from data: 
-%\begin{itemize}
-%	\item How to incorporate a priori assumptions into learning? 
-%	\item How to measure model complexity (i.e. flexibility to fit the training data)?
-%	\item How to find a optimal balance between the data and a priori knowledge? 
-%\end{itemize}
-%\cite{cherkassky1998learning}
-
-"Learning is the process of estimating an unkown (input,output) dependency of structure of a system using a limit number of observations."\cite{cherkassky1998learning}
-
-The process informal part of selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} (page 25)
-
-"Do not attempt to solve a specified problem by indirectly solving a harder general problem as an intermediate step."\cite{cherkassky1998learning}(p33)
-
-%"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)
-
-%Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
-%Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps.
-
-%Any learning process requires the following(p40): 
-%\begin{itemize}
-%	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
-%	\item A priori knowledge to impose contrains
-%	\item An inductive principle (what needs to be done)
-%		\begin{itemize}
-%			\item penalizeation (regularization) inductive principle
-%			\item early stopping rules (with ANN, difficult to control and interpret)
-%			\item structural risk minimization (SRM) (order according to complexity)
-%			\item Bayesian Inference (add subjectivity to learning machine)
-%			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
-%		\end{itemize}
-%	\item A learning method (how does it need to be done,implementation)
-%\end{itemize}
-%\cite{cherkassky1998learning}
-
-\textbf{Curse and Complexity of Dimensionality}
+    \item which input variables could have been left out? why? justify with intuition and maths
+    \item discuss epv and compare with lit: when searching for appropriate algo, came across multi papers \todo{where should be discussed?}
+%Ahmed 2017		generations 50  popu 20 2in 1out \cite{ahmed2017preparation}
+%Arabs 1994		about varying pop size
+%Fernandes 2010		MOGA 500gen 1000pop \cite{fernandes2010multi}
+%Hosseini 2016		GA 50 pop 1000 generations 3in 1out 
+%Kaczmarowski2015	GA 50 pop 50-100 generation data calculated \cite{kaczmarowski2015genetic}
+%Madhavi 2017		GA+ANN	46 data	18 hiddenlayers init pop 30, pop 100 % 5in 1out \cite{mahdavi2017hardness}
+%Soltananali 2014	GA+ANN	100 Generations 85 data points 6 input 8 hiden 1 output data from literature \cite{soltanali2014neural}
+%Panwar 2014		GA+Simulation	4 parameters    % 2in2out? \cite{panwar2014design}
+%schubert 2008		GA+simulation \cite{schubert2008design,
+%Shanaghi 2013 		MOGA (GA+ANN) population size 100 \cite{shanaghi2013experimental}
+    \item selection of in- and output vars is more important than coice of learning algorithm. 
+%The process informal part of selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} (page 25)
+    \item Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}
+    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
+    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error?
+what else?
+%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
+%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
+%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
+%\td{COMMENT: solution age was not accounted for}
+    \item main problems too many in and output vars
+%\td{two main problems: 1.
+too many input variables; 2.
+too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs.
+This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
+    \item what was goal of incorporating ml into this work? 
+%\td{The goal of introducing \gls{ml} to this project was to apply and delve/vertiefen into subject which I've been studying during my undergrad courses.
+This seemed like the perfect opputrunity.
+And indeed I learned a lot.
+Even if only although \gls{ml} is a hot topic at the moment, it can not solve every problem.
+Two important things have I learned regarding \gls{ml}:
+        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    \item curse of dimensionality
+%- "Je grösser nämlich die Anzahl freier Parameter im Modell ist, umso grösser ist der erforderliche Datenumfang und umso ungenauer wir die statistisch gewonnene Aussgae bei gleichem Datenumfang." - Gisela Härtler\cite{haertler2014statistisch}
+%\td{"An important concept in inferential statistics is that the amount of information you can learn about a population is limited by the sample size.
+The more you want to learn, the larger your sample size must be." - by \url{https://blog.minitab.com/en/adventures-in-statistics-2/the-danger-of-overfitting-regression-models} }
+%\td{"overfitting a regression model occurs when you attempt to estimate too many parameters from a sample that is too small." - same source}
+%by \url{https://blog.minitab.com/en/adventures-in-statistics-2/the-danger-of-overfitting-regression-models} 
+%\td{"However, if the effect size is small or there is high multicollinearity, you may need more observations per term." -same source} 
+%by \url{https://blog.minitab.com/en/adventures-in-statistics-2/the-danger-of-overfitting-regression-models} 
+\iffalse %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\textbf{Curse and Complexity of Dimensionality}\cite{cherkassky1998learning} chapter 3.1.
 goal is to estimate function with finite samples, so it's always inaccurate (biased). 
-meaning full estimate only possible with high sampling density, which is difficult for high dimensional functions.
+Meaning, full estimate only possible with high sampling density, which is difficult for high dimensional functions.
 \begin{enumerate}
@@
 \end{itemize}
+\fi %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 
-am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
-"ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell" \cite{haertler2014statistisch}
-Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
-Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{LINKS}
-\begin{itemize}
-    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
-    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
-    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
-\end{itemize}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Would be easier to fit with single factor at a time variation or latin hyper cuber? 
-%with same search-space to actual-data ratio
-%- Would it also be easier for MARS or ML to find fitting function?
-%plot predictions from EMMA and ML. or rather compare MAE
-
-\td{what are the reasons for large error?} 
-\begin{itemize} 
-    \item ageing of solution 
-    \item varying humidity
-    \item varying room temperature 
-    \item impurities in solutions
-    \item inhomogeneity of film 
-    \item measuring error
-    \item 
 \end{itemize}
 
-What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
-Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
-As the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\href{https://pubs.acs.org/doi/10.1021/ci0342472}{overfitting}
-\td{COMMENT: solution age was not accounted for}
-
-\td{two main problems: 1.
-too many input variables; 2.
-too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs.
-This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
-
-\td{The goal of introducing \gls{ml} to this project was to apply and delve/vertiefen into subject which I've been studying during my undergrad courses.
-This seemed like the perfect opputrunity.
-And indeed I learned a lot.
-Even if only although \gls{ml} is a hot topic at the moment, it can not solve every problem.
-Two important things have I learned regarding \gls{ml}:
-1.) The methods bringen sich nix if one doesn't know how to apply them which directly leads into my second erkenntnis
-2.) If one wants to use a tool, one should know how to use it and its innerlichkeiten in order to use it well.
-The second point is not the best comparison because one doesn't need to know how a light switch works in order to use it effectively use it.}
-
-\td{don't try to solve a problem by solving a more general problem}
-\td{search i.e. and replace with i.e.\ }
-
-\td{"An important concept in inferential statistics is that the amount of information you can learn about a population is limited by the sample size.
-The more you want to learn, the larger your sample size must be." - by \url{https://blog.minitab.com/en/adventures-in-statistics-2/the-danger-of-overfitting-regression-models} }
-\td{"overfitting a regression model occurs when you attempt to estimate too many parameters from a sample that is too small." - same source}
-\td{"However, if the effect size is small or there is high multicollinearity, you may need more observations per term." -same source}
+%Issues of methods for learning from data: 
+%\begin{itemize}
+%	\item How to incorporate a priori assumptions into learning? 
+%	\item How to measure model complexity (i.e. flexibility to fit the training data)?
+%	\item How to find a optimal balance between the data and a priori knowledge? 
+%\end{itemize}
+%\cite{cherkassky1998learning}
+%"Learning is the process of estimating an unkown (input,output) dependency of structure of a system using a limit number of observations."\cite{cherkassky1998learning}
+%"Do not attempt to solve a specified problem by indirectly solving a harder general problem as an intermediate step."\cite{cherkassky1998learning}(p33)
+%"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)
+%Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
+%Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps. 
+%Any learning process requires the following(p40): 
+%\begin{itemize}
+%	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
+%	\item A priori knowledge to impose contrains
+%	\item An inductive principle (what needs to be done)
+%		\begin{itemize}
+%			\item penalizeation (regularization) inductive principle
+%			\item early stopping rules (with ANN, difficult to control and interpret)
+%			\item structural risk minimization (SRM) (order according to complexity)
+%			\item Bayesian Inference (add subjectivity to learning machine)
+%			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
+%		\end{itemize}
+%	\item A learning method (how does it need to be done,implementation)
+%\end{itemize}
+%\cite{cherkassky1998learning}
+%am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
+%Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsubsection{LINKS}
+%\begin{itemize}
+%    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
+%    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
+%    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
+%\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-02-23 Thesis/chapter/063-discussion.tex
structure discussion chronological

@@
-\subsection{Discussion}
+\subsection{Hindsight is easier than foresight}
+%\subsection{Discussion}
 %\todo{search i.e. and replace with i.e.\ }
@@
 %- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Hindsight is easier than foresight}
+%todo{british or US?} 
+This subsection will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
+Firstly, the research, exploration and design phase, then the pre-optimisation, \td{refinement} and narrowing phase, sequentially the optimisation, modelling and \td{main measurement}  phase and finally the evaluation, interpretation and outlook phase.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Research, exploration and design phase}
 \begin{itemize}
     \item The most time consuming part was definitively the prelaminary studies. this time could have been verkürzt by testing a wide array of diverse recipes from the literature
-    \item minimize prelaminary study time by testing a wide range of designs
-    \item Dimension reduction bietet sich stark an bei solcher Datenlage. in pre-optimisation!
+    \item minimize prelaminary study time by testing a wide range of designs. scrutinize (hinterfragen) everything!
+    \item \textbf{planning} gives chance of zooming out and force oneself to get an overview and to decide how much time on each task
+    \item \textbf{research} phase is most important, dig into basics, discuss ideas with colleagues or go into detail about plan.
+Understand details of methods.
+Make a dummy run.
+Collect (dis-)advantages of different methods.
+Like in design project: do as many and as diverse solutions as possbile.
+Compare and combine the best parts.
+Reading will let learn from others mistakes.
+\\ \td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, could have been verhindert durch lesen the docu and more papers more thoughoughly.
+Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}
+    \item \textbf{objective} should be defined as clear as possible.
+It will help to set a clear goal for each todo, e.g.
+the primary goal of a screening experiment is to identify the active factors.\cite{miller2001using} Which question should be answered and aufstellen a null Hypothesis.
+This is often very trivial, but let's you focus on the correct path.
+    \item what was goal of incorporating ml into this work? 
+%\td{The goal of introducing \gls{ml} to this project was to apply and delve/vertiefen into subject which I've been studying during my undergrad courses.
+This seemed like the perfect opputrunity.
+And indeed I learned a lot.
+Even if only although \gls{ml} is a hot topic at the moment, it can not solve every problem.
+Two important things have I learned regarding \gls{ml}:
 \end{itemize}
-%
 General experimental procedure from Cherkassky and Mulier Learning from Data\cite{cherkassky1998learning}:
@@
 \fi
-
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{ad results}
+\subsubsection{Narrowing, pre-optimisation and constraint phase}
 \begin{itemize}
-    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
-    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
-\end{itemize}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Tips for next time}
-\begin{itemize}
-    \item \textbf{planning} gives chance of zooming out and force oneself to get an overview and to decide how much time on each task
-    \item \textbf{research} phase is most important, dig into basics, discuss ideas with colleagues or go into detail about plan.
-Understand details of methods.
-Make a dummy run.
-Collect (dis-)advantages of different methods.
-Like in design project: do as many and as diverse solutions as possbile.
-Compare and combine the best parts.
-Reading will let learn from others mistakes.
-\\ \td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, could have been verhindert durch lesen the docu and more papers more thoughoughly.
-Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}
-    \item \textbf{objective} should be defined as clear as possible.
-It will help to set a clear goal for each todo, e.g.
-the primary goal of a screening experiment is to identify the active factors.\cite{miller2001using} Which question should be answered and aufstellen a null Hypothesis.
-This is often very trivial, but let's you focus on the correct path.
+    \item Dimension reduction bietet sich stark an bei solcher Datenlage. in pre-optimisation!
     \item \textbf{keep it simple}: include what you already know and reduce model size to minimum, such that \gls{epv} is high.
@@
 A secondary goal is to provide a simple model that captures the essential features of the relationship between these active factors and the response—that is, to identify the active effects.
-\cite{miller2001using}} But $2^6=64$ are too many for preliminary test so maybe check base and from there do $\cdot6=12$ experiments.
+\cite{miller2001using}} But $2^6=64$ are too many for preliminary test so maybe check base and from there do $2\cdot6=12$ experiments.
 Then focus on selected input vars, which might have mutliple maxima \\ \td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
-    \item factorial design (classical \gls{doe}) is more robust at feature extraction for error laden data \cite{giunta2003overview}
-\end{itemize}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{discussion}
-\begin{itemize}
-    \item regularization
-    \item reproducability (random in code and repeat sample)
-    \item error of a sample 
-    \item only include relevant variables\cite{gunst2007fractional}, but include all variables which could contribute\cite{haertler2014statistisch}
+    \item \textbf{factorial design} (classical \gls{doe}) is more robust at feature extraction for error laden data \cite{giunta2003overview} putting data on the extrems makes trend extraction easier.
+"By moving the samples to the boundaries of the design space, the effect of the random error terms is reduced."
+    \item only include relevant variables\cite{gunst2009fractional}, but include all variables which could contribute\cite{haertler2014statistisch}
 %-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest.
@@
     \item which input variables could have been left out? why? justify with intuition and maths
+    \item selection of in- and output vars is more important than coice of learning algorithm. 
+%The process informal part of selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} (page 25)
     \item discuss epv and compare with lit: when searching for appropriate algo, came across multi papers \todo{where should be discussed?}
@@
 %Shanaghi 2013 		MOGA (GA+ANN) population size 100 \cite{shanaghi2013experimental}
-    \item selection of in- and output vars is more important than coice of learning algorithm. 
-%The process informal part of selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} (page 25)
     \item Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}
-    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
-    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error?
-what else?
-%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
-%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
-%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
-%\td{COMMENT: solution age was not accounted for}
-    \item main problems too many in and output vars
-%\td{two main problems: 1.
-too many input variables; 2.
-too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs.
-This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
-    \item what was goal of incorporating ml into this work? 
-%\td{The goal of introducing \gls{ml} to this project was to apply and delve/vertiefen into subject which I've been studying during my undergrad courses.
-This seemed like the perfect opputrunity.
-And indeed I learned a lot.
-Even if only although \gls{ml} is a hot topic at the moment, it can not solve every problem.
-Two important things have I learned regarding \gls{ml}:
         %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \fi %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-
+\end{itemize}
+\subsubsection{Optimisation, modelling and data generation}
+\begin{itemize}
+    \item regularization
+    \item reproducability (random in code and repeat sample)
+    \item main problems too many in and output vars
+%\td{two main problems: 1.
+too many input variables; 2.
+too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs.
+This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
+\end{itemize}
+\subsubsection{Evaluation, interpretation and outlook phase}
+\begin{itemize}
+    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
+    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
+    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error?
+what else?
+%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
+%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
+%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
+%\td{COMMENT: solution age was not accounted for}
+    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
 \end{itemize}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

### 2023-02-23 Thesis/chapter/063-discussion.tex
free write 1.phase

@@
 This subsection will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
-Firstly, the research, exploration and design phase, then the pre-optimisation, \td{refinement} and narrowing phase, sequentially the optimisation, modelling and \td{main measurement}  phase and finally the evaluation, interpretation and outlook phase.
+Firstly, the \textit{research, exploration and design phase}, followed by the \textit{narrowing, pre-optimisation and constraint phase}, thereupon the \textit{optimisation, modelling and data generation phase} and finally the \textit{evaluation, interpretation and outlook phase}.
+%\subsubsection{Research, exploration and design phase}
+%\subsubsection{Narrowing, pre-optimisation and constraint phase}
+%\subsubsection{Optimisation, modelling and data generation}
+%\subsubsection{Evaluation, interpretation and outlook phase}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Research, exploration and design phase}
+\td{freewriting}: \textbf{Scrutinize everthing!} At the beginning of a project it is importatnt 
+to get a feel. I took the first recipe as only true recipe and tried to tune it to perfection. 
+The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
+I only noticed this after trying out another recipe. 
+My tipp here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
+This will get you a "feel" of what works and what not. 
+Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
+Check what works, collect (dis-)advantages of methods and combine the best approaches. 
+This can save you a lot of time.
+
+Moreover, it is important to define the objective of the project as clear and disambiguous as possible. 
+Again, try to reformulate the objective in mutliple ways and choose the most fitting. 
+Answer which question should be answered, and establish hypotheses with corresponding null hypotheses. 
+A general experimental procedure was stated by Cherkassky and Mulier\cite{cerkassky1998learning}:
+\begin{enumerate}
+    \item \textbf{State the problem}
+    \item \textbf{Formulate the hypothesis}
+    \item \textbf{Design the experiment/data generation process}
+    \item \textbf{Collect the data and perform preprocessing}
+    \item \textbf{Estimate the model}
+    \item \textbf{Interpret the model/draw the conclusion}
+\end{enumerate}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
 \begin{itemize}
@@
 \fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
 \subsubsection{Narrowing, pre-optimisation and constraint phase}
+\td{This section is about 3. DAta Generation and Experiment Design from cherkessky's list. }
 \begin{itemize}
@@
 \end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
 \subsubsection{Optimisation, modelling and data generation}
@@
 \end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
 \subsubsection{Evaluation, interpretation and outlook phase}

### 2023-02-24 Thesis/chapter/063-discussion.tex
free write phase 2

@@
 This subsection will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
-Firstly, the \textit{research, exploration and design phase}, followed by the \textit{narrowing, pre-optimisation and constraint phase}, thereupon the \textit{optimisation, modelling and data generation phase} and finally the \textit{evaluation, interpretation and outlook phase}.
+Firstly, the 
+\ref{sec:phase1} \textit{\nameref{sec:phase1}}, followed by the 
+\ref{sec:phase2} \textit{\nameref{sec:phase2}}, thereupon the 
+\ref{sec:phase3} \textit{\nameref{sec:phase3}} and finally the 
+\ref{sec:phase3} \textit{\nameref{sec:phase4}}. 
 %\subsubsection{Research, exploration and design phase}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Research, exploration and design phase}
+\label{sec:phase1}
 \td{freewriting}: \textbf{Scrutinize everthing!} At the beginning of a project it is importatnt 
@@
 Answer which question should be answered, and establish hypotheses with corresponding null hypotheses. 
-A general experimental procedure was stated by Cherkassky and Mulier\cite{cerkassky1998learning}:
+A general experimental procedure was stated by Cherkassky and Mulier\cite{cherkassky1998learning}:
 \begin{enumerate}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+\iffalse
 \begin{itemize}
@@
 \fi
+\fi
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Narrowing, pre-optimisation and constraint phase}
-\td{This section is about 3. DAta Generation and Experiment Design from cherkessky's list. }
+\label{sec:phase2}
+After having decided on a base recipe, it is important to define limits and decrease the number of independent varibles. 
+The later is more important due to the curse of dimensionality\cite{cherkassky1998learning}, 
+which states that with increasing dimensionality it get exponentially more difficult to arrive at the same density of datapoints. 
+By excluding input variables from the model 
+the complexity of the model can be drastically reduced. 
+This leads to more information which can be extrated from the remaining data, 
+be it in more detail of the dependence or higher confidence interval. 
+A good measure to compare with literature and other methods is the \gls{epv}. 
+In this work there around 5~\gls{epv}, which is pretty low. 
+This is ofcourse not just as straight forward as suggested. 
+How does one decide which variables to keep and which to incorporate into the model and which to discard? 
+There is the intuitive (expert) way and the mathematical way.
+mathematical ways include: pca, step-wise regression 
+%
+Additionally having wide limit can be an advantage when the data is noisy and the dependence is not too complicated.
+"By moving the samples to the boundaries of the design space, the effect of the random term is reduced\cite{giunta2003overview}."
+%
+There are two opposing principles which can be followed: 
+By introducing a lot of variables into a model presupposes that they and their interactions (!) have a statistically significant effect.\cite{gunst2009fractional}.
+On the other hand a model can be used to tell if a variable exerts an influence. 
+%
+One regime where overfitting occurs is when there are to many parameters to be fitted with not enough data. 
+Overfitting happens in the regime where to many parameters are fitted with not enough data. 
+%
+Another step/deed which is well placed in this phase is the estimating the error by reproducing a singel sample a certain number of times. 
+Where the number will then be higher than during optimisation 
+%
+%\td{This section is about 3. DAta Generation and Experiment Design from cherkessky's list. }
 \begin{itemize}
@@
 %-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest.
-Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2007}
+Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2009}
 %but on the other hand: If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Optimisation, modelling and data generation}
+\label{sec:phase3}
 \begin{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Evaluation, interpretation and outlook phase}
+\label{sec:phase4}
 \begin{itemize}

### 2023-02-26 Thesis/chapter/063-discussion.tex
free write phase 3

@@
 %- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
-%todo{british or US?} 
+%todo{british or US?: sation vs zation} 
 This subsection will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
@@
 Where the number will then be higher than during optimisation 
+\todo{include curse of dimensionality.}
 %
@@
 \label{sec:phase3}
+During the optimisation the main problems were too many in- and output variables, reproducability and regularisation.
+The first, problem was already discussed in the previous section.
+When working with stochastic algorithms it is especially important to be introduce reproducability via a seed, which determine all subsequent pseudo-random numbers.
+Finally, during the \gls{emma} optimisation es wurde auf regularisation verzichtet, 
+because the regularization would be different 
+because regularizing with the meand and std deviation would alter previous messurements, which alread beitragen to the model and the influence the decision of the next sample. 
+On the other hand haette man auf jeden fall die input variablen normieren können. 
+Normally, for standardisation the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
+One could have assumed a standard uniform distribution. 
+rather $x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$
 \begin{itemize}

### 2023-02-26 Thesis/chapter/030-theory-materials.tex
change from article to report

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Photovoltaics}
-%\subsubsection{Problems of current energy supply}
+\section{Photovoltaics}
+%\subsection{Problems of current energy supply}
 The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{History of Photovoltaics}
+\subsection{History of Photovoltaics}
 The photoelectric effect was first described in 1839 by french scientist Alexandre 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Photovoltaics Basics}
+\subsection{Photovoltaics Basics}
 The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CIGS}
+\subsection{CIGS}
 \gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Materials and Their Analysis}
+\section{Materials and Their Analysis}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Zirconium oxide}
+\subsection{Zirconium oxide}
 Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Sol-Gel and Doctor Blading}
+\subsection{Sol-Gel and Doctor Blading}
 %\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.

### 2023-02-26 Thesis/chapter/031-theory-calculations.tex
change from article to report

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Machine Learning and Statistics}
+\section{Machine Learning and Statistics}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Artificial Inteligence and Machine Learning}
+\subsection{Artificial Inteligence and Machine Learning}
 %How can \gls{ai} and \gls{ml} be defined? 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Machine Learning Methods}
+\subsection{Machine Learning Methods}
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Population Based Optimisation Algorithms}
+\subsection{Population Based Optimisation Algorithms}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{EMMA}
+\subsection{EMMA}
 \Gls{emma} is an implementation of the \gls{pso} in the \texttt{R} programming language. 
@@
 \iffalse
-\subsubsection{Kernel Ridge Regression and Support Vector Machine}
+\subsection{Kernel Ridge Regression and Support Vector Machine}
 \textbf{goal}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Design of Experiment} %DOE
+\subsection{Design of Experiment} %DOE
 %\epigraph{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}{Grahem C.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Analysis of Variance} % ANOVA
+\subsection{Analysis of Variance} % ANOVA
 \Gls{anova} is a statistical test for estimating the influence of multiple categorical independent variables on a dependent numerical variable. 
@@
 %%% VALIDATION 
-\subsubsection{Validation}
+\subsection{Validation}
 Validation is an important part of data analysis as it allows to estimate model errors. 

### 2023-02-26 Thesis/chapter/04-experimental.tex
start incorporate post-emma into theory
change from article to report

@@
 And during the third and final step the experiments for the optimisation were performed.
-\subsection{Substrate Preparation}
+\section{Substrate Preparation}
 Five different substrates were used throughout this work: 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Solutions}\label{sec:exp-sol}
+\section{Solutions}\label{sec:exp-sol}
 All recipes for solutions can be divided into two categories:
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Aquatic solution}\label{sec:exp-sol-aq}
+\subsection{Aquatic solution}\label{sec:exp-sol-aq}
 \gls{zrpro} was added to \gls{acac} while stirring and in a separate vessel \gls{water} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Buthanolic solution}\label{sec:exp-sol-bu}
+\subsection{Buthanolic solution}\label{sec:exp-sol-bu}
 Five different concentrations of the buthanolic solutions were prepared. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Doctor blading}
+\section{Doctor blading}
 \label{sec:exp-db}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Calcination}\label{sec:exp-calc}
+\section{Calcination}\label{sec:exp-calc}
 A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Characterisation}
+\section{Characterisation}
 All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pre-optimisation}\label{sec:exp-preopt}
+\section{Pre-optimisation}\label{sec:exp-preopt}
 %\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
@@
 from which the bulk were screening experiments optimized via biotic reinforcement learning 
-(i.e. my brain) in order to obtain reasonable constraints for pre-optimization. 
+(i.e. my brain) in order to obtain reasonable constraints for computerized pre-optimization. 
 %Initially, glass plates were doctor bladed manually with aquatic solution and calcinated 

### 2023-02-26 Thesis/chapter/062-post-emma.tex
change from article to report

@@
-\subsection{Post-EMMA}
+\section{Post-EMMA}
 \label{sec:res-post-emma}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{ANOVA}\label{sec:res-anova}
+\subsection{ANOVA}\label{sec:res-anova}
 %\textbf{EMMA}
@@
 %%%%%%%%%%%%%%%%%%%% LIN REG %% lin reg %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{Linear Regression} 
+\subsection{Linear Regression} 
 %Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influennced by the Zirconium concentrain in the starting solution $c_{zr}$ and the number of layers applied $\lambda$, but their coefficients are the smallest in absolute values.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsubsection{Grid Search, KRR and SVM}
+\subsection{Grid Search, KRR and SVM}
 The optimal parameters for each \textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 

### 2023-02-26 Thesis/chapter/063-discussion.tex
change from article to report

@@
-\subsection{Hindsight is easier than foresight}
-%\subsection{Discussion}
+\section{Hindsight is easier than foresight}
+%\section{Discussion}
 %\todo{search i.e. and replace with i.e.\ }
@@
 %todo{british or US?: sation vs zation} 
-This subsection will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
+This section will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
 Firstly, the 
@@
 \ref{sec:phase3} \textit{\nameref{sec:phase4}}. 
-%\subsubsection{Research, exploration and design phase}
-%\subsubsection{Narrowing, pre-optimisation and constraint phase}
-%\subsubsection{Optimisation, modelling and data generation}
-%\subsubsection{Evaluation, interpretation and outlook phase}
+%\subsection{Research, exploration and design phase}
+%\subsection{Narrowing, pre-optimisation and constraint phase}
+%\subsection{Optimisation, modelling and data generation}
+%\subsection{Evaluation, interpretation and outlook phase}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Research, exploration and design phase}
+\subsection{Research, exploration and design phase}
 \label{sec:phase1}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Narrowing, pre-optimisation and constraint phase}
+\subsection{Narrowing, pre-optimisation and constraint phase}
 \label{sec:phase2}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Optimisation, modelling and data generation}
+\subsection{Optimisation, modelling and data generation}
 \label{sec:phase3}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Evaluation, interpretation and outlook phase}
+\subsection{Evaluation, interpretation and outlook phase}
 \label{sec:phase4}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsubsection{LINKS}
+%\subsection{LINKS}
 %\begin{itemize}

### 2023-02-26 Thesis/chapter/063-discussion.tex
finish discussion

--- 2023-02-24 Thesis/chapter/063-discussion.tex
@@
 if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
-%todo{go to anova discussion}
+%\todo{go to anova discussion}
 %- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
-%todo{british or US?} 
-This subsection will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
+%\todo{british or US?: sation vs zation} 
+%\todo{ include last phase into previous section}
+This section will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
 Firstly, the 
-\ref{sec:phase1} \textit{\nameref{sec:phase1}}, followed by the 
-\ref{sec:phase2} \textit{\nameref{sec:phase2}}, thereupon the 
-\ref{sec:phase3} \textit{\nameref{sec:phase3}} and finally the 
-\ref{sec:phase3} \textit{\nameref{sec:phase4}}. 
-%\subsubsection{Research, exploration and design phase}
-%\subsubsection{Narrowing, pre-optimisation and constraint phase}
-%\subsubsection{Optimisation, modelling and data generation}
-%\subsubsection{Evaluation, interpretation and outlook phase}
+\ref{sec:phase1} \textit{\nameref{sec:phase1}}%
+, followed by the 
+\ref{sec:phase2} \textit{\nameref{sec:phase2}}%
+%, thereupon the 
+ and finally the 
+\ref{sec:phase3} \textit{\nameref{sec:phase3}}%
+%\ref{sec:phase3} \textit{\nameref{sec:phase4}}%
+ will be discussed.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Research, exploration and design phase}
+\subsection{Research, exploration and design phase}
 \label{sec:phase1}
-\td{freewriting}: \textbf{Scrutinize everthing!} At the beginning of a project it is importatnt 
-to get a feel. I took the first recipe as only true recipe and tried to tune it to perfection. 
+%\td{freewriting}: 
+\textbf{Scrutinize everything!} At the beginning of a project it is important 
+to get a ``feel''. I took the first recipe as only true recipe and tried to tune it to perfection. 
 The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
 I only noticed this after trying out another recipe. 
-My tipp here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
-This will get you a "feel" of what works and what not. 
+My tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
+This will get you a ``feel'' of what works and what does not. 
 Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
@@
 
-Moreover, it is important to define the objective of the project as clear and disambiguous as possible. 
-Again, try to reformulate the objective in mutliple ways and choose the most fitting. 
+Moreover, it is important to define the objective of the project as clear and unambiguous as possible. 
+Again, try to reformulate the objective in multiple ways and choose the most fitting. 
 Answer which question should be answered, and establish hypotheses with corresponding null hypotheses. 
-A general experimental procedure was stated by Cherkassky and Mulier\cite{cherkassky1998learning}:
+A general experimental design procedure was stated by Cherkassky and Mulier in  ``Learning from Data''\cite{cherkassky1998learning}:
 \begin{enumerate}
-    \item \textbf{State the problem}
-    \item \textbf{Formulate the hypothesis}
-    \item \textbf{Design the experiment/data generation process}
-    \item \textbf{Collect the data and perform preprocessing}
-    \item \textbf{Estimate the model}
-    \item \textbf{Interpret the model/draw the conclusion}
+    \item {State the problem}
+    \item {Formulate the hypothesis}
+    \item {Design the experiment/data generation process}
+    \item {Collect the data and perform preprocessing}
+    \item {Estimate the model}
+    \item {Interpret the model/draw the conclusion}
 \end{enumerate}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Narrowing, pre-optimisation and constraint phase}
+\label{sec:phase2}
+The selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} %(page 25)
+After having decided on a base recipe, it is important to define limits and decrease the number of independent variables. 
+The later is more important due to the curse of dimensionality\cite{cherkassky1998learning}, 
+which states that with increasing dimensionality it get exponentially more difficult to arrive at the same density of data points. 
+By excluding input variables from the model, 
+the complexity of the model can be drastically reduced. 
+This leads to more information which can be extracted from the remaining data, 
+be it in more detail of the dependence or higher confidence interval. 
+A good measure to compare with literature and other methods is the \gls{epv}. 
+The \gls{epv} in this work is round 5,
+which is low in comparison with literature consulted
+\cite{
+ahmed2017preparation,
+fernandes2010multi,
+kaczmarowski2015genetic,
+mahdavi2017hardness,
+soltanali2014neural,
+panwar2014design,
+schubert2008design,
+shanaghi2013experimental}.
+Reducing variables is of course no easy task.
+How does one decide which variables to keep and which to incorporate into the model and which to discard? 
+There is an intuitive (expert) way and a mathematical way.
+An expert would decide which variables to discard by his expert knowledge about the domain. 
+Mathematical ways include principal component analysis and step-wise regression.
+%
+Additionally, having wide limits can be an advantage when the data is noisy and the dependence is not too complicated, because by moving samples to the boundaries of the design space, the effect of the noise is reduced\cite{giunta2003overview}.
+This suggest variable reduction favorable over limit narrowing.
+%"By moving the samples to the boundaries of the design space, the effect of the random term is reduced\cite{giunta2003overview}."
+%
+There are two opposing principles which should be kept in mind when reducing variables, though:
+By introducing a lot of variables into a model presupposes that they and their interactions (!) have a statistically significant effect\cite{gunst2009fractional}.
+On the other hand a model can be used to tell if a variable exerts an influence\cite{haertler2014statistisch}. 
+%
+%One regime where overfitting occurs is when there are to many parameters to be fitted with not enough data. 
+Another reason to avoid too many variables in a model is that they introduce more parameters to fit and overfitting happens in the regime where to many parameters are fitted with not enough data.
+%todo{Overfitting happens in the regime where to many parameters are fitted with not enough data. }
+
+Another step/deed which is well placed in this phase is the estimate the error by reproducing a single sample a certain number of times. 
+%Where the number will then be higher than during optimisation 
+%\todo{include curse of dimensionality.}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Optimisation, modelling and data generation}
+\label{sec:phase3}
+During the optimisation the main problems were too many in- and output variables, reproducibility and regularisation. 
+%The first problem 
+Variable selection has already been discussed in the previous section. 
+When working with stochastic algorithms it is especially important to introduce reproducibility via a seed, which determines all subsequent pseudo-random numbers. 
+Finally, during the \gls{emma} optimisation the input data were not regularized, %es wurde auf regularisation verzichtet, 
+because the regularization would be different for different generations.
+Regularizing with the mean and standard deviation would be either inconsistent across generations or over overvalue the distribution of the initial generation. 
+%because the distribution of 
+%
+%alter previous measurements, which alread beitragen to the model and the influence the decision of the next sample. 
+These were the reasons for not including regularization during \gls{emma} optimization. 
+On the other hand the input data could have been regularized to only take values $[-1;1]$ by defining
+$x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$.
+%On the other hand haette man auf jeden fall die input variablen normieren können. 
+%Normally, for standardisation the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
+%One could have assumed a standard uniform distribution. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+\iffalse
+\begin{itemize}
+    \item regularization
+    \item reproducability (random in code and repeat sample)
+    \item main problems too many in and output vars
+%\td{two main problems: 1.
+too many input variables; 2.
+too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs.
+This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
+\end{itemize}
+\fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\iffalse
+\subsection{Evaluation, interpretation and outlook phase}
+\label{sec:phase4}
+\begin{itemize}
+    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
+    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
+    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error?
+what else?
+%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
+%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
+%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
+%\td{COMMENT: solution age was not accounted for}
+    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
+\end{itemize}
+\fi
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%Issues of methods for learning from data: 
+%\begin{itemize}
+%	\item How to incorporate a priori assumptions into learning? 
+%	\item How to measure model complexity (i.e. flexibility to fit the training data)?
+%	\item How to find a optimal balance between the data and a priori knowledge? 
+%\end{itemize}
+%\cite{cherkassky1998learning}
+%"Learning is the process of estimating an unkown (input,output) dependency of structure of a system using a limit number of observations."\cite{cherkassky1998learning}
+%"Do not attempt to solve a specified problem by indirectly solving a harder general problem as an intermediate step."\cite{cherkassky1998learning}(p33)
+%"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)
+%Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
+%Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps. 
+%Any learning process requires the following(p40): 
+%\begin{itemize}
+%	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
+%	\item A priori knowledge to impose contrains
+%	\item An inductive principle (what needs to be done)
+%		\begin{itemize}
+%			\item penalizeation (regularization) inductive principle
+%			\item early stopping rules (with ANN, difficult to control and interpret)
+%			\item structural risk minimization (SRM) (order according to complexity)
+%			\item Bayesian Inference (add subjectivity to learning machine)
+%			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
+%		\end{itemize}
+%	\item A learning method (how does it need to be done,implementation)
+%\end{itemize}
+%\cite{cherkassky1998learning}
+%am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
+%Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{LINKS}
+%\begin{itemize}
+%    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
+%    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
+%    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
+%\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
@@
 \fi
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Narrowing, pre-optimisation and constraint phase}
-\label{sec:phase2}
-After having decided on a base recipe, it is important to define limits and decrease the number of independent varibles. 
-The later is more important due to the curse of dimensionality\cite{cherkassky1998learning}, 
-which states that with increasing dimensionality it get exponentially more difficult to arrive at the same density of datapoints. 
-By excluding input variables from the model 
-the complexity of the model can be drastically reduced. 
-This leads to more information which can be extrated from the remaining data, 
-be it in more detail of the dependence or higher confidence interval. 
-A good measure to compare with literature and other methods is the \gls{epv}. 
-In this work there around 5~\gls{epv}, which is pretty low. 
-This is ofcourse not just as straight forward as suggested. 
-How does one decide which variables to keep and which to incorporate into the model and which to discard? 
-There is the intuitive (expert) way and the mathematical way.
-mathematical ways include: pca, step-wise regression 
-%
-Additionally having wide limit can be an advantage when the data is noisy and the dependence is not too complicated.
-"By moving the samples to the boundaries of the design space, the effect of the random term is reduced\cite{giunta2003overview}."
-%
-There are two opposing principles which can be followed: 
-By introducing a lot of variables into a model presupposes that they and their interactions (!) have a statistically significant effect.\cite{gunst2009fractional}.
-On the other hand a model can be used to tell if a variable exerts an influence. 
-%
-One regime where overfitting occurs is when there are to many parameters to be fitted with not enough data. 
-Overfitting happens in the regime where to many parameters are fitted with not enough data. 
-%
-Another step/deed which is well placed in this phase is the estimating the error by reproducing a singel sample a certain number of times. 
-Where the number will then be higher than during optimisation 
-%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\td{This section is about 3. DAta Generation and Experiment Design from cherkessky's list. }
+\iffalse
 \begin{itemize}
@@
 \end{itemize}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Optimisation, modelling and data generation}
-\label{sec:phase3}
-\begin{itemize}
-    \item regularization
-    \item reproducability (random in code and repeat sample)
-    \item main problems too many in and output vars
-%\td{two main problems: 1.
-too many input variables; 2.
-too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs.
-This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
-\end{itemize}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Evaluation, interpretation and outlook phase}
-\label{sec:phase4}
-\begin{itemize}
-    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
-    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
-    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error?
-what else?
-%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
-%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
-%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
-%\td{COMMENT: solution age was not accounted for}
-    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%Issues of methods for learning from data: 
-%\begin{itemize}
-%	\item How to incorporate a priori assumptions into learning? 
-%	\item How to measure model complexity (i.e. flexibility to fit the training data)?
-%	\item How to find a optimal balance between the data and a priori knowledge? 
-%\end{itemize}
-%\cite{cherkassky1998learning}
-%"Learning is the process of estimating an unkown (input,output) dependency of structure of a system using a limit number of observations."\cite{cherkassky1998learning}
-%"Do not attempt to solve a specified problem by indirectly solving a harder general problem as an intermediate step."\cite{cherkassky1998learning}(p33)
-%"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)
-%Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
-%Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps. 
-%Any learning process requires the following(p40): 
-%\begin{itemize}
-%	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
-%	\item A priori knowledge to impose contrains
-%	\item An inductive principle (what needs to be done)
-%		\begin{itemize}
-%			\item penalizeation (regularization) inductive principle
-%			\item early stopping rules (with ANN, difficult to control and interpret)
-%			\item structural risk minimization (SRM) (order according to complexity)
-%			\item Bayesian Inference (add subjectivity to learning machine)
-%			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
-%		\end{itemize}
-%	\item A learning method (how does it need to be done,implementation)
-%\end{itemize}
-%\cite{cherkassky1998learning}
-%am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
-%Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsubsection{LINKS}
-%\begin{itemize}
-%    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
-%    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
-%    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
-%\end{itemize}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\fi

### 2023-02-26 Thesis/chapter/07-outlook.tex
start outlook

@@
+\todo{freewriting:} 
+what did i want to do? 
+The goal of this work was to find a sol-gel process resulting in a insulating zirconium ceramic on top of steel.
+This aufbau then can be used for thin layer photo voltaics. 
+The ceramic needs to be homoegeneous and defect free. 
+what was done? 
+A suitable recipe was found and optimized via \gls{emma}. 
+welche methoden wurden dafür verwendet? 
+after the optimsation the data was analysed with further/different machine learning methods like kernel ridge regression, support vector regression and linear regression. 
+was wurde herausgefunden? 
+A strong correlation of calcination temperature and conductance in the bereich of 300--400\oc{}. 
+was kann noch herausgefundne werden und wie?
+
+was kann noch veraendert werden? 
+humidity 
+solution age
+vdb and tdb on g and phd 
+Tcal on g and phd
+
 Making of the solution for the sol-gel process:
@@
 
-It should have been alos verglichen with grid search with comparable size
+It should have been also verglichen with grid search with comparable size
 but most time was used to find a vernuenfig base recipe and process

### 2023-02-27 Thesis/chapter/061-results-emma.tex
change from article to report
first draft

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{EMMA}
+\section{EMMA}
 \label{sec:res-emma}
@@
 	\centering
-    \caption{Global best per generation with experiment numbers and dependent variables/experiment conditions}
+	\caption{Global best per generation with experiment numbers and dependent variables/experiment conditions \td{include units?}}
 	\label{tab:emma-Gb}
@@
 %%% EQUATION 
-%\subsubsection{Equation}
+%\subsection{Equation}
 Equations (\ref{eq:emma-phd3})-(\ref{eq:emma-vcal3}) and (\ref{eq:emma-phd4})-(\ref{eq:emma-vcal4}) represent the \gls{rf}s at $t=3$ and $t=4$, respsectively, rounded to 2 significant digits.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%\subsubsection{how did evolve over time?}
+%\subsection{how did evolve over time?}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimisands}
+\subsection{rational behind including $v_{cal}$ and $\lambda$ as optimisands}
 }

### 2023-02-27 Thesis/chapter/07-outlook.tex
first draft

--- 2022-02-28 Thesis/chapter/07-outlook.tex
@@
+%\todo{freewriting:} 
+%what did i want to do? 
+The goal of this work was to find a sol-gel doctor blading process resulting in a insulating zirconium ceramic on top of steel.
+This structure then can be used as substrate for thin layer photo voltaics. 
+The ceramic needs to be homoegeneous and defect free in order to insulate properly.
+%what was done? 
+A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
+The recipe was improved by increasing its stability. 
+The best parameters found by the emma optimisation were 
+$c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
+%\todo{$T_{cal}=300$}. 
+%welche methoden wurden dafür verwendet? 
+After optimsation the data was analysed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
+The comparisson of methods showed that \gls{emma} performed well on predicting the correlation between conductance and process variables. 
+%was wurde herausgefunden? 
+A strong correlation of calcination temperature and conductance in the bereich of 300--400\oc{}. 
+%was kann noch herausgefundne werden und wie? 
+Next steps include to investigate if the correlation of condactance and calcination temperature are statistically significant or due to small sample size. 
+The aging process could be examined via infra red spectroscopy. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\iffalse
+was kann noch veraendert werden? 
+humidity 
+solution age
+vdb and tdb on g and phd 
+Tcal on g and phd 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+
 Making of the solution for the sol-gel process:
@@
 In the current work population size, number of generations, and most importantly boundaries (grenzen). 
+\fi

### 2023-02-27 Thesis/chapter/01-introduction.tex
formatting

@@
 An insulating layer must therefore be applied to the steel substrate before any \gls{cigs} cells can be synthesised on top.
+\td{Polymere would be a obvious choice if not for its low melting point.}
 A non-toxic material which is suitable for the insulation is \gls{zro}. 
@@
 Section \ref{sec:results} is split into three subsections: material specific results are presented in section \ref{sec:res-mat}, results regarding \gls{pso} in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
-\td{Finally, section \ref{sec:outlook} discusses the outlook and next steps}
+Finally, section \ref{sec:outlook} summarizes and discusses the outlook and next steps.

### 2023-02-27 Thesis/chapter/04-experimental.tex
formatting

@@
 Five different substrates were used throughout this work: 
-microscope glass slides (\cm{2.5}\x\cm{7.5})\ds{ from Sigma Aldrich},\ds{ thinner,} squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
+microscope glass slides 
+\linebreak[4] 
+(\cm{2.5}$\times$\cm{7.5})\ds{ from Sigma Aldrich, thinner}, 
+squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
+\gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
+\gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
 %
@@
 	\label{tab:heating}
+	\begin{subtable}{\textwidth}
+		\centering
 		\subcaption{Heating program HP1 used with the Labtech EH45C heating plate}
@@
 		\end{tabular}
+	\end{subtable}
 %%%%%%%%%%%%
+	\begin{subtable}{\textwidth}
+		\centering
 		\subcaption{Heating programs NT1 - NT6 used with the Naberterm LB410 muffle furnace}
 		\label{tab:nt}
+		\resizebox{\textwidth}{!}{
 		\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
@@
 		\end{tabular}
+	}
+	\end{subtable}
 \end{table}

### 2023-02-27 Thesis/chapter/063-discussion.tex
formatting

@@
 These were the reasons for not including regularization during \gls{emma} optimization. 
-On the other hand the input data could have been regularized to only take values $[-1;1]$ by defining
+On the other hand the input data could have been regularized to only take values $[-1;1]$ by defining the regularized varible as 
 $x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$.

### 2023-03-01 Thesis/chapter/01-introduction.tex
proof read until sputtering

--- 2022-11-08 Thesis/chapter/01-introduction.tex
@@
 Furthermore, 
-it uses the suns energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
+it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
 it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
@@
 An insulating layer must therefore be applied to the steel substrate before any \gls{cigs} cells can be synthesised on top.
+Polymere would be a obvious choice if not for its low melting point which makes high prodction temperatures inpractical.
 A non-toxic material which is suitable for the insulation is \gls{zro}. 
@@
 algorithm. 
-The resulting optimum is compared with other optimisation methods.
+%The resulting optimum is compared with other optimisation methods.
 
@@
 
-The remainder of this work is organized with section 
+The remainder of this work is organized with chapter 
 %\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
 \ref{sec:theoretical} giving 
-some background on topics of \gls{pv}, material science and computational science which were used in this work.
-In sections \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
-Section \ref{sec:results} is split into three subsections: material specific results are presented in section \ref{sec:res-mat}, results regarding \gls{pso} in \label{sec:res-emma} and further analysis in section \ref{sec:res-post}.
-\td{Finally, section \ref{sec:outlook} discusses the outlook and next steps}
+some background information on topics of \gls{pv}, material science and computational science which were used in this work.
+In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
+Section \ref{sec:results} is split into three sections: material specific results are presented in section \ref{sec:res-mat}, results regarding \gls{pso} in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
+Finally, chapter \ref{sec:outlook} summarizes and discusses the outlook and next steps.

### 2023-03-01 Thesis/chapter/030-theory-materials.tex
first draft
formatting
proof read until sputtering

@@
 This chapter can be broken down into three sections. 
-The first section tries to shine light on the evolution of PV and give some background on \gls{cigs}.
+The first section tries to shine light on the evolution of PV and give some background information on \gls{cigs}.
 The middle section reads about material-scientific methods which were used during the practical part of this work. 
@@
 The photoelectric effect was first described in 1839 by french scientist Alexandre 
-Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel (the person after whom the unit is named).
-Another relevant piece of the \gls{pv} jigsaw was brought to light
+Edmond \linebreak[4] 
+Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel (the person after whom the unit is named).
+Another relevant piece in the \gls{pv} jigsaw was brought to light
 %discovered
@@
 The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
-the creation of an electron-hole pair and then its separation by the structure of the material.\cite{markvart2013principles}
+the creation of an electron-hole pair and then its separation by the structure of the material\cite{markvart2013principles}.
 This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
@@
 silicon); if not, heterojunctions e.g.
-\ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}.\cite{breitenstein2013understanding}
+\ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}\cite{breitenstein2013understanding}.
 %
@@
 In 2022 
-over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon).\cite{breitenstein2013understanding}
+over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon)\cite{breitenstein2013understanding}.
 %
@@
 %Already in 1975 efficiencies of cells of over 10\% were achieved.\cite{kazmerski1976thin}
-Cells with efficiencies of over 10\% were achieved already by 1975.\cite{kazmerski1976thin}
+Cells with efficiencies of over 10\% were achieved already by 1975\cite{kazmerski1976thin}.
 Today, 
@@
 
-Just like CdTe, GaAs and amorphous silicon CIGS has much higher absorption coefficients 
+Just like CdTe, GaAs and amorphous silicon, CIGS has much higher absorption coefficients 
 (lower penetration depth) of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}). 
@@
     \center
+	\resizebox{\textwidth}{!}{
 		\begin{tabular}{cccccc}
@@
 			\hline
-		Material&   Type&    Band Gap [\ev{}]&    Wavelength [\nm{}]&    Absorption coef. $\alpha$ [\pcm{}]    &Penetration Depth [\um{}]\\
+			Material&   Type&    Band Gap [\ev{}]&    $\lambda$ [\nm{}]&    Abs. coef. $\alpha$ [\pcm{}]    &Penetration Depth [\um{}]\\
 			\hline
@@
 		\end{tabular}
+	}
     \caption{Photonic properties of several established \gls{pv} materials (data from \cite{mertens2020photovoltaik})}
@@
 
-\begin{figure}
+\begin{figure}[tbh]
 	\includegraphics[width=\textwidth]{./Pics/cigs.png}
@@
 The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in 112 direction\cite{hedstrom1993cigs}.
-A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporated from elemental sources controlled by a mass spectrometer.\cite{hedstrom1993cigs}
+A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporation from elemental sources controlled by a mass spectrometer.\cite{hedstrom1993cigs}
 The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
@@
 
+\pagebreak[4]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Zirconium oxide}
-Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
+Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV\cite{Anwar2017} and relative permittivity of circa 20 at room temperature\cite{kukli2001dielectric}. 
 This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
@@
 It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
-Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3})\cite{Nielsen2005}.
+%Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3})\cite{Nielsen2005}.
 %"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.
@@
 %
-\Gls{db} coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing, and ceramic industries.
+\Gls{db} coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing and ceramic industries.
 The roll-to-roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Sputtering}
+\subsection{Sputtering}
 %SPUTTERING FREEWRITING: 
@@
 \Gls{pvd} can be divided into activation by thermal energy and activation by energetic particle bombardment. 
-Sputtering is of the latter, which 
+Sputtering is of the latter kind, which 
 is advantageous if substrates can't withstand high temperatures.
@@
         the top rectangle depicts the source/cathode/target, 
-        the lower rectangle the anode/substrate holder and 
-        the bottom rectangle the substrate to be sputtered. 
+        the bottom rectangle the anode/substrate holder and 
+        the middle rectangle the substrate to be sputtered. 
     (b) example series of collision processes leading to sputtering of atoms: 
@@
 %the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
-The anode, then, emits electrons which collide with a gas particles (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
+The anode, then, emits electrons which collide with a gas particles (mostly argon because of its inert properties and potential to transfer more kinetic than lighter noble gases). 
 Some gas particles may get ionized by the collision and the gas cations are accelerated to the anode. 
@@
 The pressure in the chamber should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand 
-a minimum pressure is needed to keep the plasma "alive". 
+a minimum pressure is needed to keep the plasma ``alive''. 
 Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
@@
 A magnetron can be placed behind the cathode (target) in order to trap the plasma close to the source. 
-This lowers the pressure needed to keep the plasma "alive". 
+This lowers the pressure needed to keep the plasma ``alive''. 
 Furthermore, magnetrons prevent high energy electrons from reaching the substrate and 
@@
 The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning;
-meaning the target begin covered by an insulating layers which can lead to defects in the growing film\cite{Kelly2000}.
+meaning that the target is being covered by an insulating layers which can lead to defects in the growing film\cite{Kelly2000}.
 
 The limitation of only being able to use conducting materials as targets can be circumvented by using a radio frequency electrical field. 
-This prevents charge from building up on the target. 
+This prevents charge from building up on the target. \linebreak[2]
 Although radio frequency sputtering is more versatile, directional current sputtering is more common because of it's simpler system and economical reasons.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Scanning electron Microscopy}
+\subsection{Scanning electron Microscopy}
 The history of \gls{sem} can be traced back to 1843 when Scottish clockmaker Alexander Bain filed a patent for dissecting an image by scanning.
@@
 In this work \gls{sem} was used as a preliminary way of checking the surface condition. 
+% squeeze condition into this page 
+\enlargethispage{\baselineskip}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{UV/Vis/NIR Spectroscopy}
+\subsection{UV/Vis/NIR Spectroscopy}
 %%% WHAT? 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{X-Ray Diffraction}
+\subsection{X-Ray Diffraction}
 %\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}

### 2023-03-05 Thesis/chapter/030-theory-materials.tex
finish sputtering

@@
 
-\begin{figure}[htb]
+\begin{figure}[tbh]
     \centering
@@
 two parallel electrodes with low pressure gas in between. 
-The target acts as anode and the substrate (holder) as cathode (see figure \ref{fig:sputter0}).
+The target acts as as feedstock anode and the substrate (holder) as cathode (see figure \ref{fig:sputter0}).
 %the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
-The anode, then, emits electrons which collide with a gas particles (mostly argon because of its inert properties and potential to transfer more kinetic than lighter noble gases). 
+The anode, then, emits electrons which collide with gas particles (mostly argon because of its inert properties and potential to transfer more kinetic than lighter noble gases). 
 Some gas particles may get ionized by the collision and the gas cations are accelerated to the anode. 
-If a cation has enough energy it will bump off one or more atoms or molecules from the surface. 
+If a cation has enough energy, it will bump off one or more atoms or molecules from the surface. 
 This happens by a cascade of momentum transfers, which can reach the surface again (see figure \ref{fig:sputter1}). 
 If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
-This neutral sputtered particle travels unaffected by the electrical field perpendicular to the surface towards the substrate and condenses with other particles to form a layer.
-The pressure in the chamber should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand 
+This neutral sputtered particle travels -- unaffected by the electrical field nearly perpendicular to the surface -- towards the substrate and condenses with other particles to form a layer.
+The pressure in the chamber should be small, such that the sputtered particle has a long mean free path, but on the other hand 
 a minimum pressure is needed to keep the plasma ``alive''. 
-Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
+Usual pressures buzz around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
 
@@
 colliding with an argon atom and ionizing it, increasing the yield.
-
+%
 When oxygen or nitrogen are added to the gas this is called reactive sputtering.
@@
 The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning;
-meaning that the target is being covered by an insulating layers which can lead to defects in the growing film\cite{Kelly2000}.
-
+meaning that the target is being passivated by an insulating layers which can lead to defects in the growing film\cite{Kelly2000}. 
+%
 The limitation of only being able to use conducting materials as targets can be circumvented by using a radio frequency electrical field. 
@@
 
+\pagebreak[4]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-03-05 Thesis/chapter/030-theory-materials.tex
start calc theory

--- 2023-03-01 Thesis/chapter/030-theory-materials.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   SEM    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Scanning electron Microscopy}
 The history of \gls{sem} can be traced back to 1843 when Scottish clockmaker Alexander Bain filed a patent for dissecting an image by scanning. 
-A detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}.
+The first \gls{sem} was build in 1933, 
+the first images from scanning electron beams were published in 1935
+and the first \gls{sem} was marketed in 1965.
+A more detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}. 
 \Gls{sem} is a microscopical technique which allows visualisation of surfaces with features in the nano meter regime. 
 While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
-This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to light\cite{Kaliva2020}.
+This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to visible light\cite{Kaliva2020}.
 The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons. 
@@
 Electrons originate from either a \gls{feg}, where a strong electrical field rips electrons from the bulk, or from thermionic guns where the filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted.
-Electrons are then accelerated by a voltage of 2 to 40 kV and bundled into narrow beams by lenses\cite{Vernon2000}.
-A high \gls{mfp} is needed for electrons to travel from the source to the sample (and to the detector). 
-Thus, a very low pressure is in the inside. 
-In this work \gls{sem} was used as a preliminary way of checking the surface condition. 
+Electrons are then accelerated by a voltage of \SI{2}{\kilo\volt} to \SI{40}{\kilo\volt} and bundled into narrow beams by lenses\cite{Vernon2000}.
+A high mean free path is needed for electrons to travel from the source to the sample (and to the detector). 
+Thus, a very low pressure is needed inside the microscope. 
+In this work \gls{sem} was used as a preliminary way of checking the quality of \gls{zro} layer. 
 % squeeze condition into this page 
@@
 interactions of \gls{uv}, \gls{vis} and \gls{nir} light 
-(wavelengths $\lambda$ of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
+(wavelengths of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
 In general, light is described as periodic \gls{em} wave 
 which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
-In other materials light moves with the velocity $v=\frac{c}{n(\lambda)}$, where $n(\lambda)$ is the refractive index which is a function of the wavelength. 
-The relation of energy~$E$ of a photon, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
+In other materials light moves with the velocity $v=\frac{c}{n(\lambda)}$, where $n(\lambda)$ is the refractive index which is a function of the wavelength $\lambda$. 
+The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
 \begin{align*}
@@
  %A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
-In the two-beam-spectrometer the light emitted from the light source is split, 
+In the classic two-beam-spectrometer the light emitted from the light source is split, 
 sent through the sample and the reference and one of the two beams is alternately 

### 2023-03-05 Thesis/chapter/031-theory-calculations.tex
start calc theory

@@
 		%{Machine and deep learning in MS research are just powerful statistics – No}
-What is \gls{ml}? Some might argue that \gls{ml} is just overglorified statistics, but that's not the case. 
+%What is \gls{ml}? 
+Some might argue that \gls{ml} is just overglorified statistics, but that's not the case. 
 Although \gls{ml} uses several statistical methods, their goal and frame conditions are different. 
@@
 %
-\Gls{ml} tries to predict unseen data points and statistics is a subfield of maths 
+\Gls{ml} tries to predict unseen data points accurately and statistics is a subfield of maths 
 which tries to get insight into a given data. 
@@
 whereas (classical) statistics is the domain of representing the data. 
+Nonetheless, statistics and maths is at the basis of \gls{ml}.
 
@@
 (in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
-Another test \textit{ingenioused} by Alan Turing, is the imitation game\cite{turing1950imitation}, nowadays known as Turing test.
-An interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
+Another test \textit{ingenioused} by Alan Turing is the imitation game\cite{turing1950imitation}, nowadays known as Turing test:
+an interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
 \textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is on the interrogators side.
@@
 
-But fear not, that doesn't mean that computers are sentient or more intelligent than humans\cite{searle1980,searle1999married} and certainly not that research is over. 
+But fear not, that doesn't mean that computers are sentient or more intelligent than humans\cite{searle1980,searle1999married} even though some claim\cite{tiku2022google} and it certainly does not mean that research is over.
 AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
@@
 certain fields get incorporated into \gls{ai} research and practice,
-such that, after some time of general use it is no more considered \gls{ai} (e.g. spam filter or web searches).
+such that after some time of general use it is no more considered \gls{ai} (e.g. spam filter or web searches).
 Google CEO Sundar Pichai even goes as far and said: 
-"AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}
+"AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}.
 

### 2023-03-05 Thesis/chapter/033-linreg-krr-svm.tex
finish svm
start calc theory

@@
 \end{equation}
-Where $\mathbf{y}$ (size $\mathbb{R}^n$, where $n$ is the number of data points) is a vector of dependent variables and $\mathbf{X}$ (size $\mathbb{R}^{n\times d}$, where $d$ is the the number of independent variables) is a matrix of independent variables.
+Where $\mathbf{y}$ (size $\mathbb{R}^n$, where $n$ is the number of data points) is a vector of dependent variables which shall be predicted and $\mathbf{X}$ (size $\mathbb{R}^{n\times d}$, where $d$ is the the number of independent variables) is a matrix of independent variables.
 The parameters $\mathbf{k}$ (size $\mathbb{R}^d$) and $c$ (size $\mathbb{R}$) are chosen by minimizing an objective function (loss function in \gls{ml} chargon).
-A typical function to minimize are the L1 and L2 error, i.e. \gls{mae} and \gls{mse}, respectively.
+A typical function to minimize are the $L_1$ and $L_2$ error, i.e. \gls{mae} and \gls{mse}, respectively.
 \begin{align}
-L_1&= \sum |y_i - \hat y_i| = \sum \sum |y_i - x_{i,j}\cdot k_i+c| \\
-L_2&= \sum(y_i - \hat y_i)^2 = \sum (y_i - x_{i,j}\cdot k_i+c)^2
+L_1&= \sum_i |y_i - \hat y_i| \\%= \sum_i \sum_j |y_i - x_{i,j}\cdot k_i+c| \\
+L_2&= \sum_i(y_i - \hat y_i)^2 %= \sum_i \sum_j (y_i - x_{i,j}\cdot k_i+c)^2
 \end{align}
@@
 \textbf{Ridge Regression} is like linear regression but with an extra term which penalizes steep regression functions.
-This extra term which reduces overfitting is scaled by a correction parameter $\lambda$. 
-The larger, $\lambda$ the larger regularisation and the flatter the regression functions. 
-When $\lambda$ tends to infinity, we get an intercept-only model.
-When $\lambda$ is zero, the regularized loss function becomes the OLS loss function.
+This extra term which reduces overfitting is scaled by a correction parameter~$\alpha$. 
+The larger $\alpha$ is, the larger is the regularisation and the flatter is the regression functions. 
+When $\alpha$ tends to infinity, we get an intercept-only model.
+When $\alpha$ is zero, the regularized loss function becomes the $L_2$ loss function.
 %\td{A critique of ridge regression is that all the variables tend to end up in the model. The model only shrinks the coefficients.}
 \begin{equation}
-    L_{RR} = L_2 + \lambda \sum k_i = \sum(y_i - \hat y_i)^2 + \lambda \sum k_i
+    L_{RR} = L_2 + \alpha \sum k_i = \sum(y_i - \hat y_i)^2 + \alpha \sum k_i
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%% { Kernel Ridge Regression } KRR %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textbf{\gls{krr}} combines ridge regression with the kernel method. 
-A~kernel transforms data in such a way that a linear hyperplane (a line in two dimensions, 
+\textbf{\Gls{krr}} combines ridge regression with the kernel method. 
+A~kernel transforms data in such a way that a linear hyperplane (a point in one dimension, a line in two dimensions, 
 a plane in three dimensions) can fit data in regression problems or seperate the data in classification problems without actually doing the transormation for every data point. 
 A kernel is some kind of similarity measure 
-which fulfills the requirements of nonnegativity, symmetry, linearity\cite{rupp2015machine}.
+which fulfills the requirements of nonnegativity, symmetry and linearity\cite{rupp2015machine}.
 The following equations show definitions for 
@@
 A requirement for using kernels is having a dot product in the loss function. 
-This can be accomplished by expressing $\mathbf{k}$ with $\mathbf{X}$: $\mathbf{k}=\mathbf{X}^\top \mathbf{r}$
+This can be accomplished by expressing $\mathbf{k}$ in terms of $\mathbf{X}$: $\mathbf{k}=\mathbf{X}^\top \mathbf{r}$
 \cite{rudin2020least}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%% { Support vector machines } SVM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textbf{\Gls{svm}} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training} . 
+\textbf{\Gls{svm}} is a versatile machine learning algorithm first mentioned in 1992\cite{boser1992training} . 
 %
@@
 The distance from the points to the hyperplane is called margin $\tau$.
-These points are called support vectors and are used to define the hyperplane.
+The points with the shortest distance to the hyperplane are called support vectors and are used to define the hyperplane.
 A \gls{svm} avoids overfitting by only using a subset of the data - the support vectors - to fit the model. 
@@
 \begin{equation}
-	\hat{\mathbf{y}} = h(\mathbf{x}) = \mathbf{w} \cdot \mathbf{x} + b
+	\hat{\mathbf{y}} = h(\mathbf{X}) = \mathbf{X} \cdot \mathbf{w} + b
 \end{equation}
-with $
-\mathbf{y} \in \lbrace +1, -1 \rbrace^n ,\,
-\hat{\mathbf{y}} \in \mathbb{R}^n ,\,
-\mathbf{w} \in \mathbb{R}^d ,\,
-\mathbf{x} \in \mathbb{R}^{n \times d} 
-$.
-The constraint of the positive and negative support vectors ($x^+$ and $x^-$, respectively) satisfying
+with 
+$\mathbf{y} \in \lbrace +1, -1 \rbrace^n$, 
+$\hat{\mathbf{y}} \in \mathbb{R}^n$,
+$\mathbf{X} \in \mathbb{R}^{n \times d}$ and
+$\mathbf{w} \in \mathbb{R}^d$.
+The constraint of the positive and negative support vectors ($\mathbf{x}^+$ and $\mathbf{x}^-$, respectively) satisfying
 \begin{align}
-	\mathbf{w} \cdot x^+ + b &= 1 \\
-	\mathbf{w} \cdot x^- + b &= -1 
+	\mathbf{x}^+ \cdot \mathbf{w} + b &= 1 \\
+	\mathbf{x}^- \cdot \mathbf{w} + b &= -1 
 \end{align}
@@
 	\label{eq:svm01}
-	y_i(\mathbf{w} \cdot \mathbf{x}_i + b ) \geqslant 1 %\qquad i=1,\dots,n
+	y_i(\mathbf{x}_i \cdot \mathbf{w} + b ) \geqslant 1 %\qquad i=1,\dots,n
 \end{equation}
@@
 on opposite sides of the decision boundary onto the unit vector perpendicular to the hyperplane. 
-If we now take a vector from a positive support vector $x^+$ to a negative support vector $x^-$ and project it on to the unit vector of $w$ (which is perpendicular to the hyperplane), 
+If we now take a vector from a positive support vector $\mathbf{x}^+$ to a negative support vector $\mathbf{x}^-$ and project it on to the unit vector of $\mathbf{w}$ (which is perpendicular to the hyperplane),
 we get the width of the margin. 
@@
 	\begin{aligned} 
-		2\tau &= (x^+ - x^-) \cdot \frac{\mathbf{w}}{\|\mathbf{w}\|} \\
+		2\tau &= (\mathbf{x}^+ - \mathbf{x}^-) \cdot \frac{\mathbf{w}}{\|\mathbf{w}\|} \\
 			&= (x^+ \cdot \mathbf{w} - x^-\cdot \mathbf{w} ) \cdot \frac{1}{\|\mathbf{w}\|} \\
@@
 	\begin{aligned} 
-		2\tau &= (x^+ - x^-) \cdot \frac{\mathbf{w}}{\|\mathbf{w}\|} 
-			= (x^+ \cdot \mathbf{w} - x^-\cdot \mathbf{w} ) \cdot \frac{1}{\|\mathbf{w}\|} \\
+		2\tau &= (\mathbf{x}^+ - \mathbf{x}^-) \cdot \frac{\mathbf{w}}{\|\mathbf{w}\|} 
+			= (\mathbf{x}^+ \cdot \mathbf{w} - \mathbf{x}^-\cdot \mathbf{w} ) \cdot \frac{1}{\|\mathbf{w}\|} \\
 			&= ( (1-b) - (-1-b) ) \cdot \frac{1}{\|\mathbf{w}\|} 
@@
 %\td{draw sketch and make \ref{eq:svm02} on two lines}
-Thus maximizing the margin is equivalent with minimizing $\|\mathbf{w}\|$ and minimizing $\frac{1}{2}\|\mathbf{w}\|^2$.
-By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we arrive at the loss function which should be maximized: 
+Thus maximizing the margin is equivalent with minimizing $\|\mathbf{w}\|$ and minimizing $\frac{1}{2}\|\mathbf{w}\|^2$ (mathematical convenience for further steps).
+By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we 
+mathemagically arrive at the loss function which should be maximized: 
 \begin{equation}
@@
 Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the innerproduct of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper.
-\td{write about sv regrgession}
+%\td{write about sv regrgession}
+
+\Gls{svm}s can also be used for regression.
+The decision function becomes the regression function and the margin includes all data points instead of none. 
+In a soft margin \gls{svm} a few data point can lie outside the margin as outliers. 
+Non-linearity can be likewise introduced via the kernel trick. 
 %\td{write about kernel}

### 2023-03-05 Thesis/chapter/030-theory-materials.tex
proof read until KRR

@@
 This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to visible light\cite{Kaliva2020}.
-The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons. 
+The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons in the examined material. 
 Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
-Electrons originate from either a \gls{feg}, where a strong electrical field rips electrons from the bulk, or from thermionic guns where the filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted.
+Electrons originate from either a \gls{feg}, where a strong electrical field rips electrons from the bulk, or from thermionic guns where a filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted.
 Electrons are then accelerated by a voltage of \SI{2}{\kilo\volt} to \SI{40}{\kilo\volt} and bundled into narrow beams by lenses\cite{Vernon2000}.
@@
 In general, light is described as periodic \gls{em} wave 
-which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
-In other materials light moves with the velocity $v=\frac{c}{n(\lambda)}$, where $n(\lambda)$ is the refractive index which is a function of the wavelength $\lambda$. 
+which - in vacuum - moves with the speed of light ($c = \mps{299792458}$)\cite{gHobel2006international}.
+In other materials light moves with the velocity $v=\frac{c}{n(\lambda)}$, where $n(\lambda)$
+is the refractive index which is dependent on the wavelength $\lambda$. 
+%is the refractive index which is a function of the wavelength $\lambda$. 
 The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
@@
 \end{align*}
-where $h$ is the Planck's constant.
+where $h$ is Planck's constant.
 %In words: shorter wavelength (higher frequency) photons are more energetic.
@@
 %Molecular vibrations can be separated in valence and deformation vibrations.
-
+%
 % UVVis
@@
 Only vibrations that change the dipole moment of the molecule are \gls{ir} active. 
-The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes. 
+The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes which lead to intricate patterns called the fingerprint region. 
 These transition are mostly "forbidden" quantum mechanically and allow analysis of bulk matter without extensive preparation
@@
 
-\paragraph{Fourier Transform Spectrometer}
+\subsubsection{Fourier Transform Spectrometer}
  %A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
@@
 %
-When the refractive index of two layers differ, light can be used to measure the thickness\cite{Dumin1967} of the optical less dense material.
+%When the refractive index of two layers differ, light can be used to measure the thickness\cite{Dumin1967} of the optical less dense material.
 
@@
 \gls{xrd} is used to study the crystalline structure of materials.
-Since X-rays wavelengths (\num{0.2} to \nm{10}) are comparable to the interatomic spacing of crystalline solids the beams get reflected and contain information about the structure\cite{Kaliva2020}.
+Since X-rays wavelengths (\num{0.2} to \nm{10}) are comparable to the interatomic spacing of crystalline solids, 
+the beams get reflected and contain information about the structure\cite{Kaliva2020}.
 Each crystalline material has a discreet atomic structure, which upon irradiation with 

### 2023-03-05 Thesis/chapter/031-theory-calculations.tex
proof read until KRR

@@
 For example, in a statistical model, it is desirable to reduce the number of inputs. 
-This allows the statistician to better study how a change in the input variable can be 
-directly affected by the output variable.\cite{gontcharov2019}
+This allows a statistician to better study how a change in input variables can 
+directly affect a output variable\cite{gontcharov2019}.
 %pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
@@
 whereas (classical) statistics is the domain of representing the data. 
-Nonetheless, statistics and maths is at the basis of \gls{ml}.
+Nonetheless, statistics and maths is at the very basis of \gls{ml}.
 
@@
 At the moment it's hard to imagine a computer getting a higher ratio than a human
-but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the future.
+but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future; especially with ChatGPT's convincingly human-like answers\cite{dis2023chatgpt}.
 
-But fear not, that doesn't mean that computers are sentient or more intelligent than humans\cite{searle1980,searle1999married} even though some claim\cite{tiku2022google} and it certainly does not mean that research is over.
+But fear not, that doesn't mean that computers are 
+more intelligent than humans
+or \linebreak[4]
+sentient\cite{searle1980,searle1999married} even though some claim\cite{tiku2022google} and it certainly does not mean that research is over. 
 AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
@@
 Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and are useful in quantum mechanics too\cite{westermayr2020combining}.
-Other common architectures include linear regression, kernel ridge regression and support vector regression.
+Other common methods include linear regression, kernel ridge regression and support vector regression.
 

### 2023-03-05 Thesis/chapter/033-linreg-krr-svm.tex
proof read until KRR

@@
 \end{equation}
-Where $\mathbf{y}$ (size $\mathbb{R}^n$, where $n$ is the number of data points) is a vector of dependent variables which shall be predicted and $\mathbf{X}$ (size $\mathbb{R}^{n\times d}$, where $d$ is the the number of independent variables) is a matrix of independent variables.
-The parameters $\mathbf{k}$ (size $\mathbb{R}^d$) and $c$ (size $\mathbb{R}$) are chosen by minimizing an objective function (loss function in \gls{ml} chargon).
+Where $\mathbf{y} \in \mathbb{R}^n$ ($n$ is the number of data points) is a vector of dependent variables which shall be predicted and $\mathbf{X}\in \mathbb{R}^{n\times d}$ ($d$ is the the number of independent variables) is a matrix of independent variables.
+The parameters $\mathbf{k} \in \mathbb{R}^d$ and $c \in \mathbb{R}$ are chosen by minimizing an objective function (loss function in \gls{ml} chargon).
 A typical function to minimize are the $L_1$ and $L_2$ error, i.e. \gls{mae} and \gls{mse}, respectively.
@@
 
-\textbf{Ridge Regression} is like linear regression but with an extra term which penalizes steep regression functions.
-This extra term which reduces overfitting is scaled by a correction parameter~$\alpha$. 
+\textbf{Ridge Regression} is like linear regression with an extra term which penalizes steep regression functions.
+The extra term reduces overfitting and is scaled by a correction parameter~$\alpha$. 
 The larger $\alpha$ is, the larger is the regularisation and the flatter is the regression functions. 
@@
 \begin{equation}
-    L_{RR} = L_2 + \alpha \sum k_i = \sum(y_i - \hat y_i)^2 + \alpha \sum k_i
+    L_{RR} = L_2 + \alpha \sum |k_i| = \sum(y_i - \hat y_i)^2 + \alpha \sum |k_i| 
 \end{equation}
@@
 A~kernel transforms data in such a way that a linear hyperplane (a point in one dimension, a line in two dimensions, 
-a plane in three dimensions) can fit data in regression problems or seperate the data in classification problems without actually doing the transormation for every data point. 
+a plane in three dimensions) can fit data in regression problems or seperate the data in classification problems without actually doing the transormation for every data point, which lowers computational costs.
 A kernel is some kind of similarity measure 
 which fulfills the requirements of nonnegativity, symmetry and linearity\cite{rupp2015machine}.
+%\enlargethispage{\baselineskip}
+%\looseness=-1
 The following equations show definitions for 
-linear (eq.~\ref{eq:lin-kernel}), 
+linear~(eq.~\ref{eq:lin-kernel}), 
 polynomial (eq.~\ref{eq:pol-kernel}), 
 sigmoidal (eq.~\ref{eq:sig-kernel}) and 
-radial basis functionial kernel~(eq. \ref{eq:rbf-kernel}), with $\gamma$ as fixed hyperparameter and $c_0$ as parameter to optimize.
+radial basis functionial kernel~(eq.~\ref{eq:rbf-kernel}), with $\gamma$ as fixed hyperparameter and $c_0$ as parameter to optimize.
+A requirement for using kernels is having a dot product in the loss function. 
+This can be accomplished by expressing $\mathbf{k}$ in terms of $\mathbf{X}$: $\mathbf{k}=\mathbf{X}^\top \mathbf{r}$
+\cite{rudin2020least}.
+
 \begin{align}
@@
 \end{align}
-A requirement for using kernels is having a dot product in the loss function. 
-This can be accomplished by expressing $\mathbf{k}$ in terms of $\mathbf{X}$: $\mathbf{k}=\mathbf{X}^\top \mathbf{r}$
-\cite{rudin2020least}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%% { Support vector machines } SVM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textbf{\Gls{svm}} is a versatile machine learning algorithm first mentioned in 1992\cite{boser1992training} . 
+\textbf{\Gls{svm}} is a versatile machine learning algorithm first mentioned in 1992\cite{boser1992training}. 
 %
-The \gls{svm} was initially developed by V. Vapnik for the binary classification of seperable data, then improved to handle non-sperable data and eventually adapted to solve regression problems.
+The \gls{svm} was initially developed by V. Vapnik for the binary classification of seperable data, then improved to handle non-separable data and eventually adapted to solve regression problems.
 The concepts of \gls{svm} will be discussed in the same chronological order. 

### 2023-03-05 Thesis/chapter/060-results-material.tex
change from article to report
formatting
proof read until KRR

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Material Scientific and Pre-optimization}
+\section{Material Scientific and Pre-optimization}
 \label{sec:res-mat}
-%\subsubsection{Solution}
+%\subsection{Solution}
 %%%%%%%% AQUATIC 
@@
 \end{figure}
+\enlargethispage{-\baselineskip}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{XRD}
+\subsection{XRD}
 \begin{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Spectrometry}
+\subsection{Spectrometry}
 
@@
 %The trend is not monotonic due to inhomogenities in the sample???b
-The thicker, the layer is the more wavy the graph, which can be attributed to interference.
+The thicker, the layer is the more wavy the graph, which can be attributed to interference\cite{Dumin1967}.
 This trend can also be observed in figure \ref{fig:ir-gr}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Current Voltage Curves} 
+\subsection{Current Voltage Curves} 
 \begin{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Preoptimization}
+\subsection{Preoptimization}
 Before the optimization with the \gls{emma} algorithm, 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsubsection{SEM}
+%\subsection{SEM}
 

### 2023-03-06 Thesis/chapter/01-introduction.tex
proof read experimental

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\Gls{pv} is one viable option when becoming carbon neutral. 
+Photovoltaics (PV) is one viable option when becoming carbon neutral. 
 Furthermore, 
@@
 %
-One sort of \gls{pv} are \gls{cigs}\cite{Vasekar2010} cells. 
+One sort of PV are CIGS (copper indium gallium sulfide) cells\cite{Vasekar2010}. 
 Due to their large absorption coefficient, less material is needed and they can be made thinner and flexible. 
@@
 An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
-An insulating layer must therefore be applied to the steel substrate before any \gls{cigs} cells can be synthesised on top.
+An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be synthesised on top.
 Polymere would be a obvious choice if not for its low melting point which makes high prodction temperatures inpractical.
-A non-toxic material which is suitable for the insulation is \gls{zro}. 
-An economic and scalable method is doctor blading via a \gls{sg} process. 
-\gls{sg} processes often produce porous layers. 
+A non-toxic material which is suitable for the insulation is \ch{ZrO2}. 
+An economic and scalable method is doctor blading via a sol-gel process. 
+Sol-gel processes often produce porous layers. 
 In this work a dense, insulating and homogeneous layer is pursued. 
-\Gls{ml} can help to uncover complex non-linear relations, such as the 
+Machine learning can help to uncover complex non-linear relations, such as the 
 dependence of the thickness and resistance of the resulting layer on production factors.
@@
 \ref{sec:theoretical} giving 
-some background information on topics of \gls{pv}, material science and computational science which were used in this work.
+some background information on topics of PV, material science and computational science which were used in this work.
 In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
-Section \ref{sec:results} is split into three sections: material specific results are presented in section \ref{sec:res-mat}, results regarding \gls{pso} in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
+Section \ref{sec:results} is split into three sections: material specific results are presented in section \ref{sec:res-mat}, results regarding particle swarm optimisation in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
 Finally, chapter \ref{sec:outlook} summarizes and discusses the outlook and next steps.

### 2023-03-06 Thesis/chapter/031-theory-calculations.tex
proof read experimental

@@
 
-There are also lesser know algorithms like 
+There are also lesser know \gls{ml} algorithms like 
 evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
-\gls{pso} algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simultaneously\cite{villanova2010function}.
+Evolutionary algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simultaneously\cite{villanova2010function}.
 %
-One advantage of evolutionary algorithms is that they start with a small data set
+%One advantage 
+One particular feature of evolutionary algorithms is that they start with a small data set
 and periodically request new data in order to solve the problem iteratively.
@@
 \subsection{EMMA}
-\Gls{emma} is an implementation of the \gls{pso} in the \texttt{R} programming language. 
+\Gls{emma} is an implementation of \gls{pso} in the \texttt{R} programming language. 
 Each time step the dependent variables for all possible input variable combinations %$\mathbf{x} = \{x_1,\cdots ,x_N\}$ 
@@
 %
-The main advancements of \gls{mars} are the ability to fit (possibly complex) interactions and non-linearities without losing interpretability. 
+The main advancements of \gls{mars} is the ability to fit (possibly complex) interactions and non-linearities without losing interpretability. 
 %
@@
 This means that only two basis functions can be multiplied (excluding the constant term) to form a subsequent term.
-Pairwise added hinge functions are of the simple form $h(x-c)$ and $h(c-x)$ where $h(a)= max(0,a)$ and with $x$ being an independent variable, $c$ being a constant and $a$ being any expression. 
+Pairwise added hinge functions are of the simple form $h(x-c)$ and $h(c-x)$ where $h(e)= max(0,e)$ and with $x$ being an independent variable, $c$ being a constant and $e$ being any expression. 
 %%% BACKWARD EMMA
@@
 %
-In two cases a deliberate \gls{doe} is beneficial.
-If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
-If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.
+In two cases a deliberate \gls{doe} is especially beneficial.
+(1) If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
+(2) If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.
 %Both encompass nearly all cases. 
@@
 The Latin hypercube \gls{doe}\cite{viana2016tutorial,diwekar1997efficient} is a type of orthogonal \gls{doe}, 
-which has the advantage that each level for each variable will be tested only once. 
+which has the feature that each level for each variable will be tested only once. 
 A Latin hypercube \gls{doe} can be also created such that data points distribute more uniformly over the search space. 

### 2023-03-06 Thesis/chapter/033-linreg-krr-svm.tex
proof read experimental

@@
 A~kernel transforms data in such a way that a linear hyperplane (a point in one dimension, a line in two dimensions, 
-a plane in three dimensions) can fit data in regression problems or seperate the data in classification problems without actually doing the transormation for every data point, which lowers computational costs.
+a plane in three dimensions) can fit data in regression problems or separate the data in classification problems without actually doing the transormation for every data point, which lowers computational costs.
 A kernel is some kind of similarity measure 
@@
 %
-The \gls{svm} was initially developed by V. Vapnik for the binary classification of seperable data, then improved to handle non-separable data and eventually adapted to solve regression problems.
+The \gls{svm} was initially developed by Vladimir Vapnik for the binary classification of separable data, then improved to handle non-separable data and eventually adapted to solve regression problems.
 The concepts of \gls{svm} will be discussed in the same chronological order. 
@@
 on opposite sides of the decision boundary onto the unit vector perpendicular to the hyperplane. 
-If we now take a vector from a positive support vector $\mathbf{x}^+$ to a negative support vector $\mathbf{x}^-$ and project it on to the unit vector of $\mathbf{w}$ (which is perpendicular to the hyperplane),
+If we now take a vector from a positive support vector $\mathbf{x}^+$ to a negative support vector $\mathbf{x}^-$ and project it onto the unit vector of $\mathbf{w}$ (which is perpendicular to the hyperplane),
 we get the width of the margin. 
@@
 %%%%%%%%%% SOFT MARGIN SVM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textbf{Soft margin \gls{svm}} - in contrast to hard margin \gls{svm} is used if the data is non-seperable due to outliers\cite{cortes1995support}.
-Such data can be handeled by introducting a penalization term for wrongly categorized samples into the loss function. 
+\textbf{Soft margin \gls{svm}} -- in contrast to hard margin \gls{svm} -- is used if the data is non-separable due to outliers\cite{cortes1995support}.
+Such data can be handeled by introducing a penalization term for wrongly categorized samples into the loss function. 
 \begin{equation}
 	\label{eq:svm-soft}
-	L_{SM} = \frac{2} {\|\mathbf{w}\|} + \sum_i^n max(0, 1- y_i ( \mathbf{w} \mathbf{x}_i + b ) 
+	L_{SM} = \frac{1}{2} \|\mathbf{w}\|^2 + \sum_i^n max(0, 1- y_i ( \mathbf{w} \mathbf{x}_i + b ) 
 \end{equation}
@@
 The substraction of a negative number will result in a positive penalizisation. 
-If the sample iis correctly predicted, the product will result in a positive number, 
-the substraction in a negative number and the maximum will be 0, if the sample is ousite of the margin.
-
+If the sample is correctly predicted, the product will result in a positive number, 
+the substraction will lead to a negative number and the maximum will be 0, if the sample is ousite of the margin. 
+%
 %%%%%%%%%%% KERNELS IN SVM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %As mentioned before, a inner product is need to use the kernel trick. 
-The function we want to optimize (see eq. \ref{eq:svm04}) and its soft margin equivalent can both be expressed as inner products. 
-This allows us to seperate data not only with hyperplanes 
-but also with komplex decision boundaries due to the kernel trick. 
+The function we want to optimize (eq.~\ref{eq:svm04}) and its soft margin equivalent (eq.~\ref{eq:svm-soft}) can both be expressed as inner products. 
+This allows us to separate data not only by hyperplanes 
+but also by complex decision boundaries due to the kernel trick. 
 Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the innerproduct of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper.
@@
 
-\Gls{svm}s can also be used for regression.
+\Gls{svm}s can also be used for regression (support vector regression).
 The decision function becomes the regression function and the margin includes all data points instead of none. 
-In a soft margin \gls{svm} a few data point can lie outside the margin as outliers. 
+In soft margin support vector regression a few
+outliers are allowed.
+%data point can lie outside the margin as outliers. 
 Non-linearity can be likewise introduced via the kernel trick. 

### 2023-03-06 Thesis/chapter/04-experimental.tex
proof read experimental

@@
 \section{Substrate Preparation}
+%\ds{
 Five different substrates were used throughout this work: 
@@
 \gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
+%}
+\ds{
+Four different substrates were used throughout this work: 
+microscope glass slides, \gls{ito} glass plates, \gls{fto} glass plates and steel foil provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
+}
 %
@@
 All recipes for solutions can be divided into two categories:
-the first recipe - adopted from Anwar et. al. \cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water}.
-The second recipe - adopted from Hu et. al. \cite{Hu2016} - was based on \gls{zrpro} in \gls{buoh}.
+the first recipe - adopted from Anwar~et~al.~\cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} (aquatic solution).
+The second recipe - adopted from Hu~et~al.~\cite{Hu2016} - was based on \gls{zrpro} in \gls{buoh} (buthanolic solution).
 
@@
 Five different concentrations of the buthanolic solutions were prepared. 
-The \gls{1f} was closest to the recipe proposed by Hu et. al. \cite{Hu2016}. 
+The \gls{1f} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
 The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar with 
@@
 with the aim of producing thicker layers.
-Not all chemicals mentioned in \cite{Hu2016} were available, so chemically similar 
+Not all chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
 starting materials had to be chosen from the available inventory. 
@@
 Lower \gls{db} velocities resulted in less homogeneous layers.
-Thus, the \gls{db} wasn't altered in the manual \gls{db} process. 
+Thus, the \gls{db} velocity was not altered in the manual \gls{db} process. 
 One and two layers of adhesive tape were used to alter the depth of the valley.
@@
 figure~\ref{fig:eric}). 
-Most of them were covered with tape to increase the suction at the remaining ones. 
+Most of them were covered with tape to increase the suction intensity at the remaining ones. 
 After setting the temperature of the heating plate to 
-\SI{200}{\celsius}, the vacuum plate temperature (room temperature, \SI{40}{\celsius}, 
+\SI{200}{\celsius}, the temperature of the vacuum plate (room temperature, \SI{40}{\celsius}, 
 \SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) and the 
 \gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
-the blade was put into its original position, the sample was placed on the vacuum plate and the vacuum 
+the blade was put into its initial position, the sample was placed on the vacuum plate and the vacuum 
 was switched on. 
@@
 		\label{tab:labtech}
-		\begin{tabular}{rl ll ll ll ll ll ll }%ll ll ll ll ll ll ll}
+%		\begin{tabular}{rl ll ll ll ll ll ll }%ll ll ll ll ll ll ll}
+		\begin{tabular}{cc cc cc cc cc cc cc }%ll ll ll ll ll ll ll}
 			\hline
@@
 			T [\oc{}]	    &80		&100	&150	&160	&170 	&180	&190	&200	&250	&300	&350	&400	\\
+			\hline
 			t [\minutes{}]	&10 	&10		&5 		&5 		&5 		&5 &5 &10 &10 &10 &10 &60 \\
@@
 		\resizebox{\textwidth}{!}{
-		\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
+%		\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
+		\begin{tabular}{cc cc cc}% ll ll ll ll }%ll ll ll ll ll ll ll}
 			\hline\hline
@@
 NT5 additionally used a calcination temperature T$_{\textrm{Cal}}$ of \SI{500}{\celsius}.
-NT2-NT6 had 2 variables (heating rate and calcination temperature) in contrast to 
+NT2-NT6 had 2 variables (heating rate and one calcination temperature) in contrast to 
 NT1 which had 4 (three different heating rates and calcination temperature). 
@@
 spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
-Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter} - \SI{588}
+Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588}
 % gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
-{\nano\meter}) and a Silicon detector for visual and \gls{ir} light 
-(\SI{500}{\nano\meter} - \SI{1.2}{\micro\meter}). For transmittance the light
-entered the sample from the side with the layer. The UV and VIS+IR spectra were merged 
+{\nano\meter}) and a Silicon detector for visual and \gls{nir} light 
+(\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). For transmittance the light
+entered the sample from the side with the layer. The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged 
 in Opus software. % included in the spectrometer. 
@@
 Between sputtering and \gls{iv} measurements 
-direct contacts to the steel substrate were created by removing a patch the \gls{zro}
+direct contacts to the steel substrate were created by removing a patch of the \gls{zro}
 layer with 
@@
 Thus, 
-the buthanolic recipe was introduced, which gave rise to more homogeneous films.
+the buthanolic recipe was introduced, which gave rise to homogeneous films.
 After the blade moved over the substrate the remaining liquid needed about a minute 
@@
 			\hline
-			\\
+			\\ \\  \\
 %			\multicolumn{6}{c}{*different stabilisation reagent compositions}\\

### 2023-03-07 Thesis/chapter/05-computational-details.tex
change from article to report
formatting
proof read experimental
start EMMA

@@
-\subsection{Data Processing}
+\section{Data Processing}
 \label{sec:eval}
@@
 %\td{describe problem and solution found}
-For every sample multiple \gls{iv} curves were measured. 
-The main difficulty faced in processing the data was to present the measurements obtain 
+Multiple \gls{iv} curves were measured for every sample.
+The main difficulty faced in processing the data was to present the measurements obtained 
 from a sample in one representative number. 
@@
 %
-For every I-V curve (aluminium dot) the gradient $g$ at $V=0$ is calculated by taking 
-each 5 points before and after the origin with at least 2 points distance (which boils
+For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
+5 points before and 5 points after the origin with at one point distance from zero (which boils
 down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
-calculating averages of each point cloud $\overline{V}$ and $\overline{I}$ and taking the ratio of differences 
+calculating averages $\overline{V}$ and $\overline{I}$ of each point cloud and taking the ratio of differences:
 %averaging their V and I values and calculating
@@
     %g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
-    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}.
+    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}
 \end{equation}
@@
 %
-In order to make the metric closer and better comparable to the \gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
-to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms. 
+In order to make the metric closer 
+%and better comparable to the 
+\gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
+to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conducticity hereafter for lack of a better term. 
 %As a measure of conductance a distance $D$ from an ideal non-conducting case. 
@@
 \end{equation}
-Another measure is the density of shorted species $\rho$, calculated in following way:
+Another measure is the density of shorted species $\rho$ (pin hole density), calculated in following way:
 \begin{equation}
@@
 
-\subsection{Sample Selection}
+\section{Sample Selection}
 \label{sec:ss}
@@
 	\begin{tabular}{cc cc cc}
-		\hline
+		\hline\hline
         $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$\lambda$	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
@@
 						&		&					&20				&					&		\\
-		\hline
+		\hline\hline
 	\end{tabular}
@@
 The experiments are executed, measured and evaluated according to section 
-\ref{sec:exp} and the responses $\gamma$ (see eq. \ref{eq:gamma}), $\rho_s$ (see eq. \ref{eq:rho}), 
-$n_{layers}$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in 
+\ref{sec:exp} and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pin hole density $\rho_s$ (see eq. \ref{eq:rho}), 
+$\lambda$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in 
 \oc{}/\minutes{}) are supplied to the program. 
 The program, then, uses this data to estimate a response for each output variable 
-for the entire population space.
+for the entire population space
 (and to choose a fraction of the initial population which is allowed to propagate).
@@
 The current population - each of the particles independently - 
-have random velocity vector associated to them which is directed to the best predicted sample. 
+are given a random velocity vector associated to them which is directed to the best predicted sample. 
 %moves towards the optimum solution.
@@
 
-\subsection{Fitting via Machine Learning}
+\section{Fitting via Machine Learning}
 %\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
-Python 3.10.9 and sci-kit learn 1.1.2\cite{pedregosa2011scikit} were used to implement a linear fit model, \gls{krr} and \gls{svm} with the kernels polynomial, \gls{rbf} and sigmoid. 
-%\subsubsection{Grid Search}
-A grid search over a set of hyper parameters was executed. 
+Python 3.10.9 and sci-kit learn 1.1.2\cite{pedregosa2011scikit} were used to implement a linear fit model, \gls{krr} and \gls{svm} with polynomial, \gls{rbf} and sigmoid kernels. 
+%\subsection{Grid Search}
+A grid search over a set of hyperparameters was executed. 
 %https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
@@
 % KRR 
-The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
-The kernel took the form of \gls{rbf}, sigmoid and polynomial with degree 1--4.
+The hyperparameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
+The kernel took the form of \gls{rbf}, sigmoid or polynomial with degree 1--3.
 The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
@@
 Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$, 
-where $C$ took the values 0.05--0.95 with 0.05 steps, $\varepsilon$ 0.02--3.8 with 0.2 steps 
+where $C$ took the values 0.05--0.95 with step size 0.05, $\varepsilon$ 0.02--3.8 with 0.2 steps 
 and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 

### 2023-03-07 Thesis/chapter/060-results-material.tex
start EMMA

@@
 Starting with physical measurements and material properties. 
-Followed by the presentation and exploration of the results obtain by optimisation/exploration  with the \gls{emma} method. 
+Followed by the presentation of the results obtain by optimisation and exploration with the \gls{emma} method. 
 Finally, the results of alternative optimisation methods were let loose on the data and compared with the \gls{emma} method.
@@
 As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.\cite{Anwar2017} failed to produce a homogeneous layer. 
-The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure \ref{fig:sem-old}). 
+The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
 Altering the ratios of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't improve the resulting \gls{zro} layers. 
@@
 %
-Figure \ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
-%These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
+Figure~\ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
+%These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aquatic recipe. 
 Large cracks, non coated areas and inhomogeneity were 
@@
 		(b) 10 layers of \gls{zro} on steel substrate
-		(c) cross section of crack of 5 layers of \gls{zro} on fto 
+		(c) cross section of crack of 5 layers of \gls{zro} on \gls{fto}
 		(d) side view of scratched \gls{zro} on steel substrate
@@
 
-The sol-gel recipe optimized by Hu et al.\cite{Hu2016} for \ch{Al2O3} worked splendidly for our use case even after (not so) minor changes (see section \ref{sec:exp-sol-bu}). 
+The sol-gel recipe optimized by Hu et al.\cite{Hu2016} for \ch{Al2O3} worked splendidly for our use case even after (not so) minor changes (see section~\ref{sec:exp-sol-bu}). 
 %
-Figure \ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
+Figure~\ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
 %%%% PIN HOLES
-The large irregularity on the bottom left could depict a pin hole, a (tiny) hole that reaches to the substrate. 
+The large irregularity on the bottom left could depict a pin hole, a (tiny) hole in the layer that reaches to the substrate. 
 These irregularities are rather the exception. 
@@
 It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness 
-the addition 50\% of the volume in \gls{ipo} can even reversed the aging effect for a respectable amount of time. 
+the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
 This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
@@
 %%%%%%%%% CROSS SECTION
-Figure \ref{fig:sem-cs1} shows the cross section of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
+Figure~\ref{fig:sem-cs1} shows the cross section of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
 The large crystalline structure which makes up most of the upper part of the image is \gls{fto}. 
@@
 %
-The result can be seen in figure \ref{fig:sem-cs2}. 
+The result can be seen in figure~\ref{fig:sem-cs2}. 
 5 layers of double concentrated solution were applied to this sample. 
 Assuming that the raised structure resembling a tentacle is \gls{zro}, 
-the thickness of the layer can be estimated to be in the magnitude of \um{1}.
+the thickness of the layer can be estimated to be in the magnitude of several \nm{100}.
 
@@
 \Gls{xrd} was used in order to confirm that the produced layer is indeed \gls{zro}. 
-Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate (steel) and 
-the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix \ref{sec:app-emma}).
+Figure~\ref{fig:xrd} shows \gls{xrd} spectra of the substrate (steel) and 
+the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix~\ref{sec:app-emma}).
 In addition, two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
@@
 They confirm that the produced substance is \gls{zro}.
-To further clarify the phase Raman spectra are needed since cubic and tetragonal phases are difficult to distinguish from \gls{xrd} alone\cite{Purohit2006Combustion}.
+Raman spectra are needed 
+to further clarify the phase, 
+since cubic and tetragonal phases are difficult to distinguish from \gls{xrd} alone\cite{Purohit2006Combustion}.
 
@@
 
-In figure \ref{fig:ir-gt} transmission spectra of \gls{uv}/\gls{vis}/\gls{nir} light can be seen. 
+In figure~\ref{fig:ir-gt} transmission spectra of \gls{uv}/\gls{vis}/\gls{nir} light can be seen. 
 Each sample had different numbers of layers. 
@@
 %The trend is not monotonic due to inhomogenities in the sample???b
-The thicker, the layer is the more wavy the graph, which can be attributed to interference\cite{Dumin1967}.
-This trend can also be observed in figure \ref{fig:ir-gr}.
-The weak interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film}. 
+The thicker the layer is, the more wavy the graph, which can be attributed to interference\cite{Dumin1967}.
+This trend can also be observed in figure~\ref{fig:ir-gr}.
+The weak interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film} -- agreeing with \gls{sem} measurements.
 %
-Figure \ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 degrees. 
+Figure~\ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 degrees. 
 %The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
@@
 
-%Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
-%Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
-Figure \ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
-Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
+%Figures~\ref{fig:iv-log-good} and~\ref{fig:iv-stat-good} are measurements from a good sample. 
+%Figure~\ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
+Figure~\ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
+Each line represents a I-V measurement at a distinct aluminium contact applied by sputtering through a mask. 
 All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
-and quite a few show hardly any current which is the ideal. 
-An example for very low conductance measurement in non-logarithmic scale can be seen in figure \ref{fig:iv-nocurrent}.
-For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}). 
-Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample depicted in \ref{fig:iv-log-good}.
+and around a fifth exhibit hardly any current which is ideal (see figure~\ref{fig:iv-stat-good}).
+A single example for a very low conductance measurement in non-logarithmic scale can be seen in figure~\ref{fig:iv-nocurrent}.
+The conductance (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}) for each measurement.
+Figure~\ref{fig:iv-stat-good} shows the distribution of gradients $g$ for the same sample as depicted in \ref{fig:iv-log-good}.
 %
-Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
+Figures~\ref{fig:iv-log-okay} and~\ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
 Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
@@
 %
-In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of some curves 
+In figures~\ref{fig:iv-log-good} and~\ref{fig:iv-log-okay} the minimum of some curves 
 is not at \SI{0}{\volt}, which means that the function does not cross the origin in non-logarithmic representation. 
 %
-This deviation (see figure \ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar} because of its non-zero current at $V=0$.
+This deviation (see figure~\ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar} because of its non-zero current at $V=0$.
 %, but was not investigated further. 
@@
 %
-Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample 
+Finally, figures~\ref{fig:iv-log-bad} and~\ref{fig:iv-stat-bad} show a sample 
 where all measurement exhibit relatively high voltages and high calculated conductances. 
 This indicates a overall bad condition of the \gls{zro} layer for insulating. 
-Figure \ref{fig:iv-ohmic} shows a graph circa following Ohm's law. 
+Figure~\ref{fig:iv-ohmic} shows a \gls{iv} curve which can be approximated by Ohm's law. 
 %
@@
 The reason is that the force exerted by the blade on the liquid is not strong enough to overcome surface tension. 
-This means that behind the blade a meniscus would pull the liquid without leaving behind any for the gelling process. 
+This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
 Additionally, the temperature while \gls{db} $T_{DB}$ affects the evaporation process together with the \gls{db} velocity $v_{DB}$.

### 2023-03-07 Thesis/chapter/061-results-emma.tex
start EMMA

@@
 	\centering
-	\caption{Global best per generation with experiment numbers and dependent variables/experiment conditions \td{include units?}}
+	\caption{Global best per generation with experiment numbers and experiment conditions}% \td{include units?}}
 	\label{tab:emma-Gb}
@@
 %
-In table \ref{tab:emma-pred-G} it can be seen that the predicted $\hat{\gamma}$ 
+In table \ref{tab:emma-pred-G} it can be seen that the predicted conducticity $\hat{\gamma}$ 
 (predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
@@
 %
-Contrarily, the predicted $\hat{\gamma}$ for each generation's best 
+Contrarily, the predicted conducticity $\hat{\gamma}$ for each generation's best 
 (predicted by the very generation's \gls{rf}) does increase with each iteration 
@@
 The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
-Indeed, the samples with the lowest \textit{optimisands} are among the first generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).
+Indeed, the samples with the lowest \textit{optimisands} are among the initial generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).
 
 In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimisands}, 
-$\gamma$ and $\rho$, of each particle at each generation.
-They points at generation indicate particles which were not included to be propagated. 
-Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
+conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
+The points at generation indicate particles which were not included to be propagated. 
+%Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
+Violet lines connect individual particles, the blue line connects averages of particles of each generation and yellow lines connect average of only particles which were propagated. 
 %
@@
 Neither expected were the measurements for these samples, which might be due to the high measuring error of samples and variation of quality due to uncontrolled independent variables like room temperature or humidity.
+Measurements were expected to show clear correlation, which was only observed for $T_{cal}$.
+%\td{why}
 %
-Figures \ref{fig:g-tcal} and \ref{fig:phd-tcal} the correlation of calcination temperature $T_{cal}$ and $\gamma$ and $\rho$ can be seen clearly.
+In the scatter plots~\ref{fig:g-tcal} and \ref{fig:phd-tcal} the correlation of calcination temperature $T_{cal}$ with $\gamma$ and $\rho$ can be seen clearly.
 
@@
 %\subsection{Equation}
-Equations (\ref{eq:emma-phd3})-(\ref{eq:emma-vcal3}) and (\ref{eq:emma-phd4})-(\ref{eq:emma-vcal4}) represent the \gls{rf}s at $t=3$ and $t=4$, respsectively, rounded to 2 significant digits.
+Equations (\ref{eq:emma-phd3})-(\ref{eq:emma-vcal3}) and (\ref{eq:emma-phd4})-(\ref{eq:emma-vcal4}) represent the regression functions at $t=3$ and $t=4$, respsectively, rounded to 2 significant digits.
 %$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
@@
 %This means that the algorithm must decide on the variables which explain the most variance independent of optimization weights.
-This stems from the fact that the algorithm choses a single minimal set of \gls{bf} to predict all dependent variables. 
+This stems from the fact that the algorithm choses a single minimal set of basis functions to predict all dependent variables. 
 %
@@
 The coefficients in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) have the same signs and differ by a factor of roughly 100.
-This fits the data well (see appendix \ref{sec:app-emma}), but the positive influence of the layer count $\lambda$ is counter intuitive 
-as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
+This fits the data well (see appendix \ref{sec:app-emma}). %, but the positive influence of the layer count $\lambda$ is counter intuitive 
+%as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
 The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) 
-seem low, but - considering the minimum value of the interaction of \num{36000} - have a higher influence on $\rho_3$ and $\gamma_3$ than the $h(6-\lambda)$ term. 
+seem low, but the interaction has -- considering the minimum value of the interaction of $300 \cdot 120 =$  \num{36000} -- several orders of magnitude higher influence on $\rho_3$ and $\gamma_3$ than the $h(6-\lambda)$ term.
 %It's positive the hinge
-It is astonishing that the knot of the hinge function for equations (\ref{eq:emma-phd3})-(\ref{eq:emma-vcal3}) was chosen so low; 
-basically only including the influence of $\lambda=4$.
-Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) that the lowest layer count produces worse samples which is intuitive, but more than 6 layers don't improve the insulation. 
+It is astonishing that the knot of the hinge function for equations (\ref{eq:emma-phd3})--(\ref{eq:emma-vcal3}) was chosen so low; 
+basically only including the influence of the lowest layer count $\lambda=4$.
+Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}), that the lowest layer count produces worse samples which is intuitive, but more than 6 layers don't improve the insulation. 
 On the positive side, the calcination heating rate $v_{cal}$ (see equation (\ref{eq:emma-vcal3})) has been predicted perfectly within numerical precision.
@@
 as equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}): identical signs and factor 100. 
-The choice of \gls{bf}s in combination with their coefficient signs seems more plausibel
+The choice of basis functions in combination with their coefficient signs seems more plausibel
 for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
-$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally the lowest $\lambda$ increases the two \textit{optimisands}. 
+$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $\lambda$ increases the two \textit{optimisands}. 
 % TCAL ON OPTIMIZANDS
@@
 \textit{Optimsands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
-according to equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}, 
+according to equations~(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) (see also figures~\ref{fig:g-tcal} and \ref{fig:phd-tcal}), 
 ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.
 % DESCRIBE COEFFEICIENTS
-Furthermore, the influence of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$ and also on $\hat\lambda$ and $\hat{v}_{cal}$.
+Furthermore, the influence of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$; interestingly also on $\hat\lambda$ and $\hat{v}_{cal}$.
 The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 
-but has the extra factor $\lambda$ of up to 12, resulting in the products of coefficients and independent variable being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$.
-It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient. 
+but has the extra factor $\lambda$ (range: 4--12), resulting in the products of coefficients and independent variable being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$.
+It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}). 
 This negative correlation could hint a compensation of the overestimated influence of $T_{cal}$ on the \textit{optimisands}.
@@
 %with $T_{cal}$ and $T_{DB}$. 
-From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_DB$ and then the rest of the independent variables. 
+From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_{DB}$ and then the rest of the independent variables. 
 I highly doubt though that the specific interactions proposed by EMMA are indeed meaningful.
@@
 from the optimisation were used which were available at the time of prediction. 
-That means 15 samples for $t=1$ and 30 sampes for $t=4$ were used to calculate respective \gls{mse}s. 
-The \gls{mse} is 64, 158, 54 and 50 for $t=1,2,3,4$, respectively. 
-It is interesting that although prediction functions for $t=3$ perfectly predicted $v_{cal}$ 
-the combined \gls{mse} for $t=4$ is lower. 
+That means 15, 20, 25 and 30 samples 
+%for $t=0$, 15 samples for $t=1$ and 30 sampes for $t=4$ 
+were used to calculate \gls{mse}s at $t=1,2,3,4$, respectively (compare with table~\ref{tab:emma-Gb}).
+The \gls{mse}s are 64, 158, 54 and 50 for $t=1,2,3,4$, respectively. 
+It is interesting that although prediction functions for $t=3$ predicted $v_{cal}$ perfectly, the combined \gls{mse} for $t=4$ is lower. 
 The high \gls{mse} at $t=2$ can be explained by the prediction functions being only constant values. 
@@
 of the \gls{mars} algorithm in principle works on investigated samples. 
-
+%
 %\td{It should be noted, that the validation \gls{mse} for $t=1$ is much higher.}
-The high validation \gls{mse} (nearly 1.5 fold instead of circa 1 fold of \gls{mse}) 
-for $t=1$ shows the poor prediction ability at the beginning which improved with generations.
-This decrease in validation \gls{mse} supports the hypothesis stated at the beginning of this section: 
-the measure of conductance was underestimated and improved over time.
+When compraring the out-of-sample and in-sample \gls{mse}s it can be noted that at $t=1$ the out-of-sample \gls{mse} is close to 1.5 fold of in-sample and at $t=2$ vice versa.
+%The high validation \gls{mse} for $t=1$ (nearly 1.5 fold instead of circa 1 fold of \gls{mse}) 
+This shows the poor prediction ability at the beginning which improved with generations.
+This decrease in validation (out-of-sample) \gls{mse} supports the hypothesis stated at the beginning of this section: 
+the measure of conductance was underestimated and and the estimate improved over time.
 %\td{why is \gls{mse} higher with higher values? No homoscedasticity ( equality of variance)?
@@
 On the other side, the main problem about too many dependent variables specific to this optimisation procedure 
-is that the same set of \gls{bf}s will be used to predict \textbf{all} \textit{optimisands}.
+is that the same set of basis functions will be used to predict \textbf{all} \textit{optimisands}.
 This leads to competition between the \gls{bf}s, as not all dependent variables may depend on the same independent variables. 

### 2023-03-08 Thesis/chapter/061-results-emma.tex
proof read emma

@@
 %
-In table \ref{tab:emma-pred-G} it can be seen that the predicted conducticity $\hat{\gamma}$ 
+It can be seen in table~\ref{tab:emma-pred-G} 
+that the predicted conducticity $\hat{\gamma}$ 
 (predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
@@
 The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
+\linebreak[4]
 Indeed, the samples with the lowest \textit{optimisands} are among the initial generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).
@@
 conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
-The points at generation indicate particles which were not included to be propagated. 
+The points at generation number 0 indicate particles which were not included to be propagated. 
 %Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
-Violet lines connect individual particles, the blue line connects averages of particles of each generation and yellow lines connect average of only particles which were propagated. 
+Violet lines connect individual particles in time, the blue line connects averages of particles of each generation and yellow lines connect average of only particles which were propagated of each generation.
 %
-Both variables were to be minimized and show a clear trend towards low values with increasing generation, 
+Both $\gamma$ and $\rho$ were to be minimized and show a clear trend towards low values with increasing generation, 
 indicating that the optimization worked even though 
-the prediction functions (see equations (\ref{eq:emma-phd3}) - (\ref{eq:emma-vcal4})) 
+the prediction functions (see equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal4})) 
 and the chosen samples where not exactly as expected. 
-Neither expected were the measurements for these samples, which might be due to the high measuring error of samples and variation of quality due to uncontrolled independent variables like room temperature or humidity.
+Neither expected were the measurements for these samples, which might be due to the high measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature or humidity.
 Measurements were expected to show clear correlation, which was only observed for $T_{cal}$.
@@
 %\subsection{Equation}
-Equations (\ref{eq:emma-phd3})-(\ref{eq:emma-vcal3}) and (\ref{eq:emma-phd4})-(\ref{eq:emma-vcal4}) represent the regression functions at $t=3$ and $t=4$, respsectively, rounded to 2 significant digits.
+Equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal3}) and (\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) represent the regression functions at $t=3$ and $t=4$, respsectively, rounded to 2 significant digits.
 %$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
@@
 %    \label{eq:emma-phd1}
-%    \hat{\rho}_1 &= -26  + 0.0025 \cdot T_{DB}\cdot T{Cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{Cal} \\
+%    \hat{\rho}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{DB}\cdot T_{cal} + 0.00080 \cdot h(6-\lambda)\cdot T_{cal}\\
 %    \label{eq:emma-G1}
-%    \hat{\gamma}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{DB}\cdot T_{Cal} + 0.00080 \cdot h(6-layr)\cdot T_{cal}\\
+%    \hat{\gamma}_1 &= -26  + 0.0025 \cdot T_{DB}\cdot T{cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{cal} \\
 %    \label{eq:emma-layr1}
-%    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{DB}\cdot T_{cal} -  0.0056 \cdot  h(6-layr)\cdot T_{cal}\\
+%    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{DB}\cdot T_{cal} -  0.0056 \cdot  h(6-\lambda)\cdot T_{cal}\\
 %    \label{eq:emma-vcal1}
-%    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{DB}\cdot T_{cal} - 0.0055 \cdot  h(6-layr)\cdot T_{cal}\\
+%    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{DB}\cdot T_{cal} - 0.0055 \cdot  h(6-\lambda)\cdot T_{cal}\\
 %
 %    \label{eq:emma-phd2}
-%    \hat{\rho}_2 &= 47\\
+%    \hat{\rho}_2 &= 0.23\\
 %    \label{eq:emma-G2}
-%    \hat{\gamma}_2 &= 0.23\\
+%    \hat{\gamma}_2 &= 47\\
 %    \label{eq:emma-layr2}
@@
     \label{eq:emma-vcal3}
-    \hat{v}_{cal,3} &= -5.2\cdot 10^{-15}  +   0.016 \cdot  v_{Cal}  + 1.3\cdot 10^{-15} \cdot  h(6-\lambda)  + 3.9\cdot 10^{-21} \cdot  v_{Cal}\cdot T_{cal} \\
+    \hat{v}_{cal,3} &= -5.2\cdot 10^{-15}  +   0.016 \cdot  v_{cal}  + 1.3\cdot 10^{-15} \cdot  h(6-\lambda)  + 3.9\cdot 10^{-21} \cdot  v_{cal}\cdot T_{cal} \\
 %
@@
 The coefficients in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) have the same signs and differ by a factor of roughly 100.
-This fits the data well (see appendix \ref{sec:app-emma}). %, but the positive influence of the layer count $\lambda$ is counter intuitive 
+This fits the data well since the maxima of $\rho$ and $\gamma$ are separated by rough factor of 100 (see figure~\ref{fig:emma-gen} and appendix~\ref{sec:app-emma}).
+%, but the positive influence of the layer count $\lambda$ is counter intuitive
 %as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
@@
 Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}), that the lowest layer count produces worse samples which is intuitive, but more than 6 layers don't improve the insulation. 
-On the positive side, the calcination heating rate $v_{cal}$ (see equation (\ref{eq:emma-vcal3})) has been predicted perfectly within numerical precision.
+Encouragingly, the calcination heating rate $v_{cal}$ (see equation (\ref{eq:emma-vcal3})) has been predicted perfectly within numerical precision.
 
@@
 as equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}): identical signs and factor 100. 
-The choice of basis functions in combination with their coefficient signs seems more plausibel
-for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
-$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $\lambda$ increases the two \textit{optimisands}. 
+%The choice of basis functions in combination with their coefficient signs seems more plausible
+%for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
+%$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $\lambda$ increases the two \textit{optimisands}. 
+%LAMBDA 
 % TCAL ON OPTIMIZANDS
-The influence of $T_{cal}$ on the measures of conductance ($\rho$ and $\gamma$) is higly interesting. 
+The influence of $T_{cal}$ on the measures of conductance ($\rho$ and $\gamma$) is highly interesting. 
 It was expected that 
@@
 %\td{xxx}
-\textit{Optimsands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
+\textit{Optimisands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
 according to equations~(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) (see also figures~\ref{fig:g-tcal} and \ref{fig:phd-tcal}), 
 ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.
-% DESCRIBE COEFFEICIENTS
-Furthermore, the influence of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$; interestingly also on $\hat\lambda$ and $\hat{v}_{cal}$.
+% DESCRIBE COEFFICIENTS
+Furthermore, the coefficient of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$; interestingly also on $\hat\lambda$ and $\hat{v}_{cal}$.
 The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 
-but has the extra factor $\lambda$ (range: 4--12), resulting in the products of coefficients and independent variable being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$.
+but has the extra factor $\lambda$ (range: 4--12), resulting in the products of coefficients and process variables being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$.
 It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}). 
 This negative correlation could hint a compensation of the overestimated influence of $T_{cal}$ on the \textit{optimisands}.
+Similarly, signs of coefficients of $\lambda \cdot T_{cal}$ and $h(\lambda -6) \cdot T_{DB}$ correlate negatively in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) and the product of coefficients and input variables are again similar in order of magnitude.
 %It should be doubted, though, that the $layr$ only appears as interaction term 
@@
 %with $T_{cal}$ and $T_{DB}$. 
-From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_{DB}$ and then the rest of the independent variables. 
-I highly doubt though that the specific interactions proposed by EMMA are indeed meaningful.
+%From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_{DB}$ and then the rest of the independent variables. 
+The process variables $T_{cal}$ and $\lambda$ appear as \gls{bf}s in generation 3 and 4, whereas $v_{cal}$ only appears in generation 3's \gls{rf}s and $T_{DB}$ only in generation 4's \gls{rf}s.
+This can hint the importance of these variables in the process. 
+%I highly doubt though that the specific interactions proposed by EMMA are indeed meaningful.
 
@@
 Apart from the second generation the \gls{mse} decreases  over time, 
-which shows that the algorithm works. 
-This decrease in \gls{mse} might be attributed to overfitting, though. 
+which indicates that the algorithm works. 
+This decrease in \gls{mse} might be attributed to overfitting, though, since prediction and validation were performed on the same data. 
 %The \gls{mse} for each generation was also calculated between predicted values for pre-optimisation samples to check for overfitting, 
-The \gls{mse} for each generation's prediction function was also calculated with pre-optimisation samples, which are unseen data. 
+The \gls{mse} for each generation's prediction function was also calculated for pre-optimisation (out-of-sample) samples, which are unseen data. 
 The error sank again with each generation (except for the second generation): 102, 118, 58, 50, respectively for $t=1,2,3,4$. 
@@
 The decrease of \gls{mse} with out-of-sample data shows that the regularization method 
-of the \gls{mars} algorithm in principle works on investigated samples. 
+of the \gls{mars} algorithm in principle works on investigated samples and that decrease of \gls{mse} is not due to overfitting. 
 %
@@
 %The high validation \gls{mse} for $t=1$ (nearly 1.5 fold instead of circa 1 fold of \gls{mse}) 
-This shows the poor prediction ability at the beginning which improved with generations.
+This shows the poor prediction ability at the beginning of the optimisation which improved with generations.
 This decrease in validation (out-of-sample) \gls{mse} supports the hypothesis stated at the beginning of this section: 
-the measure of conductance was underestimated and and the estimate improved over time.
+the measure of conductance was underestimated and and the estimate improved over time (see table~\ref{tab:emma-pred-G}).
 %\td{why is \gls{mse} higher with higher values? No homoscedasticity ( equality of variance)?
@@
 Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
-Too many independent variables make it harder to distinguish variance due to random error (due to unmeasured and uncontrolled variables) from variance due to dependency.
-% of chosen dependent varibales.
+Too many independent variables make it harder to distinguish variance due to random error (e.g.
+unmeasured and uncontrolled variables) from variance due to dependency.
+% of chosen dependent variables.
 The difficulty of identifying meaningful correlation is mainly owed to the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
@@
 %(events per predictor variable EPV) are as low as 5. 
-The \gls{epv} (data points per independent varible) are as low as 5 in the here presented optimisation model. % and data acquisition method
+The \gls{epv} (data points per independent varible) are as low as 5 in the here presented optimisation. % model and data acquisition method
 By eliminating three independent variables the \gls{epv} could rise to 10, which is stated 
 as rule of thumb for mulitvariate regression\cite{vittinghoff2007relaxing}. 
-The results obtained with limited sample number deliver some insightfulness %are quite respectable. 
-considering an \gls{epv} of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
+The results obtained with limited sample number deliver remarkable insightfulness %are quite respectable. 
+comparing to an \gls{epv} of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
 and an \gls{epv} of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
@@
 
-On the other side, the main problem about too many dependent variables specific to this optimisation procedure 
+%On the other side, 
+The main problem about too many dependent variables specific to this optimisation procedure 
 is that the same set of basis functions will be used to predict \textbf{all} \textit{optimisands}.
@@
 for including them in the \gls{rf}s is an easy way to reduce the \gls{mse} and improve prediction accuracy.
+\enlargethispage{\baselineskip}
 These \gls{bf}s then "take away places" of \gls{bf}s predicting other dependent variables in the \gls{rf}. %\td{(cf. musical chairs)} 
@@
 
-The two independent variables $v{cal}$ and $\lambda$ were included as \textit{optimisands} for two reasons: 
+The two independent variables $v_{cal}$ and $\lambda$ were included as \textit{optimisands} for two reasons: 
 Maximizing the calcination velocity and minimizing the number of layer application iterations leads to minimization of process time.
@@
 The second reason for including independent variables was to check if the model works. 
-This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimisands} and thus additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables.
+This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimisands} and thus 
+additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables and chose future data points. 
 The second flaw is that there are obsiously better methods to assess the quality of a model than to make it more complex. 
 %Good alternatives would have been leave-one-out or cross validation.
-Validation methods for sparse data include resampling vie k-fold cross validation\cite{kartam1997artificial}.
+Validation methods for sparse data include resampling via leave-one-out or $k$-fold cross validation\cite{kartam1997artificial}.
 

### 2023-03-08 Thesis/chapter/061-results-emma.tex
change optimisand to optimizand

@@
 \linebreak[4]
-Indeed, the samples with the lowest \textit{optimisands} are among the initial generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).
+Indeed, the samples with the lowest \textit{optimizands} are among the initial generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).
 
-In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimisands}, 
+In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
 conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
@@
 %
-%\td{Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as \textit{optimisands} rather unfortunate. %highly questionable. 
+%\td{Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as \textit{optimizands} rather unfortunate. %highly questionable. 
 %\td{This makes including $\lambda$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
@@
 %for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
-%$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $\lambda$ increases the two \textit{optimisands}. 
+%$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $\lambda$ increases the two \textit{optimizands}. 
 %LAMBDA 
@@
 It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}). 
-This negative correlation could hint a compensation of the overestimated influence of $T_{cal}$ on the \textit{optimisands}.
+This negative correlation could hint a compensation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
 Similarly, signs of coefficients of $\lambda \cdot T_{cal}$ and $h(\lambda -6) \cdot T_{DB}$ correlate negatively in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) and the product of coefficients and input variables are again similar in order of magnitude.
@@
 %%% PROBLEMS 
-Even though the main \textit{optimisands} were minimized as required, the \gls{rf}s were not satisfactory. 
+Even though the main \textit{optimizands} were minimized as required, the \gls{rf}s were not satisfactory. 
 The two main problems were too many independent variables and too many dependent variables. 
@@
 The main problem about too many dependent variables specific to this optimisation procedure 
-is that the same set of basis functions will be used to predict \textbf{all} \textit{optimisands}.
+is that the same set of basis functions will be used to predict \textbf{all} \textit{optimizands}.
 This leads to competition between the \gls{bf}s, as not all dependent variables may depend on the same independent variables. 
@@
 
-The two independent variables $v_{cal}$ and $\lambda$ were included as \textit{optimisands} for two reasons: 
+The two independent variables $v_{cal}$ and $\lambda$ were included as \textit{optimizands} for two reasons: 
 Maximizing the calcination velocity and minimizing the number of layer application iterations leads to minimization of process time.
@@
 The second reason for including independent variables was to check if the model works. 
-This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimisands} and thus 
+This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimizands} and thus 
 additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables and chose future data points. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{rational behind including $v_{cal}$ and $\lambda$ as optimisands}
+\subsection{rational behind including $v_{cal}$ and $\lambda$ as optimizands}
 }

### 2023-03-09 Thesis/chapter/061-results-emma.tex
proof read anova and lin reg

@@
 This indicates an underestimation of $\hat\gamma$ at the beginning and a correction with time. 
-%The reason for is probably a 
 The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
@@
 
+%GENERATIONS
 In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
@@
 %\subsection{Equation}
-Equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal3}) and (\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) represent the regression functions at $t=3$ and $t=4$, respsectively, rounded to 2 significant digits.
+Equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal3}) and (\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) represent the regression functions at $t=3$ and $t=4$, respectively, rounded to 2 significant digits.
 %$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
@@
 %This means that the algorithm must decide on the variables which explain the most variance independent of optimization weights.
-This stems from the fact that the algorithm choses a single minimal set of basis functions to predict all dependent variables. 
+This stems from the fact that the algorithm chooses a single minimal set of basis functions to predict all dependent variables. 
 %
@@
 %$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $\lambda$ increases the two \textit{optimizands}. 
-%LAMBDA 
+%
 % TCAL ON OPTIMIZANDS
@@
 that therefore the resulting layer does not insulate as well. 
-%\td{xxx}
-\textit{Optimisands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
+The original recipe by Hu et al.\cite{Hu2016} used \oc{500} and thus even \oc{400} are low.
+\textit{Optimizands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
 according to equations~(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) (see also figures~\ref{fig:g-tcal} and \ref{fig:phd-tcal}), 
 ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.
+%
 % DESCRIBE COEFFICIENTS
@@
 That means 15, 20, 25 and 30 samples 
-%for $t=0$, 15 samples for $t=1$ and 30 sampes for $t=4$ 
+%for $t=0$, 15 samples for $t=1$ and 30 samples for $t=4$ 
 were used to calculate \gls{mse}s at $t=1,2,3,4$, respectively (compare with table~\ref{tab:emma-Gb}).
@@
 %\td{It should be noted, that the validation \gls{mse} for $t=1$ is much higher.}
-When compraring the out-of-sample and in-sample \gls{mse}s it can be noted that at $t=1$ the out-of-sample \gls{mse} is close to 1.5 fold of in-sample and at $t=2$ vice versa.
+When comparing the out-of-sample and in-sample \gls{mse}s it can be noted that at $t=1$ the out-of-sample \gls{mse} is close to 1.5 fold of in-sample and at $t=2$ vice versa.
 %The high validation \gls{mse} for $t=1$ (nearly 1.5 fold instead of circa 1 fold of \gls{mse}) 
@@
 This decrease in validation (out-of-sample) \gls{mse} supports the hypothesis stated at the beginning of this section: 
-the measure of conductance was underestimated and and the estimate improved over time (see table~\ref{tab:emma-pred-G}).
+the measure of conductance was underestimated and the estimate improved over time (see table~\ref{tab:emma-pred-G}).
 %\td{why is \gls{mse} higher with higher values? No homoscedasticity ( equality of variance)?
@@
 By eliminating three independent variables the \gls{epv} could rise to 10, which is stated 
-as rule of thumb for mulitvariate regression\cite{vittinghoff2007relaxing}. 
-The results obtained with limited sample number deliver remarkable insightfulness %are quite respectable. 
+as rule of thumb for multivariate regression\cite{vittinghoff2007relaxing}. 
+The results obtained with limited sample number deliver remarkable insight %are quite respectable 
 comparing to an \gls{epv} of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
@@
 additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables and chose future data points. 
-The second flaw is that there are obsiously better methods to assess the quality of a model than to make it more complex. 
+Moreover, $v_{cal}$ and $\lambda$ were only considered with 5\% weight. 
+The second flaw is that there are obviously better methods to assess the quality of a model than to make it more complex. 
 %Good alternatives would have been leave-one-out or cross validation.
-Validation methods for sparse data include resampling via leave-one-out or $k$-fold cross validation\cite{kartam1997artificial}.
+Validation methods for sparse data include re-sampling via leave-one-out or $k$-fold cross validation\cite{kartam1997artificial}.
 
@@
 all dependent variables and possibly exclude others which have more influence 
-on $\gamma$ and $\rho$ (see equations (\ref{eq:emma-G4})? and (\ref{eq:emma-phd4})?).
+on $\gamma$ and $\rho$ (see equations (\ref{eq:emma-G4})? And (\ref{eq:emma-phd4})?).
 %
@@
 \fi
-
-\td{TODO: find expression for $\gamma$: conductance measure, conducticity}
-\td{when adding dep var to model this has two folgen: - beeinflusst the BF and the optimization, but bcs relatiev weight is only 0.05 for each, no big beeinflussung on optimization}

### 2023-03-09 Thesis/chapter/062-post-emma.tex
change optimisand to optimizand
proof read anova and lin reg

@@
 %describe what awaits the reader in this chapter:
-In this section the experimental results are analyzed with different methods and compared with the original method EMMA which was integrated into the experiment selection process. 
+In this section the experimental results are analyzed with different methods and compared with EMMA which was integrated into the experiment selection process. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
@@
 
-\textbf{What can/did we test?}
-the probability of arriving at these results was by pure chance can be checked with \gls{anova}. 
+%WHAT CAN/DID WE TEST?
 The null hypothesis is that the results were obtained by pure chance without any dependence of the insulation of a sample on the process variables.
-%We tested for each input variable the influence on rho and gamma 
 A one-way \gls{anova} was performed for every independent variable on $\rho$ and $\gamma$. 
-%and also as a test on vcal and $\lambda$. 
 We used an $\alpha$ value of 0.05 which means that 
@@
 Usually, the $\alpha$-value is chosen to be 0.01 or 0.05\cite{hoffman2020concept,sellke2001pvalues}.
-The choice of a relatively high $alpha$-value is motivated by the rather small amount of data and low events per varible ratio.
-\ds{
-As mentioned by Sellke et al.\cite{sellke2001pvalues} a p-value of 0.05 might tempt 
-to guess that in 1 out of 20 cases the results could be false positives, 
-whereas the frequency is much higher. 
-A p-value of 0.01 and 0.05  mean that under the assumption that the null hypothesis is correct, 
-there is a 1\% and 5\% chance of arriving at such data as observed.
+The choice of a relatively high $alpha$-value is motivated by the rather small amount of data and low events per variable ratio.
+%As mentioned by Sellke et al.\cite{sellke2001pvalues} a p-value of 0.05 might tempt 
+%to guess that in 1 out of 20 cases the results could be false positives, 
+%whereas the frequency is much higher. 
+%A p-value of 0.01 and 0.05  mean that under the assumption that the null hypothesis is correct, 
+%there is a 1\% and 5\% chance of arriving at such data as observed.
 %The results should thus be taken with a grain of salt. 
-}
+%
 %1 out of 20 times this result could be 
@@
 
-\textbf{What were the results?}
+%WHAT WERE THE RESULTS?
 %\Gls{anova} shows that for the mentioned indep and dep pairs, the means divided by 
 %indep groups are not equal and that there is at least one group that is different. 
-For both $\rho$ and $\lambda$ (for both the \gls{emma} dataset and the extended dataset (=\gls{emma}+pre\gls{emma})) 
+For both $\rho$ and $\lambda$ (for both the \gls{emma} dataset and the whole dataset (=\gls{emma}+pre-\gls{emma})) 
 the F-values for $T_{cal}$ were in all cases under 0.01, 
@@
 Furthermore, both datasets exhibit a p-value $< 0.05$ for the interaction $T_{cal}$:$v_{cal}$ on $\rho$
-and the extended data set has p-value smaller than 0.01 of $v_{cal}$ on $\rho$. 
+and the whole data set has p-value smaller than 0.01 of $v_{cal}$ on $\rho$. 
 Whereas $v_{cal}$ on $\rho$ for \gls{emma} dataset has p-value of slightly over 0.05
-%\td{why tcal:vcal on phd the same for both datasets? zufall}
-
-\textbf{What do the results mean?} 
-\Gls{anova} confirms that $T_{cal}$ has influence on both $\gamma$ and $\rho$. 
-It seems that the probability of getting such data per chance that Tcal has no influence 
-(null hypothesis is true) is less then 5\% (even less than 1\%). 
+%\td{why tcal:vcal on phd the same for both datasets? Chance?}
+%
+%WHAT DO THE RESULTS MEAN?
+\Gls{anova} confirms that $T_{cal}$ has influence on both $\gamma$ and $\rho$ 
+and therefore agrees with \gls{emma}.
+%It seems that the probability of getting such data per chance without $T_{cal}$ influencing the \textit{optimizands}
+%(null hypothesis is true) is less then 5\% (even less than 1\%) for corresponding p-values, but Sellke et al.\cite{sellke2001pvalues} showed in 2001 that in fact the . 
 %\td{NO bcs \cite{sellke2001pvalues}}
-It is important to mention, that \gls{anova} assumes categorical data for inputs, 
-where our data is numerical and thus information is lost.
+It is important to mention, that \gls{anova} assumes categorical data for inputs. 
+Categorical inputs have no order and thus information is lost when using numerical data. 
+%where our data is numerical and thus information is lost.
 
@@
 \subsection{Linear Regression} 
-%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influennced by the Zirconium concentrain in the starting solution $c_{zr}$ and the number of layers applied $\lambda$, but their coefficients are the smallest in absolute values.
+%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influenced by the Zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$, but their coefficients are the smallest in absolute values.
 
@@
 The data obtained from the \gls{emma} optimisation was used to fit a linear model. 
-The biggest difference of the linear model to \gls{emma} is that all variables are included, that the \gls{bf}s are strictly linear and that there are no interaction terms. 
-The coefficients of the $\lambda$ term have the same sign in equations \ref{eq:emma-phd3},\ref{eq:emma-G3},\ref{eq:emma-phd4},\ref{eq:emma-G4} (\gls{emma} \gls{rf}s) and \ref{eq:linreg-phd},\ref{eq:linreg-G} and have comparable magnitudes too.
+The biggest difference between the linear model and \gls{emma} is that the linear regression function will include all input variables, that the \gls{bf}s are strictly linear and that there are no interaction terms.
+The coefficients of the $\lambda$ term have the same sign in equations \ref{eq:emma-phd3}, \ref{eq:emma-G3}, \ref{eq:emma-phd4}, \ref{eq:emma-G4} (\gls{emma} \gls{rf}s) and \ref{eq:linreg-phd}, \ref{eq:linreg-G} and have comparable magnitudes too.
 %
@@
 		\label{eq:linreg-phd}
-		\hat{\rho} &=  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{DB} + 0.0058\cdot T_{DB} \\
+		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{DB} + 0.0058\cdot T_{DB} \\
 		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
@@
 		\label{eq:linreg-G}
-		\hat{\gamma} &={}  \qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot \lambda \,\,\quad - 1.2\cdot v_{DB} + \,\,\,\quad 0.2\cdot T_{DB} \\
+		\hat{\gamma} =&  \,\,\qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot \lambda \,\,\quad - 1.2\cdot v_{DB}  \,\,\,\quad +0.2\cdot T_{DB} \\
 			& \qquad - 0.014\cdot v_{cal} \quad + 0.13\cdot T_{cal} + 7.2
@@
 %
-All terms in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign except the intercept and $c_{zr}$. 
+All terms in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign 
+except $c_{zr}$ and the intercept. 
 %
@@
 %This is only true if the extended data set is used and therefore again rather by chance. 
-When the linear regression is trained on the complete data set, all terms have the same sign compared to the \gls{emma} data set trained linear model. 
+When the linear regression is trained on the whole data set, all terms have the same sign compared to the \gls{emma} data set trained linear model. 
 %It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}.
-$v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality and thus are not displayed here. 
+$v_{cal}$ and $\lambda$ are perfectly predicted by linear regression as there is an exact direct proportionality and thus are not displayed here. 
 %
@@
 %
-Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$ are largest in value, but the values which are taken by $c_{zr}$ and $\lambda$ itself are the smallest among the input variables.
+Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$ are largest in value, but the values which are factored with these coefficients - i.e.\, $c_{zr}$ and $\lambda$ themselves -- are the smallest among the input variables.
 Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
-In order to compare, the influence was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{min}+x_{max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression.
+In order to compare, the influence of an input variable was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{min}+x_{max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression.
 %The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
@@
 They parameters are often extrema.
-The hyperparameter $\gamma_{ml}$ took minimum value possibel twice. 
+The hyperparameter $\gamma_{ml}$ took minimum value possible twice. 
 In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
@@
     \end{tabular}
-    \caption{Best parameters for each \textit{optimisand}-method-combination}
+    \caption{Best parameters for each \textit{optimizand}-method-combination}
     \label{tab:grid-search}
@@
 But as soon as unseen data enters the field, linear regression excels with its simplicity. 
-The linear regression method is only under cut by when calculatting the \gls{mae} of $\gamma$
+The linear regression method is only under cut by when calculating the \gls{mae} of $\gamma$
 for the interpolating unseen data with \gls{svm}. 

### 2023-03-10 Thesis/chapter/031-theory-calculations.tex
sation to zation

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Population Based Optimisation Algorithms}
+\subsection{Population Based Optimization Algorithms}
 
@@
 at the backwards step are selected by minimizing \gls{gcv}. 
-The coefficients for each term are then chosen via regular \gls{mse} minimisation\cite{friedman1988fitting}.
+The coefficients for each term are then chosen via regular \gls{mse} minimization\cite{friedman1988fitting}.
 
@@
     \item DOE (add data acquisition)
-    \item genetic algorithm and pso (they combine data gen with regression/prediction and optimisation, actually incorporate prediction into selection process but don't per se specify which pred and optimisation)
+    \item genetic algorithm and pso (they combine data gen with regression/prediction and optimization, actually incorporate prediction into selection process but don't per se specify which pred and optimization)
     \item comment: always tradeoff between complexity and interpretability

### 2023-03-10 Thesis/chapter/032-alt-theory-calculations.tex
change from article to report
sation to zation

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Machine Learning and Statistics}
+\section{Machine Learning and Statistics}
 
-\subsubsection{Introduction to AI, ML and statistics}
+\subsection{Introduction to AI, ML and statistics}
 \textbf{What is AI?} It is the interdisciplinary field of making a artificial inteligent agent. 
@@
 The last two are special in the sense that they don't provide a certain regression method,
-but rather a frame work to choose the next sample which should be tested in a optimisation. 
+but rather a frame work to choose the next sample which should be tested in a optimization. 
 \td{mention classification vs regression and supervised vs supervised}
@@
 This extra term is scaled by a correction parameter $\lambda$. 
-The larger $\lambda$ the larger regularisation and the flatter the regression functions. 
+The larger $\lambda$ the larger regularization and the flatter the regression functions. 
 If $\lambda$ were infinite, then the regression function would be a flat line. 

### 2023-03-10 Thesis/chapter/033-linreg-krr-svm.tex
sation to zation

@@
 The extra term reduces overfitting and is scaled by a correction parameter~$\alpha$. 
-The larger $\alpha$ is, the larger is the regularisation and the flatter is the regression functions. 
+The larger $\alpha$ is, the larger is the regularization and the flatter is the regression functions. 
 When $\alpha$ tends to infinity, we get an intercept-only model.
@@
 they have opposite signs and their product will be a negative number.
-The substraction of a negative number will result in a positive penalizisation. 
+The substraction of a negative number will result in a positive penalizization. 
 If the sample is correctly predicted, the product will result in a positive number, 

### 2023-03-10 Thesis/chapter/04-experimental.tex
start EMMA
sation to zation

@@
 In the first section the base recipe and the base process were sought. 
-In the pre-optimisation section the boundaries for the optimisation were investigated. 
-And during the third and final step the experiments for the optimisation were performed.
+In the pre-optimization section the boundaries for the optimization were investigated. 
+And during the third and final step the experiments for the optimization were performed.
 \section{Substrate Preparation}
@@
 (\gls{acac} and citric acid) were tested and later in the process - just before the 
-\gls{pso} started - the stabilisation compound (\gls{acoh}) was changed to \gls{ipo}.
-The most promising combination of solvent, chelating agent and stabilisation reagent was 
-\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimisation.
+\gls{pso} started - the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
+The most promising combination of solvent, chelating agent and stabilization reagent was 
+\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
 The main differences between the used recipe and the recipe mentioned by \cite{Hu2016} were 
@@
 stirring \minutes{\ds{10 to }15} one mole equivalent chelating agent (\gls{acac}) was 
-added and stirred for another \minutes{\ds{10 to }15}. Finally, the stabilisation 
+added and stirred for another \minutes{\ds{10 to }15}. Finally, the stabilization 
 solvent\cite{Hu2016} (\gls{ipo} or \gls{acoh}) was added to the mixture and stirred for 
@@
 
-%Most steel substrates (all pre-optimisation and optimisation samples) 
+%Most steel substrates (all pre-optimization and optimization samples) 
 All steel substrates 
@@
 was switched on. 
-During pre-optimisation samples, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
+During pre-optimization samples, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
 \mmps{1}, \mmps{2} and \mmps{5}) were tested. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Characterisation}
+\section{Characterization}
 All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Pre-optimisation}\label{sec:exp-preopt}
+\section{Pre-optimization}\label{sec:exp-preopt}
 %\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
 %\td{Screening}
-%The main part of the screening pre-optimisation samples were optimized via biotic reinforcement learning (i.e. my brain). 
+%The main part of the screening pre-optimization samples were optimized via biotic reinforcement learning (i.e. my brain). 
 The main part of all samples (around 90\%) were pre-optimization samples, 
@@
 		\centering
-        \subcaption{Hand picked experiments; $^*$varied stabilisation agent}
+        \subcaption{Hand picked experiments; $^*$varied stabilization agent}
 		\label{tab:pre-opt2}
@@
 			\\ \\  \\
-%			\multicolumn{6}{c}{*different stabilisation reagent compositions}\\
+%			\multicolumn{6}{c}{*different stabilization reagent compositions}\\
 		\end{tabular}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Shortly before the \gls{pso} the stabilisation agent was changed from \gls{acoh} to 
+Shortly before the \gls{pso} the stabilization agent was changed from \gls{acoh} to 
 \gls{ipo} because of much better solution stability.
@@
 \ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
-%\td{As the sample showed the best all ex were proceeded with ipo as stabilisation agent. }
+%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
 The sample produced with \gls{ipo} as stabilization agent 
 showed comparable passivization results and better stability. 
-Therefore \gls{ipo} was used  as stabilisation in further experiments.
+Therefore \gls{ipo} was used  as stabilization in further experiments.
 After the boundaries of the solution were fixed 
@@
 %\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
-See table \ref{tab:space} for the space spanned for the optimisation.
+See table \ref{tab:input} for the input space spanned during the optimization.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\iffalse
 \begin{table}[ht!]

### 2023-03-10 Thesis/chapter/061-results-emma.tex
sation to zation

--- 2023-03-08 Thesis/chapter/061-results-emma.tex
@@
 It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}). 
-This negative correlation could hint a compensation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
+This negative correlation could hint a compenzation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
 Similarly, signs of coefficients of $\lambda \cdot T_{cal}$ and $h(\lambda -6) \cdot T_{DB}$ correlate negatively in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) and the product of coefficients and input variables are again similar in order of magnitude.
@@
 For each generation the \gls{mse} was calculated for which only samples 
-from the optimisation were used which were available at the time of prediction. 
+from the optimization were used which were available at the time of prediction. 
 That means 15, 20, 25 and 30 samples 
@@
 This decrease in \gls{mse} might be attributed to overfitting, though, since prediction and validation were performed on the same data. 
-%The \gls{mse} for each generation was also calculated between predicted values for pre-optimisation samples to check for overfitting, 
-The \gls{mse} for each generation's prediction function was also calculated for pre-optimisation (out-of-sample) samples, which are unseen data. 
+%The \gls{mse} for each generation was also calculated between predicted values for pre-optimization samples to check for overfitting, 
+The \gls{mse} for each generation's prediction function was also calculated for pre-optimization (out-of-sample) samples, which are unseen data. 
 The error sank again with each generation (except for the second generation): 102, 118, 58, 50, respectively for $t=1,2,3,4$. 
@@
 %The high validation \gls{mse} for $t=1$ (nearly 1.5 fold instead of circa 1 fold of \gls{mse}) 
-This shows the poor prediction ability at the beginning of the optimisation which improved with generations.
+This shows the poor prediction ability at the beginning of the optimization which improved with generations.
 This decrease in validation (out-of-sample) \gls{mse} supports the hypothesis stated at the beginning of this section: 
@@
 %
-%In the here presented optimisation model 
+%In the here presented optimization model 
 %the data points per independent variable 
 %(events per predictor variable EPV) are as low as 5. 
-The \gls{epv} (data points per independent varible) are as low as 5 in the here presented optimisation. % model and data acquisition method
+The \gls{epv} (data points per independent varible) are as low as 5 in the here presented optimization. % model and data acquisition method
 By eliminating three independent variables the \gls{epv} could rise to 10, which is stated 
@@
 %On the other side, 
-The main problem about too many dependent variables specific to this optimisation procedure 
+The main problem about too many dependent variables specific to this optimization procedure 
 is that the same set of basis functions will be used to predict \textbf{all} \textit{optimizands}.
@@
 Maximizing the calcination velocity and minimizing the number of layer application iterations leads to minimization of process time.
-This optimization would be better placed in a follow up study. 
+The process time optimization would be better placed in a follow up study. 
 The second reason for including independent variables was to check if the model works. 

### 2023-03-10 Thesis/chapter/062-post-emma.tex
sation to zation

--- 2023-02-26 Thesis/chapter/062-post-emma.tex
@@
 %describe what awaits the reader in this chapter:
-In this section the experimental results are analyzed with different methods and compared with the original method EMMA which was integrated into the experiment selection process. 
+In this section the experimental results are analyzed with different methods and compared 
+with the optimization method EMMA which was integrated into the experiment selection process. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
@@
 %\todo{what was fitted how?}
-The data obtained from the \gls{emma} optimisation was used to fit a linear model. 
+The data obtained from the \gls{emma} optimization was used to fit a linear model. 
 The biggest difference of the linear model to \gls{emma} is that all variables are included, that the \gls{bf}s are strictly linear and that there are no interaction terms. 
@@
 %$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
-All these extreme values of hyperparameters stimulate regularisation and indicate noisy and difficult to fit data.
+All these extreme values of hyperparameters stimulate regularization and indicate noisy and difficult to fit data.
 \begin{table}
@@
 % pre-EMMA 21 pts 
-The next two columns were calculated with data obtained before the EMMA optimisation. 
-As the this pre-optimisation data set was mainly used to find appropriate boundaries for the input variables, 
+The next two columns were calculated with data obtained before the EMMA optimization. 
+As the this pre-optimization data set was mainly used to find appropriate boundaries for the input variables, 
 many data points are outside of the range of the \gls{emma} data set. 

### 2023-03-10 Thesis/chapter/063-discussion.tex
sation to zation

@@
 %- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
-%\todo{british or US?: sation vs zation} 
+%\todo{british or US?: zation vs zation} 
 %\todo{ include last phase into previous section}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Narrowing, pre-optimisation and constraint phase}
+\subsection{Narrowing, pre-optimization and constraint phase}
 \label{sec:phase2}
@@
 Another step/deed which is well placed in this phase is the estimate the error by reproducing a single sample a certain number of times. 
-%Where the number will then be higher than during optimisation 
+%Where the number will then be higher than during optimization 
 %\todo{include curse of dimensionality.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Optimisation, modelling and data generation}
+\subsection{Optimization, modelling and data generation}
 \label{sec:phase3}
-During the optimisation the main problems were too many in- and output variables, reproducibility and regularisation. 
+During the optimization the main problems were too many in- and output variables, reproducibility and regularization. 
 %The first problem 
@@
 When working with stochastic algorithms it is especially important to introduce reproducibility via a seed, which determines all subsequent pseudo-random numbers. 
-Finally, during the \gls{emma} optimisation the input data were not regularized, %es wurde auf regularisation verzichtet, 
+Finally, during the \gls{emma} optimization the input data were not regularized, %es wurde auf regularization verzichtet, 
 because the regularization would be different for different generations.
@@
 %On the other hand haette man auf jeden fall die input variablen normieren können. 
-%Normally, for standardisation the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
+%Normally, for standardization the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
 %One could have assumed a standard uniform distribution. 
@@
 \begin{itemize}
-    \item Dimension reduction bietet sich stark an bei solcher Datenlage. in pre-optimisation!
+    \item Dimension reduction bietet sich stark an bei solcher Datenlage. in pre-optimization!
     \item \textbf{keep it simple}: include what you already know and reduce model size to minimum, such that \gls{epv} is high.
@@
 %iterations (as in actual experiments) lead to suboptimal results.}
-    \item \textbf{pre-optimisation}{The primary goal of a screening experiment is to identify the active factors.
+    \item \textbf{pre-optimization}{The primary goal of a screening experiment is to identify the active factors.
 A secondary goal is to provide a simple model that captures the essential features of the relationship between these active factors and the response—that is, to identify the active effects.
@@
 \fi
+
+\td{when adding dep var to model this has two folgen: - beeinflusst the BF and the optimization, but bcs relatiev weight is only 0.05 for each, no big beeinflussung on optimization}

### 2023-03-10 Thesis/chapter/07-outlook.tex
sation to zation

@@
 The recipe was improved by increasing its stability. 
-The best parameters found by the emma optimisation were 
+The best parameters found by the emma optimization were 
 $c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
@@
 %welche methoden wurden dafür verwendet? 
-After optimsation the data was analysed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
+After optimzation the data was analysed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
 The comparisson of methods showed that \gls{emma} performed well on predicting the correlation between conductance and process variables. 

### 2023-03-10 Thesis/chapter/031-theory-calculations.tex
uk to us

@@
 \Gls{ml} is at the base of most \gls{ai}s.
-It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
+It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorize, predict and make decisions based on data. 
 %
 There is a platitude of different machine learning methods: 
-they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
+they can be divided into supervized (training set is labeled) and unsupervized (exploratory).  
 An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
@@
 is represented by its independent and dependent variables. 
-It was originally inspired by the behaviour of bird flocks and fish schools\cite{villanova2010function,Kennedy1995}.
+It was originally inspired by the behavior of bird flocks and fish schools\cite{villanova2010function,Kennedy1995}.
 %"PSO is a population based heuristic inspired by the flocking behavior of birds. 
@@
 residual error should follow normal distribution and variance within groups should be equal (homoscedasticity). 
-%\Gls{anova} analyses the means by means of mincing variances.
+%\Gls{anova} analyzes the means by means of mincing variances.
 %of of the continuous outputs where inputs are categories. 

### 2023-03-10 Thesis/chapter/07-outlook.tex
uk to us

@@
 %welche methoden wurden dafür verwendet? 
-After optimzation the data was analysed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
+After optimzation the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
 The comparisson of methods showed that \gls{emma} performed well on predicting the correlation between conductance and process variables. 

### 2023-03-10 Thesis/chapter/062-post-emma.tex
adjust hyper parameters

--- 2023-03-09 Thesis/chapter/062-post-emma.tex
@@
 combination can be seen in table \ref{tab:grid-search}. 
-They parameters are often extrema.
-The hyperparameter $\gamma_{ml}$ took minimum value possible twice. 
+The parameters are often extrema.
+The hyperparameter $\gamma_{ml}$ took minimum value from the grid search twice. 
 In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
 The range of the hyperparameter $\alpha$ was 0.01--10 in the grid search. 
-So 2 and 10 are high values for the regularization parameter of \gls{krr}.
+So 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
 The hyperparameter $\varepsilon$ specifies the size of the tube within which data does not contribute to the loss 
-and the value 1 is the maximum during the grid search. 
+and the value 1 is the maximum for $\varepsilon$ during this grid search. 
+%\td{why can R2 be negative? https://stats.stackexchange.com/a/279358/374563 } 
 %The value 1 for $\varepsilon$ is the highest possible, 
@@
         \hline
-        KRR($\gamma$)   &poly   &1  &0.01   &2.00 &-&-\\
-        KRR($\rho  $)   &rbf    &-   &0.2    &10.00&-&-\\
+        KRR($\gamma$)   &poly   &1  &0.01   &2 &-&-\\
+        KRR($\rho  $)   &rbf    &-   &0.2   &10&-&-\\
         SVM($\gamma$)   &poly   &2  &0.5    &-&0.7  &1.0  \\

### 2023-03-10 Thesis/chapter/062-post-emma.tex

@@
 %describe what awaits the reader in this chapter:
-In this section the experimental results are analyzed with different methods and compared with EMMA which was integrated into the experiment selection process. 
+In this section the experimental results are analyzed with different methods and compared 
+with the optimization method EMMA which was integrated into the experiment selection process. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

### 2023-03-10 Thesis/chapter/062-post-emma.tex
proof read post-emma close to finish

@@
 \subsection{Grid Search, KRR and SVM}
-The optimal parameters for each \textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 
-combination can be seen in table \ref{tab:grid-search}. 
+The optimal parameters for each combination of 
+\textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 
+can be seen in table \ref{tab:grid-search}. 
 The parameters are often extrema.
-The hyperparameter $\gamma_{ml}$ took minimum value from the grid search twice. 
+The hyperparameter $\gamma_{ml}$ took the smallest possible value (within the grid search) twice. 
 In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
 The range of the hyperparameter $\alpha$ was 0.01--10 in the grid search. 
-So 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
+So, 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
 The hyperparameter $\varepsilon$ specifies the size of the tube within which data does not contribute to the loss 
@@
 %$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
-All these extreme values of hyperparameters stimulate regularization and indicate noisy and difficult to fit data.
+All these extreme values of hyperparameters (stimulate regularization and indicate noisy and difficult to fit data.
 \begin{table}
     \center
-    \begin{tabular}{ccccccc}
+    \begin{tabular}{cccccccc}
         \hline\hline
-        method  &kernel &degree &$\gamma_{ml}$   &$\alpha$    &$C$    &$\varepsilon$\\
+        method  &$R^2$   &kernel &degree &$\gamma_{ml}$   &$\alpha$    &$C$    &$\varepsilon$\\
         \hline
-        KRR($\gamma$)   &poly   &1  &0.01   &2 &-&-\\
-        KRR($\rho  $)   &rbf    &-   &0.2   &10&-&-\\
-        SVM($\gamma$)   &poly   &2  &0.5    &-&0.7  &1.0  \\
-        SVM($\rho  $)   &poly   &3  &0.01   &-&0.1  &0.1  \\
+        KRR($\gamma$) & $-0.50 \pm 0.25$  &poly   &1  &0.01   &2 &-&-\\
+        KRR($\rho  $) & $-0.45 \pm 0.52$  &rbf    &-   &0.2   &10&-&-\\
+        SVM($\gamma$) & $-0.37 \pm 0.39$  &poly   &2  &0.5    &-&0.7  &1.0  \\
+        SVM($\rho  $) & $-0.95 \pm 0.44$  &poly   &3  &0.01   &-&0.1  &0.1  \\
         \hline\hline
     \end{tabular}
-    \caption{Best parameters for each \textit{optimizand}-method-combination}
+    \caption{$R^2$ values and best hyperparameters for each \textit{optimizand}-method-combination}
     \label{tab:grid-search}
@@
 The $R^2$ values were calculated for each of the models using cross validation. 
-Resulting $R^2$ are all below zero (see equations \ref{eq:r2-krr-g}--\ref{eq:r2-svm-p}). 
+Resulting $R^2$ are all below zero (see table~\ref{tab:grid-search}). 
 A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$.
 
+\iffalse
 \begin{align}
@@
 \end{align}
+\fi
 
 %
-Finally the \gls{mae} and \gls{mse} were calculated for different data sets with models 
-trained on the \gls{emma} data set (see table \ref{tab:post-emma}). 
+Finally, the \gls{mae} and \gls{mse} were calculated for different data sets 
+(see table \ref{tab:post-emma}). 
+Each models was trained on the \gls{emma} data set.
 % EMMA 30 pts
-The first two columns show statistics for data the model was trained with and thus, 
+The first two columns (e) show statistics validated with data the model was trained with (30 data points) and thus, 
 these columns contain the lowest numbers. 
 % pre-EMMA 21 pts 
-The next two columns were calculated with data obtained before the EMMA optimization. 
-As the this pre-optimization data set was mainly used to find appropriate boundaries for the input variables, 
+The next two columns (p) were calculated with data obtained before the EMMA optimization (21 data points). 
+As the pre-optimization data set was mainly used to find appropriate boundaries for the input variables, 
 many data points are outside of the range of the \gls{emma} data set. 
@@
 % inter/c/ pre-EMMA 5 pts
-The next two columns were produced by using pre-\gls{emma} data, 
-but only keeping points which sit inside the space spanned by the \gls{emma} constraints. 
+The next two columns (c) were produced by using pre-\gls{emma} data for validation, 
+but only keeping points which sit inside the space spanned by the \gls{emma} constraints (5 data points). 
 It should be expected that these statistics should be lower than in the previous two columns. 
-They are higher, though, because of the small sample size of 5 data points. 
+They are only lower for MARS($\rho$) and LR($\rho$), though. 
+This is likely due to the small sample size.
 % all 51 
-The last two columns show data for prediction of all available data. 
+The last two columns show data for predictions of all available data (51 data points). 
 These statistics are lower because of the inclusion of the training set in the test set.
 
-In the self test of the first two columns \gls{mars} is the one method to rule them all.
-But as soon as unseen data enters the field, linear regression excels with its simplicity. 
-The linear regression method is only under cut by when calculating the \gls{mae} of $\gamma$
-for the interpolating unseen data with \gls{svm}. 
+In the self test of the first two columns \gls{mars} is the one method to rule them all and provides the lowest metrics.
+But as soon as unseen data enters the field, linear regression excels by its simplicity. 
+\td{The linear regression method is only under cut by \gls{svm} when calculating the \gls{mae} of $\gamma$}
+for the interpolating unseen data (c).
 %
@@
 	\centering
-    \caption{Post EMMA vergleich}
-	\label{tab:post-emma}
+%    \caption{Post EMMA vergleich}
 	\begin{tabular}{c cc cc cc cc}
     \hline\hline
-    $\gamma$&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
+        $\gamma$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
     \hline
         MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
-        lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
+        LR&    13& 250&    24& 747&    34& 1327&   17& 454\\
 %        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
@@
         SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
-    \hline\hline
+        \hline
+%    \hline\hline
 	\end{tabular}
@@
     \hline\hline
-    $\rho$&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
+        $\rho$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
     \hline
         MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
-        lin Reg&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
+        LR&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
 %        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
@@
 	\end{tabular}
+    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
+	\label{tab:post-emma}
 \end{table}

### 2023-03-11 Thesis/chapter/07-outlook.tex
first complete draft

@@
 The goal of this work was to find a sol-gel doctor blading process resulting in a insulating zirconium ceramic on top of steel.
-This structure then can be used as substrate for thin layer photo voltaics. 
-The ceramic needs to be homoegeneous and defect free in order to insulate properly.
+This structure then can be used as substrate for thin layer photovoltaics. 
+The ceramic needs to be homogeneous and defect free in order to insulate properly.
 %what was done? 
@@
 The recipe was improved by increasing its stability. 
-The best parameters found by the emma optimization were 
+The best parameters found by the \gls{emma} optimization were 
 $c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
@@
 %welche methoden wurden dafür verwendet? 
-After optimzation the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
-The comparisson of methods showed that \gls{emma} performed well on predicting the correlation between conductance and process variables. 
+After optimization, the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
+The comparison of methods showed that \gls{emma} performed well on identifying the important correlation between conductance and process variables. 
 %was wurde herausgefunden? 
-A strong correlation of calcination temperature and conductance in the bereich of 300--400\oc{}. 
+A strong correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
+Furthermore, the layer count has been verified as an important factor. 
 %was kann noch herausgefundne werden und wie? 
-Next steps include to investigate if the correlation of condactance and calcination temperature are statistically significant or due to small sample size. 
+Next steps include to investigate if the correlation of conductance and calcination temperature are statistically significant or due to small sample size. 
 The aging process could be examined via infra red spectroscopy. 

### 2023-05-14 Code/ML/2022/3_calc_mse_of_best.sh
minor change

@@ -1,5 +1,5 @@
 #!/bin/bash
-CONFIG_FILE=calc_best_cmds.sh # this file is created by executing 1
+CONFIG_FILE=calc_best_cmds.sh # this file is created by executing 1_best_of_algo.sh
 
 # COMMAND LINE ARGUMENTS
 HELPTEXT="This program executes grid seach on hyper parameters

### 2023-05-14 doc/Thesis/chapter/01-introduction.tex
delete unnecessary files and rearange folder structure

--- 2023-03-06 Thesis/chapter/01-introduction.tex
@@
 algorithm. 
-%The resulting optimum is compared with other optimisation methods.
+%The resulting optimum is compared with other optimization methods.
 
@@
 In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
-Section \ref{sec:results} is split into three sections: material specific results are presented in section \ref{sec:res-mat}, results regarding particle swarm optimisation in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
+Section \ref{sec:results} is split into three sections: material specific results are presented in section \ref{sec:res-mat}, results regarding particle swarm optimization in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
 Finally, chapter \ref{sec:outlook} summarizes and discusses the outlook and next steps.

### 2023-05-14 doc/Thesis/chapter/05-computational-details.tex
delete unnecessary files and rearange folder structure

--- 2023-03-07 Thesis/chapter/05-computational-details.tex
@@
 The kernel took the form of \gls{rbf}, sigmoid or polynomial with degree 1--3.
-The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
-and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
+The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5 and 10.
+%and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
 Note that $\gamma_{ml}$ is used differently in each kernel. 
@@
 Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$, 
-where $C$ took the values 0.05--0.95 with step size 0.05, $\varepsilon$ 0.02--3.8 with 0.2 steps 
-and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
+where $C$ and $\varepsilon$ took the values 0.05--1 with step size 0.05 %, $\varepsilon$ 0.05--4.0 with 0.2 steps 
+and was the same as for \gls{krr} plus \texttt{scale}. %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
 Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
@@
 For each calculation the 5-fold cross validation score was calculated. 
-The score equals to the coefficient of determination $R^2$ which defined as 
-$1-\frac{\sum (y_i - \hat{y}_i)}{\sum (y_i - \bar{y}_i)}$.
+The score equals to the coefficient of determination $R^2$ which defined the following for non linear regression functions:
+\begin{equation}
+	\label{eq:r2}
+	R^2 = 1-\frac{\sum (y_i - \hat{y}_i)}{\sum (y_i - \bar{y}_i)}
+\end{equation}
 For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 

### 2023-05-14 doc/Thesis/chapter/060-results-material.tex
delete unnecessary files and rearange folder structure

--- 2023-03-07 Thesis/chapter/060-results-material.tex
@@
 Starting with physical measurements and material properties. 
-Followed by the presentation of the results obtain by optimisation and exploration with the \gls{emma} method. 
-Finally, the results of alternative optimisation methods were let loose on the data and compared with the \gls{emma} method.
+Followed by the presentation of the results obtain by optimization and exploration with the \gls{emma} method. 
+Finally, the results of alternative optimization methods were let loose on the data and compared with the \gls{emma} method.
 
@@
 An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
-%\td{what is this aging process chemically? oxidation, hydrolisation?}.
+%\td{what is this aging process chemically? oxidation, hydrolization?}.
 The aging process was accelerated by being in contact with "fresh" air in contrast to being sealed. 
-It therefore dependent on the water or oxygen in the air corresponding to an oxidation or hyrolisation process.
+It therefore dependent on the water or oxygen in the air corresponding to an oxidation or hyrolization process.
 %
@@
 %due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
-%- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation
+%- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualization
 
@@
 
-%\td{instead of changing the stabilisation agent before optimisation, could change after pso, was vor und nachteile?}
+%\td{instead of changing the stabilization agent before optimization, could change after pso, was vor und nachteile?}
 %after realizing the improved effectiveness of \gls{ipo} for experimentation, 

### 2023-05-14 doc/Thesis/chapter/062-post-emma.tex
delete unnecessary files and rearange folder structure

--- 2023-03-10 Thesis/chapter/062-post-emma.tex
@@
 Thus, prediction for this data set are mainly extrapolations. 
+It must be explicitly noted at this point that pre-EMMA samples differ from EMMA samples 
+in the stabilization agent and therefore might underperform. 
 % inter/c/ pre-EMMA 5 pts
@@
 In the self test of the first two columns \gls{mars} is the one method to rule them all and provides the lowest metrics.
-But as soon as unseen data enters the field, linear regression excels by its simplicity. 
-\td{The linear regression method is only under cut by \gls{svm} when calculating the \gls{mae} of $\gamma$}
-for the interpolating unseen data (c).
+But as soon as unseen data is examined, linear regression excels by its simplicity. 
+%\td{The linear regression method is only undercut by \gls{svm} when calculating 
+%the \gls{mae} of $\gamma$} for the interpolating unseen data (c).
 %

### 2023-05-14 doc/Thesis/chapter/063-discussion.tex
delete unnecessary files and rearange folder structure

--- 2023-03-10 Thesis/chapter/063-discussion.tex
@@
 %\todo{ include last phase into previous section}
-This section will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
-Firstly, the 
-\ref{sec:phase1} \textit{\nameref{sec:phase1}}%
-, followed by the 
-\ref{sec:phase2} \textit{\nameref{sec:phase2}}%
+This section will discuss mistakes, improvements and lessons learned from each phase of this project. % in chronological order. 
+Firstly,
+the \nameref{sec:phase1} will be discussed in subsection \ref{sec:phase1}, 
+followed by the \nameref{sec:phase2} reviewd in subsection \ref{sec:phase2} 
 %, thereupon the 
- and finally the 
-\ref{sec:phase3} \textit{\nameref{sec:phase3}}%
+and finally the \nameref{sec:phase3} examined in subsection \ref{sec:phase3}.
 %\ref{sec:phase3} \textit{\nameref{sec:phase4}}%
- will be discussed.
+% will be discussed.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Scrutinize everything!} At the beginning of a project it is important 
-to get a ``feel''. I took the first recipe as only true recipe and tried to tune it to perfection. 
-The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
-I only noticed this after trying out another recipe. 
-My tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
-This will get you a ``feel'' of what works and what does not. 
-Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
-Check what works, collect (dis-)advantages of methods and combine the best approaches. 
+to get a ``feel''. 
+I took the first recipe as only true recipe and tried to tune it to perfection. 
+The problem was that the base line of that recipe was so low such that 
+improving the recipe still lead to poor performance.
+%no matter how much I improved it, it was still bad. 
+This was only noticed this after trying out another recipe. 
+The author's tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever can be. 
+This will 
+make it possible to acquire 
+%get you a 
+``feel'' of what works and what does not. 
+%Thinking back to some design classes I took with \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir} for data visualization: 
+This is inspired by a quote from \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir}'s 
+data visualization classes: ``create as many and different designs as possible''.
+One should check what works, collect (dis-)advantages of methods and combine the best approaches. 
 This can save you a lot of time.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Optimization, modelling and data generation}
+\subsection{Optimization, modelling and data generation phase}
 \label{sec:phase3}

### 2023-05-14 Data/I-V/I-V_131_2021_01_20/stat.py

@@ -1,52 +1,0 @@
-import pandas as pd
-import numpy as np
-import os
-def get_sample_name():
-    path=os.getcwd()
-    dirname=path.split("/")[-1]
-    name=dirname.split("_")[1]
-    return name
-def get_conductance(filename):
-    df=pd.read_csv(filename,"\t",header=36,names=("V","I","i","J","j"))
-    i=0
-    j=-1
-    dv= (df["V"].iloc[j]-df["V"].iloc[i])
-    di= (df["I"].iloc[j]-df["I"].iloc[i])
-    R = dv/di
-    G = di/dv
-    return G
-def get_header():
-    return "exp\tconductance [S]"
-def get_Gheader():
-    return "exp\tcount"
-def get_files(sample_name):
-    measurements = filter(lambda measurment: sample_name in measurment, os.listdir())
-    return sorted(list(measurements))
-def get_measurement():
-    return 
-def make_stat(G):
-    mini=0
-    maxi=13
-    stat=np.repeat(0,maxi-mini)
-    n = len(G)
-    for i in range(mini,maxi):
-        #stat[i]=(np.absolute(np.around(np.log10(G))) == i).sum()
-        stat[i]=(np.absolute((np.log10(G)).astype(int)) == i).sum()/n*100
-        print(i,stat[i],sep="\t")
-    return stat
-
-#######################
-#print(get_header())
-sample_name = get_sample_name()
-Gs=[]
-for filename in get_files(sample_name):
-#filename="131_Ag_Ag_01"
-    G=get_conductance(filename)
-    Gs.append(G)
-#    print(filename,get_conductance(filename),sep="\t")
-print(get_Gheader())
-make_stat(Gs)
-#print(Gs)
-
-#print(get_sample_name())
-#print("G ",G)

### 2023-05-14 Data/I-V/I-V_131_2021_01_20/test.sh

@@ -1,1 +1,0 @@
-cp ../stat.py .

### 2023-05-14 Data/I-V/I-V_158_2021_02_26/stata.py

@@ -1,67 +1,0 @@
-import pandas as pd
-import numpy as np
-import os
-def get_sample_name():
-    path=os.getcwd()
-    dirname=path.split("/")[-1]
-    name=dirname.split("_")[1]
-    return name
-def get_conductance(filename):
-    n_comments=40
-    for r in range(n_comments):
-        try:
-            print(r)
-            df=pd.read_csv(filename,"\t",header=n_comments,names=("V","I","i","J","j"))
-        except:
-            print("except")
-            pass
-        else:
-            print("else")
-            break
-    i=0
-    j=-1
-    dv= (df["V"].iloc[j]-df["V"].iloc[i])
-    di= (df["I"].iloc[j]-df["I"].iloc[i])
-    R = dv/di
-    G = di/dv
-    return G
-def get_header():
-    return "exp\tconductance [S]"
-def get_Gheader():
-    return "exp\tcount"
-def get_files(sample_name):
-    measurements = filter(lambda measurment: sample_name in measurment, os.listdir())
-    return sorted(list(measurements))
-def get_measurement():
-    return 
-def make_stat(G):
-    mini=0
-    maxi=13
-    stat=np.repeat(0,maxi-mini)
-    n = len(G)
-    for i in range(mini,maxi):
-        #stat[i]=(np.absolute(np.around(np.log10(G))) == i).sum()
-        stat[i]=(np.absolute((np.log10(G)).astype(int)) == i).sum()/n*100
-        print(i,stat[i],sep="\t")
-    return stat
-
-#######################
-def main():
-    #print(get_header())
-    sample_name = get_sample_name()
-    Gs=[]
-    for filename in get_files(sample_name):
-    #filename="131_Ag_Ag_01"
-        print(filename)
-        G=get_conductance(filename)
-        Gs.append(G)
-    #    print(filename,get_conductance(filename),sep="\t")
-    print(get_Gheader())
-    make_stat(Gs)
-    #print(Gs)
-
-    #print(get_sample_name())
-    #print("G ",G)
-
-if __name__ == "__main__":
-    main()

### 2023-05-14 Data/I-V/all_make.sh

@@ -1,10 +1,0 @@
-#USAGE ./all_make.sh
-for dir in $(ls -1 | grep -e "I-V*"); do 
-#	echo $dir
-	cd $dir
-#	pwd
-#	ls ..
-	bash ../make_log_i-v.sh . > i-v-log.gp
-	gnuplot i-v-log.gp
-	cd .. 
-done

### 2023-05-14 Data/I-V/all_stat.sh

@@ -1,7 +1,0 @@
-for dir in $(ls -1 | grep -e "I-V*"); do 
-	cd $dir
-#	pwd
-	python3 ../stat.avg.py #> stat.dat
-#	python3 ../stat.py #> stat.dat
-	cd .. 
-done

### 2023-05-14 Data/I-V/comment_dir.sh

@@ -1,5 +1,0 @@
-path=$1
-for file in $(ls $path -I *.png -I *.gp); do
-	sed -i "1,36s/^/#/" $file
-#	echo $file
-done

### 2023-05-14 Data/I-V/cp_pics.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-for dir in $(ls | grep -e "2021"); do
-	echo $dir
-	cp $dir/log-i-v.png pictures/$dir.png
-	echo $dir.png
-done

### 2023-05-14 Data/I-V/make_log_i-v.sh

@@ -1,38 +1,0 @@
-#!/bin/bash
-# USAGE: bash ../make_log_i-v.sh . > i-v-log.gp
-pth=$1
-lines=($(echo $(ls -1 $pth/*L*C* ) | tr ";" "\n"))
-no_lines=${#lines[@]}
-i=0
-png=1
-
-#### SETTINGS HEAD
-echo "set xrange [-0.5:0.5]"
-echo "set logscale y"
-echo 'set xlabel "voltage [V]"'
-echo 'set ylabel "current [A]"'
-if [ $png -eq 1 ]; then 
-	echo "set term pngcairo size 1200, 900 font \",30\""
-	echo "set out \"log-i-v.png\""
-fi
-
-
-using='u 1:(abs($2))'
-style="w l t \"\""
-for line in ${lines[@]}; do 
-	((i+=1))
-#	echo $1
-	if [ $i -eq 1 ]; then 
-		echo "plot \"$line\" $using $style ,\\"
-	elif [ $i -eq $no_lines  ]; then 
-		echo -e "\t\"$line\" $using $style "
-	else
-		echo -e "\t\"$line\" $using $style ,\\"
-	fi
-done
-
-if [ ! $png -eq 1 ]; then 
-	echo pause -1
-fi
-exit 0
-

### 2023-05-14 Data/I-V/mod_stat.py

@@ -1,1 +1,0 @@
-stat.py

### 2023-05-14 Data/I-V/mytou.sh

@@ -1,12 +1,0 @@
-#!/bin/zsh
-
-for dir in I-V*;  do
-#for dir in I-V_201*;  do
-    pushd $dir
-    for file in  *L*; do 
-#    for file in  *L1C1_04; do 
-        sed "s/µ/u/" <<< $( iconv -f ISO-8859-1 -t UTF-8 $file)  > $file
-    done
-    popd
-done
-

### 2023-05-14 Data/I-V/plot-single-ivs.sh

@@ -1,21 +1,0 @@
-#!/bin/bash 
-
-if [ "x" ==  "x$1" ] ; 
-then 
-	echo "USAGE: ./plot-single-iv.sh I-V_146_2021_02_03" ; exit 1  
-fi 
-pushd $1
-mkdir -p tmp 
-pushd tmp 
-for i in $(ls ../*L*C*) ; do 
-	echo "
-	set term pngcairo size 1200, 900 font \",30\"
-	set xlabel \"voltage [V]\"
-	set ylabel \"current [A]\"
-	set out \"$i.png\"
-	set xrange [-0.5:0.5]
-	plot \"$i\" w l notitle" > plot.gp ; 
-	gnuplot plot.gp ; 
-	mv $i.png . 
-done
-rm plot.gp ; 

### 2023-05-14 Data/I-V/show_stats.sh

@@ -1,2 +1,0 @@
-feh $(ls */stat.png)                                  │
-

### 2023-05-14 Data/I-V/stat.avg.py

@@ -1,134 +1,0 @@
-import pandas as pd
-import numpy as np
-from math import ceil
-import os
-def get_sample_name():
-    path=os.getcwd()
-    dirname=path.split("/")[-1]
-    name=dirname.split("_")[1]
-    no=dirname.split("_")[2]
-    return name,no
-def get_conductance(filename):
-    n_comments=40
-#    print(filename)
-    for r in range(n_comments):
-#        print(r)
-        try:
-            df=pd.read_csv(filename,sep="\t",header=r,names=("V","I","i","J","j"))
-            #df=pd.read_csv(filename,sep="\t",header=0,names=("V","I","absI","J","jcm"))
-            #df=pd.read_csv(filename,sep="\t",names=("V","I","absI","J","jcm"))
-        except:
-            pass
-#            print("could not read",filename)
-        else:
-#            print(df)
-            i=0             #first 
-            j=len(df)-1     #last
-            #TODO find pos at which V=0
-            zero=np.where( df["V"] == 0)
-            zero=ceil(j/2)
-            vdown=0
-            vup=0
-            idown=0
-            iup=0
-            d=2 #distance from zero
-            s=5 # how many for avg 
-            for i in range(1,j):
-                if i+d+s < zero and i+s < zero:
-                    vdown=vdown + float(df["V"][i])
-                    idown=idown + float(df["I"][i])
-                if i-d-s < zero and i-s < zero:
-                    vup=vup + float(df["V"][i])
-                    iup=iup + float(df["I"][i])
-                dv= vup-vdown
-                di= iup-idown
-                i=i+1
-                j=j-1
-#            print(dv,di)
-            R = dv/di
-            G = di/dv
-            return np.absolute(G)
-    return 1    # if error with file reading
-def get_header():
-    return "exp\tconductance [S]"
-def get_Gheader():
-    return "exp\t%\tcount"
-def get_files(sample_name):
-    all_files = os.listdir()
-#    print(all_files)
-    measurements = filter(lambda measurment: sample_name in measurment, all_files)   # only return files with sample number in name
-    measurements = filter(lambda measurment: "Ag" not    in measurment, measurements)   # don't include Ag files
-    #TODO: only highest 
-    return sorted(list(measurements))
-def get_measurement():
-    return 
-def make_stat(G):
-    mini=1
-    maxi=13
-    stat=np.repeat(0,maxi)#-mini)
[…]

### 2023-05-14 Data/I-V/stat.py

@@ -1,126 +1,0 @@
-import pandas as pd
-import numpy as np
-from math import ceil
-import os
-def get_sample_name():
-    path=os.getcwd()
-    dirname=path.split("/")[-1]
-    name=dirname.split("_")[1]
-    no=dirname.split("_")[2]
-    return name,no
-def get_conductance(filename):
-    n_comments=40
-#    print(filename)
-    for r in range(n_comments):
-        try:
-            df=pd.read_csv(filename,"\t",header=r,names=("V","I","i","J","j"))
-        except:
-            pass
-            #print("could not read",filename)
-        else:
-#            break
-            i=0             #first 
-            j=len(df)-1     #last
-#            print(j)
-            #TODO find pos at which V=0
-            zero=np.where( df["V"] == 0)
-            zero=ceil(j/2)
-#            print(df["V"][zero+1])
-#            print(zero )
-            # find prev 5-10 i and v and make avg 
-            # find past 5-10 i and v and make avg 
-            vdown=0
-            vup=0
-            idown=0
-            iup=0
-            d=2 #distance from zero
-            s=5 # how many for avg 
-#            while i < j:
-            for i in range(1,j):
-                if i+d+s < zero and i+s < zero:
-                    vdown=vdown + float(df["V"][i])
-                    idown=idown + float(df["I"][i])
-                if i-d-s < zero and i-s < zero:
-                    vup=vup + float(df["V"][i])
-                    iup=iup + float(df["I"][i])
-                dv= vup-vdown
-                di= iup-idown
-#                dv= (df["V"].iloc[j]-df["V"].iloc[i])
-#                di= (df["I"].iloc[j]-df["I"].iloc[i])
-                i=i+1
-                j=j-1
-            R = dv/di
-            G = di/dv
-#            print(G)
-            return np.absolute(G)
-    return 1    # if error with file reading
-def get_header():
-    return "exp\tconductance [S]"
-def get_Gheader():
-    return "exp\t%\tcount"
-def get_files(sample_name):
-    all_files = os.listdir()
-#    print(all_files)
-    measurements = filter(lambda measurment: sample_name in measurment, all_files)   # only return files with sample number in name
[…]

### 2023-05-14 Data/I-V/uncomment_file.sh

@@ -1,2 +1,0 @@
-file=$1
-sed -i "s/^#//" $file 

### 2023-05-14 Data/Predictions/EMMA/getdata.sh

@@ -1,47 +1,0 @@
-#!/bin/bash
-
-all=9000
-conclvl=4; conck=2
-layrlvl=5; layrk=3
-vdoclvl=6; vdock=4
-tdoclvl=5; tdock=5
-vcallvl=5; vcalk=6
-tcallvl=3; tcalk=7
-
-filename=allspace.dat
-lines=$(wc -l $filename | awk '{print $1}')
-
-ffpp=/tmp/fifopipe
-touch $ffpp-1
-touch $ffpp-2
-touch $ffpp-3
-touch $ffpp-4
-touch $ffpp-5
-touch $ffpp-6
-touch $ffpp-7
-touch $ffpp-8
-touch $ffpp-9
-touch $ffpp-0
-
-part=$all
-head -n1 $filename 
-
-tail -n $(($lines-1)) $filename > $ffpp-1 & \
-	sort -hk $layrk $ffpp-1 > $ffpp-2 && part=$(($part/$layrlvl)) && head -n $(($part*5)) $ffpp-2 | tail -n $part > $ffpp-3 && \
-	sort -hk $vdock $ffpp-3 > $ffpp-4 && part=$(($part/$vdoclvl)) && head -n $(($part*1)) $ffpp-4 | tail -n $part > $ffpp-5 && \
-	sort -hk $tdock $ffpp-5 > $ffpp-6 && part=$(($part/$tdoclvl)) && head -n $(($part*1)) $ffpp-6 | tail -n $part > $ffpp-7 && \
-	sort -hk $vcalk $ffpp-7 > $ffpp-8 && part=$(($part/$vcallvl)) && head -n $(($part*1)) $ffpp-8 | tail -n $part > $ffpp-9 && \
-	sort -hk $tcalk $ffpp-9 > $ffpp-0 && part=$(($part/$tcallvl)) && head -n $(($part*2)) $ffpp-0 | tail -n $part 
-
-rm $ffpp-1
-rm $ffpp-2
-rm $ffpp-3
-rm $ffpp-4
-rm $ffpp-5
-rm $ffpp-6
-rm $ffpp-7
-rm $ffpp-8
-rm $ffpp-9
-rm $ffpp-0
-exit 
-

### 2023-05-14 data/I-V/I-V_158_2021_02_26/stata.py

@@ -1,0 +1,67 @@
+import pandas as pd
+import numpy as np
+import os
+def get_sample_name():
+    path=os.getcwd()
+    dirname=path.split("/")[-1]
+    name=dirname.split("_")[1]
+    return name
+def get_conductance(filename):
+    n_comments=40
+    for r in range(n_comments):
+        try:
+            print(r)
+            df=pd.read_csv(filename,"\t",header=n_comments,names=("V","I","i","J","j"))
+        except:
+            print("except")
+            pass
+        else:
+            print("else")
+            break
+    i=0
+    j=-1
+    dv= (df["V"].iloc[j]-df["V"].iloc[i])
+    di= (df["I"].iloc[j]-df["I"].iloc[i])
+    R = dv/di
+    G = di/dv
+    return G
+def get_header():
+    return "exp\tconductance [S]"
+def get_Gheader():
+    return "exp\tcount"
+def get_files(sample_name):
+    measurements = filter(lambda measurment: sample_name in measurment, os.listdir())
+    return sorted(list(measurements))
+def get_measurement():
+    return 
+def make_stat(G):
+    mini=0
+    maxi=13
+    stat=np.repeat(0,maxi-mini)
+    n = len(G)
+    for i in range(mini,maxi):
+        #stat[i]=(np.absolute(np.around(np.log10(G))) == i).sum()
+        stat[i]=(np.absolute((np.log10(G)).astype(int)) == i).sum()/n*100
+        print(i,stat[i],sep="\t")
+    return stat
+
+#######################
+def main():
+    #print(get_header())
+    sample_name = get_sample_name()
+    Gs=[]
+    for filename in get_files(sample_name):
+    #filename="131_Ag_Ag_01"
+        print(filename)
+        G=get_conductance(filename)
+        Gs.append(G)
+    #    print(filename,get_conductance(filename),sep="\t")
+    print(get_Gheader())
+    make_stat(Gs)
+    #print(Gs)
+
+    #print(get_sample_name())
+    #print("G ",G)
+
+if __name__ == "__main__":
+    main()

### 2023-05-14 data/I-V/comment_dir.sh

@@ -1,0 +1,5 @@
+path=$1
+for file in $(ls $path -I *.png -I *.gp); do
+	sed -i "1,36s/^/#/" $file
+#	echo $file
+done

### 2023-05-14 data/I-V/cp_pics.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+for dir in $(ls | grep -e "2021"); do
+	echo $dir
+	cp $dir/log-i-v.png pictures/$dir.png
+	echo $dir.png
+done

### 2023-05-14 data/I-V/make_log_i-v.sh

@@ -1,0 +1,38 @@
+#!/bin/bash
+# USAGE: bash ../make_log_i-v.sh . > i-v-log.gp
+pth=$1
+lines=($(echo $(ls -1 $pth/*L*C* ) | tr ";" "\n"))
+no_lines=${#lines[@]}
+i=0
+png=1
+
+#### SETTINGS HEAD
+echo "set xrange [-0.5:0.5]"
+echo "set logscale y"
+echo 'set xlabel "voltage [V]"'
+echo 'set ylabel "current [A]"'
+if [ $png -eq 1 ]; then 
+	echo "set term pngcairo size 1200, 900 font \",30\""
+	echo "set out \"log-i-v.png\""
+fi
+
+
+using='u 1:(abs($2))'
+style="w l t \"\""
+for line in ${lines[@]}; do 
+	((i+=1))
+#	echo $1
+	if [ $i -eq 1 ]; then 
+		echo "plot \"$line\" $using $style ,\\"
+	elif [ $i -eq $no_lines  ]; then 
+		echo -e "\t\"$line\" $using $style "
+	else
+		echo -e "\t\"$line\" $using $style ,\\"
+	fi
+done
+
+if [ ! $png -eq 1 ]; then 
+	echo pause -1
+fi
+exit 0
+

### 2023-05-14 data/I-V/mytou.sh

@@ -1,0 +1,12 @@
+#!/bin/zsh
+
+for dir in I-V*;  do
+#for dir in I-V_201*;  do
+    pushd $dir
+    for file in  *L*; do 
+#    for file in  *L1C1_04; do 
+        sed "s/µ/u/" <<< $( iconv -f ISO-8859-1 -t UTF-8 $file)  > $file
+    done
+    popd
+done
+

### 2023-05-14 data/I-V/plot-single-ivs.sh

@@ -1,0 +1,21 @@
+#!/bin/bash 
+
+if [ "x" ==  "x$1" ] ; 
+then 
+	echo "USAGE: ./plot-single-iv.sh I-V_146_2021_02_03" ; exit 1  
+fi 
+pushd $1
+mkdir -p tmp 
+pushd tmp 
+for i in $(ls ../*L*C*) ; do 
+	echo "
+	set term pngcairo size 1200, 900 font \",30\"
+	set xlabel \"voltage [V]\"
+	set ylabel \"current [A]\"
+	set out \"$i.png\"
+	set xrange [-0.5:0.5]
+	plot \"$i\" w l notitle" > plot.gp ; 
+	gnuplot plot.gp ; 
+	mv $i.png . 
+done
+rm plot.gp ; 

### 2023-05-14 data/I-V/stat.avg.py

@@ -1,0 +1,134 @@
+import pandas as pd
+import numpy as np
+from math import ceil
+import os
+def get_sample_name():
+    path=os.getcwd()
+    dirname=path.split("/")[-1]
+    name=dirname.split("_")[1]
+    no=dirname.split("_")[2]
+    return name,no
+def get_conductance(filename):
+    n_comments=40
+#    print(filename)
+    for r in range(n_comments):
+#        print(r)
+        try:
+            df=pd.read_csv(filename,sep="\t",header=r,names=("V","I","i","J","j"))
+            #df=pd.read_csv(filename,sep="\t",header=0,names=("V","I","absI","J","jcm"))
+            #df=pd.read_csv(filename,sep="\t",names=("V","I","absI","J","jcm"))
+        except:
+            pass
+#            print("could not read",filename)
+        else:
+#            print(df)
+            i=0             #first 
+            j=len(df)-1     #last
+            #TODO find pos at which V=0
+            zero=np.where( df["V"] == 0)
+            zero=ceil(j/2)
+            vdown=0
+            vup=0
+            idown=0
+            iup=0
+            d=2 #distance from zero
+            s=5 # how many for avg 
+            for i in range(1,j):
+                if i+d+s < zero and i+s < zero:
+                    vdown=vdown + float(df["V"][i])
+                    idown=idown + float(df["I"][i])
+                if i-d-s < zero and i-s < zero:
+                    vup=vup + float(df["V"][i])
+                    iup=iup + float(df["I"][i])
+                dv= vup-vdown
+                di= iup-idown
+                i=i+1
+                j=j-1
+#            print(dv,di)
+            R = dv/di
+            G = di/dv
+            return np.absolute(G)
+    return 1    # if error with file reading
+def get_header():
+    return "exp\tconductance [S]"
+def get_Gheader():
+    return "exp\t%\tcount"
+def get_files(sample_name):
+    all_files = os.listdir()
+#    print(all_files)
+    measurements = filter(lambda measurment: sample_name in measurment, all_files)   # only return files with sample number in name
+    measurements = filter(lambda measurment: "Ag" not    in measurment, measurements)   # don't include Ag files
+    #TODO: only highest 
+    return sorted(list(measurements))
+def get_measurement():
+    return 
+def make_stat(G):
+    mini=1
+    maxi=13
+    stat=np.repeat(0,maxi)#-mini)
[…]

### 2023-05-14 data/Predictions/EMMA/getdata.sh

@@ -1,0 +1,47 @@
+#!/bin/bash
+
+all=9000
+conclvl=4; conck=2
+layrlvl=5; layrk=3
+vdoclvl=6; vdock=4
+tdoclvl=5; tdock=5
+vcallvl=5; vcalk=6
+tcallvl=3; tcalk=7
+
+filename=allspace.dat
+lines=$(wc -l $filename | awk '{print $1}')
+
+ffpp=/tmp/fifopipe
+touch $ffpp-1
+touch $ffpp-2
+touch $ffpp-3
+touch $ffpp-4
+touch $ffpp-5
+touch $ffpp-6
+touch $ffpp-7
+touch $ffpp-8
+touch $ffpp-9
+touch $ffpp-0
+
+part=$all
+head -n1 $filename 
+
+tail -n $(($lines-1)) $filename > $ffpp-1 & \
+	sort -hk $layrk $ffpp-1 > $ffpp-2 && part=$(($part/$layrlvl)) && head -n $(($part*5)) $ffpp-2 | tail -n $part > $ffpp-3 && \
+	sort -hk $vdock $ffpp-3 > $ffpp-4 && part=$(($part/$vdoclvl)) && head -n $(($part*1)) $ffpp-4 | tail -n $part > $ffpp-5 && \
+	sort -hk $tdock $ffpp-5 > $ffpp-6 && part=$(($part/$tdoclvl)) && head -n $(($part*1)) $ffpp-6 | tail -n $part > $ffpp-7 && \
+	sort -hk $vcalk $ffpp-7 > $ffpp-8 && part=$(($part/$vcallvl)) && head -n $(($part*1)) $ffpp-8 | tail -n $part > $ffpp-9 && \
+	sort -hk $tcalk $ffpp-9 > $ffpp-0 && part=$(($part/$tcallvl)) && head -n $(($part*2)) $ffpp-0 | tail -n $part 
+
+rm $ffpp-1
+rm $ffpp-2
+rm $ffpp-3
+rm $ffpp-4
+rm $ffpp-5
+rm $ffpp-6
+rm $ffpp-7
+rm $ffpp-8
+rm $ffpp-9
+rm $ffpp-0
+exit 
+

### 2023-10-17 doc/Thesis/chapter/01-introduction.tex
corrected until comp details

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Photovoltaics (PV) is one viable option when becoming carbon neutral. 
+Photovoltaics (PV) is one viable option for becoming carbon neutral. 
 Furthermore, 
@@
 One sort of PV are CIGS (copper indium gallium sulfide) cells\cite{Vasekar2010}. 
-Due to their large absorption coefficient, less material is needed and they can be made thinner and flexible. 
+Due to their large absorption coefficient (compared to silicon based cells), less material is needed and they can be made thinner and flexible. 
 %\td{was sind vorteile?}
@@
 %\td{influence} of the production factors on the thickness and resistance of the resulting layer.
-The minimization of the conductance is performed with a particle swarm optimization 
+The minimization of the conductance of the layer is performed with a particle swarm optimization 
 algorithm. 
@@
 In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
-Section \ref{sec:results} is split into three sections: material specific results are presented in section \ref{sec:res-mat}, results regarding particle swarm optimization in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
+Section \ref{sec:results} is split into four sections: material specific results are presented in section \ref{sec:res-mat}, results regarding particle swarm optimization in section \ref{sec:res-emma}, further analysis in section \ref{sec:res-post-emma} and discussion of the process and the results in \ref{sec:res-discussion}.
 Finally, chapter \ref{sec:outlook} summarizes and discusses the outlook and next steps.

### 2023-10-17 doc/Thesis/chapter/030-theory-materials.tex
corrected until comp details

--- 2023-03-05 Thesis/chapter/030-theory-materials.tex
@@
 \subsection{Photovoltaics Basics}
-The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
+The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in human made \gls{pv} or in plants): 
 the creation of an electron-hole pair and then its separation by the structure of the material\cite{markvart2013principles}.
@@
 In figure \ref{fig:cigs} the schematic layer sequence of a standard \gls{cigs} thin film cell is shown. 
-Typically a \um{1} thick molybdenum layer is deposited on soda lime glass. 
+Typically, a \um{1} thick molybdenum layer is deposited on soda lime glass. 
 The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in 112 direction\cite{hedstrom1993cigs}.
@@
 \ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
-The \ch{ZnO} window layer (usually of thickness 50-\nm{70} is highly conductive (especially the \ch{Al} doped layer) and acts as front contact.
+The \ch{ZnO} window layer (usually of thickness 50-\nm{70} is highly conductive (especially the aluminium doped layer) and acts as front contact.
 
@@
 They both come with their own inconveniences. 
-Plastics generally have very low melting points which restrict preparation temperatures.
+Plastics generally have very low melting points which restrict preparation temperatures of \gls{cigs}.
 Steel, on the other hand, is temperature resistant enough, but is an electric conductor. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Sol-Gel and Doctor Blading}
+%\subsection{Sol-Gel and Doctor Blading}
+\subsection{Doctor Blading}
 %\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
@@
 A more detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}. 
-\Gls{sem} is a microscopical technique which allows visualisation of surfaces with features in the nano meter regime. 
+\Gls{sem} is a microscopical technique which allows visualization of surfaces with features in the nano meter regime. 
 While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
-This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to visible light\cite{Kaliva2020}.
+This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to photons of visible light\cite{Kaliva2020}.
 The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons in the examined material. 
-Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
+Secondary electrons carry information to conclude morphology and topology of the sample, while X-rays can be used to identify the elements. 
 Electrons originate from either a \gls{feg}, where a strong electrical field rips electrons from the bulk, or from thermionic guns where a filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted.
@@
 \Gls{uv}/\gls{vis}/\gls{nir} spectroscopy is a molecular spectroscopic method using 
-interactions of \gls{uv}, \gls{vis} and \gls{nir} light 
+interactions of \gls{uv}/\gls{vis}/\gls{nir} light 
 (wavelengths of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
@@
 The electron will then be excited into a energetically higher orbital.
-Secondly, the spin state of both states has to be the same otherwise the transition is "forbidden" and the absorption is extremely unlikely.
+Secondly, the spin state of both states has to be the same otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely.
 
@@
 Only vibrations that change the dipole moment of the molecule are \gls{ir} active. 
-The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes which lead to intricate patterns called the fingerprint region. 
-These transition are mostly "forbidden" quantum mechanically and allow analysis of bulk matter without extensive preparation
+The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes which lead to intricate patterns in the so called fingerprint region.
+These transition are mostly "forbidden" and allow analysis of bulk matter without extensive preparation
 due to the deep penetration depth of \gls{nir} light\cite{bec2019breakthrough}.
@@
 In the classic two-beam-spectrometer the light emitted from the light source is split, 
-sent through the sample and the reference and one of the two beams is alternately 
+sent through the sample and the reference, and one of the two beams is alternately 
 sent through a monochromator to a detector (often a thermopile).

### 2023-10-17 doc/Thesis/chapter/031-theory-calculations.tex
corrected until comp details

--- 2023-03-10 Thesis/chapter/031-theory-calculations.tex
@@
 %What is \gls{ml}? 
-Some might argue that \gls{ml} is just overglorified statistics, but that's not the case. 
+Some might argue that \gls{ml} is just overglorified statistics, but that is not the case. 
 Although \gls{ml} uses several statistical methods, their goal and frame conditions are different. 
@@
 The \gls{rf} is developed in a forward/backward stepwise recursive manner\cite{friedman1988fitting}. 
-During the forward recursion terms are added in pairs until a certain number of terms is reached. 
+During the forward recursion, terms are added in pairs until a certain number of terms is reached. 
 Each pair consists of two hinge functions (also called rectifier functions) multiplied with a term already part of the \gls{rf} (including the constant term).

### 2023-10-17 doc/Thesis/chapter/033-linreg-krr-svm.tex
corrected until comp details

--- 2023-03-10 Thesis/chapter/033-linreg-krr-svm.tex
@@
 A~kernel transforms data in such a way that a linear hyperplane (a point in one dimension, a line in two dimensions, 
-a plane in three dimensions) can fit data in regression problems or separate the data in classification problems without actually doing the transormation for every data point, which lowers computational costs.
+a plane in three dimensions) can fit data in regression problems or separate the data in classification problems without actually doing the transformation for every data point, which lowers computational costs.
 A kernel is some kind of similarity measure 
@@
 %
-The \gls{svm} was initially developed by Vladimir Vapnik for the binary classification of separable data, then improved to handle non-separable data and eventually adapted to solve regression problems.
+The \gls{svm} was initially developed by Vladimir Vapnik for the binary classification of separable data, then improved to handle non-separable data\cite{cortes1995support} and eventually adapted to solve regression problems\cite{drucker1996support}.
 The concepts of \gls{svm} will be discussed in the same chronological order. 
@@
 %\td{draw sketch and make \ref{eq:svm02} on two lines}
-Thus maximizing the margin is equivalent with minimizing $\|\mathbf{w}\|$ and minimizing $\frac{1}{2}\|\mathbf{w}\|^2$ (mathematical convenience for further steps).
+Thus, maximizing the margin is equivalent with minimizing $\|\mathbf{w}\|$ and minimizing $\frac{1}{2}\|\mathbf{w}\|^2$ (mathematical convenience for further steps).
 By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we 
-mathemagically arrive at the loss function which should be maximized: 
+\textit{mathemagically} arrive at the loss function which should be maximized: 
 \begin{equation}
@@
 $\frac{\partial \mathfrak{L}}{\partial \mathbf{w}}$ and $\frac{\partial \mathfrak{L}}{\partial b}$ 
-to zero and inserting into eq. (\ref{eq:svm03}))\cite{winston1992artificial,cherkassky1998learning}: 
+to zero and inserting into eq. (\ref{eq:svm03}))\cite{winston1992artificial,cherkassky1998learning} in the following way: 
 \begin{equation}
@@
 	\label{eq:svm-soft}
-	L_{SM} = \frac{1}{2} \|\mathbf{w}\|^2 + \sum_i^n max(0, 1- y_i ( \mathbf{w} \mathbf{x}_i + b ) 
+	L_{SM} = \frac{1}{2} \|\mathbf{w}\|^2 + \sum_i^n max \left( 0, 1- y_i ( \mathbf{w} \mathbf{x}_i + b ) \right) 
 \end{equation}
-If the prediction $\mathbf{w}\mathbf{x}_i+b$ and the true category $y_i$ don't agree, 
+If the prediction $(\mathbf{w}\mathbf{x}_i+b)$ and the true category $y_i$ don't agree, 
 they have opposite signs and their product will be a negative number.
-The substraction of a negative number will result in a positive penalizization. 
+The substraction of a negative number will result in a positive penalization. 
 If the sample is correctly predicted, the product will result in a positive number, 
-the substraction will lead to a negative number and the maximum will be 0, if the sample is ousite of the margin. 
+the substraction will lead to a negative number and the maximum will be 0 if the sample is ousite of the margin. 
 %
@@
 This allows us to separate data not only by hyperplanes 
-but also by complex decision boundaries due to the kernel trick. 
+but also by intricate decision boundaries due to the kernel trick. 
 Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the innerproduct of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper.

### 2023-10-17 doc/Thesis/chapter/04-experimental.tex
corrected until comp details

--- 2023-03-10 Thesis/chapter/04-experimental.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this section the used chemicals and substrates, experimental procedures and any used 
+In this section the used chemicals, substrates, experimental procedures and any used
 equipment are described. 
 %\td{Also, the long, exhaustive path to the base solution is described}
-The experiments can be split into three sections: 
+\td{The experiments can be split into three sections: }
 In the first section the base recipe and the base process were sought. 
@@
 Five different concentrations of the buthanolic solutions were prepared. 
+Not all chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
+starting materials had to be chosen from the available inventory. 
 The \gls{1f} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
 The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar with 
-higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
+but higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
 with the aim of producing thicker layers.
-Not all chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
-starting materials had to be chosen from the available inventory. 
 %\td{p34}
@@
 precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
-complex aluminium isopropoxide), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol), reaction temperature 
+complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
 (room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
@@
 %Most steel substrates (all pre-optimization and optimization samples) 
-All steel substrates 
+%All 
+Steel substrates 
 were doctor bladed with 
 an Erichsen Coatmaster 510 film applicator with a heatable plate.
-The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
-partially heated with a heat gun.
+%The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
+%partially heated with a heat gun.
 The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in 
@@
 %
-Eventually, a heatable vacuum plate was used. It 
+%Eventually, a heatable vacuum plate was used. It 
+The heatable vacuum plate
 had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where 
-underpressure could be applied to keep the substrate in place (see 
-figure~\ref{fig:eric}). 
-Most of them were covered with tape to increase the suction intensity at the remaining ones. 
+underpressure could be applied to keep the substrate in place. 
+Most of them were covered with tape to increase the suction intensity at the remaining ones (see figure~\ref{fig:eric}
 After setting the temperature of the heating plate to 
@@
 was switched on. 
-During pre-optimization samples, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
+During pre-optimization, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
 \mmps{1}, \mmps{2} and \mmps{5}) were tested. 
@@
 		(a)
-		Temperature regulator (1) on the left,
-		vacuum pump (2) in the background and 
-		Erichsen Coatmaster 510 film applicator (3) with heatable vacuum plate.
+		Temperature regulator (\underline{1}) on the left,
+		vacuum pump (\underline{2}) in the background and 
+		Erichsen Coatmaster 510 film applicator (\underline{3}) with heatable vacuum plate.
         (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\micro\meter}.
@@
 After the blade moved over the substrate the remaining liquid needed about a minute 
-to evaporate. 
+to evaporate at room temperature. 
 %\td{
@@
 reproducible. 
-The glass plate of the film applicator was therefore exchanged with a metal plate which 
+The \td{glass plate of the film applicator was therefore exchanged with a metal plate which}
 allowed to hold the sample in place through underpressure and simultaneously heat it to a certain 
@@
 The sample produced with \gls{ipo} as stabilization agent 
-showed comparable passivization results and better stability. 
-Therefore \gls{ipo} was used  as stabilization in further experiments.
-After the boundaries of the solution were fixed 
+showed comparable passivization results and better stability of the solution. 
+Therefore \gls{ipo} was used  as stabilzier in further experiments.
+\td{After the boundaries of the solution were fixed }
 the process variables to produce an insulating layer was examined. 
@@
 %\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
-See table \ref{tab:input} for the input space spanned during the optimization.
+\td{See} table \ref{tab:input} for the input space spanned during the optimization.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-10-17 doc/Thesis/chapter/05-computational-details.tex
corrected until comp details

@@
 For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
-5 points before and 5 points after the origin with at one point distance from zero (which boils
+5 points before and 5 points after the origin with \td{at one point distance from zero} (which boils
 down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
@@
 \end{equation}
+The density is 1 if every measurement has a conductance larger than $10^{-5} \, \Omega^{-1}$ and is 0 if every measured conductance has a value of smaller than $10^{-5} \, \Omega^{-1}$.
 %Other estimates of the conductance are the averages:
@@
 where $C$ and $\varepsilon$ took the values 0.05--1 with step size 0.05 %, $\varepsilon$ 0.05--4.0 with 0.2 steps 
-and was the same as for \gls{krr} plus \texttt{scale}. %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
+\td{and was the same as for \gls{krr} plus \texttt{scale}.} %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
 Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
@@
 The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
-of the \gls{emma} data set were scaled before each calculation.
+of the \gls{emma} data set were \td{scaled before each calculation.}
 % https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
@@
 For each calculation the 5-fold cross validation score was calculated. 
-The score equals to the coefficient of determination $R^2$ which defined the following for non linear regression functions:
+The score equals to the coefficient of determination $R^2$ which \td{ is defined the following for non linear regression functions:}
 \begin{equation}

### 2023-10-23 doc/Thesis/chapter/060-results-material.tex
start correct emma results

@@
-In this section the results will pe presented, explained and discussed. 
+In this section the results will be presented, explained and discussed. 
 Starting with physical measurements and material properties. 
 Followed by the presentation of the results obtain by optimization and exploration with the \gls{emma} method. 
-Finally, the results of alternative optimization methods were let loose on the data and compared with the \gls{emma} method.
+Finally, the results of alternative regression methods let loose on the data are compared with the \gls{emma} method.
 
@@
 %%%%%%%% AQUATIC 
-As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.\cite{Anwar2017} failed to produce a homogeneous layer. 
+As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer. 
 The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
-Altering the ratios of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't improve the resulting \gls{zro} layers. 
+Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't increase the resistance of the resulting \gls{zro} layers. 
 % ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
 % ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
-Even after the consecutive application of two layers, there was no improvement and the results reminded rather of a sparse crust than of a film. 
+Even after the consecutive application of two layers, there was no improvement and the results examined with \gls{sem} reminded rather of a sparse crust than of a film. 
 %It is assumed that the solution was far from the optimum for a sol-gel process. 
@@
 %%%%%% STABILITY
-As soon as the solution showed initial cloudiness, it was declared as unstable and no more used for \gls{db}. 
-The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
+As soon as the solution showed initial cloudiness, it was declared as unstable and used no more for \gls{db}. 
+The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent \gls{acoh} with \gls{ipo}.
 A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
@@
 Measuring the cross section on steel was not as straight forward because the ductility of steel prevents fractures of the substrate. 
-Resorting to scratching the surface with an diamond glass cutter allowed us to get an insight into the thickness of the layer on steel substrate.
+Resorting to scratching the surface with a diamond glass-cutter allowed us to get an insight into the thickness of the layer on steel substrate.
 %
@@
 Assuming that the raised structure resembling a tentacle is \gls{zro}, 
-the thickness of the layer can be estimated to be in the magnitude of several \nm{100}.
+the thickness of the layer can be estimated to be in the order of magnitude of \nm{100}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{XRD}
+\subsection{X-ray diffraction}
 \begin{figure}
@@
 Figure~\ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
-Each line represents a I-V measurement at a distinct aluminium contact applied by sputtering through a mask. 
+\td{Each line represents a I-V measurement at a distinct aluminium contact applied by sputtering through a mask. }
 All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 

### 2023-10-23 doc/Thesis/chapter/061-results-emma.tex
start correct emma results

@@
 %%% BEST PREDICTED RECIPE
-The best sample predicted by the algorithm is experiment number 13 with 
+The sample predicted as best by the algorithm is experiment number 13 with 
 lowest $c_{zr}$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$ and second highest $\lambda$. 
@@
 conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
-The points at generation number 0 indicate particles which were not included to be propagated. 
+The green points at generation number 0 indicate particles which were not included to be propagated. 
 %Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
-Violet lines connect individual particles in time, the blue line connects averages of particles of each generation and yellow lines connect average of only particles which were propagated of each generation.
+Violet lines connect individual particles in time. 
+The blue line connects averages of particles of each generation (including initial non-propagated particles) and 
+yellow lines connect averages of each generation of only those particles which were propagated. 
 %
@@
 and the chosen samples where not exactly as expected. 
-Neither expected were the measurements for these samples, which might be due to the high measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature or humidity.
-Measurements were expected to show clear correlation, which was only observed for $T_{cal}$.
+Neither expected were the measurements for these samples.
+The deviation from expectation might be due to high measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature, humidity or solution age. 
+Measurements were expected to show clear correlation of optimizands $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $\lambda$.
+The only statistically relevant correlation was observed for $T_{cal}$ with the optimizands.
 %\td{why}
 %
-In the scatter plots~\ref{fig:g-tcal} and \ref{fig:phd-tcal} the correlation of calcination temperature $T_{cal}$ with $\gamma$ and $\rho$ can be seen clearly.
+In the scatter plots~\ref{fig:g-tcal} and \ref{fig:phd-tcal} the correlation of calcination temperature~$T_{cal}$ with $\gamma$ and $\rho$ can be seen clearly.
 
@@
 		(c)~calculated conductance measures~$\gamma$ against calcination temperature $T_{cal}$
+		\td{
 		(d)~calculated pin hole density~$\rho$ against calcination temperature $T_{cal}$
+	change colors }
 		%\td{describe more in-depth in text}
@@
 % TCAL ON OPTIMIZANDS
-The influence of $T_{cal}$ on the measures of conductance ($\rho$ and $\gamma$) is highly interesting. 
+The influence of $T_{cal}$ on the measures of conductance ($\hat\rho$ and $\hat\gamma$) is highly interesting. 
 It was expected that 
-calcination temperatures under \oc{400} do not suffice to produce compact layers and 
-that therefore the resulting layer does not insulate as well. 
+calcination temperatures under \oc{400} do not suffice to produce compact layers (corresponding to $+h(400-T_{cal})$)
+and 
+that therefore the resulting layer does not insulate well if $T_{cal}$ is low. 
+%This would correspond to $+h(400-T_{cal})$
 The original recipe by Hu et al.\cite{Hu2016} used \oc{500} and thus even \oc{400} are low.
@@
 ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.
+
 %
 % DESCRIBE COEFFICIENTS
-Furthermore, the coefficient of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$; interestingly also on $\hat\lambda$ and $\hat{v}_{cal}$.
+Furthermore, the coefficient of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ (\ref{eq:emma-phd4}) and $\hat{\gamma}$ (\ref{eq:emma-G4}); interestingly also on $\hat\lambda$ (\ref{eq:emma-layr4}) and $\hat{v}_{cal}$ (\ref{eq:emma-vcal4}).
 The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 

### 2023-10-27 doc/Thesis/chapter/061-results-emma.tex
next up 063*.tex

@@
 the prediction functions (see equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal4})) 
-and the chosen samples where not exactly as expected. 
+and the chosen samples (i.e. chosen input variables) where not exactly as expected. 
 Neither expected were the measurements for these samples.
-The deviation from expectation might be due to high measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature, humidity or solution age. 
+The deviation from expectation might be due to measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature, humidity or solution age. 
 Measurements were expected to show clear correlation of optimizands $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $\lambda$.
@@
 	change colors }
-		%\td{describe more in-depth in text}
+	\td{increase font in gnuplot, change y-axis of (c)}
 	}
@@
 The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 
-but has the extra factor $\lambda$ (range: 4--12), resulting in the products of coefficients and process variables being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$.
+but has the extra factor $\lambda$ (range: 4--12), resulting in the products of coefficients and process variables being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$ terms.
 It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}). 
@@
 The process time optimization would be better placed in a follow up study. 
-The second reason for including independent variables was to check if the model works. 
+The second reason for including independent variables as \textit{optimizands} was to check if the model works. 
 This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimizands} and thus 
 additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables and chose future data points. 
-Moreover, $v_{cal}$ and $\lambda$ were only considered with 5\% weight. 
+Moreover, $v_{cal}$ and $\lambda$ were only considered with 5\% weight in the overall objective function.
 The second flaw is that there are obviously better methods to assess the quality of a model than to make it more complex. 

### 2023-10-27 doc/Thesis/chapter/062-post-emma.tex
next up 063*.tex

@@
 A one-way \gls{anova} was performed for every independent variable on $\rho$ and $\gamma$. 
-We used an $\alpha$ value of 0.05 which means that 
+We used an $\alpha$-value of 0.05 which means that 
 the null hypothesis is rejected if the p-value is under 0.05. 
@@
 Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
-In order to compare, the influence of an input variable was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{min}+x_{max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression.
+For better comparison, the influence of an input variable was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{i,min}+x_{i,max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression.
 %The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
 The biggest influence on $\hat\rho$ is  $\lambda$, followed by $T_{cal}$. 
-While $T_{cal}$ is the second largest influence on $\hat\rho$ as well it is noteworthy that $\lambda$ contributes the least to $\hat\gamma$. 
+While $T_{cal}$ is the second largest influence on $\hat\rho$ as well, it is noteworthy that $\lambda$ contributes the least to $\hat\gamma$. 
 That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
@@
 In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
-The range of the hyperparameter $\alpha$ was 0.01--10 in the grid search. 
+The range of the hyperparameter $\alpha$ (see section~\ref{sec:ml-methods}) was 0.01--10 in the grid search. 
 So, 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
@@
 %$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
-All these extreme values of hyperparameters (stimulate regularization and indicate noisy and difficult to fit data.
+All these extreme values of hyperparameters stimulate regularization and indicate noisy and difficult to fit data.
 \begin{table}
@@
 A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$. 
+\td{how can R2 be below zero?}
+% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
 
@@
 % EMMA 30 pts
-The first two columns (e) show statistics validated with data the model was trained with (30 data points) and thus, 
+The first two columns ((e)) show statistics validated with data the model was trained with (30 data points) and thus, 
 these columns contain the lowest numbers. 
@@
 many data points are outside of the range of the \gls{emma} data set. 
-Thus, prediction for this data set are mainly extrapolations. 
+Thus, predictions for this data set are mainly extrapolations. 
 It must be explicitly noted at this point that pre-EMMA samples differ from EMMA samples 
-in the stabilization agent and therefore might underperform. 
+in the stabilization agent and therefore might deviate even more. 
 % inter/c/ pre-EMMA 5 pts
@@
 The last two columns show data for predictions of all available data (51 data points). 
-These statistics are lower because of the inclusion of the training set in the test set.
+These statistics are lower than the middle columns because of the inclusion of the training set in the test set.
 

### 2023-10-27 doc/Thesis/chapter/063-discussion.tex
corrected until comp details
next up 063*.tex

@@
 \section{Hindsight is easier than foresight}
+\label{sec:res-discussion}
 %\section{Discussion}
@@
 Firstly,
-the \nameref{sec:phase1} will be discussed in subsection \ref{sec:phase1}, 
-followed by the \nameref{sec:phase2} reviewd in subsection \ref{sec:phase2} 
+the "\nameref{sec:phase1}" will be discussed in subsection \ref{sec:phase1}, 
+followed by the "\nameref{sec:phase2}" reviewd in subsection \ref{sec:phase2} 
 %, thereupon the 
-and finally the \nameref{sec:phase3} examined in subsection \ref{sec:phase3}.
+and finally the "\nameref{sec:phase3}" examined in subsection \ref{sec:phase3}.
 %\ref{sec:phase3} \textit{\nameref{sec:phase4}}%
@@
 %no matter how much I improved it, it was still bad. 
-This was only noticed this after trying out another recipe. 
+This was only noticed after trying out another recipe. 
 The author's tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever can be. 

### 2023-10-28 doc/Thesis/chapter/04-experimental.tex
finish todos

@@
 %\td{Also, the long, exhaustive path to the base solution is described}
-\td{The experiments can be split into three sections: }
-In the first section the base recipe and the base process were sought. 
-In the pre-optimization section the boundaries for the optimization were investigated. 
-And during the third and final step the experiments for the optimization were performed.
+%\td{The experiments can be split into three sections: }
+First, the base recipe and the base process settings were explored. 
+Then, the analysis of samples is discussed and the boundaries for the optimization were investigated during pre-optimization.
+Finally, the experiments for the optimization were performed.
+
 \section{Substrate Preparation}
@@
 
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=.8\textwidth]{Pics/micro-1.png}
+		\caption{}
+		\label{fig:micro1}
+	\end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=.8\textwidth]{Pics/micro-2.png}
+		\caption{}
+		\label{fig:micro2}
+	\end{subfigure}
+	\begin{subfigure}{\textwidth}
+		\centering
+		\begin{circuitikz} \draw
+			(0,0) to[european voltage source] (0,2)
+			to[ammeter] (2,2) 
+			to[generic,l=W] (4,2) 
+			to[generic,l=Au] (6,2) 
+			to[generic,l=Al] (8,2)
+			-- (8,2)
+			to[generic,l=ZrO$_2$] (8,0)
+			-- (8,0)
+			to[generic,l=steel] (6,0)
+			to[generic,l=Ag] (4,0)
+			to[generic,l=Au] (2,0) 
+			to[generic,l=W] (0,0) 
+				;
+		\end{circuitikz}
+		\caption{}
+		\label{fig:circuit}
+	\end{subfigure}
+	\caption{View of a sample through the microscope attached to the multimeter and sketch of circuit. 
+	\label{fig:micro}
+	(a) Sputtered silver contacts on sample with gilded wolfram contact probe touching one of the contacts. 
+	(b) Edge of a sample with the probe touching silver paste on top of a sanded patch.
+	(c) From the source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.}
+\end{figure}
+
 The \gls{iv} curves were measured with Agilent 4156C Precision Semiconductor 
@@
 
+\iffalse
 \begin{figure}[hbt]
@@
 \end{figure}
+\fi
 
@@
 %The main part of the screening pre-optimization samples were optimized via biotic reinforcement learning (i.e. my brain). 
-The main part of all samples (around 90\%) were pre-optimization samples, 
+The main part of all samples (200 out of 244) were pre-optimization samples, 
 from which the bulk were screening experiments optimized via biotic reinforcement learning 
@@
 reproducible. 
-The \td{glass plate of the film applicator was therefore exchanged with a metal plate which}
+The glass plate of the film applicator was therefore exchanged with a metal plate which
 allowed to hold the sample in place through underpressure and simultaneously heat it to a certain 
@@
 Therefore \gls{ipo} was used  as stabilzier in further experiments.
-\td{After the boundaries of the solution were fixed }
+%\td{After the boundaries of the solution were fixed }
+After the base recipe for the solution has been decided
 the process variables to produce an insulating layer was examined. 
@@
 %\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
-\td{See} table \ref{tab:input} for the input space spanned during the optimization.
+See table~\ref{tab:input} for the input space spanned during the optimization.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-10-28 doc/Thesis/chapter/05-computational-details.tex
finish todos

@@
 For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
-5 points before and 5 points after the origin with \td{at one point distance from zero} (which boils
+5 points before and 5 points after the origin with minimum one point distance from zero (which boils
 down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
@@
 The kernels for \gls{svm} were the same as for \gls{krr}. 
-Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$, 
-where $C$ and $\varepsilon$ took the values 0.05--1 with step size 0.05 %, $\varepsilon$ 0.05--4.0 with 0.2 steps 
-\td{and was the same as for \gls{krr} plus \texttt{scale}.} %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
-Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
+Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$. 
+$C$ and $\varepsilon$ took the values 0.05--1 with step size 0.05 for \gls{svm} and \gls{krr}.
+\Gls{svm} additionally used the \texttt{scale} for $\gamma_{ml}$.
+%\td{and was the same as for \gls{krr} plus \texttt{scale}.} %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
+\texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
 and $\sigma(\mathbf{X})$ the variance of the input variables. 
@@
 The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
-of the \gls{emma} data set were \td{scaled before each calculation.}
+of the \gls{emma} data set were scaled with the routine \texttt{sklearn.preprocessing.StandardScaler().fit\_transform()}. %\td{scaled before each calculation.}
 % https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
@@
 For each calculation the 5-fold cross validation score was calculated. 
-The score equals to the coefficient of determination $R^2$ which \td{ is defined the following for non linear regression functions:}
+The score equals to the coefficient of determination $R^2$ which is defined the following for non-linear regression functions
+%\footnote{see https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html\#sklearn.kernel\_ridge.KernelRidge.score}
+\footnote{see \href{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}}
 \begin{equation}

### 2023-10-28 doc/Thesis/chapter/060-results-material.tex
finish todos

@@
 Figure~\ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
-\td{Each line represents a I-V measurement at a distinct aluminium contact applied by sputtering through a mask. }
+Each line represents a I-V measurement at a distinct aluminium contact applied by sputtering through a mask (see figure~\ref{fig:micro}).
 All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 

### 2023-10-28 doc/Thesis/chapter/061-results-emma.tex
finish todos

@@
 The deviation from expectation might be due to measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature, humidity or solution age. 
-Measurements were expected to show clear correlation of optimizands $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $\lambda$.
-The only statistically relevant correlation was observed for $T_{cal}$ with the optimizands.
+Measurements were expected to show clear correlation of \textit{optimizands} $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $\lambda$.
+The only statistically relevant correlation was observed for $T_{cal}$ with the \textit{optimizands}.
 %\td{why}
@@
 		(c)~calculated conductance measures~$\gamma$ against calcination temperature $T_{cal}$
-		\td{
 		(d)~calculated pin hole density~$\rho$ against calcination temperature $T_{cal}$
 	change colors }
-	\td{increase font in gnuplot, change y-axis of (c)}
-	}
 

### 2023-10-28 doc/Thesis/chapter/063-discussion.tex
finish todos

@@
 the complexity of the model can be drastically reduced. 
-This leads to more information which can be extracted from the remaining data, 
+This leads to more information which can be extracted from the same amount of data, 
 be it in more detail of the dependence or higher confidence interval. 
-A good measure to compare with literature and other methods is the \gls{epv}. 
+A good measure to compare data density with literature and other methods is the element per variable ratio.
 The \gls{epv} in this work is round 5,
@@
 %One regime where overfitting occurs is when there are to many parameters to be fitted with not enough data. 
-Another reason to avoid too many variables in a model is that they introduce more parameters to fit and overfitting happens in the regime where to many parameters are fitted with not enough data.
+Another reason to avoid too many variables in a model is that they introduce more parameters to fit and overfitting happens in the regime where too many parameters are fitted with not enough data.
 %todo{Overfitting happens in the regime where to many parameters are fitted with not enough data. }
-
-Another step/deed which is well placed in this phase is the estimate the error by reproducing a single sample a certain number of times. 
+%
+Another step which is well placed in this phase is the estimate the measuring error by reproducing a single sample a certain number of times. 
 %Where the number will then be higher than during optimization 
@@
 When working with stochastic algorithms it is especially important to introduce reproducibility via a seed, which determines all subsequent pseudo-random numbers. 
-Finally, during the \gls{emma} optimization the input data were not regularized, %es wurde auf regularization verzichtet, 
-because the regularization would be different for different generations.
-Regularizing with the mean and standard deviation would be either inconsistent across generations or over overvalue the distribution of the initial generation. 
+Finally, during the \gls{emma} optimization the input data were not regularized (scaled), %es wurde auf regularization verzichtet, 
+although this could have increased the efficiency of the model.
+%because the regularization would be different for different generations.
+%Regularizing with the mean and standard deviation would be either inconsistent across generations or \td{overvalue the distribution of the initial generation.}
 %because the distribution of 
@@
 %alter previous measurements, which alread beitragen to the model and the influence the decision of the next sample. 
-These were the reasons for not including regularization during \gls{emma} optimization. 
-On the other hand the input data could have been regularized to only take values $[-1;1]$ by defining the regularized varible as 
+%These were the reasons for not including regularization during \gls{emma} optimization. 
+%On the other hand 
+The input data could have been regularized to only take values $[-1;1]$ by defining the regularized variable as 
 $x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$.
@@
 
-\td{when adding dep var to model this has two folgen: - beeinflusst the BF and the optimization, but bcs relatiev weight is only 0.05 for each, no big beeinflussung on optimization}
+%\td{0when adding dep var to model this has two folgen: - beeinflusst the BF and the optimization, but bcs relatiev weight is only 0.05 for each, no big beeinflussung on optimization}

### 2023-10-28 doc/Thesis/chapter/07-outlook.tex
finish todos

--- 2023-03-11 Thesis/chapter/07-outlook.tex
@@
 %what did i want to do? 
-The goal of this work was to find a sol-gel doctor blading process resulting in a insulating zirconium ceramic on top of steel.
+The goal of this work was to find a sol-gel doctor blading process resulting in an insulating zirconium ceramic on top of steel.
 This structure then can be used as substrate for thin layer photovoltaics. 
@@
 A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
-The recipe was improved by increasing its stability. 
+The recipe was improved by increasing the stability of the solution. 
 The best parameters found by the \gls{emma} optimization were 
@@
 %was wurde herausgefunden? 
-A strong correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
+A correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
 Furthermore, the layer count has been verified as an important factor. 

### 2023-11-25 doc/Thesis/chapter/01-introduction.tex
start correction

@@
 The cells must be applied to a non-conducting surface.
-Glass is a good non-conducting substrate, but very rigid and brittle. 
+Glass is a popular non-conducting substrate, but very rigid and brittle. 
 An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
 An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be synthesised on top.
-Polymere would be a obvious choice if not for its low melting point which makes high prodction temperatures inpractical.
+Polymers would be a obvious choice if not for its low thermal stability which makes high production temperatures impractical.
 A non-toxic material which is suitable for the insulation is \ch{ZrO2}. 
-An economic and scalable method is doctor blading via a sol-gel process. 
-Sol-gel processes often produce porous layers. 
+%An economic and scalable method is doctor blading via a sol-gel process. 
+Sol-gel roll-to-roll coating processes (e.g. tape casting) are economic and scalable methods to apply liquid precursors to substrates.
+Sol-gel processes often produce porous layers, though. 
 In this work a dense, insulating and homogeneous layer is pursued. 
@@
 %The resulting optimum is compared with other optimization methods.
+\td{and how do you transfer knowledge ...}
 
@@
 \ref{sec:theoretical} giving 
-some background information on topics of PV, material science and computational science which were used in this work.
+some background information on topics of PV, \td{material science} and \td{computational science} which were used in this work. \td{more detail}
 In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 

### 2023-11-25 doc/Thesis/chapter/030-theory-materials.tex
start correction

@@
 Edmond \linebreak[4] 
-Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel (the person after whom the unit is named).
+Becquerel\cite{becquerel1839memoire}. %, the father of Henri Becquerel (the person after whom the unit is named).
 Another relevant piece in the \gls{pv} jigsaw was brought to light
@@
 effect with his light quantum theory\cite{einstein1905erzeugung}.
-In the 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space flight. 
+In the 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space flight.  \todo{https://doi.org/10.1063/1.1716492}
 Eventually, the interest in photovoltaic and other alternative energy sources 

### 2023-11-27 doc/Thesis/chapter/030-theory-materials.tex
correct util excl DOE

@@
 effect with his light quantum theory\cite{einstein1905erzeugung}.
-In the 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space flight.  \todo{https://doi.org/10.1063/1.1716492}
+%\todo{https://doi.org/10.1063/1.1716492}
+In the late 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space exploration.  
+In 1958 the US American Vanguard I\cite{vanguard2004} and the soviet Sputnik III\cite{sputnik} were the first satellites with solar cells with efficiencies under 10 \% (\td{cite?}).
+These "solar batteries" - as they were called then - allowed the transmission system of Vanguard I to be operating for over a year after the chemical battery powered system stopped transmitting after 20 days\cite{vanguard2004}.
+%
 Eventually, the interest in photovoltaic and other alternative energy sources 
 rose - fuelled by the oil crisis in 1973 - 
-and the development of photovoltaic for the consumer market was boosted. 
+and the development of photovoltaic devices for the consumer market was boosted. 
 This development lead to a drop in 
@@
 \subsection{CIGS}
+\subsection{Copper Indium Gallium Selenide} 
 \gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
@@
 The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in 112 direction\cite{hedstrom1993cigs}.
-A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporation from elemental sources controlled by a mass spectrometer.\cite{hedstrom1993cigs}
+A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporation from elemental sources controlled by a mass spectrometer\cite{hedstrom1993cigs}.
 The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
@@
 %
-Instead of glass as substrate, steel and plastics (e.g. polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
+Instead of glass as substrate, steel and polymers (e.g. polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
 They both come with their own inconveniences. 
-Plastics generally have very low melting points which restrict preparation temperatures of \gls{cigs}.
+Polymers generally have low thermal stability compared with ceramics and metals which restrict preparation temperatures of \gls{cigs}.
 Steel, on the other hand, is temperature resistant enough, but is an electric conductor. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Materials and Their Analysis}
+\todo{COATING OF THE SUBSTRATE or sample preparation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Zirconium oxide}
+\subsection{Properties of Zirconium oxide}
 Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV\cite{Anwar2017} and relative permittivity of circa 20 at room temperature\cite{kukli2001dielectric}. 
@@
 %\subsection{Sol-Gel and Doctor Blading}
-\subsection{Doctor Blading}
+\subsection{Tape Casting}
 %\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Sputtering}
+\subsection{Contact Deposition by Sputtering}
 %SPUTTERING FREEWRITING: 
@@
 %the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
-The anode, then, emits electrons which collide with gas particles (mostly argon because of its inert properties and potential to transfer more kinetic than lighter noble gases). 
+The anode, then, emits electrons which collide with gas particles (mostly argon because of its inert nature and potential to transfer more kinetic than lighter noble gases). 
 Some gas particles may get ionized by the collision and the gas cations are accelerated to the anode. 
@@
 The pressure in the chamber should be small, such that the sputtered particle has a long mean free path, but on the other hand 
-a minimum pressure is needed to keep the plasma ``alive''. 
+a minimum pressure is needed to sustain the plasma.
 Usual pressures buzz around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
@@
 A magnetron can be placed behind the cathode (target) in order to trap the plasma close to the source. 
-This lowers the pressure needed to keep the plasma ``alive''. 
+This lowers the pressure needed to sustain the plasma. 
 Furthermore, magnetrons prevent high energy electrons from reaching the substrate and 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   SEM    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scanning electron Microscopy}
+\subsection{Scanning Electron Microscopy}
+\td{FOR ME PERSONALLY TOO MUCH GENERAL INFORMATION}
 The history of \gls{sem} can be traced back to 1843 when Scottish clockmaker Alexander Bain filed a patent for dissecting an image by scanning. 
@@
 A more detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}. 
-\Gls{sem} is a microscopical technique which allows visualization of surfaces with features in the nano meter regime. 
+\Gls{sem} is a microscopic technique which allows visualization of surfaces with features in the nanometer regime. 
 While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
@@
 The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons in the examined material. 
-Secondary electrons carry information to conclude morphology and topology of the sample, while X-rays can be used to identify the elements. 
+Secondary electrons carry information to conclude morphology and topology of the sample, while X-rays can be used to identify elements present in the surface. 
 Electrons originate from either a \gls{feg}, where a strong electrical field rips electrons from the bulk, or from thermionic guns where a filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted.
@@
 (wavelengths of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
-In general, light is described as periodic \gls{em} wave 
+\td{FORMATTING: In general, light is described as periodic \gls{em} wave 
 which - in vacuum - moves with the speed of light ($c = \mps{299792458}$)\cite{gHobel2006international}.
@@
 %is the refractive index which is a function of the wavelength $\lambda$. 
-The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
+The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:}
 \begin{align*}
@@
 from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
-X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
+X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with \td{it's adsorbed by certain groups?)} molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins.
 %Molecular vibrations can be separated in valence and deformation vibrations.
@@
 absorbed by a molecule or atom.
-Firstly, the energy must be the same as the difference between two electronic states, a lower populated and a higher empty orbital. 
+Firstly, \td{the energy must be the same as the difference between two electronic states, a lower populated and a higher empty orbital. }
 The electron will then be excited into a energetically higher orbital.
-Secondly, the spin state of both states has to be the same otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely.
+Secondly, the \td{spin state (which spins?)} of both states has to be the same otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely.
 
 % IR
-\Gls{ir} photons interact with molecular vibrations, which is only a part of the degrees of freedom of a molecule.
+\td{ \Gls{ir} photons }interact with molecular vibrations, which is only a part of the degrees of freedom of a molecule.
 A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
 %
-The number of vibrations can therefore be calculated as 
+The number of vibrations can therefore be calculated to be
 \begin{align*}
@@
 Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
-Only vibrations that change the dipole moment of the molecule are \gls{ir} active. 
+Only vibrations that change the dipole moment of the molecule are \td{\gls{ir} active. (does Raman not also use IR)}
 The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes which lead to intricate patterns in the so called fingerprint region.

### 2023-11-27 doc/Thesis/chapter/031-theory-calculations.tex
next up 063*.tex
correct util excl DOE

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Machine Learning and Statistics}
@@
 %pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
-More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of 
+More precisely, mathematical statistics (stochastics)\cite{haertler2014statistisch} is the subject of 
 finding mathematical models to describe the data 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Artificial Inteligence and Machine Learning}
+\subsection{Artificial Intelligence and Machine Learning}
 %How can \gls{ai} and \gls{ml} be defined? 
@@
 The history of \gls{ai} goes back to the middle of the \nth{20} century. 
-Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
+Researchers from the emerging field came together at a 1956 Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
 \Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
@@
 %
-At the moment it's hard to imagine a computer getting a higher ratio than a human
+At the moment it is hard to imagine a computer getting a higher ratio than a human
 but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future; especially with ChatGPT's convincingly human-like answers\cite{dis2023chatgpt}.
 
-But fear not, that doesn't mean that computers are 
+But fear not, that does not mean that computers are 
 more intelligent than humans
@@
 cyber security\cite{Sarker2021},
-facial recognition (to prevent theft of toilet paper \cite{Andrews2017}),
+facial recognition (to prevent theft of lavatory paper at public toilet in China\cite{Andrews2017}),
 financial sector (as robo-advisors)\cite{Littman2021},
@@
 %
-It is nearly hard to find a field where \gls{ai} isn't used in some way. 
+It is nearly hard to find a field where \gls{ai} is not used in some way. 
 This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
@@
 \subsection{Machine Learning Methods}
+\label{sec:ml-methods}
 %
 \Gls{ml} is at the base of most \gls{ai}s.
-It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorize, predict and make decisions based on data. 
+It is an umbrella term for programs with instructions to learn from data, i.e.\ gain knowledge, categorize, predict and make decisions based on data. 
 %
-There is a platitude of different machine learning methods: 
-they can be divided into supervized (training set is labeled) and unsupervized (exploratory).  
+There is a platitude of different machine learning methods and most of them can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
 An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
 Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
-%
+
 \Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
@@
 
-There are also lesser know \gls{ml} algorithms like 
+There are also lesser known \gls{ml} algorithms such as 
 evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
@@
 
-A \gls{ga} is a search algorithm that uses principles of natural selection and genetics to optimize a search space.
+A \gls{ga} is a search algorithm that uses principles of natural selection and \td{genetics} to optimize a search space.
 A GA starts with a population of randomly generated solutions, or chromosomes, and then proceeds to breed them together to create new solutions.
 The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes.
-This process is repeated until a satisfactory solution is found.\footnote{This paragraph was written by GPT\cite{Liu2021gpt} given the input "Introduction to genetic algorithms: "}
+This process is repeated until a \td{satisfactory} solution is found.\footnote{This paragraph was written by GPT3\cite{Liu2021gpt} given the input "Introduction to genetic algorithms: "}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{EMMA}
+%\subsection{EMMA}
+\subsection{Evolutionary Model-based Multiresponse Approach}
 \Gls{emma} is an implementation of \gls{pso} in the \texttt{R} programming language. 
@@
 "Multivariate Adaptive Regression Splines"\cite{friedman1991multivariate}. 
-The \texttt{CRAN} package which implements \gls{mars} is called \texttt{earth} due to \gls{mars} being trade marked\cite{mars}.
+The \texttt{CRAN} (Comprehensive R Archive Network) package which implements \gls{mars} is called \texttt{earth} due to \gls{mars} being trade marked\cite{mars}.
 %%% MARS 
@@
 Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g.
-kernel functions), whose number of parameter quickly exceeds the practical for moderate dimensional problems ($n>5$).
+kernel functions), whose number of parameter quickly \td{exceeds the practical} for moderate dimensional problems ($n>5$).
 %
@@
 Then, the backwards algorithm regularizes the function by removing individual terms. 
-The metric which decides if a term should be removed is called \gls{gcv} and was introduced by Wahba and Cravenin 1969\cite{wahba1979smoothing}.
+The metric which decides if a term should be removed is called \gls{gcv} and was introduced by Wahba and Cravenin 1969\cite{wahba1979smoothing}:
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Design of Experiment} %DOE
+\subsection{Design of Experiments} %DOE
 %\epigraph{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}{Grahem C.
@@
 (1) If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations).
+
 (2) If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.

### 2023-11-28 doc/Thesis/chapter/04-experimental.tex
correction transfer until excl characterization

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo{materials section and sources (incl. purities is missing!}
 In this section the used chemicals, substrates, experimental procedures and any used
-equipment are described. 
+\td{equipment (what do you mean?)} are described. 
 %\td{Also, the long, exhaustive path to the base solution is described}
@@
 \linebreak[4] 
-(\cm{2.5}$\times$\cm{7.5})\ds{ from Sigma Aldrich, thinner}, 
-squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
-\gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
-\gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
+(\cm{2.5}$\times$\cm{7.5}) from Sigma Aldrich, thinner, 
+squared glass plates (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich, 
+\gls{ito} plates (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich, 
+\gls{fto} plates (\cm{5}\x\cm{5}) from Sigma Aldrich and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
 %}
@@
 spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
-is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
+is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (don't follow?)}
 The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
@@
 \end{enumerate}
-After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.
+\td{is that the usual procedure for steel?}
+After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the coating step.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Solutions}\label{sec:exp-sol}
+\section{Precursor Solutions}
+\label{sec:exp-sol}
 All recipes for solutions can be divided into two categories:
@@
 
+\iffalse
 \begin{figure}[htb]
@@
 \end{figure}
+\iffalse
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Aquatic solution}\label{sec:exp-sol-aq}
-\gls{zrpro} was added to \gls{acac} while stirring and in a separate vessel \gls{water} 
+\subsection{Aquatic Precursor Solutions}\label{sec:exp-sol-aq}
+\gls{zrpro} was added to acetylacetone (\gls{acac}) while stirring and in a separate vessel \gls{water} 
 (including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
-was added to \gls{ipo} and both were stirred for one hour. 
-These additives were added to influence pH and surface tension with the goal to influence the resulting layer. % \td{see Parvulescu2015}
-The \gls{water}-\gls{ipo} mixture was added to the other solution and stirred over night. 
+was added to isopropyl aclohol (\gls{ipo}) and both were stirred for one hour. 
+These additives were added to influence pH and surface tension with the goal to \td{influence the resulting layer (in terms of what?)}. % \td{see Parvulescu2015}
+The \gls{water}-\gls{ipo} mixture was added to the \td{other solution (which? NOT CLEAR!)} and stirred over night. 
 The exact volumes can be taken from table~\ref{tab:rec1}.
-Unfortunately, this solution failed to produce anything near homogeneous layers. 
+Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
 Thus, an alternative solution was found.
@@
 \subsection{Buthanolic solution}\label{sec:exp-sol-bu}
+\todo{what did you did you do percisely! It must be logical and should be followed}
 Five different concentrations of the buthanolic solutions were prepared.
-Not all chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
+\td{Not all (which?)} chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
 starting materials had to be chosen from the available inventory.
-The \gls{1f} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
-The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar with 
-but higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
+
+The \td{\gls{1f}} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
+The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar 
+but with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
 with the aim of producing thicker layers.
 %\td{p34}
-Different solvents (Butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
+\td{Different} solvents (butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
 (\gls{acac} and citric acid) were tested and later in the process - just before the 
-\gls{pso} started - the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
+\td{particle swarm optimisation} started - the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
 The most promising combination of solvent, chelating agent and stabilization reagent was 
 \gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
-The main differences between the used recipe and the recipe mentioned by \cite{Hu2016} were 
-precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
+The main differences between the used recipe and the recipe mentioned in \cite{Hu2016} were 
+\td{precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
 complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
@@
 \SI{500}{\celsius}).
+( so everything is different!! now I'm confused? you dream up a recipe and optimize that? not how I would do that! also: quite a difference between alpro3 and zrpro4)}
 %me          hu
@@
 \label{sec:exp-db}
-All glass substrates were doctor bladed manually with a smooth stainless steel wire bar 
-coater. On two opposing edges adhesive tape was applied to create a valley in between. After the 
-layer was applied and dried the tape was removed and the substrate treated with heat.
+All glass substrates were doctor bladed manually with a smooth stainless steel wire bar coater. 
+On two opposing edges adhesive tape was applied to create a valley in between. 
+After the layer was applied and dried, the tape was removed and the substrate heat treated \td{(at which T?)}.
 Lower \gls{db} velocities resulted in less homogeneous layers.
@@
 %All 
-Steel substrates 
-were doctor bladed with 
-an Erichsen Coatmaster 510 film applicator with a heatable plate.
+Steel substrates were doctor bladed with an Erichsen Coatmaster 510 film applicator with a heatable plate.
 %The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
@@
 The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in 
-\SI{0.05}{\milli\meter} steps and did not substantially alter the results.
+\SI{0.05}{\milli\meter} steps and \td{did not substantially alter the results. (what do you mean?)}
 For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
@@
 underpressure could be applied to keep the substrate in place. 
-Most of them were covered with tape to increase the suction intensity at the remaining ones (see figure~\ref{fig:eric}
-After setting the temperature of the heating plate to 
+Most of them were covered with tape to increase the suction intensity at the remaining ones \td{(see figure~\ref{fig:eric}).
+After} setting the temperature of the heating plate to 
 \SI{200}{\celsius}, the temperature of the vacuum plate (room temperature, \SI{40}{\celsius}, 
@@
 was removed from the plate with a wipe. 
-The doctor bladed substrate was transferred to the \SI{200}{\celsius} heating plate and 
-rested on there for \minutes{5}. 
+The coated substrate was \td{transferred to the \SI{200}{\celsius} heating plate and rested on there for \minutes{5}. (why? what was the purpose?)}
 This process of applying a \gls{zro} layer was repeated as many times as needed.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Calcination}\label{sec:exp-calc}
-A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate 
-the doctor bladed samples. 
+\section{Calcination of Films}\label{sec:exp-calc}
+A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate the coated samples. 
 The heating plate could hold temperature for a certain amount of time, but heated with a 
-fixed rate of circa \oc{10}/\minutes{}.
+fixed rate of \td{circa (and how do you optimze ca?)} \oc{10}/\minutes{}.
 In order to achieve a lower overall heating rate several temperature ramps and plateaus 
@@
 \section{Characterization}
-All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
+\td{All \gls{sem} micrographs were taken with a Zeiss Supra 40. (conditions? were samples sputtered etc...)}
 \Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
@@
 % gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
-{\nano\meter}) and a Silicon detector for visual and \gls{nir} light 
+{\nano\meter}) and a silicon detector for visual and \gls{nir} light 
 (\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). For transmittance the light
@@
 in Opus software. % included in the spectrometer. 
-\Gls{xrd} spectra were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
+\Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
 All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.

### 2023-12-05 doc/Thesis/chapter/04-experimental.tex
correction transfer until excl 5.2 EMMA

@@
 \end{figure}
-\iffalse
+\fi
 
@@
 in Opus software. % included in the spectrometer. 
-\Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
-All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.
+\td{\Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. (where are the conditions?)}
+All \gls{xrd} diffractograms were taken at \SI{5}{\degree} incident angle and compared to the internal database.
 
@@
 	(b) Edge of a sample with the probe touching silver paste on top of a sanded patch.
-	(c) From the source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.}
+	(c) From the source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.\td{(what is XXX circuit?)}}
 \end{figure}
@@
 UNIVEX450C Sputter System.
-Directional current sputtering was used with Argon as inert gas at \SI{0.005}{\milli\bar} 
+Directional current sputtering was used with argon as inert gas at \SI{0.005}{\milli\bar} 
 and with a power of \SI{40}{\watt} for \SI{700}{\second}.
@@
 \section{Pre-optimization}\label{sec:exp-preopt}
+\td{preopt of what? recipe?}
 %\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
@@
 from which the bulk were screening experiments optimized via biotic reinforcement learning 
-(i.e. my brain) in order to obtain reasonable constraints for computerized pre-optimization. 
+(i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization. \td{(xxx but using a completely untested recipe!)} 
 %Initially, glass plates were doctor bladed manually with aquatic solution and calcinated 
@@
 %\todo{different additives, heating programs (NT1-NT5 and HP1), blade distances (distance between blade and substrate) and layer counts were tried}
-Composition of the aquatic solution, heating program, blade distance (distance between 
+Composition of the \td{aquatic solution (I thought this did not work?)}, heating program, blade distance (distance between 
 blade and substrate) and layer count were varied but no homogeneous layers resulted. 
@@
 the buthanolic recipe was introduced, which gave rise to homogeneous films.
-After the blade moved over the substrate the remaining liquid needed about a minute 
-to evaporate at room temperature. 
+\td{After the blade moved over the substrate the remaining liquid needed about a minute to evaporate at room temperature. (2x mentioned this before!)}
 %\td{
@@
 as nominal and extreme values for 
-relative concentration of Zr $c_{zr}$, number of layers $\lambda$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively.
+relative concentration of Zr $c_{zr}$, \td{number of layers $\lambda$ (layers of what?)}, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively.
 After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see table \ref{tab:pre-opt1}).
@@
 	\centering
-	\caption{Pre-optimization experiments}
+	\caption{Pre-optimization experiments \td{(still smaller?? why? what am I supposed to learn?)} }
 	\label{tab:pre-opt}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Shortly before the \gls{pso} the stabilization agent was changed from \gls{acoh} to 
-\gls{ipo} because of much better solution stability.
+Shortly before the \gls{pso} the stabilization agent was changed from \todo{ \gls{acoh} to \gls{ipo} (but why?)} because of much better \td{solution stability. (how did yo test this??)}
 The - up to this moment - best process was chosen to be tested with 
@@
 The sample produced with \gls{ipo} as stabilization agent 
-showed comparable passivization results and better stability of the solution. 
+showed \td{comparable passivization results (but where are they?)} and better stability of the solution. 
 Therefore \gls{ipo} was used  as stabilzier in further experiments.

### 2023-12-05 doc/Thesis/chapter/061-results-emma.tex
correction transfer until excl 5.2 EMMA

@@
 %%% ALL SAMPLES
-A total of 30 recipes (see appendix \ref{sec:app-emma}) have been investigated in 
+A total of 30 recipes (see appendix \ref{sec:app-emma}) was investigated in 
 five iterations ($t = 0, \dots, 4$) of the algorithm. 
 Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
-The best recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
+The \td{best (what is "best"? How do you measure that?	 recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
 The experiments for generation 5 where not executed but 

### 2023-12-28 doc/Thesis/chapter/01-introduction.tex
digitized all corrections

@@
 The remainder of this work is organized with chapter 
-%\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
 \ref{sec:theoretical} giving 
-some background information on topics of PV, \td{material science} and \td{computational science} which were used in this work. \td{more detail}
+%some background information on topics of PV, \td{material science} and \td{computational science (more detail)} which were used in this work. 
+information on the general \td{functionsweise} of PV, the structure, characteristics and properties of materials which were used and computational, statistical and machine learning methods for data processing.
+
 In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 

### 2023-12-28 doc/Thesis/chapter/061-results-emma.tex
digitized all corrections

@@
 Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
-The \td{best (what is "best"? How do you measure that?	 recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
+The \td{best (what is "best"? How do you measure that?)} recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
 The experiments for generation 5 where not executed but 
@@
 %%% OVER TIME 
-The only clear trend from table \ref{tab:emma-Gb} is the layer count, which rises with the generations. 
+The only clear trend from table \ref{tab:emma-Gb} is the \td{layer count (again not yet clear)}, which rises with \td{the generations (which?)}. 
 The remaining input variables remained more or less the same except for the 3rd generation. 
@@
 (predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
-except for sample 2947, which wasn't predicted but measured. 
+except for sample 2947, which was not predicted but measured. 
 This shows that the easiest part of the algorithm - the selection of the optimum 
@@
 %
-Contrarily, the predicted conducticity $\hat{\gamma}$ for each generation's best 
+Contrarily, the predicted conducticity $\hat{\gamma}$ for each generation's \td{best (best in what?)}
 (predicted by the very generation's \gls{rf}) does increase with each iteration 
@@
 %GENERATIONS
+\td{How did you determine the pinhole densisty}
 In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
 conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
-The green points at generation number 0 indicate particles which were not included to be propagated. 
+The \td{green} points at generation number 0 indicate particles which were not included to be propagated. 
 %Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
-Violet lines connect individual particles in time. 
-The blue line connects averages of particles of each generation (including initial non-propagated particles) and 
-yellow lines connect averages of each generation of only those particles which were propagated. 
+\td{Violet} lines connect individual particles in time. 
+The \td{blue} line connects averages of particles of each generation (including initial non-propagated particles) and 
+\td{yellow} lines connect averages of each generation of only those particles which were propagated. 
 %
@@
 The coefficients in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) have the same signs and differ by a factor of roughly 100.
-This fits the data well since the maxima of $\rho$ and $\gamma$ are separated by rough factor of 100 (see figure~\ref{fig:emma-gen} and appendix~\ref{sec:app-emma}).
+\td{This (what is "this?)} fits the data well since the maxima of $\rho$ and $\gamma$ are separated by rough factor of 100 (see figure~\ref{fig:emma-gen} and appendix~\ref{sec:app-emma}).
 %, but the positive influence of the layer count $\lambda$ is counter intuitive
@@
 basically only including the influence of the lowest layer count $\lambda=4$.
-Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}), that the lowest layer count produces worse samples which is intuitive, but more than 6 layers don't improve the insulation. 
+Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}), that the lowest layer count produces worse samples which is intuitive, but more than 6 layers do not improve the insulation. 
 Encouragingly, the calcination heating rate $v_{cal}$ (see equation (\ref{eq:emma-vcal3})) has been predicted perfectly within numerical precision.
@@
 %This would correspond to $+h(400-T_{cal})$
-The original recipe by Hu et al.\cite{Hu2016} used \oc{500} and thus even \oc{400} are low.
+The \td{original recipe by Hu et al.\cite{Hu2016} used \oc{500} (but to produce Al2O3, so not a surprise? or?)} and thus even \oc{400} are low.
 \textit{Optimizands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 

### 2023-12-28 doc/Thesis/chapter/07-outlook.tex
digitized all corrections

@@
 A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
-The recipe was improved by increasing the stability of the solution. 
+\td{The recipe was improved by increasing the stability of the solution. (no model needed)}
+\td{ALSO: How many exp would you over the computer time and effort to find this out?}
 The best parameters found by the \gls{emma} optimization were 

### 2023-12-28 doc/Thesis/chapter/021-theory-calculations.tex
rename to fit numbering

--- 2023-11-27 doc/Thesis/chapter/031-theory-calculations.tex
@@
 
-(2) If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.
+(2) If the query space is so vast, that randomly querying might explore domains\td{, which} might lead to uninteresting or even misleading information.
 %Both encompass nearly all cases. 
@@
 %
-Constraints for a given experiment include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
-%
+Constraints for a given experiment include range of input and output variables as well as total time available and total number of samples/experiments that can be taken\cite{goodwin1977experiment}.
 
@@
 Each possible combination of discrete values is tested.
-While this is the most informative design it will more often than not be infeasible due the curse of dimensionality\cite{cherkassky1998learning}.
+\td{While} this is the most informative design it will more often than not be infeasible due the curse of dimensionality\cite{cherkassky1998learning}.
 % 2-LVL FACTORIAL

### 2023-12-28 doc/Thesis/chapter/023-linreg-krr-svm.tex
rename to fit numbering

--- 2023-10-17 doc/Thesis/chapter/033-linreg-krr-svm.tex
@@
 The extra term reduces overfitting and is scaled by a correction parameter~$\alpha$. 
-The larger $\alpha$ is, the larger is the regularization and the flatter is the regression functions. 
+The larger $\alpha$ is, the larger is the regularization and the flatter is the regression function. 
 When $\alpha$ tends to infinity, we get an intercept-only model.
@@
 \end{equation}
-which can be rewritten by some mathematical wizardry (setting the partial derivatives of the Lagrangian function
+which can be rewritten by some \td{mathematical wizardry} (setting the partial derivatives of the Lagrangian function
 $\frac{\partial \mathfrak{L}}{\partial \mathbf{w}}$ and $\frac{\partial \mathfrak{L}}{\partial b}$ 
@@
 \end{equation}
-If the prediction $(\mathbf{w}\mathbf{x}_i+b)$ and the true category $y_i$ don't agree, 
+If the prediction $(\mathbf{w}\mathbf{x}_i+b)$ and the true category $y_i$ do not agree, 
 they have opposite signs and their product will be a negative number.
@@
 but also by intricate decision boundaries due to the kernel trick.
+
 Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the innerproduct of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper.

### 2023-12-28 doc/Thesis/chapter/04-computational-details.tex
rename to fit numbering

--- 2023-10-28 doc/Thesis/chapter/05-computational-details.tex
@@
+\todo{ To me this does not follow any logical order!}
 \section{Data Processing}
 \label{sec:eval}
+\todo{Why this procedure? Sounds quite arbitrary?}
 %Reading list
@@
 %\td{describe problem and solution found}
-Multiple \gls{iv} curves were measured for every sample.
+\td{Multiple \gls{iv} curves were measured (where are they?)} for every sample.
 The main difficulty faced in processing the data was to present the measurements obtained 
@@
 \end{equation}
-Another measure is the density of shorted species $\rho$ (pin hole density), calculated in following way:
+Another measure is the density of shorted species $\rho$ (pinhole density), calculated in following way:
 \begin{equation}
@@
 \label{sec:ss}
+\todo{for what?}
 An evolutionary approach was chosen, namely a multi-objective 
@@
 
-The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $\lambda$ and $v_{cal}$, 
+The \textit{optimizands} where chosen to be \td{$\gamma$, $\rho$, $\lambda$ and $v_{cal}$, (here it would help me to remind the reader what the symbols are!)}
 where $\gamma$, $\rho$ and $\lambda$ are to be minimized and $v_{cal}$ to be maximized.
@@
 The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
-The experiments are executed, measured and evaluated according to section 
-\ref{sec:exp} and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pin hole density $\rho_s$ (see eq. \ref{eq:rho}), 
-$\lambda$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in 
+The \td{experiments} are executed, \td{measured (unclear!)} and evaluated according to section 
+\ref{sec:exp} and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), 
+\todo{$\lambda$ (numbers of layers) (tstill not clear! what is meant?!)} and $v_{cal}$ (heating rate of calcination process in 
 \oc{}/\minutes{}) are supplied to the program. 
@@
 The current population - each of the particles independently - 
-are given a random velocity vector associated to them which is directed to the best predicted sample. 
+are given a random velocity vector associated to them, which is directed to the best predicted sample. 
 %moves towards the optimum solution.
-The population for the next time step is generated and the experiments are again executed, measured and evaluated.
+The population for the next time step is generated and the experiments are again \td{executed, measured and evaluated. (unclear!)}
 Each time step thus includes experiment identification, solution preparation, coating deposition and layer analysis.
@@
 %\subsection{Grid Search}
+
 A grid search over a set of hyperparameters was executed. 
@@
 The kernels for \gls{svm} were the same as for \gls{krr}. 
-Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$. 
-$C$ and $\varepsilon$ took the values 0.05--1 with step size 0.05 for \gls{svm} and \gls{krr}.
+Further hyper parameters were \td{$C$, $\varepsilon$ and $\gamma_{ml}$. 
+$C$ and $\varepsilon$ (define again, forgotten until now) } took the values 0.05--1 with step size 0.05 for \gls{svm} and \gls{krr}.
 \Gls{svm} additionally used the \texttt{scale} for $\gamma_{ml}$.
@@
 % https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVR.html#sklearn.svm.SVR.score
-For each calculation the 5-fold cross validation score was calculated. 
-The score equals to the coefficient of determination $R^2$ which is defined the following for non-linear regression functions
+For each calculation the 5-fold cross-validation score was calculated. 
+The score equals to the coefficient of determination $R^2$, which is defined the following for non-linear regression functions:
 %\footnote{see https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html\#sklearn.kernel\_ridge.KernelRidge.score}
@@
 the parameters with the highest score were noted.
-% 
+
 Finally, the different data sets were predicted for each model and \gls{mae} and \gls{mse} were calculated.
 These values were also calculated for \gls{emma} and the linear model in order to compare the different methods. 
+\todo{(and how did this output help you to optimize your exp. procedure??)}

### 2023-12-28 doc/Thesis/chapter/050-results-material.tex
rename to fit numbering

--- 2023-10-28 doc/Thesis/chapter/060-results-material.tex
@@
 Starting with physical measurements and material properties.
-Followed by the presentation of the results obtain by optimization and exploration with the \gls{emma} method. 
-Finally, the results of alternative regression methods let loose on the data are compared with the \gls{emma} method.
+Followed by the presentation of the results obtained by optimization and exploration with the \gls{emma} method. 
+Finally, the results of alternative regression methods \td{let loose on (language is too colloquial)} the data are compared with the \gls{emma} method.
 
@@
 \label{sec:res-mat}
+\todo{of what?}
 %\subsection{Solution}
 %%%%%%%% AQUATIC 
-As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer. 
+As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a \td{homogeneous layer. (of what?)}
 The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
-Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't increase the resistance of the resulting \gls{zro} layers. 
+Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant did not increase the resistance of the resulting \gls{zro} layers. 
 % ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
 % ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
-Even after the consecutive application of two layers, there was no improvement and the results examined with \gls{sem} reminded rather of a sparse crust than of a film. 
+Even after the consecutive application of two layers, there was no improvement and the results examined with \td{\gls{sem} (where is the evidence?)} reminded rather of a sparse crust than of a film. 
 %It is assumed that the solution was far from the optimum for a sol-gel process. 
@@
 %These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aquatic recipe. 
-Large cracks, non coated areas and inhomogeneity were 
+Large cracks, non-coated areas and inhomogeneity were 
 %part of (ausmachen) 
@@
 and hardly any pin holes were electrically observed on similar samples. 
+\todo{where is the evidence?}
 
 %%%%%% STABILITY
-As soon as the solution showed initial cloudiness, it was declared as unstable and used no more for \gls{db}. 
+As soon as the solution showed initial cloudiness, it was declared as unstable and used \td{no more for \gls{db}. (coating! DB = deutsche Bahn ... ist mir schon vorher aufgefallen)}
 The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent \gls{acoh} with \gls{ipo}.
@@
 The aging process was accelerated by being in contact with "fresh" air in contrast to being sealed. 
-It therefore dependent on the water or oxygen in the air corresponding to an oxidation or hyrolization process.
+It therefore dependent on the water or oxygen in the air corresponding to an \td{oxidation or hyrolization (you're a chemist. so what is it?)} process.
 %
@@
 %
-It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness 
-the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
+\td{It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time.
+(but the conc.\ changed)}
 This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
@@
 %%%%%%%%% CROSS SECTION
-Figure~\ref{fig:sem-cs1} shows the cross section of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
-The large crystalline structure which makes up most of the upper part of the image is \gls{fto}. 
+Figure~\ref{fig:sem-cs1} shows the \td{cross section} of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
+The large crystalline structure, which makes up most of the upper part of the image is \gls{fto}. 
 The boundary to glass is visible at the very top. 
 %On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
-On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe)  can be observed.
+On the lower edge of \gls{fto} a circa \nm{100} thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe)  can be observed.
 Measuring the cross section on steel was not as straight forward because the ductility of steel prevents fractures of the substrate. 
@@
 \subsection{X-ray diffraction}
+\todo{of what?}
 \begin{figure}
@@
 	\includegraphics[width=\picwidth]{Pics/xrd.png}
-	\caption{XRD spectra of steel substrate (yellow), \gls{zro} (blue), $\alpha$-Fe (green, idealized) and cubic-\gls{zro} (purple, idealized)\cite{gkatz1971xray}}
+	\caption{XRD spectra of steel substrate (yellow), \gls{zro} (blue), $\alpha$-Fe (green, idealized) and cubic-\gls{zro} (purple, idealized)\cite{gkatz1971xray} \td{(text in fig too small, use an offset, looks very amorphous to me)} }
 	\label{fig:xrd}
@@
 \Gls{xrd} was used in order to confirm that the produced layer is indeed \gls{zro}. 
-Figure~\ref{fig:xrd} shows \gls{xrd} spectra of the substrate (steel) and 
+Figure~\ref{fig:xrd} shows diffractograms of the substrate (steel) and 
 the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix~\ref{sec:app-emma}).
-In addition, two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
+In addition, two idealized diffractograms from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
 %
-The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ (highest to lowest intensity) clearly stand out against the noise from the experimental spectrum.
-%can be clearly seen in the experimental spectra.
+The four largest peaks of cubic \gls{zro} at \td{$2\theta=30, 51, 60, 35$    (why?
+For what?)} (highest to lowest intensity) clearly stand out against the noise from the experimental \td{diffractogram.
+(spectrum: or 2theta and those numbers need a unit (grad))}  %can be clearly seen in the experimental spectra.
 They confirm that the produced substance is \gls{zro}.
@@
 \subsection{Spectrometry}
-
+\todo{of what?}
 \begin{figure}[htb]
@@
 
-In figure~\ref{fig:ir-gt} transmission spectra of \gls{uv}/\gls{vis}/\gls{nir} light can be seen. 
+In figure~\ref{fig:ir-gt} \gls{uv}/\gls{vis}/\gls{nir} transmission spectra \td{of what?} can be seen. 
 Each sample had different numbers of layers. 
-The incident angle was 0 degree for each sample.
+The incident angle was 0 \td{degree} for each sample.
 %differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
@@
 %
-Figure~\ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 degrees. 
+Figure~\ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 \td{degrees}. 
 %The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
@@
 \subsection{Current Voltage Curves} 
+\todo{of what?}
 \begin{figure}
@@
 All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
-and around a fifth exhibit hardly any current which is ideal (see figure~\ref{fig:iv-stat-good}).
+and around a fifth exhibit hardly any current, which is ideal (see figure~\ref{fig:iv-stat-good}).
 A single example for a very low conductance measurement in non-logarithmic scale can be seen in figure~\ref{fig:iv-nocurrent}.
@@
 Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
-but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
+but there are some pinholes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
 %
@@
 Finally, figures~\ref{fig:iv-log-bad} and~\ref{fig:iv-stat-bad} show a sample 
-where all measurement exhibit relatively high voltages and high calculated conductances. 
+where all measurements exhibit relatively high voltages and high calculated conductances. 
 This indicates a overall bad condition of the \gls{zro} layer for insulating. 
@@
 \subsection{Preoptimization}
+\todo{of what?}
 Before the optimization with the \gls{emma} algorithm, 
 the boundaries of the input variables were explored. 
-Especially, the \gls{db} velocity $v_{DB}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
+Especially, the \td{\gls{db}} velocity $v_{DB}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
 was varied and examined during pre-optimization. 
-The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
-If the $v_{DB}$ was too slow (less than \mmps{1}), no layer was formed. 
-The reason is that the force exerted by the blade on the liquid is not strong enough to overcome surface tension. 
+The slower the \td{\gls{db}} velocity, the more uniformly the solution evaporated. 
+If the $v_{DB}$ was too slow (less than \mmps{1}), no \gls{zro} was formed. 
+The reason is that the force exerted by the blade on the liquid is not strong enough to overcome \td{surface tension. (for buoh? cant believe this?)}
 This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
-Additionally, the temperature while \gls{db} $T_{DB}$ affects the evaporation process together with the \gls{db} velocity $v_{DB}$.
+Additionally, the coating temperature affects the evaporation process together with the \gls{db} velocity $v_{DB}$.
 

### 2023-12-28 doc/Thesis/chapter/020-theory-materials.tex
work on todos until chap3

--- 2023-11-27 doc/Thesis/chapter/030-theory-materials.tex
@@
 
-\section{Materials and Their Analysis}
-\todo{COATING OF THE SUBSTRATE or sample preparation}
+%\section{Materials and Their Analysis}
+\section{Sample preparation}
+%\todo{COATING OF THE SUBSTRATE or sample preparation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\pagebreak[4]
+%\pagebreak[4]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Scanning Electron Microscopy}
+\ds{
 \td{FOR ME PERSONALLY TOO MUCH GENERAL INFORMATION}
@@
 A more detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}. 
+}
 \Gls{sem} is a microscopic technique which allows visualization of surfaces with features in the nanometer regime. 
@@
 which - in vacuum - moves with the speed of light ($c = \mps{299792458}$)\cite{gHobel2006international}.
-In other materials light moves with the velocity $v=\frac{c}{n(\lambda)}$, where $n(\lambda)$
+In other materials light moves with the velocity $v=c/n(\lambda)$, where $n(\lambda)$
 is the refractive index which is dependent on the wavelength $\lambda$. 
@@
 from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
-X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with \td{it's adsorbed by certain groups?)} molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins.
-%Molecular vibrations can be separated in valence and deformation vibrations.
+X-rays interact with core electrons, \gls{uv}/\gls{vis} with valence electrons, \gls{ir} with 
+%\td{it's adsorbed by certain groups?)} 
+vibrations of certain groups, microwaves with molecular rotations and radio with electron and nuclear spins. 
 %
 % UVVis
-Two prerequisites need to be fulfilled in order for a \gls{uv}\gls{vis} photon to be 
+Two prerequisites need to be fulfilled in order for a \gls{uv}/\gls{vis} photon to be 
 absorbed by a molecule or atom.
-Firstly, \td{the energy must be the same as the difference between two electronic states, a lower populated and a higher empty orbital. }
+Firstly, \td{the energy of the photon must be the same as the difference between two electronic states, a lower populated and a higher empty orbital.}
 The electron will then be excited into a energetically higher orbital.
-Secondly, the \td{spin state (which spins?)} of both states has to be the same otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely.
+Secondly, the electronic spin state of the molecule has to be the same before and after, otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely.
 
 % IR
-\td{ \Gls{ir} photons }interact with molecular vibrations, which is only a part of the degrees of freedom of a molecule.
+\Gls{ir} light interacts with molecular vibrations, which is only a part of the degrees of freedom of a molecule.
 A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
@@
 Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
-Only vibrations that change the dipole moment of the molecule are \td{\gls{ir} active. (does Raman not also use IR)}
+Only vibrations that change the dipole moment of the molecule are \gls{ir} active, except Raman spectroscopy. 
+%\td(does Raman not also use IR)}
 The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes which lead to intricate patterns in the so called fingerprint region.

### 2023-12-28 doc/Thesis/chapter/021-theory-calculations.tex
work on todos until chap3

@@
 
-\input{chapter/033-linreg-krr-svm.tex}
+\input{chapter/023-linreg-krr-svm.tex}
 
@@
 Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g.
-kernel functions), whose number of parameter quickly \td{exceeds the practical} for moderate dimensional problems ($n>5$).
+kernel functions).
+%, whose number of parameter quickly \td{exceeds the practical} for moderate dimensional problems ($n>5$).
+Advantages of \Gls{mars} are that it uses less parameters and it produces continuous models with continous derivatives.
 %
@@
 %
-The main advancements of \gls{mars} is the ability to fit (possibly complex) interactions and non-linearities without losing interpretability. 
+Furthermore, \gls{mars} has the ability to fit (possibly complex) interactions and non-linearities without losing interpretability. 
 %
@@
 %
+
 %%% FORWARD MARS
@@
 
-(2) If the query space is so vast, that randomly querying might explore domains\td{, which} might lead to uninteresting or even misleading information.
+(2) If the query space is so vast, that randomly querying might explore domains, which might lead to uninteresting or even misleading information.
 %Both encompass nearly all cases. 
@@
 Each possible combination of discrete values is tested.
-\td{While} this is the most informative design it will more often than not be infeasible due the curse of dimensionality\cite{cherkassky1998learning}.
+The full factorial design will mostly be infeasible due the curse of dimensionality\cite{cherkassky1998learning} despite it being the most informative design.
 % 2-LVL FACTORIAL

### 2024-01-07 doc/Thesis/chapter/01-introduction.tex
first correction round

@@
 The minimization of the conductance of the layer is performed with a particle swarm optimization 
-algorithm. 
+algorithm which has the coating process variables as input. 
 %The resulting optimum is compared with other optimization methods.
-\td{and how do you transfer knowledge ...}
+%\td{and how do you transfer knowledge ...}
 
@@
 %some background information on topics of PV, \td{material science} and \td{computational science (more detail)} which were used in this work. 
-information on the general \td{functionsweise} of PV, the structure, characteristics and properties of materials which were used and computational, statistical and machine learning methods for data processing.
+information on the general working principles of PV, the structure, characteristics and properties of materials which were used and computational, statistical and machine learning methods for data processing.
 

### 2024-01-07 doc/Thesis/chapter/020-theory-materials.tex
first correction round

@@
 In the late 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space exploration.  
-In 1958 the US American Vanguard I\cite{vanguard2004} and the soviet Sputnik III\cite{sputnik} were the first satellites with solar cells with efficiencies under 10 \% (\td{cite?}).
+In 1958 the US American Vanguard I\cite{vanguard2004} and the soviet Sputnik III\cite{sputnik1959} were the first satellites with solar cells with efficiencies under 10 \% (\td{cite?}).
 These "solar batteries" - as they were called then - allowed the transmission system of Vanguard I to be operating for over a year after the chemical battery powered system stopped transmitting after 20 days\cite{vanguard2004}.

### 2024-01-07 doc/Thesis/chapter/021-theory-calculations.tex
first correction round

@@
 
-A \gls{ga} is a search algorithm that uses principles of natural selection and \td{genetics} to optimize a search space.
+A \gls{ga} is a search algorithm that uses principles of natural selection and genetics (mutations and recombination) to optimize a search space.
 A GA starts with a population of randomly generated solutions, or chromosomes, and then proceeds to breed them together to create new solutions.
 The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes.
-This process is repeated until a \td{satisfactory} solution is found.\footnote{This paragraph was written by GPT3\cite{Liu2021gpt} given the input "Introduction to genetic algorithms: "}
+This process is repeated until a \td{satisfactory} solution is found.\footnote{This paragraph was written by GPT3\cite{Liu2021gpt} given the input "Introduction to genetic algorithms:"}
 

### 2024-01-07 doc/Thesis/chapter/03-experimental.tex
first correction round

--- 2023-11-28 doc/Thesis/chapter/04-experimental.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo{materials section and sources (incl. purities is missing!}
-In this section the used chemicals, substrates, experimental procedures and any used
-\td{equipment (what do you mean?)} are described. 
+\todo{materials section and sources (incl. purities is missing!) }
+In this section the used chemicals, substrates, experimental procedures and any used lab equipment are described. 
+\td{All chemicals used in this work are of reagent-grade purity and without further purification.}
 %\td{Also, the long, exhaustive path to the base solution is described}
@@
 %}
-\ds{
-Four different substrates were used throughout this work: 
-microscope glass slides, \gls{ito} glass plates, \gls{fto} glass plates and steel foil provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
-}
 %
-Glass was used because of its availability and to measure transmission and reflectance 
-spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
-is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (don't follow?)}
+Glass was used because of its low price point and availability and to measure transmission and reflectance spectra. 
+\gls{fto} and \gls{ito} were used in order to have a conducting substrate. 
+%, which is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (don't follow?)}
+The conducting substrate allows for easy measurement of electric conductance in vertical direction.
+Furthermore, while taking a \gls{sem} micrograph the sample would quickly accumulate negative charge and repell further electrons without a conducting substrate.
 The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Aquatic Precursor Solutions}\label{sec:exp-sol-aq}
+\subsection{Aquatic Precursor Solutions}
+\label{sec:exp-sol-aq}
 \gls{zrpro} was added to acetylacetone (\gls{acac}) while stirring and in a separate vessel \gls{water} 
@@
 was added to isopropyl aclohol (\gls{ipo}) and both were stirred for one hour. 
-These additives were added to influence pH and surface tension with the goal to \td{influence the resulting layer (in terms of what?)}. % \td{see Parvulescu2015}
-The \gls{water}-\gls{ipo} mixture was added to the \td{other solution (which? NOT CLEAR!)} and stirred over night. 
+These additives were added to influence pH and surface tension with the goal to influence the homogeneity of the resulting layer. %(in terms of what?)}. % \td{see Parvulescu2015}
+The \gls{water}-\gls{ipo} mixture was added to the \gls{zrpro}-gls{acac} solution and stirred over night. 
 The exact volumes can be taken from table~\ref{tab:rec1}.
-Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
+%Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
+Unfortunately, this solution failed to produce homogeneous layers, but instead only resulted in sparse patches of \gls{zro} on the substrate.
 Thus, an alternative solution was found.
@@
 \subsection{Buthanolic solution}\label{sec:exp-sol-bu}
-\todo{what did you did you do percisely! It must be logical and should be followed}
+%\todo{what did you did you do percisely! It must be logical and should be followed}
 Five different concentrations of the buthanolic solutions were prepared.
+\ds{
 \td{Not all (which?)} chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
 starting materials had to be chosen from the available inventory. 
+}
+The base recipe (\gls{1f}) was inspired by Hu~et~al.\cite{Hu2016}.
+\Gls{buoh}, \gls{zrpro}, \gls{acac} and \gls{ipo}/\gls{acoh} were used as solvent, precursor, chelating agent and stabilization agent, respectively.
 
-The \td{\gls{1f}} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
-The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar 
+%The \td{\gls{1f}} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
+The other four buthanolic solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar 
 but with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
@@
 %\td{p34}
-\td{Different} solvents (butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
-(\gls{acac} and citric acid) were tested and later in the process - just before the 
-\td{particle swarm optimisation} started - the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
+Solvents (butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
+(\gls{acac} and citric acid) were tested and later in the process - just before 
+starting the optimization of the process variables
+%the \td{particle swarm optimisation} started 
+- the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
 The most promising combination of solvent, chelating agent and stabilization reagent was 
@@
 %15-15-30    30-30-120
-%DB          spin coating
+%C          spin coating
 %200C        200/400C
@@
 On two opposing edges adhesive tape was applied to create a valley in between. 
-After the layer was applied and dried, the tape was removed and the substrate heat treated \td{(at which T?)}.
+After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
+%\td{(at which T?)}.
 Lower \gls{db} velocities resulted in less homogeneous layers.
@@
 %partially heated with a heat gun.
-The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in 
-\SI{0.05}{\milli\meter} steps and \td{did not substantially alter the results. (what do you mean?)}
-For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
+%The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in \SI{0.05}{\milli\meter} steps and \td{did not substantially alter the results. (what do you mean?)}
+%For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
+All experiments were performed with a blade height of \SI{0.2}{\milli\meter}.
 %
 %Eventually, a heatable vacuum plate was used. It 
-The heatable vacuum plate
-had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where 
-underpressure could be applied to keep the substrate in place. 
-Most of them were covered with tape to increase the suction intensity at the remaining ones \td{(see figure~\ref{fig:eric}).
-After} setting the temperature of the heating plate to 
-\SI{200}{\celsius}, the temperature of the vacuum plate (room temperature, \SI{40}{\celsius}, 
-\SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) and the 
-\gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
+The heatable vacuum plate had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where underpressure could be applied to keep the substrate in place. 
+Most of them were covered with tape (see figure~\ref{fig:eric}) to increase the suction intensity at the remaining ones.
+After setting the temperature of the heating plate to \SI{200}{\celsius}, the temperature of the vacuum plate 
+(room temperature, \SI{40}{\celsius}, \SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) 
+and the \gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
 the blade was put into its initial position, the sample was placed on the vacuum plate and the vacuum 
@@
 was removed from the plate with a wipe. 
-The coated substrate was \td{transferred to the \SI{200}{\celsius} heating plate and rested on there for \minutes{5}. (why? what was the purpose?)}
+The coated substrate was dried for \minutes{5} on a \SI{200}{\celsius} heating plate.
+%\td{transferred to the \SI{200}{\celsius} heating plate and rested on there for \minutes{5}. (why? what was the purpose?)}
 This process of applying a \gls{zro} layer was repeated as many times as needed.
@@
 		Erichsen Coatmaster 510 film applicator (\underline{3}) with heatable vacuum plate.
-        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\micro\meter}.
+        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\milli\meter}.
 		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
@@
 A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate the coated samples. 
-The heating plate could hold temperature for a certain amount of time, but heated with a 
-fixed rate of \td{circa (and how do you optimze ca?)} \oc{10}/\minutes{}.
-In order to achieve a lower overall heating rate several temperature ramps and plateaus 
-were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
+The heating plate could hold temperature for a certain amount of time, but heated with a fixed rate of \oc{10}/\minutes{}.
+In order to achieve a lower overall heating rate several temperature ramps and plateaus were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
 This heating procedure was called HP1.
@@
 \section{Characterization}
-\td{All \gls{sem} micrographs were taken with a Zeiss Supra 40. (conditions? were samples sputtered etc...)}
+All characterization procedures were executed at room temperature.
+All \gls{sem} micrographs were taken with a Zeiss Supra 40 with  \SI{5}{\kilo\volt} acceleration voltages.
+%\td{5kV, raum temperature, vacuum???}
 \Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
@@
 in Opus software. % included in the spectrometer. 
+%\td{
 \Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer.
-All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.
+The diffractograms were measured for \SI{2}{\minute} in reflection mode with \ch{Cu}-$K_{\alpha}$ radiation ($\lambda$=\SI{1.541874}{\angstrom}).
+%. (where are the conditions?)}
+All \gls{xrd} diffractograms were taken at \SI{5}{\degree} incident angle and compared to the internal database.
 
@@
 	(b) Edge of a sample with the probe touching silver paste on top of a sanded patch.
-	(c) From the source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.}
+	(c) From the voltage source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.\td{(what is XXX circuit?)}}
 \end{figure}
@@
 
-\iffalse
-\begin{figure}[hbt]
-    \centering
-    \begin{circuitikz} \draw
-        (0,0) to[european voltage source] (0,2)
-        to[ammeter] (2,2) 
-        to[generic,l=W] (4,2) 
-        to[generic,l=Au] (6,2) 
-        to[generic,l=Al] (8,2)
-        -- (8,2)
-        to[generic,l=ZrO$_2$] (8,0)
-        -- (8,0)
-        to[generic,l=steel] (6,0)
-        to[generic,l=Ag] (4,0)
-        to[generic,l=Au] (2,0) 
-        to[generic,l=W] (0,0) 
-            ;
-    \end{circuitikz}
-    \caption{Sketch of circuit, from the source clockwise: varibale voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.}
-    \label{fig:circuit}
-\end{figure}
-\fi
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Pre-optimization}\label{sec:exp-preopt}
+\section{Pre-optimization of Coating Procedure}
+\label{sec:exp-preopt}
+%\td{preopt of what? recipe?}
 %\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
 %\td{Screening}
-%The main part of the screening pre-optimization samples were optimized via biotic reinforcement learning (i.e. my brain). 
-The main part of all samples (200 out of 244) were pre-optimization samples, 
-from which the bulk were screening experiments optimized via biotic reinforcement learning 
-(i.e. my brain) in order to obtain reasonable constraints for computerized pre-optimization. 
+%244 - 93 aquatic - 103 testing - 191 buthanol - 206 preopt - 244 emma
+% 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
+244 samples were produced: 93 samples with the aquatic recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimisation to find fitting constraints for the final optimization (see section \ref{sec:ss}).
+
+%The first 200 recipes were optimized via biotic refinforcement learning (i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization.
+\td{(xxx but using a completely untested recipe!)}
+%The main part of all samples (200 out of 244) were pre-optimization samples,  from which the bulk were screening experiments optimized via biotic reinforcement learning  (i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization.
+\td{(xxx but using a completely untested recipe!)}
 %Initially, glass plates were doctor bladed manually with aquatic solution and calcinated 
@@
 %\todo{different additives, heating programs (NT1-NT5 and HP1), blade distances (distance between blade and substrate) and layer counts were tried}
-Composition of the aquatic solution, heating program, blade distance (distance between 
-blade and substrate) and layer count were varied but no homogeneous layers resulted. 
-Thus, 
-the buthanolic recipe was introduced, which gave rise to homogeneous films.
-After the blade moved over the substrate the remaining liquid needed about a minute 
-to evaporate at room temperature. 
+%Composition of the \td{aquatic solution (I thought this did not work?)}, heating program, blade distance (distance between blade and substrate) and layer count were varied but no homogeneous layers resulted.
+%
+%The buthanolic recipe was introduced, which gave rise to homogeneous films.
+%\td{After the blade moved over the substrate the remaining liquid needed about a minute to evaporate at room temperature. (2x mentioned this before!)}
 %\td{
-The then current procedure resulted in clear and continuous films, but was plagued from 
-inhomogeneities due to drying stains. 
-The drying stains could be circumvented by using a heat gun, but the results were not 
-reproducible. 
-The glass plate of the film applicator was therefore exchanged with a metal plate which
-allowed to hold the sample in place through underpressure and simultaneously heat it to a certain 
-temperature. The bounds of the process variables were then explored in a preliminary study 
-using the Plackett-Burman\cite{Plackett1946} design implemented in the \texttt{python3} 
-library \texttt{pyDOE}. With 
+%The then current procedure resulted in clear and continuous films, but was plagued from inhomogeneities due to drying stains. 
+%The drying stains could be circumvented by using a heat gun, but the results were not reproducible. 
+The glass plate of the film applicator was exchanged with a metal plate.
+This allowed to hold the sample in place through underpressure and control temperature. 
+The bounds of the process variables were then explored in a preliminary study 
+using the Plackett-Burman\cite{Plackett1946} design implemented in the \td{\texttt{python3}}
+library texttt{pyDOE} \td{(Version 0.3.8)}; 
+with 
 (1,5), (4,10), (400,500), (120,480), (0.1,5) and  (20,80) 
 as nominal and extreme values for 
-relative concentration of Zr $c_{zr}$, number of layers $\lambda$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively.
+relative concentration of Zr $c_{zr}$, number of coating layers $\lambda$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{C}$[\mm{}/\s{}] and \gls{db} temperature $T_{C}$[\oc{}], respectively.
 After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see table \ref{tab:pre-opt1}).
@@
 	%		&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
-			$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
+			$c_{zr}$	&$\lambda$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
 			\hline
@@
 			\hline\hline
-			$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
-	%conc	&layers	&$v_{\textrm{DB}}$	&$T_{\textrm{DB}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\
+			$c_{zr}$	&$\lambda$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
+	%conc	&layers	&$v_{\textrm{C}}$	&$T_{\textrm{C}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\
 			\hline
@@
 
-%$T_{DB}$[\oc{}]
-%$v_{DB}$[\mm{}/\s{}]
+%$T_{C}$[\oc{}]
+%$v_{C}$[\mm{}/\s{}]
 %$T_{cal}$[\oc{}]
@@
 %implemented in the \texttt{python3} library \texttt{pyDOE}.
-%For the preliminary study a DB machine and NT were used and the steel. 
+%For the preliminary study a C machine and NT were used and the steel. 
 \ds{In the preliminary study only steel was used as substrate.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Shortly before the \gls{pso} the stabilization agent was changed from \gls{acoh} to 
-\gls{ipo} because of much better solution stability.
+The stabilization agent was changed from \td{\gls{acoh} to \gls{ipo} 
+shortly before the \gls{pso}
+(but why?)} because of much better \td{solution stability. (how did you test this?? see section \ref{sec:res-mat})}
 The - up to this moment - best process was chosen to be tested with 
-\ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
+\ml{1} \gls{acoh} (sample no.~199), \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} (sample no.~201) and \ml{1} \gls{ipo} (sample no.~192).
 %\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
-The sample produced with \gls{ipo} as stabilization agent 
-showed comparable passivization results and better stability of the solution. 
-Therefore \gls{ipo} was used  as stabilzier in further experiments.
+The sample produced with \gls{ipo} as stabilization agent showed comparable passivization results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
+Therefore, \gls{ipo} was used  as stabilzier in further experiments.
 %\td{After the boundaries of the solution were fixed }
@@
 %There were many variables which had to be taken into account. 
-%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
+%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, C velocity and C temperature as input variables.}
 See table~\ref{tab:input} for the input space spanned during the optimization.
@@
         \hline\hline
-		$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
+		$c_{zr}$	&$\lambda$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
 %        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\

### 2024-01-07 doc/Thesis/chapter/04-computational-details.tex
first correction round

@@
 %\td{describe problem and solution found}
-\td{Multiple \gls{iv} curves were measured (where are they?)} for every sample.
+Multiple \gls{iv} curves were measured (see figure \ref{fig:iv}) for every sample.
 The main difficulty faced in processing the data was to present the measurements obtained 
@@
 
-\section{Sample Selection}
+\section{Evolutionary Model-based Multiresponse Approach}
 \label{sec:ss}
-\todo{for what?}
+%\todo{for what?}
 An evolutionary approach was chosen, namely a multi-objective 
@@
 		\hline\hline
-        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$\lambda$	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
+        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$\lambda$	&$T_{C}$[\oc{}]	&$v_{C}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
 		\hline
@@
 
-The \textit{optimizands} where chosen to be \td{$\gamma$, $\rho$, $\lambda$ and $v_{cal}$, (here it would help me to remind the reader what the symbols are!)}
+The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $\lambda$ and $v_{cal}$, 
+(i.e. conducticity, pinhole density, coating layer count and heating rate)
 where $\gamma$, $\rho$ and $\lambda$ are to be minimized and $v_{cal}$ to be maximized.
@@
 The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
-The \td{experiments} are executed, \td{measured (unclear!)} and evaluated according to section 
+The samples are produced, the \gls{iv} curves are measured and measurements evaluated according to section 
 \ref{sec:exp} and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), 
-\todo{$\lambda$ (numbers of layers) (tstill not clear! what is meant?!)} and $v_{cal}$ (heating rate of calcination process in 
+$\lambda$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in 
 \oc{}/\minutes{}) are supplied to the program. 
@@
 %moves towards the optimum solution.
-The population for the next time step is generated and the experiments are again \td{executed, measured and evaluated. (unclear!)}
+The population for the next time step is generated and 
+again the samples are produced, the \gls{iv} curves are measured and measurements evaluated.
+%the experiments are again \td{executed, measured and evaluated. (unclear!)}
 Each time step thus includes experiment identification, solution preparation, coating deposition and layer analysis.
@@
 % KRR 
-The hyperparameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
+The hyperparameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$  and $\alpha$ (regularization parameter).
 The kernel took the form of \gls{rbf}, sigmoid or polynomial with degree 1--3.
 The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5 and 10.
-%and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
 Note that $\gamma_{ml}$ is used differently in each kernel.
+
 % SVM
 The kernels for \gls{svm} were the same as for \gls{krr}. 
-Further hyper parameters were \td{$C$, $\varepsilon$ and $\gamma_{ml}$. 
-$C$ and $\varepsilon$ (define again, forgotten until now) } took the values 0.05--1 with step size 0.05 for \gls{svm} and \gls{krr}.
+\Gls{svm} uses $C$ instead of $\alpha$ as regularization parameter) and  $\varepsilon$ as \gls{svm} tube size parameter.
+$C$ and $\varepsilon$ took the values 0.05--1 with step size 0.05. 
 \Gls{svm} additionally used the \texttt{scale} for $\gamma_{ml}$.
-%\td{and was the same as for \gls{krr} plus \texttt{scale}.} %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
 \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
 and $\sigma(\mathbf{X})$ the variance of the input variables.
+
 % GRID SEARCH 
-The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
+The input variables ($c_{zr}$, $\lambda$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$) 
 of the \gls{emma} data set were scaled with the routine \texttt{sklearn.preprocessing.StandardScaler().fit\_transform()}. %\td{scaled before each calculation.}

### 2024-01-07 doc/Thesis/chapter/050-results-material.tex
first correction round

@@
 Followed by the presentation of the results obtained by optimization and exploration with the \gls{emma} method. 
-Finally, the results of alternative regression methods \td{let loose on (language is too colloquial)} the data are compared with the \gls{emma} method.
+Finally, alternative regression methods were applied to the data and the results are compared with the results of the \gls{emma} method.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Material Scientific and Pre-optimization}
+\section{Material Properties of the Produced Layers}
 \label{sec:res-mat}
-\todo{of what?}
+%\todo{of what?}
 %\subsection{Solution}
 %%%%%%%% AQUATIC 
-As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a \td{homogeneous layer. (of what?)}
+As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer of \gls{zro}.
 The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
@@
 %%%%%% STABILITY
-As soon as the solution showed initial cloudiness, it was declared as unstable and used \td{no more for \gls{db}. (coating! DB = deutsche Bahn ... ist mir schon vorher aufgefallen)}
+As soon as the solution showed initial cloudiness, it was declared as unstable and used no more for \gls{db}. %\td{(coating! DB = deutsche Bahn ... ist mir schon vorher aufgefallen)}
 The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent \gls{acoh} with \gls{ipo}.
@@
 The aging process was accelerated by being in contact with "fresh" air in contrast to being sealed. 
-It therefore dependent on the water or oxygen in the air corresponding to an \td{oxidation or hyrolization (you're a chemist. so what is it?)} process.
+It therefore dependent on the water in the air corresponding to an hyrolization process\cite{Hu2016}.
 %
@@
 %
-\td{It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time.
-(but the conc.\ changed)}
+It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
 This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
@@
 %%%%%%%%% CROSS SECTION
-Figure~\ref{fig:sem-cs1} shows the \td{cross section} of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
+Figure~\ref{fig:sem-cs1} shows the cross-section of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
 The large crystalline structure, which makes up most of the upper part of the image is \gls{fto}. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{X-ray diffraction}
-\todo{of what?}
+\subsection{X-ray diffractogram of \ch{ZrO2}}
+%\todo{of what?}
 \begin{figure}
@@
 %
-The four largest peaks of cubic \gls{zro} at \td{$2\theta=30, 51, 60, 35$    (why?
-For what?)} (highest to lowest intensity) clearly stand out against the noise from the experimental \td{diffractogram.
-(spectrum: or 2theta and those numbers need a unit (grad))}  %can be clearly seen in the experimental spectra.
-They confirm that the produced substance is \gls{zro}.
-Raman spectra are needed 
-to further clarify the phase, 
+The four largest peaks of the cubic \gls{zro} reference diffractogram at $2\theta=$ \ang{30}, \ang{51}, \ang{60}, \ang{35} (highest to lowest intensity) can also be observed in the experimental diffractogram.
+%.
+clearly stand out against the noise from the experimental diffractogram.
+They confirm that the produced substance is indeed \gls{zro}.
+Raman spectra are needed to further clarify the phase, 
 since cubic and tetragonal phases are difficult to distinguish from \gls{xrd} alone\cite{Purohit2006Combustion}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Spectrometry}
-\todo{of what?}
+\subsection{Spectrometry of \ch{ZrO2} layers}
+%\todo{of what?}
 \begin{figure}[htb]
@@
 
-In figure~\ref{fig:ir-gt} \gls{uv}/\gls{vis}/\gls{nir} transmission spectra \td{of what?} can be seen. 
+In figure~\ref{fig:ir-gt} \gls{uv}/\gls{vis}/\gls{nir} transmission spectra of \gls{zro} layers on glass slides can be seen. 
 Each sample had different numbers of layers. 
-The incident angle was 0 \td{degree} for each sample.
+The incident angle was \ang{0} for each sample.
 %differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
@@
 %
-Figure~\ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 \td{degrees}. 
+Figure~\ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of \ang{45}. 
 %The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Current Voltage Curves} 
-\todo{of what?}
+\subsection{Current Voltage Curves of \ch{ZrO2} layers} 
+%\todo{of what?}
 \begin{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Preoptimization}
-\todo{of what?}
+\subsection{Preoptimization of Coating Procedure}
+%\todo{of what?}
 Before the optimization with the \gls{emma} algorithm, 
 the boundaries of the input variables were explored. 
-Especially, the \td{\gls{db}} velocity $v_{DB}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
+Especially, the \gls{db} velocity $v_{C}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
 was varied and examined during pre-optimization. 
-The slower the \td{\gls{db}} velocity, the more uniformly the solution evaporated. 
-If the $v_{DB}$ was too slow (less than \mmps{1}), no \gls{zro} was formed. 
-The reason is that the force exerted by the blade on the liquid is not strong enough to overcome \td{surface tension. (for buoh? cant believe this?)}
+The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
+If the $v_{C}$ was too slow (less than \mmps{1}), no \gls{zro} layer was formed. 
+The reason could be that the force exerted by the blade on the liquid is not strong enough to overcome the combination of gravity and the surface tension of the alkoxide solution.
 This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
-Additionally, the coating temperature affects the evaporation process together with the \gls{db} velocity $v_{DB}$.
+Additionally, the coating temperature affects the evaporation process together with the \gls{db} velocity $v_{C}$.
 

### 2024-01-07 doc/Thesis/chapter/051-results-emma.tex
first correction round

--- 2023-12-28 doc/Thesis/chapter/061-results-emma.tex
@@
 Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
-The \td{best (what is "best"? How do you measure that?)} recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
+The most insulating recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
 The experiments for generation 5 where not executed but 
@@
 %%% BEST PREDICTED RECIPE
-The sample predicted as best by the algorithm is experiment number 13 with 
-lowest $c_{zr}$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$ and second highest $\lambda$. 
+The sample predicted as optimum by the algorithm is experiment number 13 with 
+lowest possible $c_{zr}$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$ and second highest possibel $\lambda$ (see table \ref{tab:input}). 
 %lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
@@
 	\centering
-	\caption{Global best per generation with experiment numbers and experiment conditions}% \td{include units?}}
+	\caption{Global optimum per generation with experiment numbers and experiment conditions}% \td{include units?}}
 	\label{tab:emma-Gb}
@@
         \hline\hline
-		generation& measurements &enr &$c_{zr}$ &$\lambda$ &$v_{DB}$ &$T_{DB}$ &$v_{cal}$ &$T_{cal}$\\
+		generation& measurements &enr &$c_{zr}$ &$\lambda$ &$v_{C}$ &$T_{C}$ &$v_{cal}$ &$T_{cal}$\\
         \hline
@@
 %%% OVER TIME 
-The only clear trend from table \ref{tab:emma-Gb} is the \td{layer count (again not yet clear)}, which rises with \td{the generations (which?)}. 
+The only clear trend from table \ref{tab:emma-Gb} is the count of \gls{zro} layers count, which rises with the generations of the \gls{emma} algorithm.
 The remaining input variables remained more or less the same except for the 3rd generation. 
@@
 %
-Contrarily, the predicted conducticity $\hat{\gamma}$ for each generation's \td{best (best in what?)}
+Contrarily, the predicted conducticity $\hat{\gamma}$ for each generation's optimum
 (predicted by the very generation's \gls{rf}) does increase with each iteration 
@@
 %GENERATIONS
-\td{How did you determine the pinhole densisty}
 In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
-conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
+conducticity $\gamma$ and pin hole density $\rho$ (see section \ref{sec:eval}), of each particle at each generation.
 The \td{green} points at generation number 0 indicate particles which were not included to be propagated. 
@@
 %    \label{eq:emma-phd1}
-%    \hat{\rho}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{DB}\cdot T_{cal} + 0.00080 \cdot h(6-\lambda)\cdot T_{cal}\\
+%    \hat{\rho}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{C}\cdot T_{cal} + 0.00080 \cdot h(6-\lambda)\cdot T_{cal}\\
 %    \label{eq:emma-G1}
-%    \hat{\gamma}_1 &= -26  + 0.0025 \cdot T_{DB}\cdot T{cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{cal} \\
+%    \hat{\gamma}_1 &= -26  + 0.0025 \cdot T_{C}\cdot T{cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{cal} \\
 %    \label{eq:emma-layr1}
-%    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{DB}\cdot T_{cal} -  0.0056 \cdot  h(6-\lambda)\cdot T_{cal}\\
+%    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{C}\cdot T_{cal} -  0.0056 \cdot  h(6-\lambda)\cdot T_{cal}\\
 %    \label{eq:emma-vcal1}
-%    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{DB}\cdot T_{cal} - 0.0055 \cdot  h(6-\lambda)\cdot T_{cal}\\
+%    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{C}\cdot T_{cal} - 0.0055 \cdot  h(6-\lambda)\cdot T_{cal}\\
 %
@@
     \label{eq:emma-phd4}
-    \hat{\rho}_4 &=  -0.87 + 0.0047 \cdot  T_{cal} - 0.00036 \cdot  \lambda\cdot T_{cal}  +  0.0024 \cdot  h(\lambda-6)\cdot T_{DB} \\
+    \hat{\rho}_4 &=  -0.87 + 0.0047 \cdot  T_{cal} - 0.00036 \cdot  \lambda\cdot T_{cal}  +  0.0024 \cdot  h(\lambda-6)\cdot T_{C} \\
     \label{eq:emma-G4}
-    \hat{\gamma}_4 &=     -19 + 0.28 \cdot  T_{cal}  - 0.022 \cdot  \lambda\cdot T_{cal}  +  0.16 \cdot  h(\lambda-6)\cdot T_{DB} \\
+    \hat{\gamma}_4 &=     -19 + 0.28 \cdot  T_{cal}  - 0.022 \cdot  \lambda\cdot T_{cal}  +  0.16 \cdot  h(\lambda-6)\cdot T_{C} \\
     \label{eq:emma-layr4}
-    \hat{\lambda}_4 &=  6.8 - 0.014 \cdot  T_{cal}  + 0.0018 \cdot  \lambda\cdot T_{cal}  + 0.0060 \cdot  h(\lambda-6)\cdot T_{DB} \\
+    \hat{\lambda}_4 &=  6.8 - 0.014 \cdot  T_{cal}  + 0.0018 \cdot  \lambda\cdot T_{cal}  + 0.0060 \cdot  h(\lambda-6)\cdot T_{C} \\
     \label{eq:emma-vcal4}
-    \hat{v}_{cal,4} &=  29 - 0.052 \cdot  T_{cal}  + 0.0011 \cdot  \lambda\cdot T_{cal}  -  0.011 \cdot  h(\lambda-6)\cdot T_{DB} 
+    \hat{v}_{cal,4} &=  29 - 0.052 \cdot  T_{cal}  + 0.0011 \cdot  \lambda\cdot T_{cal}  -  0.011 \cdot  h(\lambda-6)\cdot T_{C} 
 \end{align}
@@
 The coefficients in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) have the same signs and differ by a factor of roughly 100.
-\td{This (what is "this?)} fits the data well since the maxima of $\rho$ and $\gamma$ are separated by rough factor of 100 (see figure~\ref{fig:emma-gen} and appendix~\ref{sec:app-emma}).
+This difference in magnitude fits the data well since the maxima of $\rho$ and $\gamma$ are separated by rough factor of 100 (see figure~\ref{fig:emma-gen} and appendix~\ref{sec:app-emma}).
 %, but the positive influence of the layer count $\lambda$ is counter intuitive
@@
 and 
-that therefore the resulting layer does not insulate well if $T_{cal}$ is low. 
+that therefore the resulting layer does not insulate well if $T_{cal}$ is low (under \oc{400}). 
+The oppisite is the case, though. % (see figures \ref{fig:g-tcal} and \ref{fig:phd-tcal}).
 %This would correspond to $+h(400-T_{cal})$
-The \td{original recipe by Hu et al.\cite{Hu2016} used \oc{500} (but to produce Al2O3, so not a surprise? or?)} and thus even \oc{400} are low.
+%The \td{original recipe by Hu et al.\cite{Hu2016} used \oc{500} (but to produce Al2O3, so not a surprise? or?)} and thus even \oc{400} are low.
 \textit{Optimizands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
@@
 This negative correlation could hint a compenzation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
-Similarly, signs of coefficients of $\lambda \cdot T_{cal}$ and $h(\lambda -6) \cdot T_{DB}$ correlate negatively in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) and the product of coefficients and input variables are again similar in order of magnitude.
+Similarly, signs of coefficients of $\lambda \cdot T_{cal}$ and $h(\lambda -6) \cdot T_{C}$ correlate negatively in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) and the product of coefficients and input variables are again similar in order of magnitude.
 %It should be doubted, though, that the $layr$ only appears as interaction term 
-%together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
+%together with $T_{cal}$ and $T_{C}$, which seems rather than an artefact. 
 %
 %It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
-%with $T_{cal}$ and $T_{DB}$. 
-%From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_{DB}$ and then the rest of the independent variables. 
-The process variables $T_{cal}$ and $\lambda$ appear as \gls{bf}s in generation 3 and 4, whereas $v_{cal}$ only appears in generation 3's \gls{rf}s and $T_{DB}$ only in generation 4's \gls{rf}s.
+%with $T_{cal}$ and $T_{C}$. 
+%From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_{C}$ and then the rest of the independent variables. 
+The process variables $T_{cal}$ and $\lambda$ appear as \gls{bf}s in generation 3 and 4, whereas $v_{cal}$ only appears in generation 3's \gls{rf}s and $T_{C}$ only in generation 4's \gls{rf}s.
 This can hint the importance of these variables in the process. 

### 2024-01-07 doc/Thesis/chapter/052-post-emma.tex
rename to fit numbering
first correction round

--- 2023-10-27 doc/Thesis/chapter/062-post-emma.tex
@@
 		\label{eq:linreg-phd}
-		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{DB} + 0.0058\cdot T_{DB} \\
+		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{C} + 0.0058\cdot T_{C} \\
 		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
@@
 		\label{eq:linreg-G}
-		\hat{\gamma} =&  \,\,\qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot \lambda \,\,\quad - 1.2\cdot v_{DB}  \,\,\,\quad +0.2\cdot T_{DB} \\
+		\hat{\gamma} =&  \,\,\qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot \lambda \,\,\quad - 1.2\cdot v_{C}  \,\,\,\quad +0.2\cdot T_{C} \\
 			& \qquad - 0.014\cdot v_{cal} \quad + 0.13\cdot T_{cal} + 7.2
-%		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot \lambda - 1.2\cdot v_{DB} + 0.2\cdot T_{DB} \\
+%		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot \lambda - 1.2\cdot v_{C} + 0.2\cdot T_{C} \\
 %			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
@@
 %
-More particularly, $T_{cal}$ and $T_{DB}$ have positive coefficients, i.e. a negative influence on the resistance 
-and $\lambda$, $v_{DB}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
+More particularly, $T_{cal}$ and $T_{C}$ have positive coefficients, i.e. a negative influence on the resistance 
+and $\lambda$, $v_{C}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
 An indication that the data is strongly tainted by noise (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
@@
 	\begin{tabular}{cccccccc}
-		        & $c_{zr}$      & $\lambda$     & $v_{DB}$      & $T_{DB}$      & $v_{cal}$     & $T_{cal}$\\
+		        & $c_{zr}$      & $\lambda$     & $v_{C}$      & $T_{C}$      & $v_{cal}$     & $T_{cal}$\\
 				\hline\hline
@@
 For better comparison, the influence of an input variable was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{i,min}+x_{i,max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression.
-%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
+%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{C}$. 
 The biggest influence on $\hat\rho$ is  $\lambda$, followed by $T_{cal}$. 
@@
 Resulting $R^2$ are all below zero (see table~\ref{tab:grid-search}). 
-A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$. 
-\td{how can R2 be below zero?}
+A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$ (see \ref{eq:r2}). 
+%\td{how can R2 be below zero?}
 % https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score

### 2024-01-07 doc/Thesis/chapter/06-outlook.tex
first correction round

--- 2023-10-28 doc/Thesis/chapter/07-outlook.tex
@@
 %what did i want to do? 
-The goal of this work was to find a sol-gel doctor blading process resulting in an insulating zirconium ceramic on top of steel.
+The goal of this work was to find a sol-gel blade coating process resulting in an exlectrical insulating zirconium ceramic on top of steel.
 This structure then can be used as substrate for thin layer photovoltaics. 
@@
 %what was done? 
-A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
+A suitable recipe was found\cite{Hu2016} and adapted. 
 The recipe was improved by increasing the stability of the solution. 
+The process variables were optimized via \gls{emma}. 
+%\td{ALSO: How many exp would you over the computer time and effort to find this out?}
 The best parameters found by the \gls{emma} optimization were 
-$c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
+$c_{zr}=2$, $\lambda=10$, $v_{C}=10$, $T_{C}=40$, $v_{cal}=120$ and $T_{cal}=300$.
 %\todo{$T_{cal}=300$}. 

### 2024-01-07 doc/Thesis/chapter/020-theory-materials.tex
rough corrections finished

@@
 absorbed by a molecule or atom.
-Firstly, \td{the energy of the photon must be the same as the difference between two electronic states, a lower populated and a higher empty orbital.}
+Firstly, the energy of the photon must be the same as the difference between two electronic states. %, a lower populated and a higher empty orbital.}
 The electron will then be excited into a energetically higher orbital.

### 2024-01-07 doc/Thesis/chapter/021-theory-calculations.tex
rough corrections finished

@@
 The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes.
-This process is repeated until a \td{satisfactory} solution is found.\footnote{This paragraph was written by GPT3\cite{Liu2021gpt} given the input "Introduction to genetic algorithms:"}
+This process is repeated until a satisfactory solution is found (mostly after a predefined number of repetitions).\footnote{This paragraph was written by GPT3\cite{Liu2021gpt} given the input "Introduction to genetic algorithms:"}
 

### 2024-01-07 doc/Thesis/chapter/03-experimental.tex
rough corrections finished

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo{materials section and sources (incl. purities is missing!) }
+%\todo{materials section and sources (incl. purities is missing!) }
 In this section the used chemicals, substrates, experimental procedures and any used lab equipment are described. 
-\td{All chemicals used in this work are of reagent-grade purity and without further purification.}
+%\td{
+All chemicals used in this work are of reagent-grade purity and without further purification. 
+%}
 %\td{Also, the long, exhaustive path to the base solution is described}
@@
 \end{enumerate}
-\td{is that the usual procedure for steel?}
-After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the coating step.
+%\td{is that the usual procedure for steel?}
+After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the coating step (cf. \cite{YAMASHITA2018,Kohli2010}).
 
@@
 \gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
+\ds{
 The main differences between the used recipe and the recipe mentioned in \cite{Hu2016} were 
-\td{precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
-complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
+\td{precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature
 (room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
@@
 ( so everything is different!! now I'm confused? you dream up a recipe and optimize that? not how I would do that! also: quite a difference between alpro3 and zrpro4)}
+}
 %me          hu
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Doctor blading}
+\section{Blade Coating}
 \label{sec:exp-db}
@@
 	(b) Edge of a sample with the probe touching silver paste on top of a sanded patch.
-	(c) From the voltage source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.\td{(what is XXX circuit?)}}
+	(c) From the voltage source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.
+}%\td{(what is XXX circuit?)}}
 \end{figure}
@@
 The bounds of the process variables were then explored in a preliminary study 
-using the Plackett-Burman\cite{Plackett1946} design implemented in the \td{\texttt{python3}}
-library texttt{pyDOE} \td{(Version 0.3.8)}; 
+using the Plackett-Burman\cite{Plackett1946} design implemented in the \texttt{python3} (version 3.9)
+library \texttt{pyDOE} (version 0.3.8); 
 with 
@@
 relative concentration of Zr $c_{zr}$, number of coating layers $\lambda$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{C}$[\mm{}/\s{}] and \gls{db} temperature $T_{C}$[\oc{}], respectively.
-After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see table \ref{tab:pre-opt1}).
+After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see appendix \ref{sec:app-pre-emma}).
+%
+\ds{
+table \ref{tab:pre-opt1}).
 \begin{table}[hbt]
@@
 \end{table}
+}
 
@@
 %See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
-Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
+Some additional hand picked experiments (see appendix~\ref{sec:app-pre-emma}) were introduced to further narrow down the limits of 
 the optimization as every reduction in variables or levels meant a faster convergence.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The stabilization agent was changed from \td{\gls{acoh} to \gls{ipo} 
+The stabilization agent was changed from \gls{acoh} to \gls{ipo} 
 shortly before the \gls{pso}
-(but why?)} because of much better \td{solution stability. (how did you test this?? see section \ref{sec:res-mat})}
+because of much better solution stability and similar electric properties of resulting layers (how did you test this?? see appendix \ref{sec:app-pre-emma}).
 The - up to this moment - best process was chosen to be tested with 

### 2024-01-07 doc/Thesis/chapter/03-experimental.tex
move data processing into experimental

@@
 
+\todo{ To me this does not follow any logical order!}
+\section{Data Processing}
+\label{sec:eval}
+\todo{Why this procedure? Sounds quite arbitrary?}
+%Reading list
+%\begin{itemize}
+    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
+    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
+    %\item Curse of dimensionality scholar
+    %\item linear regression von ungar 
+    %\item ridge regression + support vector machine
+    %\item correlation vs covariance
+    %\item https://en.wikipedia.org/wiki/Regression_analysis
+    %\item https://en.wikipedia.org/wiki/Noise_reduction
+    %\item https://en.wikipedia.org/wiki/Feature_extraction
+    %\item https://en.wikipedia.org/wiki/Feature_selection
+    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
+    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
+    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
+    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
+%    \item 
+%\end{itemize}
+%\td{describe problem and solution found}
+Multiple \gls{iv} curves were measured (see figure \ref{fig:iv}) for every sample.
+The main difficulty faced in processing the data was to present the measurements obtained 
+from a sample in one representative number. 
+%
+%\todo{why didn't i just take this?}
+%\td{L2 norm because it might be easier to compare to other methods. }
+%\td{inspired by euclidean norm/L2 distance from ideal case} 
+%\td{wanted to put more weight on bad shunts}
+%\td{plot avg, avg(log), avg(log-13)}
+%
+For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
+5 points before and 5 points after the origin with minimum one point distance from zero (which boils
+down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
+calculating averages $\overline{V}$ and $\overline{I}$ of each point cloud and taking the ratio of differences:
+%averaging their V and I values and calculating
+\begin{equation}
+    %g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
+    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}
+\end{equation}
+%
+The average of each conductance would be an easy and naive choice but difficult to represent a 
+sample correctly since the possible values of conductance span across several magnitudes.
+So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
+%
+In order to make the metric closer 
+%and better comparable to the 
+\gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
+to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conducticity hereafter for lack of a better term. 
+%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
+%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
+%and the mean of all conductances was taken
+%
+\begin{equation}
+    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
+	\label{eq:gamma}
+\end{equation}
+Another measure is the density of shorted species $\rho$ (pinhole density), calculated in following way:
+\begin{equation}
+	s_i = \begin{cases}
+        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
+        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
+	\end{cases}
+\end{equation}
+\begin{equation}
+	\rho = \sum_i^N \frac{s_i}{N}
+	\label{eq:rho}
+\end{equation}
+The density is 1 if every measurement has a conductance larger than $10^{-5} \, \Omega^{-1}$ and is 0 if every measured conductance has a value of smaller than $10^{-5} \, \Omega^{-1}$.
+%Other estimates of the conductance are the averages:
+%\begin{equation}
+%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
+%\end{equation}
+%
+%\begin{equation}
+%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
+%%\end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-01-07 doc/Thesis/chapter/04-computational-details.tex
move data processing into experimental

@@
-\todo{ To me this does not follow any logical order!}
-\section{Data Processing}
-\label{sec:eval}
-\todo{Why this procedure? Sounds quite arbitrary?}
-%Reading list
-%\begin{itemize}
-    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
-    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
-    %\item Curse of dimensionality scholar
-    %\item linear regression von ungar 
-    %\item ridge regression + support vector machine
-    %\item correlation vs covariance
-    %\item https://en.wikipedia.org/wiki/Regression_analysis
-    %\item https://en.wikipedia.org/wiki/Noise_reduction
-    %\item https://en.wikipedia.org/wiki/Feature_extraction
-    %\item https://en.wikipedia.org/wiki/Feature_selection
-    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
-    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
-    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
-    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
-%    \item 
-%\end{itemize}
-%\td{describe problem and solution found}
-Multiple \gls{iv} curves were measured (see figure \ref{fig:iv}) for every sample.
-The main difficulty faced in processing the data was to present the measurements obtained 
-from a sample in one representative number. 
-%
-%\todo{why didn't i just take this?}
-%\td{L2 norm because it might be easier to compare to other methods. }
-%\td{inspired by euclidean norm/L2 distance from ideal case} 
-%\td{wanted to put more weight on bad shunts}
-%\td{plot avg, avg(log), avg(log-13)}
-%
-For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
-5 points before and 5 points after the origin with minimum one point distance from zero (which boils
-down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
-calculating averages $\overline{V}$ and $\overline{I}$ of each point cloud and taking the ratio of differences:
-%averaging their V and I values and calculating
-\begin{equation}
-    %g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
-    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}
-\end{equation}
-%
-The average of each conductance would be an easy and naive choice but difficult to represent a 
-sample correctly since the possible values of conductance span across several magnitudes.
-So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
-%
-In order to make the metric closer 
-%and better comparable to the 
-\gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
-to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conducticity hereafter for lack of a better term. 
-%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
-%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
-%and the mean of all conductances was taken
-%
-\begin{equation}
-    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
-	\label{eq:gamma}
-\end{equation}
-Another measure is the density of shorted species $\rho$ (pinhole density), calculated in following way:
-\begin{equation}
-	s_i = \begin{cases}
-        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
-        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
-	\end{cases}
-\end{equation}
-\begin{equation}
-	\rho = \sum_i^N \frac{s_i}{N}
-	\label{eq:rho}
-\end{equation}
-The density is 1 if every measurement has a conductance larger than $10^{-5} \, \Omega^{-1}$ and is 0 if every measured conductance has a value of smaller than $10^{-5} \, \Omega^{-1}$.
-%Other estimates of the conductance are the averages:
-%\begin{equation}
-%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
-%\end{equation}
-%
-%\begin{equation}
-%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
-%%\end{equation}
-
 \section{Evolutionary Model-based Multiresponse Approach}

### 2024-01-09 code/Statistics/scripts/graphs/00_plot_all.sh
adapt uvvis and xrd figs

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+for GPSCRIPT in $(ls *gp)
+do 
+    gnuplot $GPSCRIPT
+done

### 2024-01-09 doc/Thesis/chapter/020-theory-materials.tex
change lambda to n_L

@@
 %\todo{https://doi.org/10.1063/1.1716492}
-In the late 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space exploration.  
-In 1958 the US American Vanguard I\cite{vanguard2004} and the soviet Sputnik III\cite{sputnik1959} were the first satellites with solar cells with efficiencies under 10 \% (\td{cite?}).
+In the late 1950s the first solar cells (with efficiencies around 10 percent\cite{prince1958}) were used in niche applications such as space exploration.  
+In 1958 the US American Vanguard I\cite{vanguard2004} and the soviet Sputnik III\cite{sputnik1959} were the first satellites with solar cells.
 These "solar batteries" - as they were called then - allowed the transmission system of Vanguard I to be operating for over a year after the chemical battery powered system stopped transmitting after 20 days\cite{vanguard2004}.

### 2024-01-09 doc/Thesis/chapter/022-alt-theory-calculations.tex
change lambda to n_L

--- 2023-03-10 Thesis/chapter/032-alt-theory-calculations.tex
@@
 but rather a frame work to choose the next sample which should be tested in a optimization. 
-\td{mention classification vs regression and supervised vs supervised}
+\td{mention classification vs regression and supervized vs supervized}
 %
@@
 \textbf{Ridge Regression} is like linear regression but with an extra term which penalizes steep regression functions.
-This extra term is scaled by a correction parameter $\lambda$. 
-The larger $\lambda$ the larger regularization and the flatter the regression functions. 
-If $\lambda$ were infinite, then the regression function would be a flat line. 
+This extra term is scaled by a correction parameter $\lambda_{RR}$. 
+The larger $\lambda_{RR}$ the larger regularization and the flatter the regression functions. 
+If $\lambda_{RR}$ were infinite, then the regression function would be a flat line. 
 The correction term avoids overfitting. 
 \begin{equation}
-    L_{RR} = L_2 + \lambda \sum k_i = \sum(y_i - \hat y_i)^2 + \lambda \sum k_i
+	L_{RR} = L_2 + \lambda_{RR} \sum k_i = \sum(y_i - \hat y_i)^2 + \lambda_{RR} \sum k_i
 \end{equation}
@@
 These kernels fulfill the requirements of nonnegativity, symmetry, linearity\cite{rupp2015machine}.
-\td{Note that when $\lambda$ tends to zero, the regularized loss function becomes the OLS loss function.
-When $\lambda$ tends to infinity, we get an intercept-only model}
+\td{Note that when $\lambda_{RR}$ tends to zero, the regularized loss function becomes the OLS loss function.
+When $\lambda_{RR}$ tends to infinity, we get an intercept-only model}
 \td{A critique of ridge regression is that all the variables tend to end up in the model. The model only shrinks the coefficients.}
@@
 %If the data is not seperable by a hyperplane the kernel trick can be used. 
-%\td{$\text{min}\frac{1}{N} \sum_{i=1}^{N} max(0,1- y_i(\mathbf{x}x_i-b)) + \lambda \|w\|$
+%\td{$\text{min}\frac{1}{N} \sum_{i=1}^{N} max(0,1- y_i(\mathbf{x}x_i-b)) + \lambda_{RR} \|w\|$
 %The downside of \gls{svm} is that it is very sensitive to outliers.}

### 2024-01-09 doc/Thesis/chapter/03-experimental.tex
change lambda to n_L

@@
 
-\todo{ To me this does not follow any logical order!}
+%\todo{ To me this does not follow any logical order!}
 \section{Data Processing}
 \label{sec:eval}
-\todo{Why this procedure? Sounds quite arbitrary?}
+%\todo{Why this procedure? Sounds quite arbitrary?}
 %Reading list
@@
 as nominal and extreme values for 
-relative concentration of Zr $c_{zr}$, number of coating layers $\lambda$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{C}$[\mm{}/\s{}] and \gls{db} temperature $T_{C}$[\oc{}], respectively.
+relative concentration of Zr $c_{zr}$, number of coating layers $n_L$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{C}$[\mm{}/\s{}] and \gls{db} temperature $T_{C}$[\oc{}], respectively.
 After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see appendix \ref{sec:app-pre-emma}).
@@
 	%		&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
-			$c_{zr}$	&$\lambda$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
+			$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
 			\hline
@@
 			\hline\hline
-			$c_{zr}$	&$\lambda$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
+			$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
 	%conc	&layers	&$v_{\textrm{C}}$	&$T_{\textrm{C}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\
@@
         \hline\hline
-		$c_{zr}$	&$\lambda$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
+		$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
 %        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\

### 2024-01-09 doc/Thesis/chapter/04-computational-details.tex
change lambda to n_L

@@
 		\hline\hline
-        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$\lambda$	&$T_{C}$[\oc{}]	&$v_{C}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
+        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$n_L$	&$T_{C}$[\oc{}]	&$v_{C}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
 		\hline
@@
 
-The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $\lambda$ and $v_{cal}$, 
+The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $n_L$ and $v_{cal}$, 
 (i.e. conducticity, pinhole density, coating layer count and heating rate)
-where $\gamma$, $\rho$ and $\lambda$ are to be minimized and $v_{cal}$ to be maximized.
+where $\gamma$, $\rho$ and $n_L$ are to be minimized and $v_{cal}$ to be maximized.
 %which all should be minimized except for $v_{cal}$.
@@
 \ref{sec:exp} and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), 
-$\lambda$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in 
+$n_L$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in 
 \oc{}/\minutes{}) are supplied to the program. 
@@
 % GRID SEARCH 
-The input variables ($c_{zr}$, $\lambda$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$) 
+The input variables ($c_{zr}$, $n_L$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$) 
 of the \gls{emma} data set were scaled with the routine \texttt{sklearn.preprocessing.StandardScaler().fit\_transform()}. %\td{scaled before each calculation.}
@@
 These values were also calculated for \gls{emma} and the linear model in order to compare the different methods. 
-\todo{(and how did this output help you to optimize your exp. procedure??)}
+%\todo{(and how did this output help you to optimize your exp. procedure??)}

### 2024-01-09 doc/Thesis/chapter/050-results-material.tex
change lambda to n_L

@@
 % ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
-Even after the consecutive application of two layers, there was no improvement and the results examined with \td{\gls{sem} (where is the evidence?)} reminded rather of a sparse crust than of a film. 
+Even after the consecutive application of two layers, 
+there was no significant improvement and the results examined with \gls{sem} (see figure~\ref{fig:sem-old}) reminded rather of a sparse crust than of a film. 
 %It is assumed that the solution was far from the optimum for a sol-gel process. 
@@
         \centering
-        \includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
+        %\includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
+        \includegraphics[width=.99\textwidth]{Pics/sem/071_fto_old_2x.png}
 		\caption{}%SEM picture of \gls{zro} produces by H2O solution} 
@@
         \centering
-        \includegraphics[width=.79\textwidth]{Pics/sem/147_steel_ph_10x.png}
+        \includegraphics[width=.99\textwidth]{Pics/sem/147_steel_ph_10x.png}
 		\caption{}%SEM picture of \gls{zro} produced by buoh solution} 
@@
         \centering
-        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
+        \includegraphics[width=.99\textwidth]{Pics/sem/115_fto_cs_1x.png}
 		\caption{}%115 fto cs 5x} 
@@
         %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
-        \includegraphics[width=.8\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
+        \includegraphics[width=.99\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
 		\caption{}%150 steel 2Fx5} 
@@
 		SEM images of of \gls{zro}:
-		(a) \gls{zro} produces by aquatic solution on \gls{fto}
+		(a) \gls{zro} produces by 2 layers aquatic solution on \gls{fto}
 		(b) 10 layers of \gls{zro} on steel substrate
@@
 Alternatively, the small, hardly visible slits spread across the surface could depict such pin holes. 
-These - I think - are rather only one layer deep irregularities since they are so prevalent
-and hardly any pin holes were electrically observed on similar samples. 
-\todo{where is the evidence?}
+% These - I think - are rather only one layer deep irregularities since they are so prevalent and hardly any pin holes were electrically observed on similar samples. \todo{where is the evidence?}
 
@@
 	\includegraphics[width=\picwidth]{Pics/xrd.png}
-	\caption{XRD spectra of steel substrate (yellow), \gls{zro} (blue), $\alpha$-Fe (green, idealized) and cubic-\gls{zro} (purple, idealized)\cite{gkatz1971xray} \td{(text in fig too small, use an offset, looks very amorphous to me)} }
+	\caption{XRD spectra of steel substrate (yellow; below), \gls{zro} (blue; above), $\alpha$-Fe (green; wide; idealized) and cubic-\gls{zro} (purple; narrow; idealized)\cite{gkatz1971xray} }%\td{(text in fig too small, use an offset, looks very amorphous to me)} }
 	\label{fig:xrd}

### 2024-01-09 doc/Thesis/chapter/051-results-emma.tex
change lambda to n_L

@@
 The sample predicted as optimum by the algorithm is experiment number 13 with 
-lowest possible $c_{zr}$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$ and second highest possibel $\lambda$ (see table \ref{tab:input}). 
+lowest possible $c_{zr}$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$ and second highest possibel $n_L$ (see table \ref{tab:input}). 
 %lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
@@
         \hline\hline
-		generation& measurements &enr &$c_{zr}$ &$\lambda$ &$v_{C}$ &$T_{C}$ &$v_{cal}$ &$T_{cal}$\\
+		generation& measurements &enr &$c_{zr}$ &$n_L$ &$v_{C}$ &$T_{C}$ &$v_{cal}$ &$T_{cal}$\\
         \hline
@@
 conducticity $\gamma$ and pin hole density $\rho$ (see section \ref{sec:eval}), of each particle at each generation.
-The \td{green} points at generation number 0 indicate particles which were not included to be propagated. 
+The the solid circles at generation number 0 indicate particles which were not included to be propagated. 
 %Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
-\td{Violet} lines connect individual particles in time. 
-The \td{blue} line connects averages of particles of each generation (including initial non-propagated particles) and 
-\td{yellow} lines connect averages of each generation of only those particles which were propagated. 
+Solid lines connect individual particles in time. 
+The dashed line connects averages of particles of each generation (including initial non-propagated particles) and 
+pointed lines connect averages of each generation of only those particles which were propagated. 
 %
@@
 The deviation from expectation might be due to measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature, humidity or solution age. 
-Measurements were expected to show clear correlation of \textit{optimizands} $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $\lambda$.
+Measurements were expected to show clear correlation of \textit{optimizands} $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $n_L$.
 The only statistically relevant correlation was observed for $T_{cal}$ with the \textit{optimizands}.
@@
     \centering
-    \begin{subfigure}{.24\textwidth}
+    \begin{subfigure}{.44\textwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}{.24\textwidth}
+    \begin{subfigure}{.44\textwidth}
         \centering
@@
 %$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
-The expression $h(\lambda-6)$ translates into layer count only has an influence if larger than 6 
-and $h(6-\lambda)$ into layer count influential only if under 6.
+The expression $h(n_L-6)$ translates into layer count only has an influence if larger than 6 
+and $h(6-n_L)$ into layer count influential only if under 6.
 %
@@
 %
-%\td{Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as \textit{optimizands} rather unfortunate. %highly questionable. 
-%\td{This makes including $\lambda$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
+%\td{Knowing this, makes the decision of adding $n_L$ and $v_{cal}$ as \textit{optimizands} rather unfortunate. %highly questionable. 
+%\td{This makes including $n_L$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
 %As the \gls{mars} algorithm is greedy,
@@
 %    \label{eq:emma-phd1}
-%    \hat{\rho}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{C}\cdot T_{cal} + 0.00080 \cdot h(6-\lambda)\cdot T_{cal}\\
+%    \hat{\rho}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{C}\cdot T_{cal} + 0.00080 \cdot h(6-n_L)\cdot T_{cal}\\
 %    \label{eq:emma-G1}
-%    \hat{\gamma}_1 &= -26  + 0.0025 \cdot T_{C}\cdot T{cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{cal} \\
+%    \hat{\gamma}_1 &= -26  + 0.0025 \cdot T_{C}\cdot T{cal}  +  0.056 \cdot  h(6-n_L)\cdot T_{cal} \\
 %    \label{eq:emma-layr1}
-%    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{C}\cdot T_{cal} -  0.0056 \cdot  h(6-\lambda)\cdot T_{cal}\\
+%    \hat{n_L}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{C}\cdot T_{cal} -  0.0056 \cdot  h(6-n_L)\cdot T_{cal}\\
 %    \label{eq:emma-vcal1}
-%    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{C}\cdot T_{cal} - 0.0055 \cdot  h(6-\lambda)\cdot T_{cal}\\
+%    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{C}\cdot T_{cal} - 0.0055 \cdot  h(6-n_L)\cdot T_{cal}\\
 %
@@
 %    \label{eq:emma-layr2}
-%    \hat{\lambda}_2 &= 7.3\\
+%    \hat{n_L}_2 &= 7.3\\
 %    \label{eq:emma-vcal2}
@@
     \label{eq:emma-phd3}
-    \hat{\rho}_3 &= 0.075  -   0.0014 \cdot  v_{cal}  +    0.18 \cdot  h(6-\lambda)  + 3.9\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
+    \hat{\rho}_3 &= 0.075  -   0.0014 \cdot  v_{cal}  +    0.18 \cdot  h(6-n_L)  + 3.9\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
     \label{eq:emma-G3}
-    \hat{\gamma}_3 &= 43  -   0.097 \cdot  v_{cal}  +     10 \cdot  h(6-\lambda)  + 0.00026 \cdot  v_{cal}\cdot T_{cal} \\
+    \hat{\gamma}_3 &= 43  -   0.097 \cdot  v_{cal}  +     10 \cdot  h(6-n_L)  + 0.00026 \cdot  v_{cal}\cdot T_{cal} \\
     \label{eq:emma-layr3}
-    \hat{\lambda}_3 &= 9.9  - 0.00064 \cdot  v_{cal}  -     2.7 \cdot  h(6-\lambda)  - 1.3\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
+    \hat{n_L}_3 &= 9.9  - 0.00064 \cdot  v_{cal}  -     2.7 \cdot  h(6-n_L)  - 1.3\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
     \label{eq:emma-vcal3}
-    \hat{v}_{cal,3} &= -5.2\cdot 10^{-15}  +   0.016 \cdot  v_{cal}  + 1.3\cdot 10^{-15} \cdot  h(6-\lambda)  + 3.9\cdot 10^{-21} \cdot  v_{cal}\cdot T_{cal} \\
+    \hat{v}_{cal,3} &= -5.2\cdot 10^{-15}  +   0.016 \cdot  v_{cal}  + 1.3\cdot 10^{-15} \cdot  h(6-n_L)  + 3.9\cdot 10^{-21} \cdot  v_{cal}\cdot T_{cal} \\
 %
     \label{eq:emma-phd4}
-    \hat{\rho}_4 &=  -0.87 + 0.0047 \cdot  T_{cal} - 0.00036 \cdot  \lambda\cdot T_{cal}  +  0.0024 \cdot  h(\lambda-6)\cdot T_{C} \\
+    \hat{\rho}_4 &=  -0.87 + 0.0047 \cdot  T_{cal} - 0.00036 \cdot  n_L\cdot T_{cal}  +  0.0024 \cdot  h(n_L-6)\cdot T_{C} \\
     \label{eq:emma-G4}
-    \hat{\gamma}_4 &=     -19 + 0.28 \cdot  T_{cal}  - 0.022 \cdot  \lambda\cdot T_{cal}  +  0.16 \cdot  h(\lambda-6)\cdot T_{C} \\
+    \hat{\gamma}_4 &=     -19 + 0.28 \cdot  T_{cal}  - 0.022 \cdot  n_L\cdot T_{cal}  +  0.16 \cdot  h(n_L-6)\cdot T_{C} \\
     \label{eq:emma-layr4}
-    \hat{\lambda}_4 &=  6.8 - 0.014 \cdot  T_{cal}  + 0.0018 \cdot  \lambda\cdot T_{cal}  + 0.0060 \cdot  h(\lambda-6)\cdot T_{C} \\
+    \hat{n_L}_4 &=  6.8 - 0.014 \cdot  T_{cal}  + 0.0018 \cdot  n_L\cdot T_{cal}  + 0.0060 \cdot  h(n_L-6)\cdot T_{C} \\
     \label{eq:emma-vcal4}
-    \hat{v}_{cal,4} &=  29 - 0.052 \cdot  T_{cal}  + 0.0011 \cdot  \lambda\cdot T_{cal}  -  0.011 \cdot  h(\lambda-6)\cdot T_{C} 
+    \hat{v}_{cal,4} &=  29 - 0.052 \cdot  T_{cal}  + 0.0011 \cdot  n_L\cdot T_{cal}  -  0.011 \cdot  h(n_L-6)\cdot T_{C} 
 \end{align}
@@
 This difference in magnitude fits the data well since the maxima of $\rho$ and $\gamma$ are separated by rough factor of 100 (see figure~\ref{fig:emma-gen} and appendix~\ref{sec:app-emma}).
-%, but the positive influence of the layer count $\lambda$ is counter intuitive
+%, but the positive influence of the layer count $n_L$ is counter intuitive
 %as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
 The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) 
-seem low, but the interaction has -- considering the minimum value of the interaction of $300 \cdot 120 =$  \num{36000} -- several orders of magnitude higher influence on $\rho_3$ and $\gamma_3$ than the $h(6-\lambda)$ term.
+seem low, but the interaction has -- considering the minimum value of the interaction of $300 \cdot 120 =$  \num{36000} -- several orders of magnitude higher influence on $\rho_3$ and $\gamma_3$ than the $h(6-n_L)$ term.
 %It's positive the hinge
 It is astonishing that the knot of the hinge function for equations (\ref{eq:emma-phd3})--(\ref{eq:emma-vcal3}) was chosen so low; 
-basically only including the influence of the lowest layer count $\lambda=4$.
+basically only including the influence of the lowest layer count $n_L=4$.
 Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}), that the lowest layer count produces worse samples which is intuitive, but more than 6 layers do not improve the insulation. 
@@
 %for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
-%$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $\lambda$ increases the two \textit{optimizands}. 
+%$n_L$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $n_L$ increases the two \textit{optimizands}. 
 %
@@
 % DESCRIBE COEFFICIENTS
-Furthermore, the coefficient of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ (\ref{eq:emma-phd4}) and $\hat{\gamma}$ (\ref{eq:emma-G4}); interestingly also on $\hat\lambda$ (\ref{eq:emma-layr4}) and $\hat{v}_{cal}$ (\ref{eq:emma-vcal4}).
-The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 
-but has the extra factor $\lambda$ (range: 4--12), resulting in the products of coefficients and process variables being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$ terms.
-It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}). 
+Furthermore, the coefficient of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ (\ref{eq:emma-phd4}) and $\hat{\gamma}$ (\ref{eq:emma-G4}); interestingly also on $\hat{n_L}$ (\ref{eq:emma-layr4}) and $\hat{v}_{cal}$ (\ref{eq:emma-vcal4}).
+The coefficient of the $n_L\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 
+but has the extra factor $n_L$ (range: 4--12), resulting in the products of coefficients and process variables being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$ terms.
+It can be noted that the coefficient of the $n_L\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}). 
 This negative correlation could hint a compenzation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
-Similarly, signs of coefficients of $\lambda \cdot T_{cal}$ and $h(\lambda -6) \cdot T_{C}$ correlate negatively in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) and the product of coefficients and input variables are again similar in order of magnitude.
+Similarly, signs of coefficients of $n_L \cdot T_{cal}$ and $h(n_L -6) \cdot T_{C}$ correlate negatively in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) and the product of coefficients and input variables are again similar in order of magnitude.
 %It should be doubted, though, that the $layr$ only appears as interaction term 
@@
 %
-%It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
+%It seems rather an artefact of noise that the $n_L$ only appears as interaction 
 %with $T_{cal}$ and $T_{C}$. 
-%From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_{C}$ and then the rest of the independent variables. 
-The process variables $T_{cal}$ and $\lambda$ appear as \gls{bf}s in generation 3 and 4, whereas $v_{cal}$ only appears in generation 3's \gls{rf}s and $T_{C}$ only in generation 4's \gls{rf}s.
+%From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $n_L$, then $T_{C}$ and then the rest of the independent variables. 
+The process variables $T_{cal}$ and $n_L$ appear as \gls{bf}s in generation 3 and 4, whereas $v_{cal}$ only appears in generation 3's \gls{rf}s and $T_{C}$ only in generation 4's \gls{rf}s.
 This can hint the importance of these variables in the process. 
@@
 
-The two independent variables $v_{cal}$ and $\lambda$ were included as \textit{optimizands} for two reasons: 
+The two independent variables $v_{cal}$ and $n_L$ were included as \textit{optimizands} for two reasons: 
 Maximizing the calcination velocity and minimizing the number of layer application iterations leads to minimization of process time.
@@
 additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables and chose future data points. 
-Moreover, $v_{cal}$ and $\lambda$ were only considered with 5\% weight in the overall objective function.
+Moreover, $v_{cal}$ and $n_L$ were only considered with 5\% weight in the overall objective function.
 The second flaw is that there are obviously better methods to assess the quality of a model than to make it more complex. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{rational behind including $v_{cal}$ and $\lambda$ as optimizands}
+\subsection{rational behind including $v_{cal}$ and $n_L$ as optimizands}
 }
@@
 \td{
-(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
+(1) The true function for predicting $v_{cal}$ and $n_L$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $n_L$, respectively. 
 The algorithm will tend to include those values into the prediction function for 
@@
 %
-(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
+(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $n_L$ but not $G$ or $\rho$. 
 %

### 2024-01-09 doc/Thesis/chapter/052-post-emma.tex
change lambda to n_L

@@
 %indep groups are not equal and that there is at least one group that is different. 
-For both $\rho$ and $\lambda$ (for both the \gls{emma} dataset and the whole dataset (=\gls{emma}+pre-\gls{emma})) 
+For both $\rho$ and $n_L$ (for both the \gls{emma} dataset and the whole dataset (=\gls{emma}+pre-\gls{emma})) 
 the F-values for $T_{cal}$ were in all cases under 0.01, 
@@
 \subsection{Linear Regression} 
-%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influenced by the Zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$, but their coefficients are the smallest in absolute values.
+%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influenced by the Zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $n_L$, but their coefficients are the smallest in absolute values.
 
@@
 The biggest difference between the linear model and \gls{emma} is that the linear regression function will include all input variables, that the \gls{bf}s are strictly linear and that there are no interaction terms.
-The coefficients of the $\lambda$ term have the same sign in equations \ref{eq:emma-phd3}, \ref{eq:emma-G3}, \ref{eq:emma-phd4}, \ref{eq:emma-G4} (\gls{emma} \gls{rf}s) and \ref{eq:linreg-phd}, \ref{eq:linreg-G} and have comparable magnitudes too.
+The coefficients of the $n_L$ term have the same sign in equations \ref{eq:emma-phd3}, \ref{eq:emma-G3}, \ref{eq:emma-phd4}, \ref{eq:emma-G4} (\gls{emma} \gls{rf}s) and \ref{eq:linreg-phd}, \ref{eq:linreg-G} and have comparable magnitudes too.
 %
@@
 		\label{eq:linreg-phd}
-		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{C} + 0.0058\cdot T_{C} \\
+		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot n_L -0.0029\cdot v_{C} + 0.0058\cdot T_{C} \\
 		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
@@
 		\label{eq:linreg-G}
-		\hat{\gamma} =&  \,\,\qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot \lambda \,\,\quad - 1.2\cdot v_{C}  \,\,\,\quad +0.2\cdot T_{C} \\
+		\hat{\gamma} =&  \,\,\qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot n_L \,\,\quad - 1.2\cdot v_{C}  \,\,\,\quad +0.2\cdot T_{C} \\
 			& \qquad - 0.014\cdot v_{cal} \quad + 0.13\cdot T_{cal} + 7.2
-%		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot \lambda - 1.2\cdot v_{C} + 0.2\cdot T_{C} \\
+%		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot n_L - 1.2\cdot v_{C} + 0.2\cdot T_{C} \\
 %			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
@@
 More particularly, $T_{cal}$ and $T_{C}$ have positive coefficients, i.e. a negative influence on the resistance 
-and $\lambda$, $v_{C}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
+and $n_L$, $v_{C}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
 An indication that the data is strongly tainted by noise (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
@@
 %It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}.
-$v_{cal}$ and $\lambda$ are perfectly predicted by linear regression as there is an exact direct proportionality and thus are not displayed here. 
+$v_{cal}$ and $n_L$ are perfectly predicted by linear regression as there is an exact direct proportionality and thus are not displayed here. 
 %
@@
 	\begin{tabular}{cccccccc}
-		        & $c_{zr}$      & $\lambda$     & $v_{C}$      & $T_{C}$      & $v_{cal}$     & $T_{cal}$\\
+		        & $c_{zr}$      & $n_L$     & $v_{C}$      & $T_{C}$      & $v_{cal}$     & $T_{cal}$\\
 				\hline\hline
@@
 %
-Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$ are largest in value, but the values which are factored with these coefficients - i.e.\, $c_{zr}$ and $\lambda$ themselves -- are the smallest among the input variables.
+Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $n_L$ are largest in value, but the values which are factored with these coefficients - i.e.\, $c_{zr}$ and $n_L$ themselves -- are the smallest among the input variables.
 Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
@@
 %The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{C}$. 
-The biggest influence on $\hat\rho$ is  $\lambda$, followed by $T_{cal}$. 
-While $T_{cal}$ is the second largest influence on $\hat\rho$ as well, it is noteworthy that $\lambda$ contributes the least to $\hat\gamma$. 
+The biggest influence on $\hat\rho$ is  $n_L$, followed by $T_{cal}$. 
+While $T_{cal}$ is the second largest influence on $\hat\rho$ as well, it is noteworthy that $n_L$ contributes the least to $\hat\gamma$. 
 That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
 Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artefact of the noise rather than a process property. 
-%Furthermore the influence on $\hat\rho$ is dominated by $\lambda$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
+%Furthermore the influence on $\hat\rho$ is dominated by $n_L$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
 %Different distributions were not expected. 

### 2024-01-09 doc/Thesis/chapter/020-theory-materials.tex
feinschliff

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CIGS}
-\subsection{Copper Indium Gallium Selenide} 
+\subsection{Copper Indium Gallium Selenide Solar Cell}
+%\subsection{Copper Indium Gallium Selenide} 
 \gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
@@
 %
-\Gls{db} coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing and ceramic industries.
+\Gls{db} (also known as tape casting) is widely used in the textile, paper, photographic film, printing and ceramic industries.
 The roll-to-roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.

### 2024-01-09 doc/Thesis/chapter/03-experimental.tex
feinschliff

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Buthanolic solution}\label{sec:exp-sol-bu}
+\subsection{Buthanolic Solution}\label{sec:exp-sol-bu}
 %\todo{what did you did you do percisely! It must be logical and should be followed}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Blade Coating}
+\section{Tape Casting}
 \label{sec:exp-db}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Calcination of Films}\label{sec:exp-calc}
+\section{Calcination of \ch{ZrO2}}
+\label{sec:exp-calc}
 A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate the coated samples. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Characterization}
+\section{Characterization of \ch{ZrO2} layers}
 All characterization procedures were executed at room temperature.
@@
 %\todo{ To me this does not follow any logical order!}
-\section{Data Processing}
+\section{Data Processing of Electrical Measurements}
 \label{sec:eval}

### 2024-01-09 doc/Thesis/chapter/050-results-material.tex
feinschliff

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{X-ray diffractogram of \ch{ZrO2}}
+\subsection{X-ray Diffractogram of \ch{ZrO2}}
 %\todo{of what?}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Spectrometry of \ch{ZrO2} layers}
+\subsection{Spectrometry of \ch{ZrO2} Layers}
 %\todo{of what?}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Current Voltage Curves of \ch{ZrO2} layers} 
+\subsection{Current Voltage Curves of \ch{ZrO2} Layers} 
 %\todo{of what?}
@@
 	%
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
+    \begin{subfigure}{.32\textwidth}
+        \includegraphics[width=.99\textwidth]{Pics/iv/log-154-good-3x4F.png}
 		\caption{}%log good 3x4F} 
@@
     \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
+    \begin{subfigure}{.32\textwidth}
+        \includegraphics[width=.99\textwidth]{Pics/iv/log-146-okay-10x1F.png}
 		\caption{}%log okay 10x1F} 
@@
     \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
-        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
+    \begin{subfigure}{.32\textwidth}
+        \includegraphics[width=.99\textwidth]{Pics/iv/log-156-bad-3x3F.png}
 		\caption{}%log bad 3x3F} 
@@
 	%
-    \begin{subfigure}{.3\textwidth}
+    \begin{subfigure}{.32\textwidth}
         \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
@@
     \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
+    \begin{subfigure}{.32\textwidth}
         \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
@@
     \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
+    \begin{subfigure}{.32\textwidth}
         \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
@@
 	%
-    \begin{subfigure}{.3\textwidth}
+    \begin{subfigure}{.32\textwidth}
         \includegraphics[width=\textwidth]{Pics/iv/146-nocurrent.png}
@@
     \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
+    \begin{subfigure}{.32\textwidth}
         \includegraphics[width=\textwidth]{Pics/iv/146-diodic.png}
@@
     \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
+    \begin{subfigure}{.32\textwidth}
         \includegraphics[width=\textwidth]{Pics/iv/146-ohmic.png}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Preoptimization of Coating Procedure}
+\subsection{Pre-optimization of Coating Procedure}
 %\todo{of what?}

### 2024-06-16 doc/Thesis/chapter/01-introduction.tex
TD: intro

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Photovoltaics (PV) is one viable option for becoming carbon neutral. 
+Photovoltaics (PV) is a viable renewable energy source towards energy neutrality.
 Furthermore, 
 it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
-it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
+it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search, kardashev1964transmission} which harness the whole power output of the sun.
 %
-One sort of PV are CIGS (copper indium gallium sulfide) cells\cite{Vasekar2010}. 
-Due to their large absorption coefficient (compared to silicon based cells), less material is needed and they can be made thinner and flexible. 
+One type  of thin film PV is based on the CIGS (copper indium gallium sulfide) semiconductor absorber\cite{Vasekar2010}. 
+Due to the large light absorption coefficient of CIGS (compared to silicon), less absorber material is needed (a couple of micrometers) and the PV cell can be made thinner and flexible. 
 %\td{was sind vorteile?}
-In order to make a module, multiple cells are operated in series. 
-The cells must be applied to a non-conducting surface.
-Glass is a popular non-conducting substrate, but very rigid and brittle. 
-An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
-An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be synthesised on top.
-Polymers would be a obvious choice if not for its low thermal stability which makes high production temperatures impractical.
-A non-toxic material which is suitable for the insulation is \ch{ZrO2}. 
+In order to make a module, multiple solar cells are connected in series. 
+The solar cells must be deposited on a non-conducting surface.
+Glass is a popular non-conducting substrate, but rigid and brittle. 
+A flexible alternative is steel foil, which is ductile, inexpensive and highly available, but electrically conducting. 
+An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be deposited on top.
+Polymers would be a choice if not for their low thermal stability which does not permit high production temperatures.
+A non-toxic material which is suitable for the insulation is zirconium oxide (\ch{ZrO2}). 
 %An economic and scalable method is doctor blading via a sol-gel process. 
-Sol-gel roll-to-roll coating processes (e.g. tape casting) are economic and scalable methods to apply liquid precursors to substrates.
+Sol-gel roll-to-roll coating processes (e.g.
+tape casting) are economic and scalable methods to apply liquid precursors to substrates, and have been also reported for the deposition of \ch{ZrO2}\cite{yeo1998design,michalek2015comparison}.
 Sol-gel processes often produce porous layers, though.
-In this work a dense, insulating and homogeneous layer is pursued. 
+
+In this work a dense, insulating and homogeneous layer of \ch{ZrO2} is pursued. 
 Machine learning can help to uncover complex non-linear relations, such as the 
-dependence of the thickness and resistance of the resulting layer on production factors.
+dependence of the thickness and resistance of the deposited layer on the coating parameters.
 %\td{influence} of the production factors on the thickness and resistance of the resulting layer.
-The minimization of the conductance of the layer is performed with a particle swarm optimization 
+The minimization of the electrical conductance of the layer is performed with a particle swarm optimization 
 algorithm which has the coating process variables as input. 
@@
 
-The remainder of this work is organized with chapter 
-\ref{sec:theoretical} giving 
+This work is organized as follows: chapter 
+\ref{sec:theoretical} gives 
 %some background information on topics of PV, \td{material science} and \td{computational science (more detail)} which were used in this work. 
-information on the general working principles of PV, the structure, characteristics and properties of materials which were used and computational, statistical and machine learning methods for data processing.
+information on the general working principles of PV, the structure, characteristics and properties of materials which were used and the employed computational, statistical and machine learning methods for data processing.
 

### 2024-06-16 doc/Thesis/chapter/03-experimental.tex
TD: intro

@@
 starting the optimization of the process variables
-%the \td{particle swarm optimisation} started 
+%the \td{particle swarm optimization} started 
 - the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREOPTIMISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREOPTIMIZATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
-244 samples were produced: 93 samples with the aquatic recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimisation to find fitting constraints for the final optimization (see section \ref{sec:ss}).
+244 samples were produced: 93 samples with the aquatic recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).
 

### 2024-06-16 doc/Thesis/chapter/052-post-emma.tex
feinschliff
TD: intro

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsection{ANOVA}\label{sec:res-anova}
+\subsection{Analysis of Variance}
+\label{sec:res-anova}
 %\textbf{EMMA}
@@
 %\todo{what was fitted how?}
-The data obtained from the \gls{emma} optimisation was used to fit a linear model. 
+The data obtained from the \gls{emma} optimization was used to fit a linear model. 
 The biggest difference between the linear model and \gls{emma} is that the linear regression function will include all input variables, that the \gls{bf}s are strictly linear and that there are no interaction terms.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsection{Grid Search, KRR and SVM}
+%\clearpage
+%\subsection{Grid Search, KRR and SVM}
+\subsection{Grid Search, Kernel Ridge Regression and Support Vector Machine}
+
 The optimal parameters for each combination of 

### 2024-06-18 doc/Thesis/chapter/020-theory-materials.tex
edit 020 until excl sputtering

@@
 %\td{https://en.wikipedia.org/wiki/Thesis}
-\ds{what is it? What is it used for? How does it work? What different kinds are there? }
-\ds{what? how? why?}
+%\ds{what is it? What is it used for? How does it work? What different kinds are there? }
+%\ds{what? how? why?}
 This chapter can be broken down into three sections. 
-The first section tries to shine light on the evolution of PV and give some background information on \gls{cigs}.
-The middle section reads about material-scientific methods which were used during the practical part of this work. 
-The last and third part focuses on the algorithmic, statistical and analytical methods used to optimize and predict material properties.
+The first section tries to shine light on the evolution of PV and give some background information on \gls{cigs} absorber.
+The next section concerns the description of materials and scientific methods used during the experminental part of this work. 
+The third and last part focuses on the algorithmic, statistical and analytical methods used to optimize and predict material properties.
 
@@
 Even though this time period is not exact and highly dependent on detection methods of resources, 
-this number is rather small and brings us in \textit{zugzwang} to develop sustainable energy sources. 
+the situation demands the fast 
+development of sustainable energy sources. 
+% this number is rather small and brings us in \textit{zugzwang} to develop sustainable energy sources. 
 One viable option is \gls{pv}.
@@
 %\todo{https://doi.org/10.1063/1.1716492}
-In the late 1950s the first solar cells (with efficiencies around 10 percent\cite{prince1958}) were used in niche applications such as space exploration.  
+In the late 1950s the first solar cells (with power conversion efficiencies around 10 percent\cite{prince1958}) were used in niche applications such as space exploration.  
 In 1958 the US American Vanguard I\cite{vanguard2004} and the soviet Sputnik III\cite{sputnik1959} were the first satellites with solar cells.
@@
 This development lead to a drop in 
-average price for \gls{pv} module from \$ 100 per watt in 1975 to \$ 4 per watt in 2007\cite{pagliaro2008flexible}.
+average price for \gls{pv} module from \$ 100 per watt in 1975 
+%to \$ 4 per watt in 2007\cite{pagliaro2008flexible}. 
+to under \$ 1 per watt in 2022\cite{irena2023renewable}.
 
@@
 \subsection{Photovoltaics Basics}
-The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in human made \gls{pv} or in plants): 
-the creation of an electron-hole pair and then its separation by the structure of the material\cite{markvart2013principles}.
+The process of conversion of photons into electric energy can be broken down into two essential steps: 
+the generation of an electron-hole pair through photon absorption, the electron-hole separation by the built in electric field at the p-n junction and finally collection of the electrons and holes at the opposite terminals of the device\cite{markvart2013principles}.
 This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
-This is often achieved through a p-n junction.
-The n-type side has excess electrons and p-type side has excess electron holes. 
+%This is often achieved through a p-n junction.
+The n-type side of the p-n junction has excess electrons and p-type side has excess electron holes. 
 If the n- and p-type are of the same basis material, they are called homojunctions (e.g.
-silicon); if not, heterojunctions e.g.
-\ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}\cite{breitenstein2013understanding}.
+silicon); if not, heterojunctions (e.g.
+\ch{CdS}/\gls{cigs} and \ch{CdS/CdTe})\cite{breitenstein2013understanding}.
 %
@@
 have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
-In 2022 
-over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon)\cite{breitenstein2013understanding}.
+In 2022 over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon)\cite{breitenstein2013understanding}.
 %
@@
 Today, 
-\gls{cigs} modules (multiple \gls{pv} cells in series) 
-reach efficiencies of up to 16\%\cite{feurer2017cigs},
-monocrystalline silicon \gls{pv} modules reach efficiencies of 14-20\%
-and polycrystalline silicon \gls{pv} modules 12-17\%\cite{mcevoy2011practical}.
+\gls{cigs} (multiple \gls{pv} cells in series) 
+reach efficiencies of up to 19\%,
+monocrystalline silicon \gls{pv} modules reach efficiencies of 24\%
+and polycrystalline silicon \gls{pv} modules 20\%\cite{green2023solar}.
 
-Just like CdTe, GaAs and amorphous silicon, CIGS has much higher absorption coefficients 
-(lower penetration depth) of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}). 
+Just like CdTe, GaAs and amorphous silicon solar cells, CIGS has much higher absorption coefficients of UV, visible and IR light than crystalline silicon (see table \ref{tab:cigs:alpha}). 
 This is due to a direct band gap rather than an indirect band gap (like crystalline silicon). 
@@
 
-Amazingly, the band gap of CIGS can be varied between \ev{1} and \ev{1.7} by varying the indium gallium ratio.
+The band gap of CIGS can be varied between \ev{1} and \ev{1.7} by varying the indium-gallium and sulfur-selenium ratios.
 This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}). 
@@
 Typically, a \um{1} thick molybdenum layer is deposited on soda lime glass. 
-The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in 112 direction\cite{hedstrom1993cigs}.
-A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporation from elemental sources controlled by a mass spectrometer\cite{hedstrom1993cigs}.
+The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in the 112 direction\cite{hedstrom1993cigs}.
+A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporation from elemental sources\cite{hedstrom1993cigs}.
 The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
-The heterojunction is then completed by deposition of \ch{CdS} (typically \nm{50} thick).
+The heterojunction is then completed by deposition of \ch{CdS} n-type layer (typically \nm{50} thick).
 \ch{CdS} was earlier used as front contact, but now only acts as n-type wide-gap window and buffer. 
+After the \ch{CdS} layer 
+A window layer of intrinsic \ch{ZnO} is deposited after the \ch{CdS}, followed by a highly conductive aluminium doped layer. 
 \ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
@@
 They both come with their own inconveniences. 
-Polymers generally have low thermal stability compared with ceramics and metals which restrict preparation temperatures of \gls{cigs}.
-Steel, on the other hand, is temperature resistant enough, but is an electric conductor. 
-The conductance of steel can be masked by a insulator layer (e.g. \ch{ZrO2}, \ch{Al2O3}).
+Polymers generally have low thermal stability compared with ceramics and metals which restrict the fabrication temperature of \gls{cigs}.
+Steel, on the other hand, is temperature resistant enough, but is an electric conductor, which is problematic for the serial interconnection of cells into modules. 
+Thus, an insulating layer has to be deposited on the steel substrate. 
+%The conductance of steel can be masked by a insulator layer (e.g. \ch{ZrO2}, \ch{Al2O3}).
 
@@
 It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
-The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
+The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}). 
+This prevents mechanical failing due to shrinkage 
 when cooling and undergoing phase transition\cite{Nielsen2005}.
-It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
+\ch{ZrO2} is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and bases\cite{Nielsen2005}.
 %Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3})\cite{Nielsen2005}.
@@
 %
-\Gls{db} (also known as tape casting) is widely used in the textile, paper, photographic film, printing and ceramic industries.
-The roll-to-roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
-A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
+Tape casting (also known as tape casting) is widely used in the textile, paper, photographic film, printing and ceramic industries.
+The roll-to-roll compatible process gives rise to highly uniform films over large areas\cite{yang2010large}.
+A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed speed.
 In roll-to-roll processes the substrate moves instead of the blade.

### 2024-06-21 doc/Thesis/chapter/020-theory-materials.tex
edit 020 until incl sputtering

@@
 %SPUTTERING FREEWRITING: 
-%what is sputtering? \\
-Sputtering is the processes of highly energetic ions hitting a surface and atoms or molecules being expelled. 
-This is called a \gls{pvd} technique in contrast to chemical vapor deposition. 
-\Gls{pvd} can be divided into activation by thermal energy and activation by energetic particle bombardment. 
-Sputtering is of the latter kind, which 
-is advantageous if substrates can't withstand high temperatures.
-%\td{what can it be used for?}\\
-Sputtering evolved from being a curious experiment in the middle of the 20th century to 
-having various applications in research and engineering.
+% what is sputtering?
+Sputtering describes the process of highly energetic ions bombarding a surface and atoms being ejected from the surface as a consequence.
+% what can it be used for? 
+%It can be used for high precision etching (semiconductors and nanomaterial) or to deposit thin films. 
+%
 Use cases vary from thin films depositions for \gls{pv}, 
@@
 and good step coverage\cite{Swann1988}.
+% how does it work? 
+%A plasma is created and the ions are accelerated to the surface. 
+The ions, which are accelerated to the surface, mostly originate from a plasma.
+The ion bombardment leads to a transfer of momentum from the ions to the surface atoms which in turn leads to a collision cascade. 
+The cascade can reach the surface again. 
+If the energy of an atom is larger than the binding energy, the atom is ejected. 
+%If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
+This neutral ejected particle travels -- unaffected by the electrical field nearly perpendicular to the surface -- towards the substrate and condenses with other particles to form a layer.
+The pressure in the chamber should be small, such that the sputtered particle has a long mean free path, but on the other hand 
+a minimum pressure is needed to sustain the plasma.
+Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
+% what is used? 
+Nobel gases (e.g. argon) in plasma phase are mainly used for bombardmnt because of their inert properties. 
+Oxygen or nitrogen can be added to the plasme to deposit oxides or nitrides, respectively.
+%Reactive gases can be added (e.g. \ch{O2} or \ch{N2}).
+In order to use sputtering for depositing a target material on top of a substrate material, 
+the target and the substrate are positioned parallel and in between the gas is transitioned into plasma and the ions are accelerated in the direction of the target (by a high electrostatic potential).
+
+%what is sputtering? \\
+% Sputtering is the processes of highly energetic ions hitting a surface and atoms or molecules being expelled. 
+%This is called a \gls{pvd} technique in contrast to chemical vapor deposition. 
+%\Gls{pvd} can be divided into activation by thermal energy and activation by energetic particle bombardment. 
+%Sputtering is of the latter kind, which is advantageous if substrates can't withstand high temperatures.
+%\td{what can it be used for?}\\
+%Sputtering evolved from being a curious experiment in the middle of the 20th century to 
+%having various applications in research and engineering.
 
@@
 
+\iffalse
 %\td{how does it work?}\\
@@
 This happens by a cascade of momentum transfers, which can reach the surface again (see figure \ref{fig:sputter1}). 
-If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
-This neutral sputtered particle travels -- unaffected by the electrical field nearly perpendicular to the surface -- towards the substrate and condenses with other particles to form a layer.
-The pressure in the chamber should be small, such that the sputtered particle has a long mean free path, but on the other hand 
-a minimum pressure is needed to sustain the plasma.
-Usual pressures buzz around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
+\fi
 
+\iffalse
 A magnetron can be placed behind the cathode (target) in order to trap the plasma close to the source. 
@@
 %\td{sputtered particles are neutral and not influenced by the electrical field}
+\fi
 

### 2024-07-06 doc/Thesis/chapter/020-theory-materials.tex
edit 020 until excl uvvis

@@
 \subsection{Scanning Electron Microscopy}
+%
 \ds{
@@
 }
-\Gls{sem} is a microscopic technique which allows visualization of surfaces with features in the nanometer regime. 
+%
+\Gls{sem} is a technique which allows visualization of surfaces with features in the nanometer regime. 
 While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
@@
 Electrons are then accelerated by a voltage of \SI{2}{\kilo\volt} to \SI{40}{\kilo\volt} and bundled into narrow beams by lenses\cite{Vernon2000}.
+All micrographs in this work were made at 
+%Scanning electron microscopy was performed at 
+an acceleration voltage of 5 kV.
 A high mean free path is needed for electrons to travel from the source to the sample (and to the detector). 
 Thus, a very low pressure is needed inside the microscope. 
-In this work \gls{sem} was used as a preliminary way of checking the quality of \gls{zro} layer. 
+In this work \gls{sem} was used as a preliminary way of checking the quality of the deposited layer. 
 % squeeze condition into this page 
 \enlargethispage{\baselineskip}
+\todo{specifications of instruments used: acceleration voltage of 5 kV ??and with an in-lens detector??}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\iffalse
 \subsection{UV/Vis/NIR Spectroscopy}
@@
 Secondly, the electronic spin state of the molecule has to be the same before and after, otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely. 
+\fi
 

### 2024-07-07 doc/Thesis/chapter/020-theory-materials.tex
edit until incl FTIR/XRD

@@
 Electrons are then accelerated by a voltage of \SI{2}{\kilo\volt} to \SI{40}{\kilo\volt} and bundled into narrow beams by lenses\cite{Vernon2000}.
-All micrographs in this work were made at 
-%Scanning electron microscopy was performed at 
-an acceleration voltage of 5 kV.
+%%Scanning electron microscopy was performed at 
+%All micrographs in this work were made at 
+%an acceleration voltage of 5 kV.
+All SEM micrographs were taken with a Zeiss Supra 40 with 5 kV acceleration voltages.
 A high mean free path is needed for electrons to travel from the source to the sample (and to the detector). 
@@
 \enlargethispage{\baselineskip}
-\todo{specifications of instruments used: acceleration voltage of 5 kV ??and with an in-lens detector??}
+%\todo{specifications of instruments used: acceleration voltage of 5 kV ??and with an in-lens detector??}
 
@@
 Secondly, the electronic spin state of the molecule has to be the same before and after, otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely.
-\fi
 
+\subsubsection{Infrared spectroscopy}
 % IR
@@
 due to the deep penetration depth of \gls{nir} light\cite{bec2019breakthrough}.
-
+\fi
 %\td{describe simple IR with monochromator}
@@
 %
-In the \gls{ft} spectrometer the beam is sent through the sample, split and 
+In the \gls{ft} spectrometer, on the other hand, the beam is sent through the sample, split and 
 reflected from a static and from a moving mirror, recombined and detected by a photo 
 multiplier (a device which transforms photons into electrical signals). 
-How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
+%How the two beams will interfere upon recombination 
+The interference of the two beams 
+depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
 In a \gls{ft} spectrometer the reference has to be measured before the sample.
+
+\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident angle) were recorded with a Bruker Vertex 70 spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588} {\nano\meter}) and a silicon detector for visual and \gls{nir} light (\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}).
+% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
+For transmittance the light entered the sample from the side with the layer. 
+The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged in Opus software. % included in the spectrometer. 
 %
@@
 %differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
+\td{specifications of instruments}
 
@@
 
+\Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer.
+The diffractograms were measured for \SI{2}{\minute} in reflection mode with \ch{Cu}-$K_{\alpha}$ radiation ($\lambda$=\SI{1.541874}{\angstrom}).
+%. (where are the conditions?)}
+All \gls{xrd} diffractograms were taken at \SI{5}{\degree} incident angle and compared to the internal database.
+
 %\url{https://chem.libretexts.org/Courses/Franklin_and_Marshall_College/Introduction_to_Materials_Characterization__CHM_412_Collaborative_Text/Diffraction_Techniques/X-ray_diffraction_(XRD)_basics_and_application}\\

### 2024-07-07 doc/Thesis/chapter/03-experimental.tex
edit until incl FTIR/XRD

@@
 All characterization procedures were executed at room temperature.
-All \gls{sem} micrographs were taken with a Zeiss Supra 40 with  \SI{5}{\kilo\volt} acceleration voltages.
+\iffalse
+%All \gls{sem} micrographs were taken with a Zeiss Supra 40 with  \SI{5}{\kilo\volt} acceleration voltages.
 %\td{5kV, raum temperature, vacuum???}
-\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
-angle) were recorded with a Bruker Vertex 70 
-%transmission [\%] and reflection?  which angle? 
-spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
-Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588}
+%
+\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident angle) were recorded with a Bruker Vertex 70 spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588} {\nano\meter}) and a silicon detector for visual and \gls{nir} light (\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}).
 % gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
-{\nano\meter}) and a silicon detector for visual and \gls{nir} light 
-(\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). For transmittance the light
-entered the sample from the side with the layer. The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged 
-in Opus software. % included in the spectrometer. 
+For transmittance the light entered the sample from the side with the layer. 
+The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged in Opus software. % included in the spectrometer. 
 %\td{
+%
 \Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer.
@@
 All \gls{xrd} diffractograms were taken at \SI{5}{\degree} incident angle and compared to the internal database.
+\fi
 

### 2024-07-07 doc/Thesis/chapter/021-theory-calculations.tex
edit until excl 030

@@
 Although \gls{ml} uses several statistical methods, their goal and frame conditions are different.
+%
+Statistics and \gls{ml} are two closely related field and statistics influences \gls{ml} a lot, but \gls{ml} is not just statistics with repackages with a new hip buzzword. 
+They differ in their methods, approachs and goals. 
+%
 %\td{The goal of machine learning is to ???}
 %
-\Gls{ml} tries to predict unseen data points accurately and statistics is a subfield of maths 
-which tries to get insight into a given data. 
+\Gls{ml} tries to predict unseen data points accurately and statistics is a subfield of maths which tries to get insight into a given data. 
 For example, in a statistical model, it is desirable to reduce the number of inputs. 
-This allows a statistician to better study how a change in input variables can 
-directly affect a output variable\cite{gontcharov2019}.
+This reduction of inputs allows a statistician to better study how a change in input variables can directly affect a output variable\cite{gontcharov2019}.
 %pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
-More precisely, mathematical statistics (stochastics)\cite{haertler2014statistisch} is the subject of 
-finding mathematical models to describe the data 
-whereas (classical) statistics is the domain of representing the data. 
+More precisely, mathematical statistics (stochastics)\cite{haertler2014statistisch} is the subject of finding mathematical models to describe the data whereas (classical) statistics is the domain of representing the data.
 Nonetheless, statistics and maths is at the very basis of \gls{ml}.
@@
 
-But fear not, that does not mean that computers are 
-more intelligent than humans
-or \linebreak[4]
-sentient\cite{searle1980,searle1999married} even though some claim\cite{tiku2022google} and it certainly does not mean that research is over. 
+But this does not mean that computers are more intelligent than humans or \linebreak[4] sentient\cite{searle1980,searle1999married} even though some claim\cite{tiku2022google} and it certainly does not mean that research is over.
 AI is still a young field, which is strongly growing and is gaining ubiquitous status. 

### 2024-07-07 doc/Thesis/chapter/03-experimental.tex
change aquatic to aqueous

@@
 \section{Substrate Preparation}
-%\ds{
 Five different substrates were used throughout this work: 
-microscope glass slides 
-\linebreak[4] 
+1 mm-thick, soda-lime microscope glass slides 
+%\linebreak[4] 
 (\cm{2.5}$\times$\cm{7.5}) from Sigma Aldrich, thinner, 
-squared glass plates (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich, 
-\gls{ito} plates (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich, 
-\gls{fto} plates (\cm{5}\x\cm{5}) from Sigma Aldrich and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
-%}
+squared glass plates (\cm{2.5}\x\cm{2.5}) Menzel Gläser,
+\gls{ito} coated glass (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich with a sheet resistance of approximately 12 $\Omega$/sq, 
+\gls{fto} coated glass (\cm{5}\x\cm{5}) from Sigma Aldrich and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
 %
+The steel foil was cut with a foil cutter into \cm{2.5}\x\cm{2.5} squares.
 Glass was used because of its low price point and availability and to measure transmission and reflectance spectra. 
-\gls{fto} and \gls{ito} were used in order to have a conducting substrate. 
+\Gls{fto} and \gls{ito} coated conducting substrates were used for \gls{sem} investigation and for electrical measurements (serving as one of the electrical contacts).
+%\gls{fto} and \gls{ito} were used in order to have a conducting substrate. 
 %, which is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (don't follow?)}
@@
 Furthermore, while taking a \gls{sem} micrograph the sample would quickly accumulate negative charge and repell further electrons without a conducting substrate.
-The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
-The steel foil was cut with a foil cutter into squares of the same dimensions. 
+%The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
+%The steel foil was cut with a foil cutter into squares of the same dimensions. 
 %, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
@@
 \begin{enumerate}
-	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
-	\item \minutes{15} in \gls{water} in a sonic bath
-	\item \minutes{15} in \gls{ipo} in a sonic bath 
+	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a ultrasonic bath
+	\item \minutes{15} in \gls{water} in a ultrasonic bath
+	\item \minutes{15} in \gls{ipo} in a ultrasonic bath 
 \end{enumerate}
@@
 All recipes for solutions can be divided into two categories:
-the first recipe - adopted from Anwar~et~al.~\cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} (aquatic solution).
+the first recipe - adopted from Anwar~et~al.~\cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} (aqueous solution).
 The second recipe - adopted from Hu~et~al.~\cite{Hu2016} - was based on \gls{zrpro} in \gls{buoh} (buthanolic solution).
@@
 		\label{fig:sol-aq}
-		\caption{Aquatic solution}
+		\caption{Aqueous solution}
 	\end{subfigure}
@@
 	\label{fig:sol}
-	\caption{Aquatic and buthanolic solution with magnetic stirring bars in beaker glass sealed with Parafilm} 
+	\caption{Aqueous and buthanolic solution with magnetic stirring bars in beaker glass sealed with Parafilm} 
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Aquatic Precursor Solutions}
+\subsection{Aqueous Precursor Solutions}
 \label{sec:exp-sol-aq}
@@
 	\centering
-	\caption{Compositions of different aquatic solutions}
+	\caption{Compositions of different aqueous solutions}
 	\label{tab:rec1}
@@
 %\td{Screening}
-%244 - 93 aquatic - 103 testing - 191 buthanol - 206 preopt - 244 emma
+%244 - 93 aqueous - 103 testing - 191 buthanol - 206 preopt - 244 emma
 % 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
-244 samples were produced: 93 samples with the aquatic recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).
+244 samples were produced: 93 samples with the aqueous recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).
 
@@
 \td{(xxx but using a completely untested recipe!)}
-%Initially, glass plates were doctor bladed manually with aquatic solution and calcinated 
+%Initially, glass plates were doctor bladed manually with aqueous solution and calcinated 
 %via HP1. 
@@
 %\todo{different additives, heating programs (NT1-NT5 and HP1), blade distances (distance between blade and substrate) and layer counts were tried}
-%Composition of the \td{aquatic solution (I thought this did not work?)}, heating program, blade distance (distance between blade and substrate) and layer count were varied but no homogeneous layers resulted.
+%Composition of the \td{aqueous solution (I thought this did not work?)}, heating program, blade distance (distance between blade and substrate) and layer count were varied but no homogeneous layers resulted.
 %

### 2024-07-07 doc/Thesis/chapter/050-results-material.tex
change aquatic to aqueous

@@
 %%%%%%%% AQUATIC 
-As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer of \gls{zro}.
+As already indicated in the experimental section the aqueous recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer of \gls{zro}.
 The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
@@
 Figure~\ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
-%These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aquatic recipe. 
+%These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aqueous recipe. 
 Large cracks, non-coated areas and inhomogeneity were 
@@
 shared characteristics among 
-all samples created with the aquatic recipe. 
+all samples created with the aqueous recipe. 
 %even after several/multiple/various alteration to the recipe.
@@
 		SEM images of of \gls{zro}:
-		(a) \gls{zro} produces by 2 layers aquatic solution on \gls{fto}
+		(a) \gls{zro} produces by 2 layers aqueous solution on \gls{fto}
 		(b) 10 layers of \gls{zro} on steel substrate

### 2024-07-07 doc/Thesis/chapter/03-experimental.tex
edit until excl. Pre-optimization of Coating Procedure

@@
 %Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
-Unfortunately, this solution failed to produce homogeneous layers, but instead only resulted in sparse patches of \gls{zro} on the substrate.
+Unfortunately, this solution failed to produce homogeneous layers, but instead only resulted in sparse patches of deposits on the substrate.
 Thus, an alternative solution was found.
@@
 \label{sec:exp-db}
-All glass substrates were doctor bladed manually with a smooth stainless steel wire bar coater. 
-On two opposing edges adhesive tape was applied to create a valley in between. 
+All glass substrates were tape-casted manually with a smooth stainless steel wire bar coater. 
+On two opposing edges adhesive tape was applied. %to create a valley in between. 
+This allowed material to only be deposited on the area between the tape.
 After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
@@
 \ul{100} of solution were 
-applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the 
-liquid evenly. After evaporation of the solution, the vacuum was turned off, the 'blade 
-pusher' was put into initial position, the blade was removed and excess solution 
-was removed from the plate with a wipe. 
+applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the liquid evenly. 
+After evaporation of the solution, the vacuum was turned off, the pushing bar
+%'blade pusher' \td{film applicator, travel pusher, traverse something, pushing bar} 
+was put into initial position, the blade was removed and excess solution was removed from the plate with a wipe. 
 The coated substrate was dried for \minutes{5} on a \SI{200}{\celsius} heating plate.
@@
 
-\begin{figure}[htb]
+\begin{figure}[tb]
 	\centering
@@
 
-The \gls{iv} curves were measured with Agilent 4156C Precision Semiconductor 
-Parameter Analyzer from \SI{-0.5}{\volt} to \SI{0.5}{\volt} with steps of 
-\SI{10}{\milli\volt}.
-Prior to \gls{iv} measurements the samples were sputtered with aluminium 
-through a mask to produce a multitude of equidistant contacts with a Leybold 
-UNIVEX450C Sputter System.
-Directional current sputtering was used with argon as inert gas at \SI{0.005}{\milli\bar} 
-and with a power of \SI{40}{\watt} for \SI{700}{\second}.
-Between sputtering and \gls{iv} measurements 
-direct contacts to the steel substrate were created by removing a patch of the \gls{zro}
-layer with 
-sand paper on two opposing edges of a sample and then by applying silver paste.
+The \gls{iv} curves were measured with Agilent 4156C Precision Semiconductor Parameter Analyzer from \SI{-0.5}{\volt} to \SI{0.5}{\volt} with steps of \SI{10}{\milli\volt}.
+
+Top contacts for the I-V measurements were formed 
+with a Leybold UNIVEX450C Sputter System.
+by sputtering 200 nm of aluminum through a shadow mask, defining circular contacts of a diameter approximately \SI{6}{\milli\meter}. 
+The bottom contacts to the steel substrate or to the ITO- or FTO-coated glass were formed by removing the ZrO2 deposit from a corner of the substrate, by soft abrasion with sand paper, and then applying conductive silver paste.
+%Prior to \gls{iv} measurements the samples were sputtered with aluminium through a mask to produce a multitude of equidistant contacts with a Leybold UNIVEX450C Sputter System.
+%Directional current sputtering was used with argon as inert gas at \SI{0.005}{\milli\bar} and with a power of \SI{40}{\watt} for \SI{700}{\second}.
+%Between sputtering and \gls{iv} measurements direct contacts to the steel substrate were created by removing a patch of the \gls{zro} layer with sand paper on two opposing edges of a sample and then by applying silver paste.
 See figure~\ref{fig:circuit} for a sketch of the connectivity.
+
+The measured I-V curves therefore represent the vertical resistance of the deposited layer. 
+This resistance will be predominantly influence by the presence of shunts (hotspots or short-cuts between the top and bottom contact), appearing due to the inhomogenous thickness, and pinholes through the ZrO2 layer.
 
@@
 %
-The average of each conductance would be an easy and naive choice but difficult to represent a 
+The average of each conductance would be an easy choice but difficult to represent a 
 sample correctly since the possible values of conductance span across several magnitudes.
@@
 \gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
-to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conducticity hereafter for lack of a better term. 
+to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conductivity hereafter. % for lack of a better term. 
 %As a measure of conductance a distance $D$ from an ideal non-conducting case. 
@@
 \end{equation}
-Another measure is the density of shorted species $\rho$ (pinhole density), calculated in following way:
+Another measure is the density of shorted elements $\rho$ (pinhole density), calculated in following way:
 \begin{equation}
@@
 % 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
-244 samples were produced: 93 samples with the aqueous recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).
+% 244 samples were produced: 93 samples with the aqueous recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).
 

### 2024-07-24 doc/Thesis/chapter/03-experimental.tex
finish editing 03

@@
 %The drying stains could be circumvented by using a heat gun, but the results were not reproducible.
-The glass plate of the film applicator was exchanged with a metal plate.
-This allowed to hold the sample in place through underpressure and control temperature. 
+
+%starting with pre-optimisation
+%The glass plate of the film applicator was exchanged with a metal plate.
+A metal plate with vacuum chuck and temperature control was used as a base in the film applicator. 
+%This allowed to hold the sample in place through underpressure and control temperature. 
 The bounds of the process variables were then explored in a preliminary study 
@@
 as nominal and extreme values for 
-relative concentration of Zr $c_{zr}$, number of coating layers $n_L$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{C}$[\mm{}/\s{}] and \gls{db} temperature $T_{C}$[\oc{}], respectively.
-After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see appendix \ref{sec:app-pre-emma}).
+relative concentration of Zr $c_{zr}$, number of coating layers $n_L$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} speed $v_{C}$[\mm{}/\s{}] and \gls{db} temperature $T_{C}$[\oc{}], respectively.
+After testing the first samples, the lower limit for \gls{db} speed was altered from 0.1 to 1 (see appendix \ref{sec:app-pre-emma}).
 %
@@
 because of much better solution stability and similar electric properties of resulting layers (how did you test this?? see appendix \ref{sec:app-pre-emma}).
-The - up to this moment - best process was chosen to be tested with 
+The best process after this set of experiments was chosen to be tested with 
 \ml{1} \gls{acoh} (sample no.~199), \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} (sample no.~201) and \ml{1} \gls{ipo} (sample no.~192).
 %\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
-The sample produced with \gls{ipo} as stabilization agent showed comparable passivization results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
+The sample produced with \gls{ipo} as stabilization agent showed comparable electric insulation results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
 Therefore, \gls{ipo} was used  as stabilzier in further experiments.

### 2024-07-24 doc/Thesis/chapter/04-computational-details.tex
feinschliff
finish editing 04 comp details

@@
-\section{Evolutionary Model-based Multiresponse Approach}
+\section{Evolutionary Model-based Multiresponse Approach (EMMA)}
 \label{sec:ss}
@@
 The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $n_L$ and $v_{cal}$, 
-(i.e. conducticity, pinhole density, coating layer count and heating rate)
+(i.e. conducticity, pinhole density, number of coated layers and heating rate)
 where $\gamma$, $\rho$ and $n_L$ are to be minimized and $v_{cal}$ to be maximized.
@@
 The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
-The samples are produced, the \gls{iv} curves are measured and measurements evaluated according to section 
-\ref{sec:exp} and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), 
-$n_L$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in 
-\oc{}/\minutes{}) are supplied to the program. 
+The samples are produced, the \gls{iv} curves are measured and the measurements evaluated according to section 
+\ref{sec:exp}, yielding the quantities 
+$\gamma$, $\rho_s$, $n_L$ and $v_{cal}$, which were used as inputs for the program.
+% and the responses conducticity $\gamma$ (see eq.
+\ref{eq:gamma}), pinhole density $\rho_s$ (see eq.
+\ref{eq:rho}), $n_L$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program.
+
 The program, then, uses this data to estimate a response for each output variable 

### 2024-08-06 doc/Thesis/chapter/050-results-material.tex
finish editing 050 results material

@@
 %\subsection{Solution}
-%%%%%%%% AQUATIC 
+%%%%%%%% AQUATIC AQUEOUS
 As already indicated in the experimental section the aqueous recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer of \gls{zro}.
-The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
-Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant did not increase the resistance of the resulting \gls{zro} layers. 
+The aqueous solution started out as opaque slurry in contrast to the buthanolic recipe which became opaque only after degrading. 
+%\td{Die wässrige Lösung hatte direkt nach erzeugung viskose und undurchsichtige Eigenschaften - im Gegensatz zu der anderen Lösung, welche erst nach Stunden von klar auf undurchsichtig umschwenkte.}
+%The solution was opaque from the beginning and 
+Furthermore, the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
+Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant did not increase the measured resistance through the resulting \gls{zro} layers.
 % ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
@@
 Even after the consecutive application of two layers, 
-there was no significant improvement and the results examined with \gls{sem} (see figure~\ref{fig:sem-old}) reminded rather of a sparse crust than of a film. 
+there was no significant improvement and the \gls{sem} images (see figure~\ref{fig:sem-old}) 
+showed highly inhomogeneous deposition, with deposited  areas next to other areas where the conductive substrate (ITO or FTO) can be clearly seen  uncoated.
+%reminded rather of a sparse crust than of a film. 
 %It is assumed that the solution was far from the optimum for a sol-gel process. 
@@
 	\caption{
-		SEM images of of \gls{zro}:
+		SEM images of \gls{zro}:
 		(a) \gls{zro} produces by 2 layers aqueous solution on \gls{fto}
@@
 
-The sol-gel recipe optimized by Hu et al.\cite{Hu2016} for \ch{Al2O3} worked splendidly for our use case even after (not so) minor changes (see section~\ref{sec:exp-sol-bu}). 
+The sol-gel recipe reported by Hu et al.\cite{Hu2016} and further optimzed, led to improved results (see section~\ref{sec:exp-sol-bu}). 
 %
@@
 %%%% PIN HOLES
-The large irregularity on the bottom left could depict a pin hole, a (tiny) hole in the layer that reaches to the substrate. 
+The large irregularity on the bottom left could depict a pin hole, a hole in the layer that reaches to the substrate. 
 These irregularities are rather the exception. 
-Alternatively, the small, hardly visible slits spread across the surface could depict such pin holes. 
+Alternatively, the small, hardly visible cracks spread across the surface could depict such pin holes. 
 % These - I think - are rather only one layer deep irregularities since they are so prevalent and hardly any pin holes were electrically observed on similar samples. \todo{where is the evidence?}
@@
 As soon as the solution showed initial cloudiness, it was declared as unstable and used no more for \gls{db}. %\td{(coating! DB = deutsche Bahn ... ist mir schon vorher aufgefallen)}
+The solution becoming opaque indicated build-up of precipitation and was not further used.
 The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent \gls{acoh} with \gls{ipo}.
@@
 %\td{what is this aging process chemically? oxidation, hydrolization?}.
-The aging process was accelerated by being in contact with "fresh" air in contrast to being sealed. 
-It therefore dependent on the water in the air corresponding to an hyrolization process\cite{Hu2016}.
+The aging process was accelerated by absence of proper sealing.
+\td{The aging process dependends on the water in the air corresponding to an hyrolization process\cite{Hu2016}.}
 %
-Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
-as they could be stored until the next time needed, instead of producing a separate solution for each sample.
+The introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
+as they could be stored until the next day, instead of producing a new, separate solution for each day.
 %
-It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
+It was found that after a \gls{4f} \gls{acoh} solution has 
+%aged beyond cloudiness 
+shown precipitation (became opaque)
+the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
 This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
@@
 On the lower edge of \gls{fto} a circa \nm{100} thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe) can be observed.
-Measuring the cross section on steel was not as straight forward because the ductility of steel prevents fractures of the substrate. 
-Resorting to scratching the surface with a diamond glass-cutter allowed us to get an insight into the thickness of the layer on steel substrate.
+Measuring the cross section on steel was not as straight forward. 
+%because the ductility of steel prevents fractures of the substrate. 
+%Resorting to 
+Scratching the surface with a diamond glass-cutter allowed us to get an insight into the thickness of the layer on steel substrate.
 %
@@
 clearly stand out against the noise from the experimental diffractogram.
-They confirm that the produced substance is indeed \gls{zro}.
+They confirm that the coated material is indeed \gls{zro}.
 Raman spectra are needed to further clarify the phase, 
@@
 
-In figure~\ref{fig:ir-gt} \gls{uv}/\gls{vis}/\gls{nir} transmission spectra of \gls{zro} layers on glass slides can be seen. 
-Each sample had different numbers of layers. 
+In figure~\ref{fig:ir-gt} \gls{uv}/\gls{vis}/\gls{nir} transmittance spectra of \gls{zro} layers on glass slides can be seen. 
+Each sample had different numbers of coated layers. 
 The incident angle was \ang{0} for each sample.

### 2024-08-11 doc/Thesis/chapter/020-theory-materials.tex
edit until excl. Pre-optimization of Coating Procedure
correct misspellings

@@
 The first section tries to shine light on the evolution of PV and give some background information on \gls{cigs} absorber.
-The next section concerns the description of materials and scientific methods used during the experminental part of this work. 
+The next section concerns the description of materials and scientific methods used during the experinental part of this work. 
 The third and last part focuses on the algorithmic, statistical and analytical methods used to optimize and predict material properties.
@@
 % what is used? 
-Nobel gases (e.g. argon) in plasma phase are mainly used for bombardmnt because of their inert properties. 
-Oxygen or nitrogen can be added to the plasme to deposit oxides or nitrides, respectively.
+Nobel gases (e.g. argon) in plasma phase are mainly used for bombardment because of their inert properties. 
+Oxygen or nitrogen can be added to the plasma to deposit oxides or nitrides, respectively.
 %Reactive gases can be added (e.g. \ch{O2} or \ch{N2}).
@@
 the target and the substrate are positioned parallel and in between the gas is transitioned into plasma and the ions are accelerated in the direction of the target (by a high electrostatic potential).
+
+\todo{what were the used settings: leybold etc.}
+%Prior to \gls{iv} measurements the samples were sputtered with aluminium through a mask to produce a multitude of equidistant contacts with a Leybold UNIVEX450C Sputter System.
+%Directional current sputtering was used with argon as inert gas at \SI{0.005}{\milli\bar} and with a power of \SI{40}{\watt} for \SI{700}{\second}.
 

### 2024-08-11 doc/Thesis/chapter/021-theory-calculations.tex
correct misspellings

@@
 		%{Machine and deep learning in MS research are just powerful statistics – No}
+		%{https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=35376367cf98}
 %What is \gls{ml}? 
-Some might argue that \gls{ml} is just overglorified statistics, but that is not the case. 
+Some might argue that \gls{ml} is just over glorified statistics, but that is not the case\cite{Healy2021Machine}. 
 Although \gls{ml} uses several statistical methods, their goal and frame conditions are different.
@@
 Statistics and \gls{ml} are two closely related field and statistics influences \gls{ml} a lot, but \gls{ml} is not just statistics with repackages with a new hip buzzword. 
-They differ in their methods, approachs and goals. 
+They differ in their methods, approaches and goals. 
 %
@@
 For example, in a statistical model, it is desirable to reduce the number of inputs. 
-This reduction of inputs allows a statistician to better study how a change in input variables can directly affect a output variable\cite{gontcharov2019}.
+This reduction of inputs allows a statistician to better study how a change in input variables can directly affect an output variable\cite{gontcharov2019}.
 %pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
@@
 
-\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
+\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modelled after the brain\cite{bishop1994neural}.
 Artificial neurons (also called nodes), which are arranged in layers, 
@@
 %, whose number of parameter quickly \td{exceeds the practical} for moderate dimensional problems ($n>5$).
-Advantages of \Gls{mars} are that it uses less parameters and it produces continuous models with continous derivatives.
+Advantages of \Gls{mars} are that it uses less parameters and it produces continuous models with continuous derivatives.
 %

### 2024-08-11 doc/Thesis/chapter/023-linreg-krr-svm.tex
work on todos until chap3
correct misspellings

@@
 \end{equation}
-Where $\mathbf{y} \in \mathbb{R}^n$ ($n$ is the number of data points) is a vector of dependent variables which shall be predicted and $\mathbf{X}\in \mathbb{R}^{n\times d}$ ($d$ is the the number of independent variables) is a matrix of independent variables.
-The parameters $\mathbf{k} \in \mathbb{R}^d$ and $c \in \mathbb{R}$ are chosen by minimizing an objective function (loss function in \gls{ml} chargon).
+Where $\mathbf{y} \in \mathbb{R}^n$ ($n$ is the number of data points) is a vector of dependent variables which shall be predicted and $\mathbf{X}\in \mathbb{R}^{n\times d}$ ($d$ is the number of independent variables) is a matrix of independent variables.
+The parameters $\mathbf{k} \in \mathbb{R}^d$ and $c \in \mathbb{R}$ are chosen by minimizing an objective function (loss function in \gls{ml} jargon).
 A typical function to minimize are the $L_1$ and $L_2$ error, i.e. \gls{mae} and \gls{mse}, respectively.
@@
 A kernel is some kind of similarity measure 
-which fulfills the requirements of nonnegativity, symmetry and linearity\cite{rupp2015machine}.
+which fulfills the requirements of non-negativity, symmetry and linearity\cite{rupp2015machine}.
 %\enlargethispage{\baselineskip}
@@
 sigmoidal (eq.~\ref{eq:sig-kernel}) and 
-radial basis functionial kernel~(eq.~\ref{eq:rbf-kernel}), with $\gamma$ as fixed hyperparameter and $c_0$ as parameter to optimize.
+radial basis functional kernel~(eq.~\ref{eq:rbf-kernel}), with $\gamma$ as fixed hyperparameter and $c_0$ as parameter to optimize.
 A requirement for using kernels is having a dot product in the loss function. 
@@
 %
-Classifiction works by spanning a hyperplane between two linearly separable categories in a way such that the closest points from each category have the largest distance to the hyperplane. 
+Classification works by spanning a hyperplane between two linearly separable categories in a way such that the closest points from each category have the largest distance to the hyperplane. 
 The distance from the points to the hyperplane is called margin $\tau$.
@@
 %
-The decision boundary can be expressed as an hyperplane
+The decision boundary can be expressed as a hyperplane
 \begin{equation}
@@
 Thus, maximizing the margin is equivalent with minimizing $\|\mathbf{w}\|$ and minimizing $\frac{1}{2}\|\mathbf{w}\|^2$ (mathematical convenience for further steps).
-By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we 
+By incorporation the constraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we 
 \textit{mathemagically} arrive at the loss function which should be maximized: 
@@
 \end{equation}
-which can be rewritten by some \td{mathematical wizardry} (setting the partial derivatives of the Lagrangian function
+which can be rewritten by some mathematical 
+%wizardry
+acrobatics
+(setting the partial derivatives of the Lagrangian function
 $\frac{\partial \mathfrak{L}}{\partial \mathbf{w}}$ and $\frac{\partial \mathfrak{L}}{\partial b}$ 
@@
 \textbf{Soft margin \gls{svm}} -- in contrast to hard margin \gls{svm} -- is used if the data is non-separable due to outliers\cite{cortes1995support}.
-Such data can be handeled by introducing a penalization term for wrongly categorized samples into the loss function. 
+Such data can be handled by introducing a penalization term for wrongly categorized samples into the loss function. 
 \begin{equation}
@@
 they have opposite signs and their product will be a negative number.
-The substraction of a negative number will result in a positive penalization. 
+The subtraction of a negative number will result in a positive penalization. 
 If the sample is correctly predicted, the product will result in a positive number, 
-the substraction will lead to a negative number and the maximum will be 0 if the sample is ousite of the margin. 
+the substraction will lead to a negative number and the maximum will be 0 if the sample is outside of the margin. 
 %
@@
 
-Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the innerproduct of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper.
+Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the inner product of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper.
 %\td{write about sv regrgession}

### 2024-08-11 doc/Thesis/chapter/03-experimental.tex
correct misspellings

@@
 The conducting substrate allows for easy measurement of electric conductance in vertical direction.
-Furthermore, while taking a \gls{sem} micrograph the sample would quickly accumulate negative charge and repell further electrons without a conducting substrate.
+Furthermore, while taking a \gls{sem} micrograph the sample would quickly accumulate negative charge and repel further electrons without a conducting substrate.
 %The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
@@
 \begin{enumerate}
-	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a ultrasonic bath
-	\item \minutes{15} in \gls{water} in a ultrasonic bath
-	\item \minutes{15} in \gls{ipo} in a ultrasonic bath 
+	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in an ultrasonic bath
+	\item \minutes{15} in \gls{water} in an ultrasonic bath
+	\item \minutes{15} in \gls{ipo} in an ultrasonic bath 
 \end{enumerate}
@@
 (including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
-was added to isopropyl aclohol (\gls{ipo}) and both were stirred for one hour. 
+was added to isopropyl alcohol (\gls{ipo}) and both were stirred for one hour. 
 These additives were added to influence pH and surface tension with the goal to influence the homogeneity of the resulting layer. %(in terms of what?)}. % \td{see Parvulescu2015}
-The \gls{water}-\gls{ipo} mixture was added to the \gls{zrpro}-gls{acac} solution and stirred over night. 
+The \gls{water}-\gls{ipo} mixture was added to the \gls{zrpro}-\gls{acac} solution and stirred over night. 
 The exact volumes can be taken from table~\ref{tab:rec1}.
@@
 plate in the Naberterm muffle furnace. 
-NT2 is an simplification of NT1 and programs NT3~-~NT6 are the same as NT2 with altered 
+NT2 is a simplification of NT1 and programs NT3~-~NT6 are the same as NT2 with altered 
 heating rate and 
@@
 The measured I-V curves therefore represent the vertical resistance of the deposited layer. 
-This resistance will be predominantly influence by the presence of shunts (hotspots or short-cuts between the top and bottom contact), appearing due to the inhomogenous thickness, and pinholes through the ZrO2 layer.
+This resistance will be predominantly influence by the presence of shunts (hotspots or short-cuts between the top and bottom contact), appearing due to the inhomogeneous thickness, and pinholes through the ZrO2 layer.
 
@@
 shortly before the \gls{pso}
-because of much better solution stability and similar electric properties of resulting layers (how did you test this?? see appendix \ref{sec:app-pre-emma}).
-The best process after this set of experiments was chosen to be tested with 
+because of much better solution stability and similar electric properties of resulting layers (see samples 192, 199 and 201 in appendix \ref{sec:app-pre-emma}).
+The best process variables up to this point were chosen to be tested with 
 \ml{1} \gls{acoh} (sample no.~199), \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} (sample no.~201) and \ml{1} \gls{ipo} (sample no.~192).
@@
 The sample produced with \gls{ipo} as stabilization agent showed comparable electric insulation results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
-Therefore, \gls{ipo} was used  as stabilzier in further experiments.
+Therefore, \gls{ipo} was used  as stabilizer in further experiments.
 %\td{After the boundaries of the solution were fixed }

### 2024-08-11 doc/Thesis/chapter/050-results-material.tex
correct misspellings

@@
 
-The sol-gel recipe reported by Hu et al.\cite{Hu2016} and further optimzed, led to improved results (see section~\ref{sec:exp-sol-bu}). 
+The sol-gel recipe reported by Hu et al.\cite{Hu2016} and further optimized, led to improved results (see section~\ref{sec:exp-sol-bu}). 
 %
@@
 The aging process was accelerated by absence of proper sealing.
-\td{The aging process dependends on the water in the air corresponding to an hyrolization process\cite{Hu2016}.}
+The aging process depends on the water in the air corresponding to an hydrolization process\cite{Hu2016}.
 %

### 2024-08-11 doc/Thesis/chapter/051-results-emma.tex
correct misspellings

@@
 Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
-The most insulating recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
+%The most insulating recipes 
+The recipes that produced the most insulating coating for each generation can be seen in table \ref{tab:emma-Gb}. 
 The experiments for generation 5 where not executed but 
@@
 The sample predicted as optimum by the algorithm is experiment number 13 with 
-lowest possible $c_{zr}$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$ and second highest possibel $n_L$ (see table \ref{tab:input}). 
+lowest possible $c_{zr}$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$ and second highest possible $n_L$ (see table \ref{tab:input}). 
 %lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
@@
 that therefore the resulting layer does not insulate well if $T_{cal}$ is low (under \oc{400}). 
-The oppisite is the case, though. % (see figures \ref{fig:g-tcal} and \ref{fig:phd-tcal}).
+The opposite is the case, though. % (see figures \ref{fig:g-tcal} and \ref{fig:phd-tcal}).
 %This would correspond to $+h(400-T_{cal})$
@@
 %(events per predictor variable EPV) are as low as 5. 
-The \gls{epv} (data points per independent varible) are as low as 5 in the here presented optimization. % model and data acquisition method
+The \gls{epv} (data points per independent variable) are as low as 5 in the here presented optimization. % model and data acquisition method
 By eliminating three independent variables the \gls{epv} could rise to 10, which is stated 

### 2024-08-11 doc/Thesis/chapter/052-post-emma.tex
correct misspellings

@@
 That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
-Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artefact of the noise rather than a process property. 
+Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artifact of the noise rather than a process property. 
 %Furthermore the influence on $\hat\rho$ is dominated by $n_L$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.

### 2024-08-11 doc/Thesis/chapter/053-discussion.tex
rename to fit numbering
change lambda to n_L
correct misspellings

--- 2023-10-28 doc/Thesis/chapter/063-discussion.tex
@@
 the "\nameref{sec:phase1}" will be discussed in subsection \ref{sec:phase1}, 
-followed by the "\nameref{sec:phase2}" reviewd in subsection \ref{sec:phase2} 
+followed by the "\nameref{sec:phase2}" reviewed in subsection \ref{sec:phase2} 
 %, thereupon the 
@@
 the complexity of the model can be drastically reduced. 
-This leads to more information which can be extracted from the same amount of data, 
+This leads to more information, which can be extracted from the same amount of data, 
 be it in more detail of the dependence or higher confidence interval. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Optimization, modelling and data generation phase}
+\subsection{Optimization, modeling and data generation phase}
 \label{sec:phase3}
@@
     \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
-    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
+    \item why $\gamma ~ n_L$? (minimum for layer count?) according which eq? emma? 
     \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error?

### 2024-08-11 doc/Thesis/chapter/06-outlook.tex
change lambda to n_L
correct misspellings

@@
 %what did i want to do? 
-The goal of this work was to find a sol-gel blade coating process resulting in an exlectrical insulating zirconium ceramic on top of steel.
+The goal of this work was to find a sol-gel blade coating process resulting in an electrical insulating zirconium ceramic on top of steel.
 This structure then can be used as substrate for thin layer photovoltaics. 
@@
 The best parameters found by the \gls{emma} optimization were 
-$c_{zr}=2$, $\lambda=10$, $v_{C}=10$, $T_{C}=40$, $v_{cal}=120$ and $T_{cal}=300$.
+$c_{zr}=2$, $n_L=10$, $v_{C}=10$, $T_{C}=40$, $v_{cal}=120$ and $T_{cal}=300$.
 %\todo{$T_{cal}=300$}. 

### 2024-08-11 doc/Thesis/chapter/01-introduction.tex
start doing todo.md

@@
 Furthermore, 
-it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
+it uses the sun's energy directly in contrast to other energy sources (e.g.\ wind, water or even carbon based) and therefore 
 it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search, kardashev1964transmission} which harness the whole power output of the sun.
@@
 %An economic and scalable method is doctor blading via a sol-gel process. 
-Sol-gel roll-to-roll coating processes (e.g.
-tape casting) are economic and scalable methods to apply liquid precursors to substrates, and have been also reported for the deposition of \ch{ZrO2}\cite{yeo1998design,michalek2015comparison}.
+Sol-gel roll-to-roll coating processes (e.g.\ tape casting) are economic and scalable methods to apply liquid precursors to substrates, and have been also reported for the deposition of \ch{ZrO2}\cite{yeo1998design,michalek2015comparison}.
 Sol-gel processes often produce porous layers, though.

### 2024-08-11 doc/Thesis/chapter/020-theory-materials.tex
start doing todo.md

@@
 The n-type side of the p-n junction has excess electrons and p-type side has excess electron holes. 
-If the n- and p-type are of the same basis material, they are called homojunctions (e.g.
-silicon); if not, heterojunctions (e.g.
-\ch{CdS}/\gls{cigs} and \ch{CdS/CdTe})\cite{breitenstein2013understanding}.
+If the n- and p-type are of the same basis material, they are called homojunctions (e.g.\ silicon); if not, heterojunctions (e.g.\ \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe})\cite{breitenstein2013understanding}.
 %
@@
 	\includegraphics[width=\textwidth]{./Pics/cigs.png}
-    \caption{Schematic layer sequence of a standard \ch{ZnO}/\ch{CdS}/\ch{Cu(In,Ga)Se2} thin-film solar cell.\cite{rau2013cigs}}
+    \caption{Schematic layer sequence of a standard \ch{ZnO}/\ch{CdS}/\ch{Cu(In,Ga)Se2} thin-film solar cell\cite{rau2013cigs}.}
 	\label{fig:cigs}
@@
 %
-Instead of glass as substrate, steel and polymers (e.g. polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
+Instead of glass as substrate, steel and polymers (e.g.\ polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
 They both come with their own inconveniences. 
@@
 Thus, an insulating layer has to be deposited on the steel substrate. 
-%The conductance of steel can be masked by a insulator layer (e.g. \ch{ZrO2}, \ch{Al2O3}).
+%The conductance of steel can be masked by a insulator layer (e.g.\ \ch{ZrO2}, \ch{Al2O3}).
 
@@
 % what is used? 
-Nobel gases (e.g. argon) in plasma phase are mainly used for bombardment because of their inert properties. 
+Nobel gases (e.g.\ argon) in plasma phase are mainly used for bombardment because of their inert properties. 
 Oxygen or nitrogen can be added to the plasma to deposit oxides or nitrides, respectively.
-%Reactive gases can be added (e.g. \ch{O2} or \ch{N2}).
+%Reactive gases can be added (e.g.\ \ch{O2} or \ch{N2}).
 In order to use sputtering for depositing a target material on top of a substrate material, 
@@
 %\Gls{pvd} can be divided into activation by thermal energy and activation by energetic particle bombardment. 
-%Sputtering is of the latter kind, which is advantageous if substrates can't withstand high temperatures.
+%Sputtering is of the latter kind, which is advantageous if substrates can not withstand high temperatures.
 %\td{what can it be used for?}\\
@@
 This prevents charge from building up on the target. \linebreak[2]
-Although radio frequency sputtering is more versatile, directional current sputtering is more common because of it's simpler system and economical reasons.
+Although radio frequency sputtering is more versatile, directional current sputtering is more common because of its simpler system and economical reasons.
 %\td{sputtered particles are neutral and not influenced by the electrical field}
@@
 which - in vacuum - moves with the speed of light ($c = \mps{299792458}$)\cite{gHobel2006international}.
-In other materials light moves with the velocity $v=c/n(\lambda)$, where $n(\lambda)$
+In other materials light moves with the speed $v=c/n(\lambda)$, where $n(\lambda)$
 is the refractive index which is dependent on the wavelength $\lambda$. 
@@
 X-rays interact with core electrons, \gls{uv}/\gls{vis} with valence electrons, \gls{ir} with 
-%\td{it's adsorbed by certain groups?)} 
+%\td{it is adsorbed by certain groups?)} 
 vibrations of certain groups, microwaves with molecular rotations and radio with electron and nuclear spins. 

### 2024-08-11 doc/Thesis/chapter/021-theory-calculations.tex
start doing todo.md

@@
 At the moment it is hard to imagine a computer getting a higher ratio than a human
-but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future; especially with ChatGPT's convincingly human-like answers\cite{dis2023chatgpt}.
+but when reading AI written articles\cite{gpt2020}, it is easy to see this test being passed in the near future; especially with ChatGPT's convincingly human-like answers\cite{dis2023chatgpt}.
 
@@
 certain fields get incorporated into \gls{ai} research and practice,
-such that after some time of general use it is no more considered \gls{ai} (e.g. spam filter or web searches).
+such that after some time of general use it is no more considered \gls{ai} (e.g.\ spam filter or web searches).
 Google CEO Sundar Pichai even goes as far and said: 
@@
 and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
-are optimised during training. 
+are optimized during training. 
 %
@@
 There are also lesser known \gls{ml} algorithms such as 
-evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
+evolutionary algorithms (e.g.\ \gls{ga} and \gls{pso}).
 Evolutionary algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simultaneously\cite{villanova2010function}.
@@
 %To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
-Each particle has an associated position and velocity. 
+Each particle has an associated position and speed. 
 Every movement across the search space is, 
@@
 %stochastic and 
-influenced by its particle velocity and position as well as its and the swarm's best visited position.
+influenced by its particle speed and position as well as its and the swarm's best visited position.
 
@@
 \gls{mars} is an extension of multivariate linear regression.
-Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g.
-kernel functions).
+Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g.\ kernel functions).
 %, whose number of parameter quickly \td{exceeds the practical} for moderate dimensional problems ($n>5$).
@@
     \item anova (categorical), PCA, step wise regression
-    \item all previous ananlyse data to predict, but don't tell me which data point is needed next 
+    \item all previous ananlyse data to predict, but dont tell me which data point is needed next 
     \item DOE (add data acquisition)
-    \item genetic algorithm and pso (they combine data gen with regression/prediction and optimization, actually incorporate prediction into selection process but don't per se specify which pred and optimization)
+    \item genetic algorithm and pso (they combine data gen with regression/prediction and optimization, actually incorporate prediction into selection process but dont per se specify which pred and optimization)
     \item comment: always tradeoff between complexity and interpretability
@@
 In two cases a deliberate \gls{doe} is especially beneficial.
-(1) If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations).
+(1) If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g.\ drilling for oil or quantum chemical calculations).
 

### 2024-08-11 doc/Thesis/chapter/022-alt-theory-calculations.tex
start doing todo.md

@@
 kernel trick, support vector machines, genetic algorithms and particle swarm algorithms. 
-The last two are special in the sense that they don't provide a certain regression method,
+The last two are special in the sense that they dont provide a certain regression method,
 but rather a frame work to choose the next sample which should be tested in a optimization. 
@@
 The parameters $\mathbf{k}$ (size $\mathbb{R}^d$) and $c$ (size $\mathbb{R}$) are chosen by minimizing an objective function (loss function in \gls{ml} chargon).
-A typical function to minimize are the L1 and L2 error, i.e. \gls{mae} and \gls{mse}, respectively.
+A typical function to minimize are the L1 and L2 error, i.e.\ \gls{mae} and \gls{mse}, respectively.
 \begin{align}

### 2024-08-11 doc/Thesis/chapter/03-experimental.tex
start doing todo.md

@@
 %\gls{fto} and \gls{ito} were used in order to have a conducting substrate. 
-%, which is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (don't follow?)}
+%, which is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (dont follow?)}
 The conducting substrate allows for easy measurement of electric conductance in vertical direction.
@@
 Lower \gls{db} velocities resulted in less homogeneous layers.
-Thus, the \gls{db} velocity was not altered in the manual \gls{db} process. 
+Thus, the \gls{db} speed was not altered in the manual \gls{db} process. 
 One and two layers of adhesive tape were used to alter the depth of the valley.
@@
 (room temperature, \SI{40}{\celsius}, \SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) 
-and the \gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
+and the \gls{db} speed (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
 the blade was put into its initial position, the sample was placed on the vacuum plate and the vacuum 
@@
 %
-%\todo{why didn't i just take this?}
+%\todo{why did not i just take this?}
 %\td{L2 norm because it might be easier to compare to other methods. }
@@
 %
-For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
+For every I-V curve (i.e.\ for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
 5 points before and 5 points after the origin with minimum one point distance from zero (which boils
@@
 %\td{preopt of what? recipe?}
-%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
+%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e.\ my brain)}
 %\td{Screening}
@@
 %\td{should maybe put this into beginning of section \ref{sec:exp}?}
-%otherwise the sample would charge and can't be pictured anymore. 
-%this means if the produced layer is thick and homogeneous enough, it's difficult to see in sem
+%otherwise the sample would charge and can not be pictured anymore. 
+%this means if the produced layer is thick and homogeneous enough, it is difficult to see in sem
 %Different additives were included in the recipe (see table \ref{tab:rec1}) and the resistance was checked with a multimeter. 
@@
 %$v_{cal}$[\oc{}/\h{}]
-%Especially the doctor blading velocity.
+%Especially the doctor blading speed.
 %}
@@
 %There were many variables which had to be taken into account. 
-%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, C velocity and C temperature as input variables.}
+%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, C speed and C temperature as input variables.}
 See table~\ref{tab:input} for the input space spanned during the optimization.
@@
 		$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
-%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
+%        concentration   &layers &\gls{db} speed  &\gls{db} temperature   &heating rate   &calcination temperature    \\
         \hline
@@
 layers 4 - 12 (2),
-\gls{db} velocity 10 - 20 (2),
+\gls{db} speed 10 - 20 (2),
 \gls{db} temperature 20 - 80 (20),

### 2024-08-11 doc/Thesis/chapter/04-computational-details.tex
start doing todo.md

@@
 %
-%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
+%An initial population of particles, i.e.\ experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
 \begin{table}[htb]
@@
 The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $n_L$ and $v_{cal}$, 
-(i.e. conducticity, pinhole density, number of coated layers and heating rate)
+(i.e.\ conductivity, pinhole density, number of coated layers and heating rate)
 where $\gamma$, $\rho$ and $n_L$ are to be minimized and $v_{cal}$ to be maximized.
@@
 $\gamma$, $\rho_s$, $n_L$ and $v_{cal}$, which were used as inputs for the program.
-% and the responses conducticity $\gamma$ (see eq.
+% and the responses conductivity $\gamma$ (see eq.
 \ref{eq:gamma}), pinhole density $\rho_s$ (see eq.

### 2024-08-11 doc/Thesis/chapter/050-results-material.tex
start doing todo.md

@@
 A single example for a very low conductance measurement in non-logarithmic scale can be seen in figure~\ref{fig:iv-nocurrent}.
-The conductance (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}) for each measurement.
+The conductance (i.e.\ the gradient at V=0) was calculated (see section~\ref{sec:eval}) for each measurement.
 Figure~\ref{fig:iv-stat-good} shows the distribution of gradients $g$ for the same sample as depicted in \ref{fig:iv-log-good}.
@@
 the boundaries of the input variables were explored. 
-Especially, the \gls{db} velocity $v_{C}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
+Especially, the \gls{db} speed $v_{C}$ (i.e.\ the speed with which the blade moves and spreads the solution over the sample)
 was varied and examined during pre-optimization. 
-The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
+The slower the \gls{db} speed, the more uniformly the solution evaporated. 
 If the $v_{C}$ was too slow (less than \mmps{1}), no \gls{zro} layer was formed. 
@@
 This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
-Additionally, the coating temperature affects the evaporation process together with the \gls{db} velocity $v_{C}$.
+Additionally, the coating temperature affects the evaporation process together with the \gls{db} speed $v_{C}$.
 
@@
 %No effect on the solution or the resulting layer was noticed \td{from the initial stirring}
-%\todo{Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
+%\todo{Following stirring times (in minutes) were tested and did not have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
 %The stirring time was untersucht, but not much difference so shortest was used because 
@@
 %but the recipe should be altered thoroughly. 
-%two layers were also tried but didn't even pass the visual examination/test/inspection. 
+%two layers were also tried but did not even pass the visual examination/test/inspection. 
 %A curst was produced. 

### 2024-08-11 doc/Thesis/chapter/051-results-emma.tex
start doing todo.md

@@
 lowest possible $c_{zr}$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$ and second highest possible $n_L$ (see table \ref{tab:input}). 
-%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
+%lowest solution concentration, second highest layer count, lowest \gls{db} speed and temperature, 
 %and lowest calcination heating rate and temperature.
@@
 It can be seen in table~\ref{tab:emma-pred-G} 
-that the predicted conducticity $\hat{\gamma}$ 
+that the predicted conductivity $\hat{\gamma}$ 
 (predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
@@
 	\centering
-    \caption{Predicted conductance measure $\hat{\gamma}$ for each generation by each generation's regression function}  
+    \caption{Predicted conductivity measure $\hat{\gamma}$ for each generation by each generation's regression function}  
     \label{tab:emma-pred-G}
@@
 %
-Contrarily, the predicted conducticity $\hat{\gamma}$ for each generation's optimum
+Contrarily, the predicted conductivity $\hat{\gamma}$ for each generation's optimum
 (predicted by the very generation's \gls{rf}) does increase with each iteration 
@@
 In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
-conducticity $\gamma$ and pin hole density $\rho$ (see section \ref{sec:eval}), of each particle at each generation.
+conductivity $\gamma$ and pin hole density $\rho$ (see section \ref{sec:eval}), of each particle at each generation.
 The the solid circles at generation number 0 indicate particles which were not included to be propagated. 
@@
 the prediction functions (see equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal4})) 
-and the chosen samples (i.e. chosen input variables) where not exactly as expected. 
+and the chosen samples (i.e.\ chosen input variables) where not exactly as expected. 
 Neither expected were the measurements for these samples.
@@
 	\caption{
-		(a)~calculated conductance measures~$\gamma$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation.
+		(a)~calculated conductivity measures~$\gamma$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation.
 		(b)~calculated pin hole density~$\rho$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation.
-		(c)~calculated conductance measures~$\gamma$ against calcination temperature $T_{cal}$
+		(c)~calculated conductivity measures~$\gamma$ against calcination temperature $T_{cal}$
 		(d)~calculated pin hole density~$\rho$ against calcination temperature $T_{cal}$
@@
 %, but the positive influence of the layer count $n_L$ is counter intuitive
-%as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
+%as one would expect more layers to be more insulating and thus result in lower conductivity and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
 The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) 
@@
 % TCAL ON OPTIMIZANDS
-The influence of $T_{cal}$ on the measures of conductance ($\hat\rho$ and $\hat\gamma$) is highly interesting. 
+The influence of $T_{cal}$ on the measures of conductivity ($\hat\rho$ and $\hat\gamma$) is highly interesting. 
 It was expected that 
@@
 according to equations~(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) (see also figures~\ref{fig:g-tcal} and \ref{fig:phd-tcal}), 
-ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.
+ergo the resistance decreases and the conductivity increases with increasing calcination temperature contrary to expectations.
 
@@
 This decrease in validation (out-of-sample) \gls{mse} supports the hypothesis stated at the beginning of this section: 
-the measure of conductance was underestimated and the estimate improved over time (see table~\ref{tab:emma-pred-G}).
+the measure of conductivity was underestimated and the estimate improved over time (see table~\ref{tab:emma-pred-G}).
 %\td{why is \gls{mse} higher with higher values? No homoscedasticity ( equality of variance)?
@@
 Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
-Too many independent variables make it harder to distinguish variance due to random error (e.g.
-unmeasured and uncontrolled variables) from variance due to dependency.
+Too many independent variables make it harder to distinguish variance due to random error (e.g.\ unmeasured and uncontrolled variables) from variance due to dependency.
 % of chosen dependent variables.
@@
 The two independent variables $v_{cal}$ and $n_L$ were included as \textit{optimizands} for two reasons: 
-Maximizing the calcination velocity and minimizing the number of layer application iterations leads to minimization of process time.
+Maximizing the calcination speed and minimizing the number of layer application iterations leads to minimization of process time.
 The process time optimization would be better placed in a follow up study. 
@@
 It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
-Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
+Even if it did not influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
 Overall there were too many variables involved for such a small dataset

### 2024-08-11 doc/Thesis/chapter/052-post-emma.tex
start doing todo.md

@@
 %\textbf{Pre-writing:}
-%\Gls{anova} doesn't provide a lot of extra information. 
+%\Gls{anova} does not provide a lot of extra information. 
 %wrong the second is not for phd but for extended data set
@@
 %
-More particularly, $T_{cal}$ and $T_{C}$ have positive coefficients, i.e. a negative influence on the resistance 
-and $n_L$, $v_{C}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
+More particularly, $T_{cal}$ and $T_{C}$ have positive coefficients, i.e.\ a negative influence on the resistance 
+and $n_L$, $v_{C}$ and $v_{cal}$ have negative coefficients, i.e.\ a positive influence on resistance. 
 An indication that the data is strongly tainted by noise (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
@@
 %
-Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $n_L$ are largest in value, but the values which are factored with these coefficients - i.e.\, $c_{zr}$ and $n_L$ themselves -- are the smallest among the input variables.
+Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $n_L$ are largest in value, but the values which are factored with these coefficients - i.e.\ $c_{zr}$ and $n_L$ themselves -- are the smallest among the input variables.
 Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 

### 2024-08-11 doc/Thesis/chapter/053-discussion.tex
start doing todo.md

@@
 \label{sec:phase2}
-The selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} %(page 25)
+The selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself\cite{cherkassky1998learning}.
+%(page 25)
 After having decided on a base recipe, it is important to define limits and decrease the number of independent variables. 
@@
 The \gls{epv} in this work is round 5,
-which is low in comparison with literature consulted
-\cite{
+which is low in comparison with literature consulted\cite{
 ahmed2017preparation,
@@
 %	\item How to incorporate a priori assumptions into learning? 
-%	\item How to measure model complexity (i.e. flexibility to fit the training data)?
+%	\item How to measure model complexity (i.e.\ flexibility to fit the training data)?
 %	\item How to find a optimal balance between the data and a priori knowledge? 
@@
     \item \textbf{objective} should be defined as clear as possible.
-It will help to set a clear goal for each todo, e.g.
-the primary goal of a screening experiment is to identify the active factors.\cite{miller2001using} Which question should be answered and aufstellen a null Hypothesis.
+It will help to set a clear goal for each todo, e.g.\ the primary goal of a screening experiment is to identify the active factors\cite{miller2001using}.
+Which question should be answered and aufstellen a null Hypothesis.
 This is often very trivial, but let's you focus on the correct path.
@@
 More complex and flexible models might lead to better estimates with less interpretability.
-Identifying the most important input variables.
-\cite{cherkassky1998learning}
+Identifying the most important input variables\cite{cherkassky1998learning}.
 \fi
@@
 \cite{miller2001using}} But $2^6=64$ are too many for preliminary test so maybe check base and from there do $2\cdot6=12$ experiments.
-Then focus on selected input vars, which might have mutliple maxima \\ \td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
-    \item \textbf{factorial design} (classical \gls{doe}) is more robust at feature extraction for error laden data \cite{giunta2003overview} putting data on the extrems makes trend extraction easier.
+Then focus on selected input vars, which might have mutliple maxima \\ \td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see Miller 2001\cite{miller2001using} section 1) }
+    \item \textbf{factorial design} (classical \gls{doe}) is more robust at feature extraction for error laden data\cite{giunta2003overview} putting data on the extrems makes trend extraction easier.
 "By moving the samples to the boundaries of the design space, the effect of the random error terms is reduced."
@@
 %-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest.
-Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2009}
-%but on the other hand: If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
+Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e.,\ that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2009}
+%but on the other hand: If one is not sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
     \item which input variables could have been left out? why? justify with intuition and maths
@@
 \textbf{Curse and Complexity of Dimensionality}\cite{cherkassky1998learning} chapter 3.1.
-goal is to estimate function with finite samples, so it's always inaccurate (biased). 
+goal is to estimate function with finite samples, so it is always inaccurate (biased). 
 Meaning, full estimate only possible with high sampling density, which is difficult for high dimensional functions.

### 2024-08-11 doc/Thesis/chapter/01-introduction.tex
nearly finish with todos from todo.md

@@
 it uses the sun's energy directly in contrast to other energy sources (e.g.\ wind, water or even carbon based) and therefore 
-it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search, kardashev1964transmission} which harness the whole power output of the sun.
+it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search, kardashev1964transmission}, which harness the whole power output of the sun.
 %
@@
 An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be deposited on top.
-Polymers would be a choice if not for their low thermal stability which does not permit high production temperatures.
+Polymers would be a choice if not for their low thermal stability, which does not permit high production temperatures.
 A non-toxic material which is suitable for the insulation is zirconium oxide (\ch{ZrO2}). 
@@
 %\td{influence} of the production factors on the thickness and resistance of the resulting layer.
-The minimization of the electrical conductance of the layer is performed with a particle swarm optimization 
+The minimization of the electrical conductance of the coating layer is performed with a particle swarm optimization 
 algorithm which has the coating process variables as input. 

### 2024-08-11 doc/Thesis/chapter/020-theory-materials.tex
nearly finish with todos from todo.md

@@
 %
-The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still 
+The first marketable \gls{pv} were crystalline silicon photovoltaic modules, which still 
 have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
@@
 \ch{CdS} was earlier used as front contact, but now only acts as n-type wide-gap window and buffer. 
-After the \ch{CdS} layer 
-A window layer of intrinsic \ch{ZnO} is deposited after the \ch{CdS}, followed by a highly conductive aluminium doped layer. 
+%After the \ch{CdS} layer 
+A window layer of intrinsic \ch{ZnO} is deposited after the \ch{CdS} layer, followed by a highly conductive aluminium doped layer. 
 \ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
@@
 They both come with their own inconveniences. 
-Polymers generally have low thermal stability compared with ceramics and metals which restrict the fabrication temperature of \gls{cigs}.
+Polymers generally have low thermal stability compared with ceramics and metals, which restrict the fabrication temperature of \gls{cigs}.
 Steel, on the other hand, is temperature resistant enough, but is an electric conductor, which is problematic for the serial interconnection of cells into modules. 
@@
 %\section{Materials and Their Analysis}
-\section{Sample preparation}
+\section{Sample Preparation}
 %\todo{COATING OF THE SUBSTRATE or sample preparation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Properties of Zirconium oxide}
+\subsection{Properties of Zirconium Oxide}
 Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV\cite{Anwar2017} and relative permittivity of circa 20 at room temperature\cite{kukli2001dielectric}. 
@@
 %A plasma is created and the ions are accelerated to the surface. 
-The ions, which are accelerated to the surface, mostly originate from a plasma.
+The ions which are accelerated to the surface originate mostly from a plasma.
 The ion bombardment leads to a transfer of momentum from the ions to the surface atoms which in turn leads to a collision cascade. 
@@
 %the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
-The anode, then, emits electrons which collide with gas particles (mostly argon because of its inert nature and potential to transfer more kinetic than lighter noble gases). 
+The anode, then, emits electrons, which collide with gas particles (mostly argon because of its inert nature and potential to transfer more kinetic than lighter noble gases). 
 Some gas particles may get ionized by the collision and the gas cations are accelerated to the anode. 
@@
 
-\subsubsection{Infrared spectroscopy}
+\subsubsection{Infrared Spectroscopy}
 % IR
@@
 % gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
-For transmittance the light entered the sample from the side with the layer. 
+For transmittance the light entered the sample from the side with the coating layer. 
 The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged in Opus software. % included in the spectrometer. 
@@
 the beams get reflected and contain information about the structure\cite{Kaliva2020}.
-Each crystalline material has a discreet atomic structure, which upon irradiation with 
+Each crystalline material has a discreet atomic structure which upon irradiation with 
 X-rays causes constructive and destructive interference according to Bragg's law and generates unique diffraction patterns. 

### 2024-08-11 doc/Thesis/chapter/021-theory-calculations.tex
nearly finish with todos from todo.md

@@
 But this does not mean that computers are more intelligent than humans or \linebreak[4] sentient\cite{searle1980,searle1999married} even though some claim\cite{tiku2022google} and it certainly does not mean that research is over.
-AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
+\Gls{ai} is still a young field, which is strongly growing and is gaining ubiquitous status. 
 It is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
@@
 %\subsection{EMMA}
-\subsection{Evolutionary Model-based Multiresponse Approach}
+\subsection{Evolutionary Model-Based Multiresponse Approach}
 \Gls{emma} is an implementation of \gls{pso} in the \texttt{R} programming language. 
@@
 A Latin hypercube \gls{doe} can be also created such that data points distribute more uniformly over the search space. 
-Latin hypercube \gls{doe}s are mainly used in computer simulations which are purely deterministic and therefore are very precise.
+Latin hypercube \gls{doe}s are mainly used in computer simulations, which are purely deterministic and therefore are very precise.
 %
@@
 Validation is an important part of data analysis as it allows to estimate model errors. 
-Often used methods are analysis of residual error, cross validation and leave-one-out validation\cite{kartam1997artificial}.
+Often used methods are analysis of residual error, cross-validation and leave-one-out validation\cite{kartam1997artificial}.
 \td{to do read kartam}
 statistical methods to bewerten a model are: 
-cross validation, leave-one-out validation ( special case of cross validation), correlation coefficient for linear fits, mean square error, mean absolute erro
+cross-validation, leave-one-out validation (special case of cross-validation), correlation coefficient for linear fits, mean square error, mean absolute erro
 \td{cite from Hawkins 2004\cite{hawkins2004overfitting}}

### 2024-08-11 doc/Thesis/chapter/023-linreg-krr-svm.tex
start doing todo.md
nearly finish with todos from todo.md

@@
 The parameters $\mathbf{k} \in \mathbb{R}^d$ and $c \in \mathbb{R}$ are chosen by minimizing an objective function (loss function in \gls{ml} jargon).
-A typical function to minimize are the $L_1$ and $L_2$ error, i.e. \gls{mae} and \gls{mse}, respectively.
+A typical function to minimize are the $L_1$ and $L_2$ error, i.e.\ \gls{mae} and \gls{mse}, respectively.
 \begin{align}
@@
 
-\textbf{Ridge Regression} is like linear regression with an extra term which penalizes steep regression functions.
+\textbf{Ridge regression} is like linear regression with an extra term, which penalizes steep regression functions.
 The extra term reduces overfitting and is scaled by a correction parameter~$\alpha$. 
@@
 a plane in three dimensions) can fit data in regression problems or separate the data in classification problems without actually doing the transformation for every data point, which lowers computational costs.
-A kernel is some kind of similarity measure 
-which fulfills the requirements of non-negativity, symmetry and linearity\cite{rupp2015machine}.
+A kernel is some kind of similarity measure, which fulfills the requirements of non-negativity, symmetry and linearity\cite{rupp2015machine}.
 %\enlargethispage{\baselineskip}

### 2024-08-11 doc/Thesis/chapter/03-experimental.tex
nearly finish with todos from todo.md

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Precursor Solutions}
+\section{Production of Precursor Solutions}
 \label{sec:exp-sol}
@@
 %Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
-Unfortunately, this solution failed to produce homogeneous layers, but instead only resulted in sparse patches of deposits on the substrate.
+Unfortunately, this solution failed to produce homogeneous coating layers, but instead only resulted in sparse patches of deposits on the substrate.
 Thus, an alternative solution was found.
@@
 but with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
-with the aim of producing thicker layers.
+with the aim of producing thicker coating layers.
 %\td{p34}
@@
 \gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
-the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
+the heat treatment between coating layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
 {\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
@@
 This allowed material to only be deposited on the area between the tape.
-After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
+After the coating layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
 %\td{(at which T?)}.
-Lower \gls{db} velocities resulted in less homogeneous layers.
+Lower \gls{db} velocities resulted in less homogeneous coating layers.
 Thus, the \gls{db} speed was not altered in the manual \gls{db} process. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Characterization of \ch{ZrO2} layers}
+\section{Characterization of \ch{ZrO2} Layers}
 All characterization procedures were executed at room temperature.
@@
 The measured I-V curves therefore represent the vertical resistance of the deposited layer. 
-This resistance will be predominantly influence by the presence of shunts (hotspots or short-cuts between the top and bottom contact), appearing due to the inhomogeneous thickness, and pinholes through the ZrO2 layer.
+This resistance will be predominantly influence by the presence of shunts (hotspots or short-cuts between the top and bottom contact), appearing due to the inhomogeneous thickness, and pinholes through the \gls{zro} layer.
 
@@
 \end{equation}
-Another measure is the density of shorted elements $\rho$ (pinhole density), calculated in following way:
+Another measure is the density of shorted elements $\rho$ (pinhole ratio), calculated in following way:
 \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Pre-optimization of Coating Procedure}
+\section{Pre-Optimization of Coating Procedure}
 \label{sec:exp-preopt}

### 2024-08-11 doc/Thesis/chapter/04-computational-details.tex
nearly finish with todos from todo.md

@@
-\section{Evolutionary Model-based Multiresponse Approach (EMMA)}
+\section{Evolutionary Model-Based Multiresponse Approach (EMMA)}
 \label{sec:ss}
@@
 The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $n_L$ and $v_{cal}$, 
-(i.e.\ conductivity, pinhole density, number of coated layers and heating rate)
+(i.e.\ conductivity, pinhole ratio, number of coated layers and heating rate)
 where $\gamma$, $\rho$ and $n_L$ are to be minimized and $v_{cal}$ to be maximized.
@@
 % and the responses conductivity $\gamma$ (see eq.
-\ref{eq:gamma}), pinhole density $\rho_s$ (see eq.
+\ref{eq:gamma}), pinhole ratio $\rho_s$ (see eq.
 \ref{eq:rho}), $n_L$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program.
@@
 %the experiments are again \td{executed, measured and evaluated. (unclear!)}
-Each time step thus includes experiment identification, solution preparation, coating deposition and layer analysis.
+Each time step thus includes experiment identification, solution preparation, coating deposition and coating layer analysis.
 
@@
 
-\section{Fitting via Machine Learning}
+\section{Fitting Data via Machine Learning}
 %\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\

### 2024-08-11 doc/Thesis/chapter/050-results-material.tex
nearly finish with todos from todo.md

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Material Properties of the Produced Layers}
+\section{Material Properties of Produced Layers}
 \label{sec:res-mat}
@@
 % ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
-Even after the consecutive application of two layers, 
+Even after the consecutive application of two coating layers, 
 there was no significant improvement and the \gls{sem} images (see figure~\ref{fig:sem-old}) 
@@
 		SEM images of \gls{zro}:
-		(a) \gls{zro} produces by 2 layers aqueous solution on \gls{fto}
+		(a) \gls{zro} produced by 2 layers aqueous solution on \gls{fto}
 		(b) 10 layers of \gls{zro} on steel substrate
-		(c) cross section of crack of 5 layers of \gls{zro} on \gls{fto}
+		(c) cross-section of crack of 5 layers of \gls{zro} on \gls{fto}
 		(d) side view of scratched \gls{zro} on steel substrate
@@
 %
-Figure~\ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
+Figure~\ref{fig:sem-ph} shows a top view of 10 coating layers produced from  the buthanolic solution on top of a steel substrate. 
 %%%% PIN HOLES
-The large irregularity on the bottom left could depict a pin hole, a hole in the layer that reaches to the substrate. 
+The large irregularity on the bottom left could depict a pinhole, a hole in the coating layer that reaches to the substrate. 
 These irregularities are rather the exception. 
-Alternatively, the small, hardly visible cracks spread across the surface could depict such pin holes. 
-% These - I think - are rather only one layer deep irregularities since they are so prevalent and hardly any pin holes were electrically observed on similar samples. \todo{where is the evidence?}
+Alternatively, the small, hardly visible cracks spread across the surface could depict such pinholes. 
+% These - I think - are rather only one layer deep irregularities since they are so prevalent and hardly any pinholes were electrically observed on similar samples. \todo{where is the evidence?}
 
@@
 On the lower edge of \gls{fto} a circa \nm{100} thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe) can be observed.
-Measuring the cross section on steel was not as straight forward. 
+Measuring the cross-section on steel was not as straight forward. 
 %because the ductility of steel prevents fractures of the substrate. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{X-ray Diffractogram of \ch{ZrO2}}
+\subsection{X-Ray Diffractogram of \ch{ZrO2}}
 %\todo{of what?}
@@
 %differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
-The more layers, the more of the light is absorbed (at 600-\nm{1100}) by the \gls{zro} layers. 
+The more coating layers, the more of the light is absorbed (at 600-\nm{1100}) by the \gls{zro} layers. 
 %The trend is not monotonic due to inhomogenities in the sample???b
-The thicker the layer is, the more wavy the graph, which can be attributed to interference\cite{Dumin1967}.
+The thicker the layer is, the more turning points can be identified on the graph, which can be attributed to interference\cite{Dumin1967}.
 This trend can also be observed in figure~\ref{fig:ir-gr}.
@@
 %The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
-Thicker layers reflect more light between approximately \nm{800} and \nm{1000}. 
+Thicker coating layers reflect more light between approximately \nm{800} and \nm{1000}. 
 Again, this effect is most likely not observed across the whole spectrum because of interferences. 
@@
 		(a)-(c) I-V curves with log transformed current; 
-		(d)-(f) frequency histograms of the conductance with pin hole threshold marked as vertical line; 
+		(d)-(f) frequency histograms of the conductance with pinhole threshold marked as vertical line; 
 		(g)-(i) individual I-V measurements
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pre-optimization of Coating Procedure}
+\subsection{Pre-Optimization of Coating Procedure}
 %\todo{of what?}

### 2024-08-11 doc/Thesis/chapter/051-results-emma.tex
nearly finish with todos from todo.md

@@
 In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
-conductivity $\gamma$ and pin hole density $\rho$ (see section \ref{sec:eval}), of each particle at each generation.
+conductivity $\gamma$ and pinhole ratio $\rho$ (see section \ref{sec:eval}), of each particle at each generation.
 The the solid circles at generation number 0 indicate particles which were not included to be propagated. 
@@
 		(a)~calculated conductivity measures~$\gamma$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation.
-		(b)~calculated pin hole density~$\rho$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation.
+		(b)~calculated pinhole ratio~$\rho$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation.
 		(c)~calculated conductivity measures~$\gamma$ against calcination temperature $T_{cal}$
-		(d)~calculated pin hole density~$\rho$ against calcination temperature $T_{cal}$
+		(d)~calculated pinhole ratio~$\rho$ against calcination temperature $T_{cal}$
 	change colors }
@@
 %$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
-The expression $h(n_L-6)$ translates into layer count only has an influence if larger than 6 
-and $h(6-n_L)$ into layer count influential only if under 6.
+The expression $h(n_L-6)$ translates into number of coating layers only has an influence if larger than 6 
+and $h(6-n_L)$ into number of coating layers is influential only if under 6.
 %
@@
 %, but the positive influence of the layer count $n_L$ is counter intuitive
-%as one would expect more layers to be more insulating and thus result in lower conductivity and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
+%as one would expect more layers to be more insulating and thus result in lower conductivity and a lower probability of holes going all the way trough the \gls{zro} layers. %pinhole ratio. 
 The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) 
@@
 It is astonishing that the knot of the hinge function for equations (\ref{eq:emma-phd3})--(\ref{eq:emma-vcal3}) was chosen so low; 
-basically only including the influence of the lowest layer count $n_L=4$.
-Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}), that the lowest layer count produces worse samples which is intuitive, but more than 6 layers do not improve the insulation. 
+basically only including the influence of the lowest number of coating layers $n_L=4$.
+Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}), that the lowest number of coating layer produces worse samples which is intuitive, but more than 6 layers do not improve the insulation.
 Encouragingly, the calcination heating rate $v_{cal}$ (see equation (\ref{eq:emma-vcal3})) has been predicted perfectly within numerical precision.
@@
 It was expected that 
-calcination temperatures under \oc{400} do not suffice to produce compact layers (corresponding to $+h(400-T_{cal})$)
+calcination temperatures under \oc{400} do not suffice to produce compact coating layers (corresponding to $+h(400-T_{cal})$)
 and 
@@
 The second flaw is that there are obviously better methods to assess the quality of a model than to make it more complex. 
-%Good alternatives would have been leave-one-out or cross validation.
-Validation methods for sparse data include re-sampling via leave-one-out or $k$-fold cross validation\cite{kartam1997artificial}.
+%Good alternatives would have been leave-one-out or cross-validation.
+Validation methods for sparse data include re-sampling via leave-one-out or $k$-fold cross-validation\cite{kartam1997artificial}.
 

### 2024-08-11 doc/Thesis/chapter/052-post-emma.tex
nearly finish with todos from todo.md

@@
 \subsection{Linear Regression} 
-%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influenced by the Zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $n_L$, but their coefficients are the smallest in absolute values.
+%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influenced by the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $n_L$, but their coefficients are the smallest in absolute values.
 
@@
 While $T_{cal}$ is the second largest influence on $\hat\rho$ as well, it is noteworthy that $n_L$ contributes the least to $\hat\gamma$. 
-That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
-Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artifact of the noise rather than a process property. 
+That means that according to the linear regression, the number of coating layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects.
+Interestingly, the number of coating layers has the least amount of influence on the number probability of defects, which seems to be an artifact of the noise rather than a process property. 
 %Furthermore the influence on $\hat\rho$ is dominated by $n_L$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
@@
 % R2
-The $R^2$ values were calculated for each of the models using cross validation. 
+The $R^2$ values were calculated for each of the models using cross-validation. 
 Resulting $R^2$ are all below zero (see table~\ref{tab:grid-search}). 

### 2024-08-11 doc/Thesis/chapter/053-discussion.tex
nearly finish with todos from todo.md

@@
-\section{Hindsight is easier than foresight}
+\section{Hindsight Is Easier than Foresight}
 \label{sec:res-discussion}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Research, exploration and design phase}
+\subsection{Research, Exploration and Design Phase}
 \label{sec:phase1}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Narrowing, pre-optimization and constraint phase}
+\subsection{Narrowing, Pre-Optimization and Constraint Phase}
 \label{sec:phase2}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Optimization, modeling and data generation phase}
+\subsection{Optimization, Modeling and Data Generation Phase}
 \label{sec:phase3}
@@
 \iffalse
-\subsection{Evaluation, interpretation and outlook phase}
+\subsection{Evaluation, Interpretation And Outlook Phase}
 \label{sec:phase4}
@@
     \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
-    \item why $\gamma ~ n_L$? (minimum for layer count?) according which eq? emma? 
+    \item why $\gamma ~ n_L$? (minimum for number of coating layers?) according which eq? emma? 
     \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error?

### 2024-08-11 doc/Thesis/chapter/06-outlook.tex
start doing todo.md
nearly finish with todos from todo.md

@@
 A correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
-Furthermore, the layer count has been verified as an important factor. 
+Furthermore, the number of coating layers has been verified as an important factor. 
 %was kann noch herausgefundne werden und wie? 
@@
 The sol-gel process produces am homogeneous transparent crystalline zirconia oxide layer. 
-homogeneity can be mainly controlled via blade velocity and temperature and layers can be stacked.
+Homogeneity can be mainly controlled via blade speed and temperature and layers can be stacked.
 

### 2024-08-12 doc/Thesis/chapter/020-theory-materials.tex
leybold and spectrometer info added

@@
 
-\todo{what were the used settings: leybold etc.}
+%\todo{what were the used settings: leybold etc.}
+%\todo{40W, t=700s, p=0.002 mbar, gas inlet= 6 sccm (Ar), no heating or cooling
+%sccm = Standard cubic centimetres per minute}
+The settings on the Leybold sputtering system were as follows: 40 W for 700 seconds at 0.002 mbar and a argon gas inlet of 6 sccm (standard cubic centimeters per minute).
+% with a pressure of 0.002 mbar.
 %Prior to \gls{iv} measurements the samples were sputtered with aluminium through a mask to produce a multitude of equidistant contacts with a Leybold UNIVEX450C Sputter System.
@@
 %differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
-\td{specifications of instruments}
+%\td{specifications of instruments}
+Reflectance and transmittance were measured at \ang{0} and \ang{20} incident angle, respectively, with a Bruker Vertex 70.
 

### 2024-10-11 doc/Thesis/chapter/000-abstract.tex
add german abstract

Passivated steel can act as fit substrate for thin-film photovoltaics.
A thin zirconium oxide layer was applied via blade coating onto a steel foil substrate with the goal of getting a homogeneous and insulating layer.
Layers were qualitatively characterized with SEM and XRD and quantitatively characterized via current-voltage curves.
The process variables (solution concentration, number of coating layers, coating speed, coating temperature, calcination speed and calcination temperature) were optimized by particle swarm optimization (PSO) algorithm in combination with multivariate adaptive regression splines (MARS).
A correlation between the calcination temperature and the electrical properties of the ceramic layers has been revealed. 
The MARS model performed well compared to 
linear regression, kernel ridge regression and support vector regression.

\vspace{2em}

\noindent Passivierter Stahl kann als geeignetes Substrat für Dünnschicht-Photovoltaik fungieren. 
Eine dünne Schicht aus Zirkoniumoxid wurde mittels Rakelbeschichtung auf ein Stahlfolien-Substrat aufgebracht, mit dem Ziel, eine homogene und isolierende Schicht zu erhalten. 
Die Schichten wurden qualitativ mit SEM und XRD und quantitativ über Strom-Spannungs-Kurven charakterisiert. 
Die Prozessvariablen (Precursorlösungskonzentration, Anzahl der Schichten, Beschichtungsgeschwindigkeit, Beschichtungstemperatur, Kalzinationsgeschwindigkeit und Kalzinationstemperatur) wurden mithilfe des Partikelschwarmoptimierungs (PSO)-Algorithmus in Kombination mit multivariaten adaptiven Regression Splines (MARS) optimiert. Eine Korrelation zwischen der Kalzinationstemperatur und den elektrischen Eigenschaften der keramischen Schichten wurde festgestellt. Das MARS-Modell schnitt im Vergleich zu linearer Regression, Kernel-Ridge-Regression und Support Vector Regression gut ab.

### 2024-10-24 doc/presentations/defensio/defense.tex
first draft of defense

%01. title slide 
	%- aufhänger
%02. agenda
%03. background info
%04. hypothesis 
%05. manual methods
%06. computational pipeline 
%07. results measuring 
%08. results EMMA 
%09. comparison with other statistics 
%10. summary 
%11. conclusion 
%12. end

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  Die vorliegenden LaTeX-Folien stehen Mitarbeiter*innen und Studierenden der Universität Wien
%%  zur Verfügung und sind ausschließlich zur Verwendung in Forschung und Lehre der Universität  
%%  Wien vorgesehen. Das Copyright der LaTeX-Vorlagen liegt bei der Universität Wien.
%%
%%  These LaTeX slides are available to employees and students of the University of Vienna 
%%  and are intended exclusively for use in research and teaching at the University of Vienna. 
%%  The copyright of the LaTeX templates is held by the University of Vienna.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t]{beamer}  %% Choose aspectratio=43 or aspectratio=169

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ====== Define Style ======= %% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% ======== required inputs ========

	%% ====== title page ======
	\title{Particle Swarm Optimization of Chemical Passivation of Steel Substrate with Zirconium Oxide Layers} %% Presentation Title
	\newcommand{\titleBackground}{2}    						%% Background graphic: 0 = no; 1 = yes; 2 = yes with more text space
	\newcommand{\gPath}{figures/}									%% set graphics path
	\newcommand{\graphicsTitleBackground}{title}    %% Filename of background graphic

%% ======== optional inputs ========

	%% ====== title page ======
	\subtitle{PSO for Steel Passivation with ZrO}  %% (optional) Subtitle, comment out to avoid include
	\newcommand{\authorText}{Johann Dorn}				%% (optional) Author
	\newcommand{\logoTitleFooterR}{grey}  %% (optional) additional logo in title page footer, most right
	\newcommand{\logoTitleFooterM}{grey}  %% (optional) additional logo in title page footer, more right (if horizontal spacing not adequate, save multiple logos in one file, use \logoTitleFooterR)
	\newcommand{\logoTitleFooterL}{grey}  %% (optional) additional logo in title page footer, right (if horizontal spacing not adequate, save multiple logos in one file, use \logoTitleFooterR)

	%% ====== footer ======
	\newcommand{\textFooter}{\subtitle - \authorText} %% (optional) Text for footline, e.g. title, comment out lines to avoid include, max. 1 line
	\newcommand{\slideNumberLabelFooter}{Slide}    	%% Page/Slide/Folie/Seite
%	\date{November 2017}              									%% Date, comment out to get current date

	%% ====== header ====== 
	%\newcommand{\sectionHeader}{Section (optional)} %% (optional) Text before section number, e.g. Section or Kapitel; comment out to avoid headline

	%% ====== TOC ====== 
	%\newcommand{\includeTocAtBeginSection}{}   		 %% (optional) Table of contents at begin of every section, comment out to avoid include

%% ======== load beamer style ========
	\usepackage{beamerthemeuniwien2017}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ====== Further Preamble ======= %% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% ====== settings (optional) ======
	\usenavigationsymbolstemplate{}     %% (optional) Comment out to include navigation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ====== Begin Document ======= %% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%% ====== Title Page ======

\maketitle

%% ====== Outline at beginning of document ======

%\begin{frame}{Outline (optional)}
%	\tableofcontents							%% (optional) Table of contents, comment out lines to avoid include
%\end{frame}

%% ====== Slides ======

\begin{graphicsFrame}{Layout ``Body with figure, small right''}{short}{0.63}{left}{graphic_rs}{\textcopyright~Universität Wien/derknopfdruecker.com}

		Random formula
		\[
			(0,1)\ni t\mapsto\frac{\partial}{\partial t} g(t,\omega)=\int_{( 0,1-t]}\frac{G(dr,\omega)}{1-r}
		\]
		Another random formula
		\begin{equation}\label{eq1}
			\int_{( G(0+,\cdot),1)}\frac{ f_{\mathcal{G},G^{\leftarrow}(t,\cdot),X}}{1-G^{\leftarrow}(t,\cdot)}\,dt
			= f_{\mathcal{G},G,X}\quad \textrm{a.s.}
		\end{equation}
		And another, even more random formula
		\[
			\mathbb{P}(X\leq Z-\varepsilon)\leq
			\mathbb{P}(X\leq q_{\mathcal{G},\delta}(X)-\varepsilon )< \delta
		\]

\end{graphicsFrame}

\begin{textFrame}{Layout ``Titel und Inhalt'' = Standardlayout Überschriften}{1}{Referenz, Quellen- oder Copyright-Angabe bei Bedarf einfügen}

	\begin{itemize}
		\item Fließtext 22 pt, Mustertext: Weit hinten, hinter den Wortbergen, fern der Länder Vokalien und Konsonantien leben die Blindtexte.
		\item Abgeschieden wohnen sie in Buchstabhausen an der Küste des Semantik, eines großen Sprachozeans. Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
		\item Es ist ein paradiesmatisches Land, in dem einem gebratene Satzteile in den Mund fliegen. Nicht einmal von der allmächtigen Interpunktion werden die Blindtexte beherrscht – ein geradezu unorthographisches Leben.

	\end{itemize}
\end{textFrame}

\begin{textFrame}{Layout ``Titel und Inhalt wenig Text''}{0.7}{Referenz, Quellen- oder Copyright-Angabe bei Bedarf einfügen}

	\begin{itemize}
		\item Mustertext: Weit hinten, hinter den Wortbergen, fern der Länder Vokalien und Konsonantien leben die Blindtexte.
		\item Abgeschieden wohnen sie in Buchstabhausen an der Küste des Semantik, eines großen Sprachozeans. Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
		\item Nicht einmal von der allmächtigen Interpunktion werden die Blindtexte beherrscht – ein geradezu unorthographisches Leben.
	\end{itemize}
\end{textFrame}

%% ====== Section  ======

\section{Layout ``Abschnittsüberschrift''}

\begin{sectionFrame}{section.jpg}{mit Untertitel}
\end{sectionFrame}

\section{Layout ``Abschnittsüberschrift ohne Bild''~-- Titel kann auch mehrzeilig sein}

\begin{sectionFrame}{}{mit Untertitel}
\end{sectionFrame}

\begin{textFrame2}{Layout ``Zwei Inhalte''}{}{
		\begin{itemize}
			\item In die Inhaltsplatzhalter können unterschiedliche Elemente eingefügt werden.
			\item Mustertext: Abgeschieden wohnen sie in Buchstabhausen an der Küste des Semantik, eines großen Sprachozeans. 
					Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
		\end{itemize}
}{Referenz, Quellen- oder Copyright-Angabe}{}{\includegraphics[width=\linewidth]{\gPath diagram.jpg}}%
{Referenz, Quellen- oder Copyright-Angabe}
\end{textFrame2}

\begin{textFrame2}{Layout ``Vergleich''}{Vorteile des XYZ-Modells in Zusammenhang mit dem Projekt}%
{
		\begin{itemize}
			\item Weit hinten, hinter den Wortbergen, fern der Länder Vokalien und Konsonantien leben die Blindtexte.
			\item Abgeschieden wohnen sie in Buchstabhausen an der Küste des Semantik, eines großen Sprachozeans. 
		\end{itemize}
}{}{Nachteile des XYZ-Modells in Zusammenhang mit dem Projekt}{
		\begin{itemize}
			\item Abgeschieden wohnen sie in Buchstabhausen an der Küste des Semantik, eines großen Sprachozeans.
			\item Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien. 
		\end{itemize}
}{}
\end{textFrame2}

\begin{graphicsFrame}{Layout ``Inhalt mit Bild \\ klein rechts''}{short}{0.6}{left}{graphic_rs}{\textcopyright~Universität Wien/derknopfdruecker.com}

		\begin{itemize}
			\item Abgeschieden wohnen sie in Buchstab-hausen an der Küste des Semantik, eines großen Sprachozeans.
			\item Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
			\item Es ist ein paradiesmatisches Land, in dem einem gebratene Satzteile in den Mund fliegen. Abgeschieden wohnen sie in Buchstabhausen an der Küste des Semantik, eines großen Sprachozeans. 
		\end{itemize}

\end{graphicsFrame}

\begin{graphicsFrame}{Layout ``Inhalt mit Bild klein \\ links''}{short}{0.6}{right}{graphic_ls}{\textcopyright~Universität Wien/derknopfdruecker.com}

		\begin{itemize}
			\item Abgeschieden wohnen sie in Buchstab-hausen an der Küste des Semantik, eines großen Sprachozeans.
			\item Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
			\item Es ist ein paradiesmatisches Land, in dem einem gebratene Satzteile in den Mund fliegen. Abgeschieden wohnen sie in Buchstabhausen an der Küste des Semantik, eines großen Sprachozeans.
		\end{itemize}

\end{graphicsFrame}

\begin{graphicsFrame}{Layout ``Inhalt mit Bild größer rechts''}{}{0.37}{left}{graphic_rm}{\textcopyright~Universität Wien/Barbara Mair}

		\begin{itemize}
			\item Abgeschieden wohnen sie in Buchstab-hausen an der Küste des Semantik, eines großen Sprachozeans.
			\item Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
		\end{itemize}

\end{graphicsFrame}

\begin{graphicsFrame}{Layout ``Inhalt mit Bild größer links''}{}{0.37}{right}{graphic_lm}{\textcopyright~Universität Wien/Barbara Mair}

		\begin{itemize}
			\item Abgeschieden wohnen sie in Buchstab-hausen an der Küste des Semantik, eines großen Sprachozeans.
			\item Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
		\end{itemize}

\end{graphicsFrame}

\begin{graphicsFrame}{Layout ``Bild groß mit Titel''}{}{0.1}{}{graphic_xl}{\textcopyright~Universität Wien/Barbara Mair}

\end{graphicsFrame}

\begin{graphicsFrame}{}{}{0.24}{right}{graphic_ll}{\textcopyright~Universität Wien/derknopfdruecker.com}

		\begin{itemize}
			\item Layout „Bild groß mit Text“ 
			\item Abgeschieden woh-nen sie in Buchstab-hausen an der Küste des Semantik, eines großen Sprachozeans.
			\item Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
			\item Es ist ein paradiesma-tisches Land, in dem einem gebratene Satzteile in den Mund fliegen.
		\end{itemize}

\end{graphicsFrame}

\begin{graphicsFrame}{Layout ``Bild abfallend mit Titel''}{}{-1}{}{graphic_xxl}{\textcopyright~Universität Wien/derknopfdruecker.com}

\end{graphicsFrame}

\begin{graphicsFrame2}{}{0.19}{graphic_2c_lm}{\textcopyright~Universität Wien/derknopfdruecker.com}{graphic_2c_rm}{\textcopyright~Universität Wien/Barbara Mair}

		\begin{itemize}
			\item Layout „Twei Bilder mit Text rechts“ 
			\item Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
			\item Es ist ein para-diesmatisches Land, in dem einem gebratene Satzteile in den Mund fliegen.
		\end{itemize}

\end{graphicsFrame2}

\begin{graphicsFrame2}{Layout ``Titel, zwei Bilder mit Text rechts''}{0.17}{graphic_2c_ls}{\textcopyright~Universität Wien/Barbara Mair}{graphic_2c_rs}{\textcopyright~Universität Wien/Barbara Mair}

	\textbf{Ein kleines Bächlein namens Duden} fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
	\smallskip

	Es ist ein paradiesmatisches Land, in dem einem gebratene Satzteile in den Mund fliegen.

\end{graphicsFrame2}

\begin{graphicsFrame2}{Layout ``Titel, zwei Bilder''}{0}{graphic_2c_ll}{\textcopyright~Universität Wien/Barbara Mair}{graphic_2c_rl}{\textcopyright~Universität Wien/derknopfdruecker.com}

\end{graphicsFrame2}

%% ====== End Document ====== %%
\end{document}

### 2024-10-28 doc/presentations/defensio/defense.tex
first ugly defensio draft

@@
-%01. title slide 
-	%- aufhänger
-%02. agenda
-%03. background info
-%04. hypothesis 
-%05. manual methods
-%06. computational pipeline 
-%07. results measuring 
-%08. results EMMA 
-%09. comparison with other statistics 
-%10. summary 
-%11. conclusion 
-%12. end
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t, draft]{beamer}  %% Choose aspectratio=43 or aspectratio=169
 \documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t]{beamer}  %% Choose aspectratio=43 or aspectratio=169
@@
 	%% ====== title page ======
-	\title{Particle Swarm Optimization of Chemical Passivation of Steel Substrate with Zirconium Oxide Layers} %% Presentation Title
+	\title{Particle Swarm Optimization for Chemical Passivation of Steel Substrate with Zirconium Oxide Layers} %% Presentation Title
 	\newcommand{\titleBackground}{2}    						%% Background graphic: 0 = no; 1 = yes; 2 = yes with more text space
@@
 	\newcommand{\authorText}{Johann Dorn}				%% (optional) Author
-	\newcommand{\logoTitleFooterR}{grey}  %% (optional) additional logo in title page footer, most right
-	\newcommand{\logoTitleFooterM}{grey}  %% (optional) additional logo in title page footer, more right (if horizontal spacing not adequate, save multiple logos in one file, use \logoTitleFooterR)
-	\newcommand{\logoTitleFooterL}{grey}  %% (optional) additional logo in title page footer, right (if horizontal spacing not adequate, save multiple logos in one file, use \logoTitleFooterR)
+%	\newcommand{\logoTitleFooterR}{grey}  %% (optional) additional logo in title page footer, most right
+%	\newcommand{\logoTitleFooterM}{grey}  %% (optional) additional logo in title page footer, more right (if horizontal spacing not adequate, save multiple logos in one file, use \logoTitleFooterR)
+%	\newcommand{\logoTitleFooterL}{grey}  %% (optional) additional logo in title page footer, right (if horizontal spacing not adequate, save multiple logos in one file, use \logoTitleFooterR)
 
@@
 	\newcommand{\slideNumberLabelFooter}{Slide}    	%% Page/Slide/Folie/Seite
-%	\date{November 2017}              									%% Date, comment out to get current date
+	\date{2024-10-30} %% Date, comment out to get current date
 
@@
 	\usenavigationsymbolstemplate{}     %% (optional) Comment out to include navigation
+
+\usepackage{siunitx}
+\usepackage{chemformula}
 
@@
 %% ====== Slides ======
+%TODO: - read aqua/good recipe/mars paper
+%01. title slide 
+	% - aufhänger
+	% - AI and PV
+	% - Lab or Computer 
+%02. agenda
+	% - more like process  from beginning to finish
+%03. background info
+	% - PV CIGS substrate % https://de.wikipedia.org/wiki/Chalkopyrit
+	% https://en.wikipedia.org/wiki/Copper_indium_gallium_selenide_solar_cell
+\begin{textFrame}
+	{Copper indium gallium selenide solar cell}
+	{1}{}
+%	\begin{itemize}
+%		\item lorem
+%		\item ipsum
+%		\item \dots
+%	\end{itemize}
+\begin{table}[tbh]
+	\small
+    \center
+%	\iffalse
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{cccccc}
+			\hline
+			\hline
+			Material&   Type&    Band Gap [eV]&    $\lambda$ [nm]&    Abs. coef. $\alpha$ [cm$^{-1}$]    &Penetration Depth [$\mu$m]\\
+			\hline
+			c-Si&   indirect&   1.12&   600&    \num{4000}&    2.5\\
+			c-Si&   indirect&   1.12&   1000&    \num{64}&    150\\
+			c-Si&   indirect&   1.12&   1100&    \num{3.5}&    290\\
+			a-Si&   direct&      1.7&    600&    \num{40000}&  0.25\\
+			CdTe&   direct&      1.45&    600&    \num{37000}&  0.3\\
+			GaAs&   direct&      1.42&    600&    \num{40000}&  0.2\\
+			\hline
+			\hline
+		\end{tabular}
+	}
+    \caption{Photonic properties of several established PV materials (\cite{mertens2020photovoltaik})}
+	\label{tab:cigs:alpha}
+%	\fi
+%
+	\resizebox{.45\textwidth}{!}{
+    \begin{tabular}{cccc}
+        \hline\hline
+		Empirical Formula&   Band Gap [\si{eV}{}]\\
+        \hline
+		\ch{CuInSe2}&  1.04\\
+		\ch{CuInS2}&  1.5\\
+		\ch{CuGaSe2}&  1.7\\
+		\ch{CuGaS2}&  1.55\\
+        \hline\hline
+    \end{tabular}
+}
+    \caption{Band gaps of different chalcopyrites (K. Mertens 2015 "Photovoltaik")}
+\end{table}
+\end{textFrame}
 
+\begin{graphicsFrame}{Copper Indium Gallium Sulfide}{}{0.37}{left}{cigs}{Rau, Schock (2013) "Solar Cells"}
+		\begin{itemize}
+			\item Abgeschieden wohnen sie in Buchstab-hausen an der Küste des Semantik, eines großen Sprachozeans.
+			\item Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
+		\end{itemize}
+\end{graphicsFrame}
+
+\begin{graphicsFrame}{CIGS modules}{}{0.1}{}{cigs_mod}{}
+
+\end{graphicsFrame}
+%04. hypothesis 
+%05. manual methods
+	% - precursor solution preparation 
+		% Anwar 2017 https://iopscience.iop.org/article/10.1088/1757-899X/257/1/012087
+		% Hu 2016 https://www.sciencedirect.com/science/article/abs/pii/S0272884216312548
+\begin{frame}{test}
+
+\begin{table}[h]
+	\center
+	\caption{Composition of different buthanolic solutions}
+	\label{tab:rec2}
+	\begin{tabular}{rlllll}
+		\hline
+		recipe	&1F		&2F		&3F		&4F		&5F		\\
+		\hline
+		\ch{BuOH} [ml]	&4.95	&4.9	&4.85	&4.8	&4.75	\\
+		\ch{ZrPro} [ml]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
+		\ch{AcAc} [ml]	&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
+		\ch{IPO}/\ch{AcOH} [ml]	&2		&2		&2		&2		&2		\\
+		\hline
+	\end{tabular}
+\end{table}
+\end{frame}
+
+	% - doctor blading = tape castig 
+	% - calcination 
+\begin{frame}{Tape casting and Calcination}
+	\begin{itemize}
+		\item doctor blading construction 
+		\item calcination infos (max temperatur, heating rate)
+	\end{itemize}
+\end{frame}
+	% - sputtering contacts
+	% - measuring current-voltage characteristics
+\begin{frame}{Sputtering and I-V measurement}
+	\begin{itemize}
+		\item Aluminium Contact through mask
+		\item Silver paste
+	\end{itemize}
+\end{frame}
+%06. computational pipeline 
+	% - PSO + MARS = EMMA
+	% PSO https://doi.org/10.1109/CEC.2010.5586165
+\begin{frame}{EMMA = PSO + MARS}
+	\begin{itemize}
+		\item Particle Swarm Opitimisation 
+	\end{itemize}
+\end{frame}
+%07. results measuring 
+	% - SEM % check which sample 
+\begin{graphicsFrame}{SEM micrographs}{}{0.37}{right}{sem}{}
+		\begin{itemize}
+			\item (a) first recipe on FTO
+			\item (b) 10 layers on steel
+			\item (c) cross section of 5 layers on FTO
+			\item (d) side view of scratched layer on steel
+		\end{itemize}
+\end{graphicsFrame}
+
+	% - I-V % https://en.wikipedia.org/wiki/Current%E2%80%93voltage_characteristic
+\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv1}{}\end{graphicsFrame}
+\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv2}{}\end{graphicsFrame}
+\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv3}{}\end{graphicsFrame}
+	% - EMMA 
+%08. results EMMA 
+\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
+\begin{graphicsFrame}{Leakage Current}{}{0.1}{}{leakage_w}{}\end{graphicsFrame}
+\begin{graphicsFrame}{Leakage Current}{}{-1}{}{leakage}{}\end{graphicsFrame}
+\begin{graphicsFrame}{Leakage Current}{}{0.24}{right}{leakage}{}\end{graphicsFrame}
+\begin{graphicsFrame}{Leakage Current}{}{0.37}{right}{leakage}{}\end{graphicsFrame}
+\begin{graphicsFrame}{EMMA generations}{}{0.1}{}{emma-gen}{}\end{graphicsFrame}
+	% - gen 
+%09. comparison with other statistics 
+	% - comparing with other stats
+	\begin{frame}{Comparison with Statistics}
+\begin{table}[htb]
+	\centering
+%    \caption{Post EMMA vergleich}
+	\resizebox{.95\textwidth}{!}{
+	\begin{tabular}{c cc cc cc cc}
+    \hline\hline
+        $\gamma$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
+    \hline
+        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
+        LR&    13& 250&    24& 747&    34& 1327&   17& 454\\
+%        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
+        KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
+        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
+        \hline
+%    \hline\hline
+	\end{tabular}
+}
+	\vspace{1em}
+    %
+	\resizebox{.95\textwidth}{!}{
+	\begin{tabular}{c cc cc cc cc}
+    \hline\hline
+        $\rho$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
+    \hline
+        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
+        LR&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
+%        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
+        KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
+%        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
+        SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
+    \hline\hline
+	\end{tabular}
+}
+    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
+	\label{tab:post-emma}
+\end{table}
+\end{frame}
+
+%10. summary 
+	% - created ZrO2
+	% - optimized with EMMA
+	% - double checked with stats
+%11. conclusion 
+%12. end
+
+\iffalse
 \begin{graphicsFrame}{Layout ``Body with figure, small right''}{short}{0.63}{left}{graphic_rs}{\textcopyright~Universität Wien/derknopfdruecker.com}
@@
 
+\fi
+
 %% ====== End Document ====== %%

### 2024-10-28 doc/presentations/defensio/defense.tex
first real draft of densio

@@
+%\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t, draft]{beamer}  %% Choose aspectratio=43 or aspectratio=169
+\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t]{beamer}  %% Choose aspectratio=43 or aspectratio=169
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t, draft]{beamer}  %% Choose aspectratio=43 or aspectratio=169
-\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t]{beamer}  %% Choose aspectratio=43 or aspectratio=169
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	%% ====== title page ======
-	\title{Particle Swarm Optimization for Chemical Passivation of Steel Substrate with Zirconium Oxide Layers} %% Presentation Title
+	\title{Particle Swarm Optimization for Chemical Passivation of Steel Substrate with Zirconium Oxide} %% Presentation Title
 	\newcommand{\titleBackground}{2}    						%% Background graphic: 0 = no; 1 = yes; 2 = yes with more text space
@@
 \usepackage{chemformula}
+\usepackage{upgreek}
 
@@
 %02. agenda
+\begin{frame}{Agenda}
+	\vspace{2em}
+	\begin{itemize}
+		\item Motivation: CIGS substrate
+		\item Methods: recipe and sample preparation
+		\item Calculation: PSO and data pipeline
+		\item Results: materials and optimisation
+	\end{itemize}
+\end{frame}
 	% - more like process  from beginning to finish
@@
 	% https://en.wikipedia.org/wiki/Copper_indium_gallium_selenide_solar_cell
-\begin{textFrame}
-	{Copper indium gallium selenide solar cell}
-	{1}{}
+\begin{graphicsFrame}{Copper Indium Gallium Selenide (CIGS)}{}{0.37}{left}{cigs}{U. Rau, H.W. Schock (2013) "Solar Cells"}
+\begin{table}
+	\resizebox{.95\textwidth}{!}{
+    \begin{tabular}{cccc}
+        \hline\hline
+		Empirical Formula&   Band Gap [\SI{}{\electronvolt}]\\
+        \hline
+		\ch{CuInSe2}&  1.04\\
+		\ch{CuGaSe2}&  1.7\\
+		\ch{CuInS2}&  1.5\\
+		\ch{CuGaS2}&  1.55\\
+        \hline\hline
+    \end{tabular}
+}
+    \caption{Band gaps of different chalcopyrites (K. Mertens 2015 "Photovoltaik")}
+\end{table}
+\end{graphicsFrame}
+
+\iffalse
+\begin{textFrame}{Thin Film Solar Cell}{1}{}
 %	\begin{itemize}
@@
     \center
-%	\iffalse
 	\resizebox{\textwidth}{!}{
@@
 			\hline
-			Material&   Type&    Band Gap [eV]&    $\lambda$ [nm]&    Abs. coef. $\alpha$ [cm$^{-1}$]    &Penetration Depth [$\mu$m]\\
+			Material&   Type&    Band Gap [\SI{}{\electronvolt}]&    $\lambda$ [\SI{}{\nano\meter}]&    Abs. coef. $\upalpha$ [\SI{}{\centi\meter^{-1}}]    &Penetration Depth [\SI{}{\micro\meter}]\\
 			\hline
-			c-Si&   indirect&   1.12&   600&    \num{4000}&    2.5\\
-			c-Si&   indirect&   1.12&   1000&    \num{64}&    150\\
-			c-Si&   indirect&   1.12&   1100&    \num{3.5}&    290\\
-			a-Si&   direct&      1.7&    600&    \num{40000}&  0.25\\
-			CdTe&   direct&      1.45&    600&    \num{37000}&  0.3\\
-			GaAs&   direct&      1.42&    600&    \num{40000}&  0.2\\
+			c-Si&   indirect&   1.12&   600&    4000&    2.5\\
+			c-Si&   indirect&   1.12&   1000&    64&    150\\
+			c-Si&   indirect&   1.12&   1100&    3.5&    290\\
+			a-Si&   direct&      1.7&    600&    40000&  0.25\\
+			CdTe&   direct&      1.45&    600&    37000&  0.3\\
+			GaAs&   direct&      1.42&    600&    40000&  0.2\\
 			\hline
@@
 	}
-    \caption{Photonic properties of several established PV materials (\cite{mertens2020photovoltaik})}
+    \caption{Photonic properties of several established PV materials (K. Mertens 2015 "Photovoltaik")}
 	\label{tab:cigs:alpha}
-%	\fi
-%
-	\resizebox{.45\textwidth}{!}{
-    \begin{tabular}{cccc}
-        \hline\hline
-		Empirical Formula&   Band Gap [\si{eV}{}]\\
-        \hline
-		\ch{CuInSe2}&  1.04\\
-		\ch{CuInS2}&  1.5\\
-		\ch{CuGaSe2}&  1.7\\
-		\ch{CuGaS2}&  1.55\\
-        \hline\hline
-    \end{tabular}
-}
-    \caption{Band gaps of different chalcopyrites (K. Mertens 2015 "Photovoltaik")}
 \end{table}
 \end{textFrame}
+\fi
 
-\begin{graphicsFrame}{Copper Indium Gallium Sulfide}{}{0.37}{left}{cigs}{Rau, Schock (2013) "Solar Cells"}
-		\begin{itemize}
-			\item Abgeschieden wohnen sie in Buchstab-hausen an der Küste des Semantik, eines großen Sprachozeans.
-			\item Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
-		\end{itemize}
+\begin{graphicsFrame}{CIGS modules}{}{0.1}{}{cigs_mod}{}
 \end{graphicsFrame}
 
-\begin{graphicsFrame}{CIGS modules}{}{0.1}{}{cigs_mod}{}
-
-\end{graphicsFrame}
 %04. hypothesis 
@@
 		% Hu 2016 https://www.sciencedirect.com/science/article/abs/pii/S0272884216312548
-\begin{frame}{test}
-
+\begin{frame}{Recipes for Precursor Solutions}
+	\begin{figure}
+		\includegraphics[width=.79\textwidth]{figures/huetal.png}
+	\end{figure}
+	\pause
 \begin{table}[h]
 	\center
-	\caption{Composition of different buthanolic solutions}
 	\label{tab:rec2}
@@
 	\end{tabular}
+	%\caption{Composition of different buthanolic solutions}
 \end{table}
@@
 \begin{frame}{Tape casting and Calcination}
-	\begin{itemize}
-		\item doctor blading construction 
-		\item calcination infos (max temperatur, heating rate)
-	\end{itemize}
+	\begin{figure}
+		\center
+		\includegraphics[width=.65\textwidth]{figures/tc.jpg}
+	\end{figure}
 \end{frame}
+%	\begin{itemize}
+%		\item doctor blading construction 
+%		\item calcination infos (max temperatur, heating rate)
+%	\end{itemize}
+%\end{frame}
 	% - sputtering contacts
@@
 \begin{frame}{Sputtering and I-V measurement}
+	\begin{figure}
+		\includegraphics<1>[width=.63\textwidth]{figures/sample1.jpg}
+		\includegraphics<2>[width=.63\textwidth]{figures/sample2.jpg}
+		\includegraphics<3>[width=.63\textwidth]{figures/sample3.jpg}
+	\end{figure}
+\end{frame}
+
+%06. computational pipeline 
+\begin{frame}{Pin Hole Density and Leakage Current}
+	\vspace{2em}
 	\begin{itemize}
-		\item Aluminium Contact through mask
-		\item Silver paste
+		\item Pin Hole Density 
+			\begin{itemize}
+				\item $
+%	\rho = \frac{n_{-}}{(n_{-} + n_{+})}
+	\rho = \sum_i^N \frac{s_i}{N}
+					$
+				\item $
+	s_i = \begin{cases}
+        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
+        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
+	\end{cases}
+					$
+			\end{itemize}
+	\vspace{0.5em}
+		\item Leakage Current 
+			\begin{itemize}
+				\item $
+    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
+	$
+			\end{itemize}
 	\end{itemize}
 \end{frame}
-%06. computational pipeline 
 	% - PSO + MARS = EMMA
 	% PSO https://doi.org/10.1109/CEC.2010.5586165
-\begin{frame}{EMMA = PSO + MARS}
+\begin{graphicsFrame}{Particle Swarm Optimisation}{}{0.37}{right}{swarm}{}
+	\vspace{2em}
 	\begin{itemize}
-		\item Particle Swarm Opitimisation 
+		\item ispired by bird flocks and fish schools %# swarm intelligence
+		\item iterative process % nice bcs sample prep takes long time 
+		\item particles: 
+			\begin{itemize}
+				\item position 
+				\item velocity
 			\end{itemize}
+		\item update model
+		\item R package \texttt{emma} 
+	\end{itemize}
+\end{graphicsFrame}
+
+\begin{frame}{PSO variables}
+\begin{table}[htb]
+	\centering
+	\begin{tabular}{cc cc cc}
+		\hline\hline
+		$c_{zr}$ [\SI{22}{\milli\mol/\liter}]	&$n_L$	&$T_{C}$[\SI{}{\degreeCelsius}]	&$v_{C}$[\SI{}{\milli\meter/\second}]	&$T_{cal}$[\SI{}{\degreeCelsius}]	&$v_{cal}$[\SI{}{\degreeCelsius/\hour}]	\\
+		\hline
+		2				&4		&40					&10				&300				&120	\\
+		3				&6		&50					&12				&400				&360	\\
+		4				&8		&60					&14				&500				&600	\\
+		5				&10		&70					&16				&					&840	\\
+						&12		&80					&18				&					&1080	\\
+						&		&					&20				&					&		\\
+		\hline\hline
+	\end{tabular}
+	\caption{Discrete levels of each input parameter }
+	\label{tab:input}
+\end{table}
 \end{frame}
+
+%	\begin{itemize}
+%		\item Aluminium Contact through mask
+%		\item Silver paste
+%	\end{itemize}
+%\end{frame}
 %07. results measuring 
@@
 %08. results EMMA 
-\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
-\begin{graphicsFrame}{Leakage Current}{}{0.1}{}{leakage_w}{}\end{graphicsFrame}
-\begin{graphicsFrame}{Leakage Current}{}{-1}{}{leakage}{}\end{graphicsFrame}
-\begin{graphicsFrame}{Leakage Current}{}{0.24}{right}{leakage}{}\end{graphicsFrame}
-\begin{graphicsFrame}{Leakage Current}{}{0.37}{right}{leakage}{}\end{graphicsFrame}
-\begin{graphicsFrame}{EMMA generations}{}{0.1}{}{emma-gen}{}\end{graphicsFrame}
+\begin{frame}{Pin Hole Density}\begin{figure}\includegraphics[width=.66\textwidth]{figures/phd.png}\end{figure}\end{frame}
+\begin{frame}{Leakage Current}\begin{figure}\includegraphics[width=.66\textwidth]{figures/leakage.png}\end{figure}\end{frame}
+\begin{frame}{PSO generations}\begin{figure}\includegraphics[width=.96\textwidth]{figures/emma-gen.png}\end{figure}\end{frame}
+%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
+%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
+%\begin{graphicsFrame}{Leakage Current}{}{0.1}{}{leakage_w}{}\end{graphicsFrame}
+%\begin{graphicsFrame}{Leakage Current}{}{-1}{}{leakage}{}\end{graphicsFrame}
+%\begin{graphicsFrame}{Leakage Current}{}{0.24}{right}{leakage}{}\end{graphicsFrame}
+%\begin{graphicsFrame}{Leakage Current}{}{0.37}{right}{leakage}{}\end{graphicsFrame}
+%\begin{graphicsFrame}{EMMA generations}{}{0.1}{}{emma-gen}{}\end{graphicsFrame}
 	% - gen 
@@
 	% - comparing with other stats
+
 \begin{frame}{Comparison with Statistics}
@@
 	\centering
-%    \caption{Post EMMA vergleich}
+%	\resizebox{.95\textwidth}{!}{
+	\begin{tabular}{c cc }
+    \hline\hline
+        $\gamma$&  MAE(e)&   MSE(e)\\
+    \hline
+		PSO&   \textbf{10}& 171\\
+        LR&    13& 250\\
+        KRR &17 &548 \\
+        SVM& 15&  415\\
+    \hline\hline
+	\end{tabular}
+%}
+	\pause
+%	\vspace{1em}
+%	\resizebox{.95\textwidth}{!}{
+	\begin{tabular}{c cc cc cc cc}
+    \hline\hline
+        $\rho$&  MAE(e)&   MSE(e)\\
+    \hline
+		PSO&   \textbf{0.14}&   0.03\\
+        LR&    0.19&   0.06\\
+        KRR &0.25 &0.12 \\
+        SVM &0.23 &0.13 \\
+    \hline\hline
+	\end{tabular}
+%}
+%    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
+	\label{tab:post-emma}
+\end{table}
+\end{frame}
+
+\iffalse
+\begin{frame}{Comparison with Statistics}
+\begin{table}[htb]
+	\centering
 	\resizebox{.95\textwidth}{!}{
@@
         LR&    13& 250&    24& 747&    34& 1327&   17& 454\\
-%        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
         KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
@@
 	\vspace{1em}
-    %
 	\resizebox{.95\textwidth}{!}{
@@
         LR&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
-%        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
         KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
-%        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
         SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
@@
 \end{frame}
+\fi
 
 %10. summary 
+\begin{frame}{Summary}
+	\vspace{2em}
+	\begin{itemize}
+		\item new recipe for dense \ch{ZrO2}
+			\vspace{.5em}
+		\item optimzed method with PSO
+	\end{itemize}
+\end{frame}
 	% - created ZrO2

### 2024-10-29 doc/presentations/defensio/defense.tex
fix formatting
improve formulas for metrics
work in feedback by ditus

@@
 	%% ====== title page ======
-	\title{Particle Swarm Optimization for Chemical Passivation of Steel Substrate with Zirconium Oxide} %% Presentation Title
+	\title{Particle Swarm Optimization for Passivation of Steel Substrate with Zirconium Oxide} %% Presentation Title
 	\newcommand{\titleBackground}{2}    						%% Background graphic: 0 = no; 1 = yes; 2 = yes with more text space
@@
 \usepackage{upgreek}
+\usepackage{physics}
+\usepackage{xcolor}
+\newcommand{\red}[1]{\textcolor{red}{#1}}
 
@@
 %02. agenda
+%\begin{frame}{The Iterative Process}
+%	\begin{figure}
+%		\center
+%		\includegraphics[width=.8\textwidth]{figures/iteration.png}
+%	\end{figure}
+%\end{frame}
+\begin{graphicsFrame}{}{}{0.1}{}{iteration}{}\end{graphicsFrame}
+	\iffalse
 \begin{frame}{Agenda}
@@
 \end{frame}
+\fi
 	% - more like process  from beginning to finish
@@
 	% https://en.wikipedia.org/wiki/Copper_indium_gallium_selenide_solar_cell
+\iffalse
 \begin{graphicsFrame}{Copper Indium Gallium Selenide (CIGS)}{}{0.37}{left}{cigs}{U. Rau, H.W. Schock (2013) "Solar Cells"}
@@
 \end{graphicsFrame}
+\fi
 
@@
 
-\begin{graphicsFrame}{CIGS modules}{}{0.1}{}{cigs_mod}{}
+\begin{graphicsFrame}{Thin-Film Photovoltaics: CIGS modules}{}{0.1}{}{cigs_mod}{}
 \end{graphicsFrame}
@@
 		% Hu 2016 https://www.sciencedirect.com/science/article/abs/pii/S0272884216312548
-\begin{frame}{Recipes for Precursor Solutions}
+\begin{frame}{Adaption of Precursor Solutions Recipe}
 	\begin{figure}
@@
 	\end{figure}
-	\pause
+%	\pause
+\begin{table}[h]
+	\center
+	\begin{tabular}{lll}
+		\hline\hline
+		recipe	&original	&adapted \\
+		\hline
+		solvent & \ch{EtOEt} & \ch{BuOH} \\
+		precusor & \ch{Al(OPr^i)3} & \ch{Zr(OPr)4} \\
+		chelating agent & \ch{AcAc} & \ch{AcAc} \\
+		stabilzing agent & \ch{AcOH} & \ch{iPrOH}/\ch{AcOH}	\\
+		\hline\hline
+	\end{tabular}
+	%\caption{Composition of different buthanolic solutions}
+\end{table}
+\end{frame}
+%\iffalse
+\begin{frame}{Different Precusor Concentrations}
+	\begin{figure}
+		\includegraphics[width=.79\textwidth]{figures/huetal.png}
+	\end{figure}
 \begin{table}[h]
@@
 	\begin{tabular}{rlllll}
+		\hline\hline
+		&\red{1x}		&2x		&3x		&4x		&5x		\\
 		\hline
-		recipe	&1F		&2F		&3F		&4F		&5F		\\
-		\hline
-		\ch{BuOH} [ml]	&4.95	&4.9	&4.85	&4.8	&4.75	\\
-		\ch{ZrPro} [ml]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
-		\ch{AcAc} [ml]	&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
-		\ch{IPO}/\ch{AcOH} [ml]	&2		&2		&2		&2		&2		\\
-		\hline
+		\ch{BuOH} [ml]	&\red{4.95}	&4.9	&4.85	&4.8	&4.75	\\
+		\ch{ZrPro} [ml]	&\red{0.05}	&0.1	&0.15	&0.2	&0.25	\\
+		\ch{AcAc} [ml]	&\red{0.0125}	&0.025	&0.0375	&0.05	&0.0625	\\
+		\ch{IPO}/\ch{AcOH} [ml]	&\red{2}		&2		&2		&2		&2		\\
+		\hline\hline
 	\end{tabular}
@@
 \end{table}
+%\fi
 \end{frame}
@@
 	% - calcination 
-\begin{frame}{Tape casting and Calcination}
-	\begin{figure}
-		\center
-		\includegraphics[width=.65\textwidth]{figures/tc.jpg}
-	\end{figure}
-\end{frame}
+\begin{graphicsFrame}{Tape Casting and Calcination}{}{0.37}{left}{tc}{}
+
+		\vspace{1em}
+		\begin{itemize}
+			\item Tape Casting
+				\begin{itemize}
+					\item temperature: 40-\SI{80}{\degreeCelsius}
+					\item blade speed: 10-\SI{20}{\milli\meter/\second}
+				\end{itemize}
+				\vspace{1em}
+			\item Calcination
+				\begin{itemize}
+					\item temperature: 300-\SI{500}{\degreeCelsius}
+					\item heating rate: 2-\SI{12}{\degreeCelsius/\hour}
+				\end{itemize}
+		\end{itemize}
+\end{graphicsFrame}
+
+	% - SEM % check which sample 
+\begin{graphicsFrame}{Cross Section of \ch{ZrO2}}{}{0.37}{right}{sem_cs}{}
+	\vspace{3em}
+		\begin{itemize}
+			\item Scanning Electron Microscope 
+			\item substrate: FTO (Fluorine Doped Tin Oxide)
+			\item single layer of \ch{ZrO2}
+		\end{itemize}
+\end{graphicsFrame}
+
+%\begin{frame}{Tape casting and Calcination}
+%	\begin{figure}
+%		\center
+%		\includegraphics[width=.65\textwidth]{figures/tc.jpg}
+%	\end{figure}
+%\end{frame}
 %	\begin{itemize}
@@
 	% - measuring current-voltage characteristics
-\begin{frame}{Sputtering and I-V measurement}
+\iffalse
+\begin{frame}{Application of Contacts}
 	\begin{figure}
@@
 \end{frame}
+\fi
+%\begin{graphicsFrame}{Application of Contacts}{}{0.37}{right}{sample1}{}
+%		\begin{itemize}
+%			\item Left: Shadow mask
+%			\item Right: Steel substrate \ch{ZrO2} layer
+%		\end{itemize}
+%\end{graphicsFrame}
+%
+\begin{graphicsFrame}{Application of Contacts}{}{0.37}{left}{sput1}{}
+		\begin{itemize}
+			\item Bottom left: Shadow mask
+			\item Bottom right: Steel substrate \ch{ZrO2} layer
+			\item Top: samples with mask attached
+		\end{itemize}
+\end{graphicsFrame}
+%
+\begin{graphicsFrame}{Applied Contacts}{}{0.37}{right}{sample2}{}
+	\vspace{1em}
+		\begin{itemize}
+			\item passivated sample with array of contacts
+				\vspace{.5em}
+			\item contacts to steel on edges
+		\end{itemize}
+\end{graphicsFrame}
+%
+\begin{graphicsFrame}{Measuring Current Voltage Characteristics}{}{0.37}{left}{sample3}{}
+	\vspace{3em}
+		\begin{itemize}
+			\item left needle touches top contact (\ch{ZrO2})
+				\vspace{1.5em}
+			\item right needle touches bottom contact (steel)
+		\end{itemize}
+\end{graphicsFrame}
+
+	% - I-V % https://en.wikipedia.org/wiki/Current%E2%80%93voltage_characteristic
+\begin{graphicsFrame}{Current-Voltage characteristics}{}{0.37}{left}{iv-noi}{}
+	\vspace{2em}
+	\begin{itemize}
+		\item voltage sweep
+		\vspace{.5em}
+		\item \SI{10}{\milli\volt} steps
+		\vspace{.5em}
+		\item very low current 
+		\vspace{.5em}
+		\item low conductivity 
+		\vspace{.5em}
+		\item high resistance 
+	\end{itemize}
+\end{graphicsFrame}
+\begin{graphicsFrame}{Current-Voltage characteristics II}{}{0.37}{left}{iv-log}{}
+	\vspace{2em}
+	\begin{itemize}
+		\item all measurements of single sample
+		\vspace{.5em}
+		\item huge range 
+		\vspace{.5em}
+		\item low current
+		\vspace{.5em}
+		\item high current
+	\end{itemize}
+\end{graphicsFrame}
 
 %06. computational pipeline 
-\begin{frame}{Pin Hole Density and Leakage Current}
+\begin{graphicsFrame}
+	{Pin Hole Density and Leakage Current}
+	{}{0.37}
+	{left}{calc}{}
 	\vspace{2em}
 	\begin{itemize}
+		\item Conductivity
+			\begin{itemize}
+				\item $
+					g = \eval{\dv{I}{V}}_{V =0}
+					$
+			\end{itemize}
+	\vspace{0.5em}
+%	\pause
 		\item Pin Hole Density 
@@
 				\item $
-%	\rho = \frac{n_{-}}{(n_{-} + n_{+})}
-	\rho = \sum_i^N \frac{s_i}{N}
+	s_i = \begin{cases}
+		1 &\text{if} \quad g_i < 10^{-5} \\
+		0 &\text{if} \quad g_i \geq 10^{-5} \\
+%        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
+%        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
+	\end{cases}
 					$
 				\item $
-	s_i = \begin{cases}
-        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
-        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
-	\end{cases}
+	\rho = \sum_i^N \frac{s_i}{N}
 					$
@@
 	\vspace{0.5em}
+%	\pause
 		\item Leakage Current 
@@
 	\end{itemize}
-\end{frame}
+\end{graphicsFrame}
 	% - PSO + MARS = EMMA
@@
 \begin{graphicsFrame}{Particle Swarm Optimisation}{}{0.37}{right}{swarm}{}
-	\vspace{2em}
+	\vspace{3em}
 	\begin{itemize}
-		\item ispired by bird flocks and fish schools %# swarm intelligence
+		\item inspired by fish schools %# swarm intelligence
 		\item iterative process % nice bcs sample prep takes long time 
@@
 			\begin{itemize}
-				\item position 
+				\item input vars: position 
 				\item velocity
 			\end{itemize}
-		\item update model
+%		\item update model
 		\item R package \texttt{emma} 
@@
 
-\begin{frame}{PSO variables}
+\begin{frame}{Input Variables for Optimisation}
 \begin{table}[htb]
@@
 		\hline
+		\pause
 		2				&4		&40					&10				&300				&120	\\
@@
 %07. results measuring 
-	% - SEM % check which sample 
-\begin{graphicsFrame}{SEM micrographs}{}{0.37}{right}{sem}{}
-		\begin{itemize}
-			\item (a) first recipe on FTO
-			\item (b) 10 layers on steel
-			\item (c) cross section of 5 layers on FTO
-			\item (d) side view of scratched layer on steel
-		\end{itemize}
-\end{graphicsFrame}
-
-	% - I-V % https://en.wikipedia.org/wiki/Current%E2%80%93voltage_characteristic
-\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv1}{}\end{graphicsFrame}
-\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv2}{}\end{graphicsFrame}
-\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv3}{}\end{graphicsFrame}
+%\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv2}{}\end{graphicsFrame}
+%\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv3}{}\end{graphicsFrame}
 	% - EMMA 
 %08. results EMMA 
-\begin{frame}{Pin Hole Density}\begin{figure}\includegraphics[width=.66\textwidth]{figures/phd.png}\end{figure}\end{frame}
-\begin{frame}{Leakage Current}\begin{figure}\includegraphics[width=.66\textwidth]{figures/leakage.png}\end{figure}\end{frame}
+%\begin{frame}{Pin Hole Density}\begin{figure}\includegraphics[width=.66\textwidth]{figures/phd.png}\end{figure}\end{frame}
+%\begin{frame}{Leakage Current}\begin{figure}\includegraphics[width=.66\textwidth]{figures/leakage.png}\end{figure}\end{frame}
 \begin{frame}{PSO generations}\begin{figure}\includegraphics[width=.96\textwidth]{figures/emma-gen.png}\end{figure}\end{frame}
@@
 
+	\iffalse
 \begin{frame}{Comparison with Statistics}
@@
     \hline\hline
-        $\gamma$&  MAE(e)&   MSE(e)\\
+        $\gamma$&  MAE&   MSE\\
     \hline
@@
     \hline\hline
-        $\rho$&  MAE(e)&   MSE(e)\\
+        $\rho$&  MAE&   MSE\\
     \hline
@@
 \end{frame}
+\fi
 

### 2024-10-29 doc/presentations/defensio/defense.tex
final defense.tex

@@
 
-\begin{graphicsFrame}{Thin-Film Photovoltaics: CIGS modules}{}{0.1}{}{cigs_mod}{}
-\end{graphicsFrame}
+%\begin{graphicsFrame}{Thin-Film Photovoltaics: CIGS modules}{}{0.1}{}{cigs_mod}{}
+	\begin{frame}{Thin-Film Photovoltaics: CIGS modules}
+	\begin{itemize}
+		\item high absorption coefficient
+		\item connected in series 
+		\item substrate:
+			\begin{itemize}
+				\item must be insulating 
+				\item mostly glass
+			\end{itemize}
+	\end{itemize}
+	\begin{figure}
+		\includegraphics[width=.9\textwidth]{figures/cigs_mod.png}
+	\end{figure}
+\end{frame}
+%\end{graphicsFrame}
 
@@
 				\begin{itemize}
-					\item temperature: 40-\SI{80}{\degreeCelsius}
-					\item blade speed: 10-\SI{20}{\milli\meter/\second}
+					\item temperature: 40-80\SI{}{\degreeCelsius}
+					\item blade speed: 10-20\SI{}{\milli\meter/\second}
 				\end{itemize}
@@
 				\begin{itemize}
-					\item temperature: 300-\SI{500}{\degreeCelsius}
-					\item heating rate: 2-\SI{12}{\degreeCelsius/\hour}
+					\item temperature: 300-500\SI{}{\degreeCelsius}
+					\item heating rate: 2-18\SI{}{\degreeCelsius/\minute}
 				\end{itemize}
@@
 		\vspace{.5em}
-		\item \SI{10}{\milli\volt} steps
+		\item 10\SI{}{\milli\volt} steps
 		\vspace{.5em}
@@
 \begin{frame}{Input Variables for Optimisation}
+	\begin{itemize}
+		\item precursor solution concentration
+		\item number of layers 
+		\item coating temperature
+		\item blade speed
+		\item calcination temperature
+		\item calcination heating rate
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Input Variables for Optimisation}
 \begin{table}[htb]
@@
 		\hline\hline
-		$c_{zr}$ [\SI{22}{\milli\mol/\liter}]	&$n_L$	&$T_{C}$[\SI{}{\degreeCelsius}]	&$v_{C}$[\SI{}{\milli\meter/\second}]	&$T_{cal}$[\SI{}{\degreeCelsius}]	&$v_{cal}$[\SI{}{\degreeCelsius/\hour}]	\\
+		$c_{zr}$ [22\SI{}{\milli\mol/\liter}]	&$n_L$	&$T_{C}$[\SI{}{\degreeCelsius}]	&$v_{C}$[\SI{}{\milli\meter/\second}]	&$T_{cal}$[\SI{}{\degreeCelsius}]	&$v_{cal}$[\SI{}{\degreeCelsius/\minute}]	\\
 		\hline
-		\pause
-		2				&4		&40					&10				&300				&120	\\
-		3				&6		&50					&12				&400				&360	\\
-		4				&8		&60					&14				&500				&600	\\
-		5				&10		&70					&16				&					&840	\\
-						&12		&80					&18				&					&1080	\\
+%		\pause
+		2				&4		&40					&10				&300				&2	\\
+		3				&6		&50					&12				&400				&6	\\
+		4				&8		&60					&14				&500				&10	\\
+		5				&10		&70					&16				&					&14	\\
+						&12		&80					&18				&					&18	\\
 						&		&					&20				&					& \\
@@
 %\begin{frame}{Leakage Current}\begin{figure}\includegraphics[width=.66\textwidth]{figures/leakage.png}\end{figure}\end{frame}
-\begin{frame}{PSO generations}\begin{figure}\includegraphics[width=.96\textwidth]{figures/emma-gen.png}\end{figure}\end{frame}
+\begin{frame}{Particle Swarm Optimisation Iterations}
+	\begin{itemize}
+		\item metrics are reduced per generation
+		\item model learned to represent data
+	\end{itemize}
+	\begin{figure}
+		\includegraphics[width=.96\textwidth]{figures/emma-gen.png}
+	\end{figure}
+\end{frame}
+
 %\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
@@
 	\begin{itemize}
-		\item new recipe for dense \ch{ZrO2}
+		\item found recipe for dense \ch{ZrO2} via sol-gel
 			\vspace{.5em}
-		\item optimzed method with PSO
+		\item prepared insulating \ch{ZrO2} layers
+			\vspace{.5em}
+		\item optimization chose correct input variables
 	\end{itemize}

### 2024-10-30 doc/presentations/defensio/defense.tex
real final
remove commented out stuff

@@
 	%% ====== title page ======
-	\title{Particle Swarm Optimization for Passivation of Steel Substrate with Zirconium Oxide} %% Presentation Title
+	\title{Particle Swarm Optimization for Electrical Passivation of Steel Substrate Using Zirconium Oxide} %% Presentation Title
 	\newcommand{\titleBackground}{2}    						%% Background graphic: 0 = no; 1 = yes; 2 = yes with more text space
@@
 %% ====== Slides ======
-%TODO: - read aqua/good recipe/mars paper
-%01. title slide 
-	% - aufhänger
-	% - AI and PV
-	% - Lab or Computer 
-%02. agenda
-%\begin{frame}{The Iterative Process}
-%	\begin{figure}
-%		\center
-%		\includegraphics[width=.8\textwidth]{figures/iteration.png}
-%	\end{figure}
-%\end{frame}
 \begin{graphicsFrame}{}{}{0.1}{}{iteration}{}\end{graphicsFrame}
-	\iffalse
-\begin{frame}{Agenda}
-	\vspace{2em}
-	\begin{itemize}
-		\item Motivation: CIGS substrate
-		\item Methods: recipe and sample preparation
-		\item Calculation: PSO and data pipeline
-		\item Results: materials and optimisation
-	\end{itemize}
-\end{frame}
-\fi
-	% - more like process  from beginning to finish
-%03. background info
-	% - PV CIGS substrate % https://de.wikipedia.org/wiki/Chalkopyrit
-	% https://en.wikipedia.org/wiki/Copper_indium_gallium_selenide_solar_cell
-\iffalse
-\begin{graphicsFrame}{Copper Indium Gallium Selenide (CIGS)}{}{0.37}{left}{cigs}{U. Rau, H.W. Schock (2013) "Solar Cells"}
-\begin{table}
-	\resizebox{.95\textwidth}{!}{
-    \begin{tabular}{cccc}
-        \hline\hline
-		Empirical Formula&   Band Gap [\SI{}{\electronvolt}]\\
-        \hline
-		\ch{CuInSe2}&  1.04\\
-		\ch{CuGaSe2}&  1.7\\
-		\ch{CuInS2}&  1.5\\
-		\ch{CuGaS2}&  1.55\\
-        \hline\hline
-    \end{tabular}
-}
-    \caption{Band gaps of different chalcopyrites (K. Mertens 2015 "Photovoltaik")}
-\end{table}
-\end{graphicsFrame}
-\fi
 
-\iffalse
-\begin{textFrame}{Thin Film Solar Cell}{1}{}
-%	\begin{itemize}
-%		\item lorem
-%		\item ipsum
-%		\item \dots
-%	\end{itemize}
-\begin{table}[tbh]
-	\small
-    \center
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{cccccc}
-			\hline
-			\hline
-			Material&   Type&    Band Gap [\SI{}{\electronvolt}]&    $\lambda$ [\SI{}{\nano\meter}]&    Abs. coef. $\upalpha$ [\SI{}{\centi\meter^{-1}}]    &Penetration Depth [\SI{}{\micro\meter}]\\
-			\hline
-			c-Si&   indirect&   1.12&   600&    4000&    2.5\\
-			c-Si&   indirect&   1.12&   1000&    64&    150\\
-			c-Si&   indirect&   1.12&   1100&    3.5&    290\\
-			a-Si&   direct&      1.7&    600&    40000&  0.25\\
-			CdTe&   direct&      1.45&    600&    37000&  0.3\\
-			GaAs&   direct&      1.42&    600&    40000&  0.2\\
-			\hline
-			\hline
-		\end{tabular}
-	}
-    \caption{Photonic properties of several established PV materials (K. Mertens 2015 "Photovoltaik")}
-	\label{tab:cigs:alpha}
-\end{table}
-\end{textFrame}
-\fi
-
-%\begin{graphicsFrame}{Thin-Film Photovoltaics: CIGS modules}{}{0.1}{}{cigs_mod}{}
 \begin{frame}{Thin-Film Photovoltaics: CIGS modules}
@@
 \end{frame}
-%\end{graphicsFrame}
 
-%04. hypothesis 
-%05. manual methods
-	% - precursor solution preparation 
-		% Anwar 2017 https://iopscience.iop.org/article/10.1088/1757-899X/257/1/012087
-		% Hu 2016 https://www.sciencedirect.com/science/article/abs/pii/S0272884216312548
 \begin{frame}{Adaption of Precursor Solutions Recipe}
@@
 	\end{figure}
-%	\pause
+	\pause
 \begin{table}[h]
@@
 \end{frame}
-%\iffalse
+
 \begin{frame}{Different Precusor Concentrations}
@@
 \end{table}
-%\fi
 \end{frame}
 
-	% - doctor blading = tape castig 
-	% - calcination 
 \begin{graphicsFrame}{Tape Casting and Calcination}{}{0.37}{left}{tc}{}
-
 		\vspace{1em}
@@
 
-	% - SEM % check which sample 
 \begin{graphicsFrame}{Cross Section of \ch{ZrO2}}{}{0.37}{right}{sem_cs}{}
@@
 
-%\begin{frame}{Tape casting and Calcination}
-%	\begin{figure}
-%		\center
-%		\includegraphics[width=.65\textwidth]{figures/tc.jpg}
-%	\end{figure}
-%\end{frame}
-%	\begin{itemize}
-%		\item doctor blading construction 
-%		\item calcination infos (max temperatur, heating rate)
-%	\end{itemize}
-%\end{frame}
-	% - sputtering contacts
-	% - measuring current-voltage characteristics
-\iffalse
-\begin{frame}{Application of Contacts}
-	\begin{figure}
-		\includegraphics<1>[width=.63\textwidth]{figures/sample1.jpg}
-		\includegraphics<2>[width=.63\textwidth]{figures/sample2.jpg}
-		\includegraphics<3>[width=.63\textwidth]{figures/sample3.jpg}
-	\end{figure}
-\end{frame}
-\fi
-%\begin{graphicsFrame}{Application of Contacts}{}{0.37}{right}{sample1}{}
-%		\begin{itemize}
-%			\item Left: Shadow mask
-%			\item Right: Steel substrate \ch{ZrO2} layer
-%		\end{itemize}
-%\end{graphicsFrame}
-%
 \begin{graphicsFrame}{Application of Contacts}{}{0.37}{left}{sput1}{}
@@
 
-	% - I-V % https://en.wikipedia.org/wiki/Current%E2%80%93voltage_characteristic
 \begin{graphicsFrame}{Current-Voltage characteristics}{}{0.37}{left}{iv-noi}{}
@@
 \end{graphicsFrame}
+
 \begin{graphicsFrame}{Current-Voltage characteristics II}{}{0.37}{left}{iv-log}{}
@@
 	s_i = \begin{cases}
-		1 &\text{if} \quad g_i < 10^{-5} \\
-		0 &\text{if} \quad g_i \geq 10^{-5} \\
+		1 &\text{if} \quad g_i \geq 10^{-5} \\
+		0 &\text{if} \quad g_i < 10^{-5} \\
 %        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
@@
 \end{graphicsFrame}
-	% - PSO + MARS = EMMA
-	% PSO https://doi.org/10.1109/CEC.2010.5586165
+
 \begin{graphicsFrame}{Particle Swarm Optimisation}{}{0.37}{right}{swarm}{}
@@
 			\end{itemize}
-%		\item update model
+		\item next times step
 		\item R package \texttt{emma} 
@@
 
-%	\begin{itemize}
-%		\item Aluminium Contact through mask
-%		\item Silver paste
-%	\end{itemize}
-%\end{frame}
-%07. results measuring 
-%\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv2}{}\end{graphicsFrame}
-%\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv3}{}\end{graphicsFrame}
-	% - EMMA 
-%08. results EMMA 
-%\begin{frame}{Pin Hole Density}\begin{figure}\includegraphics[width=.66\textwidth]{figures/phd.png}\end{figure}\end{frame}
-%\begin{frame}{Leakage Current}\begin{figure}\includegraphics[width=.66\textwidth]{figures/leakage.png}\end{figure}\end{frame}
 \begin{frame}{Particle Swarm Optimisation Iterations}
@@
 
-%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
-%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
-%\begin{graphicsFrame}{Leakage Current}{}{0.1}{}{leakage_w}{}\end{graphicsFrame}
-%\begin{graphicsFrame}{Leakage Current}{}{-1}{}{leakage}{}\end{graphicsFrame}
-%\begin{graphicsFrame}{Leakage Current}{}{0.24}{right}{leakage}{}\end{graphicsFrame}
-%\begin{graphicsFrame}{Leakage Current}{}{0.37}{right}{leakage}{}\end{graphicsFrame}
-%\begin{graphicsFrame}{EMMA generations}{}{0.1}{}{emma-gen}{}\end{graphicsFrame}
-	% - gen 
-%09. comparison with other statistics 
-	% - comparing with other stats
-
-	\iffalse
-\begin{frame}{Comparison with Statistics}
-\begin{table}[htb]
-	\centering
-%	\resizebox{.95\textwidth}{!}{
-	\begin{tabular}{c cc }
-    \hline\hline
-        $\gamma$&  MAE&   MSE\\
-    \hline
-		PSO&   \textbf{10}& 171\\
-        LR&    13& 250\\
-        KRR &17 &548 \\
-        SVM& 15&  415\\
-    \hline\hline
-	\end{tabular}
-%}
-	\pause
-%	\vspace{1em}
-%	\resizebox{.95\textwidth}{!}{
-	\begin{tabular}{c cc cc cc cc}
-    \hline\hline
-        $\rho$&  MAE&   MSE\\
-    \hline
-		PSO&   \textbf{0.14}&   0.03\\
-        LR&    0.19&   0.06\\
-        KRR &0.25 &0.12 \\
-        SVM &0.23 &0.13 \\
-    \hline\hline
-	\end{tabular}
-%}
-%    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
-	\label{tab:post-emma}
-\end{table}
-\end{frame}
-\fi
-
-\iffalse
-\begin{frame}{Comparison with Statistics}
-\begin{table}[htb]
-	\centering
-	\resizebox{.95\textwidth}{!}{
-	\begin{tabular}{c cc cc cc cc}
-    \hline\hline
-        $\gamma$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
-    \hline
-        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
-        LR&    13& 250&    24& 747&    34& 1327&   17& 454\\
-        KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
-        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
-        \hline
-%    \hline\hline
-	\end{tabular}
-}
-	\vspace{1em}
-	\resizebox{.95\textwidth}{!}{
-	\begin{tabular}{c cc cc cc cc}
-    \hline\hline
-        $\rho$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
-    \hline
-        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
-        LR&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
-        KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
-        SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
-    \hline\hline
-	\end{tabular}
-}
-    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
-	\label{tab:post-emma}
-\end{table}
-\end{frame}
-\fi
-
-%10. summary 
 \begin{frame}{Summary}
+	\center
 	\vspace{2em}
